### 2022-06-24 manuscript/appendix-A-lexical-covariates.Rmd
24062022

# Appendix A: Selection of lexical covariates {#appendix-A-lexical-covariates}

```{r}

# This appendix inherits the libraries, the working directory and the
# data sets loaded in manuscript.Rmd, when the latter is knitted.

```

Lexical covariates are usually used in conceptual processing studies due to the widespread connections among lexical and semantic variables. Including these covariates---or nuisance variables---in the model allows a more rigorous analysis of the predictors of interest [@sassenhagenCommonMisapplicationStatistical2016].

In each study, the covariates were selected out of a group of 5 variables that had been used as covariates in @wingfieldUnderstandingRoleLinguistic2022, and are widely used [e.g., @petilli2021a]. Some of these covariates were highly intercorrelated ($r$ > .70), as shown below. To avoid the problem of multicollinearity, the maximum zero-order correlation allowed between any two covariates was of $r$ = $\pm$.70 [@dormannCollinearityReviewMethods2013; @harrison2018a]. In cases of higher correlations, the covariate with the largest effect in the model, based on the estimate ($\upbeta$), was selected.

In Studies 1 (semantic priming) and 2 (semantic decision), the lexical covariates were selected out of five variables, which mirrored those used by @wingfieldUnderstandingRoleLinguistic2022: namely, number of letters (i.e., orthographic length, which we computed in R), word frequency, number of syllables  [both the latter from @balota2007a], orthographic Levenshtein distance [@yarkoniMovingColtheartNew2008] and phonological Levenshtein distance [@suarezObservingNeighborhoodEffects2011]. In Study 3 (lexical decision), the procedure was identical except that word frequency could not be selected as a covariate because it constituted a predictor of interest, specifically corresponding to linguistic information (for details, see Study 3 in the main article).

All the models included by-participant and by-word random intercepts, as well as by-participant random slopes for every predictor. Below, the correlations and the selection model are shown for each study.

## Study 1: Semantic priming

All lexical covariates considered in the semantic priming study were based on the target words. Figure \@ref(fig:semanticpriming-lexical-covariates-correlations) shows the zero-order correlations among the lexical covariates considered in the selection.

```{r semanticpriming-lexical-covariates-correlations, fig.cap = 'Zero-order correlations among lexical covariates pretested in the semantic priming study.', fig.width = 6, fig.height = 3.5, out.width = '50%'}

# Using the following variables...
semanticpriming[, c('z_target_word_frequency', 'z_target_length', 
                    'z_target_number_syllables',
                    'z_target_phonological_Levenshtein_distance', 
                    'z_target_orthographic_Levenshtein_distance')] %>%

  # renamed for the sake of clarity
  rename('Word frequency' = z_target_word_frequency,
         'Number of letters' = z_target_length,
         'Number of syllables' = z_target_number_syllables,
         'Phonological Levenshtein distance' = z_target_phonological_Levenshtein_distance,
         'Orthographic Levenshtein distance' = z_target_orthographic_Levenshtein_distance) %>%

  # make correlation matrix (custom function from 'R_functions' folder)
  correlation_matrix() + 
  theme(plot.margin = unit(c(0, -0.5, 0.05, -3.78), 'in'))

```

Table \@ref(tab:semanticpriming-lexical-covariates-selection) shows the results of the selection model.

```{r semanticpriming-lexical-covariates-selection, results = 'asis'}

# Read in model and confidence intervals
KR_summary_lexical_covariates_selection_semanticpriming_lmerTest = 
  readRDS('semanticpriming/frequentist_analysis/lexical_covariates_selection/results/KR_summary_lexical_covariates_selection_semanticpriming_lmerTest.rds')

confint_lexical_covariates_selection_semanticpriming_lmerTest = 
  readRDS('semanticpriming/frequentist_analysis/lexical_covariates_selection/results/confint_lexical_covariates_selection_semanticpriming_lmerTest.rds')

# Rename effects in plain language...
# first, in the summary object
rownames(KR_summary_lexical_covariates_selection_semanticpriming_lmerTest$coefficients) =
  rownames(KR_summary_lexical_covariates_selection_semanticpriming_lmerTest$coefficients) %>%
  str_replace(pattern = 'z_target_word_frequency', 
              replacement = 'Word frequency') %>%
  str_replace(pattern = 'z_target_length', 
              replacement = 'Number of letters') %>%
  str_replace(pattern = 'z_target_number_syllables', 
              replacement = 'Number of syllables') %>%
  str_replace(pattern = 'z_target_phonological_Levenshtein_distance', 
              replacement = 'Phonological Levenshtein distance') %>%
  str_replace(pattern = 'z_target_orthographic_Levenshtein_distance',
              replacement = 'Orthographic Levenshtein distance')

# next, in the confidence intervals object
rownames(confint_lexical_covariates_selection_semanticpriming_lmerTest) =
  rownames(confint_lexical_covariates_selection_semanticpriming_lmerTest) %>%
  str_replace(pattern = 'z_target_word_frequency', 
              replacement = 'Word frequency') %>%
  str_replace(pattern = 'z_target_length', 
              replacement = 'Number of letters') %>%
  str_replace(pattern = 'z_target_number_syllables', 
              replacement = 'Number of syllables') %>%
  str_replace(pattern = 'z_target_phonological_Levenshtein_distance', 
              replacement = 'Phonological Levenshtein distance') %>%
  str_replace(pattern = 'z_target_orthographic_Levenshtein_distance',
              replacement = 'Orthographic Levenshtein distance')

# Create table (using custom function from the 'R_functions' folder)
frequentist_model_table(
  KR_summary_lexical_covariates_selection_semanticpriming_lmerTest, 
  confidence_intervals = confint_lexical_covariates_selection_semanticpriming_lmerTest,
  caption = 'Mixed-effects model for the selection of lexical covariates in the semantic priming study.') %>% 
  # Place table close to designated position
  kable_styling(latex_options = 'HOLD_position') %>%

  # Footnote describing abbreviations, random slopes, etc. 
  # LaTeX code used to format the text.
  footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on z-scored variables; \\\\textit{SE} = standard error;',
                           'CI = confidence interval. By-participant random slopes were included for',
                           'every effect.', 
                           # Begin lines after first one with a dot-sized indent
                           sep = ' \\\\linebreak \\\\phantom{.}'))

```

Considering the maximum correlation allowed ($r$ = $\pm$.70) and the results of the model, the variables that will be included as covariates in the main analysis are word frequency and number of syllables.

## Study 2: Semantic decision

Figure \@ref(fig:semanticdecision-lexical-covariates-correlations) shows the zero-order correlations among the lexical covariates considered in the selection.

```{r semanticdecision-lexical-covariates-correlations, fig.cap = 'Zero-order correlations for the lexical covariates pretested in the semantic decision study.', fig.width = 6, fig.height = 3.5, out.width = '50%'}

# Using the following variables...
semanticdecision[, c('z_word_frequency', 'z_word_length', 'z_number_syllables',
                     'z_phonological_Levenshtein_distance', 
                     'z_orthographic_Levenshtein_distance')] %>%

  # renamed for the sake of clarity
  rename('Word frequency' = z_word_frequency,
         'Number of letters' = z_word_length,
         'Number of syllables' = z_number_syllables,
         'Phonological Levenshtein distance' = z_phonological_Levenshtein_distance,
         'Orthographic Levenshtein distance' = z_orthographic_Levenshtein_distance) %>%

  # make correlation matrix (custom function from 'R_functions' folder)
  correlation_matrix() + 
  theme(plot.margin = unit(c(0, -0.5, 0.05, -3.78), 'in'))

```

Table \@ref(tab:semanticdecision-lexical-covariates-selection) shows the results of the selection model.

```{r semanticdecision-lexical-covariates-selection, results = 'asis'}

# Read in model and confidence intervals
KR_summary_lexical_covariates_selection_semanticdecision_lmerTest = 
  readRDS('semanticdecision/frequentist_analysis/lexical_covariates_selection/results/KR_summary_lexical_covariates_selection_semanticdecision_lmerTest.rds')

confint_lexical_covariates_selection_semanticdecision_lmerTest = 
  readRDS('semanticdecision/frequentist_analysis/lexical_covariates_selection/results/confint_lexical_covariates_selection_semanticdecision_lmerTest.rds')

# Rename effects in plain language...
# first, in the summary object
rownames(KR_summary_lexical_covariates_selection_semanticdecision_lmerTest$coefficients) =
  rownames(KR_summary_lexical_covariates_selection_semanticdecision_lmerTest$coefficients) %>%
  str_replace(pattern = 'z_word_frequency', 
              replacement = 'Word frequency') %>%
  str_replace(pattern = 'z_word_length', 
              replacement = 'Number of letters') %>%
  str_replace(pattern = 'z_number_syllables', 
              replacement = 'Number of syllables') %>%
  str_replace(pattern = 'z_orthographic_Levenshtein_distance',
              replacement = 'Orthographic Levenshtein distance') %>%
  str_replace(pattern = 'z_phonological_Levenshtein_distance', 
              replacement = 'Phonological Levenshtein distance')

# next, in the confidence intervals object
rownames(confint_lexical_covariates_selection_semanticdecision_lmerTest) =
  rownames(confint_lexical_covariates_selection_semanticdecision_lmerTest) %>%
  str_replace(pattern = 'z_word_frequency', 
              replacement = 'Word frequency') %>%
  str_replace(pattern = 'z_word_length', 
              replacement = 'Number of letters') %>%
  str_replace(pattern = 'z_number_syllables', 
              replacement = 'Number of syllables') %>%
  str_replace(pattern = 'z_orthographic_Levenshtein_distance',
              replacement = 'Orthographic Levenshtein distance') %>%
  str_replace(pattern = 'z_phonological_Levenshtein_distance', 
              replacement = 'Phonological Levenshtein distance')

# Create table (using custom function from the 'R_functions' folder)
frequentist_model_table(
  KR_summary_lexical_covariates_selection_semanticdecision_lmerTest, 
  confidence_intervals = confint_lexical_covariates_selection_semanticdecision_lmerTest,
  caption = 'Mixed-effects model for the selection of lexical covariates in the semantic decision study.') %>% 
  # Place table close to designated position
  kable_styling(latex_options = 'HOLD_position') %>%

  # Footnote describing abbreviations, random slopes, etc. 
  # LaTeX code used to format the text.
  footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on z-scored variables; \\\\textit{SE} = standard error;',
                           'CI = confidence interval. By-participant random slopes were included for',
                           'every effect.', 
                           # Begin lines after first one with a dot-sized indent
                           sep = ' \\\\linebreak \\\\phantom{.}'))

```

Considering the maximum correlation allowed ($r$ = $\pm$.70) and the results of the model, the variables that will be included as covariates in the main analysis are word frequency and orthographic Levenshtein distance.

## Study 3: Lexical decision

Figure \@ref(fig:lexicaldecision-lexical-covariates-correlations) shows the zero-order correlations among the lexical covariates considered in the selection.

```{r lexicaldecision-lexical-covariates-correlations, fig.cap = 'Zero-order correlations for the lexical covariates pretested in the lexical decision study.', fig.width = 6, fig.height = 3.5, out.width = '50%'}

# Using the following variables...
lexicaldecision[, c('z_word_frequency', 'z_word_length', 'z_number_syllables',
                     'z_phonological_Levenshtein_distance', 
                     'z_orthographic_Levenshtein_distance')] %>%

  # renamed for the sake of clarity
  rename('Word frequency' = z_word_frequency,
         'Number of letters' = z_word_length,
         'Number of syllables' = z_number_syllables,
         'Phonological Levenshtein distance' = z_phonological_Levenshtein_distance,
         'Orthographic Levenshtein distance' = z_orthographic_Levenshtein_distance) %>%

  # Use plain names and specify

  # make correlation matrix (custom function from 'R_functions' folder)
  correlation_matrix() + 
  theme(plot.margin = unit(c(0, 0, 0.05, -4.26), 'in'))

```

Table \@ref(tab:lexicaldecision-lexical-covariates-selection) shows the results of the selection model.

```{r lexicaldecision-lexical-covariates-selection, results = 'asis'}

# Read in model and confidence intervals
KR_summary_lexical_covariates_selection_lexicaldecision_lmerTest = 
  readRDS('lexicaldecision/frequentist_analysis/lexical_covariates_selection/results/KR_summary_lexical_covariates_selection_lexicaldecision_lmerTest.rds')

confint_lexical_covariates_selection_lexicaldecision_lmerTest = 
  readRDS('lexicaldecision/frequentist_analysis/lexical_covariates_selection/results/confint_lexical_covariates_selection_lexicaldecision_lmerTest.rds')

# Rename effects in plain language...
# first, in the summary object
rownames(KR_summary_lexical_covariates_selection_lexicaldecision_lmerTest$coefficients) =
  rownames(KR_summary_lexical_covariates_selection_lexicaldecision_lmerTest$coefficients) %>%
  str_replace(pattern = 'z_word_frequency', 
              replacement = 'Word frequency') %>%
  str_replace(pattern = 'z_word_length', 
              replacement = 'Number of letters') %>%
  str_replace(pattern = 'z_number_syllables', 
              replacement = 'Number of syllables') %>%
  str_replace(pattern = 'z_orthographic_Levenshtein_distance',
              replacement = 'Orthographic Levenshtein distance') %>%
  str_replace(pattern = 'z_phonological_Levenshtein_distance', 
              replacement = 'Phonological Levenshtein distance')

# next, in the confidence intervals object
rownames(confint_lexical_covariates_selection_lexicaldecision_lmerTest) =
  rownames(confint_lexical_covariates_selection_lexicaldecision_lmerTest) %>%
  str_replace(pattern = 'z_word_frequency', 
              replacement = 'Word frequency') %>%
  str_replace(pattern = 'z_word_length', 
              replacement = 'Number of letters') %>%
  str_replace(pattern = 'z_number_syllables', 
              replacement = 'Number of syllables') %>%
  str_replace(pattern = 'z_orthographic_Levenshtein_distance',
              replacement = 'Orthographic Levenshtein distance') %>%
  str_replace(pattern = 'z_phonological_Levenshtein_distance', 
              replacement = 'Phonological Levenshtein distance')

# Create table (using custom function from the 'R_functions' folder)
frequentist_model_table(
  KR_summary_lexical_covariates_selection_lexicaldecision_lmerTest, 
  confidence_intervals = confint_lexical_covariates_selection_lexicaldecision_lmerTest,
  caption = 'Mixed-effects model for the selection of lexical covariates in the lexical decision study.') %>% 
  # Place table close to designated position
  kable_styling(latex_options = 'HOLD_position') %>%

  # Footnote describing abbreviations, random slopes, etc. 
  # LaTeX code used to format the text.
  footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on z-scored variables; \\\\textit{SE} = standard error;',
                           'CI = confidence interval. By-participant random slopes were included for',
                           'every effect.', 
                           # Begin lines after first one with a dot-sized indent
                           sep = ' \\\\linebreak \\\\phantom{.}'))

```

Considering the maximum correlation allowed ($r$ = $\pm$.70), the results of the model, and the use of word frequency as a predictor of interest in the model, the variable that will be included as a covariate in the main analysis is orthographic Levenshtein distance.

## Conclusion

Word frequency presented the largest effect in the three models. Orthographic Levenshtein distance was the second largest effect in the semantic decision and the lexical decision studies, whereas its phonological counterpart was not significant in any of the studies. The latter difference makes sense, as participants read the stimulus words in the three studies [@brysbaertWordRecognitionII2022].

### 2022-06-24 manuscript/appendix-B-frequentist-analysis-diagnostics.Rmd
24062022

# Appendix B: Diagnostics for the frequentist analyses {#appendix-B-frequentist-analysis-diagnostics}

```{r}

# This appendix inherits the libraries, the working directory and the
# data sets loaded in manuscript.Rmd, when the latter is knitted.

```

Below, the convergence warnings and the non-normal residuals are first addressed generally, and then in more detail in the context of each study.

## Lack of convergence

The challenge of convergence is well known in the area of mixed-effects models. The solutions proposed range from the removal of random slopes under certain conditions [@matuschekBalancingTypeError2017] to the maintenance of random slopes in spite of convergence warnings, which seeks to avoid an inflation of the Type I error caused by non-independence in the data [@brauer2018a; @singmann2019a].

### The multiple-optimizers sanity check from `lme4::allFit()`

Framed within the drive to maintain random slopes wherever possible, the developers of the 'lme4' package propose a sanity check that uses a part of the 'lme4' *engine* called 'optimizer'. Every model has a default optimizer, unless a specific one is chosen through `control = lmerControl(optimizer = '...')` (in `lmer` models) or `control = glmerControl(optimizer = '...')` (in `glmer` models). The 7 widely-available optimizers are:

- bobyqa
- Nelder_Mead
- nlminbwrap
- nmkbw
- optimx.L-BFGS-B
- nloptwrap.NLOPT_LN_NELDERMEAD
- nloptwrap.NLOPT_LN_BOBYQA

To assess whether convergence warnings render the results invalid, or on the contrary, the results can be deemed valid in spite of the warnings, @batesPackageLme42021 suggest refitting models affected by convergence warnings with a variety of optimizers. The authors argue that if the different optimizers produce practically-equivalent results, the results are valid. For this purpose, the 'allFit' function from the 'lme4' package allows the refitting of models using a number of optimizers. To use the 7 optimizers listed above, two extra packages were installed: 'dfoptim' and 'optimx' (see [lme4 manual](https://cran.r-project.org/web/packages/lme4/lme4.pdf)). The output from 'allFit' contains several statistics on the fixed and the random effects fitted by each optimizer (see [example](https://github.com/lme4/lme4/issues/512#issue-425198940)).

The severity of convergence problems in each study will be examined below using the 'allFit' function from the 'lme4' package.

## Residual errors not normally distributed

The residuals of the linear mixed-effects models in all three studies violated the assumption of normality. Even though linear mixed-effects models tend to be quite robust to deviations from normality [@kniefViolatingNormalityAssumption2021; @schielzethRobustnessLinearMixed2020], we sought to verify our results. To this end, two robust models were performed in each study, as described below.

### Method A: *robustlmm* model

The first method uses the R package 'robustlmm' v2.4-4 [@R-robustlmm]. To calculate the p values, we followed the procedure of @sleegersPupillometryHindsightBias2021, but used the Kenward-Roger method instead of Satterthwaite [see @luke2017a].

### Method B: Inverse Gaussian model with identity link function

We followed a method proposed by @loTransformNotTransform2015, based on generalized linear mixed-effects models (GLMM) implementing an identity link function. According to @loTransformNotTransform2015, the link function helps avoid directly transforming the dependent variable, which can hinder the interpretability of the results [also see @kniefViolatingNormalityAssumption2021].

GLMMs require the use of families of distributions. @loTransformNotTransform2015 tested the Gaussian, Gamma and Inverse Gaussian families, with either an identity or an inverse link function. The authors found that the Inverse Gaussian family with an identity link yielded the most normal residuals. The Inverse Gaussian and the Gamma families only accept positive values in the outcome variable [see Table 15.2 in @foxGeneralizedLinearModels2016]. Due to this restriction, the dependent variable in the present model is raw RT, unlike the standardised RT that was used in the main analysis.

*P* values were to be calculated through parametric bootstrapping, which is the most robust method for GLMMs, as the Kenward-Roger and Satterthwaite methods are not available for these models [@luke2017a; @R-afex].

Neither Method A nor Method B could finally be used, as the code produced errors. These errors are shown in the corresponding scripts inside the 'model_diagnostics' folder in each study. Nonetheless, the residuals are shown below.

## Study 1: Semantic priming

### Lack of convergence

In the initial model, the optimizer used (the default one in 'lmerTest') was '`r semanticpriming_lmerTest@optinfo$optimizer`', and the convergence warning read: '`r semanticpriming_lmerTest@optinfo$conv$lme4$messages`'.

Based on the reanalysis using 7 optimizers, Figure \@ref(fig:main-effects-semanticpriming-allFit-convergence) shows the fixed, main effects, and Figure \@ref(fig:interactions-semanticpriming-allFit-convergence) shows the fixed interactions.

```{r main-effects-semanticpriming-allFit-convergence, fig.cap = 'Fixed, main effects from the semantic priming study fitted by 7 optimizers.'}

# Display plot, which was produced in advance due to memory overload. Code available at:
# semanticpriming/frequentist_analysis/model_diagnostics/semanticpriming_allFit_convergence.R

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticpriming/frequentist_analysis/model_diagnostics/plots/main_effects_semanticpriming_allFit_convergence.png'
  ))

```

```{r interactions-semanticpriming-allFit-convergence, fig.cap = 'Fixed interaction effects from the semantic priming study fitted by 7 optimizers.'}

# Display plot, which was produced in advance due to memory overload. Code available at:
# semanticpriming/frequentist_analysis/model_diagnostics/semanticpriming_allFit_convergence.R

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticpriming/frequentist_analysis/model_diagnostics/plots/interactions_semanticpriming_allFit_convergence.png'
  ))

```

### Residual errors not normally distributed

Figure \@ref(fig:semanticpriming-residuals) shows the deviation from normality of the residuals of the linear mixed-effects model.

```{r semanticpriming-residuals, fig.cap = 'Residuals of the linear mixed-effects model from the semantic priming study. \\linebreak KS = Kolmogorov-Smirnov test; TS = tail-sensitive confidence bands.', out.width = '65%'}

# Display plot, which was produced in advance due to memory overload. Code available at:
# semanticpriming/frequentist_analysis/model_diagnostics/semanticpriming_residuals.R

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticpriming/frequentist_analysis/model_diagnostics/plots/semanticpriming_residuals.png'
  ))

```

### Semantic priming model including visual similarity

#### Convergence

In the initial model, the optimizer used (the default one in 'lmerTest') was '`r semanticpriming_with_visualsimilarity_lmerTest@optinfo$optimizer`', and the convergence warning read: '`r semanticpriming_with_visualsimilarity_lmerTest@optinfo$conv$lme4$messages`'.

Based on the reanalysis using 7 optimizers, Figure \@ref(fig:main-effects-semanticpriming-with-visualsimilarity-allFit-convergence) shows the fixed, main effects, and Figure \@ref(fig:interactions-semanticpriming-with-visualsimilarity-allFit-convergence) shows the fixed interactions.

```{r main-effects-semanticpriming-with-visualsimilarity-allFit-convergence, fig.cap = 'Fixed, main effects from the semantic priming study fitted by 7 optimizers.'}

# Display plot, which was produced in advance due to memory overload. Code available at:
# semanticpriming/analysis_with_visualsimilarity/model_diagnostics/semanticpriming_with_visualsimilarity_allFit_convergence.R

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticpriming/analysis_with_visualsimilarity/model_diagnostics/plots/main_effects_semanticpriming_with_visualsimilarity_allFit_convergence.png'
  ))

```

```{r interactions-semanticpriming-with-visualsimilarity-allFit-convergence, fig.cap = 'Fixed interaction effects from the semantic priming study fitted by 7 optimizers.'}

# Display plot, which was produced in advance due to memory overload. Code available at:
# semanticpriming/analysis_with_visualsimilarity/model_diagnostics/semanticpriming_with_visualsimilarity_allFit_convergence.R

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticpriming/analysis_with_visualsimilarity/model_diagnostics/plots/interactions_semanticpriming_with_visualsimilarity_allFit_convergence.png'
  ))

```

#### Residual errors not normally distributed

Figure \@ref(fig:semanticpriming-with-visualsimilarity-residuals) shows the deviation from normality of the residuals of the linear mixed-effects model.

```{r semanticpriming-with-visualsimilarity-residuals, fig.cap = 'Residuals of the linear mixed-effects model from the semantic priming study. \\linebreak KS = Kolmogorov-Smirnov test; TS = tail-sensitive confidence bands.', out.width = '65%'}

# Display plot, which was produced in advance due to memory overload. Code available at:
# semanticpriming/analysis_with_visualsimilarity/model_diagnostics/semanticpriming_with_visualsimilarity_residuals.R

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticpriming/analysis_with_visualsimilarity/model_diagnostics/plots/semanticpriming_with_visualsimilarity_residuals.png'
  ))

```

## Study 2: Semantic decision

### Convergence

In the initial model, the optimizer used (the default one in 'lmerTest') was '`r semanticdecision_lmerTest@optinfo$optimizer`', and the convergence warning read: '`r semanticdecision_lmerTest@optinfo$conv$lme4$messages`'.

Based on the reanalysis using 7 optimizers, Figure \@ref(fig:main-effects-semanticdecision-allFit-convergence) shows the fixed, main effects, and Figure \@ref(fig:interactions-semanticdecision-allFit-convergence) shows the fixed interactions.

```{r main-effects-semanticdecision-allFit-convergence, fig.cap = 'Fixed, main effects from the semantic decision study fitted by 7 optimizers.'}

# Display plot, which was produced in advance due to memory overload. Code available at:
# semanticdecision/frequentist_analysis/model_diagnostics/semanticdecision_allFit_convergence.R

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticdecision/frequentist_analysis/model_diagnostics/plots/main_effects_semanticdecision_allFit_convergence.png'
  ))

```

```{r interactions-semanticdecision-allFit-convergence, fig.cap = 'Fixed interaction effects from the semantic decision study fitted by 7 optimizers.'}

# Display plot, which was produced in advance due to memory overload. Code available at:
# semanticdecision/frequentist_analysis/model_diagnostics/semanticdecision_allFit_convergence.R

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticdecision/frequentist_analysis/model_diagnostics/plots/interactions_semanticdecision_allFit_convergence.png'
  ))

```

### Residual errors not normally distributed

Figure \@ref(fig:semanticdecision-residuals) shows the deviation from normality of the residuals.

```{r semanticdecision-residuals, fig.cap = 'Residuals of the linear mixed-effects model from the semantic decision study. \\linebreak KS = Kolmogorov-Smirnov test; TS = tail-sensitive confidence bands.', out.width = '65%'}

# Display plot, which was produced in advance due to memory overload. Code available at:
# semanticdecision/frequentist_analysis/model_diagnostics/semanticdecision_residuals.R

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticdecision/frequentist_analysis/model_diagnostics/plots/semanticdecision_residuals.png'
  ))

```

## Study 3: Lexical decision

### Convergence

In the initial model, the optimizer used (the default one in 'lmerTest') was '`r lexicaldecision_lmerTest@optinfo$optimizer`', and the convergence warning read: '`r lexicaldecision_lmerTest@optinfo$conv$lme4$messages`'.

Based on the reanalysis using 7 optimizers, Figure \@ref(fig:main-effects-lexicaldecision-allFit-convergence) shows the fixed, main effects, and Figure \@ref(fig:interactions-lexicaldecision-allFit-convergence) shows the fixed interactions.

```{r main-effects-lexicaldecision-allFit-convergence, fig.cap = 'Fixed, main effects from the lexical decision study fitted by 7 optimizers.'}

# Display plot, which was produced in advance due to memory overload. Code available at:
# lexicaldecision/frequentist_analysis/model_diagnostics/lexicaldecision_allFit_convergence.R

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/lexicaldecision/frequentist_analysis/model_diagnostics/plots/main_effects_lexicaldecision_allFit_convergence.png'
  ))

```

```{r interactions-lexicaldecision-allFit-convergence, fig.cap = 'Fixed interaction effects from the lexical decision study fitted by 7 optimizers.'}

# Display plot, which was produced in advance due to memory overload. Code available at:
# lexicaldecision/frequentist_analysis/model_diagnostics/lexicaldecision_allFit_convergence.R

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/lexicaldecision/frequentist_analysis/model_diagnostics/plots/interactions_lexicaldecision_allFit_convergence.png'
  ))

```

### Residual errors not normally distributed

Figure \@ref(fig:lexicaldecision-residuals) shows the deviation from normality of the residuals.

```{r lexicaldecision-residuals, fig.cap = 'Residuals of the linear mixed-effects model from the lexical decision study. The outliers in the residuals deviate from the coloured areas indicating an acceptable normality. \\linebreak KS = Kolmogorov-Smirnov test; TS = tail-sensitive confidence bands.', out.width = '65%'}

# Display plot, which was produced in advance due to memory overload. Code available at:
# lexicaldecision/frequentist_analysis/model_diagnostics/lexicaldecision_residuals.R

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/lexicaldecision/frequentist_analysis/model_diagnostics/plots/lexicaldecision_residuals.png'
  ))

```

### 2022-06-24 manuscript/appendix-C-Bayesian-analysis-diagnostics.Rmd
24062022

# Appendix C: Diagnostics for the Bayesian analyses {#appendix-C-Bayesian-analysis-diagnostics}

```{r}

# This appendix inherits the libraries, the working directory and the
# data sets loaded in manuscript.Rmd, when the latter is knitted.

```

This appendix presents diagnostics for the Bayesian analyses. In each study, prior predictive checks are presented before posterior predictive checks. Furthermore, in each of these checks, the models presented first have the default Gaussian distribution, whereas the next series have an exponentially modified Gaussian (dubbed 'ex-Gaussian') distribution with an identity link function (for details, see the section titled 'Distributions and prior predictive checks' in the main article). Eyeball estimation is used to assess the outcomes of these checks [for background on predictive checks and for alternative estimation procedures, see @gelmanPosteriorPredictiveAssessment1996; @moranPosteriorPredictiveNull2021; @schootBayesianStatisticsModelling2021]. One diagnostic not shown in this appendix is the $\widehat R$, which is shown in [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results) instead.

## Study 1: Semantic priming {#study1-bayesian-diagnostics}

### Prior predictive checks

Figures \@ref(fig:semanticpriming-priorpredictivecheck-informativepriors), \@ref(fig:semanticpriming-priorpredictivecheck-weaklyinformativepriors) and \@ref(fig:semanticpriming-priorpredictivecheck-diffusepriors) show the prior predictive checks for the Gaussian models. These plots show the maximum, mean and minimum values of the observed data ($y$) and those of the predicted distribution ($y_{rep}$, which stands for *rep*lications of the outcome). The way of interpreting these plots is by comparing the observed data to the predicted distribution. The specifics of this vary across the three plots in the series. Firstly, in the upper plot, which shows the maximum values, the ideal scenario would have the observed ($y$) value overlapping with the maximum value of the predicted distribution ($y_{rep}$). Secondly, in the middle plot, showing the mean values, the ideal scenario would show the observed ($y$) value overlapping with the mean value of the predicted distribution ($y_{rep}$). Lastly, in the lower plot, which shows the minimum values, the ideal scenario would have the observed ($y$) value overlapping with the minimum value of the predicted distribution ($y_{rep}$). The overlap need not be absolute but the closer the observed and the predicted values on the X axis, the better. As such, the three predictive checks below---corresponding to models that used the default Gaussian distribution---show that the priors fitted the data acceptably but not very well.

(ref:semanticpriming-priorpredictivecheck-informativepriors) Prior predictive checks for the Gaussian, informative prior model from the semantic priming study. $y$ = observed data; $y_{rep}$ = predicted data.

```{r semanticpriming-priorpredictivecheck-informativepriors, fig.cap = '(ref:semanticpriming-priorpredictivecheck-informativepriors)', out.width = '80%'}

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_informativepriors.pdf'
  ))

```

(ref:semanticpriming-priorpredictivecheck-weaklyinformativepriors) Prior predictive checks for the Gaussian, weakly-informative prior model from the semantic priming study. $y$ = observed data; $y_{rep}$ = predicted data.

```{r semanticpriming-priorpredictivecheck-weaklyinformativepriors, fig.cap = '(ref:semanticpriming-priorpredictivecheck-weaklyinformativepriors)', out.width = '80%'}

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_weaklyinformativepriors.pdf'
  ))

```

(ref:semanticpriming-priorpredictivecheck-diffusepriors) Prior predictive checks for the Gaussian, diffuse prior model from the semantic priming study. $y$ = observed data; $y_{rep}$ = predicted data.

```{r semanticpriming-priorpredictivecheck-diffusepriors, fig.cap = '(ref:semanticpriming-priorpredictivecheck-diffusepriors)', out.width = '80%'}

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_diffusepriors.pdf'
  ))

```

In contrast to the above results, Figures \@ref(fig:semanticpriming-priorpredictivecheck-informativepriors-exgaussian), \@ref(fig:semanticpriming-priorpredictivecheck-weaklyinformativepriors-exgaussian) and \@ref(fig:semanticpriming-priorpredictivecheck-diffusepriors-exgaussian) demonstrate that, when an ex-Gaussian distribution was used, the priors fitted the data far better, which converged with the results of a similar comparison performed by @rodriguez-ferreiroSemanticPrimingSchizotypal2020 (see supplementary materials of the latter study).

(ref:semanticpriming-priorpredictivecheck-informativepriors-exgaussian) Prior predictive checks for the ex-Gaussian, informative prior model from the semantic priming study. $y$ = observed data; $y_{rep}$ = predicted data.

```{r semanticpriming-priorpredictivecheck-informativepriors-exgaussian, fig.cap = '(ref:semanticpriming-priorpredictivecheck-informativepriors-exgaussian)', out.width = '80%'}

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_informativepriors_exgaussian.pdf'
  ))

```

(ref:semanticpriming-priorpredictivecheck-weaklyinformativepriors-exgaussian) Prior predictive checks for the ex-Gaussian, weakly-informative prior model from the semantic priming study. $y$ = observed data; $y_{rep}$ = predicted data.

```{r semanticpriming-priorpredictivecheck-weaklyinformativepriors-exgaussian, fig.cap = '(ref:semanticpriming-priorpredictivecheck-weaklyinformativepriors-exgaussian)', out.width = '80%'}

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_weaklyinformativepriors_exgaussian.pdf'
  ))

```

(ref:semanticpriming-priorpredictivecheck-diffusepriors-exgaussian) Prior predictive checks for the ex-Gaussian, diffuse prior model from the semantic priming study. $y$ = observed data; $y_{rep}$ = predicted data.

```{r semanticpriming-priorpredictivecheck-diffusepriors-exgaussian, fig.cap = '(ref:semanticpriming-priorpredictivecheck-diffusepriors-exgaussian)', out.width = '80%'}

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_diffusepriors_exgaussian.pdf'
  ))

```

### Posterior predictive checks

Based on the above results, the ex-Gaussian distribution was used in the final models. Figure \@ref(fig:semanticpriming-posteriorpredictivechecks-allpriors-exgaussian) presents the posterior predictive checks the latter models. The interpretation of these plots is simple: the distributions of the observed ($y$) and the predicted data ($y_{rep}$) should be as similar as possible. As such, the plots below suggest that the results are trustworthy.

(ref:semanticpriming-posteriorpredictivechecks-allpriors-exgaussian) Posterior predictive checks for the (ex-Gaussian) models from the semantic priming study. $y$ = observed data; $y_{rep}$ = predicted data.

```{r semanticpriming-posteriorpredictivechecks-allpriors-exgaussian, fig.cap = '(ref:semanticpriming-posteriorpredictivechecks-allpriors-exgaussian)'}

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticpriming/bayesian_analysis/posterior_predictive_checks/plots/semanticpriming_posteriorpredictivechecks_allpriors_exgaussian.pdf'
  ))

```

## Study 2: Semantic decision

### Prior predictive checks

Figures \@ref(fig:semanticdecision-priorpredictivecheck-informativepriors), \@ref(fig:semanticdecision-priorpredictivecheck-weaklyinformativepriors) and \@ref(fig:semanticdecision-priorpredictivecheck-diffusepriors) show the prior predictive checks for the Gaussian models (for background on these checks, see [\underline{Study 1 above}](#study1-bayesian-diagnostics)). The three plots---corresponding to models that used the default Gaussian distribution---show that the priors fitted the data acceptably but not very well.

(ref:semanticdecision-priorpredictivecheck-informativepriors) Prior predictive checks for the Gaussian, informative prior model from the semantic decision study. $y$ = observed data; $y_{rep}$ = predicted data.

```{r semanticdecision-priorpredictivecheck-informativepriors, fig.cap = '(ref:semanticdecision-priorpredictivecheck-informativepriors)', out.width = '80%'}

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_informativepriors.pdf'
  ))

```

(ref:semanticdecision-priorpredictivecheck-weaklyinformativepriors) Prior predictive checks for the Gaussian, weakly-informative prior model from the semantic decision study. $y$ = observed data; $y_{rep}$ = predicted data.

```{r semanticdecision-priorpredictivecheck-weaklyinformativepriors, fig.cap = '(ref:semanticdecision-priorpredictivecheck-weaklyinformativepriors)', out.width = '80%'}

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_weaklyinformativepriors.pdf'
  ))

```

(ref:semanticdecision-priorpredictivecheck-diffusepriors) Prior predictive checks for the Gaussian, diffuse prior model from the semantic decision study. $y$ = observed data; $y_{rep}$ = predicted data.

```{r semanticdecision-priorpredictivecheck-diffusepriors, fig.cap = '(ref:semanticdecision-priorpredictivecheck-diffusepriors)', out.width = '80%'}

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_diffusepriors.pdf'
  ))

```

In contrast to the results from the Gaussian models, Figures \@ref(fig:semanticdecision-priorpredictivecheck-informativepriors-exgaussian), \@ref(fig:semanticdecision-priorpredictivecheck-weaklyinformativepriors-exgaussian) and \@ref(fig:semanticdecision-priorpredictivecheck-diffusepriors-exgaussian) demonstrate that, when an ex-Gaussian distribution was used, the priors fitted the data far better, which converged with the results found in Study 1.

(ref:semanticdecision-priorpredictivecheck-informativepriors-exgaussian) Prior predictive checks for the ex-Gaussian, informative prior model from the semantic decision study. $y$ = observed data; $y_{rep}$ = predicted data.

```{r semanticdecision-priorpredictivecheck-informativepriors-exgaussian, fig.cap = '(ref:semanticdecision-priorpredictivecheck-informativepriors-exgaussian)', out.width = '80%'}

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_informativepriors_exgaussian.pdf'
  ))

```

(ref:semanticdecision-priorpredictivecheck-weaklyinformativepriors-exgaussian) Prior predictive checks for the ex-Gaussian, weakly-informative prior model from the semantic decision study. $y$ = observed data; $y_{rep}$ = predicted data.

```{r semanticdecision-priorpredictivecheck-weaklyinformativepriors-exgaussian, fig.cap = '(ref:semanticdecision-priorpredictivecheck-weaklyinformativepriors-exgaussian)', out.width = '80%'}

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_weaklyinformativepriors_exgaussian.pdf'
  ))

```

(ref:semanticdecision-priorpredictivecheck-diffusepriors-exgaussian) Prior predictive checks for the ex-Gaussian, diffuse prior model from the semantic decision study. $y$ = observed data; $y_{rep}$ = predicted data.

```{r semanticdecision-priorpredictivecheck-diffusepriors-exgaussian, fig.cap = '(ref:semanticdecision-priorpredictivecheck-diffusepriors-exgaussian)', out.width = '80%'}

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_diffusepriors_exgaussian.pdf'
  ))

```

### Posterior predictive checks

Based on the above results, the ex-Gaussian distribution was used in the final models. Figure \@ref(fig:semanticdecision-posteriorpredictivechecks-allpriors-exgaussian) presents the posterior predictive checks for the latter models. The interpretation of these plots is simple: the distributions of the observed ($y$) and the predicted data ($y_{rep}$) should be as similar as possible. As such, the plots below suggest that the results are not entirely trustworthy. Indeed, the results themselves ([\underline{Appendix E}](#appendix-E-Bayesian-analysis-results)) are clearly not valid.

(ref:semanticdecision-posteriorpredictivechecks-allpriors-exgaussian) Posterior predictive checks for the (ex-Gaussian) models from the semantic decision study. $y$ = observed data; $y_{rep}$ = predicted data.

```{r semanticdecision-posteriorpredictivechecks-allpriors-exgaussian, fig.cap = '(ref:semanticdecision-posteriorpredictivechecks-allpriors-exgaussian)'}

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticdecision/bayesian_analysis/posterior_predictive_checks/plots/semanticdecision_posteriorpredictivechecks_allpriors_exgaussian.pdf'
  ))

```

## Study 3: Lexical decision

### Prior predictive checks

Figures \@ref(fig:lexicaldecision-priorpredictivecheck-informativepriors), \@ref(fig:lexicaldecision-priorpredictivecheck-weaklyinformativepriors) and \@ref(fig:lexicaldecision-priorpredictivecheck-diffusepriors) show the prior predictive checks for the Gaussian models (for background on these checks, see [\underline{Study 1 above}](#study1-bayesian-diagnostics)). The three plots---corresponding to models that used the default Gaussian distribution---show that the priors fitted the data acceptably but not very well.

(ref:lexicaldecision-priorpredictivecheck-informativepriors) Prior predictive checks for the Gaussian, informative prior model from the lexical decision study. $y$ = observed data; $y_{rep}$ = predicted data.

```{r lexicaldecision-priorpredictivecheck-informativepriors, fig.cap = '(ref:lexicaldecision-priorpredictivecheck-informativepriors)', out.width = '80%'}

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_informativepriors.pdf'
  ))

```

(ref:lexicaldecision-priorpredictivecheck-weaklyinformativepriors) Prior predictive checks for the Gaussian, weakly-informative prior model from the lexical decision study. $y$ = observed data; $y_{rep}$ = predicted data.

```{r lexicaldecision-priorpredictivecheck-weaklyinformativepriors, fig.cap = '(ref:lexicaldecision-priorpredictivecheck-weaklyinformativepriors)', out.width = '80%'}

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_weaklyinformativepriors.pdf'
  ))

```

(ref:lexicaldecision-priorpredictivecheck-diffusepriors) Prior predictive checks for the Gaussian, diffuse prior model from the lexical decision study. $y$ = observed data; $y_{rep}$ = predicted data.

```{r lexicaldecision-priorpredictivecheck-diffusepriors, fig.cap = '(ref:lexicaldecision-priorpredictivecheck-diffusepriors)', out.width = '80%'}

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_diffusepriors.pdf'
  ))

```

In contrast to the results from the Gaussian models, Figures \@ref(fig:lexicaldecision-priorpredictivecheck-informativepriors-exgaussian), \@ref(fig:lexicaldecision-priorpredictivecheck-weaklyinformativepriors-exgaussian) and \@ref(fig:lexicaldecision-priorpredictivecheck-diffusepriors-exgaussian) demonstrate that, when an ex-Gaussian distribution was used, the priors fitted the data far better, which converged with the results found in Studies 1 and 2.

(ref:lexicaldecision-priorpredictivecheck-informativepriors-exgaussian) Prior predictive checks for the ex-Gaussian, informative prior model from the lexical decision study. $y$ = observed data; $y_{rep}$ = predicted data.

```{r lexicaldecision-priorpredictivecheck-informativepriors-exgaussian, fig.cap = '(ref:lexicaldecision-priorpredictivecheck-informativepriors-exgaussian)', out.width = '80%'}

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_informativepriors_exgaussian.pdf'
  ))

```

(ref:lexicaldecision-priorpredictivecheck-weaklyinformativepriors-exgaussian) Prior predictive checks for the ex-Gaussian, weakly-informative prior model from the lexical decision study. $y$ = observed data; $y_{rep}$ = predicted data.

```{r lexicaldecision-priorpredictivecheck-weaklyinformativepriors-exgaussian, fig.cap = '(ref:lexicaldecision-priorpredictivecheck-weaklyinformativepriors-exgaussian)', out.width = '80%'}

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_weaklyinformativepriors_exgaussian.pdf'
  ))

```

(ref:lexicaldecision-priorpredictivecheck-diffusepriors-exgaussian) Prior predictive checks for the ex-Gaussian, diffuse prior model from the lexical decision study. $y$ = observed data; $y_{rep}$ = predicted data.

```{r lexicaldecision-priorpredictivecheck-diffusepriors-exgaussian, fig.cap = '(ref:lexicaldecision-priorpredictivecheck-diffusepriors-exgaussian)', out.width = '80%'}

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_diffusepriors_exgaussian.pdf'
  ))

```

### Posterior predictive checks

Based on the above results, the ex-Gaussian distribution was used in the final models. Figure \@ref(fig:lexicaldecision-posteriorpredictivechecks-allpriors-exgaussian) presents the posterior predictive checks for the latter models. The interpretation of these plots is simple: the distributions of the observed ($y$) and the predicted data ($y_{rep}$) should be as similar as possible. As such, the plots below suggest that the results are trustworthy.

(ref:lexicaldecision-posteriorpredictivechecks-allpriors-exgaussian) Posterior predictive checks for the (ex-Gaussian) models from the lexical decision study. $y$ = observed data; $y_{rep}$ = predicted data.

```{r lexicaldecision-posteriorpredictivechecks-allpriors-exgaussian, fig.cap = '(ref:lexicaldecision-posteriorpredictivechecks-allpriors-exgaussian)'}

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/lexicaldecision/bayesian_analysis/posterior_predictive_checks/plots/lexicaldecision_posteriorpredictivechecks_allpriors_exgaussian.pdf'
  ))

```

### 2022-06-24 manuscript/appendix-D-interaction-plots.Rmd
24062022

# Appendix D: Further plots of interactions {#appendix-D-interaction-plots}

```{r}

# This appendix inherits the libraries, the working directory and the
# data sets loaded in manuscript.Rmd, when the latter is knitted.

```

This appendix presents plots of interactions that did not fit in the main text.

## Study 1: Semantic priming

```{r semanticpriming-interactions-with-gender, fig.cap = 'Interactions with gender in the semantic priming study.', out.height = '70%'}

# Run plot through source() rather than directly in this R Markdown document 
# to preserve the italicised text.

source('semanticpriming/frequentist_analysis/semanticpriming-interactions-with-gender.R', 
       local = TRUE)

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-gender.pdf'
  ))

```

... TBC

## Study 2: Semantic decision

...

## Study 3: Lexical decision

...

### 2022-06-24 manuscript/appendix-E-Bayesian-analysis-results.Rmd
24062022

# Appendix E: Results from the Bayesian analyses {#appendix-E-Bayesian-analysis-results}

```{r}

# This appendix inherits the libraries, the working directory and the
# data sets loaded in manuscript.Rmd, when the latter is knitted.

```

This appendix presents extended results from the Bayesian analyses, containing a prior sensitivity analysis [@schootBayesianStatisticsModelling2021]. For each study, three tables are presented that contain the results from the informative prior model ($SD$ = 0.1), the weakly-informative prior model ($SD$ = 0.2) and the diffuse prior model ($SD$ = 0.3). All models had an exponentially modified Gaussian (dubbed ‘ex-Gaussian’) distribution with an identity link function (for background, see main article and [\underline{Appendix C}](#appendix-C-Bayesian-analysis-diagnostics)). The $\widehat R$ value is a convergence diagnostic that should ideally be smaller than 1.01 [@vehtariRanknormalizationFoldingLocalization2021].

The approach used in this Bayesian analysis is that of estimation [@tendeiroReviewIssuesNull2019; also see @schmalzWhatBayesFactor2021]. Thus, the estimates were interpreted by considering the position of their credible intervals in relation to the predicted value of RT ($z$). That is, the closer an interval is to a value of 0 on the predicted RT ($z$), the smaller the effect of that predictor. For instance, an interval that is symmetrically centred on 0 indicates a very small effect, whereas---in comparison---an interval that does not include 0 indicates a far larger effect [for other examples of this approach, see @milekEavesdroppingHappinessRevisited2018; @preglaVariabilitySentenceComprehension2021; @rodriguez-ferreiroSemanticPrimingSchizotypal2020].

## Study 1: Semantic priming

Table \@ref(tab:semanticpriming-informativepriors-model) presents the results of the informative prior model, and Table \@ref(tab:semanticpriming-diffusepriors-model) presents those of the diffuse prior model (further to this, the weakly-informative prior model will be added when it finishes running).

```{r semanticpriming-informativepriors-model, results = 'asis'}

# Rename effects in plain language and specify the random slopes
# (if any) for each effect, in the footnote. For this purpose, 
# superscripts are added to the names of the appropriate effects.
# 
# In the interactions below, word-level variables are presented 
# first for the sake of consistency (the order does not affect 
# the results in any way). Also in the interactions, double 
# colons are used to inform the 'bayesian_model_table' function 
# that the two terms in the interaction must be split into two 
# lines.

rownames(semanticpriming_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_informativepriors_exgaussian$fixed) == 
    'z_attentional_control'] = 'Attentional control'

rownames(semanticpriming_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_informativepriors_exgaussian$fixed) == 
    'z_vocabulary_size'] = 'Vocabulary size $^{\\text{a}}$'

rownames(semanticpriming_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_informativepriors_exgaussian$fixed) == 
    'z_recoded_participant_gender'] = 'Gender $^{\\text{a}}$'

rownames(semanticpriming_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_informativepriors_exgaussian$fixed) == 
    'z_target_word_frequency'] = 'Word frequency'

rownames(semanticpriming_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_informativepriors_exgaussian$fixed) == 
    'z_target_number_syllables'] = 'Number of syllables'

rownames(semanticpriming_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_informativepriors_exgaussian$fixed) == 
    'z_word_concreteness_diff'] = 'Word-concreteness difference'

rownames(semanticpriming_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_informativepriors_exgaussian$fixed) == 
    'z_cosine_similarity'] = 'Language-based similarity $^{\\text{b}}$'

rownames(semanticpriming_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_informativepriors_exgaussian$fixed) == 
    'z_visual_rating_diff'] = 'Visual-strength difference $^{\\text{b}}$'

rownames(semanticpriming_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_informativepriors_exgaussian$fixed) == 
    'z_recoded_interstimulus_interval'] = 'Stimulus-onset asynchrony (SOA) $^{\\text{b}}$'

rownames(semanticpriming_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_informativepriors_exgaussian$fixed) == 
    'z_word_concreteness_diff:z_vocabulary_size'] = 
  'Word-concreteness difference :: Vocabulary size'

rownames(semanticpriming_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_informativepriors_exgaussian$fixed) == 
    'z_word_concreteness_diff:z_recoded_interstimulus_interval'] = 
  'Word-concreteness difference : SOA'

rownames(semanticpriming_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_informativepriors_exgaussian$fixed) == 
    'z_word_concreteness_diff:z_recoded_participant_gender'] = 
  'Word-concreteness difference : Gender'

rownames(semanticpriming_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_informativepriors_exgaussian$fixed) == 
    'z_attentional_control:z_cosine_similarity'] = 
  'Language-based similarity :: Attentional control'

rownames(semanticpriming_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_informativepriors_exgaussian$fixed) == 
    'z_attentional_control:z_visual_rating_diff'] = 
  'Visual-strength difference :: Attentional control'

rownames(semanticpriming_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_informativepriors_exgaussian$fixed) == 
    'z_vocabulary_size:z_cosine_similarity'] = 
  'Language-based similarity :: Vocabulary size'

rownames(semanticpriming_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_informativepriors_exgaussian$fixed) == 
    'z_vocabulary_size:z_visual_rating_diff'] = 
  'Visual-strength difference :: Vocabulary size'

rownames(semanticpriming_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_informativepriors_exgaussian$fixed) == 
    'z_recoded_participant_gender:z_cosine_similarity'] = 
  'Language-based similarity : Gender'

rownames(semanticpriming_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_informativepriors_exgaussian$fixed) == 
    'z_recoded_participant_gender:z_visual_rating_diff'] = 
  'Visual-strength difference : Gender'

rownames(semanticpriming_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_informativepriors_exgaussian$fixed) == 
    'z_cosine_similarity:z_recoded_interstimulus_interval'] = 
  'Language-based similarity : SOA $^{\\text{b}}$'

rownames(semanticpriming_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_informativepriors_exgaussian$fixed) == 
    'z_visual_rating_diff:z_recoded_interstimulus_interval'] = 
  'Visual-strength difference : SOA $^{\\text{b}}$'

# Create table (using custom function from the 'R_functions' folder)
bayesian_model_table(
  semanticpriming_summary_informativepriors_exgaussian, 
  order_effects = c('(Intercept)',
                    'Attentional control',
                    'Vocabulary size $^{\\text{a}}$',
                    'Gender $^{\\text{a}}$',
                    'Word frequency',
                    'Number of syllables',
                    'Word-concreteness difference',
                    'Language-based similarity $^{\\text{b}}$',
                    'Visual-strength difference $^{\\text{b}}$',
                    'Stimulus-onset asynchrony (SOA) $^{\\text{b}}$',
                    'Word-concreteness difference :: Vocabulary size',
                    'Word-concreteness difference : SOA',
                    'Word-concreteness difference : Gender',
                    'Language-based similarity :: Attentional control',
                    'Visual-strength difference :: Attentional control',
                    'Language-based similarity :: Vocabulary size',
                    'Visual-strength difference :: Vocabulary size',
                    'Language-based similarity : Gender',
                    'Visual-strength difference : Gender',
                    'Language-based similarity : SOA $^{\\text{b}}$',
                    'Visual-strength difference : SOA $^{\\text{b}}$'),
  interaction_symbol_x = TRUE,
  caption = 'Informative prior model for the semantic priming study.') %>%
  # kable_styling(latex_options = 'scale_down') %>%

  # Group predictors under headings
  pack_rows('Individual differences', 2, 4) %>% 
  pack_rows('Target-word lexical covariates', 5, 6) %>% 
  pack_rows('Prime-target semantic relationship', 7, 9) %>% 
  pack_rows('Task condition', 10, 10) %>% 
  pack_rows('Interactions', 11, 21) %>%

  # Place table close to designated position and highlight covariates
  kable_styling(latex_options = c('HOLD_position', 'striped'), 
                stripe_index = c(2, 5:7, 11:15)) %>%

  # Footnote describing abbreviations, random slopes, etc. 
  # LaTeX code used to format the text.
  footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on z-scored variables; \\\\textit{SE} = standard error;',
                           'CrI = credible interval. Shaded rows contain covariates. Some interactions',
                           'are split over two lines, with the second line indented. \\\\linebreak', 
                           '$^{\\\\text{a}}$ By-word random slopes were included for this effect.',
                           '$^{\\\\text{b}}$ By-participant random slopes were included for this effect.', 
                           # Begin lines after first one with a dot-sized indent
                           sep = ' \\\\linebreak \\\\phantom{.}'))

```

```{r semanticpriming-diffusepriors-model, results = 'asis'}

# Rename effects in plain language and specify the random slopes
# (if any) for each effect, in the footnote. For this purpose, 
# superscripts are added to the names of the appropriate effects.
# 
# In the interactions below, word-level variables are presented 
# first for the sake of consistency (the order does not affect 
# the results in any way). Also in the interactions, double 
# colons are used to inform the 'bayesian_model_table' function 
# that the two terms in the interaction must be split into two 
# lines.

rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
    'z_attentional_control'] = 'Attentional control'

rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
    'z_vocabulary_size'] = 'Vocabulary size $^{\\text{a}}$'

rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
    'z_recoded_participant_gender'] = 'Gender $^{\\text{a}}$'

rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
    'z_target_word_frequency'] = 'Word frequency'

rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
    'z_target_number_syllables'] = 'Number of syllables'

rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
    'z_word_concreteness_diff'] = 'Word-concreteness difference'

rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
    'z_cosine_similarity'] = 'Language-based similarity $^{\\text{b}}$'

rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
    'z_visual_rating_diff'] = 'Visual-strength difference $^{\\text{b}}$'

rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
    'z_recoded_interstimulus_interval'] = 'Stimulus-onset asynchrony (SOA) $^{\\text{b}}$'

rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
    'z_word_concreteness_diff:z_vocabulary_size'] = 
  'Word-concreteness difference :: Vocabulary size'

rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
    'z_word_concreteness_diff:z_recoded_interstimulus_interval'] = 
  'Word-concreteness difference : SOA'

rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
    'z_word_concreteness_diff:z_recoded_participant_gender'] = 
  'Word-concreteness difference : Gender'

rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
    'z_attentional_control:z_cosine_similarity'] = 
  'Language-based similarity :: Attentional control'

rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
    'z_attentional_control:z_visual_rating_diff'] = 
  'Visual-strength difference :: Attentional control'

rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
    'z_vocabulary_size:z_cosine_similarity'] = 
  'Language-based similarity :: Vocabulary size'

rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
    'z_vocabulary_size:z_visual_rating_diff'] = 
  'Visual-strength difference :: Vocabulary size'

rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
    'z_recoded_participant_gender:z_cosine_similarity'] = 
  'Language-based similarity : Gender'

rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
    'z_recoded_participant_gender:z_visual_rating_diff'] = 
  'Visual-strength difference : Gender'

rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
    'z_cosine_similarity:z_recoded_interstimulus_interval'] = 
  'Language-based similarity : SOA $^{\\text{b}}$'

rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
    'z_visual_rating_diff:z_recoded_interstimulus_interval'] = 
  'Visual-strength difference : SOA $^{\\text{b}}$'

# Create table (using custom function from the 'R_functions' folder)
bayesian_model_table(
  semanticpriming_summary_diffusepriors_exgaussian, 
  order_effects = c('(Intercept)',
                    'Attentional control',
                    'Vocabulary size $^{\\text{a}}$',
                    'Gender $^{\\text{a}}$',
                    'Word frequency',
                    'Number of syllables',
                    'Word-concreteness difference',
                    'Language-based similarity $^{\\text{b}}$',
                    'Visual-strength difference $^{\\text{b}}$',
                    'Stimulus-onset asynchrony (SOA) $^{\\text{b}}$',
                    'Word-concreteness difference :: Vocabulary size',
                    'Word-concreteness difference : SOA',
                    'Word-concreteness difference : Gender',
                    'Language-based similarity :: Attentional control',
                    'Visual-strength difference :: Attentional control',
                    'Language-based similarity :: Vocabulary size',
                    'Visual-strength difference :: Vocabulary size',
                    'Language-based similarity : Gender',
                    'Visual-strength difference : Gender',
                    'Language-based similarity : SOA $^{\\text{b}}$',
                    'Visual-strength difference : SOA $^{\\text{b}}$'),
  interaction_symbol_x = TRUE,
  caption = 'Diffuse prior model for the semantic priming study.') %>%
  # kable_styling(latex_options = 'scale_down') %>%

  # Group predictors under headings
  pack_rows('Individual differences', 2, 4) %>% 
  pack_rows('Target-word lexical covariates', 5, 6) %>% 
  pack_rows('Prime-target semantic relationship', 7, 9) %>% 
  pack_rows('Task condition', 10, 10) %>% 
  pack_rows('Interactions', 11, 21) %>%

  # Place table close to designated position and highlight covariates
  kable_styling(latex_options = c('HOLD_position', 'striped'), 
                stripe_index = c(2, 5:7, 11:15)) %>%

  # Footnote describing abbreviations, random slopes, etc. 
  # LaTeX code used to format the text.
  footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on z-scored variables; \\\\textit{SE} = standard error;',
                           'CrI = credible interval. Shaded rows contain covariates. Some interactions',
                           'are split over two lines, with the second line indented. \\\\linebreak', 
                           '$^{\\\\text{a}}$ By-word random slopes were included for this effect.',
                           '$^{\\\\text{b}}$ By-participant random slopes were included for this effect.', 
                           # Begin lines after first one with a dot-sized indent
                           sep = ' \\\\linebreak \\\\phantom{.}'))

```

Figure \@ref(fig:semanticpriming-frequentist-bayesian-plot-allpriors-exgaussian) presents the posterior distribution of each effect in each model. The frequentist estimates are also shown to facilitate the comparison.

```{r semanticpriming-frequentist-bayesian-plot-allpriors-exgaussian, fig.cap = 'Estimates from the frequentist analysis (in red) and from the Bayesian analysis (in blue) for the semantic priming study, in each model. The frequentist means (represented by points) are flanked by 95\\% confidence intervals. The Bayesian means (represented by vertical lines) are flanked by 95\\% credible intervals, in light blue (in some cases, the interval is covered up by the bar of the mean).'}

# Run plot through source() rather than directly in this R Markdown document
# to preserve the format.

source('semanticpriming/frequentist_bayesian_plots/semanticpriming_frequentist_bayesian_plots.R', 
       local = TRUE)

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticpriming/frequentist_bayesian_plots/plots/semanticpriming_frequentist_bayesian_plot_allpriors_exgaussian.pdf'
  ))

```

## Study 2: Semantic decision

Table \@ref(tab:semanticdecision-informativepriors-model) presents the results of the informative prior model, Table \@ref(tab:semanticdecision-weaklyinformativepriors-model) presents those of the weakly-informative prior model and Table \@ref(tab:semanticdecision-diffusepriors-model) presents those of the diffuse prior model.

```{r semanticdecision-informativepriors-model, results = 'asis'}

# Rename effects in plain language and specify the random slopes
# (if any) for each effect, in the footnote. For this purpose, 
# superscripts are added to the names of the appropriate effects.
# 
# In the interactions below, word-level variables are presented 
# first for the sake of consistency (the order does not affect 
# the results in any way). Also in the interactions, double 
# colons are used to inform the 'bayesian_model_table' function 
# that the two terms in the interaction must be split into two 
# lines.

rownames(semanticdecision_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_informativepriors_exgaussian$fixed) == 
    'z_information_uptake'] = 'Information uptake'

rownames(semanticdecision_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_informativepriors_exgaussian$fixed) == 
    'z_vocabulary_size'] = 'Vocabulary size $^{\\text{a}}$'

rownames(semanticdecision_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_informativepriors_exgaussian$fixed) == 
    'z_recoded_participant_gender'] = 'Gender $^{\\text{a}}$'

rownames(semanticdecision_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_informativepriors_exgaussian$fixed) == 
    'z_word_frequency'] = 'Word frequency'

rownames(semanticdecision_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_informativepriors_exgaussian$fixed) == 
    'z_orthographic_Levenshtein_distance'] = 'Orthographic Levenshtein distance'

rownames(semanticdecision_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_informativepriors_exgaussian$fixed) == 
    'z_word_concreteness'] = 'Word concreteness'

rownames(semanticdecision_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_informativepriors_exgaussian$fixed) == 
    'z_word_cooccurrence'] = "Distance to word 'abstract' $^{\\text{b}}$"

rownames(semanticdecision_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_informativepriors_exgaussian$fixed) == 
    'z_visual_rating'] = 'Visual strength $^{\\text{b}}$'

rownames(semanticdecision_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_informativepriors_exgaussian$fixed) == 
    'z_word_concreteness:z_vocabulary_size'] = 
  'Word concreteness : Vocabulary size'

rownames(semanticdecision_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_informativepriors_exgaussian$fixed) == 
    'z_word_concreteness:z_recoded_participant_gender'] = 
  'Word concreteness : Gender'

rownames(semanticdecision_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_informativepriors_exgaussian$fixed) == 
    'z_information_uptake:z_word_cooccurrence'] = 
  "Information uptake :: Distance to word 'abstract'"

rownames(semanticdecision_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_informativepriors_exgaussian$fixed) == 
    'z_information_uptake:z_visual_rating'] = 
  'Visual strength : Information uptake'

rownames(semanticdecision_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_informativepriors_exgaussian$fixed) == 
    'z_vocabulary_size:z_word_cooccurrence'] = 
  "Distance to word 'abstract' :: Vocabulary size"

rownames(semanticdecision_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_informativepriors_exgaussian$fixed) == 
    'z_vocabulary_size:z_visual_rating'] = 
  'Visual strength : Vocabulary size'

rownames(semanticdecision_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_informativepriors_exgaussian$fixed) == 
    'z_recoded_participant_gender:z_word_cooccurrence'] = 
  "Distance to word 'abstract' : Gender"

rownames(semanticdecision_summary_informativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_informativepriors_exgaussian$fixed) == 
    'z_recoded_participant_gender:z_visual_rating'] = 
  'Visual strength : Gender'

# Create table (using custom function from the 'R_functions' folder)
bayesian_model_table(
  semanticdecision_summary_informativepriors_exgaussian, 
  order_effects = c('(Intercept)',
                    'Information uptake',
                    'Vocabulary size $^{\\text{a}}$',
                    'Gender $^{\\text{a}}$',
                    'Word frequency',
                    'Orthographic Levenshtein distance',
                    'Word concreteness',
                    "Distance to word 'abstract' $^{\\text{b}}$",
                    'Visual strength $^{\\text{b}}$',
                    'Vocabulary size : Word concreteness',
                    'Word concreteness : Gender',
                    "Distance to word 'abstract' :: Information uptake",
                    'Visual strength : Information uptake',
                    "Distance to word 'abstract' :: Vocabulary size",
                    'Visual strength : Vocabulary size',
                    "Distance to word 'abstract' : Gender",
                    'Visual strength : Gender'),
  interaction_symbol_x = TRUE,
  caption = 'Informative prior model for the semantic decision study.') %>%
  # kable_styling(latex_options = 'scale_down') %>%

  # Group predictors under headings
  pack_rows('Individual differences', 2, 4) %>% 
  pack_rows('Lexical covariates', 5, 6) %>% 
  pack_rows('Semantic variables', 7, 9) %>% 
  pack_rows('Interactions', 10, 17) %>%

  # Place table close to designated position and highlight covariates
  kable_styling(latex_options = c('HOLD_position', 'striped'), 
                stripe_index = c(2, 5:7, 10:11)) %>%

  # Footnote describing abbreviations, random slopes, etc. 
  # LaTeX code used to format the text.
  footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on z-scored variables; \\\\textit{SE} = standard error;',
                           'CrI = credible interval. Shaded rows contain covariates. Some interactions',
                           'are split over two lines, with the second line indented. \\\\linebreak', 
                           '$^{\\\\text{a}}$ By-word random slopes were included for this effect.',
                           '$^{\\\\text{b}}$ By-participant random slopes were included for this effect.', 
                           # Begin lines after first one with a dot-sized indent
                           sep = ' \\\\linebreak \\\\phantom{.}'))

```

```{r semanticdecision-weaklyinformativepriors-model, results = 'asis'}

# Rename effects in plain language and specify the random slopes
# (if any) for each effect, in the footnote. For this purpose, 
# superscripts are added to the names of the appropriate effects.
# 
# In the interactions below, word-level variables are presented 
# first for the sake of consistency (the order does not affect 
# the results in any way). Also in the interactions, double 
# colons are used to inform the 'bayesian_model_table' function 
# that the two terms in the interaction must be split into two 
# lines.

rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_information_uptake'] = 'Information uptake'

rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_vocabulary_size'] = 'Vocabulary size $^{\\text{a}}$'

rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_recoded_participant_gender'] = 'Gender $^{\\text{a}}$'

rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_word_frequency'] = 'Word frequency'

rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_orthographic_Levenshtein_distance'] = 'Orthographic Levenshtein distance'

rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_word_concreteness'] = 'Word concreteness'

rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_word_cooccurrence'] = "Distance to word 'abstract' $^{\\text{b}}$"

rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_visual_rating'] = 'Visual strength $^{\\text{b}}$'

rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_word_concreteness:z_vocabulary_size'] = 
  'Word concreteness : Vocabulary size'

rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_word_concreteness:z_recoded_participant_gender'] = 
  'Word concreteness : Gender'

rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_information_uptake:z_word_cooccurrence'] = 
  "Information uptake :: Distance to word 'abstract'"

rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_information_uptake:z_visual_rating'] = 
  'Visual strength : Information uptake'

rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_vocabulary_size:z_word_cooccurrence'] = 
  "Distance to word 'abstract' :: Vocabulary size"

rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_vocabulary_size:z_visual_rating'] = 
  'Visual strength : Vocabulary size'

rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_recoded_participant_gender:z_word_cooccurrence'] = 
  "Distance to word 'abstract' : Gender"

rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_recoded_participant_gender:z_visual_rating'] = 
  'Visual strength : Gender'

# Create table (using custom function from the 'R_functions' folder)
bayesian_model_table(
  semanticdecision_summary_weaklyinformativepriors_exgaussian, 
  order_effects = c('(Intercept)',
                    'Information uptake',
                    'Vocabulary size $^{\\text{a}}$',
                    'Gender $^{\\text{a}}$',
                    'Word frequency',
                    'Orthographic Levenshtein distance',
                    'Word concreteness',
                    "Distance to word 'abstract' $^{\\text{b}}$",
                    'Visual strength $^{\\text{b}}$',
                    'Vocabulary size : Word concreteness',
                    'Word concreteness : Gender',
                    "Distance to word 'abstract' :: Information uptake",
                    'Visual strength : Information uptake',
                    "Distance to word 'abstract' :: Vocabulary size",
                    'Visual strength : Vocabulary size',
                    "Distance to word 'abstract' : Gender",
                    'Visual strength : Gender'),
  interaction_symbol_x = TRUE,
  caption = 'Weakly-informative prior model for the semantic decision study.') %>%
  # kable_styling(latex_options = 'scale_down') %>%

  # Group predictors under headings
  pack_rows('Individual differences', 2, 4) %>% 
  pack_rows('Lexical covariates', 5, 6) %>% 
  pack_rows('Semantic variables', 7, 9) %>% 
  pack_rows('Interactions', 10, 17) %>%

  # Place table close to designated position and highlight covariates
  kable_styling(latex_options = c('HOLD_position', 'striped'), 
                stripe_index = c(2, 5:7, 10:11)) %>%

  # Footnote describing abbreviations, random slopes, etc. 
  # LaTeX code used to format the text.
  footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on z-scored variables; \\\\textit{SE} = standard error;',
                           'CrI = credible interval. Shaded rows contain covariates. Some interactions',
                           'are split over two lines, with the second line indented. \\\\linebreak', 
                           '$^{\\\\text{a}}$ By-word random slopes were included for this effect.',
                           '$^{\\\\text{b}}$ By-participant random slopes were included for this effect.', 
                           # Begin lines after first one with a dot-sized indent
                           sep = ' \\\\linebreak \\\\phantom{.}'))

```

```{r semanticdecision-diffusepriors-model, results = 'asis'}

# Rename effects in plain language and specify the random slopes
# (if any) for each effect, in the footnote. For this purpose, 
# superscripts are added to the names of the appropriate effects.
# 
# In the interactions below, word-level variables are presented 
# first for the sake of consistency (the order does not affect 
# the results in any way). Also in the interactions, double 
# colons are used to inform the 'bayesian_model_table' function 
# that the two terms in the interaction must be split into two 
# lines.

rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_information_uptake'] = 'Information uptake'

rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_vocabulary_size'] = 'Vocabulary size $^{\\text{a}}$'

rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_recoded_participant_gender'] = 'Gender $^{\\text{a}}$'

rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_word_frequency'] = 'Word frequency'

rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_orthographic_Levenshtein_distance'] = 'Orthographic Levenshtein distance'

rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_word_concreteness'] = 'Word concreteness'

rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_word_cooccurrence'] = "Distance to word 'abstract' $^{\\text{b}}$"

rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_visual_rating'] = 'Visual strength $^{\\text{b}}$'

rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_word_concreteness:z_vocabulary_size'] = 
  'Word concreteness : Vocabulary size'

rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_word_concreteness:z_recoded_participant_gender'] = 
  'Word concreteness : Gender'

rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_information_uptake:z_word_cooccurrence'] = 
  "Information uptake :: Distance to word 'abstract'"

rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_information_uptake:z_visual_rating'] = 
  'Visual strength : Information uptake'

rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_vocabulary_size:z_word_cooccurrence'] = 
  "Distance to word 'abstract' :: Vocabulary size"

rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_vocabulary_size:z_visual_rating'] = 
  'Visual strength : Vocabulary size'

rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_recoded_participant_gender:z_word_cooccurrence'] = 
  "Distance to word 'abstract' : Gender"

rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_recoded_participant_gender:z_visual_rating'] = 
  'Visual strength : Gender'

# Create table (using custom function from the 'R_functions' folder)
bayesian_model_table(
  semanticdecision_summary_diffusepriors_exgaussian, 
  order_effects = c('(Intercept)',
                    'Information uptake',
                    'Vocabulary size $^{\\text{a}}$',
                    'Gender $^{\\text{a}}$',
                    'Word frequency',
                    'Orthographic Levenshtein distance',
                    'Word concreteness',
                    "Distance to word 'abstract' $^{\\text{b}}$",
                    'Visual strength $^{\\text{b}}$',
                    'Vocabulary size : Word concreteness',
                    'Word concreteness : Gender',
                    "Distance to word 'abstract' :: Information uptake",
                    'Visual strength : Information uptake',
                    "Distance to word 'abstract' :: Vocabulary size",
                    'Visual strength : Vocabulary size',
                    "Distance to word 'abstract' : Gender",
                    'Visual strength : Gender'),
  interaction_symbol_x = TRUE,
  caption = 'Diffuse prior model for the semantic decision study.') %>%
  # kable_styling(latex_options = 'scale_down') %>%

  # Group predictors under headings
  pack_rows('Individual differences', 2, 4) %>% 
  pack_rows('Lexical covariates', 5, 6) %>% 
  pack_rows('Semantic variables', 7, 9) %>% 
  pack_rows('Interactions', 10, 17) %>%

  # Place table close to designated position and highlight covariates
  kable_styling(latex_options = c('HOLD_position', 'striped'), 
                stripe_index = c(2, 5:7, 10:11)) %>%

  # Footnote describing abbreviations, random slopes, etc. 
  # LaTeX code used to format the text.
  footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on z-scored variables; \\\\textit{SE} = standard error;',
                           'CrI = credible interval. Shaded rows contain covariates. Some interactions',
                           'are split over two lines, with the second line indented. \\\\linebreak', 
                           '$^{\\\\text{a}}$ By-word random slopes were included for this effect.',
                           '$^{\\\\text{b}}$ By-participant random slopes were included for this effect.', 
                           # Begin lines after first one with a dot-sized indent
                           sep = ' \\\\linebreak \\\\phantom{.}'))

```

Figure \@ref(fig:semanticdecision-frequentist-bayesian-plot-allpriors-exgaussian) presents the posterior distribution of each effect in each model. The frequentist estimates are also shown to facilitate the comparison.

```{r semanticdecision-frequentist-bayesian-plot-allpriors-exgaussian, fig.cap = 'Estimates from the frequentist analysis (in red) and from the Bayesian analysis (in blue) for the semantic decision study, in each model. The frequentist means (represented by points) are flanked by 95\\% confidence intervals. The Bayesian means (represented by vertical lines) are flanked by 95\\% credible intervals, in light blue (in some cases, the interval is covered up by the bar of the mean).'}

# Run plot through source() rather than directly in this R Markdown document
# to preserve the format.

source('semanticdecision/frequentist_bayesian_plots/semanticdecision_frequentist_bayesian_plots.R', 
       local = TRUE)

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticdecision/frequentist_bayesian_plots/plots/semanticdecision_frequentist_bayesian_plot_allpriors_exgaussian.pdf'
  ))

```

## Study 3: Lexical decision

Table \@ref(tab:lexicaldecision-informativepriors-model) presents the results of the informative prior model, Table \@ref(tab:lexicaldecision-weaklyinformativepriors-model) presents those of the weakly-informative prior model and Table \@ref(tab:lexicaldecision-diffusepriors-model) presents those of the diffuse prior model.

```{r lexicaldecision-informativepriors-model, results = 'asis'}

# Rename effects in plain language and specify the random slopes
# (if any) for each effect, in the footnote. For this purpose, 
# superscripts are added to the names of the appropriate effects.
# 
# In the interactions below, word-level variables are presented 
# first for the sake of consistency (the order does not affect 
# the results in any way). Also in the interactions, double 
# colons are used to inform the 'bayesian_model_table' function 
# that the two terms in the interaction must be split into two 
# lines.

rownames(lexicaldecision_summary_informativepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_informativepriors_exgaussian$fixed) == 
    'z_vocabulary_age'] = 'Vocabulary age $^{\\text{a}}$'

rownames(lexicaldecision_summary_informativepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_informativepriors_exgaussian$fixed) == 
    'z_recoded_participant_gender'] = 'Gender $^{\\text{a}}$'

rownames(lexicaldecision_summary_informativepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_informativepriors_exgaussian$fixed) == 
    'z_orthographic_Levenshtein_distance'] = 'Orthographic Levenshtein distance $^{\\text{b}}$'

rownames(lexicaldecision_summary_informativepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_informativepriors_exgaussian$fixed) == 
    'z_word_concreteness'] = 'Word concreteness $^{\\text{b}}$'

rownames(lexicaldecision_summary_informativepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_informativepriors_exgaussian$fixed) == 
    'z_word_frequency'] = 'Word frequency $^{\\text{b}}$'

rownames(lexicaldecision_summary_informativepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_informativepriors_exgaussian$fixed) == 
    'z_visual_rating'] = 'Visual strength $^{\\text{b}}$'

rownames(lexicaldecision_summary_informativepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_informativepriors_exgaussian$fixed) == 
    'z_word_concreteness:z_vocabulary_age'] = 
  'Word concreteness : Vocabulary age'

rownames(lexicaldecision_summary_informativepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_informativepriors_exgaussian$fixed) == 
    'z_word_concreteness:z_recoded_participant_gender'] = 
  'Word concreteness : Gender'

rownames(lexicaldecision_summary_informativepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_informativepriors_exgaussian$fixed) == 
    'z_vocabulary_age:z_word_frequency'] = 
  'Word frequency : Vocabulary age'

rownames(lexicaldecision_summary_informativepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_informativepriors_exgaussian$fixed) == 
    'z_vocabulary_age:z_visual_rating'] = 
  'Visual strength : Vocabulary age'

rownames(lexicaldecision_summary_informativepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_informativepriors_exgaussian$fixed) == 
    'z_recoded_participant_gender:z_word_frequency'] = 
  'Word frequency : Gender'

rownames(lexicaldecision_summary_informativepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_informativepriors_exgaussian$fixed) == 
    'z_recoded_participant_gender:z_visual_rating'] = 
  'Visual strength : Gender'

# Create table (using custom function from the 'R_functions' folder)
bayesian_model_table(
  lexicaldecision_summary_informativepriors_exgaussian, 
  order_effects = c('(Intercept)',
                    'Vocabulary age $^{\\text{a}}$',
                    'Gender $^{\\text{a}}$',
                    'Orthographic Levenshtein distance $^{\\text{b}}$',
                    'Word concreteness $^{\\text{b}}$',
                    'Word frequency $^{\\text{b}}$',
                    'Visual strength $^{\\text{b}}$',
                    'Word concreteness : Vocabulary age',
                    'Word concreteness : Gender',
                    'Word frequency : Vocabulary age',
                    'Visual strength : Vocabulary age',
                    'Word frequency : Gender',
                    'Visual strength : Gender'),
  interaction_symbol_x = TRUE,
  caption = 'Informative prior model for the lexical decision study.') %>%
  # kable_styling(latex_options = 'scale_down') %>%

  # Group predictors under headings
  pack_rows('Individual differences', 2, 3) %>% 
  pack_rows('Lexical covariate', 4, 4) %>% 
  pack_rows('Semantic variables', 5, 7) %>% 
  pack_rows('Interactions', 8, 13) %>%

  # Place table close to designated position and highlight covariates
  kable_styling(latex_options = c('HOLD_position', 'striped'), 
                stripe_index = c(4:5, 8:9)) %>%

  # Footnote describing abbreviations, random slopes, etc. 
  # LaTeX code used to format the text.
  footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on z-scored variables; \\\\textit{SE} = standard error;',
                           'CrI = credible interval. Shaded rows contain covariates. \\\\linebreak', 
                           '$^{\\\\text{a}}$ By-word random slopes were included for this effect.',
                           '$^{\\\\text{b}}$ By-participant random slopes were included for this effect.', 
                           # Begin lines after first one with a dot-sized indent
                           sep = ' \\\\linebreak \\\\phantom{.}'))

```

```{r lexicaldecision-weaklyinformativepriors-model, results = 'asis'}

rownames(lexicaldecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_vocabulary_age'] = 'Vocabulary age $^{\\text{a}}$'

rownames(lexicaldecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_recoded_participant_gender'] = 'Gender $^{\\text{a}}$'

rownames(lexicaldecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_orthographic_Levenshtein_distance'] = 'Orthographic Levenshtein distance $^{\\text{b}}$'

rownames(lexicaldecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_word_concreteness'] = 'Word concreteness $^{\\text{b}}$'

rownames(lexicaldecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_word_frequency'] = 'Word frequency $^{\\text{b}}$'

rownames(lexicaldecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_visual_rating'] = 'Visual strength $^{\\text{b}}$'

rownames(lexicaldecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_word_concreteness:z_vocabulary_age'] = 
  'Word concreteness : Vocabulary age'

rownames(lexicaldecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_word_concreteness:z_recoded_participant_gender'] = 
  'Word concreteness : Gender'

rownames(lexicaldecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_vocabulary_age:z_word_frequency'] = 
  'Word frequency : Vocabulary age'

rownames(lexicaldecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_vocabulary_age:z_visual_rating'] = 
  'Visual strength : Vocabulary age'

rownames(lexicaldecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_recoded_participant_gender:z_word_frequency'] = 
  'Word frequency : Gender'

rownames(lexicaldecision_summary_weaklyinformativepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
    'z_recoded_participant_gender:z_visual_rating'] = 
  'Visual strength : Gender'

# Create table (using custom function from the 'R_functions' folder)
bayesian_model_table(
  lexicaldecision_summary_weaklyinformativepriors_exgaussian, 
  order_effects = c('(Intercept)',
                    'Vocabulary age $^{\\text{a}}$',
                    'Gender $^{\\text{a}}$',
                    'Orthographic Levenshtein distance $^{\\text{b}}$',
                    'Word concreteness $^{\\text{b}}$',
                    'Word frequency $^{\\text{b}}$',
                    'Visual strength $^{\\text{b}}$',
                    'Word concreteness : Vocabulary age',
                    'Word concreteness : Gender',
                    'Word frequency : Vocabulary age',
                    'Visual strength : Vocabulary age',
                    'Word frequency : Gender',
                    'Visual strength : Gender'),
  interaction_symbol_x = TRUE,
  caption = 'Weakly-informative prior model for the lexical decision study.') %>%
  # kable_styling(latex_options = 'scale_down') %>%

  # Group predictors under headings
  pack_rows('Individual differences', 2, 3) %>% 
  pack_rows('Lexical covariate', 4, 4) %>% 
  pack_rows('Semantic variables', 5, 7) %>% 
  pack_rows('Interactions', 8, 13) %>%

  # Place table close to designated position and highlight covariates
  kable_styling(latex_options = c('HOLD_position', 'striped'), 
                stripe_index = c(4:5, 8:9)) %>%

  # Footnote describing abbreviations, random slopes, etc. 
  # LaTeX code used to format the text.
  footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on z-scored variables; \\\\textit{SE} = standard error;',
                           'CrI = credible interval. Shaded rows contain covariates. \\\\linebreak', 
                           '$^{\\\\text{a}}$ By-word random slopes were included for this effect.',
                           '$^{\\\\text{b}}$ By-participant random slopes were included for this effect.', 
                           # Begin lines after first one with a dot-sized indent
                           sep = ' \\\\linebreak \\\\phantom{.}'))

```

```{r lexicaldecision-diffusepriors-model, results = 'asis'}

rownames(lexicaldecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_vocabulary_age'] = 'Vocabulary age $^{\\text{a}}$'

rownames(lexicaldecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_recoded_participant_gender'] = 'Gender $^{\\text{a}}$'

rownames(lexicaldecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_orthographic_Levenshtein_distance'] = 'Orthographic Levenshtein distance $^{\\text{b}}$'

rownames(lexicaldecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_word_concreteness'] = 'Word concreteness $^{\\text{b}}$'

rownames(lexicaldecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_word_frequency'] = 'Word frequency $^{\\text{b}}$'

rownames(lexicaldecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_visual_rating'] = 'Visual strength $^{\\text{b}}$'

rownames(lexicaldecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_word_concreteness:z_vocabulary_age'] = 
  'Word concreteness : Vocabulary age'

rownames(lexicaldecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_word_concreteness:z_recoded_participant_gender'] = 
  'Word concreteness : Gender'

rownames(lexicaldecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_vocabulary_age:z_word_frequency'] = 
  'Word frequency : Vocabulary age'

rownames(lexicaldecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_vocabulary_age:z_visual_rating'] = 
  'Visual strength : Vocabulary age'

rownames(lexicaldecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_recoded_participant_gender:z_word_frequency'] = 
  'Word frequency : Gender'

rownames(lexicaldecision_summary_diffusepriors_exgaussian$fixed)[
  rownames(lexicaldecision_summary_diffusepriors_exgaussian$fixed) == 
    'z_recoded_participant_gender:z_visual_rating'] = 
  'Visual strength : Gender'

# Create table (using custom function from the 'R_functions' folder)
bayesian_model_table(
  lexicaldecision_summary_diffusepriors_exgaussian, 
  order_effects = c('(Intercept)',
                    'Vocabulary age $^{\\text{a}}$',
                    'Gender $^{\\text{a}}$',
                    'Orthographic Levenshtein distance $^{\\text{b}}$',
                    'Word concreteness $^{\\text{b}}$',
                    'Word frequency $^{\\text{b}}$',
                    'Visual strength $^{\\text{b}}$',
                    'Word concreteness : Vocabulary age',
                    'Word concreteness : Gender',
                    'Word frequency : Vocabulary age',
                    'Visual strength : Vocabulary age',
                    'Word frequency : Gender',
                    'Visual strength : Gender'),
  interaction_symbol_x = TRUE,
  caption = 'Diffuse prior model for the lexical decision study.') %>%
  # kable_styling(latex_options = 'scale_down') %>%

  # Group predictors under headings
  pack_rows('Individual differences', 2, 3) %>% 
  pack_rows('Lexical covariate', 4, 4) %>% 
  pack_rows('Semantic variables', 5, 7) %>% 
  pack_rows('Interactions', 8, 13) %>%

  # Place table close to designated position and highlight covariates
  kable_styling(latex_options = c('HOLD_position', 'striped'), 
                stripe_index = c(4:5, 8:9)) %>%

  # Footnote describing abbreviations, random slopes, etc. 
  # LaTeX code used to format the text.
  footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on z-scored variables; \\\\textit{SE} = standard error;',
                           'CrI = credible interval. Shaded rows contain covariates. \\\\linebreak', 
                           '$^{\\\\text{a}}$ By-word random slopes were included for this effect.',
                           '$^{\\\\text{b}}$ By-participant random slopes were included for this effect.', 
                           # Begin lines after first one with a dot-sized indent
                           sep = ' \\\\linebreak \\\\phantom{.}'))

```

Figure \@ref(fig:lexicaldecision-frequentist-bayesian-plot-allpriors-exgaussian) presents the posterior distribution of each effect in each model. The frequentist estimates are also shown to facilitate the comparison.

```{r lexicaldecision-frequentist-bayesian-plot-allpriors-exgaussian, fig.cap = 'Estimates from the frequentist analysis (in red) and from the Bayesian analysis (in blue) for the lexical decision study, in each model. The frequentist means (represented by points) are flanked by 95\\% confidence intervals. The Bayesian means (represented by vertical lines) are flanked by 95\\% credible intervals, in light blue (in some cases, the interval is covered up by the bar of the mean).'}

# Run plot through source() rather than directly in this R Markdown document
# to preserve the format.

source('lexicaldecision/frequentist_bayesian_plots/lexicaldecision_frequentist_bayesian_plots.R', 
       local = TRUE)

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/lexicaldecision/frequentist_bayesian_plots/plots/lexicaldecision_frequentist_bayesian_plot_allpriors_exgaussian.pdf'
  ))

```

### 2022-06-24 manuscript/manuscript.Rmd
24062022

---
title: 'Language and vision in conceptual processing: Multilevel analysis and statistical power'

shorttitle: LANGUAGE AND VISION IN CONCEPTUAL PROCESSING

authornote: |
  \addORCIDlink{Pablo Bernabeu}{0000-0003-1083-2460}

  \addORCIDlink{Dermot Lynott}{0000-0001-7338-0567}

  \addORCIDlink{Louise Connell}{0000-0002-5291-5267}

  This manuscript is a draft and includes some appendices. Correspondence can be addressed to Pablo Bernabeu on pcbernabeu@gmail.com. All materials are available at [http://doi.org/10.17605/OSF.IO/UERYQ](http://doi.org/10.17605/OSF.IO/UERYQ).

abstract: |
   Research over the past two decades has suggested that conceptual processing depends on both language-based and vision-based information. We tested this interplay at three levels of the data: individual differences, words and tasks. To this aim, we drew on three existing data sets that were composed of large samples, and implemented the paradigms of semantic priming, semantic decision and lexical decision. After extending these data sets with language-based and vision-based measures, we performed the analysis using mixed-effects models that included a comprehensive array of fixed effects---including covariates---and random effects. Overall, language-based information was found to be more important than vision-based information. Furthermore, in the semantic priming study---whose task required distinguishing between words and nonwords---, both language-based and vision-based information were more influential when words were presented faster. In addition, higher-vocabulary participants presented a greater effect of language-based similarity than lower-vocabulary participants. Conversely, lower-vocabulary participants presented a greater effect of vision-based information, which was less relevant to the task. This 'relevance advantage' for higher-vocabulary participants also appeared in the semantic decision study, whose task required distinguishing between concrete and abstract words. Specifically, higher-vocabulary participants were more strongly influenced by word concreteness than lower-vocabulary participants. Furthermore, we compared the effects of different measures of visual information. Lastly, we estimated the sample size required to reliably examine each effect of interest. We found that 300 participants would suffice to examine language-based information contained in words, whereas more than 1,000 participants would be necessary to examine vision-based information as well as the interactions between both the former variables and vocabulary size, gender and presentation speed.

keywords: semantic, conceptual processing, vocabulary size, statistical power

bibliography: ['references.bib', 'package-references.bib']

# APPENDICES are inserted through code chunks at the end of this document.
# The source code for each appendix is in the 'manuscript' folder.

floatsintext:       yes
figurelist:         no
tablelist:          no
footnotelist:       no
linenumbers:        no
mask:               no

csl:                "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass:      apa7
classoption:        man

fontsize:           12pt
linestretch:        1.5

output:
  papaja::apa6_pdf:
    extra_dependencies: ["flafter"]   # Place figures and tables below where they are first mentioned in the text.

# Latex preamble specifying layout
header-includes: 
# Background on the first four lines: https://stackoverflow.com/a/70658799/7050882
  - \renewcommand\author[1]{}
  - \renewcommand\affiliation[1]{}
  - \authorsnames[1, 2, 2]{Pablo Bernabeu, Dermot Lynott, Louise Connell}
  - \authorsaffiliations{{Department of Psychology, Lancaster University, UK}, {Department of Psychology, Maynooth University, Ireland}}
  - \renewcommand{\topfraction}{.75}        # Reduce page margins
  - \renewcommand{\bottomfraction}{.4}      # Reduce page margins
  - \renewcommand{\textfraction}{.15}       # Reduce page margins
  - \renewcommand{\floatpagefraction}{.6}   # Reduce page margins
  - \setlength{\@fptop}{0pt}                # Vertically-align tables & figures to the top
  - \setcounter{topnumber}{3}               # Reduce page margins
  - \setcounter{bottomnumber}{2}            # Reduce page margins
  - \setcounter{totalnumber}{4}             # Reduce page margins
  - \usepackage{amsmath}                    # Maths formatting
  - \usepackage{upgreek}                    # Disable the italicisation of Greek letters
  - \usepackage{booktabs}                   # Dependency for R package 'kableExtra' (table formatting)
  - \usepackage{longtable}                  # Dependency for R package 'kableExtra' (table formatting)
  - \usepackage{array}                      # Dependency for R package 'kableExtra' (table formatting)
  - \usepackage{multirow}                   # Dependency for R package 'kableExtra' (table formatting)
  - \usepackage{wrapfig}                    # Dependency for R package 'kableExtra' (table formatting)
  - \usepackage{float}                      # Dependency for R package 'kableExtra' (table formatting)
  - \usepackage{colortbl}                   # Dependency for R package 'kableExtra' (table formatting)
  - \usepackage{pdflscape}                  # Dependency for R package 'kableExtra' (table formatting)
  - \usepackage{tabu}                       # Dependency for R package 'kableExtra' (table formatting)
  - \usepackage{threeparttable}             # Dependency for R package 'kableExtra' (table formatting)
  - \usepackage{threeparttablex}            # Dependency for R package 'kableExtra' (table formatting)
  - \usepackage[normalem]{ulem}             # Dependency for R package 'kableExtra' (table formatting)
  - \usepackage{makecell}                   # Dependency for R package 'kableExtra' (table formatting)
  - \usepackage{xcolor}                     # Dependency for R package 'kableExtra' (table formatting)
  - \renewcommand\appendix{}                # Remove redundant label
---

```{r setup, include = FALSE}

# General knitr options
knitr::opts_chunk$set(cache = FALSE, message = FALSE, warning = FALSE, 
                      error = FALSE, echo = FALSE, 
                      knitr.duplicate.label = 'allow', 
                      fig.align = 'center', dev = 'CairoPDF', 
                      knitr.graphics.auto_pdf = TRUE, dpi = 72, 
                      out.width = '100%')

library(papaja)       # APA-formatted manuscript
library(knitr)        # Document rendering
options(kableExtra.latex.load_packages = FALSE)  # instead, LaTeX packages loaded in header/preamble above
library(kableExtra)   # Tables
library(dplyr)        # Data wrangling
library(formattable)  # Format numbers
library(kableExtra)   # Table formatting (e.g., `pack_rows()`)
library(stringr)      # Text processing
library(ggplot2)      # Plots
library(GGally)       # Correlation plots
library(sjPlot)       # Model plots
library(RColorBrewer) # Colours in plots
library(patchwork)    # Combination of plots
library(Cairo)        # Allows use of special characters such as dashes in plots
library(magick)       # Image rendering
library(tikzDevice)   # Image rendering

# Move working directory to the project root
knitr::opts_knit$set(root.dir = '../')

```

```{r load-functions-data-models, include = FALSE}

# Read in all custom functions
setwd('R_functions')
sapply(list.files(), source, echo = FALSE)
setwd('../')

# Load main data sets and models. These objects are loaded directly, rather than 
# being run on the go, to keep the knitting of the manuscript reasonably fast. 
# Crucially, however, all the objects can be reproduced from the appropriate R 
# scripts in the current project. For further details, see 'README.pdf' in 
# 'manuscript' directory.

# Study 1: Semantic priming

# Code for data set below in 'semanticpriming/data' folder
semanticpriming = read.csv('semanticpriming/data/final_dataset/semanticpriming.csv')

# Code for models below in 'semanticpriming/frequentist_analysis' folder
semanticpriming_lmerTest =   # Primary model object
  readRDS('semanticpriming/frequentist_analysis/results/semanticpriming_lmerTest.rds')
KR_summary_semanticpriming_lmerTest =   # Model with Kenward-Roger p values
  readRDS('semanticpriming/frequentist_analysis/results/KR_summary_semanticpriming_lmerTest.rds')
confint_semanticpriming_lmerTest =   # Confidence intervals
  readRDS('semanticpriming/frequentist_analysis/results/confint_semanticpriming_lmerTest.rds')

# Subset of the semantic priming study that included visual similarity.
# Code for data set below in 'semanticpriming/data' folder
semanticpriming_with_visualsimilarity = 
  read.csv('semanticpriming/data/subset_with_visualsimilarity/semanticpriming_with_visualsimilarity.csv')

# Code for models below in 'semanticpriming/semanticpriming_with_visualsimilarity' folder
semanticpriming_with_visualsimilarity_lmerTest =   # Primary model object
  readRDS('semanticpriming/analysis_with_visualsimilarity/results/semanticpriming_with_visualsimilarity_lmerTest.rds')
KR_summary_semanticpriming_with_visualsimilarity_lmerTest =   # Model with Kenward-Roger p values
  readRDS('semanticpriming/analysis_with_visualsimilarity/results/KR_summary_semanticpriming_with_visualsimilarity_lmerTest.rds')
confint_semanticpriming_with_visualsimilarity_lmerTest =   # Confidence intervals
  readRDS('semanticpriming/analysis_with_visualsimilarity/results/confint_semanticpriming_with_visualsimilarity_lmerTest.rds')

# Code for models below in 'semanticpriming/bayesian_analysis' folder
semanticpriming_summary_informativepriors_exgaussian =   # Primary model object
  readRDS('semanticpriming/bayesian_analysis/results/semanticpriming_summary_informativepriors_exgaussian.rds')
# semanticpriming_summary_weaklyinformativepriors_exgaussian =   # Primary model object
#   readRDS('semanticpriming/bayesian_analysis/results/semanticpriming_summary_weaklyinformativepriors_exgaussian.rds')
semanticpriming_summary_diffusepriors_exgaussian =   # Primary model object
  readRDS('semanticpriming/bayesian_analysis/results/semanticpriming_summary_diffusepriors_exgaussian.rds')

# Study 2: Semantic decision
# Code for data set below in 'semanticdecision/data' folder
semanticdecision = read.csv('semanticdecision/data/final_dataset/semanticdecision.csv')

# Code for models below in 'semanticdecision/frequentist_analysis' folder
semanticdecision_lmerTest =   # Primary model object
  readRDS('semanticdecision/frequentist_analysis/results/semanticdecision_lmerTest.rds')
KR_summary_semanticdecision_lmerTest =   # Model with Kenward-Roger p values
  readRDS('semanticdecision/frequentist_analysis/results/KR_summary_semanticdecision_lmerTest.rds')
confint_semanticdecision_lmerTest =   # Confidence intervals
  readRDS('semanticdecision/frequentist_analysis/results/confint_semanticdecision_lmerTest.rds')

# Code for models below in 'semanticdecision/bayesian_analysis' folder
semanticdecision_summary_informativepriors_exgaussian =   # Primary model object
  readRDS('semanticdecision/bayesian_analysis/results/semanticdecision_summary_informativepriors_exgaussian.rds')
semanticdecision_summary_weaklyinformativepriors_exgaussian =   # Primary model object
  readRDS('semanticdecision/bayesian_analysis/results/semanticdecision_summary_weaklyinformativepriors_exgaussian.rds')
semanticdecision_summary_diffusepriors_exgaussian =   # Primary model object
  readRDS('semanticdecision/bayesian_analysis/results/semanticdecision_summary_diffusepriors_exgaussian.rds')

# Study 3: Lexical decision
# Code for data set below in 'lexicaldecision/data' folder
lexicaldecision = read.csv('lexicaldecision/data/final_dataset/lexicaldecision.csv')

# Code for models below in 'lexicaldecision/frequentist_analysis' folder
lexicaldecision_lmerTest =   # Primary model object
  readRDS('lexicaldecision/frequentist_analysis/results/lexicaldecision_lmerTest.rds')
KR_summary_lexicaldecision_lmerTest =   # Model with Kenward-Roger p values
  readRDS('lexicaldecision/frequentist_analysis/results/KR_summary_lexicaldecision_lmerTest.rds')
confint_lexicaldecision_lmerTest =   # Confidence intervals
  readRDS('lexicaldecision/frequentist_analysis/results/confint_lexicaldecision_lmerTest.rds')

# Code for models below in 'lexicaldecision/bayesian_analysis' folder
lexicaldecision_summary_informativepriors_exgaussian =   # Primary model object
  readRDS('lexicaldecision/bayesian_analysis/results/lexicaldecision_summary_informativepriors_exgaussian.rds')
lexicaldecision_summary_weaklyinformativepriors_exgaussian =   # Primary model object
  readRDS('lexicaldecision/bayesian_analysis/results/lexicaldecision_summary_weaklyinformativepriors_exgaussian.rds')
lexicaldecision_summary_diffusepriors_exgaussian =   # Primary model object
  readRDS('lexicaldecision/bayesian_analysis/results/lexicaldecision_summary_diffusepriors_exgaussian.rds')

```

#

Research over the past two decades has suggested that conceptual processing involves both 'linguistic' and 'embodied' systems of the brain. The language system is characterised by associations across networks of words [@landauerIntroductionLatentSemantic1998; @pylyshynWhatMindEye1973], whereas the embodiment system is characterised by associations within perceptual, motor, affective and social domains [@barsalouPerceptualSymbolSystems1999; @diveicaQuantifyingSocialSemantics2022]. Both systems have strengths and limitations [@connell2019a; @dove2020a; @kumar2021a; @louwerse2015a; @mahon2016a]. As a result, conceptual processing flexibly draws on these systems following the demands of the context [@satoTaskRelatedModulation2008; @shebaniFlexibilityLanguageAction2018; @willemsFlexibilityEmbodiedLanguage2011].

The language system is involved in the representation of both abstract and concrete concepts [@ponari2018a; @regginDevelopmentAbstractWord2021]. For instance, measures of distributional semantic distance---solely based on texts---have been shown to capture aspects of the real world with considerable accuracy [@contreraskallensQuantifyingInterdisciplinarityCognitive2022; @dedeyneBetterExplanationsLexical2013; @kumarDistantConnectivityMultiplestep2020; @louwerseLanguageEncodesGeographical2009]. Although the language system is likely more important for the processing of abstract---rather than concrete---concepts [@barca2020a; @dunabeitiaQualitativeDifferencesRepresentation2009; @hultenNeuralRepresentationAbstract2021], although the degree of this difference could be small [@dedeyneBetterExplanationsLexical2013]. Language-based regularities may even allow distinguishing between concrete and abstract words, as word concreteness is consistently related to linguistic characteristics such as part of speech, morphological structure, countability and etymology [@lieversLinguisticDimensionsConcrete2021].

Regarding the time course, the language system is activated more quickly in semantically-deep tasks [@connell2013a; @louwerseTasteWordsLinguistic2011], whereas both systems are similarly fast in semantically-shallow tasks [@petilli2021a]. As a result of these characteristics, the language system is equipped to support a major part of conceptual processing [@connell2019a; @connellSeeHearWhat2014]. However, the language system is hindered by the symbol grounding problem, which refers to the impossibility of obtaining meaning---or 'grounding' lexical content in reality---on the sole basis of word-to-word associations [@guntherLimitsAutomaticSensorimotor2021; @guntherSymbolGroundingDirect2018; @louwerseSymbolInterdependencySymbolic2011; @harnadSymbolGroundingProblem1990]. Another limitation is caused by the finite vocabularies of languages, which sometimes fall short of the richness of sensorimotor experience [@guntherLimitsAutomaticSensorimotor2021; @dedeyneVisualAffectiveMultimodal2021; @majidOdorsAreExpressible2014; @majidSensesLanguageCulture2011; @majidCanNomenclatureBody2015]. In conclusion, word-to-word associations appear to be necessary but not sufficient for conceptual processing.

The embodiment system is best suited for the representation of concrete concepts, such as those involving perceptual features [@pecherDoesPizzaPrime1998; @yeeColorlessGreenIdeas2012; @ostarekTaskdependentCausalRole2017] and actions [@riccardiDissociatingActionAbstract2019]. Some research has suggested that embodied simulation plays an integral role in conceptual processing [@pulvermullerHowNeuronsMake2013], at least in the context of relatively-semantic tasks and stimuli [@leboisAreAutomaticConceptual2015; @pecherDoesPizzaPrime1998; @yeeColorlessGreenIdeas2012; @ostarekTaskdependentCausalRole2017; @connellWeKnowWhat2016; @garciaTimeFaceLanguage2020; @shebaniWhatImpairedSpatial2021; @vitaleNeuralInhibitionNetwork2021; @vukovicPrimaryMotorCortex2017; @wangSocialEmotionDimensional2021]. For instance, @riccardiDissociatingActionAbstract2019 investigated the comprehension of action verbs and abstract verbs in left-hemisphere stroke patients, and found that the processing of action concepts relied more heavily on sensory-motor areas. Furthermore, studies have suggested that even abstract concepts may be partially grounded in modality-specific domains such as emotion, sociality and interoception [@concaSearchDifferentCategories2021; @connellInteroceptionForgottenModality2018; @diveicaQuantifyingSocialSemantics2022; @kousta2011a; @vigliocco2014a; @wangSocialEmotionDimensional2021].

However, other research has curtailed the importance of this system [@mahonCriticalLookEmbodied2008; @bottiniConcretenessAdvantageLexical2021; @garceaPreservedToolKnowledge2013; @guntherSymbolGroundingDirect2018; @guntherLimitsAutomaticSensorimotor2021; @montero-melisNoEvidenceEmbodiment2022; @vannuscorpsPersistentSparingAction2016]. For instance, studies have found that lesions to motor brain areas did not systematically impair the processing of action concepts in language [@papeoActionPerformanceActionword2010; @negriWhatRoleMotor2007].

## Interplay between language and embodiment systems

The above characteristics make the language and the embodiment systems complementary to each other [@andrewsIntegratingExperientialDistributional2009; @dedeyneVisualAffectiveMultimodal2021; @wangNeuralRepresentationAbstract2010]. A comprehensive approach to both these systems requires a direct comparison of them. Studies tackling such a comparison have found that the systems are selectively engaged, following contextual demands [@connell2013a; @louwerseTasteWordsLinguistic2011; @ostarekTaskdependentCausalRole2017; @petilli2021a]. For instance, the role of perceptual simulation appears to be augmented in slower responses [@louwerseTasteWordsLinguistic2011], when words are presented more slowly [@lam2015a], and in tasks prompting deeper semantic processing [@connell2013a; @louwerseTasteWordsLinguistic2011; @ostarekTaskdependentCausalRole2017; @petilli2021a].

# The present study

There is considerable evidence supporting the 'hybrid' theory positing that conceptual processing depends on both language and embodiment systems [@barsalouLanguageSimulationConceptual2008; @louwerseSymbolInterdependencySymbolic2011; @connell2013a]. Nonetheless, there are also reasons to continue testing this theory. Firstly, the coexistence of several systems in a scientific theory must be thoroughly justified, due to the value of simplicity, as epitomised by Occam's razor [@galleseBrainConceptsRole2005; @tillmanHowSharpOccam2015]. This point is particularly pressing because the language system has consistently produced larger effect sizes than the embodiment system [@lam2015a; @pecherDoesPizzaPrime1998; @petilli2021a; @banksLinguisticDistributionalKnowledge2021; @kiela2014a; @louwerse2015a]. Secondly, mixed evidence has appeared regarding some aspects of the interplay. For instance, whereas some studies have suggested that the language system becomes relevant before the embodiment system [@lam2015a; @louwerseTasteWordsLinguistic2011], a recent study found the opposite pattern [@petilli2021a]. Similarly, whereas some evidence has suggested that female participants might draw on the language system more prominently than males [@hutchinson2013a], other research has suggested that this difference could be negligible [@wallentinChapterGenderDifferences2020]. Thirdly, the role of individual differences has not been examined in most of the studies addressing the language--embodiment interplay. Fourthly and last, the scarcity of statistical power that has ailed some studies in cognitive psychology and neuroscience [@vasishthHowEmbraceVariation2021; @marekReproducibleBrainwideAssociation2022] is likely to have affected some studies in the present topic area, too [see @lynottReplicationExperiencingPhysical2014; @montero-melisNoEvidenceEmbodiment2022].

The above open questions were addressed in the present study. These questions were overarched by the main research question, which examined whether the interplay between linguistic and visual processing held in the expected direction and at multiple levels of the experimental structure. To study this question, we drew on the data sets from three previous studies whose samples of participants were larger than average. These studies implemented the paradigms of semantic priming [@hutchison2013a], semantic decision [@pexman2017a] and lexical decision [@balota2007a]. Importantly, we extended these data sets with

# Levels of analysis

Experimental data in psycholinguistics often consists of various levels, such as participants, words and tasks. A simultaneous examination of these levels should improve our understanding of the evidence collected [@ostarekStrongInferenceResearch2021]. For instance, this cross-examination can help increase our certainty on the attribution of explanatory power to each level, as well as allowing a comparison of the explanatory power across levels. This multilevel approach is complementary to another approach in the field which seeks to test the causal contribution of different sources of information to conceptual processing---e.g., language [@ponari2018a], perception [@stasenkoWhenConceptsLose2014] and action [@speedImpairedComprehensionSpeed2017].

The three levels examined in this study are described below.

## Participant level

*** to be edited *** Individual differences in domains such as language, perception, mental imagery and physical experience [e.g., @davies2017a; @dils2010a; @fettermanFeelingWarmBeing2018; @holt2006a; @mak2019a; @miceliDifferencesRelatedAging2022; @pexman2018a; @vukovic2015a; @yap2012a; @yap2017a].^[According to @lamiellStatisticalThinkingPsychology2019, 'individual differences' is a misnomer in that the methods used to analyse individual differences (e.g, regression) are not participant-specific. We think that this observation is mitigated in the context of mixed-effects models (as used in our current study), which incorporate by-participant random intercepts and random slopes.] Furthermore, in some topic areas in which individual differences have not featured as prominently, the data have revealed a non-trivial role of individual differences [@montero-melisConsistencyMotionEvent2021; @kosIndividualVariationLate2012].

### Vocabulary size

Vocabulary size refers to the number of words a person can recognise out of a discrete set. Higher-vocabulary participants are expected to respond faster overall [@pexman2018a]. Some previous studies have found that the effect of vocabulary size was moderated by variables related to general intelligence, such as processing speed [@ratcliff2010a; @yap2012a]. Owing to those findings, and the recommendations from other studies [@james2018a; @pexman2018a; @sassenhagenCommonMisapplicationStatistical2016], the present studies included covariates of vocabulary size, where available.These covariates were measures of intelligence that were not vocabulary-based, namely, attentional control in Study 1 and information uptake in Study 2 (such a variable was not available for Study 3).

## Word level

*** to be edited *** Semantic or lexical information in words [e.g., @dedeyneVisualAffectiveMultimodal2021; @lam2015a; @lund1995a; @lund1996a; @lynott2020a; @mandera2017a; @pexman2017a; @santosPropertyGenerationReflects2011; @wingfieldUnderstandingRoleLinguistic2022]

- *Variables in this study:* degree of association between words, degree of vision-based information in single words

- Covariates: lexical variables and word concreteness.

  - Lexical variables: The lexical covariates were selected in each study out of the same 5 variables, which have been identified as important in previous research (Wingfield & Connell, 2022; see [\underline{General statistical analysis}](#general-statistical-analyses) for details).

  - Word concreteness: Adjusting for word concreteness was deemed important due to the pervasive effect of this variable across lexical-semantic tasks [@brysbaert2014a; @connellStrengthPerceptualExperience2012; @pexman2018a]. Furthermore, it has been recently suggested that the effect of word concreteness does not stem from perceptual simulation, but instead from modality-independent properties of words [@bottiniConcretenessAdvantageLexical2021].

Studies have operationalised the *language system* using measures that capture the relationships among words without explicitly drawing on any sensory or affective modalities. Two main types of linguistic measures exist: those based on text corpora---dubbed *word co-occurrence* measures [@bullinariaExtractingSemanticRepresentations2007; @petilli2021a; @wingfieldUnderstandingRoleLinguistic2022]---and those based on associations collected from human participants---dubbed *word association* measures [@de2016a; @de2019a]. Word co-occurrence is more purely linguistic, as word association captures more of the sensory and affective meaning of words [@dedeyneVisualAffectiveMultimodal2021]. In Studies 1 and 2 below, word co-occurrence measures are used to represent the language system at the word level. In Study 3, however, such a measure could not be implemented. The measurement of priming across consecutive trials was not possible due to the high prevalence of nonword trials throughout the experiment.

The embodiment system has been represented by measures that explicitly draw on perceptual, motor or affective modalities [@fernandinoDecodingInformationStructure2022]. The perceptual modalities used in studies have often matched the 5 prototypical senses---vision, hearing, touch, taste, smell [@bernabeu2017a; @bernabeu2021a; @louwerseTasteWordsLinguistic2011]---and, less often, interoception [@connellInteroceptionForgottenModality2018]. Yet, out of these senses, vision has been most frequently used in research [e.g., @bottiniConcretenessAdvantageLexical2021; @dedeyneVisualAffectiveMultimodal2021; @pearsonHeterogeneityMentalRepresentation2015; @petilli2021a; @yeeColorlessGreenIdeas2012]. The prevalence of vision in research could be due to the prevalence of this sense in the brain [@reillyEnglishLexiconMirrors2020] and in language [@lynott2020a; @winterVisionDominatesPerceptual2018]. Furthermore, for the purpose of examining individual differences along with word-level variables, vision is easier to tap into than other senses. For instance, the perception of visual motion can be measured using a standard computer screen [@rajanandaRandomdotKinematogramWebbased2018]. Owing to these reasons, the three studies reported below implement the visual modality to represent the embodiment system at the word level.

## Task level

*** to be edited ***

- *Variable in this study:* stimulus-onset asynchrony (SOA), present in Study 1 only.^[The names of all variables were slightly adjusted for this text to facilitate their understanding---for instance, by replacing underscores with spaces (see code scripts at [https://osf.io/ueryq](https://osf.io/ueryq)). One specific case deserves further comment. We use the formula of the 'stimulus-onset asynchrony' (SOA) in this paper, instead of the 'interstimulus interval' (ISI), as the SOA has been more commonly used in previous papers [e.g., @hutchison2013a; @pecherDoesPizzaPrime1998; @petilli2021a; @yap2017a]. The difference between these formulas is that the ISI does not count the presentation of the prime word [example equivalences between ISI and SOA are available in @lam2015a, and in Figure 1A of @dilolloDecouplingStimulusDuration2004]. In the current study, the presentation of the prime word lasts 150 ms. Thus, the 200-ms SOA is equivalent to an ISI of 50 ms, and the 1,200-ms SOA corresponds to an ISI of 1,050 ms [@hutchison2013a]. The use of either formula in the analysis would not change our results, as we recoded the levels of the factor as -0.5 and +0.5, and then $z$-scored those, following the advice of @brauer2018a. In our analyses ([https://osf.io/ueryq](https://osf.io/ueryq)), we used the ISI formula as it was the one present in the data set of @hutchison2013a (retrieved from [https://www.montana.edu/attmemlab/documents/all%20ldt%20subs_all%20trials3.xlsx](https://www.montana.edu/attmemlab/documents/all%20ldt%20subs_all%20trials3.xlsx)]).

In addition, the different paradigms applied across the three studies can be compared, albeit cautiously as the studies differ in other influential ways, such as the number of participants and stimulus words. The three tasks examined in the present studies are likely to reflect different degrees of semantic depth, in the following order [for background, see @connell2013a; @lam2015a; @ostarekTaskdependentCausalRole2017; @versaceImpactEmbodiedSimulation2021; @wingfieldUnderstandingRoleLinguistic2022].

1. **Semantic decision** (Study 2) likely elicits the deepest semantic processing, as the instructions of this task ask for a concreteness judgement. In this task, participants are asked to classify words as abstract or concrete.

2. **Semantic priming** (Study 1). The task in the semantic priming paradigm is often lexical decision, as in Study 1 herein. The fundamental characteristic of this paradigm is that, in each trial, a prime word is presented for a very short period before the target word. The prime word is not relevant to the task. Nonetheless, participants process both the prime word and the target word, and this combination allows researchers to analyse responses based on the relationship between those words. Therefore, this paradigm is more deeply semantic than the lexical decision paradigm. Indeed, slower responses in semantic priming studies---reflecting difficult lexical decisions---have been linked to larger priming effects [@balotaMeanResponseLatency2008; @hoedemakerItTakesTime2014; @yapAdditiveInteractiveEffects2013], suggesting a degree of semantic association that does not appear in the standard lexical decision paradigm.

3. **Lexical decision** (Study 3) is likely the semantically-shallowest task [see @balotaDepthAutomaticSpreading1986; @beckerLongtermSemanticPriming1997; @connell2013a; @dewitMaskedSemanticPriming2015; @joordensLongShortSemantic1997; @ostarekTaskdependentCausalRole2017].

## Interactions across levels

The three levels are strongly intertwined, and studies have probed into more than one level at once: for instance, word level and individual level [@aujlaLanguageExperiencePredicts2021; @lim2020a; @pexman2018a; @yapIndividualDifferencesJoint2009], or word level and task level [@al-azaryCanYouTouch2022; @connell2013a; @ostarekSixChallengesEmbodiment2019; @petilli2021a]. Thus, hypotheses are available regarding interactions across levels, as addressed below.

### Vocabulary size and linguistic features

Three hypotheses exist regarding the interaction between vocabulary size and lexical-semantic features. First, higher-vocabulary participants---compared to lower-vocabulary ones---might be more sensitive to linguistic features, thanks to a larger number of semantic associations [@connell2019a; @landauerIntroductionLatentSemantic1998; @louwerse2015a; @paivioMentalRepresentationsDual1990; @pylyshynWhatMindEye1973]. For instance, @yap2017a observed a larger semantic priming effect in higher-vocabulary participants from [@hutchinson2013a]. The second hypothesis, in contrast, states that higher-vocabulary participants would be *less* sensitive to linguistic features, thanks to a more automatic process. For instance, @yapIndividualDifferencesJoint2009 observed a smaller semantic priming effect in higher-vocabulary participants. Similarly, @yap2012a found that higher-vocabulary participants in a lexical decision task [@balota2007a] were less sensitive to a cluster of lexical and semantic features (i.e., word frequency, semantic neighborhood density and number of senses). Last, the third hypothesis proposes that higher-vocabulary participants might present a selective sensitivity, tailored to the task. For instance, @pexman2018a analysed the semantic decision task of @pexman2017a, in which participants assessed the concreteness of words. Pexman and Yap found that higher-vocabulary participants---compared to lower-vocabulary ones---were more sensitive to word concreteness and less sensitive to word frequency and age of acquisition, which were less relevant to the task [also see @lim2020a]. The three hypotheses herein were tested in the present study by revisiting some of the aforementioned studies [@hutchinson2013a; @pexman2017a; @balota2007a].

### Vocabulary size and visual strength

Research demonstrating the interplay between linguistic and embodied information [@connell2019a; @louwerse2015a; @paivioMentalRepresentationsDual1990] affords the hypothesis that lower-vocabulary participants---compared to higher-vocabulary ones---might profit more from sensory, motor, affective and social associations of the words.

### Gender and linguistic features

In addition, the language system is expected to be more important in female than male participants [@burman2008a; @hutchinson2013a; @jung2019a; @ullman2008a], provided that this interaction effect is not too small to be detected [@wallentinChapterGenderDifferences2020].

In another study, @schmidtke2018a collected human ratings on the association between words that make up compounds. Some compounds were found to be relatively transparent---e.g., *doorbell*---, and others relatively opaque---e.g., *deadline*. Furthermore, @schmidtke2018a found an interaction between semantic transparency and participants' reading experience (the latter measure encompassing vocabulary size and exposure to printed materials): namely, more experienced readers processed transparent compounds more quickly than opaque ones, whereas less experienced readers processed opaque compounds more quickly than transparent ones. This interaction suggests __________________________. Thus, ________________________.

## Power analysis

Statistical power depends on the following factors: (1) sample size---comprising the number of participants, items, trials, etc.---, (2) effect size, (3) measurement variability and (4) number of comparisons being performed [@kumleEstimatingPowerGeneralized2021]. Out of these, sample size is the factor that can best be controlled by researchers [@kumleEstimatingPowerGeneralized2021]. The three studies we present below, containing larger-than-average sample sizes, offer an opportunity to conduct an a-priori power analysis to help determine the sample size of future studies [@albersWhenPowerAnalyses2018].

### Motivations

Insufficient statistical power lowers the reliability of effect sizes, and increases the likelihood of false positive results---i.e., Type I error---and of false negative results---i.e., Type II error [@gelmanPowerCalculationsAssessing2014; @lokenMeasurementErrorReplication2017; @tverskyBeliefLawSmall1971; @vondermalsburgFalsePositivesOther2017]. For instance, @vasishthHowEmbraceVariation2021 illustrate how, in low-powered studies, effect sizes associated with significant results tend to be overestimated [also see @vasishthStatisticalSignificanceFilter2018].

Over the past decade, replication studies and power analyses have uncovered insufficient sample sizes in psychology [@brysbaertHowManyParticipants2019; @lynottReplicationExperiencingPhysical2014; @montero-melisSatelliteVsVerbframing2017; @montero-melisNoEvidenceEmbodiment2022; @rodriguez-ferreiroSemanticPrimingSchizotypal2020; @vasishthStatisticalSignificanceFilter2018]. In the neighbouring field of neuroscience, @marekReproducibleBrainwideAssociation2022 recently estimated the sample size that is required to reliably study the mapping between individual differences, such as fluid intelligence, and brain structures. Marek et al. found that the current median of 25 participants contributing to one of these studies contrasted with the thousands of participants---around 10,000---that would be needed for a well-powered study [also see @buttonPowerFailureWhy2013].

More topic-specific power analyses are necessary due to three reasons. Firstly, power analyses provide greater certainty on the reasons behind non-replications [e.g., @opensciencecollaborationEstimatingReproducibilityPsychological2015], and behind non-significant results. Indeed, insufficient power is one of the possible reasons, alongside procedural errors or subtler methodological differences, and publication bias [@andersonResponseCommentEstimating2016; @barsalouEstablishingGeneralizableMechanisms2019; @corkerHighQualityDirect2014; @gilbertCommentEstimatingReproducibility2016; @williamsImprovingPsychologicalScience2014]. Currently, if we consider---for instance---research on individual differences, we will find several non-significant results, both in behavioural studies [e.g., @hedge2018a; @rodriguez-ferreiroSemanticPrimingSchizotypal2020; for a Bayes factor analysis, see @rouderPsychometricsIndividualDifferences2019] and in neuroscientific studies [e.g., @diazNeuralSensitivityPhonological2021]. A greater availability of power analyses in specific topics will at least shed light on the role of power in the results. Secondly, power analyses facilitate the identification of sensible sample sizes for future studies. Thirdly, power analyses help maximise the use of research funding in the long term by fostering studies that are more replicable [see @vasishthHowEmbraceVariation2021].

# Methods

The analytical method was largely similar across the three studies. Below, we present the commonalities in the statistical analyses and in the power analyses.

## General method for statistical analyses {#general-statistical-analyses}

The statistical analysis was designed to examine the unique contribution of each effect of interest. In all three studies, the dependent variable---response time (RT)---was $z$-scored around each participant's mean to curb the influence of each participant's baseline speed [@balota2007a; @lim2020a; @kumarDistantConnectivityMultiplestep2020; @pexman2017a; @pexman2018a; @yap2012a; @yap2017a]. This was important because the size of experimental effects is known to increase with longer RTs [@faust1999a]. Next, binary predictors were recoded into continuous variables [@brauer2018a]. Specifically, participants' gender was recoded as follows: male = -0.5; female = 0.5; NA = 0. The SOAs in Study 1 were recoded as follows: 150 ms = -0.5; 1,200 ms = 0.5. Finally, following @brauer2018a, all predictors were $z$-scored (i.e., $M \approx$ 0, $SD \approx$ 1).

Several covariates---or nuisance variables---were included, as detailed in each study, to allow a rigorous analysis of the effects of interest [@sassenhagenCommonMisapplicationStatistical2016]. Unlike the effects of interest, these covariates were not critical to the research question. They comprised lexical variables (e.g., word frequency) and participant-specific variables (e.g., attentional control). The lexical covariates were selected in every study out of the same 5 variables, which had been used as covariates in @wingfieldUnderstandingRoleLinguistic2022, and are widely used [e.g., @petilli2021a]. They comprised: number of letters (i.e., orthographic length), word frequency, number of syllables [both the latter from @balota2007a], orthographic Levenshtein distance [@yarkoniMovingColtheartNew2008] and phonological Levenshtein distance [@suarezObservingNeighborhoodEffects2011]. The selection among these candidates was performed because some of them were highly intercorrelated---i.e., $r$ > .70 [@dormannCollinearityReviewMethods2013; @harrison2018a]. The correlations and the selection models are available in [\underline{Appendix A}](#appendix-A-lexical-covariates).

### Random effects

The participants and the stimulus items were crossed in the three studies. That is, each participant was presented with a subset of the stimulus words. Conversely, each word was presented to a subset of participants. Therefore, linear mixed-effects models were implemented. These models included a maximal random-effects structure, with by-participant and by-word random intercepts, and the appropriate random slopes for all effects of interest [@barrRandomEffectsStructure2013]. In the case of interactions, random slopes were included only when the variables interacting varied within the same unit [@brauer2018a]---e.g., an interaction of two variables varying within participants (only present in Study 1). Owing to convergence warnings, random slopes for controlled covariates were removed, inspired by Remedy 11 from @brauer2018a. Exceptionally, in the Bayesian models for the lexical decision study, the random slopes for the covariates did not have to be removed.

To avoid inflating the Type I error rate (false positives), the random slopes for the effects of interest were never removed [see Table 17 in @brauer2018a; for an example of this approach, see @diazNeuralSensitivityPhonological2021]. This approach provides a better protection against false positives [@barrRandomEffectsStructure2013; @brauer2018a; @singmann2019a] than the practice of removing random slopes when they do not significantly improve the fit [e.g., @bernabeu2017a; @pexman2018a; see @batesFittingLinearMixedeffects2015].

### Frequentist analysis

*P* values were calculated with the Kenward-Roger approximation for degrees of freedom [@luke2017a], using the 'lmerTest' package, Version 3.1-3 [@R-lmerTest]. The latter package in turn used 'lme4', Version 1.1-26 [@batesPackageLme42021; @batesFittingLinearMixedeffects2015]. Diagnostics regarding convergence and normality are provided in [\underline{Appendix B}](#appendix-B-frequentist-analysis-diagnostics).

### Bayesian analysis

In addition to the frequentist analysis, a Bayesian analysis was performed for two purposes: firstly, to enhance the interpretation of the smaller effects (which were identified as low-powered), and secondly, to complement the estimates obtained in the frequentist analysis. The latter purpose was pertinent because the frequentist models presented convergence warnings---even though it must be noted that a previous study found that frequentist and Bayesian estimates were similar despite convergence warnings appearing in the frequentist analysis [@rodriguez-ferreiroSemanticPrimingSchizotypal2020]. Furthermore, the complementary analysis was pertinent because the frequentist models presented residual errors that deviated from normality---even though mixed-effects models are fairly robust to such a deviation [@kniefViolatingNormalityAssumption2021; @schielzethRobustnessLinearMixed2020]. Owing to these precedents, we expected to find broadly similar estimates in the two approaches.

Each frequentist model in the three studies has a Bayesian counterpart, with the exception of a sub-analysis performed in the first study (semantic priming), which included 'visual similarity' as a predictor. Due to time constraints, this analysis did not include a Bayesian model. Furthermore, it must be noted that the Bayesian models in the semantic decision study did not produce valid results. Therefore, the estimates produced by these models are not shown in the main text, but they are instead in [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results).

Just as the frequentist estimates include 95% confidence intervals (CI), the Bayesian estimates include 95% credible intervals (CrI). These two types differ at a theoretical level, in that frequentist statistics are designed for the long run of testing, whereas Bayesian statistics are specific to each study [@schootBayesianStatisticsModelling2021; @vasishthStatisticalSignificanceFilter2018].

The random effects included in these models were largely the same as those included in the frequentist models. The only exception regarded the lexical decision models. In the frequentist models for lexical decision, the covariates did not carry random slopes due to the presence of convergence warnings [see Remedy 11 in @brauer2018a], whereas in the Bayesian analysis, covariates did carry random slopes because the models converged.

This Bayesian analysis was not aimed at hypothesis testing. Instead, it was designed to complement and verify the estimates that had been obtained in the frequentist analysis. Accordingly, we estimated the posterior distribution of every effect, without calculating Bayes factors [for other examples of this approach, see @milekEavesdroppingHappinessRevisited2018; @preglaVariabilitySentenceComprehension2021; @rodriguez-ferreiroSemanticPrimingSchizotypal2020; for comparisons between estimation and hypothesis testing, see @cummingNewStatisticsWhy2014; @kruschkeBayesianNewStatistics2018; @schmalzWhatBayesFactor2021; @tendeiroReviewIssuesNull2019; @tendeiroOnTheWhite2022; @rouderBayesianInferencePsychology2018; @vanravenzwaaijAdvantagesMasqueradingIssues2021]. In the estimation approach, the estimates are interpreted by considering the position of their credible intervals in relation to the predicted value of RT ($z$). That is, the closer an interval is to a value of 0 on the predicted RT ($z$), the smaller the effect of that predictor. For instance, an interval that is symmetrically centred on 0 indicates a very small effect, whereas---in comparison---an interval that does not include 0 at all indicates a far larger effect.

The R package 'brms', Version 2.17.0, was used for this analysis [@burknerPackageBrms2022; @burknerAdvancedBayesianMultilevel2018].

#### Priors

The priors were established by inspecting the effect sizes obtained in previous studies as well as the effect sizes obtained in our frequentist analyses of Studies 1, 2 and 3.

The previous studies that were considered for determining the priors were selected because they had used experimental paradigms and analytical procedures similar to those used in the current studies. Specifically, the paradigms were (I) semantic priming with a lexical decision task---as in Study 1---, (II) semantic decision---as in Study 2---,and (III) lexical decision---as in Study 3. The analytical procedures consisted of the z-scoring of the dependent and the independent variables. We found two studies that matched these characteristics: @lim2020a (see Table 5 therein) and @pexman2018a (see Tables 6 and 7 therein). These studies and the frequentist analyses reported below yielded effect sizes smaller than ±0.30. The bounds of this range were determined by the results from @pexman2018a, who found a word-concreteness effect of $\upbeta$ = 0.41 in the concrete-words analysis, and an effect of $\upbeta$ = 0.20 in the abstract-words analysis. Since we did not separate abstract from concrete words, we averaged the former values, and set -0.30 as the lower bound, and 0.30 as the upper bound. This provided the basis for informative priors. Specifically, in these informative priors, 95% of values would fall within the range [-0.30, 0.30].

Next, we considered the direction of effects. In the results of @lim2020a and @pexman2018a, and in our frequentist results, some effects consistently presented a negative direction---i.e., an inhibitory effect on RT---, whereas some other effects were consistently positive. We only incorporated the direction of effects into the priors in cases of large effects that had presented consistent directions in previous studies and in our frequentist analyses. These criteria were matched by the following variables: word frequency---with a negative direction, as higher word frequency leads to shorter RTs [@brysbaertImpactWordPrevalence2016; @brysbaertWordFrequencyEffect2018a; @lim2020a; @mendesPervasiveEffectWord2021; @pexman2018a]---, number of letters and number of syllables---both with positive directions [@bartonWordlengthEffectReading2014; @beyersmannEvidenceEmbeddedWord2020; @pexman2018a]---, and orthographic Levenshtein distance---with a positive direction [@cerniMotorExpertiseTyping2016; @dijkstraMultilinkComputationalModel2019; @kimEffectsLexicalFeatures2018; @yarkoniMovingColtheartNew2008]. We did not incorporate information about the direction of the word concreteness effect as this effect can follow different directions in abstract and concrete words [@pexman2018a], and we analysed both sets of words together. Last, it is noteworthy that some previous studies have integrated effect direction in some priors [e.g., @stoneInteractionGrammaticallyDistinct2021], but most have not [e.g., @preglaVariabilitySentenceComprehension2021; @rodriguez-ferreiroSemanticPrimingSchizotypal2020; @stoneEffectDecayLexical2020]. In conclusion, the four predictors that had directional priors were covariates (also known as nuisance variables). All the other predictors had priors centred on 0.

These priors were used on the fixed effects and on the corresponding standard deviation parameters. The correlation among the random effects had a weakly-informative prior, LKJ(2) [@lewandowskiGeneratingRandomCorrelation2009], which assumes that high correlations among the random effects are rare [also used in @rodriguez-ferreiroSemanticPrimingSchizotypal2020; @stoneEffectDecayLexical2020; @stoneInteractionGrammaticallyDistinct2021; @vasishthBayesianDataAnalysis2018].

##### Prior distributions and prior predictive checks

We aimed to perform prior sensitivity analyses of our results. Prior sensitivity analyses are checks that assess the influence of different priors on the results [@leeBayesianCognitiveModeling2014; @schootBayesianStatisticsModelling2021; @stoneEffectDecayLexical2020]. The range of priors established for this purpose varied in their standard deviations. Their means were the same, most being centred on 0, as explained above.

The priors we settled upon---shown in Figure \@ref(fig:bayesian-priors)---comprised an 'informative' prior ($SD$ = 0.1), a 'weakly-informative' one ($SD$ = 0.2) and a 'diffuse' one ($SD$ = 0.3). These priors resembled others from previous psycholinguistic studies [@preglaVariabilitySentenceComprehension2021; @stoneEffectDecayLexical2020; @stoneInteractionGrammaticallyDistinct2021]. For instance, @stoneEffectDecayLexical2020 used the following priors: $Normal$(0, 0.1), $Normal$(0, 0.3) and $Normal$(0, 1). The range of standard deviations we used---i.e., 0.1, 0.2 and 0.3---was narrower than those of previous studies because our dependent variable and our predictors were $z$-scored, resulting in small estimates and small $SD$s [see @lim2020a; @pexman2018a].

```{r bayesian-priors, fig.cap = 'Priors used in the three studies. The green vertical rectangle shows the range of plausible effect sizes based on previous studies and on our frequentist analyses.'}

source('bayesian_priors/bayesian_priors.R', local = TRUE)

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/bayesian_priors/plots/bayesian_priors.pdf'
  ))

```

The adequacy of each of these priors was assessed with prior predictive checks, in which we compared the observed data to data predicted by the priors [@schootBayesianStatisticsModelling2021]. In these checks, we also tested the adequacy of two model-wide distributions: the traditional Gaussian distribution (default in most analyses) and an exponentially modified Gaussian---dubbed 'ex-Gaussian'---distribution [@matzkePsychologicalInterpretationExGaussian2009]. The ex-Gaussian distribution was considered because the residual errors of the frequentist models were not normally distributed [@loTransformNotTransform2015], and because this distribution was found to be more appropriate than the Gaussian one in a related, previous study [see supplementary materials of @rodriguez-ferreiroSemanticPrimingSchizotypal2020]. The ex-Gaussian distribution had an identity link function, which preserves the interpretability of the coefficients, as opposed to a transformation applied directly to the dependent variable [@loTransformNotTransform2015].

Prior predictive checks revealed that the priors were adequate, and that the ex-Gaussian distribution was more appropriate than the Gaussian one, converging with @rodriguez-ferreiroSemanticPrimingSchizotypal2020 (see the corresponding plots in [\underline{Appendix D}](#appendix-D-interaction-plots)). Therefore, the ex-Gaussian distribution was used in the final models.

##### Prior sensitivity analysis

In the main analyses, the informative, weakly-informative and diffuse priors were used in separate models. In other words, in each model, all priors had the same degree of informativeness [as done in @preglaVariabilitySentenceComprehension2021; @rodriguez-ferreiroSemanticPrimingSchizotypal2020; @stoneEffectDecayLexical2020; @stoneInteractionGrammaticallyDistinct2021]. In this way, a prior sensitivity analysis was performed to acknowledge the likely influence of the priors on the posterior distributions---that is, on the results [@leeBayesianCognitiveModeling2014; @schootBayesianStatisticsModelling2021; @stoneEffectDecayLexical2020].

#### Posterior distributions

As a last diagnostic, posterior predictive checks were performed to assess the fit between the observed data and new data predicted by the posterior [@schootBayesianStatisticsModelling2021]. These checks are available in [\underline{Appendix C}](#appendix-C-Bayesian-analysis-diagnostics).

## General method for statistical power analyses

Power curves based on Monte Carlo simulations were performed for most of the effects of interest, using the R package 'simr', Version 1.0.5 [@greenSIMRPackagePower2016]. Obtaining power curves for a range of effects in each study allows for a comprehensive assessment of the plausibility of the power estimated for each effect.

Monte Carlo simulations are performed by running the statistical model a large number of times, under slight, random variations of the dependent variable [@greenSIMRPackagePower2016; for a comparable approach, see @lokenMeasurementErrorReplication2017]. The power to detect each effect of interest is calculated by dividing the number of times that the effect is significant by the total number of simulations run. For instance, if an effect is significant on 85 simulations out of 100, the power for that effect is 85% [@kumleEstimatingPowerGeneralized2021]. The sample sizes tested in the semantic priming study ranged from 50 to 800 participants, whereas those tested in the semantic decision and lexical decision studies ranged from 50 to 2,000 participants. These sample sizes were unequally spaced to limit the computational requirements. They comprised the following: 50, 100, 200, 300, 400, 500, 600, 700, 800, 1,200, 1,600 and 2,000 participants.^[For the semantic priming study, the remaining sample sizes up to 2,000 participants have not finished running yet. Upon finishing, they will be reported in this manuscript.] The variance of the results decreases as more simulations are run. In each of our three studies, 200 simulations [as in @brysbaertPowerAnalysisEffect2018] were run for each effect of interest and for each sample size under consideration. Thus, for a power curve examining the power for an effect across 12 sample sizes, 2,400 simulations were run. In each study, the item-level sample size---i.e., the number of words---was not modified. Thus, each of the power curves we present assume the same number of words that existed in each of our studies (these numbers are detailed in each study below). *P* values were calculated using the Satterthwaite approximation for degrees of freedom, which is faster than Kenward-Roger but similarly accurate [@luke2017a].

It is difficult to determine an effect size for each effect examined in a power analysis, as the amount and the scope of relevant research are usually finite and biased [@albersWhenPowerAnalyses2018; @gelmanPowerCalculationsAssessing2014; @kumleEstimatingPowerGeneralized2021]. Power analyses sometimes use the original effect sizes from previous studies [e.g., @paciniExocentricCodingMapping2021; @villalongaPerceptualTimingPrecision2021]. In contrast, some authors have opted to reduce the previous effect sizes to account for factors that can influence the effect size of the planned study. First, publication bias and low-powered studies cause published effect sizes to be inflated [@brysbaertHowManyParticipants2019; @lokenMeasurementErrorReplication2017; @vasishthStatisticalSignificanceFilter2018; @vasishthHowEmbraceVariation2021; @opensciencecollaborationEstimatingReproducibilityPsychological2015]. Second, there might be differences between the studies used in the power analysis and the study to be conducted. Some of these differences could be foreseeable---for instance, if they are due to a limitation in the literature available for the power analysis---, whereas other differences might arise from unexpected circumstances arising during the project or from random variation [@barsalouEstablishingGeneralizableMechanisms2019]. Reducing the effect size in the power analysis leads to an increase of the sample size of the planned study [@brysbaertPowerAnalysisEffect2018; @greenSIMRPackagePower2016; @hoenigAbusePower2001]. The reduced effect size---sometimes dubbed the smallest effect size of interest---is often set with a certain arbitrariness. For instance, @fleurDefinitelySawIt2020 applied a reduction of 1/8 (i.e., 12.5%), whereas @kumleEstimatingPowerGeneralized2021 applied a 15% reduction. In the present study, a reduction of 20% was applied to every effect examined in the power analysis. By comparison with the power analyses reviewed in this paragraph, the present reduction will lead to a relatively-conservative estimate of required sample sizes. Yet, it is intrinsically difficult to determine how conservative a power analysis is, once we consider the insufficient power of most studies in psychology, and the resulting overestimation of effect sizes.

Both the primary analysis and the power analysis were performed in R [@R-base]. Version 4.0.2 was used for the frequentist analysis, Version 4.1.0 was used for the Bayesian analysis, and Version 4.1.2 was used for fast operations such as plotting. All the statistical and the power analyses were run on the High-End Computing facility at Lancaster University.^[Information about this facility is available at [https://answers.lancaster.ac.uk/display/ISS/High+End+Computing+%28HEC%29+help](https://answers.lancaster.ac.uk/display/ISS/High+End+Computing+%28HEC%29+help)]

# Study 1: Semantic priming

The core data set in this study was that of the Semantic Priming Project [@hutchison2013a; also see @yap2017a]. Out of the tasks delivered in the experiment, we used the lexical decision one because it was most relevant to our forthcoming research. In the lexical decision task, participants judged whether strings of letters constituted real words (e.g., 'building') or nonwords (e.g., 'gop'). Crucially, in the experimental manipulation that characterises semantic priming, a prime word was presented before the target word in each trial. Since prime words facilitate the comprehension of target words, the participants' responses to the targets can be analysed as a function of the semantic relationship between primes and targets [@hoedemakerItTakesTime2014].

In some studies, the association between prime and target words has been examined in terms of related versus unrelated pairs [@pecherDoesPizzaPrime1998; @trumppMaskedPrimingConceptual2013], and in terms of first- and second-order relationships [@hutchison2013a]. In contrast to these categorical associations, other studies have measured the association between the prime and the target words using language-based similarity estimates [@guntherLatentSemanticAnalysis2016; @guenther2016a; @hutchisonPredictingSemanticPriming2008; @jones2006a; @lam2015a; @lund1995a; @lund1996a; @mandera2017a; @mcdonald2002a; @pad2007a; @petilli2021a; @wingfieldUnderstandingRoleLinguistic2022]. In one of these studies, @mandera2017a found that the latter computational measures outperformed human-based associations at explaining the priming effect.

Priming associations beyond the linguistic realm have also been examined, with early studies finding perceptual priming effects [@floresdarcaisSemanticActivationRecognition1985; @schreuderEffectsPerceptualConceptual1984]. Yet, the earliest findings were soon reframed by @pecherDoesPizzaPrime1998, who conducted a follow-up with an improved design, and observed the perceptual priming effect only when the word processing task was preceded by a visually-intensive task [@pecherDoesPizzaPrime1998]. This moderating condition, replicated by @yeeColorlessGreenIdeas2012, is consistent with other conceptual-processing studies using a non-priming paradigm [@ostarekTaskdependentCausalRole2017]. However, a considerable number of studies have observed perceptual priming even in the absence of a preparatory perceptual task. A set of these studies used the Conceptual Modality Switch paradigm, in which the primes and the targets are presented in separate, consecutive trials [@pecherVerifyingDifferentmodalityProperties2003; @lynottModalityExclusivityNorms2009; @louwerseTasteWordsLinguistic2011; @collinsModalitySwitchingProperty2011; @hald2011a; @hald2013a; @trumppMaskedPrimingConceptual2013; @bernabeu2017a]. The other set of studies, using the more standard priming intervals, are described below.

@lam2015a conducted a semantic priming experiment containing a lexical decision task. Participants were instructed to respond whether the prime word and the target word in each trial were both real words or pseudowords. The semantic-priming manipulation consisted of the following types of associations between the prime and the target words: (1) semantic association (e.g., bolt → screwdriver), (2) action association (e.g., housekey → screwdriver), (3) visual association (e.g., soldering iron → screwdriver), and (4) no association (e.g., charger → screwdriver). In addition, four conditions were present that consisted of SOAs of 500, 650, 800 and 1,400 ms. In the results, Lam et al. firstly observed priming effects of the semantic-association type with all SOAs. Secondly, the authors observed motor-association priming effects with the SOAs of 500, 650 and 1,400 ms. Lastly, they observed visual-association priming effects only with the SOA of 1,400 ms. Overall, semantic-association priming---corresponding to language-based association---was more consistent than the priming based on visual and action associations. This greater influence of the language system converges with other studies on semantic priming [@lam2015a; @pecherDoesPizzaPrime1998; @petilli2021a] and with studies using other paradigms [@banksLinguisticDistributionalKnowledge2021; @kiela2014a; @louwerse2015a].

Similarly, the results of @lam2015a regarding the time course of language-based and vision-based priming were consistent with a wealth of literature observing that perceptual systems, such as vision, are activated later than the language system [@barsalouLanguageSimulationConceptual2008; @connell2013a; @louwerseTasteWordsLinguistic2011; @santosPropertyGenerationReflects2011]. For instance, studies using electroencephalography have found that perceptual priming effects emerged in the first 300 ms. Following the 300-ms stage, the perceptual priming increased in some studies [@bernabeu2017a; @amselEmpiricallyGroundingGrounded2014], whereas other studies it stabilised [@kieferDifferentialTemporospatialPattern2022], and in a third set of studies, the effect fluctuated [@amselTrackingRealtimeNeural2011]. Taken together, the most prevalent pattern is of a gradual accumulation of information throughout word processing [also see @haukOnlyTimeWill2016], which is consistent with the accummulation of information required for the integration of context in sentences [@haldEEGThetaGamma2006]. This progression invites two hypotheses regarding SOA in the current study: (1) that language-based information will be more prevalent than vision-based information in both the short and the long SOA, and (2) that vision-based information will be more prevalent in the long SOA than in the short one. Consistent with the first hypothesis, @petilli2021a observed that language-based information was more influential in both the short and the long SOA, within the data set of @hutchison2013a. The second hypothesis, in contrast, is challenged by other findings. First, @hutchisonSemanticPrimingDue2003 concluded that the vision-based priming effect was negligible. Second, other studies have observed the effect only when the word processing task was preceded by a visually-intensive task [@pecherDoesPizzaPrime1998; @yeeColorlessGreenIdeas2012]. Third, Petilli et al. observed vision-based priming with the short SOA (150 ms) but not with the long one (1,200 ms).

The findings of @petilli2021a were based on a novel analysis of the data set of @hutchison2013a. The strengths of Petilli et al.'s study centred on the simultaneous analysis of language- and vision-based similarity using predictors that were continuous [see @cohenCostDichotomization1983; @guntherLatentSemanticAnalysis2016; @mandera2017a] and not based on human ratings [cf. @hutchisonPredictingSemanticPriming2008; @hutchison2013a; @lam2015a; @pecherDoesPizzaPrime1998]. The authors used such measures to pursue a comprehensive analysis that was not affected by the problem of circularity between the independent and the dependent variables. The circularity problem obtains even though the participants who contributed to the ratings---or 'norms'---are always different from those who participate in the main experiment.

Petilli et al. operationalised language-based similarity based on text-based co-occurrence, producing a continuous measure in contrast to the categorical factors used earlier. Next, Petilli et al. created a visual-similarity measure by retrieving ImageNet images for each word, and training vector representations on those images using neural networks. Importantly, the authors compared the resulting visual-similarity measure to previous scores based on human ratings [@pecherDoesPizzaPrime1998], and found a comparable pattern. Using these materials, Petilli et al. examined language-based and vision-based priming in two tasks---lexical decision and naming---and with both a short and a long SOA. In lexical decision, the largest effect observed by the authors was that of language-based priming with the short SOA (150 ms). The second largest effect was that of language-based priming with the long SOA (1,200 ms). Next, the weakest effect that was significant was that of vision-based priming with the short SOA. Last, there was no effect of vision-based priming with the long SOA. @petilli2021a explained the absence of vision-based priming with the long SOA in lexical decision by contending that visual activation had likely decayed before participants processed the target words [also see @yeeFunctionFollowsForm2011], owing to the limited semantic processing required for lexical decision [also see @balotaDepthAutomaticSpreading1986; @beckerLongtermSemanticPriming1997; @connell2013a; @dewitMaskedSemanticPriming2015; @joordensLongShortSemantic1997; @ostarekTaskdependentCausalRole2017]. Therefore, the authors suggested that perceptual simulation does *not* outlast language-based processing in lexical decision, in contrast to the longer latency found in other tasks [@barsalouLanguageSimulationConceptual2008; @louwerseTasteWordsLinguistic2011].

In the naming task of @petilli2021a, the largest effect was that of language-based priming with the long SOA. The second largest effect was that of language-based priming with the short SOA. Last, there was no effect of vision-based priming with either SOA. This finding contrasted with @connellSeeHearWhat2014, who found facilitatory effects of visual strength in both lexical decision and naming. Petilli et al. explained the lack of vision-based priming in the naming task by alluding to the lower semantic depth of this task---compared to lexical decision---, and the mixture of visual and auditory processing in the naming task [@connellSeeHearWhat2014].

In the present study, we revisited the interplay between linguistic and perceptual simulation by conceptually replicating @petilli2021a. Specifically, we used the same primary data set [@hutchison2013a], and a language-based similarity measure that was very similar to that used by @petilli2021a [both our measure and theirs originated from @mandera2017a]. In contrast, in the domain of vision, the operationalisation of visual-strength difference in our study---based one variable from [@lynott2020a]---was simpler than that of Petilli et al.'s visual similarity---which involved convolutional neural networks. As a counterpoint, Petilli et al.'s measure was superior in that it was independent from human ratings, thus precluding the problem of circularity between the independent and the dependent variables. At [\underline{the end of the Results section}](#comparing-two-measures-of-vision-based-information), we compare the performance of these two measures.

## Methods

### Effects of interest

- $Z$-scored vocabulary size [`z_vocabulary_size`; calculated from average of `vocaba`, `vocabb` and `vocabc` in @hutchison2013a]. The test used by @hutchison2013a comprised a synonym test, an antonym test, and an analogy test, all three extracted from the Woodcock–Johnson III diagnostic reading battery [@woodcockWoodcockJohnsonIII2001]. We operationalised the vocabulary measure as the mean score across the three tasks per participant.

- $Z$-scored, recoded participant's gender [`z_recoded_participant_gender`; calculated from `gender` in @hutchison2013a]

- $Z$-scored language-based similarity between prime and target words [`z_cosine_similarity`]. This measure was calculated using a semantic space from @mandera2017a, which the authors found to be the second-best predictor ($R$^2^ = .465) of the semantic priming effect in the lexical decision task of @hutchison2013a (we could not use the best semantic space, $R$^2^ = .471, owing to computational limitations). The second-best semantic space [see first row in Table 5 of @mandera2017a] was based on lemmas from a subtitle corpus, processed in a Continuous Bag Of Words model, and the space had 300 dimensions and a window size of 6.

- $Z$-scored vision-based information in words [`z_visual_rating`; calculated from `Visual.mean` in @lynott2020a]

- $Z$-scored, recoded SOA [`z_recoded_interstimulus_interval`; calculated from `isi` in @hutchison2013a]

```{r}

# Calculate numbers to be reported in the paragraph below

# Save number of participants and prime-target pairs
semanticpriming_number_participants = 
  length(unique(semanticpriming$Participant))

semanticpriming_number_primetarget_pairs = 
  length(unique(semanticpriming$primeword_targetword))

# Number of prime-target pairs per participant.
# Save mean as integer and SD rounded while keeping trailing zeros
semanticpriming_mean_primetarget_pairs_per_participant = 
  semanticpriming %>% group_by(Participant) %>% 
  summarise(length(unique(primeword_targetword))) %>% 
  select(2) %>% unlist %>% mean %>% round(0)

semanticpriming_SD_primetarget_pairs_per_participant = 
  semanticpriming %>% group_by(Participant) %>% 
  summarise(length(unique(primeword_targetword))) %>% 
  select(2) %>% unlist %>% sd %>% sprintf('%.2f', .)

# Number of participants per prime-target pair.
# Save mean as integer and SD rounded while keeping trailing zeros
semanticpriming_mean_participants_per_primetarget_pair = 
  semanticpriming %>% group_by(primeword_targetword) %>% 
  summarise(length(unique(Participant))) %>% 
  select(2) %>% unlist %>% mean %>% round(0)

semanticpriming_SD_participants_per_primetarget_pair = 
  semanticpriming %>% group_by(primeword_targetword) %>% 
  summarise(length(unique(Participant))) %>% 
  select(2) %>% unlist %>% sd %>% sprintf('%.2f', .)

```

The final data set contained `r semanticpriming_number_participants` participants, `r semanticpriming_number_primetarget_pairs %>% formattable::comma(digits = 0)` prime-target pairs, and a total of `r length(semanticpriming$z_target.RT) %>% formattable::comma(digits = 0)` RTs. On average, there were `r semanticpriming_mean_primetarget_pairs_per_participant` prime-target pairs per participant ($SD$ = `r semanticpriming_SD_primetarget_pairs_per_participant`), and conversely, `r semanticpriming_mean_participants_per_primetarget_pair` participants per prime-target pair ($SD$ = `r semanticpriming_SD_participants_per_primetarget_pair`).

Figure \@ref(fig:semanticpriming-correlations) shows the zero-order correlations among the predictors and the dependent variable.

```{r semanticpriming-correlations, fig.cap = 'Zero-order correlations in the semantic priming study.', fig.width = 7.5, fig.height = 4.5, out.width = '65%'}

# Using the following variables...
semanticpriming[, c('z_target.RT', 'z_vocabulary_size', 
                    'z_attentional_control',  'z_cosine_similarity', 
                    'z_visual_rating_diff', 'z_word_concreteness_diff', 
                    'z_target_word_frequency', 
                    'z_target_number_syllables')] %>%

  # renamed for the sake of clarity
  rename('RT' = z_target.RT, 
         'Vocabulary size' = z_vocabulary_size,
         'Attentional control' = z_attentional_control,
         'Language-based similarity' = z_cosine_similarity,
         'Visual-strength difference' = z_visual_rating_diff,
         'Word-concreteness difference' = z_word_concreteness_diff,
         'Word frequency' = z_target_word_frequency,
         'Number of syllables' = z_target_number_syllables) %>%

  # make correlation matrix (custom function from the 'R_functions' folder)
  correlation_matrix() + 
  theme(plot.margin = unit(c(0, 0, 0.1, -3.1), 'in'))

```

### Covariates

The following covariates were included in the model to allow a rigorous analysis of the effects of interest.

- Lexical (see [\underline{Appendix A}](#appendix-A-lexical-covariates)): $z$-scored word frequency and orthographic Levenshtein distance [@balota2007a]

- Semantic: $z$-scored word concreteness [@brysbaert2014a], used as a covariate of visual rating.

- Individual differences: $z$-scored attentional control [@hutchison2013a]. This covariate is related to vocabulary size [@ratcliff2010a], and previous studies have pointed out the desirability of including these kinds of covariates in analyses [@james2018a; @pexman2018a]. Attentional control was operationalised as the average score across three attention-demanding tasks: namely, operation span, Stroop, antisaccade.

### Diagnostics for the frequentist model

The model presented convergence warnings. To avoid removing important random slopes, which could increase the Type I error [@brauer2018a; @singmann2019a], we examined the model after refitting it using seven optimization algorithms through the 'allFit' function of the 'lme4' package [@batesPackageLme42021]. The results showed that all optimizers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential (Bates et al., 2021; see [\underline{Appendix B}](#appendix-B-frequentist-analysis-diagnostics)).

The residual errors were not normally distributed, and attempts to mitigate this deviation proved unsuccessful (see [\underline{Appendix B}](#appendix-B-frequentist-analysis-diagnostics)). However, this is not likely to have posed a major problem, as mixed-effects models are fairly robust to deviations from normality [@kniefViolatingNormalityAssumption2021; @schielzethRobustnessLinearMixed2020].

```{r}

# Calculate VIF for every predictor and return only the maximum VIF rounded up
maxVIF_semanticpriming = car::vif(semanticpriming_lmerTest) %>% max %>% ceiling

```

The model did not present multicollinearity problems, all variance inflation factors (VIF) being smaller than `r maxVIF_semanticpriming` [@dormannCollinearityReviewMethods2013; @harrison2018a].

### Diagnostics for the Bayesian model

```{r}

# Calculate number of post-warmup draws (as in 'brms' version 2.17.0).
# Informative prior model used but same numbers in all three models.
semanticpriming_post_warmup_draws = 
  (semanticpriming_summary_informativepriors_exgaussian$iter -
     semanticpriming_summary_informativepriors_exgaussian$warmup) *
  semanticpriming_summary_informativepriors_exgaussian$chains

# As a convergence diagnostic, find maximum R-hat value for the 
# fixed effects across the three models.
semanticpriming_fixedeffects_max_Rhat = 
  max(semanticpriming_summary_informativepriors_exgaussian$fixed$Rhat,
      # semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed$Rhat,
      semanticpriming_summary_diffusepriors_exgaussian$fixed$Rhat) %>% 
  # Round
  sprintf('%.2f', .)

# Next, find find maximum R-hat value for the random effects 
# across the three models. 
semanticpriming_randomeffects_max_Rhat = 
  max(semanticpriming_summary_informativepriors_exgaussian$random[['Participant']]$Rhat,
      # semanticpriming_summary_weaklyinformativepriors_exgaussian$random[['Participant']]$Rhat,
      semanticpriming_summary_diffusepriors_exgaussian$random[['Participant']]$Rhat,
      semanticpriming_summary_informativepriors_exgaussian$random[['primeword_targetword']]$Rhat,
      # semanticpriming_summary_weaklyinformativepriors_exgaussian$random[['primeword_targetword']]$Rhat,
      semanticpriming_summary_diffusepriors_exgaussian$random[['primeword_targetword']]$Rhat) %>% 
  # Round
  sprintf('%.2f', .)

```

Three Bayesian models were run that were respectively characterised by informative, weakly-informative and diffuse priors. In each model, `r semanticpriming_summary_informativepriors_exgaussian$chains` chains were used. In each chain, `r semanticpriming_summary_informativepriors_exgaussian$warmup %>% formattable::comma(digits = 0)` warmup iterations were run, followed by `r (semanticpriming_summary_informativepriors_exgaussian$iter - semanticpriming_summary_informativepriors_exgaussian$warmup) %>% formattable::comma(digits = 0)` post-warmup iterations. Thus, a total of `r semanticpriming_post_warmup_draws %>% formattable::comma(digits = 0)` post-warmup draws were produced over all the chains.

The maximum $\widehat R$ value for the fixed effects across the three models was `r semanticpriming_fixedeffects_max_Rhat`, suggesting that these parameters had converged [@schootBayesianStatisticsModelling2021; @vehtariRanknormalizationFoldingLocalization2021]. In contrast, the maximum $\widehat R$ value for the random effects was `r semanticpriming_randomeffects_max_Rhat`, exceeding the 1.01 threshold [@vehtariRanknormalizationFoldingLocalization2021]. Therefore, models with more iterations will be run, and once completed, they will be reported in this manuscript.

The posterior predictive checks were sound (see [\underline{Appendix C}](#appendix-C-Bayesian-analysis-diagnostics)). Furthermore, in the prior sensitivity analysis, the results were virtually identical with the three priors that were considered (to recall the priors, see Figure \@ref(fig:bayesian-priors) above; to view the results in detail, see [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results)).

## Results {#semanticpriming-results}

Table \@ref(tab:semanticpriming-frequentist-model) presents the results of the mixed-effects model.

```{r semanticpriming-frequentist-model, results = 'asis'}

# Rename effects in plain language and specify the random slopes
# (if any) for each effect, in the footnote. For this purpose, 
# superscripts are added to the names of the appropriate effects.
# 
# In the interactions below, word-level variables are presented 
# first for the sake of consistency (the order does not affect 
# the results in any way). Also in the interactions, double 
# colons are used to inform the 'frequentist_model_table' 
# function that the two terms in the interaction must be split 
# into two lines.

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_attentional_control'] = 'Attentional control'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_vocabulary_size'] = 'Vocabulary size $^{\\text{a}}$'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_recoded_participant_gender'] = 'Gender $^{\\text{a}}$'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_target_word_frequency'] = 'Word frequency'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_target_number_syllables'] = 'Number of syllables'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_word_concreteness_diff'] = 'Word-concreteness difference'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_cosine_similarity'] = 'Language-based similarity $^{\\text{b}}$'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_visual_rating_diff'] = 'Visual-strength difference $^{\\text{b}}$'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_recoded_interstimulus_interval'] = 'Stimulus-onset asynchrony (SOA) $^{\\text{b}}$'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_word_concreteness_diff:z_vocabulary_size'] = 
  'Word-concreteness difference :: Vocabulary size'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_word_concreteness_diff:z_recoded_interstimulus_interval'] = 
  'Word-concreteness difference : SOA'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_word_concreteness_diff:z_recoded_participant_gender'] = 
  'Word-concreteness difference : Gender'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_attentional_control:z_cosine_similarity'] = 
  'Language-based similarity :: Attentional control'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_attentional_control:z_visual_rating_diff'] = 
  'Visual-strength difference :: Attentional control'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_vocabulary_size:z_cosine_similarity'] = 
  'Language-based similarity :: Vocabulary size'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_vocabulary_size:z_visual_rating_diff'] = 
  'Visual-strength difference :: Vocabulary size'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_recoded_participant_gender:z_cosine_similarity'] = 
  'Language-based similarity : Gender'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_recoded_participant_gender:z_visual_rating_diff'] = 
  'Visual-strength difference : Gender'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_recoded_interstimulus_interval:z_cosine_similarity'] = 
  'Language-based similarity : SOA $^{\\text{b}}$'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_recoded_interstimulus_interval:z_visual_rating_diff'] = 
  'Visual-strength difference : SOA $^{\\text{b}}$'

# Next, change the names in the confidence intervals object

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_attentional_control'] = 'Attentional control'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_vocabulary_size'] = 'Vocabulary size $^{\\text{a}}$'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_recoded_participant_gender'] = 'Gender $^{\\text{a}}$'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_target_word_frequency'] = 'Word frequency'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_target_number_syllables'] = 'Number of syllables'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_word_concreteness_diff'] = 'Word-concreteness difference'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_cosine_similarity'] = 'Language-based similarity $^{\\text{b}}$'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_visual_rating_diff'] = 'Visual-strength difference $^{\\text{b}}$'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_recoded_interstimulus_interval'] = 'Stimulus-onset asynchrony (SOA) $^{\\text{b}}$'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_word_concreteness_diff:z_vocabulary_size'] = 
  'Word-concreteness difference :: Vocabulary size'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_word_concreteness_diff:z_recoded_interstimulus_interval'] = 
  'Word-concreteness difference : SOA'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_word_concreteness_diff:z_recoded_participant_gender'] = 
  'Word-concreteness difference : Gender'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_attentional_control:z_cosine_similarity'] = 
  'Language-based similarity :: Attentional control'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_attentional_control:z_visual_rating_diff'] = 
  'Visual-strength difference :: Attentional control'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_vocabulary_size:z_cosine_similarity'] = 
  'Language-based similarity :: Vocabulary size'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_vocabulary_size:z_visual_rating_diff'] = 
  'Visual-strength difference :: Vocabulary size'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_recoded_participant_gender:z_cosine_similarity'] = 
  'Language-based similarity : Gender'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_recoded_participant_gender:z_visual_rating_diff'] = 
  'Visual-strength difference : Gender'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_recoded_interstimulus_interval:z_cosine_similarity'] = 
  'Language-based similarity : SOA $^{\\text{b}}$'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_recoded_interstimulus_interval:z_visual_rating_diff'] = 
  'Visual-strength difference : SOA $^{\\text{b}}$'

# Create table (using custom function from the 'R_functions' folder)
frequentist_model_table(
  KR_summary_semanticpriming_lmerTest, 
  confint_semanticpriming_lmerTest,
  order_effects = c('(Intercept)',
                    'Attentional control',
                    'Vocabulary size $^{\\text{a}}$',
                    'Gender $^{\\text{a}}$',
                    'Word frequency',
                    'Number of syllables',
                    'Word-concreteness difference',
                    'Language-based similarity $^{\\text{b}}$',
                    'Visual-strength difference $^{\\text{b}}$',
                    'Stimulus-onset asynchrony (SOA) $^{\\text{b}}$',
                    'Word-concreteness difference :: Vocabulary size',
                    'Word-concreteness difference : SOA',
                    'Word-concreteness difference : Gender',
                    'Language-based similarity :: Attentional control',
                    'Visual-strength difference :: Attentional control',
                    'Language-based similarity :: Vocabulary size',
                    'Visual-strength difference :: Vocabulary size',
                    'Language-based similarity : Gender',
                    'Visual-strength difference : Gender',
                    'Language-based similarity : SOA $^{\\text{b}}$',
                    'Visual-strength difference : SOA $^{\\text{b}}$'),
  interaction_symbol_x = TRUE,
  caption = 'Frequentist model for the semantic priming study.') %>%
  # kable_styling(latex_options = 'scale_down') %>%

  # Group predictors under headings
  pack_rows('Individual differences', 2, 4) %>% 
  pack_rows('Target-word lexical covariates', 5, 6) %>% 
  pack_rows('Prime-target semantic relationship', 7, 9) %>% 
  pack_rows('Task condition', 10, 10) %>% 
  pack_rows('Interactions', 11, 21) %>%

  # Place table close to designated position and highlight covariates
  kable_styling(latex_options = c('hold_position', 'striped'), 
                stripe_index = c(2, 5:7, 11:15)) %>%

  # Footnote describing abbreviations, random slopes, etc. 
  # LaTeX code used to format the text.
  footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored variables; \\\\textit{SE} = standard error;',
                           'CI = confidence interval. Shaded rows contain covariates. Some interactions are',
                           'split over two lines, with the second line indented. \\\\linebreak', 
                           '$^{\\\\text{a}}$ By-word random slopes were included for this effect.',
                           '$^{\\\\text{b}}$ By-participant random slopes were included for this effect.', 
                           # Begin lines after first one with a dot-sized indent
                           sep = ' \\\\linebreak \\\\phantom{.}'))

# Calculate R^2. This coefficient must be interpreted with caution 
# (Nakagawa et al., 2017; https://doi.org/10.1098/rsif.2017.0213). 
# Also, transform coefficient to rounded percentage.

Nakagawa2017_fixedeffects_R2_semanticpriming_lmerTest = 
  paste0(
    (MuMIn::r.squaredGLMM(semanticpriming_lmerTest)[1, 'R2m'][[1]] * 100) %>% 
      sprintf('%.2f', .), '%'
  )

Nakagawa2017_randomeffects_R2_semanticpriming_lmerTest = 
  paste0(
    (MuMIn::r.squaredGLMM(semanticpriming_lmerTest)[1, 'R2c'][[1]] * 100) %>% 
      sprintf('%.2f', .), '%'
  )

```

The fixed effects of this model explained `r Nakagawa2017_fixedeffects_R2_semanticpriming_lmerTest` of the variance, and the random effects explained `r Nakagawa2017_randomeffects_R2_semanticpriming_lmerTest` [@nakagawaCoefficientDeterminationR22017]. It is to be expected that random effects explain more variance, as they involve a far larger number of coefficients for each effect. For instance, the by-word random slopes for a single individual-level variable (e.g., vocabulary size) involve as many coefficients as the number of words. Similarly, the by-participant random slopes for a single word-level variable (e.g., language-based similarity) involve as many coefficients as the number of participants. In contrast, a fixed effect involves 1 coefficient only.

Figure \@ref(fig:semanticpriming-interactions-with-vocabulary-size)-a shows the interaction between vocabulary size and language-based similarity, whereby higher-vocabulary participants presented a greater benefit from the language-based similarity between prime and target words. That is, the greater the similarity between prime and target words, the greater the advantage for participants with higher vocabularies. This interaction replicates the results of @yap2017a, who analysed the same data set but using a categorical measure of similarity instead. Indeed, this replication is noteworthy as it holds in spite of some methodological differences between the studies. First, @yap2017a operationalised the priming effect as a categorical difference between related and unrelated prime-target pairs. In contrast, the present study applied a continuous measure of relatedness---i.e., cosine similarity---, which is more precise and may thus afford more statistical power [@mandera2017a; @petilli2021a]. Second, the analysis conducted by @yap2017a was correlational, whereas the present analysis used mixed-effects models that included several covariates to measure the effects of interest as rigorously as possible.

Figure \@ref(fig:semanticpriming-interactions-with-vocabulary-size)-b presents the interaction between vocabulary size and vision-based similarity. Albeit a non-significant interaction, it is noteworthy that the effect of vision-based information is larger in lower-vocabulary participants.

(ref:semanticpriming-interactions-with-vocabulary-size) Interactions of vocabulary size with language- and vision-based similarity. Vocabulary size is constrained to deciles, whereas in the statistical analysis it contained more values within the current range. *n* = number of participants contained between decile values.

```{r semanticpriming-interactions-with-vocabulary-size, fig.cap = '(ref:semanticpriming-interactions-with-vocabulary-size)', out.width = '85%'}

# Run plot through source() rather than directly in this R Markdown document 
# to preserve the italicised text.

source('semanticpriming/frequentist_analysis/semanticpriming-interactions-with-vocabulary-size.R', 
       local = TRUE)

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-vocabulary-size.pdf'
  ))

```

Methodologically, the interaction between vocabulary size and language-based similarity underscores the consistency that exists between human ratings and computational approximations to meaning [e.g., @charbonnierPredictingWordConcreteness2019; @charbonnierPredictingConcretenessGerman2020; @guenther2016a; @louwerse2015a; @mandera2017a; @petilli2021a; @solovyevConcretenessAbstractnessConcept2021; @wingfieldUnderstandingRoleLinguistic2022]. In contrast to this consistency, some studies have found human ratings to have more explanatory power than computational measures [@de2016a; @de2019a; @gagneProcessingEnglishCompounds2016; @schmidtke2018a], and other research has suggested that some computational measures are not intrinsically contentful, but arise from a missing-data problem [@snefjella2020a]. In sum, this evidence suggests that computational measures are artificial, and yet valid for the study of cognition.

Figure \@ref(fig:semanticpriming-interactions-with-SOA) shows that the effects of language-based similarity and visual strength were both larger with the short SOA. Yet there is a notable difference: whereas the effect of language-based similarity is present with both SOAs (i.e., 150 ms and 1,200 ms), the effect of visual strength is almost reserved to the the long SOA. This finding replicates @petilli2021a, and stands in contrast to previous findings regarding the slower pace of the visual system in semantic priming [@lam2015a] and in other paradigms [@connell2013a; @louwerseTasteWordsLinguistic2011]. __conclude_______________

```{r semanticpriming-interactions-with-SOA, fig.cap = 'Interactions of SOA with language-based similarity and visual strength. SOA was analysed using $z$-scores, but for clarity, the variable is shown in its simpler form here.', out.width = '80%'}

# Run plot through source() rather than directly in this R Markdown document 
# to preserve the italicised text.

source('semanticpriming/frequentist_analysis/semanticpriming-interactions-with-SOA.R', 
       local = TRUE)

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-SOA.pdf'
  ))

```

#### The importance of outliers

The interaction in Figure \@ref(fig:semanticpriming-interactions-with-vocabulary-size) is patent in all deciles of vocabulary size but most notably in the participants who lie more than 1 standard deviation away from the mean. Outliers in individual differences have played important roles in other areas of cognition as well, such as in the domains of aphantasia and hyperphantasia---traits characterised, respectively, by a diminished and an extraordinary ability to mentally visualise objects [@milton2021a; @zeman2020a]. Furthermore, if we consider the difficulty of detecting effects involving individual differences [@diazNeuralSensitivityPhonological2021; @hedge2018a; @rodriguez-ferreiroSemanticPrimingSchizotypal2020], and the limited representativeness of most samples of participants [@henrich2010a], it may be fruitful to study more varied samples, where possible.

### Visualising the estimates

Figure \@ref(fig:semanticpriming-frequentist-bayesian-plot-informativepriors-exgaussian) presents the posterior distribution of each effect, based on the informative prior model. The models with the other priors produced virtually identical results (see [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results)). The figure also shows the frequentist estimates from Table \@ref(tab:semanticpriming-frequentist-model), to facilitate the comparison.

```{r semanticpriming-frequentist-bayesian-plot-informativepriors-exgaussian, fig.cap = 'Estimates from the frequentist analysis (in red) and from the Bayesian analysis (in blue) for the semantic priming study. The frequentist means (represented by points) are flanked by 95\\% confidence intervals. The Bayesian means (represented by vertical lines) are flanked by 95\\% credible intervals, in light blue (in some cases, the interval is covered up by the bar of the mean).'}

# Run plot through source() rather than directly in this R Markdown document
# to preserve the format.

source('semanticpriming/frequentist_bayesian_plots/semanticpriming_frequentist_bayesian_plots.R', 
       local = TRUE)

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticpriming/frequentist_bayesian_plots/plots/semanticpriming_frequentist_bayesian_plot_informativepriors_exgaussian.pdf'
  ))

```

### Comparing two measures of vision-based information {#comparing-two-measures-of-vision-based-information}

Next, we reflected on the adequacy of visual-strength difference as a measurement instrument, as it had never been used before to operationalise the semantic priming effect. On the one hand, its effect on RT was negative, as we would expect. However, we were concerned about the low correlation between this variable and language-based similarity ($r$ = `r cor(semanticpriming$z_cosine_similarity, semanticpriming$z_visual_rating_diff) %>% sprintf('%.2f', .)`). This concern was especially motivated by the correlation that @petilli2021a had found between their 'vision-based similarity' measure and language-based similarity, which reached $r$ = .50. Based on this information, we set out to run a model with the aim of comparing the performance of our measures of vision-based information.

```{r}

# Calculate numbers to be reported in the paragraph below

# Save number of participants and prime-target pairs
semanticpriming_with_visualsimilarity_number_participants = 
  length(unique(semanticpriming_with_visualsimilarity$Participant))

semanticpriming_with_visualsimilarity_number_primetarget_pairs =
  length(unique(semanticpriming_with_visualsimilarity$primeword_targetword))

# Number of prime-target pairs per participant.
# Save mean as integer and SD rounded while keeping trailing zeros
semanticpriming_with_visualsimilarity_mean_primetarget_pairs_per_participant = 
  semanticpriming_with_visualsimilarity %>% group_by(Participant) %>% 
  summarise(length(unique(primeword_targetword))) %>% 
  select(2) %>% unlist %>% mean %>% round(0)

semanticpriming_with_visualsimilarity_SD_primetarget_pairs_per_participant = 
  semanticpriming_with_visualsimilarity %>% group_by(Participant) %>% 
  summarise(length(unique(primeword_targetword))) %>% 
  select(2) %>% unlist %>% sd %>% sprintf('%.2f', .)

# Number of participants per prime-target pair.
# Save mean as integer and SD rounded while keeping trailing zeros
semanticpriming_with_visualsimilarity_mean_participants_per_primetarget_pair = 
  semanticpriming_with_visualsimilarity %>% group_by(primeword_targetword) %>% 
  summarise(length(unique(Participant))) %>% 
  select(2) %>% unlist %>% mean %>% round(0)

semanticpriming_with_visualsimilarity_SD_participants_per_primetarget_pair = 
  semanticpriming_with_visualsimilarity %>% group_by(primeword_targetword) %>% 
  summarise(length(unique(Participant))) %>% 
  select(2) %>% unlist %>% sd %>% sprintf('%.2f', .)

```

We created a subset of our data set in which we ensured that all the trials contained data from all the relevant variables---i.e., from all the existing variables and from the newly-added visual similarity from Petilli et al. This subsetting resulted in the loss of 83% of trials, owing to the strict selection criteria applied by Petilli et al. in the creation of the visual-similarity measure (e.g., both the target and the prime word had to be associated to at least 100 pictures in ImageNet). As a result, our data set in this analysis contained `r semanticpriming_with_visualsimilarity_number_participants` participants, `r semanticpriming_with_visualsimilarity_number_primetarget_pairs %>% formattable::comma(digits = 0)` prime-target pairs, and a total of `r length(semanticpriming_with_visualsimilarity$z_target.RT) %>% formattable::comma(digits = 0)` RTs. On average, there were `r semanticpriming_with_visualsimilarity_mean_primetarget_pairs_per_participant` prime-target pairs per participant ($SD$ = `r semanticpriming_with_visualsimilarity_SD_primetarget_pairs_per_participant`), and conversely, `r semanticpriming_with_visualsimilarity_mean_participants_per_primetarget_pair` participants per prime-target pair ($SD$ = `r semanticpriming_with_visualsimilarity_SD_participants_per_primetarget_pair`).

Figure \@ref(fig:semanticpriming-with-visualsimilarity-correlations) shows the zero-order correlations among the predictors and the dependent variable.

```{r semanticpriming-with-visualsimilarity-correlations, fig.cap = 'Zero-order correlations in the semantic priming data set that included visual similarity.', fig.width = 8.3, fig.height = 5, out.width = '73%'}

# Using the following variables...
semanticpriming_with_visualsimilarity %>%

  select(z_target.RT, z_vocabulary_size, z_attentional_control, 
         z_cosine_similarity, z_visual_similarity, 
         z_visual_rating_diff, z_word_concreteness_diff, 
         z_target_word_frequency, z_target_number_syllables) %>%

  # Use plain names
  rename('RT' = z_target.RT, 
         'Vocabulary size' = z_vocabulary_size,
         'Attentional control' = z_attentional_control,
         'Language-based similarity' = z_cosine_similarity,
         'Visual-strength difference' = z_visual_rating_diff,
         'Vision-based similarity' = z_visual_similarity,
         'Word-concreteness difference' = z_word_concreteness_diff,
         'Target-word frequency' = z_target_word_frequency,
         'Number of target-word syllables' = z_target_number_syllables) %>%

  # make correlation matrix (custom function from the 'R_functions' folder)
  correlation_matrix() + 
  theme(plot.margin = unit(c(0, 0, 0.1, -3.1), 'in'))

```

### Diagnostics for the frequentist model

The model presented convergence warnings. To avoid removing important random slopes, which could increase the Type I error [@brauer2018a; @singmann2019a], we examined the model after refitting it using seven optimization algorithms through the 'allFit' function of the 'lme4' package [@batesPackageLme42021]. The results showed that all optimizers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential (Bates et al., 2021; see [\underline{Appendix B}](#appendix-B-frequentist-analysis-diagnostics)).

The residual errors were not normally distributed, and attempts to mitigate this deviation proved unsuccessful (see [\underline{Appendix B}](#appendix-B-frequentist-analysis-diagnostics)). However, this is not likely to have posed a major problem, as mixed-effects models are fairly robust to deviations from normality [@kniefViolatingNormalityAssumption2021; @schielzethRobustnessLinearMixed2020].

```{r}

# Calculate VIF for every predictor and return only the maximum VIF rounded up
maxVIF_semanticpriming_with_visualsimilarity = 
  car::vif(semanticpriming_with_visualsimilarity_lmerTest) %>% max %>% ceiling

```

The model did not present multicollinearity problems, all VIFs being smaller than `r maxVIF_semanticpriming_with_visualsimilarity` [@dormannCollinearityReviewMethods2013; @harrison2018a].

Due to time constraints, this analysis did not include a Bayesian model.

#### Results

Table \@ref(tab:semanticpriming-with-visualsimilarity-frequentist-model) presents the results of the mixed-effects model. Due to space, the covariates are shown in Table \@ref(tab:semanticpriming-with-visualsimilarity-frequentist-model-covariates).

```{r semanticpriming-with-visualsimilarity-frequentist-model, results = 'asis'}

# Rename effects in plain language and specify the random slopes
# (if any) for each effect, in the footnote. For this purpose, 
# superscripts are added to the names of the appropriate effects.
# 
# In the interactions below, word-level variables are presented 
# first for the sake of consistency (the order does not affect 
# the results in any way). Also in the interactions, double 
# colons are used to inform the 'frequentist_model_table' 
# function that the two terms in the interaction must be split 
# into two lines.

rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) ==
    'z_attentional_control'] = 'Attentional control'

rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) == 
    'z_vocabulary_size'] = 'Vocabulary size $^{\\text{a}}$'

rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) == 
    'z_recoded_participant_gender'] = 'Gender $^{\\text{a}}$'

rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) ==
    'z_target_word_frequency'] = 'Word frequency'

rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) ==
    'z_target_number_syllables'] = 'Number of syllables'

rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) ==
    'z_word_concreteness_diff'] = 'Word-concreteness difference'

rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) == 
    'z_cosine_similarity'] = 'Language-based similarity $^{\\text{b}}$'

rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) == 
    'z_visual_rating_diff'] = 'Visual-strength difference $^{\\text{b}}$'

rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) == 
    'z_visual_similarity'] = 'Vision-based similarity $^{\\text{b}}$'

rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) == 
    'z_recoded_interstimulus_interval'] = 'Stimulus-onset asynchrony (SOA) $^{\\text{b}}$'

rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) ==
    'z_word_concreteness_diff:z_vocabulary_size'] =
  'Word-concreteness difference :: Vocabulary size'

rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) ==
    'z_word_concreteness_diff:z_recoded_interstimulus_interval'] =
  'Word-concreteness difference : SOA'

rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) ==
    'z_word_concreteness_diff:z_recoded_participant_gender'] =
  'Word-concreteness difference : Gender'

rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) ==
    'z_attentional_control:z_cosine_similarity'] =
  'Language-based similarity :: Attentional control'

rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) ==
    'z_attentional_control:z_visual_rating_diff'] =
  'Visual-strength difference :: Attentional control'

rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) ==
    'z_attentional_control:z_visual_similarity'] =
  'Vision-based similarity :: Attentional control'

rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) == 
    'z_vocabulary_size:z_cosine_similarity'] = 
  'Language-based similarity :: Vocabulary size'

rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) == 
    'z_vocabulary_size:z_visual_rating_diff'] = 
  'Visual-strength difference :: Vocabulary size'

rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) == 
    'z_vocabulary_size:z_visual_similarity'] = 
  'Vision-based similarity :: Vocabulary size'

rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) == 
    'z_recoded_participant_gender:z_cosine_similarity'] = 
  'Language-based similarity : Gender'

rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) == 
    'z_recoded_participant_gender:z_visual_rating_diff'] = 
  'Visual-strength difference : Gender'

rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) == 
    'z_recoded_participant_gender:z_visual_similarity'] = 
  'Vision-based similarity : Gender'

rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) == 
    'z_recoded_interstimulus_interval:z_cosine_similarity'] = 
  'Language-based similarity : SOA $^{\\text{b}}$'

rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) == 
    'z_recoded_interstimulus_interval:z_visual_rating_diff'] = 
  'Visual-strength difference : SOA $^{\\text{b}}$'

rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) == 
    'z_recoded_interstimulus_interval:z_visual_similarity'] = 
  'Vision-based similarity : SOA $^{\\text{b}}$'

# Next, change the names in the confidence intervals object

rownames(confint_semanticpriming_with_visualsimilarity_lmerTest)[
  rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) ==
    'z_attentional_control'] = 'Attentional control'

rownames(confint_semanticpriming_with_visualsimilarity_lmerTest)[
  rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) == 
    'z_vocabulary_size'] = 'Vocabulary size $^{\\text{a}}$'

rownames(confint_semanticpriming_with_visualsimilarity_lmerTest)[
  rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) == 
    'z_recoded_participant_gender'] = 'Gender $^{\\text{a}}$'

rownames(confint_semanticpriming_with_visualsimilarity_lmerTest)[
  rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) ==
    'z_target_word_frequency'] = 'Word frequency'

rownames(confint_semanticpriming_with_visualsimilarity_lmerTest)[
  rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) ==
    'z_target_number_syllables'] = 'Number of syllables'

rownames(confint_semanticpriming_with_visualsimilarity_lmerTest)[
  rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) ==
    'z_word_concreteness_diff'] = 'Word-concreteness difference'

rownames(confint_semanticpriming_with_visualsimilarity_lmerTest)[
  rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) == 
    'z_cosine_similarity'] = 'Language-based similarity $^{\\text{b}}$'

rownames(confint_semanticpriming_with_visualsimilarity_lmerTest)[
  rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) == 
    'z_visual_rating_diff'] = 'Visual-strength difference $^{\\text{b}}$'

rownames(confint_semanticpriming_with_visualsimilarity_lmerTest)[
  rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) == 
    'z_visual_similarity'] = 'Vision-based similarity $^{\\text{b}}$'

rownames(confint_semanticpriming_with_visualsimilarity_lmerTest)[
  rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) == 
    'z_recoded_interstimulus_interval'] = 'Stimulus-onset asynchrony (SOA) $^{\\text{b}}$'

rownames(confint_semanticpriming_with_visualsimilarity_lmerTest)[
  rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) ==
    'z_word_concreteness_diff:z_vocabulary_size'] =
  'Word-concreteness difference :: Vocabulary size'

rownames(confint_semanticpriming_with_visualsimilarity_lmerTest)[
  rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) ==
    'z_word_concreteness_diff:z_recoded_interstimulus_interval'] =
  'Word-concreteness difference : SOA'

rownames(confint_semanticpriming_with_visualsimilarity_lmerTest)[
  rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) ==
    'z_word_concreteness_diff:z_recoded_participant_gender'] =
  'Word-concreteness difference : Gender'

rownames(confint_semanticpriming_with_visualsimilarity_lmerTest)[
  rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) ==
    'z_attentional_control:z_cosine_similarity'] =
  'Language-based similarity :: Attentional control'

rownames(confint_semanticpriming_with_visualsimilarity_lmerTest)[
  rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) ==
    'z_attentional_control:z_visual_rating_diff'] =
  'Visual-strength difference :: Attentional control'

rownames(confint_semanticpriming_with_visualsimilarity_lmerTest)[
  rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) ==
    'z_attentional_control:z_visual_similarity'] =
  'Vision-based similarity :: Attentional control'

rownames(confint_semanticpriming_with_visualsimilarity_lmerTest)[
  rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) == 
    'z_vocabulary_size:z_cosine_similarity'] = 
  'Language-based similarity :: Vocabulary size'

rownames(confint_semanticpriming_with_visualsimilarity_lmerTest)[
  rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) == 
    'z_vocabulary_size:z_visual_rating_diff'] = 
  'Visual-strength difference :: Vocabulary size'

rownames(confint_semanticpriming_with_visualsimilarity_lmerTest)[
  rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) == 
    'z_vocabulary_size:z_visual_similarity'] = 
  'Vision-based similarity :: Vocabulary size'

rownames(confint_semanticpriming_with_visualsimilarity_lmerTest)[
  rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) == 
    'z_recoded_participant_gender:z_cosine_similarity'] = 
  'Language-based similarity : Gender'

rownames(confint_semanticpriming_with_visualsimilarity_lmerTest)[
  rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) == 
    'z_recoded_participant_gender:z_visual_rating_diff'] = 
  'Visual-strength difference : Gender'

rownames(confint_semanticpriming_with_visualsimilarity_lmerTest)[
  rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) == 
    'z_recoded_participant_gender:z_visual_similarity'] = 
  'Vision-based similarity : Gender'

rownames(confint_semanticpriming_with_visualsimilarity_lmerTest)[
  rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) == 
    'z_recoded_interstimulus_interval:z_cosine_similarity'] = 
  'Language-based similarity : SOA $^{\\text{b}}$'

rownames(confint_semanticpriming_with_visualsimilarity_lmerTest)[
  rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) == 
    'z_recoded_interstimulus_interval:z_visual_rating_diff'] = 
  'Visual-strength difference : SOA $^{\\text{b}}$'

rownames(confint_semanticpriming_with_visualsimilarity_lmerTest)[
  rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) == 
    'z_recoded_interstimulus_interval:z_visual_similarity'] = 
  'Vision-based similarity : SOA $^{\\text{b}}$'

# Create table (using custom function from the 'R_functions' folder)

# Covariates are commented out as they do not fit in the table. 
# They are instead shown in the subsequent table.

frequentist_model_table(
  KR_summary_semanticpriming_with_visualsimilarity_lmerTest, 
  confint_semanticpriming_with_visualsimilarity_lmerTest,
  select_effects = c('(Intercept)',
                     # 'Attentional control',
                     'Vocabulary size $^{\\text{a}}$',
                     'Gender $^{\\text{a}}$',
                     # 'Word frequency',
                     # 'Number of syllables',
                     # 'Word-concreteness difference',
                     'Language-based similarity $^{\\text{b}}$',
                     'Visual-strength difference $^{\\text{b}}$',
                     'Vision-based similarity $^{\\text{b}}$',
                     'Stimulus-onset asynchrony (SOA) $^{\\text{b}}$',
                     # 'Word-concreteness difference :: Vocabulary size',
                     # 'Word-concreteness difference : SOA',
                     # 'Word-concreteness difference : Gender',
                     # 'Language-based similarity :: Attentional control',
                     # 'Visual-strength difference :: Attentional control',
                     # 'Vision-based similarity :: Attentional control',
                     'Language-based similarity :: Vocabulary size',
                     'Visual-strength difference :: Vocabulary size',
                     'Vision-based similarity :: Vocabulary size',
                     'Language-based similarity : Gender',
                     'Visual-strength difference : Gender',
                     'Vision-based similarity : Gender',
                     'Language-based similarity : SOA $^{\\text{b}}$',
                     'Visual-strength difference : SOA $^{\\text{b}}$',
                     'Vision-based similarity : SOA $^{\\text{b}}$'),
  interaction_symbol_x = TRUE,
  caption = 'Effects of interest in the semantic priming model that included visual similarity.') %>%
  # kable_styling(latex_options = 'scale_down') %>%

  # Group predictors under headings
  pack_rows('Individual differences', 2, 3) %>% 
  pack_rows('Prime-target semantic relationship', 4, 6) %>% 
  pack_rows('Task condition', 7, 7) %>% 
  pack_rows('Interactions', 8, 16) %>%

  # Place table close to designated position
  kable_styling(latex_options = c('hold_position')) %>%

  # Footnote describing abbreviations, random slopes, etc. 
  # LaTeX code used to format the text.
  footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored variables; \\\\textit{SE} = standard error;',
                           'CI = confidence interval. Covariates shown in next table due to space. Some ',
                           'interactions are split over two lines, with the second line indented. \\\\linebreak', 
                           '$^{\\\\text{a}}$ By-word random slopes were included for this effect.',
                           '$^{\\\\text{b}}$ By-participant random slopes were included for this effect.', 
                           # Begin lines after first one with a dot-sized indent
                           sep = ' \\\\linebreak \\\\phantom{.}'))

```

```{r semanticpriming-with-visualsimilarity-frequentist-model-covariates, results = 'asis'}

# Create table (using custom function from the 'R_functions' folder)

# Only the covariates are shown, and the effects of interest are
# commented out as they were shown in the table above.

frequentist_model_table(
  KR_summary_semanticpriming_with_visualsimilarity_lmerTest, 
  confint_semanticpriming_with_visualsimilarity_lmerTest,
  select_effects = c('Attentional control',
                     # 'Vocabulary size $^{\\text{a}}$',
                     # 'Gender $^{\\text{a}}$',
                     'Word frequency',
                     'Number of syllables',
                     'Word-concreteness difference',
                     # 'Language-based similarity $^{\\text{b}}$',
                     # 'Visual-strength difference $^{\\text{b}}$',
                     # 'Vision-based similarity $^{\\text{b}}$',
                     # 'Stimulus-onset asynchrony (SOA) $^{\\text{b}}$',
                     'Word-concreteness difference :: Vocabulary size',
                     'Word-concreteness difference : SOA',
                     'Word-concreteness difference : Gender',
                     'Language-based similarity :: Attentional control',
                     'Visual-strength difference :: Attentional control',
                     'Vision-based similarity :: Attentional control'  # comma deleted
                     # 'Language-based similarity :: Vocabulary size',
                     # 'Visual-strength difference :: Vocabulary size',
                     # 'Vision-based similarity :: Vocabulary size',
                     # 'Language-based similarity : Gender',
                     # 'Visual-strength difference : Gender',
                     # 'Language-based similarity : SOA $^{\\text{b}}$',
                     # 'Visual-strength difference : SOA $^{\\text{b}}$',
                     # 'Vision-based similarity : SOA $^{\\text{b}}$'
  ),
  interaction_symbol_x = TRUE,
  caption = 'Covariates in the semantic priming model that included visual similarity.') %>%
  # kable_styling(latex_options = 'scale_down') %>%

  # Group predictors under headings
  pack_rows('Individual-differences covariate', 1, 1) %>% 
  pack_rows('Target-word lexical covariates', 2, 3) %>% 
  pack_rows('Prime-target semantic covariate', 4, 4) %>% 
  pack_rows('Covariate interactions', 5, 10) %>%

  # Place table close to designated position
  kable_styling(latex_options = c('hold_position')) %>%

  # Footnote describing abbreviations, random slopes, etc. 
  # LaTeX code used to format the text.
  footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored variables; \\\\textit{SE} = standard error;',
                           'CI = confidence interval. Some interactions are split over two lines, with the',
                           'second line indented. \\\\linebreak', 
                           # '$^{\\\\text{a}}$ By-word random slopes were included for this effect.',
                           # '$^{\\\\text{b}}$ By-participant random slopes were included for this effect.', 
                           # Begin lines after first one with a dot-sized indent
                           sep = ' \\\\linebreak \\\\phantom{.}'))

# Calculate R^2. This coefficient must be interpreted with caution 
# (Nakagawa et al., 2017; https://doi.org/10.1098/rsif.2017.0213). 
# Also, transform coefficient to rounded percentage.

Nakagawa2017_fixedeffects_R2_semanticpriming_with_visualsimilarity_lmerTest = 
  paste0(
    (MuMIn::r.squaredGLMM(semanticpriming_with_visualsimilarity_lmerTest)[1, 'R2m'][[1]] * 100) %>% 
      sprintf('%.2f', .), '%'
  )

Nakagawa2017_randomeffects_R2_semanticpriming_with_visualsimilarity_lmerTest = 
  paste0(
    (MuMIn::r.squaredGLMM(semanticpriming_with_visualsimilarity_lmerTest)[1, 'R2c'][[1]] * 100) %>% 
      sprintf('%.2f', .), '%'
  )

```

The fixed effects of this model explained `r Nakagawa2017_fixedeffects_R2_semanticpriming_with_visualsimilarity_lmerTest` of the variance, and the random effects explained `r Nakagawa2017_randomeffects_R2_semanticpriming_with_visualsimilarity_lmerTest` (Nakagawa et al., 2017; for background on why random effects explain more variance, see [Results in Study 1](#semanticpriming-results)).

Figure \@ref(fig:semanticpriming-with-visualsimilarity-confidence-intervals-plot) presents the means and 95% confidence intervals for the effects of interest.

```{r semanticpriming-with-visualsimilarity-confidence-intervals-plot, fig.cap = 'Means and 95\\% confidence intervals for the effects of interest in the semantic priming model that included visual similarity.', out.width = '89%'}

# Run plot through source() rather than directly in this R Markdown document
# to preserve the format.

source('semanticpriming/analysis_with_visualsimilarity/semanticpriming_with_visualsimilarity_confidence_intervals_plot.R', 
       local = TRUE)

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticpriming/analysis_with_visualsimilarity/plots/semanticpriming_with_visualsimilarity_confidence_intervals_plot.pdf'
  ))

```

The results revealed that visual-strength difference had a significantly larger effect. This difference was not due to an excessive collinearity between these measures ($r$ = `r cor(semanticpriming_with_visualsimilarity$z_visual_rating_diff, semanticpriming_with_visualsimilarity$z_visual_similarity) %>% sprintf('%.2f', .)`). Also importantly, both measures appeared to be valid based on their correlations with language-based similarity and with word concreteness.

### Statistical power analysis

Power curves were performed for most effects of interest in the main model (no power analysis was performed for the model that included visual similarity). Figures \@ref(fig:semanticpriming-powercurve-plots-1-2-3) and \@ref(fig:semanticpriming-powercurve-plots-4-5-6-7-8-9) show the estimated power for the main effects and the interactions, respectively.

```{r semanticpriming-powercurve-plots-1-2-3, fig.cap = 'Power curves for some main effects in the semantic priming study.'}

# Run plot through source() rather than directly in this R Markdown document 
# to preserve the italicised text.
source('semanticpriming/power_analysis/semanticpriming_all_powercurves.R', 
       local = TRUE)

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticpriming/power_analysis/plots/semanticpriming_powercurve_plots_1_2_3.pdf'
  ))

```

```{r semanticpriming-powercurve-plots-4-5-6-7-8-9, fig.cap = 'Power curves for some interactions in the semantic priming study.', out.width = '92%'}

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticpriming/power_analysis/plots/semanticpriming_powercurve_plots_4_5_6_7_8_9.pdf'
  ))

```

_______ interpret ____________

## Discussion

___________________

\clearpage

# Study 2: Semantic decision

The semantic decision task probes into the role of concreteness in conceptual processing. Specifically, this task requires participants to classify words as abstract or concrete. Researchers then analyse whether the responses can be explained by the sensory experientiality of the referents---that is, the degree to which they can be experienced through our senses---and by other variables, such as word frequency. The core data set in this study was that of the Calgary Semantic Decision Project [@pexman2017a; @pexman2018a]. The experimental task is semantic decision, in which participants judge whether words are relatively concrete (e.g., 'building') or abstract (e.g., 'thought').

Research has found that the processing of relatively concrete words relies considerably on sensorimotor information [@hultenNeuralRepresentationAbstract2021; @kousta2011a; @vigliocco2014a]. In contrast, the processing of relatively abstract words seems to draw more heavily on information from language [@barca2020a; @dunabeitiaQualitativeDifferencesRepresentation2009; @snefjella2020a], emotion [@kousta2011a; @ponari2018a; @ponari2018b; @ponariRoleEmotionalValence2020; @vigliocco2014a] and sociality [@borghiWordsSocialTools2019; @diveicaQuantifyingSocialSemantics2022].

## Word co-occurrence

@wingfieldUnderstandingRoleLinguistic2022 reanalysed the data from @pexman2017a using language-based variables that are more related to the language system than to the visual system. The authors found that the variables that best explained RTs were word co-occurrence measures. Specifically, the measures corresponded to the distance from each stimulus word to two labels that were central to the task, namely, the words ‘abstract’ and ‘concrete’. Wingfield and Connell studied these distance measures in various forms, and found that cosine and correlation distance yielded the best results. We used the correlation distance following the advice of [@kiela2014a]. Furthermore, we sought to avoid the collinearity between these variables ($r$ = .99) and to facilitate the analysis of interactions with other variables. For this purpose, we created a difference score by subtracting distance to 'abstract' from the distance to 'concrete'. The resulting variable was practically equivalent to the distance to 'abstract', as attested by its large correlation with word concreteness ($r$ = `r cor(semanticdecision$word_cooccurrence, semanticdecision$information_uptake) %>% sprintf('%.2f', .)`). Last, it should be noted that this difference score may not be affected by the reduced sensitivity of other ones [see @rodriguez-ferreiroSemanticPrimingSchizotypal2020], as this difference score did not entail an aggregation of data points over any third variables.

## Methods

### Effects of interest

- $Z$-scored vocabulary size [`z_vocabulary_size`; calculated from `NAART` in @pexman2017a]. In the test used by @pexman2018a, participants were presented with 35 rare words, whose pronunciations are not regular (e.g., *gaoled*, *ennui*), and they were asked to read the words aloud. When they pronounced a word correctly, it was inferred that they knew the word. This test was based on NAART35, a short version of the North American Adult Reading Test [@uttlNorthAmericanAdult2002].

- $Z$-scored, recoded participant's gender [`z_recoded_participant_gender`; calculated from `Gender` in @pexman2018a]

- $Z$-scored distance to word 'abstract': a distributional semantic distance measure obtained from @wingfieldUnderstandingRoleLinguistic2022 that reflects the correlation distance between each stimulus word and the word 'abstract'.^[Specifically, this measure is a difference score that merges both the distance to the word 'abstract' and the distance to the word 'concrete'. We drew on both variables because @wingfieldUnderstandingRoleLinguistic2022 found them to be similarly important. Yet, we had to create a difference score because these variables were highly correlated ($r$ = .99), we created a difference score by subtracting the distance to 'abstract' from the distance to 'concrete'. The resulting difference score was practically equivalent to the distance to the word 'abstract', as attested by its correlation with word concreteness (see Figure \@ref(fig:semanticdecision-correlations)). Our difference score in practice  The variable `Conditional_probability_BNC_r5_correlation_abstract_distance` was subtracted from `Conditional_probability_BNC_r5_correlation_concrete_distance`.]

- $Z$-scored vision-based information in words [`z_visual_rating`; calculated from `Visual.mean` in @lynott2020a]

```{r}

# Calculate numbers to be reported in the paragraph below

# Save number of participants and words
semanticdecision_number_participants = 
  length(unique(semanticdecision$Participant))

semanticdecision_number_words = length(unique(semanticdecision$Word))

# Number of words per participant.
# Save mean as integer and SD rounded while keeping trailing zeros
semanticdecision_mean_words_per_participant = 
  semanticdecision %>% group_by(Participant) %>% 
  summarise(length(unique(Word))) %>% 
  select(2) %>% unlist %>% mean %>% round(0)

semanticdecision_SD_words_per_participant = 
  semanticdecision %>% group_by(Participant) %>% 
  summarise(length(unique(Word))) %>% 
  select(2) %>% unlist %>% sd %>% sprintf('%.2f', .)

# Number of participants per word.
# Save mean as integer and SD rounded while keeping trailing zeros
semanticdecision_mean_participants_per_word = 
  semanticdecision %>% group_by(Word) %>% 
  summarise(length(unique(Participant))) %>% 
  select(2) %>% unlist %>% mean %>% round(0)

semanticdecision_SD_participants_per_word = 
  semanticdecision %>% group_by(Word) %>% 
  summarise(length(unique(Participant))) %>% 
  select(2) %>% unlist %>% sd %>% sprintf('%.2f', .)

```

The final data set contained `r semanticdecision_number_participants` participants, `r semanticdecision_number_words %>% formattable::comma(digits = 0)` words, and a total of `r length(semanticdecision$z_RTclean) %>% formattable::comma(digits = 0)` RTs. On average, there were `r semanticdecision_mean_words_per_participant` words per participant ($SD$ = `r semanticdecision_SD_words_per_participant`), and conversely, `r semanticdecision_mean_participants_per_word` participants per word ($SD$ = `r semanticdecision_SD_participants_per_word`).

Figure \@ref(fig:semanticdecision-correlations) shows the zero-order correlations among the predictors among the predictors and the dependent variable.

```{r semanticdecision-correlations, fig.cap = 'Zero-order correlations in the semantic decision study.', fig.width = 7, fig.height = 4.5, out.width = '57%'}

# Using the following variables...
semanticdecision[, c('z_RTclean', 'z_vocabulary_size', 
                     'z_information_uptake', 'z_word_cooccurrence', 
                     'z_visual_rating', 'z_word_concreteness', 
                     'z_word_frequency', 
                     'z_orthographic_Levenshtein_distance')] %>%

  # renamed for the sake of clarity
  rename('RT' = z_RTclean, 
         'Vocabulary size' = z_vocabulary_size,
         'Information uptake' = z_information_uptake,
         "Distance to word 'abstract'" = z_word_cooccurrence,
         'Visual strength' = z_visual_rating,
         'Word concreteness' = z_word_concreteness,
         'Word frequency' = z_word_frequency,
         'Orthographic Levenshtein distance' = z_orthographic_Levenshtein_distance) %>%

  # make correlation matrix (custom function from the 'R_functions' folder)
  correlation_matrix() + 
  theme(plot.margin = unit(c(0, 0, 0.1, -3.1), 'in'))

```

### Covariates

The following covariates were included in the model to allow a rigorous analysis of the effects of interest.

- Lexical (see [\underline{Appendix A}](#appendix-A-lexical-covariates)): $z$-scored word frequency and orthographic Levenshtein distance [@balota2007a]

- Semantic: $z$-scored word concreteness [@brysbaert2014a]. This variable is used as a covariate of visual strength, and it is especially fundamental in the semantic decision task, in which participants judge whether words are concrete or abstract [for a more general consideration of concreteness, see @bottiniConcretenessAdvantageLexical2021]. Indeed, owing to the instructions of the task, word concreteness is likely to be more relevant to the participants' task than our effects of interest.

- Individual differences: $z$-scored information uptake [@pexman2018a]. This covariate is related to vocabulary size [@ratcliff2010a; also see @james2018a; @pexman2018a].

### Diagnostics for the frequentist model

The model presented convergence warnings. To avoid removing important random slopes, which could increase the Type I error [@brauer2018a; @singmann2019a], we examined the model after refitting it using seven optimization algorithms through the 'allFit' function of the 'lme4' package [@batesPackageLme42021]. The results showed that all optimizers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential (Bates et al., 2021; see [\underline{Appendix B}](#appendix-B-frequentist-analysis-diagnostics)).

The residual errors were not normally distributed, and attempts to mitigate this deviation proved unsuccessful (see [\underline{Appendix B}](#appendix-B-frequentist-analysis-diagnostics)). However, this is not likely to have posed a major problem, as mixed-effects models are fairly robust to deviations from normality [@kniefViolatingNormalityAssumption2021; @schielzethRobustnessLinearMixed2020].

```{r}

# Calculate VIF for every predictor and return only the maximum VIF rounded up
maxVIF_semanticdecision = car::vif(semanticdecision_lmerTest) %>% max %>% ceiling

```

The model did not present multicollinearity problems, all VIFs being smaller than `r maxVIF_semanticdecision` [@dormannCollinearityReviewMethods2013; @harrison2018a].

### Diagnostics for the Bayesian model

```{r}

# Calculate number of post-warmup draws (as in 'brms' version 2.17.0).
# Informative prior model used but same numbers in all three models.
semanticdecision_post_warmup_draws = 
  (semanticdecision_summary_informativepriors_exgaussian$iter -
     semanticdecision_summary_informativepriors_exgaussian$warmup) *
  semanticdecision_summary_informativepriors_exgaussian$chains

# As a convergence diagnostic, find maximum R-hat value for the 
# fixed effects across the three models.
semanticdecision_fixedeffects_max_Rhat = 
  max(semanticdecision_summary_informativepriors_exgaussian$fixed$Rhat,
      semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed$Rhat,
      semanticdecision_summary_diffusepriors_exgaussian$fixed$Rhat) %>% 
  # Round
  sprintf('%.2f', .)

# Next, find find maximum R-hat value for the random effects 
# across the three models. 
semanticdecision_randomeffects_max_Rhat = 
  max(semanticdecision_summary_informativepriors_exgaussian$random[['Participant']]$Rhat,
      semanticdecision_summary_weaklyinformativepriors_exgaussian$random[['Participant']]$Rhat,
      semanticdecision_summary_diffusepriors_exgaussian$random[['Participant']]$Rhat,
      semanticdecision_summary_informativepriors_exgaussian$random[['Word']]$Rhat,
      semanticdecision_summary_weaklyinformativepriors_exgaussian$random[['Word']]$Rhat,
      semanticdecision_summary_diffusepriors_exgaussian$random[['Word']]$Rhat) %>% 
  # Round
  sprintf('%.2f', .)

```

Three Bayesian models were run that were respectively characterised by informative, weakly-informative and diffuse priors. In each model, `r semanticdecision_summary_informativepriors_exgaussian$chains` chains were used. In each chain, `r semanticdecision_summary_informativepriors_exgaussian$warmup %>% formattable::comma(digits = 0)` warmup iterations were run, followed by `r (semanticdecision_summary_informativepriors_exgaussian$iter - semanticdecision_summary_informativepriors_exgaussian$warmup) %>% formattable::comma(digits = 0)` post-warmup iterations. Thus, a total of `r semanticdecision_post_warmup_draws %>% formattable::comma(digits = 0)` post-warmup draws were produced over all the chains.

The maximum $\widehat R$ value for the fixed effects across the three models was `r semanticdecision_fixedeffects_max_Rhat`, far exceeding the 1.01 threshold [@vehtariRanknormalizationFoldingLocalization2021; also see @schootBayesianStatisticsModelling2021]. Similarly, the maximum $\widehat R$ value for the random effects was `r semanticdecision_randomeffects_max_Rhat`. Furthermore, the posterior predictive checks revealed major divergences between the observed data and the predicted outcome (see [\underline{Appendix C}](#appendix-C-Bayesian-analysis-diagnostics)). Since the results were not valid, they are not shown in the main text but instead in [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results).

## Results

Table \@ref(tab:semanticdecision-frequentist-model) presents the results of the mixed-effects model.

```{r semanticdecision-frequentist-model, results = 'asis'}

# Rename effects in plain language and specify the random slopes
# (if any) for each effect, in the footnote. For this purpose, 
# superscripts are added to the names of the appropriate effects.
# 
# In the interactions below, word-level variables are presented 
# first for the sake of consistency (the order does not affect 
# the results in any way). Also in the interactions, double 
# colons are used to inform the 'frequentist_model_table' 
# function that the two terms in the interaction must be split 
# into two lines.

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_information_uptake'] = 'Information uptake'

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_vocabulary_size'] = 'Vocabulary size $^{\\text{a}}$'

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_recoded_participant_gender'] = 'Gender $^{\\text{a}}$'

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_word_frequency'] = 'Word frequency'

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_orthographic_Levenshtein_distance'] = 'Orthographic Levenshtein distance'

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_word_concreteness'] = 'Word concreteness'

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_word_cooccurrence'] = "Distance to word 'abstract' $^{\\text{b}}$"

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_visual_rating'] = 'Visual strength $^{\\text{b}}$'

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_word_concreteness:z_vocabulary_size'] = 
  'Word concreteness : Vocabulary size'

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_word_concreteness:z_recoded_participant_gender'] = 
  'Word concreteness : Gender'

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_information_uptake:z_word_cooccurrence'] = 
  "Information uptake :: Distance to word 'abstract'"

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_information_uptake:z_visual_rating'] = 
  'Visual strength : Information uptake'

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_vocabulary_size:z_word_cooccurrence'] = 
  "Distance to word 'abstract' :: Vocabulary size"

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_vocabulary_size:z_visual_rating'] = 
  'Visual strength : Vocabulary size'

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_recoded_participant_gender:z_word_cooccurrence'] = 
  "Distance to word 'abstract' : Gender"

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_recoded_participant_gender:z_visual_rating'] = 
  'Visual strength : Gender'

# Next, change the names in the confidence intervals object

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_information_uptake'] = 'Information uptake'

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_vocabulary_size'] = 'Vocabulary size $^{\\text{a}}$'

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_recoded_participant_gender'] = 'Gender $^{\\text{a}}$'

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_word_frequency'] = 'Word frequency'

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_orthographic_Levenshtein_distance'] = 'Orthographic Levenshtein distance'

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_word_concreteness'] = 'Word concreteness'

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_word_cooccurrence'] = "Distance to word 'abstract' $^{\\text{b}}$"

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_visual_rating'] = 'Visual strength $^{\\text{b}}$'

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_word_concreteness:z_vocabulary_size'] = 
  'Word concreteness : Vocabulary size'

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_word_concreteness:z_recoded_participant_gender'] = 
  'Word concreteness : Gender'

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_information_uptake:z_word_cooccurrence'] = 
  "Information uptake :: Distance to word 'abstract'"

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_information_uptake:z_visual_rating'] = 
  'Visual strength : Information uptake'

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_vocabulary_size:z_word_cooccurrence'] = 
  "Distance to word 'abstract' :: Vocabulary size"

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_vocabulary_size:z_visual_rating'] = 
  'Visual strength : Vocabulary size'

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_recoded_participant_gender:z_word_cooccurrence'] = 
  "Distance to word 'abstract' : Gender"

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_recoded_participant_gender:z_visual_rating'] = 
  'Visual strength : Gender'

# Create table (using custom function from the 'R_functions' folder)
frequentist_model_table(
  KR_summary_semanticdecision_lmerTest, 
  confint_semanticdecision_lmerTest,
  order_effects = c('(Intercept)',
                    'Information uptake',
                    'Vocabulary size $^{\\text{a}}$',
                    'Gender $^{\\text{a}}$',
                    'Word frequency',
                    'Orthographic Levenshtein distance',
                    'Word concreteness',
                    "Distance to word 'abstract' $^{\\text{b}}$",
                    'Visual strength $^{\\text{b}}$',
                    'Vocabulary size : Word concreteness',
                    'Word concreteness : Gender',
                    "Distance to word 'abstract' :: Information uptake",
                    'Visual strength : Information uptake',
                    "Distance to word 'abstract' :: Vocabulary size",
                    'Visual strength : Vocabulary size',
                    "Distance to word 'abstract' : Gender",
                    'Visual strength : Gender'),
  interaction_symbol_x = TRUE,
  caption = 'Frequentist model for the semantic decision study.') %>%
  # kable_styling(latex_options = 'scale_down') %>%

  # Group predictors under headings
  pack_rows('Individual differences', 2, 4) %>% 
  pack_rows('Lexical covariates', 5, 6) %>% 
  pack_rows('Semantic variables', 7, 9) %>% 
  pack_rows('Interactions', 10, 17) %>%

  # Place table close to designated position and highlight covariates
  kable_styling(latex_options = c('hold_position', 'striped'), 
                stripe_index = c(2, 5:7, 10:11)) %>%

  # Footnote describing abbreviations, random slopes, etc. 
  # LaTeX code used to format the text.
  footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored variables; \\\\textit{SE} = standard error;',
                           'CI = confidence interval. Shaded rows contain covariates. Some interactions are',
                           'split over two lines, with the second line indented. \\\\linebreak', 
                           '$^{\\\\text{a}}$ By-word random slopes were included for this effect.',
                           '$^{\\\\text{b}}$ By-participant random slopes were included for this effect.', 
                           # Begin lines after first one with a dot-sized indent
                           sep = ' \\\\linebreak \\\\phantom{.}'))

# Calculate R^2. This coefficient must be interpreted with caution 
# (Nakagawa et al., 2017; https://doi.org/10.1098/rsif.2017.0213). 
# Also, transform coefficient to rounded percentage.

Nakagawa2017_fixedeffects_R2_semanticdecision_lmerTest = 
  paste0(
    (MuMIn::r.squaredGLMM(semanticdecision_lmerTest)[1, 'R2m'][[1]] * 100) %>% 
      sprintf('%.2f', .), '%'
  )

Nakagawa2017_randomeffects_R2_semanticdecision_lmerTest = 
  paste0(
    (MuMIn::r.squaredGLMM(semanticdecision_lmerTest)[1, 'R2c'][[1]] * 100) %>% 
      sprintf('%.2f', .), '%'
  )

```

The fixed effects of this model explained `r Nakagawa2017_fixedeffects_R2_semanticdecision_lmerTest` of the variance, and the random effects explained `r Nakagawa2017_randomeffects_R2_semanticdecision_lmerTest` [@nakagawaCoefficientDeterminationR22017].

Figures \@ref(fig:semanticdecision-interactions-with-vocabulary-size)-a and \@ref(fig:semanticdecision-interactions-with-vocabulary-size)-b demonstrate how lower-vocabulary participants (compared to higher-vocabulary participants) were more strongly influenced by both language- and vision-based similarity. In contrast, Figure \@ref(fig:semanticdecision-interactions-with-vocabulary-size)-c shows that higher-vocabulary participants benefitted more strongly from word concreteness. Since the variable that is most relevant to the semantic decision task is word concreteness, the present interactions suggest that higher-vocabulary participants were better able to focus on the most relevant information, whereas lower-vocabulary participants were sensitive to a greater breadth of information [@lim2020a; @pexman2018a; @yap2012a; @yap2017a].

(ref:semanticdecision-interactions-with-vocabulary-size) Interactions of vocabulary size with (a) language-based information, (b) visual strength and (c) word concreteness. Vocabulary size is constrained to deciles, whereas in the statistical analysis it contained more values within the current range. *n* = number of participants contained between decile values.

```{r semanticdecision-interactions-with-vocabulary-size, fig.cap = '(ref:semanticdecision-interactions-with-vocabulary-size)', out.height = '95%'}

# Run plot through source() rather than directly in this R Markdown document 
# to preserve the italicised text.

source('semanticdecision/frequentist_analysis/semanticdecision-interactions-with-vocabulary-size.R', 
       local = TRUE)

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticdecision/frequentist_analysis/plots/semanticdecision-interactions-with-vocabulary-size.pdf'
  ))

```

The present analysis uses a continuous measure of word concreteness. In contrast, @pexman2018a analysed the same data set after dividing the stimulus words into abstract and concrete subsets, which they analysed separately. Pexman and Yap found that high-vocabulary participants were more sensitive to the relative abstractness of words. Specifically, these participants were faster to classify very abstract words than mid-abstract ones, thus presenting a reverse concreteness effect. Such a reverse effect might stem from the bimodal distributions of concreteness ratings [@brysbaert2014a] and semantic decisions [@pexman2018a]. The reverse effect has also been found in semantic dementia patients [@connellStrengthPerceptualExperience2012]. Since the reverse effect contrasted with the long-established concreteness effect, the former has sometimes been regarded as an inconsistency.

Notwithstanding the aforementioned bimodal distributions, @trocheDefiningConceptualTopography2017 suggested that a continuous analysis remains necessary to study word concreteness [also see @cohenCostDichotomization1983]. Consistent with this, our present findings demonstrated the sensitivity of a continuous word-concreteness variable to patterns such as the greater role of task-relevant variables in high-vocabulary participants. In conclusion, the literature and our findings suggest that the split-data approach and the continuous approach to word concreteness are both useful. Where feasible, the application of both approaches would provide the most information.

### Visualising the estimates

Figure \@ref(fig:semanticdecision-confidence-intervals-plot) presents the means and 95% confidence intervals for the effects of interest.^[Bayesian estimates not shown as they were not valid. They are nonetheless available in [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results).]

```{r semanticdecision-confidence-intervals-plot, fig.cap = 'Means and 95\\% confidence intervals for the effects of interest in the semantic decision model.', out.width = '110%'}

# Run plot through source() rather than directly in this R Markdown document
# to preserve the format.

source('semanticdecision/frequentist_analysis/semanticdecision_confidence_intervals_plot.R', 
       local = TRUE)

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticdecision/frequentist_analysis/plots/semanticdecision_confidence_intervals_plot.pdf'
  ))

```

### Statistical power analysis

Figures \@ref(fig:semanticdecision-powercurve-plots-1-2-3) and \@ref(fig:semanticdecision-powercurve-plots-4-5-6-7) show the estimated power available for main effects and interactions of interest, respectively.

```{r semanticdecision-powercurve-plots-1-2-3, fig.cap = 'Power curves for some main effects in the semantic decision study.'}

# Run plot through source() rather than directly in this R Markdown document 
# to preserve the italicised text.
source('semanticdecision/power_analysis/semanticdecision_all_powercurves.R', 
       local = TRUE)

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticdecision/power_analysis/plots/semanticdecision_powercurve_plots_1_2_3.pdf'
  ))

```

```{r semanticdecision-powercurve-plots-4-5-6-7, fig.cap = 'Power curves for some interactions in the semantic decision study.'}

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/semanticdecision/power_analysis/plots/semanticdecision_powercurve_plots_4_5_6_7.pdf'
  ))

```

_______ interpret ____________

## Discussion

___________________

\clearpage

# Study 3: Lexical decision

The core data set in this study was the lexical decision subset of the English Lexicon Project---ELP [@balota2007a]. The lexical decision task differs from semantic priming and semantic decision in two important aspects.

1. **Less semantic processing.** The lexical decision paradigm is likely to involve less semantic processing than the other paradigms. ____________

2. **Single-word measures.** Compared to semantic priming and semantic decision, it is more difficult in the lexical decision paradigm to create word-to-word distance measures to capture language-based and vision-based information. The possibility of calculating the distance between words in consecutive trials is hindered by the need to skip trials, owing to the high prevalence of nonword trials in the lexical decision paradigm. Therefore, the measures must be based on each word alone. Accordingly, vision-based information can be operationalised as the visual strength of each word. Language-based information could be operationalised as any of several lexical variables. In the present study, word frequency was chosen as it had the most explanatory power out of 5 candidates---the other candidates being number of letters, number of syllables, orthographic Levenshtein distance and phonological Levenshtein distance (see [\underline{Appendix A}](#appendix-A-lexical-covariates)). It should also be noted that word frequency has been found to be more closely related to semantic variables than to lexical ones, such as word length, orthography, phonology [see Table 4 in @yap2012a].

Word frequency is also of interest due to its varying relationship to vocabulary size across different paradigms. @yap2012a found that higher-vocabulary participants in the ELP were more strongly influenced by word frequency than lower-vocabulary participants. The same finding also appeared in a lexical decision study in Chinese [@lim2020a]. In contrast, deeper semantic tasks, such as semantic priming [@yap2017a] and semantic decision [@pexman2018a], have yielded the opposite pattern, with the effect of word frequency decreasing in higher-vocabulary participants.

## Effects of interest

- $Z$-scored vocabulary age [`z_vocabulary_age`; calculated from `vocabAge` in @balota2007a]

- $Z$-scored, recoded participant's gender [`z_recoded_participant_gender`; calculated from `Gender` in @balota2007a]

- $Z$-scored word frequency [`z_word_frequency`; calculated from `LgSUBTLWF` in @balota2007a]

- $Z$-scored vision-based information in words [`z_visual_rating`; calculated from `Visual.mean` in @lynott2020a]

```{r}

# Calculate numbers to be reported in the paragraph below

# Save number of participants and words
lexicaldecision_number_participants = 
  length(unique(lexicaldecision$Participant))

lexicaldecision_number_words = length(unique(lexicaldecision$word))

# Number of words per participant.
# Save mean as integer and SD rounded while keeping trailing zeros
lexicaldecision_mean_words_per_participant = 
  lexicaldecision %>% group_by(Participant) %>% 
  summarise(length(unique(word))) %>% 
  select(2) %>% unlist %>% mean %>% round(0)

lexicaldecision_SD_words_per_participant = 
  lexicaldecision %>% group_by(Participant) %>% 
  summarise(length(unique(word))) %>% 
  select(2) %>% unlist %>% sd %>% sprintf('%.2f', .)

# Number of participants per word.
# Save mean as integer and SD rounded while keeping trailing zeros
lexicaldecision_mean_participants_per_word = 
  lexicaldecision %>% group_by(word) %>% 
  summarise(length(unique(Participant))) %>% 
  select(2) %>% unlist %>% mean %>% round(0)

lexicaldecision_SD_participants_per_word = 
  lexicaldecision %>% group_by(word) %>% 
  summarise(length(unique(Participant))) %>% 
  select(2) %>% unlist %>% sd %>% sprintf('%.2f', .)

```

The final data set contained `r lexicaldecision_number_participants` participants, `r lexicaldecision_number_words %>% formattable::comma(digits = 0)` words, and a total of `r length(lexicaldecision$z_RT) %>% formattable::comma(digits = 0)` RTs. On average, there were `r lexicaldecision_mean_words_per_participant` words per participant ($SD$ = `r lexicaldecision_SD_words_per_participant`), and conversely, `r lexicaldecision_mean_participants_per_word` participants per word ($SD$ = `r lexicaldecision_SD_participants_per_word`).

Figure \@ref(fig:lexicaldecision-correlations) shows the zero-order correlations among the predictors and the dependent variable.

```{r lexicaldecision-correlations, fig.cap = 'Zero-order correlations in the lexical decision study.', fig.width = 6, fig.height = 3.5, out.width = '50%'}

# Using the following variables...
lexicaldecision[, c('z_RT', 'z_vocabulary_age', 'z_word_frequency', 
                    'z_visual_rating', 'z_word_concreteness', 
                    'z_orthographic_Levenshtein_distance')] %>%

  # renamed for the sake of clarity
  rename('RT' = z_RT, 
         'Vocabulary age' = z_vocabulary_age, 
         'Word frequency' = z_word_frequency,
         'Visual strength' = z_visual_rating,
         'Word concreteness' = z_word_concreteness,
         'Orthographic Levenshtein distance' = z_orthographic_Levenshtein_distance) %>%

  # make correlation matrix (custom function from the 'R_functions' folder)
  correlation_matrix() + 
  theme(plot.margin = unit(c(0, 0, 0.1, -2), 'in'))

```

## Covariates

The following lexical covariates were included in the model to allow a rigorous analysis of the effects of interest.

- Lexical (see [\underline{Appendix A}](#appendix-A-lexical-covariates)): $Z$-scored orthographic Levenshtein distance [@balota2007a]

- Semantic: $z$-scored word concreteness [@brysbaert2014a], used as a covariate of visual rating.

### Diagnostics for the frequentist model

The model presented convergence warnings. To avoid removing important random slopes, which could increase the Type I error [@brauer2018a; @singmann2019a], we examined the model after refitting it using seven optimization algorithms through the 'allFit' function of the 'lme4' package [@batesPackageLme42021]. The results showed that all optimizers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential (Bates et al., 2021; see [\underline{Appendix B}](#appendix-B-frequentist-analysis-diagnostics)).

The residual errors were not normally distributed, and attempts to mitigate this deviation proved unsuccessful (see [\underline{Appendix B}](#appendix-B-frequentist-analysis-diagnostics)). However, this is not likely to have posed a major problem, as mixed-effects models are fairly robust to deviations from normality [@kniefViolatingNormalityAssumption2021; @schielzethRobustnessLinearMixed2020].

```{r}

# Calculate VIF for every predictor and return only the maximum VIF rounded up
maxVIF_lexicaldecision = car::vif(lexicaldecision_lmerTest) %>% max %>% ceiling

```

The model did not present multicollinearity problems, all VIFs being smaller than `r maxVIF_lexicaldecision` [@dormannCollinearityReviewMethods2013; @harrison2018a].

### Diagnostics for the Bayesian model

```{r}

# Calculate number of post-warmup draws (as in 'brms' version 2.17.0).
# Informative prior model used but same numbers in all three models.
lexicaldecision_post_warmup_draws = 
  (lexicaldecision_summary_informativepriors_exgaussian$iter -
     lexicaldecision_summary_informativepriors_exgaussian$warmup) *
  lexicaldecision_summary_informativepriors_exgaussian$chains

# As a convergence diagnostic, find maximum R-hat value for the 
# fixed effects across the three models.
lexicaldecision_fixedeffects_max_Rhat = 
  max(lexicaldecision_summary_informativepriors_exgaussian$fixed$Rhat,
      lexicaldecision_summary_weaklyinformativepriors_exgaussian$fixed$Rhat,
      lexicaldecision_summary_diffusepriors_exgaussian$fixed$Rhat) %>% 
  # Round
  sprintf('%.2f', .)

# Next, find find maximum R-hat value for the random effects 
# across the three models. 
lexicaldecision_randomeffects_max_Rhat = 
  max(lexicaldecision_summary_informativepriors_exgaussian$random[['Participant']]$Rhat,
      lexicaldecision_summary_weaklyinformativepriors_exgaussian$random[['Participant']]$Rhat,
      lexicaldecision_summary_diffusepriors_exgaussian$random[['Participant']]$Rhat,
      lexicaldecision_summary_informativepriors_exgaussian$random[['word']]$Rhat,
      lexicaldecision_summary_weaklyinformativepriors_exgaussian$random[['word']]$Rhat,
      lexicaldecision_summary_diffusepriors_exgaussian$random[['word']]$Rhat) %>% 
  # Round
  sprintf('%.2f', .)

```

Three Bayesian models were run that were respectively characterised by informative, weakly-informative and diffuse priors. In each model, `r lexicaldecision_summary_informativepriors_exgaussian$chains` chains were used. In each chain, `r lexicaldecision_summary_informativepriors_exgaussian$warmup %>% formattable::comma(digits = 0)` warmup iterations were run, followed by `r (lexicaldecision_summary_informativepriors_exgaussian$iter - lexicaldecision_summary_informativepriors_exgaussian$warmup) %>% formattable::comma(digits = 0)` post-warmup iterations. Thus, a total of `r lexicaldecision_post_warmup_draws %>% formattable::comma(digits = 0)` post-warmup draws were produced over all the chains.

The maximum $\widehat R$ value for the fixed effects across the three models was `r lexicaldecision_fixedeffects_max_Rhat`, suggesting that these effects converged [@schootBayesianStatisticsModelling2021; @vehtariRanknormalizationFoldingLocalization2021]. For the random effects, the maximum $\widehat R$ value was `r lexicaldecision_randomeffects_max_Rhat`, barely exceeding the 1.01 threshold [@vehtariRanknormalizationFoldingLocalization2021].

The posterior predictive checks were sound (see [\underline{Appendix C}](#appendix-C-Bayesian-analysis-diagnostics)). Furthermore, in the prior sensitivity analysis, the results were virtually identical with the three priors that were considered (to recall the priors, see Figure \@ref(fig:bayesian-priors) above; to view the results in detail, see [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results)).

## Results

Table \@ref(tab:lexicaldecision-frequentist-model) presents the results of the mixed-effects model.

```{r lexicaldecision-frequentist-model, results = 'asis'}

# Rename effects in plain language and specify the random slopes
# (if any) for each effect, in the footnote. For this purpose, 
# superscripts are added to the names of the appropriate effects.
# 
# In the interactions below, word-level variables are presented 
# first for the sake of consistency (the order does not affect 
# the results in any way). Also in the interactions, double 
# colons are used to inform the 'frequentist_model_table' 
# function that the two terms in the interaction must be split 
# into two lines.

rownames(KR_summary_lexicaldecision_lmerTest$coefficients)[
  rownames(KR_summary_lexicaldecision_lmerTest$coefficients) == 
    'z_vocabulary_age'] = 'Vocabulary age $^{\\text{a}}$'

rownames(KR_summary_lexicaldecision_lmerTest$coefficients)[
  rownames(KR_summary_lexicaldecision_lmerTest$coefficients) == 
    'z_recoded_participant_gender'] = 'Gender $^{\\text{a}}$'

rownames(KR_summary_lexicaldecision_lmerTest$coefficients)[
  rownames(KR_summary_lexicaldecision_lmerTest$coefficients) == 
    'z_orthographic_Levenshtein_distance'] = 'Orthographic Levenshtein distance'

rownames(KR_summary_lexicaldecision_lmerTest$coefficients)[
  rownames(KR_summary_lexicaldecision_lmerTest$coefficients) == 
    'z_word_concreteness'] = 'Word concreteness'

rownames(KR_summary_lexicaldecision_lmerTest$coefficients)[
  rownames(KR_summary_lexicaldecision_lmerTest$coefficients) == 
    'z_word_frequency'] = 'Word frequency $^{\\text{b}}$'

rownames(KR_summary_lexicaldecision_lmerTest$coefficients)[
  rownames(KR_summary_lexicaldecision_lmerTest$coefficients) == 
    'z_visual_rating'] = 'Visual strength $^{\\text{b}}$'

rownames(KR_summary_lexicaldecision_lmerTest$coefficients)[
  rownames(KR_summary_lexicaldecision_lmerTest$coefficients) == 
    'z_word_concreteness:z_vocabulary_age'] = 
  'Word concreteness : Vocabulary age'

rownames(KR_summary_lexicaldecision_lmerTest$coefficients)[
  rownames(KR_summary_lexicaldecision_lmerTest$coefficients) == 
    'z_word_concreteness:z_recoded_participant_gender'] = 
  'Word concreteness : Gender'

rownames(KR_summary_lexicaldecision_lmerTest$coefficients)[
  rownames(KR_summary_lexicaldecision_lmerTest$coefficients) == 
    'z_vocabulary_age:z_word_frequency'] = 
  'Word frequency : Vocabulary age'

rownames(KR_summary_lexicaldecision_lmerTest$coefficients)[
  rownames(KR_summary_lexicaldecision_lmerTest$coefficients) == 
    'z_vocabulary_age:z_visual_rating'] = 
  'Visual strength : Vocabulary age'

rownames(KR_summary_lexicaldecision_lmerTest$coefficients)[
  rownames(KR_summary_lexicaldecision_lmerTest$coefficients) == 
    'z_recoded_participant_gender:z_word_frequency'] = 
  'Word frequency : Gender'

rownames(KR_summary_lexicaldecision_lmerTest$coefficients)[
  rownames(KR_summary_lexicaldecision_lmerTest$coefficients) == 
    'z_recoded_participant_gender:z_visual_rating'] = 
  'Visual strength : Gender'

# Next, change the names in the confidence intervals object

rownames(confint_lexicaldecision_lmerTest)[
  rownames(confint_lexicaldecision_lmerTest) == 
    'z_vocabulary_age'] = 'Vocabulary age $^{\\text{a}}$'

rownames(confint_lexicaldecision_lmerTest)[
  rownames(confint_lexicaldecision_lmerTest) == 
    'z_recoded_participant_gender'] = 'Gender $^{\\text{a}}$'

rownames(confint_lexicaldecision_lmerTest)[
  rownames(confint_lexicaldecision_lmerTest) == 
    'z_orthographic_Levenshtein_distance'] = 'Orthographic Levenshtein distance'

rownames(confint_lexicaldecision_lmerTest)[
  rownames(confint_lexicaldecision_lmerTest) == 
    'z_word_concreteness'] = 'Word concreteness'

rownames(confint_lexicaldecision_lmerTest)[
  rownames(confint_lexicaldecision_lmerTest) == 
    'z_word_frequency'] = 'Word frequency $^{\\text{b}}$'

rownames(confint_lexicaldecision_lmerTest)[
  rownames(confint_lexicaldecision_lmerTest) == 
    'z_visual_rating'] = 'Visual strength $^{\\text{b}}$'

rownames(confint_lexicaldecision_lmerTest)[
  rownames(confint_lexicaldecision_lmerTest) == 
    'z_word_concreteness:z_vocabulary_age'] = 
  'Word concreteness : Vocabulary age'

rownames(confint_lexicaldecision_lmerTest)[
  rownames(confint_lexicaldecision_lmerTest) == 
    'z_word_concreteness:z_recoded_participant_gender'] = 
  'Word concreteness : Gender'

rownames(confint_lexicaldecision_lmerTest)[
  rownames(confint_lexicaldecision_lmerTest) == 
    'z_vocabulary_age:z_word_frequency'] = 
  'Word frequency : Vocabulary age'

rownames(confint_lexicaldecision_lmerTest)[
  rownames(confint_lexicaldecision_lmerTest) == 
    'z_vocabulary_age:z_visual_rating'] = 
  'Visual strength : Vocabulary age'

rownames(confint_lexicaldecision_lmerTest)[
  rownames(confint_lexicaldecision_lmerTest) == 
    'z_recoded_participant_gender:z_word_frequency'] = 
  'Word frequency : Gender'

rownames(confint_lexicaldecision_lmerTest)[
  rownames(confint_lexicaldecision_lmerTest) == 
    'z_recoded_participant_gender:z_visual_rating'] = 
  'Visual strength : Gender'

# Create table (using custom function from the 'R_functions' folder)
frequentist_model_table(
  KR_summary_lexicaldecision_lmerTest, 
  confint_lexicaldecision_lmerTest,
  order_effects = c('(Intercept)',
                    'Vocabulary age $^{\\text{a}}$',
                    'Gender $^{\\text{a}}$',
                    'Orthographic Levenshtein distance',
                    'Word concreteness',
                    'Word frequency $^{\\text{b}}$',
                    'Visual strength $^{\\text{b}}$',
                    'Word concreteness : Vocabulary age',
                    'Word concreteness : Gender',
                    'Word frequency : Vocabulary age',
                    'Visual strength : Vocabulary age',
                    'Word frequency : Gender',
                    'Visual strength : Gender'),
  interaction_symbol_x = TRUE,
  caption = 'Frequentist model for the lexical decision study.') %>%
  # kable_styling(latex_options = 'scale_down') %>%

  # Group predictors under headings
  pack_rows('Individual differences', 2, 3) %>% 
  pack_rows('Lexical covariate', 4, 4) %>% 
  pack_rows('Semantic variables', 5, 7) %>% 
  pack_rows('Interactions', 8, 13) %>%

  # Place table close to designated position and highlight covariates
  kable_styling(latex_options = c('HOLD_position', 'striped'), 
                stripe_index = c(4:5, 8:9)) %>%

  # Footnote describing abbreviations, random slopes, etc. 
  # LaTeX code used to format the text.
  footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored variables; \\\\textit{SE} = standard error;',
                           'CI = confidence interval. Shaded rows contain covariates. \\\\linebreak', 
                           '$^{\\\\text{a}}$ By-word random slopes were included for this effect.',
                           '$^{\\\\text{b}}$ By-participant random slopes were included for this effect.', 
                           # Begin lines after first one with a dot-sized indent
                           sep = ' \\\\linebreak \\\\phantom{.}'))

# Calculate R^2. This coefficient must be interpreted with caution 
# (Nakagawa et al., 2017; https://doi.org/10.1098/rsif.2017.0213). 
# Also, transform coefficient to rounded percentage.

Nakagawa2017_fixedeffects_R2_lexicaldecision_lmerTest = 
  paste0(
    (MuMIn::r.squaredGLMM(lexicaldecision_lmerTest)[1, 'R2m'][[1]] * 100) %>% 
      sprintf('%.2f', .), '%'
  )

Nakagawa2017_randomeffects_R2_lexicaldecision_lmerTest = 
  paste0(
    (MuMIn::r.squaredGLMM(lexicaldecision_lmerTest)[1, 'R2c'][[1]] * 100) %>% 
      sprintf('%.2f', .), '%'
  )

```

The fixed effects of this model explained `r Nakagawa2017_fixedeffects_R2_lexicaldecision_lmerTest` of the variance, and the random effects explained `r Nakagawa2017_randomeffects_R2_lexicaldecision_lmerTest` [@nakagawaCoefficientDeterminationR22017].

### Visualising the estimates

Figure \@ref(fig:lexicaldecision-frequentist-bayesian-plot-weaklyinformativepriors-exgaussian) presents the posterior distribution of each effect, based on the informative prior model. The models with the other priors produced virtually identical results (see [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results)). The figure also shows the frequentist estimates from Table \@ref(tab:lexicaldecision-frequentist-model), to facilitate the comparison.

```{r lexicaldecision-frequentist-bayesian-plot-weaklyinformativepriors-exgaussian, fig.cap = 'Estimates from the frequentist analysis (in red) and from the Bayesian analysis (in blue) for the lexical decision study. The frequentist means (represented by points) are flanked by 95\\% confidence intervals. The Bayesian means (represented by vertical lines) are flanked by 95\\% credible intervals, in light blue (in some cases, the interval is covered up by the bar of the mean).'}

# Run plot through source() rather than directly in this R Markdown document
# to preserve the format.

source('lexicaldecision/frequentist_bayesian_plots/lexicaldecision_frequentist_bayesian_plots.R', 
       local = TRUE)

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/lexicaldecision/frequentist_bayesian_plots/plots/lexicaldecision_frequentist_bayesian_plot_weaklyinformativepriors_exgaussian.pdf'
  ))

```

### Statistical power analysis

Figures \@ref(fig:lexicaldecision-powercurve-plots-1-2-3) and \@ref(fig:lexicaldecision-powercurve-plots-4-5-6-7) show the estimated power available for main effects and interactions of interest, respectively.

```{r lexicaldecision-powercurve-plots-1-2-3, fig.cap = 'Power curves for some main effects in the lexical decision study.'}

# Run plot through source() rather than directly in this R Markdown document 
# to preserve the italicised text.
source('lexicaldecision/power_analysis/lexicaldecision_all_powercurves.R', 
       local = TRUE)

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/lexicaldecision/power_analysis/plots/lexicaldecision_powercurve_plots_1_2_3.pdf'
  ))

```

```{r lexicaldecision-powercurve-plots-4-5-6-7, fig.cap = 'Power curves for some interactions in the lexical decision study.'}

include_graphics(
  paste0(
    getwd(),  # Circumvent illegal characters in file path
    '/lexicaldecision/power_analysis/plots/lexicaldecision_powercurve_plots_4_5_6_7.pdf'
  ))

```

_______ interpret ____________

## Discussion

___________________

# General discussion

In all three studies, the main effects and the interactions of language-based information were larger than those of vision-based information, consistent with previous research [...]. Beyond that, the results revealed a dynamic process influenced by three levels of variation: participants, words and tasks. The associations that appeared across these levels revealed the roles of language-based and vision-based mechanisms in conceptual processing.

The RTs of higher-vocabulary participants were influenced by a smaller number of variables than those of lower-vocabulary participants. This converges with previous findings suggesting that higher and lower-vocabulary participants are affected by different variables. Potentially, the variables affecting higher-vocabulary participants are more relevant to the task [@lim2020a; @pexman2018a; @yap2012a; @yap2017a].

## Differences between measurement instruments and the associated risks

We also compared two measures of visual priming. The first measure was operationalised as the difference in visual strength [@lynott2020a] between the prime and the target word in each trial. The second measure, created by [@petilli2021a], was based on vector representations trained on images. The results revealed that the visual strength measure was significantly superior in explaining RTs. This difference was not due to an excessive collinearity between these measures ($r$ = .02). Also importantly, both measures appeared to be valid based on their correlations with language-based similarity and with word concreteness.

If we indeed accept that both the above measures were valid, we must reflect on the possibility that measurement instruments create confounds when different systems are compared. That is, in the case of linguistic and embodied processing, the large difference between the effect sizes of these systems---found in the three current studies and in the previous literature [...]---would not be trustworthy if the instruments that were used to measure the language system were far more precise than the instruments used to measure the embodiment system. In this sense, consider how variables are refined in research: it is done by comparing the performance of different variables. Critically, the literature seems to contain many comparisons of text-based variables, some dating from the 1990s [@jones2006a; @lund1996a; @mikolovEfficientEstimationWord2013; @dedeyneBetterExplanationsLexical2013; @de2016a; @guenther2016a; @guntherLatentSemanticAnalysis2016; @wingfieldUnderstandingRoleLinguistic2022]. In contrast, the work on embodiment variables began more than a decade afterwards, and this work has been more concerned with comparisons of different *modalities*---e.g., valence, visual strength, auditory strength, etc. [@lynott2020a; @lynottModalityExclusivityNorms2009; @newcombeEffectsEmotionalSensorimotor2012]. Thus, this historical accident could account for a portion of the superiority of linguistic information over embodied information [as found in @lam2015a; @pecherDoesPizzaPrime1998; @petilli2021a; @banksLinguisticDistributionalKnowledge2021; @kiela2014a; @louwerse2015a].

The case of different measurement instruments is one of several factors that can exert a great influence in analyses. In the medium term, it may pay dividends to devote more work to comparing different instruments and, more generally, different analyses [see @barsalouEstablishingGeneralizableMechanisms2019; @botvinik-nezerVariabilityAnalysisSingle2020; @wagenmakersOneStatisticalAnalysis2022].

## Statistical power

Power analyses were performed to _____________________. _______________________. The sample sizes required for some of the effects are not easily feasible with the usual distribution of funding in psychological research projects.

\clearpage

# References

::: {#refs}
:::

\newpage

# (APPENDIX) Appendix {-}

<!-- Every appendix must be referenced below (see https://github.com/crsh/papaja/issues/496#issuecomment-996084228) -->

<!-- Following APA format, precede figure and table numbers with the title letter of this appendix -->
\renewcommand{\thefigure}{A\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{A\arabic{table}} \setcounter{table}{0}

```{r, child = 'manuscript/appendix-A-lexical-covariates.Rmd'}
```

\clearpage

<!-- Following APA format, precede figure and table numbers with the title letter of this appendix -->
\renewcommand{\thefigure}{B\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{B\arabic{table}} \setcounter{table}{0}

```{r, child = 'manuscript/appendix-B-frequentist-analysis-diagnostics.Rmd'}
```

\clearpage

<!-- Following APA format, precede figure and table numbers with the title letter of this appendix -->
\renewcommand{\thefigure}{C\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{C\arabic{table}} \setcounter{table}{0}

```{r, child = 'manuscript/appendix-C-Bayesian-analysis-diagnostics.Rmd'}
```

\clearpage

<!-- Following APA format, precede figure and table numbers with the title letter of this appendix -->
\renewcommand{\thefigure}{D\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{D\arabic{table}} \setcounter{table}{0}

```{r, child = 'manuscript/appendix-D-interaction-plots.Rmd'}
```

\clearpage

<!-- Following APA format, precede figure and table numbers with the title letter of this appendix -->
\renewcommand{\thefigure}{E\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{E\arabic{table}} \setcounter{table}{0}

```{r, child = 'manuscript/appendix-E-Bayesian-analysis-results.Rmd'}
```

\clearpage

### 2022-06-24 manuscript/manuscript.tex
24062022

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
  man,floatsintext]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Language and vision in conceptual processing: Multilevel analysis and statistical power},
  pdflang={en-EN},
  pdfkeywords={semantic, conceptual processing, vocabulary size, statistical power},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{semantic, conceptual processing, vocabulary size, statistical power}
\usepackage{csquotes}
\renewcommand\author[1]{}
\renewcommand\affiliation[1]{}
\authorsnames[1, 2, 2]{Pablo Bernabeu, Dermot Lynott, Louise Connell}
\authorsaffiliations{{Department of Psychology, Lancaster University, UK}, {Department of Psychology, Maynooth University, Ireland}}
\renewcommand{\topfraction}{.75}
\renewcommand{\bottomfraction}{.4}
\renewcommand{\textfraction}{.15}
\renewcommand{\floatpagefraction}{.6}
\setlength{\@fptop}{0pt}
\setcounter{topnumber}{3}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{4}
\usepackage{amsmath}
\usepackage{upgreek}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\renewcommand\appendix{}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Language and vision in conceptual processing: Multilevel analysis and statistical power}
\author{\phantom{0}}
\date{}

\shorttitle{LANGUAGE AND VISION IN CONCEPTUAL PROCESSING}

\authornote{

\addORCIDlink{Pablo Bernabeu}{0000-0003-1083-2460}

\addORCIDlink{Dermot Lynott}{0000-0001-7338-0567}

\addORCIDlink{Louise Connell}{0000-0002-5291-5267}

This manuscript is a draft and includes some appendices. Correspondence can be addressed to Pablo Bernabeu on \href{mailto:pcbernabeu@gmail.com}{\nolinkurl{pcbernabeu@gmail.com}}. All materials are available at \url{http://doi.org/10.17605/OSF.IO/UERYQ}.

}

\affiliation{\phantom{0}}

\abstract{%
Research over the past two decades has suggested that conceptual processing depends on both language-based and vision-based information. We tested this interplay at three levels of the data: individual differences, words and tasks. To this aim, we drew on three existing data sets that were composed of large samples, and implemented the paradigms of semantic priming, semantic decision and lexical decision. After extending these data sets with language-based and vision-based measures, we performed the analysis using mixed-effects models that included a comprehensive array of fixed effects---including covariates---and random effects. Overall, language-based information was found to be more important than vision-based information. Furthermore, in the semantic priming study---whose task required distinguishing between words and nonwords---, both language-based and vision-based information were more influential when words were presented faster. In addition, higher-vocabulary participants presented a greater effect of language-based similarity than lower-vocabulary participants. Conversely, lower-vocabulary participants presented a greater effect of vision-based information, which was less relevant to the task. This `relevance advantage' for higher-vocabulary participants also appeared in the semantic decision study, whose task required distinguishing between concrete and abstract words. Specifically, higher-vocabulary participants were more strongly influenced by word concreteness than lower-vocabulary participants. Furthermore, we compared the effects of different measures of visual information. Lastly, we estimated the sample size required to reliably examine each effect of interest. We found that 300 participants would suffice to examine language-based information contained in words, whereas more than 1,000 participants would be necessary to examine vision-based information as well as the interactions between both the former variables and vocabulary size, gender and presentation speed.
}

\begin{document}
\maketitle

\setstretch{1.5}
\hypertarget{section}{%
\section{}\label{section}}

Research over the past two decades has suggested that conceptual processing involves both `linguistic' and `embodied' systems of the brain. The language system is characterised by associations across networks of words (Landauer et al., 1998; Pylyshyn, 1973), whereas the embodiment system is characterised by associations within perceptual, motor, affective and social domains (Barsalou, 1999; Diveica et al., 2022). Both systems have strengths and limitations (Connell, 2019; Dove, 2020; Kumar, 2021; Louwerse et al., 2015; Mahon \& Hickok, 2016). As a result, conceptual processing flexibly draws on these systems following the demands of the context (Sato et al., 2008; Shebani \& Pulvermüller, 2018; Willems \& Casasanto, 2011).

The language system is involved in the representation of both abstract and concrete concepts (Ponari, Norbury, Rotaru, et al., 2018; Reggin et al., 2021). For instance, measures of distributional semantic distance---solely based on texts---have been shown to capture aspects of the real world with considerable accuracy (Contreras Kallens et al., 2022; De Deyne et al., 2013; Kumar et al., 2020; Louwerse \& Zwaan, 2009). Although the language system is likely more important for the processing of abstract---rather than concrete---concepts (Barca et al., 2020; Duñabeitia et al., 2009; Hultén et al., 2021), although the degree of this difference could be small (De Deyne et al., 2013). Language-based regularities may even allow distinguishing between concrete and abstract words, as word concreteness is consistently related to linguistic characteristics such as part of speech, morphological structure, countability and etymology (Lievers et al., 2021).

Regarding the time course, the language system is activated more quickly in semantically-deep tasks (Connell \& Lynott, 2013; Louwerse \& Connell, 2011), whereas both systems are similarly fast in semantically-shallow tasks (Petilli et al., 2021). As a result of these characteristics, the language system is equipped to support a major part of conceptual processing (Connell, 2019; Connell \& Lynott, 2014). However, the language system is hindered by the symbol grounding problem, which refers to the impossibility of obtaining meaning---or `grounding' lexical content in reality---on the sole basis of word-to-word associations (Günther et al., 2021, 2018; Harnad, 1990; Louwerse, 2011). Another limitation is caused by the finite vocabularies of languages, which sometimes fall short of the richness of sensorimotor experience (De Deyne et al., 2021; Günther et al., 2021; Majid \& Burenhult, 2014; Majid \& Levinson, 2011; Majid \& van Staden, 2015). In conclusion, word-to-word associations appear to be necessary but not sufficient for conceptual processing.

The embodiment system is best suited for the representation of concrete concepts, such as those involving perceptual features (Ostarek \& Huettig, 2017; Pecher et al., 1998; Yee et al., 2012) and actions (Riccardi et al., 2019). Some research has suggested that embodied simulation plays an integral role in conceptual processing (Pulvermüller, 2013), at least in the context of relatively-semantic tasks and stimuli (Connell \& Lynott, 2016; García et al., 2020; Lebois et al., 2015; Ostarek \& Huettig, 2017; Pecher et al., 1998; Shebani et al., 2021; Vitale et al., 2021; Vukovic et al., 2017; X. Wang et al., 2021; Yee et al., 2012). For instance, Riccardi et al. (2019) investigated the comprehension of action verbs and abstract verbs in left-hemisphere stroke patients, and found that the processing of action concepts relied more heavily on sensory-motor areas. Furthermore, studies have suggested that even abstract concepts may be partially grounded in modality-specific domains such as emotion, sociality and interoception (Conca et al., 2021; Connell et al., 2018; Diveica et al., 2022; Kousta et al., 2011; Vigliocco et al., 2014; X. Wang et al., 2021).

However, other research has curtailed the importance of this system (Bottini et al., 2021; Garcea et al., 2013; Günther et al., 2021, 2018; Mahon \& Caramazza, 2008; Montero-Melis et al., 2022; Vannuscorps et al., 2016). For instance, studies have found that lesions to motor brain areas did not systematically impair the processing of action concepts in language (Negri et al., 2007; Papeo et al., 2010).

\hypertarget{interplay-between-language-and-embodiment-systems}{%
\subsection{Interplay between language and embodiment systems}\label{interplay-between-language-and-embodiment-systems}}

The above characteristics make the language and the embodiment systems complementary to each other (Andrews et al., 2009; De Deyne et al., 2021; J. Wang et al., 2010). A comprehensive approach to both these systems requires a direct comparison of them. Studies tackling such a comparison have found that the systems are selectively engaged, following contextual demands (Connell \& Lynott, 2013; Louwerse \& Connell, 2011; Ostarek \& Huettig, 2017; Petilli et al., 2021). For instance, the role of perceptual simulation appears to be augmented in slower responses (Louwerse \& Connell, 2011), when words are presented more slowly (Lam et al., 2015), and in tasks prompting deeper semantic processing (Connell \& Lynott, 2013; Louwerse \& Connell, 2011; Ostarek \& Huettig, 2017; Petilli et al., 2021).

\hypertarget{the-present-study}{%
\section{The present study}\label{the-present-study}}

There is considerable evidence supporting the `hybrid' theory positing that conceptual processing depends on both language and embodiment systems (Barsalou et al., 2008; Connell \& Lynott, 2013; Louwerse, 2011). Nonetheless, there are also reasons to continue testing this theory. Firstly, the coexistence of several systems in a scientific theory must be thoroughly justified, due to the value of simplicity, as epitomised by Occam's razor (Gallese \& Lakoff, 2005; Tillman et al., 2015). This point is particularly pressing because the language system has consistently produced larger effect sizes than the embodiment system (Banks et al., 2021; Kiela \& Bottou, 2014; Lam et al., 2015; Louwerse et al., 2015; Pecher et al., 1998; Petilli et al., 2021). Secondly, mixed evidence has appeared regarding some aspects of the interplay. For instance, whereas some studies have suggested that the language system becomes relevant before the embodiment system (Lam et al., 2015; Louwerse \& Connell, 2011), a recent study found the opposite pattern (Petilli et al., 2021). Similarly, whereas some evidence has suggested that female participants might draw on the language system more prominently than males (Hutchinson \& Louwerse, 2013), other research has suggested that this difference could be negligible (Wallentin, 2020). Thirdly, the role of individual differences has not been examined in most of the studies addressing the language--embodiment interplay. Fourthly and last, the scarcity of statistical power that has ailed some studies in cognitive psychology and neuroscience (Marek et al., 2022; Vasishth \& Gelman, 2021) is likely to have affected some studies in the present topic area, too (see Lynott et al., 2014; Montero-Melis et al., 2022).

The above open questions were addressed in the present study. These questions were overarched by the main research question, which examined whether the interplay between linguistic and visual processing held in the expected direction and at multiple levels of the experimental structure. To study this question, we drew on the data sets from three previous studies whose samples of participants were larger than average. These studies implemented the paradigms of semantic priming (Hutchison et al., 2013), semantic decision (Pexman et al., 2017) and lexical decision (Balota et al., 2007). Importantly, we extended these data sets with

\hypertarget{levels-of-analysis}{%
\section{Levels of analysis}\label{levels-of-analysis}}

Experimental data in psycholinguistics often consists of various levels, such as participants, words and tasks. A simultaneous examination of these levels should improve our understanding of the evidence collected (Ostarek \& Bottini, 2021). For instance, this cross-examination can help increase our certainty on the attribution of explanatory power to each level, as well as allowing a comparison of the explanatory power across levels. This multilevel approach is complementary to another approach in the field which seeks to test the causal contribution of different sources of information to conceptual processing---e.g., language (Ponari, Norbury, Rotaru, et al., 2018), perception (Stasenko et al., 2014) and action (Speed et al., 2017).

The three levels examined in this study are described below.

\hypertarget{participant-level}{%
\subsection{Participant level}\label{participant-level}}

*** to be edited *** Individual differences in domains such as language, perception, mental imagery and physical experience (e.g., Davies et al., 2017; Dils \& Boroditsky, 2010; Fetterman et al., 2018; Holt \& Beilock, 2006; Mak \& Willems, 2019; Miceli et al., 2022; Pexman \& Yap, 2018; Vukovic \& Williams, 2015; Yap et al., 2012, 2017).\footnote{According to Lamiell (2019), `individual differences' is a misnomer in that the methods used to analyse individual differences (e.g, regression) are not participant-specific. We think that this observation is mitigated in the context of mixed-effects models (as used in our current study), which incorporate by-participant random intercepts and random slopes.} Furthermore, in some topic areas in which individual differences have not featured as prominently, the data have revealed a non-trivial role of individual differences (Kos et al., 2012; Montero-Melis, 2021).

\hypertarget{vocabulary-size}{%
\subsubsection{Vocabulary size}\label{vocabulary-size}}

Vocabulary size refers to the number of words a person can recognise out of a discrete set. Higher-vocabulary participants are expected to respond faster overall (Pexman \& Yap, 2018). Some previous studies have found that the effect of vocabulary size was moderated by variables related to general intelligence, such as processing speed (Ratcliff et al., 2010; Yap et al., 2012). Owing to those findings, and the recommendations from other studies (James et al., 2018; Pexman \& Yap, 2018; Sassenhagen \& Alday, 2016), the present studies included covariates of vocabulary size, where available.These covariates were measures of intelligence that were not vocabulary-based, namely, attentional control in Study 1 and information uptake in Study 2 (such a variable was not available for Study 3).

\hypertarget{word-level}{%
\subsection{Word level}\label{word-level}}

*** to be edited *** Semantic or lexical information in words (e.g., De Deyne et al., 2021; Lam et al., 2015; Lund et al., 1995; Lund \& Burgess, 1996; Lynott et al., 2020; Mandera et al., 2017; Pexman et al., 2017; Santos et al., 2011; Wingfield \& Connell, 2022)

\begin{itemize}
\item
  \emph{Variables in this study:} degree of association between words, degree of vision-based information in single words
\item
  Covariates: lexical variables and word concreteness.
\item
  Lexical variables: The lexical covariates were selected in each study out of the same 5 variables, which have been identified as important in previous research {[}Wingfield and Connell (2022); see \protect\hyperlink{general-statistical-analyses}{\underline{General statistical analysis}} for details{]}.
\item
  Word concreteness: Adjusting for word concreteness was deemed important due to the pervasive effect of this variable across lexical-semantic tasks (Brysbaert et al., 2014; Connell \& Lynott, 2012; Pexman \& Yap, 2018). Furthermore, it has been recently suggested that the effect of word concreteness does not stem from perceptual simulation, but instead from modality-independent properties of words (Bottini et al., 2021).
\end{itemize}

Studies have operationalised the \emph{language system} using measures that capture the relationships among words without explicitly drawing on any sensory or affective modalities. Two main types of linguistic measures exist: those based on text corpora---dubbed \emph{word co-occurrence} measures (Bullinaria \& Levy, 2007; Petilli et al., 2021; Wingfield \& Connell, 2022)---and those based on associations collected from human participants---dubbed \emph{word association} measures (De Deyne et al., 2016, 2019). Word co-occurrence is more purely linguistic, as word association captures more of the sensory and affective meaning of words (De Deyne et al., 2021). In Studies 1 and 2 below, word co-occurrence measures are used to represent the language system at the word level. In Study 3, however, such a measure could not be implemented. The measurement of priming across consecutive trials was not possible due to the high prevalence of nonword trials throughout the experiment.

The embodiment system has been represented by measures that explicitly draw on perceptual, motor or affective modalities (Fernandino et al., 2022). The perceptual modalities used in studies have often matched the 5 prototypical senses---vision, hearing, touch, taste, smell (Bernabeu et al., 2017, 2021; Louwerse \& Connell, 2011)---and, less often, interoception (Connell et al., 2018). Yet, out of these senses, vision has been most frequently used in research (e.g., Bottini et al., 2021; De Deyne et al., 2021; Pearson \& Kosslyn, 2015; Petilli et al., 2021; Yee et al., 2012). The prevalence of vision in research could be due to the prevalence of this sense in the brain (Reilly et al., 2020) and in language (Lynott et al., 2020; Winter et al., 2018). Furthermore, for the purpose of examining individual differences along with word-level variables, vision is easier to tap into than other senses. For instance, the perception of visual motion can be measured using a standard computer screen (Rajananda et al., 2018). Owing to these reasons, the three studies reported below implement the visual modality to represent the embodiment system at the word level.

\hypertarget{task-level}{%
\subsection{Task level}\label{task-level}}

*** to be edited ***

\begin{itemize}
\tightlist
\item
  \emph{Variable in this study:} stimulus-onset asynchrony (SOA), present in Study 1 only.\footnote{The names of all variables were slightly adjusted for this text to facilitate their understanding---for instance, by replacing underscores with spaces (see code scripts at \url{https://osf.io/ueryq}). One specific case deserves further comment. We use the formula of the `stimulus-onset asynchrony' (SOA) in this paper, instead of the `interstimulus interval' (ISI), as the SOA has been more commonly used in previous papers (e.g., Hutchison et al., 2013; Pecher et al., 1998; Petilli et al., 2021; Yap et al., 2017). The difference between these formulas is that the ISI does not count the presentation of the prime word (example equivalences between ISI and SOA are available in Lam et al. (2015), and in Figure 1A of Di Lollo et al. (2004)). In the current study, the presentation of the prime word lasts 150 ms. Thus, the 200-ms SOA is equivalent to an ISI of 50 ms, and the 1,200-ms SOA corresponds to an ISI of 1,050 ms (Hutchison et al., 2013). The use of either formula in the analysis would not change our results, as we recoded the levels of the factor as -0.5 and +0.5, and then z-scored those, following the advice of Brauer and Curtin (2018). In our analyses (\url{https://osf.io/ueryq}), we used the ISI formula as it was the one present in the data set of Hutchison et al. (2013) (retrieved from \url{https://www.montana.edu/attmemlab/documents/all\%20ldt\%20subs_all\%20trials3.xlsx}}).
\end{itemize}

In addition, the different paradigms applied across the three studies can be compared, albeit cautiously as the studies differ in other influential ways, such as the number of participants and stimulus words. The three tasks examined in the present studies are likely to reflect different degrees of semantic depth, in the following order (for background, see Connell \& Lynott, 2013; Lam et al., 2015; Ostarek \& Huettig, 2017; Versace et al., 2021; Wingfield \& Connell, 2022).

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Semantic decision} (Study 2) likely elicits the deepest semantic processing, as the instructions of this task ask for a concreteness judgement. In this task, participants are asked to classify words as abstract or concrete.
\item
  \textbf{Semantic priming} (Study 1). The task in the semantic priming paradigm is often lexical decision, as in Study 1 herein. The fundamental characteristic of this paradigm is that, in each trial, a prime word is presented for a very short period before the target word. The prime word is not relevant to the task. Nonetheless, participants process both the prime word and the target word, and this combination allows researchers to analyse responses based on the relationship between those words. Therefore, this paradigm is more deeply semantic than the lexical decision paradigm. Indeed, slower responses in semantic priming studies---reflecting difficult lexical decisions---have been linked to larger priming effects (Balota et al., 2008; Hoedemaker \& Gordon, 2014; Yap et al., 2013), suggesting a degree of semantic association that does not appear in the standard lexical decision paradigm.
\item
  \textbf{Lexical decision} (Study 3) is likely the semantically-shallowest task (see Balota \& Lorch, 1986; Becker et al., 1997; Connell \& Lynott, 2013; de Wit \& Kinoshita, 2015; Joordens \& Becker, 1997; Ostarek \& Huettig, 2017).
\end{enumerate}

\hypertarget{interactions-across-levels}{%
\subsection{Interactions across levels}\label{interactions-across-levels}}

The three levels are strongly intertwined, and studies have probed into more than one level at once: for instance, word level and individual level (Aujla, 2021; Lim et al., 2020; Pexman \& Yap, 2018; Yap et al., 2009), or word level and task level (Connell \& Lynott, 2013; Ostarek \& Huettig, 2019; Petilli et al., 2021). Thus, hypotheses are available regarding interactions across levels, as addressed below.

\hypertarget{vocabulary-size-and-linguistic-features}{%
\subsubsection{Vocabulary size and linguistic features}\label{vocabulary-size-and-linguistic-features}}

Three hypotheses exist regarding the interaction between vocabulary size and lexical-semantic features. First, higher-vocabulary participants---compared to lower-vocabulary ones---might be more sensitive to linguistic features, thanks to a larger number of semantic associations (Connell, 2019; Landauer et al., 1998; Louwerse et al., 2015; Paivio, 1990; Pylyshyn, 1973). For instance, Yap et al. (2017) observed a larger semantic priming effect in higher-vocabulary participants from (Hutchinson \& Louwerse, 2013). The second hypothesis, in contrast, states that higher-vocabulary participants would be \emph{less} sensitive to linguistic features, thanks to a more automatic process. For instance, Yap et al. (2009) observed a smaller semantic priming effect in higher-vocabulary participants. Similarly, Yap et al. (2012) found that higher-vocabulary participants in a lexical decision task (Balota et al., 2007) were less sensitive to a cluster of lexical and semantic features (i.e., word frequency, semantic neighborhood density and number of senses). Last, the third hypothesis proposes that higher-vocabulary participants might present a selective sensitivity, tailored to the task. For instance, Pexman and Yap (2018) analysed the semantic decision task of Pexman et al. (2017), in which participants assessed the concreteness of words. Pexman and Yap found that higher-vocabulary participants---compared to lower-vocabulary ones---were more sensitive to word concreteness and less sensitive to word frequency and age of acquisition, which were less relevant to the task (also see Lim et al., 2020). The three hypotheses herein were tested in the present study by revisiting some of the aforementioned studies (Balota et al., 2007; Hutchinson \& Louwerse, 2013; Pexman et al., 2017).

\hypertarget{vocabulary-size-and-visual-strength}{%
\subsubsection{Vocabulary size and visual strength}\label{vocabulary-size-and-visual-strength}}

Research demonstrating the interplay between linguistic and embodied information (Connell, 2019; Louwerse et al., 2015; Paivio, 1990) affords the hypothesis that lower-vocabulary participants---compared to higher-vocabulary ones---might profit more from sensory, motor, affective and social associations of the words.

\hypertarget{gender-and-linguistic-features}{%
\subsubsection{Gender and linguistic features}\label{gender-and-linguistic-features}}

In addition, the language system is expected to be more important in female than male participants (Burman et al., 2008; Hutchinson \& Louwerse, 2013; Jung et al., 2019; Ullman et al., 2008), provided that this interaction effect is not too small to be detected (Wallentin, 2020).

In another study, Schmidtke et al. (2018) collected human ratings on the association between words that make up compounds. Some compounds were found to be relatively transparent---e.g., \emph{doorbell}---, and others relatively opaque---e.g., \emph{deadline}. Furthermore, Schmidtke et al. (2018) found an interaction between semantic transparency and participants' reading experience (the latter measure encompassing vocabulary size and exposure to printed materials): namely, more experienced readers processed transparent compounds more quickly than opaque ones, whereas less experienced readers processed opaque compounds more quickly than transparent ones. This interaction suggests \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_. Thus, \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_.

\hypertarget{power-analysis}{%
\subsection{Power analysis}\label{power-analysis}}

Statistical power depends on the following factors: (1) sample size---comprising the number of participants, items, trials, etc.---, (2) effect size, (3) measurement variability and (4) number of comparisons being performed (Kumle et al., 2021). Out of these, sample size is the factor that can best be controlled by researchers (Kumle et al., 2021). The three studies we present below, containing larger-than-average sample sizes, offer an opportunity to conduct an a-priori power analysis to help determine the sample size of future studies (Albers \& Lakens, 2018).

\hypertarget{motivations}{%
\subsubsection{Motivations}\label{motivations}}

Insufficient statistical power lowers the reliability of effect sizes, and increases the likelihood of false positive results---i.e., Type I error---and of false negative results---i.e., Type II error (Gelman \& Carlin, 2014; Loken \& Gelman, 2017; Tversky \& Kahneman, 1971; von der Malsburg \& Angele, 2017). For instance, Vasishth and Gelman (2021) illustrate how, in low-powered studies, effect sizes associated with significant results tend to be overestimated (also see Vasishth et al., 2018).

Over the past decade, replication studies and power analyses have uncovered insufficient sample sizes in psychology (Brysbaert, 2019; Lynott et al., 2014; Montero-Melis et al., 2017, 2022; Rodríguez-Ferreiro et al., 2020; Vasishth et al., 2018). In the neighbouring field of neuroscience, Marek et al. (2022) recently estimated the sample size that is required to reliably study the mapping between individual differences, such as fluid intelligence, and brain structures. Marek et al.~found that the current median of 25 participants contributing to one of these studies contrasted with the thousands of participants---around 10,000---that would be needed for a well-powered study (also see Button et al., 2013).

More topic-specific power analyses are necessary due to three reasons. Firstly, power analyses provide greater certainty on the reasons behind non-replications (e.g., Open Science Collaboration, 2015), and behind non-significant results. Indeed, insufficient power is one of the possible reasons, alongside procedural errors or subtler methodological differences, and publication bias (Anderson et al., 2016; Barsalou, 2019; Corker et al., 2014; Gilbert et al., 2016; Williams, 2014). Currently, if we consider---for instance---research on individual differences, we will find several non-significant results, both in behavioural studies (e.g., Hedge et al., 2018; Rodríguez-Ferreiro et al., 2020; for a Bayes factor analysis, see Rouder \& Haaf, 2019) and in neuroscientific studies (e.g., Diaz et al., 2021). A greater availability of power analyses in specific topics will at least shed light on the role of power in the results. Secondly, power analyses facilitate the identification of sensible sample sizes for future studies. Thirdly, power analyses help maximise the use of research funding in the long term by fostering studies that are more replicable (see Vasishth \& Gelman, 2021).

\hypertarget{methods}{%
\section{Methods}\label{methods}}

The analytical method was largely similar across the three studies. Below, we present the commonalities in the statistical analyses and in the power analyses.

\hypertarget{general-statistical-analyses}{%
\subsection{General method for statistical analyses}\label{general-statistical-analyses}}

The statistical analysis was designed to examine the unique contribution of each effect of interest. In all three studies, the dependent variable---response time (RT)---was z-scored around each participant's mean to curb the influence of each participant's baseline speed (Balota et al., 2007; Kumar et al., 2020; Lim et al., 2020; Pexman et al., 2017; Pexman \& Yap, 2018; Yap et al., 2012, 2017). This was important because the size of experimental effects is known to increase with longer RTs (Faust et al., 1999). Next, binary predictors were recoded into continuous variables (Brauer \& Curtin, 2018). Specifically, participants' gender was recoded as follows: male = -0.5; female = 0.5; NA = 0. The SOAs in Study 1 were recoded as follows: 150 ms = -0.5; 1,200 ms = 0.5. Finally, following Brauer and Curtin (2018), all predictors were z-scored (i.e., \(M \approx\) 0, \(SD \approx\) 1).

Several covariates---or nuisance variables---were included, as detailed in each study, to allow a rigorous analysis of the effects of interest (Sassenhagen \& Alday, 2016). Unlike the effects of interest, these covariates were not critical to the research question. They comprised lexical variables (e.g., word frequency) and participant-specific variables (e.g., attentional control). The lexical covariates were selected in every study out of the same 5 variables, which had been used as covariates in Wingfield and Connell (2022), and are widely used (e.g., Petilli et al., 2021). They comprised: number of letters (i.e., orthographic length), word frequency, number of syllables (both the latter from Balota et al., 2007), orthographic Levenshtein distance (Yarkoni et al., 2008) and phonological Levenshtein distance (Suárez et al., 2011). The selection among these candidates was performed because some of them were highly intercorrelated---i.e., \(r\) \textgreater{} .70 (Dormann et al., 2013; Harrison et al., 2018). The correlations and the selection models are available in \protect\hyperlink{appendix-A-lexical-covariates}{\underline{Appendix A}}.

\hypertarget{random-effects}{%
\subsubsection{Random effects}\label{random-effects}}

The participants and the stimulus items were crossed in the three studies. That is, each participant was presented with a subset of the stimulus words. Conversely, each word was presented to a subset of participants. Therefore, linear mixed-effects models were implemented. These models included a maximal random-effects structure, with by-participant and by-word random intercepts, and the appropriate random slopes for all effects of interest (Barr et al., 2013). In the case of interactions, random slopes were included only when the variables interacting varied within the same unit (Brauer \& Curtin, 2018)---e.g., an interaction of two variables varying within participants (only present in Study 1). Owing to convergence warnings, random slopes for controlled covariates were removed, inspired by Remedy 11 from Brauer and Curtin (2018). Exceptionally, in the Bayesian models for the lexical decision study, the random slopes for the covariates did not have to be removed.

To avoid inflating the Type I error rate (false positives), the random slopes for the effects of interest were never removed (see Table 17 in Brauer \& Curtin, 2018; for an example of this approach, see Diaz et al., 2021). This approach provides a better protection against false positives (Barr et al., 2013; Brauer \& Curtin, 2018; Singmann \& Kellen, 2019) than the practice of removing random slopes when they do not significantly improve the fit (e.g., Bernabeu et al., 2017; Pexman \& Yap, 2018; see Bates et al., 2015).

\hypertarget{frequentist-analysis}{%
\subsubsection{Frequentist analysis}\label{frequentist-analysis}}

\emph{P} values were calculated with the Kenward-Roger approximation for degrees of freedom (Luke, 2017), using the `lmerTest' package, Version 3.1-3 (Kuznetsova et al., 2017). The latter package in turn used `lme4', Version 1.1-26 (Bates et al., 2015; Bates et al., 2021). Diagnostics regarding convergence and normality are provided in \protect\hyperlink{appendix-B-frequentist-analysis-diagnostics}{\underline{Appendix B}}.

\hypertarget{bayesian-analysis}{%
\subsubsection{Bayesian analysis}\label{bayesian-analysis}}

In addition to the frequentist analysis, a Bayesian analysis was performed for two purposes: firstly, to enhance the interpretation of the smaller effects (which were identified as low-powered), and secondly, to complement the estimates obtained in the frequentist analysis. The latter purpose was pertinent because the frequentist models presented convergence warnings---even though it must be noted that a previous study found that frequentist and Bayesian estimates were similar despite convergence warnings appearing in the frequentist analysis (Rodríguez-Ferreiro et al., 2020). Furthermore, the complementary analysis was pertinent because the frequentist models presented residual errors that deviated from normality---even though mixed-effects models are fairly robust to such a deviation (Knief \& Forstmeier, 2021; Schielzeth et al., 2020). Owing to these precedents, we expected to find broadly similar estimates in the two approaches.

Each frequentist model in the three studies has a Bayesian counterpart, with the exception of a sub-analysis performed in the first study (semantic priming), which included `visual similarity' as a predictor. Due to time constraints, this analysis did not include a Bayesian model. Furthermore, it must be noted that the Bayesian models in the semantic decision study did not produce valid results. Therefore, the estimates produced by these models are not shown in the main text, but they are instead in \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}.

Just as the frequentist estimates include 95\% confidence intervals (CI), the Bayesian estimates include 95\% credible intervals (CrI). These two types differ at a theoretical level, in that frequentist statistics are designed for the long run of testing, whereas Bayesian statistics are specific to each study (Schoot et al., 2021; Vasishth et al., 2018).

The random effects included in these models were largely the same as those included in the frequentist models. The only exception regarded the lexical decision models. In the frequentist models for lexical decision, the covariates did not carry random slopes due to the presence of convergence warnings (see Remedy 11 in Brauer \& Curtin, 2018), whereas in the Bayesian analysis, covariates did carry random slopes because the models converged.

This Bayesian analysis was not aimed at hypothesis testing. Instead, it was designed to complement and verify the estimates that had been obtained in the frequentist analysis. Accordingly, we estimated the posterior distribution of every effect, without calculating Bayes factors (for examples of this approach, see Milek et al., 2018; Rodríguez-Ferreiro et al., 2020; for comparisons between estimation and hypothesis testing, see Cumming, 2014; Kruschke \& Liddell, 2018; Rouder et al., 2018; Schmalz et al., 2021; Tendeiro \& Kiers, 2019, in press; van Ravenzwaaij \& Wagenmakers, 2021). In the estimation approach, the estimates are interpreted by considering the position of their credible intervals in relation to the predicted value of RT (\(z\)). That is, the closer an interval is to a value of 0 on the predicted RT (\(z\)), the smaller the effect of that predictor. For instance, an interval that is symmetrically centred on 0 indicates a very small effect, whereas---in comparison---an interval that does not include 0 at all indicates a far larger effect.

The R package `brms', Version 2.17.0, was used for this analysis (Bürkner, 2018; Bürkner et al., 2022).

\hypertarget{priors}{%
\paragraph{Priors}\label{priors}}

The priors were established by inspecting the effect sizes obtained in previous studies as well as the effect sizes obtained in our frequentist analyses of the present studies, reported below. These sources revealed highly-similar ranges. The previous studies that were considered were selected because they implemented experimental experimental paradigms and analytical procedures similar to those used in the current studies. The paradigms were lexical decision, semantic decision or semantic priming with a lexical decision task. The analytical procedures consisted of the z-scoring of the dependent and the independent variables. Two studies matched these characteristics: Lim et al. (2020) (see Table 5 therein) and Pexman and Yap (2018) (see Tables 6 and 7 therein). These studies and the frequentist analyses reported below yielded effect sizes smaller than ±0.30. The bounds of this range were determined by the results from Pexman and Yap (2018), who found a word-concreteness effect of \(\upbeta\) = 0.41 in the concrete-words analysis, and an effect of \(\upbeta\) = 0.20 in the abstract-words analysis. Since we did not separate abstract from concrete words, we averaged the former values, and set -0.30 as the lower bound, and 0.30 as the upper bound.

The sources used to determine the effect size range also revealed that some effects consistently presented a negative direction, whereas some other effects were consistently positive. We only incorporated the direction of effects into the priors of those variables that had produced large effects with consistent directions in previous studies and in our frequentist analyses. These variables were: word frequency---with a negative direction, as higher word frequency leads to shorter RTs (Brysbaert et al., 2018; Brysbaert et al., 2016; Lim et al., 2020; Mendes \& Undorf, 2021; Pexman \& Yap, 2018)---, number of letters and number of syllables---both with positive directions (Barton et al., 2014; Beyersmann et al., 2020; Pexman \& Yap, 2018)---, and orthographic Levenshtein distance---with a positive direction (Cerni et al., 2016; Dijkstra et al., 2019; Kim et al., 2018; Yarkoni et al., 2008). We did not incorporate information about the direction of the word concreteness effect as this effect can follow different directions in abstract and concrete words (Pexman \& Yap, 2018), and we analysed both sets of words together. Last, it is noteworthy that some previous studies have integrated effect direction in some priors (e.g., Stone et al., 2021), but most have not (e.g., Pregla et al., 2021; Rodríguez-Ferreiro et al., 2020; Stone et al., 2020).

\hypertarget{distributions-and-prior-predictive-checks}{%
\subparagraph{Distributions and prior predictive checks}\label{distributions-and-prior-predictive-checks}}

The priors we settled upon---shown in Figure \ref{fig:bayesian-priors}---comprised an `informative' prior (\(SD\) = 0.1), a `weakly-informative' one (\(SD\) = 0.2) and a `diffuse' one (\(SD\) = 0.3). These priors resembled others from previous psycholinguistic studies (Pregla et al., 2021; Stone et al., 2021; Stone et al., 2020). For instance, Stone et al. (2020) used the following priors: \(Normal\)(0, 0.1), \(Normal\)(0, 0.3) and \(Normal\)(0, 1). The range of standard deviations we used---i.e., 0.1, 0.2 and 0.3---was narrower than those of previous studies because our dependent variable and our predictors were z-scored, resulting in small estimates and small \(SD\)s (see Lim et al., 2020; Pexman \& Yap, 2018).

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/bayesian_priors/plots/bayesian_priors}

}

\caption{Priors used in the three studies. The green vertical rectangle shows the range of plausible effect sizes based on relevant previous studies and on our frequentist analyses.}\label{fig:bayesian-priors}
\end{figure}

The adequacy of each of these priors was assessed with prior predictive checks, in which we compared the observed data to data predicted by the priors (Schoot et al., 2021). In these checks, we also tested the adequacy of two model-wide distributions: the traditional Gaussian distribution (default in most analyses) and an exponentially modified Gaussian---dubbed `ex-Gaussian'---distribution (Matzke \& Wagenmakers, 2009). The ex-Gaussian distribution was considered because the residual errors of the frequentist models were not normally distributed (Lo \& Andrews, 2015), and because this distribution was found to be more appropriate than the Gaussian one in a related, previous study (see supplementary materials of Rodríguez-Ferreiro et al., 2020). The ex-Gaussian distribution had an identity link function, which preserves the interpretability of the coefficients, as opposed to a transformation applied directly to the dependent variable (Lo \& Andrews, 2015).

Prior predictive checks revealed that the priors were adequate, and that the ex-Gaussian distribution was more appropriate than the Gaussian one, converging with Rodríguez-Ferreiro et al. (2020) (see the corresponding plots in \protect\hyperlink{appendix-D-interaction-plots}{\underline{Appendix D}}). Therefore, the ex-Gaussian distribution was used in the final models.

\hypertarget{prior-sensitivity-analysis}{%
\subparagraph{Prior sensitivity analysis}\label{prior-sensitivity-analysis}}

The priors were used in the main analyses within separate models. In other words, in each model, all priors had the same degree of informativeness (for similar approaches, see Pregla et al., 2021; Rodríguez-Ferreiro et al., 2020; Stone et al., 2021; Stone et al., 2020). In this way, a prior sensitivity analysis was performed to acknowledge the likely influence of the priors on the posterior distributions---that is, on the results (Lee \& Wagenmakers, 2014; Schoot et al., 2021; Stone et al., 2020).

\hypertarget{posterior-distributions}{%
\paragraph{Posterior distributions}\label{posterior-distributions}}

As a last diagnostic, posterior predictive checks were performed to assess the fit between the observed data and new data predicted by the posterior (Schoot et al., 2021). These checks are available in \protect\hyperlink{appendix-C-Bayesian-analysis-diagnostics}{\underline{Appendix C}}.

\hypertarget{general-method-for-statistical-power-analyses}{%
\subsection{General method for statistical power analyses}\label{general-method-for-statistical-power-analyses}}

Power curves based on Monte Carlo simulations were performed for most of the effects of interest, using the R package `simr', Version 1.0.5 (Green \& MacLeod, 2016). Obtaining power curves for a range of effects in each study allows for a comprehensive assessment of the plausibility of the power estimated for each effect.

Monte Carlo simulations are performed by running the statistical model a large number of times, under slight, random variations of the dependent variable (Green \& MacLeod, 2016; for a comparable approach, see Loken \& Gelman, 2017). The power to detect each effect of interest is calculated by dividing the number of times that the effect is significant by the total number of simulations run. For instance, if an effect is significant on 85 simulations out of 100, the power for that effect is 85\% (Kumle et al., 2021). The sample sizes tested in the semantic priming study ranged from 50 to 800 participants, whereas those tested in the semantic decision and lexical decision studies ranged from 50 to 2,000 participants. These sample sizes were unequally spaced to limit the computational requirements. They comprised the following: 50, 100, 200, 300, 400, 500, 600, 700, 800, 1,200, 1,600 and 2,000 participants.\footnote{For the semantic priming study, the remaining sample sizes up to 2,000 participants have not finished running yet. Upon finishing, they will be reported in this manuscript.} The variance of the results decreases as more simulations are run. In each of our three studies, 200 simulations (as in Brysbaert \& Stevens, 2018) were run for each effect of interest and for each sample size under consideration. Thus, for a power curve examining the power for an effect across 12 sample sizes, 2,400 simulations were run. In each study, the item-level sample size---i.e., the number of words---was not modified. Thus, each of the power curves we present assume the same number of words that existed in each of our studies (these numbers are detailed in each study below). \emph{P} values were calculated using the Satterthwaite approximation for degrees of freedom, which is faster than Kenward-Roger but similarly accurate (Luke, 2017).

It is difficult to determine an effect size for each effect examined in a power analysis, as the amount and the scope of relevant research are usually finite and biased (Albers \& Lakens, 2018; Gelman \& Carlin, 2014; Kumle et al., 2021). Power analyses sometimes use the original effect sizes from previous studies (e.g., Pacini \& Barnard, 2021; Villalonga et al., 2021). In contrast, some authors have opted to reduce the previous effect sizes to account for factors that can influence the effect size of the planned study. First, publication bias and low-powered studies cause published effect sizes to be inflated (Brysbaert, 2019; Loken \& Gelman, 2017; Open Science Collaboration, 2015; Vasishth et al., 2018; Vasishth \& Gelman, 2021). Second, there might be differences between the studies used in the power analysis and the study to be conducted. Some of these differences could be foreseeable---for instance, if they are due to a limitation in the literature available for the power analysis---, whereas other differences might arise from unexpected circumstances arising during the project or from random variation (Barsalou, 2019). Reducing the effect size in the power analysis leads to an increase of the sample size of the planned study (Brysbaert \& Stevens, 2018; Green \& MacLeod, 2016; Hoenig \& Heisey, 2001). The reduced effect size---sometimes dubbed the smallest effect size of interest---is often set with a certain arbitrariness. For instance, Fleur et al. (2020) applied a reduction of 1/8 (i.e., 12.5\%), whereas Kumle et al. (2021) applied a 15\% reduction. In the present study, a reduction of 20\% was applied to every effect examined in the power analysis. By comparison with the power analyses reviewed in this paragraph, the present reduction will lead to a relatively-conservative estimate of required sample sizes. Yet, it is intrinsically difficult to determine how conservative a power analysis is, once we consider the insufficient power of most studies in psychology, and the resulting overestimation of effect sizes.

Both the primary analysis and the power analysis were performed in R (R Core Team, 2021). Version 4.0.2 was used for the frequentist analysis, Version 4.1.0 was used for the Bayesian analysis, and Version 4.1.2 was used for fast operations such as plotting. All the statistical and the power analyses were run on the High-End Computing facility at Lancaster University.\footnote{Information about this facility is available at \url{https://answers.lancaster.ac.uk/display/ISS/High+End+Computing+\%28HEC\%29+help}}

\hypertarget{study-1-semantic-priming}{%
\section{Study 1: Semantic priming}\label{study-1-semantic-priming}}

The core data set in this study was that of the Semantic Priming Project (Hutchison et al., 2013; also see Yap et al., 2017). Out of the tasks delivered in the experiment, we used the lexical decision one because it was most relevant to our forthcoming research. In the lexical decision task, participants judged whether strings of letters constituted real words (e.g., `building') or nonwords (e.g., `gop'). Crucially, in the experimental manipulation that characterises semantic priming, a prime word was presented before the target word in each trial. Since prime words facilitate the comprehension of target words, the participants' responses to the targets can be analysed as a function of the semantic relationship between primes and targets (Hoedemaker \& Gordon, 2014).

In some studies, the association between prime and target words has been examined in terms of related versus unrelated pairs (Pecher et al., 1998; Trumpp et al., 2013), and in terms of first- and second-order relationships (Hutchison et al., 2013). In contrast to these categorical associations, other studies have measured the association between the prime and the target words using language-based similarity estimates (Günther et al., 2016a, 2016b; Hutchison et al., 2008; Jones et al., 2006; Lam et al., 2015; Lund et al., 1995; Lund \& Burgess, 1996; Mandera et al., 2017; McDonald \& Brew, 2002; Padó \& Lapata, 2007; Petilli et al., 2021; Wingfield \& Connell, 2022). In one of these studies, Mandera et al. (2017) found that the latter computational measures outperformed human-based associations at explaining the priming effect.

Priming associations beyond the linguistic realm have also been examined, with early studies finding perceptual priming effects (Flores d'Arcais et al., 1985; Schreuder et al., 1984). Yet, the earliest findings were soon reframed by Pecher et al. (1998), who conducted a follow-up with an improved design, and observed the perceptual priming effect only when the word processing task was preceded by a visually-intensive task (Pecher et al., 1998). This moderating condition, replicated by Yee et al. (2012), is consistent with other conceptual-processing studies using a non-priming paradigm (Ostarek \& Huettig, 2017). However, a considerable number of studies have observed perceptual priming even in the absence of a preparatory perceptual task. A set of these studies used the Conceptual Modality Switch paradigm, in which the primes and the targets are presented in separate, consecutive trials (Bernabeu et al., 2017; Collins et al., 2011; Hald et al., 2011, 2013; Louwerse \& Connell, 2011; Lynott \& Connell, 2009; Pecher et al., 2003; Trumpp et al., 2013). The other set of studies, using the more standard priming intervals, are described below.

Lam et al. (2015) conducted a semantic priming experiment containing a lexical decision task. Participants were instructed to respond whether the prime word and the target word in each trial were both real words or pseudowords. The semantic-priming manipulation consisted of the following types of associations between the prime and the target words: (1) semantic association (e.g., bolt → screwdriver), (2) action association (e.g., housekey → screwdriver), (3) visual association (e.g., soldering iron → screwdriver), and (4) no association (e.g., charger → screwdriver). In addition, four conditions were present that consisted of SOAs of 500, 650, 800 and 1,400 ms. In the results, Lam et al.~firstly observed priming effects of the semantic-association type with all SOAs. Secondly, the authors observed motor-association priming effects with the SOAs of 500, 650 and 1,400 ms. Lastly, they observed visual-association priming effects only with the SOA of 1,400 ms. Overall, semantic-association priming---corresponding to language-based association---was more consistent than the priming based on visual and action associations. This greater influence of the language system converges with other studies on semantic priming (Lam et al., 2015; Pecher et al., 1998; Petilli et al., 2021) and with studies using other paradigms (Banks et al., 2021; Kiela \& Bottou, 2014; Louwerse et al., 2015).

Similarly, the results of Lam et al. (2015) regarding the time course of language-based and vision-based priming were consistent with a wealth of literature observing that perceptual systems, such as vision, are activated later than the language system (Barsalou et al., 2008; Connell \& Lynott, 2013; Louwerse \& Connell, 2011; Santos et al., 2011). For instance, studies using electroencephalography have found that perceptual priming effects emerged in the first 300 ms. Following the 300-ms stage, the perceptual priming increased in some studies (Amsel et al., 2014; Bernabeu et al., 2017), whereas other studies it stabilised (Kiefer et al., 2022), and in a third set of studies, the effect fluctuated (Amsel, 2011). Taken together, the most prevalent pattern is of a gradual accumulation of information throughout word processing (also see Hauk, 2016), which is consistent with the accummulation of information required for the integration of context in sentences (Hald et al., 2006). This progression invites two hypotheses regarding SOA in the current study: (1) that language-based information will be more prevalent than vision-based information in both the short and the long SOA, and (2) that vision-based information will be more prevalent in the long SOA than in the short one. Consistent with the first hypothesis, Petilli et al. (2021) observed that language-based information was more influential in both the short and the long SOA, within the data set of Hutchison et al. (2013). The second hypothesis, in contrast, is challenged by other findings. First, Hutchison (2003) concluded that the vision-based priming effect was negligible. Second, other studies have observed the effect only when the word processing task was preceded by a visually-intensive task (Pecher et al., 1998; Yee et al., 2012). Third, Petilli et al.~observed vision-based priming with the short SOA (150 ms) but not with the long one (1,200 ms).

The findings of Petilli et al. (2021) were based on a novel analysis of the data set of Hutchison et al. (2013). The strengths of Petilli et al.'s study centred on the simultaneous analysis of language- and vision-based similarity using predictors that were continuous (see Cohen, 1983; Günther et al., 2016a; Mandera et al., 2017) and not based on human ratings (cf. Hutchison et al., 2008, 2013; Lam et al., 2015; Pecher et al., 1998). The authors used such measures to pursue a comprehensive analysis that was not affected by the problem of circularity between the independent and the dependent variables. The circularity problem obtains even though the participants who contributed to the ratings---or `norms'---are always different from those who participate in the main experiment.

Petilli et al.~operationalised language-based similarity based on text-based co-occurrence, producing a continuous measure in contrast to the categorical factors used earlier. Next, Petilli et al.~created a visual-similarity measure by retrieving ImageNet images for each word, and training vector representations on those images using neural networks. Importantly, the authors compared the resulting visual-similarity measure to previous scores based on human ratings (Pecher et al., 1998), and found a comparable pattern. Using these materials, Petilli et al.~examined language-based and vision-based priming in two tasks---lexical decision and naming---and with both a short and a long SOA. In lexical decision, the largest effect observed by the authors was that of language-based priming with the short SOA (150 ms). The second largest effect was that of language-based priming with the long SOA (1,200 ms). Next, the weakest effect that was significant was that of vision-based priming with the short SOA. Last, there was no effect of vision-based priming with the long SOA. Petilli et al. (2021) explained the absence of vision-based priming with the long SOA in lexical decision by contending that visual activation had likely decayed before participants processed the target words (also see Yee et al., 2011), owing to the limited semantic processing required for lexical decision (also see Balota \& Lorch, 1986; Becker et al., 1997; Connell \& Lynott, 2013; de Wit \& Kinoshita, 2015; Joordens \& Becker, 1997; Ostarek \& Huettig, 2017). Therefore, the authors suggested that perceptual simulation does \emph{not} outlast language-based processing in lexical decision, in contrast to the longer latency found in other tasks (Barsalou et al., 2008; Louwerse \& Connell, 2011).

In the naming task of Petilli et al. (2021), the largest effect was that of language-based priming with the long SOA. The second largest effect was that of language-based priming with the short SOA. Last, there was no effect of vision-based priming with either SOA. This finding contrasted with Connell and Lynott (2014), who found facilitatory effects of visual strength in both lexical decision and naming. Petilli et al.~explained the lack of vision-based priming in the naming task by alluding to the lower semantic depth of this task---compared to lexical decision---, and the mixture of visual and auditory processing in the naming task (Connell \& Lynott, 2014).

In the present study, we revisited the interplay between linguistic and perceptual simulation by conceptually replicating Petilli et al. (2021). Specifically, we used the same primary data set (Hutchison et al., 2013), and a language-based similarity measure that was very similar to that used by Petilli et al. (2021; both our measure and theirs originated from Mandera et al., 2017). In contrast, in the domain of vision, the operationalisation of visual-strength difference in our study---based one variable from (Lynott et al., 2020)---was simpler than that of Petilli et al.'s visual similarity---which involved convolutional neural networks. As a counterpoint, Petilli et al.'s measure was superior in that it was independent from human ratings, thus precluding the problem of circularity between the independent and the dependent variables. At \protect\hyperlink{comparing-two-measures-of-vision-based-information}{\underline{the end of the Results section}}, we compare the performance of these two measures.

\hypertarget{methods-1}{%
\subsection{Methods}\label{methods-1}}

\hypertarget{effects-of-interest}{%
\subsubsection{Effects of interest}\label{effects-of-interest}}

\begin{itemize}
\item
  Z-scored vocabulary size {[}\texttt{z\_vocabulary\_size}; calculated from average of \texttt{vocaba}, \texttt{vocabb} and \texttt{vocabc} in Hutchison et al. (2013){]}. The test used by Hutchison et al. (2013) comprised a synonym test, an antonym test, and an analogy test, all three extracted from the Woodcock--Johnson III diagnostic reading battery (Woodcock et al., 2001). We operationalised the vocabulary measure as the mean score across the three tasks per participant.
\item
  Z-scored, recoded participant's gender {[}\texttt{z\_recoded\_participant\_gender}; calculated from \texttt{gender} in Hutchison et al. (2013){]}
\item
  Z-scored language-based similarity between prime and target words {[}\texttt{z\_cosine\_similarity}{]}. This measure was calculated using a semantic space from Mandera et al. (2017), which the authors found to be the second-best predictor (\(R\)\textsuperscript{2} = .465) of the semantic priming effect in the lexical decision task of Hutchison et al. (2013) (we could not use the best semantic space, \(R\)\textsuperscript{2} = .471, owing to computational limitations). The second-best semantic space (see first row in Table 5 of Mandera et al., 2017) was based on lemmas from a subtitle corpus, processed in a Continuous Bag Of Words model, and the space had 300 dimensions and a window size of 6.
\item
  Z-scored vision-based information in words {[}\texttt{z\_visual\_rating}; calculated from \texttt{Visual.mean} in Lynott et al. (2020){]}
\item
  Z-scored, recoded SOA {[}\texttt{z\_recoded\_interstimulus\_interval}; calculated from \texttt{isi} in Hutchison et al. (2013){]}
\end{itemize}

The final data set contained 496 participants, 5,943 prime-target pairs, and a total of 345,666 RTs. On average, there were 697 prime-target pairs per participant (\(SD\) = 33.34), and conversely, 58 participants per prime-target pair (\(SD\) = 4.25).

Figure \ref{fig:semanticpriming-correlations} shows the zero-order correlations among the predictors and the dependent variable.

\begin{figure}

{\centering \includegraphics[width=0.65\linewidth]{manuscript_files/figure-latex/semanticpriming-correlations-1}

}

\caption{Zero-order correlations in the semantic priming study.}\label{fig:semanticpriming-correlations}
\end{figure}

\hypertarget{covariates}{%
\subsubsection{Covariates}\label{covariates}}

The following covariates were included in the model to allow a rigorous analysis of the effects of interest.

\begin{itemize}
\item
  Lexical (see \protect\hyperlink{appendix-A-lexical-covariates}{\underline{Appendix A}}): z-scored word frequency and orthographic Levenshtein distance (Balota et al., 2007)
\item
  Semantic: z-scored word concreteness (Brysbaert et al., 2014), used as a covariate of visual rating.
\item
  Individual differences: z-scored attentional control (Hutchison et al., 2013). This covariate is related to vocabulary size (Ratcliff et al., 2010), and previous studies have pointed out the desirability of including these kinds of covariates in analyses (James et al., 2018; Pexman \& Yap, 2018). Attentional control was operationalised as the average score across three attention-demanding tasks: namely, operation span, Stroop, antisaccade.
\end{itemize}

\hypertarget{diagnostics-for-the-frequentist-model}{%
\subsubsection{Diagnostics for the frequentist model}\label{diagnostics-for-the-frequentist-model}}

The model presented convergence warnings. To avoid removing important random slopes, which could increase the Type I error (Brauer \& Curtin, 2018; Singmann \& Kellen, 2019), we examined the model after refitting it using seven optimization algorithms through the `allFit' function of the `lme4' package (Bates et al., 2021). The results showed that all optimizers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential (Bates et al., 2021) (see \protect\hyperlink{appendix-B-frequentist-analysis-diagnostics}{\underline{Appendix B}}).

The residual errors were not normally distributed, and attempts to mitigate this deviation proved unsuccessful (see \protect\hyperlink{appendix-B-frequentist-analysis-diagnostics}{\underline{Appendix B}}). However, this is not likely to have posed a major problem, as mixed-effects models are fairly robust to deviations from normality (Knief \& Forstmeier, 2021; Schielzeth et al., 2020).

The model did not present multicollinearity problems, all variance inflation factors (VIF) being smaller than 2 (Dormann et al., 2013; Harrison et al., 2018).

\hypertarget{diagnostics-for-the-bayesian-model}{%
\subsubsection{Diagnostics for the Bayesian model}\label{diagnostics-for-the-bayesian-model}}

Three Bayesian models were run that were respectively characterised by informative, weakly-informative and diffuse priors. In each model, 16 chains were used. In each chain, 1,500 warmup iterations were run, followed by 4,500 post-warmup iterations. Thus, a total of 72,000 post-warmup draws were produced over all the chains.

The maximum \(\widehat R\) value for the fixed effects across the three models was 1.00, suggesting that these parameters had converged (Schoot et al., 2021; Vehtari et al., 2021). In contrast, the maximum \(\widehat R\) value for the random effects was 1.13, exceeding the 1.01 threshold (Vehtari et al., 2021). Therefore, models with more iterations will be run, and once completed, they will be reported in this manuscript.

The posterior predictive checks were sound (see \protect\hyperlink{appendix-C-Bayesian-analysis-diagnostics}{\underline{Appendix C}}). Furthermore, in the prior sensitivity analysis, the results were virtually identical with the three priors that were considered (to recall the priors, see Figure \ref{fig:bayesian-priors} above; to view the results in detail, see \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}).

\hypertarget{semanticpriming-results}{%
\subsection{Results}\label{semanticpriming-results}}

Table \ref{tab:semanticpriming-frequentist-model} presents the results of the mixed-effects model.

\begin{table}[!h]

\caption{\label{tab:semanticpriming-frequentist-model}Frequentist model for the semantic priming study.}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lrrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{$\upbeta$} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$}\\
\midrule
(Intercept) & 0.00 & 0.00 & {}[0.00, 0.01] & 1.59 & .112\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Individual differences}}\\
\cellcolor{gray!6}{\hspace{1em}Attentional control} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.00, 0.00]} & \cellcolor{gray!6}{-0.56} & \cellcolor{gray!6}{.577}\\
\hspace{1em}Vocabulary size $^{\text{a}}$ & 0.00 & 0.00 & {}[0.00, 0.00] & 0.02 & .987\\
\hspace{1em}Gender $^{\text{a}}$ & 0.00 & 0.00 & {}[0.00, 0.00] & -0.03 & .979\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Target-word lexical covariates}}\\
\cellcolor{gray!6}{\hspace{1em}Word frequency} & \cellcolor{gray!6}{-0.16} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[-0.16, -0.15]} & \cellcolor{gray!6}{-49.40} & \cellcolor{gray!6}{<.001}\\
\cellcolor{gray!6}{\hspace{1em}Number of syllables} & \cellcolor{gray!6}{0.07} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.07, 0.08]} & \cellcolor{gray!6}{22.81} & \cellcolor{gray!6}{<.001}\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Prime-target semantic relationship}}\\
\cellcolor{gray!6}{\hspace{1em}Word-concreteness difference} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.01, 0.02]} & \cellcolor{gray!6}{3.48} & \cellcolor{gray!6}{.001}\\
\hspace{1em}Language-based similarity $^{\text{b}}$ & -0.08 & 0.00 & {}[-0.08, -0.07] & -22.44 & <.001\\
\hspace{1em}Visual-strength difference $^{\text{b}}$ & 0.01 & 0.00 & {}[0.01, 0.02] & 4.18 & <.001\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Task condition}}\\
\hspace{1em}Stimulus-onset asynchrony (SOA) $^{\text{b}}$ & 0.06 & 0.01 & {}[0.04, 0.07] & 7.47 & <.001\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Interactions}}\\
\cellcolor{gray!6}{\hspace{1em}\makecell[l]{Word-concreteness difference  $\times$ \\ \hspace{0.3cm} Vocabulary size}} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.00, 0.01]} & \cellcolor{gray!6}{1.31} & \cellcolor{gray!6}{.189}\\
\cellcolor{gray!6}{\hspace{1em}Word-concreteness difference  $\times$  SOA} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.00, 0.01]} & \cellcolor{gray!6}{2.57} & \cellcolor{gray!6}{.010}\\
\cellcolor{gray!6}{\hspace{1em}Word-concreteness difference  $\times$  Gender} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[-0.01, 0.00]} & \cellcolor{gray!6}{-0.97} & \cellcolor{gray!6}{.332}\\
\cellcolor{gray!6}{\hspace{1em}\makecell[l]{Language-based similarity  $\times$ \\ \hspace{0.3cm} Attentional control}} & \cellcolor{gray!6}{-0.01} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[-0.01, 0.00]} & \cellcolor{gray!6}{-2.46} & \cellcolor{gray!6}{.014}\\
\cellcolor{gray!6}{\hspace{1em}\makecell[l]{Visual-strength difference  $\times$ \\ \hspace{0.3cm} Attentional control}} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.00, 0.00]} & \cellcolor{gray!6}{0.24} & \cellcolor{gray!6}{.810}\\
\hspace{1em}\makecell[l]{Language-based similarity  $\times$ \\ \hspace{0.3cm} Vocabulary size} & -0.01 & 0.00 & {}[-0.01, 0.00] & -2.34 & .020\\
\hspace{1em}\makecell[l]{Visual-strength difference  $\times$ \\ \hspace{0.3cm} Vocabulary size} & 0.00 & 0.00 & {}[-0.01, 0.00] & -1.37 & .172\\
\hspace{1em}Language-based similarity  $\times$  Gender & 0.00 & 0.00 & {}[-0.01, 0.00] & -0.79 & .433\\
\hspace{1em}Visual-strength difference  $\times$  Gender & 0.00 & 0.00 & {}[0.00, 0.01] & 1.46 & .144\\
\hspace{1em}Language-based similarity  $\times$  SOA $^{\text{b}}$ & 0.01 & 0.00 & {}[0.00, 0.01] & 3.22 & .001\\
\hspace{1em}Visual-strength difference  $\times$  SOA $^{\text{b}}$ & 0.00 & 0.00 & {}[-0.01, 0.00] & -2.25 & .025\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \textit{\linebreak} 
\item \textit{Note}. $\upbeta$ = Estimate based on z-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CI = confidence interval. Shaded rows contain covariates. Some interactions are \linebreak \phantom{.}split over two lines, with the second line indented. \linebreak \linebreak \phantom{.}$^{\text{a}}$ By-word random slopes were included for this effect. \linebreak \phantom{.}$^{\text{b}}$ By-participant random slopes were included for this effect.
\end{tablenotes}
\end{threeparttable}
\end{table}

The fixed effects of this model explained 4.22\% of the variance, and the random effects explained 11.01\% (Nakagawa et al., 2017). It is to be expected that random effects explain more variance, as they involve a far larger number of coefficients for each effect. For instance, the by-word random slopes for a single individual-level variable (e.g., vocabulary size) involve as many coefficients as the number of words. Similarly, the by-participant random slopes for a single word-level variable (e.g., language-based similarity) involve as many coefficients as the number of participants. In contrast, a fixed effect involves 1 coefficient only.

Figure \ref{fig:semanticpriming-interactions-with-vocabulary-size}-a shows the interaction between vocabulary size and language-based similarity, whereby higher-vocabulary participants presented a greater benefit from the language-based similarity between prime and target words. That is, the greater the similarity between prime and target words, the greater the advantage for participants with higher vocabularies. This interaction replicates the results of Yap et al. (2017), who analysed the same data set but using a categorical measure of similarity instead. Indeed, this replication is noteworthy as it holds in spite of some methodological differences between the studies. First, Yap et al. (2017) operationalised the priming effect as a categorical difference between related and unrelated prime-target pairs. In contrast, the present study applied a continuous measure of relatedness---i.e., cosine similarity---, which is more precise and may thus afford more statistical power (Mandera et al., 2017; Petilli et al., 2021). Second, the analysis conducted by Yap et al. (2017) was correlational, whereas the present analysis used mixed-effects models that included several covariates to measure the effects of interest as rigorously as possible.

Figure \ref{fig:semanticpriming-interactions-with-vocabulary-size}-b presents the interaction between vocabulary size and vision-based similarity. Albeit a non-significant interaction, it is noteworthy that the effect of vision-based information is larger in lower-vocabulary participants.

\begin{figure}

{\centering \includegraphics[width=0.85\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-vocabulary-size}

}

\caption{Interactions of vocabulary size with language- and vision-based similarity. Vocabulary size is constrained to deciles, whereas in the statistical analysis it contained more values within the current range. \emph{n} = number of participants contained between decile values.}\label{fig:semanticpriming-interactions-with-vocabulary-size}
\end{figure}

Methodologically, the interaction between vocabulary size and language-based similarity underscores the consistency that exists between human ratings and computational approximations to meaning (e.g., Charbonnier \& Wartena, 2019, 2020; Günther et al., 2016b; Louwerse et al., 2015; Mandera et al., 2017; Petilli et al., 2021; Solovyev, 2021; Wingfield \& Connell, 2022). In contrast to this consistency, some studies have found human ratings to have more explanatory power than computational measures (De Deyne et al., 2016, 2019; Gagné et al., 2016; Schmidtke et al., 2018), and other research has suggested that some computational measures are not intrinsically contentful, but arise from a missing-data problem (Snefjella \& Blank, 2020). In sum, this evidence suggests that computational measures are artificial, and yet valid for the study of cognition.

Figure \ref{fig:semanticpriming-interactions-with-SOA} shows that the effects of language-based similarity and visual strength were both larger with the short SOA. Yet there is a notable difference: whereas the effect of language-based similarity is present with both SOAs (i.e., 150 ms and 1,200 ms), the effect of visual strength is almost reserved to the the long SOA. This finding replicates Petilli et al. (2021), and stands in contrast to previous findings regarding the slower pace of the visual system in semantic priming (Lam et al., 2015) and in other paradigms (Connell \& Lynott, 2013; Louwerse \& Connell, 2011). \textbf{conclude}\_\_\_\_\_\_\_\_\_\_\_\_\_

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-SOA}

}

\caption{Interactions of SOA with language-based similarity and visual strength. SOA was analysed using z-scores, but for clarity, the variable is shown in its simpler form here.}\label{fig:semanticpriming-interactions-with-SOA}
\end{figure}

\hypertarget{the-importance-of-outliers}{%
\paragraph{The importance of outliers}\label{the-importance-of-outliers}}

The interaction in Figure \ref{fig:semanticpriming-interactions-with-vocabulary-size} is patent in all deciles of vocabulary size but most notably in the participants who lie more than 1 standard deviation away from the mean. Outliers in individual differences have played important roles in other areas of cognition as well, such as in the domains of aphantasia and hyperphantasia---traits characterised, respectively, by a diminished and an extraordinary ability to mentally visualise objects (Milton et al., 2021; Zeman et al., 2020). Furthermore, if we consider the difficulty of detecting effects involving individual differences (Diaz et al., 2021; Hedge et al., 2018; Rodríguez-Ferreiro et al., 2020), and the limited representativeness of most participant samples (Henrich et al., 2010), it seems recommendable to examine more varied samples in future studies, where possible.

\hypertarget{visualising-the-estimates}{%
\subsubsection{Visualising the estimates}\label{visualising-the-estimates}}

Figure \ref{fig:semanticpriming-frequentist-bayesian-plot-informativepriors-exgaussian} presents the posterior distribution of each effect, based on the informative prior model (for the models with the other priors, see \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}). The frequentist estimates are also shown to facilitate the comparison with them.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_bayesian_plots/plots/semanticpriming_frequentist_bayesian_plot_informativepriors_exgaussian}

}

\caption{Estimates from the frequentist analysis (in red) and from the Bayesian analysis (in blue) for the semantic priming study. The frequentist means (represented by points) are flanked by 95\% confidence intervals. The Bayesian means (represented by vertical lines) are flanked by 95\% credible intervals, in light blue (in some cases, the interval is covered up by the bar of the mean).}\label{fig:semanticpriming-frequentist-bayesian-plot-informativepriors-exgaussian}
\end{figure}

\hypertarget{comparing-two-measures-of-vision-based-information}{%
\subsubsection{Comparing two measures of vision-based information}\label{comparing-two-measures-of-vision-based-information}}

Next, we reflected on the adequacy of visual-strength difference as a measurement instrument, as it had never been used before to operationalise the semantic priming effect. On the one hand, its effect on RT was negative, as we would expect. However, we were concerned about the low correlation between this variable and language-based similarity (\(r\) = 0.01). This concern was especially motivated by the correlation that Petilli et al. (2021) had found between their `vision-based similarity' measure and language-based similarity, which reached \(r\) = .50. Based on this information, we set out to run a model with the aim of comparing the performance of our measures of vision-based information.

We created a subset of our data set in which we ensured that all the trials contained data from all the relevant variables---i.e., from all the existing variables and from the newly-added visual similarity from Petilli et al.~This subsetting resulted in the loss of 83\% of trials, owing to the strict selection criteria applied by Petilli et al.~in the creation of the visual-similarity measure (e.g., both the target and the prime word had to be associated to at least 100 pictures in ImageNet). As a result, our data set in this analysis contained 496 participants, 1,091 prime-target pairs, and a total of 254,140 RTs. On average, there were 128 prime-target pairs per participant (\(SD\) = 10.37), and conversely, 58 participants per prime-target pair (\(SD\) = 4.90).

Figure \ref{fig:semanticpriming-with-visualsimilarity-correlations} shows the zero-order correlations among the predictors and the dependent variable.

\begin{figure}

{\centering \includegraphics[width=0.73\linewidth]{manuscript_files/figure-latex/semanticpriming-with-visualsimilarity-correlations-1}

}

\caption{Zero-order correlations in the semantic priming data set that included visual similarity.}\label{fig:semanticpriming-with-visualsimilarity-correlations}
\end{figure}

\hypertarget{diagnostics-for-the-frequentist-model-1}{%
\subsubsection{Diagnostics for the frequentist model}\label{diagnostics-for-the-frequentist-model-1}}

The model presented convergence warnings. To avoid removing important random slopes, which could increase the Type I error (Brauer \& Curtin, 2018; Singmann \& Kellen, 2019), we examined the model after refitting it using seven optimization algorithms through the `allFit' function of the `lme4' package (Bates et al., 2021). The results showed that all optimizers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential {[}Bates et al. (2021); see \protect\hyperlink{appendix-B-frequentist-analysis-diagnostics}{\underline{Appendix B}}{]}.

The residual errors were not normally distributed, and attempts to mitigate this deviation proved unsuccessful (see \protect\hyperlink{appendix-B-frequentist-analysis-diagnostics}{\underline{Appendix B}}). However, this is not likely to have posed a major problem, as mixed-effects models are fairly robust to deviations from normality (Knief \& Forstmeier, 2021; Schielzeth et al., 2020).

The model did not present multicollinearity problems, all VIFs being smaller than 2 (Dormann et al., 2013; Harrison et al., 2018).

Due to time constraints, this analysis did not include a Bayesian model.

\hypertarget{results}{%
\paragraph{Results}\label{results}}

Table \ref{tab:semanticpriming-with-visualsimilarity-frequentist-model} presents the results of the mixed-effects model. Due to space, the covariates are shown in Table \ref{tab:semanticpriming-with-visualsimilarity-frequentist-model-covariates}.

\begin{table}[!h]

\caption{\label{tab:semanticpriming-with-visualsimilarity-frequentist-model}Effects of interest in the semantic priming model that included visual similarity.}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lrrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{$\upbeta$} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$}\\
\midrule
(Intercept) & 0.01 & 0.01 & {}[-0.01, 0.02] & 0.90 & .370\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Individual differences}}\\
\hspace{1em}Vocabulary size $^{\text{a}}$ & 0.00 & 0.00 & {}[-0.01, 0.01] & 0.21 & .834\\
\hspace{1em}Gender $^{\text{a}}$ & 0.00 & 0.00 & {}[-0.01, 0.01] & -0.05 & .962\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Prime-target semantic relationship}}\\
\hspace{1em}Language-based similarity $^{\text{b}}$ & -0.07 & 0.01 & {}[-0.09, -0.06] & -8.33 & <.001\\
\hspace{1em}Visual-strength difference $^{\text{b}}$ & 0.03 & 0.01 & {}[0.01, 0.04] & 3.04 & .002\\
\hspace{1em}Vision-based similarity $^{\text{b}}$ & -0.02 & 0.01 & {}[-0.04, -0.01] & -2.55 & .011\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Task condition}}\\
\hspace{1em}Stimulus-onset asynchrony (SOA) $^{\text{b}}$ & 0.06 & 0.01 & {}[0.04, 0.08] & 6.80 & <.001\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Interactions}}\\
\hspace{1em}\makecell[l]{Language-based similarity  $\times$ \\ \hspace{0.3cm} Vocabulary size} & -0.01 & 0.01 & {}[-0.02, 0.01] & -0.96 & .339\\
\hspace{1em}\makecell[l]{Visual-strength difference  $\times$ \\ \hspace{0.3cm} Vocabulary size} & -0.01 & 0.01 & {}[-0.02, 0.01] & -1.02 & .309\\
\hspace{1em}\makecell[l]{Vision-based similarity  $\times$ \\ \hspace{0.3cm} Vocabulary size} & 0.00 & 0.01 & {}[-0.01, 0.01] & -0.01 & .991\\
\hspace{1em}Language-based similarity  $\times$  Gender & 0.00 & 0.01 & {}[-0.02, 0.01] & -0.75 & .456\\
\hspace{1em}Visual-strength difference  $\times$  Gender & -0.01 & 0.01 & {}[-0.02, 0.01] & -1.05 & .294\\
\hspace{1em}Vision-based similarity  $\times$  Gender & 0.00 & 0.01 & {}[-0.01, 0.01] & 0.39 & .696\\
\hspace{1em}Language-based similarity  $\times$  SOA $^{\text{b}}$ & 0.00 & 0.00 & {}[0.00, 0.01] & 0.87 & .382\\
\hspace{1em}Visual-strength difference  $\times$  SOA $^{\text{b}}$ & -0.01 & 0.00 & {}[-0.02, 0.00] & -2.60 & .010\\
\hspace{1em}Vision-based similarity  $\times$  SOA $^{\text{b}}$ & 0.01 & 0.00 & {}[0.00, 0.01] & 1.28 & .201\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \textit{\linebreak} 
\item \textit{Note}. $\upbeta$ = Estimate based on z-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CI = confidence interval. Covariates shown in next table due to space. Some  \linebreak \phantom{.}interactions are split over two lines, with the second line indented. \linebreak \linebreak \phantom{.}$^{\text{a}}$ By-word random slopes were included for this effect. \linebreak \phantom{.}$^{\text{b}}$ By-participant random slopes were included for this effect.
\end{tablenotes}
\end{threeparttable}
\end{table}

\begin{table}[!h]

\caption{\label{tab:semanticpriming-with-visualsimilarity-frequentist-model-covariates}Covariates in the semantic priming model that included visual similarity.}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lrrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{$\upbeta$} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$}\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Individual-differences covariate}}\\
\hspace{1em}Attentional control & 0.00 & 0.00 & {}[-0.01, 0.00] & -1.06 & .288\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Target-word lexical covariates}}\\
\hspace{1em}Word frequency & -0.15 & 0.01 & {}[-0.17, -0.14] & -21.97 & <.001\\
\hspace{1em}Number of syllables & 0.02 & 0.01 & {}[0.01, 0.04] & 3.54 & <.001\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Prime-target semantic covariate}}\\
\hspace{1em}Word-concreteness difference & 0.02 & 0.01 & {}[0.01, 0.04] & 2.73 & .006\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Covariate interactions}}\\
\hspace{1em}\makecell[l]{Word-concreteness difference  $\times$ \\ \hspace{0.3cm} Vocabulary size} & -0.01 & 0.00 & {}[-0.01, 0.00] & -1.15 & .252\\
\hspace{1em}Word-concreteness difference  $\times$  SOA & 0.01 & 0.00 & {}[0.01, 0.02] & 5.64 & <.001\\
\hspace{1em}Word-concreteness difference  $\times$  Gender & 0.01 & 0.00 & {}[0.00, 0.01] & 1.34 & .179\\
\hspace{1em}\makecell[l]{Language-based similarity  $\times$ \\ \hspace{0.3cm} Attentional control} & 0.00 & 0.00 & {}[-0.01, 0.01] & -0.91 & .362\\
\hspace{1em}\makecell[l]{Visual-strength difference  $\times$ \\ \hspace{0.3cm} Attentional control} & 0.00 & 0.00 & {}[-0.01, 0.01] & 0.71 & .477\\
\hspace{1em}\makecell[l]{Vision-based similarity  $\times$ \\ \hspace{0.3cm} Attentional control} & 0.00 & 0.00 & {}[-0.01, 0.01] & 0.80 & .423\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \textit{\linebreak} 
\item \textit{Note}. $\upbeta$ = Estimate based on z-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CI = confidence interval. Some interactions are split over two lines, with the \linebreak \phantom{.}second line indented. \linebreak
\end{tablenotes}
\end{threeparttable}
\end{table}

The fixed effects of this model explained 3.53\% of the variance, and the random effects explained 18.47\% {[}Nakagawa et al. (2017); for background on why random effects explain more variance, see \protect\hyperlink{semanticpriming-results}{Results in Study 1}{]}.

Figure \ref{fig:semanticpriming-with-visualsimilarity-confidence-intervals-plot} presents the means and 95\% confidence intervals for the effects of interest.

\begin{figure}

{\centering \includegraphics[width=0.89\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/analysis_with_visualsimilarity/plots/semanticpriming_with_visualsimilarity_confidence_intervals_plot}

}

\caption{Means and 95\% confidence intervals for the effects of interest in the semantic priming model that included visual similarity.}\label{fig:semanticpriming-with-visualsimilarity-confidence-intervals-plot}
\end{figure}

The results revealed that visual-strength difference had a significantly larger effect. This difference was not due to an excessive collinearity between these measures (\(r\) = -0.04). Also importantly, both measures appeared to be valid based on their correlations with language-based similarity and with word concreteness.

\hypertarget{statistical-power-analysis}{%
\subsubsection{Statistical power analysis}\label{statistical-power-analysis}}

Power curves were performed for most effects of interest in the main model (no power analysis was performed for the model that included visual similarity). Figures \ref{fig:semanticpriming-powercurve-plots-1-2-3} and \ref{fig:semanticpriming-powercurve-plots-4-5-6-7-8-9} show the estimated power for the main effects and the interactions, respectively.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/power_analysis/plots/semanticpriming_powercurve_plots_1_2_3}

}

\caption{Power curves for some main effects in the semantic priming study.}\label{fig:semanticpriming-powercurve-plots-1-2-3}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=0.9\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/power_analysis/plots/semanticpriming_powercurve_plots_4_5_6_7_8_9}

}

\caption{Power curves for some interactions in the semantic priming study.}\label{fig:semanticpriming-powercurve-plots-4-5-6-7-8-9}
\end{figure}

\_\_\_\_\_\_\_ interpret \_\_\_\_\_\_\_\_\_\_\_\_

\hypertarget{discussion}{%
\subsection{Discussion}\label{discussion}}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\clearpage

\hypertarget{study-2-semantic-decision}{%
\section{Study 2: Semantic decision}\label{study-2-semantic-decision}}

The semantic decision task probes into the role of concreteness in conceptual processing. Specifically, this task requires participants to classify words as abstract or concrete. Researchers then analyse whether the responses can be explained by the sensory experientiality of the referents---that is, the degree to which they can be experienced through our senses---and by other variables, such as word frequency. The core data set in this study was that of the Calgary Semantic Decision Project (Pexman et al., 2017; Pexman \& Yap, 2018). The experimental task is semantic decision, in which participants judge whether words are relatively concrete (e.g., `building') or abstract (e.g., `thought').

Research has found that the processing of relatively concrete words relies considerably on sensorimotor information (Hultén et al., 2021; Kousta et al., 2011; Vigliocco et al., 2014). In contrast, the processing of relatively abstract words seems to draw more heavily on information from language (Barca et al., 2020; Duñabeitia et al., 2009; Snefjella \& Blank, 2020), emotion (Kousta et al., 2011; Ponari et al., 2020; Ponari, Norbury, Rotaru, et al., 2018; Ponari, Norbury, \& Vigliocco, 2018; Vigliocco et al., 2014) and sociality (Borghi et al., 2019; Diveica et al., 2022).

\hypertarget{word-co-occurrence}{%
\subsection{Word co-occurrence}\label{word-co-occurrence}}

Wingfield and Connell (2022) reanalysed the data from Pexman et al. (2017) using language-based variables that are more related to the language system than to the visual system. The authors found that the variables that best explained RTs were word co-occurrence measures. Specifically, the measures corresponded to the distance from each stimulus word to two labels that were central to the task, namely, the words `abstract' and `concrete'. Wingfield and Connell studied these distance measures in various forms, and found that cosine and correlation distance yielded the best results. We used the correlation distance following the advice of (Kiela \& Bottou, 2014). Furthermore, we sought to avoid the collinearity between these variables (\(r\) = .99) and to facilitate the analysis of interactions with other variables. For this purpose, we created a difference score by subtracting distance to `abstract' from the distance to `concrete'. The resulting variable was practically equivalent to the distance to `abstract', as attested by its large correlation with word concreteness (\(r\) = 0.02). Last, it should be noted that this difference score may not be affected by the reduced sensitivity of other ones (see Rodríguez-Ferreiro et al., 2020), as this difference score did not entail an aggregation of data points over any third variables.

\hypertarget{methods-2}{%
\subsection{Methods}\label{methods-2}}

\hypertarget{effects-of-interest-1}{%
\subsubsection{Effects of interest}\label{effects-of-interest-1}}

\begin{itemize}
\item
  Z-scored vocabulary size {[}\texttt{z\_vocabulary\_size}; calculated from \texttt{NAART} in Pexman et al. (2017){]}. In the test used by Pexman and Yap (2018), participants were presented with 35 rare words, whose pronunciations are not regular (e.g., \emph{gaoled}, \emph{ennui}), and they were asked to read the words aloud. When they pronounced a word correctly, it was inferred that they knew the word. This test was based on NAART35, a short version of the North American Adult Reading Test (Uttl, 2002).
\item
  Z-scored, recoded participant's gender {[}\texttt{z\_recoded\_participant\_gender}; calculated from \texttt{Gender} in Pexman and Yap (2018){]}
\item
  Z-scored distance to word `abstract': a distributional semantic distance measure obtained from Wingfield and Connell (2022) that reflects the correlation distance between each stimulus word and the word `abstract'.\footnote{Specifically, this measure is a difference score that merges both the distance to the word `abstract' and the distance to the word `concrete'. We drew on both variables because Wingfield and Connell (2022) found them to be similarly important. Yet, we had to create a difference score because these variables were highly correlated (\(r\) = .99), we created a difference score by subtracting the distance to `abstract' from the distance to `concrete'. The resulting difference score was practically equivalent to the distance to the word `abstract', as attested by its correlation with word concreteness (see Figure \ref{fig:semanticdecision-correlations}). Our difference score in practice The variable \texttt{Conditional\_probability\_BNC\_r5\_correlation\_abstract\_distance} was subtracted from \texttt{Conditional\_probability\_BNC\_r5\_correlation\_concrete\_distance}.}
\item
  Z-scored vision-based information in words {[}\texttt{z\_visual\_rating}; calculated from \texttt{Visual.mean} in Lynott et al. (2020){]}
\end{itemize}

The final data set contained 306 participants, 8,927 words, and a total of 246,432 RTs. On average, there were 755 words per participant (\(SD\) = 42.05), and conversely, 26 participants per word (\(SD\) = 4.80).

Figure \ref{fig:semanticdecision-correlations} shows the zero-order correlations among the predictors among the predictors and the dependent variable.

\begin{figure}

{\centering \includegraphics[width=0.57\linewidth]{manuscript_files/figure-latex/semanticdecision-correlations-1}

}

\caption{Zero-order correlations in the semantic decision study.}\label{fig:semanticdecision-correlations}
\end{figure}

\hypertarget{covariates-1}{%
\subsubsection{Covariates}\label{covariates-1}}

The following covariates were included in the model to allow a rigorous analysis of the effects of interest.

\begin{itemize}
\item
  Lexical (see \protect\hyperlink{appendix-A-lexical-covariates}{\underline{Appendix A}}): z-scored word frequency and orthographic Levenshtein distance (Balota et al., 2007)
\item
  Semantic: z-scored word concreteness (Brysbaert et al., 2014). This variable is used as a covariate of visual strength, and it is especially fundamental in the semantic decision task, in which participants judge whether words are concrete or abstract (for a more general consideration of concreteness, see Bottini et al., 2021). Indeed, owing to the instructions of the task, word concreteness is likely to be more relevant to the participants' task than our effects of interest.
\item
  Individual differences: z-scored information uptake (Pexman \& Yap, 2018). This covariate is related to vocabulary size (Ratcliff et al., 2010; also see James et al., 2018; Pexman \& Yap, 2018).
\end{itemize}

\hypertarget{diagnostics-for-the-frequentist-model-2}{%
\subsubsection{Diagnostics for the frequentist model}\label{diagnostics-for-the-frequentist-model-2}}

The model presented convergence warnings. To avoid removing important random slopes, which could increase the Type I error (Brauer \& Curtin, 2018; Singmann \& Kellen, 2019), we examined the model after refitting it using seven optimization algorithms through the `allFit' function of the `lme4' package (Bates et al., 2021). The results showed that all optimizers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential {[}Bates et al. (2021); see \protect\hyperlink{appendix-B-frequentist-analysis-diagnostics}{\underline{Appendix B}}{]}.

The residual errors were not normally distributed, and attempts to mitigate this deviation proved unsuccessful (see \protect\hyperlink{appendix-B-frequentist-analysis-diagnostics}{\underline{Appendix B}}). However, this is not likely to have posed a major problem, as mixed-effects models are fairly robust to deviations from normality (Knief \& Forstmeier, 2021; Schielzeth et al., 2020).

The model did not present multicollinearity problems, all VIFs being smaller than 2 (Dormann et al., 2013; Harrison et al., 2018).

\hypertarget{diagnostics-for-the-bayesian-model-1}{%
\subsubsection{Diagnostics for the Bayesian model}\label{diagnostics-for-the-bayesian-model-1}}

Three Bayesian models were run that were respectively characterised by informative, weakly-informative and diffuse priors. In each model, 16 chains were used. In each chain, 2,000 warmup iterations were run, followed by 6,000 post-warmup iterations. Thus, a total of 96,000 post-warmup draws were produced over all the chains.

The maximum \(\widehat R\) value for the fixed effects across the three models was 1.42, far exceeding the 1.01 threshold (Vehtari et al., 2021; also see Schoot et al., 2021). Similarly, the maximum \(\widehat R\) value for the random effects was 1.31. Furthermore, the posterior predictive checks revealed major divergences between the observed data and the predicted outcome (see \protect\hyperlink{appendix-C-Bayesian-analysis-diagnostics}{\underline{Appendix C}}). Since the results were not valid, they are not shown in the main text but instead in \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}.

\hypertarget{results-1}{%
\subsection{Results}\label{results-1}}

Table \ref{tab:semanticdecision-frequentist-model} presents the results of the mixed-effects model.

\begin{table}[!h]

\caption{\label{tab:semanticdecision-frequentist-model}Frequentist model for the semantic decision study.}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lrrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{$\upbeta$} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$}\\
\midrule
(Intercept) & 0.05 & 0.00 & {}[0.04, 0.06] & 11.87 & <.001\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Individual differences}}\\
\cellcolor{gray!6}{\hspace{1em}Information uptake} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.00, 0.00]} & \cellcolor{gray!6}{0.20} & \cellcolor{gray!6}{.844}\\
\hspace{1em}Vocabulary size $^{\text{a}}$ & 0.00 & 0.00 & {}[-0.01, 0.00] & -1.42 & .155\\
\hspace{1em}Gender $^{\text{a}}$ & 0.00 & 0.00 & {}[0.00, 0.00] & -0.47 & .636\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Lexical covariates}}\\
\cellcolor{gray!6}{\hspace{1em}Word frequency} & \cellcolor{gray!6}{-0.12} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[-0.13, -0.12]} & \cellcolor{gray!6}{-28.63} & \cellcolor{gray!6}{<.001}\\
\cellcolor{gray!6}{\hspace{1em}Orthographic Levenshtein distance} & \cellcolor{gray!6}{-0.01} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[-0.02, 0.00]} & \cellcolor{gray!6}{-3.05} & \cellcolor{gray!6}{.002}\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Semantic variables}}\\
\cellcolor{gray!6}{\hspace{1em}Word concreteness} & \cellcolor{gray!6}{-0.13} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[-0.14, -0.11]} & \cellcolor{gray!6}{-21.39} & \cellcolor{gray!6}{<.001}\\
\hspace{1em}Distance to word 'abstract' $^{\text{b}}$ & -0.03 & 0.01 & {}[-0.04, -0.02] & -4.48 & <.001\\
\hspace{1em}Visual strength $^{\text{b}}$ & -0.02 & 0.01 & {}[-0.03, -0.01] & -2.91 & .004\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Interactions}}\\
\cellcolor{gray!6}{\hspace{1em}Word concreteness  $\times$  Gender} & \cellcolor{gray!6}{-0.01} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[-0.02, 0.00]} & \cellcolor{gray!6}{-3.50} & \cellcolor{gray!6}{<.001}\\
\cellcolor{gray!6}{\hspace{1em}Visual strength  $\times$  Information uptake} & \cellcolor{gray!6}{0.02} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[0.01, 0.03]} & \cellcolor{gray!6}{3.05} & \cellcolor{gray!6}{.003}\\
\hspace{1em}\makecell[l]{Distance to word 'abstract'  $\times$ \\ \hspace{0.3cm} Vocabulary size} & 0.01 & 0.01 & {}[0.00, 0.02] & 1.66 & .098\\
\hspace{1em}Visual strength  $\times$  Vocabulary size & 0.01 & 0.01 & {}[0.00, 0.02] & 2.03 & .043\\
\hspace{1em}Distance to word 'abstract'  $\times$  Gender & 0.00 & 0.00 & {}[-0.01, 0.01] & 0.86 & .393\\
\hspace{1em}Visual strength  $\times$  Gender & 0.00 & 0.00 & {}[-0.01, 0.01] & -0.08 & .940\\
\hspace{1em}Word concreteness  $\times$  Vocabulary size & -0.02 & 0.00 & {}[-0.03, -0.02] & -7.66 & <.001\\
\hspace{1em}\makecell[l]{Information uptake  $\times$ \\ \hspace{0.3cm} Distance to word 'abstract'} & 0.01 & 0.01 & {}[0.00, 0.02] & 1.48 & .141\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \textit{\linebreak} 
\item \textit{Note}. $\upbeta$ = Estimate based on z-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CI = confidence interval. Shaded rows contain covariates. Some interactions are \linebreak \phantom{.}split over two lines, with the second line indented. \linebreak \linebreak \phantom{.}$^{\text{a}}$ By-word random slopes were included for this effect. \linebreak \phantom{.}$^{\text{b}}$ By-participant random slopes were included for this effect.
\end{tablenotes}
\end{threeparttable}
\end{table}

The fixed effects of this model explained 4.11\% of the variance, and the random effects explained 17.48\% (Nakagawa et al., 2017).

Figures \ref{fig:semanticdecision-interactions-with-vocabulary-size}-a and \ref{fig:semanticdecision-interactions-with-vocabulary-size}-b show that lower-vocabulary participants benefited more strongly than higher-vocabulary participants from both language- and vision-based similarity. In contrast, Figure \ref{fig:semanticdecision-interactions-with-vocabulary-size}-c shows that higher-vocabulary participants benefitted more strongly from word concreteness. Since the variable that is most relevant to the semantic decision task is word concreteness, the present interactions may suggest that higher-vocabulary participants were better able to focus on the most relevant information, whereas lower-vocabulary participants were sensitive to a greater breadth of information (Lim et al., 2020; Pexman \& Yap, 2018; Yap et al., 2012, 2017).

\begin{figure}

{\centering \includegraphics[width=1\linewidth,height=0.95\textheight]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/plots/semanticdecision-interactions-with-vocabulary-size}

}

\caption{Interactions of vocabulary size with (a) language-based information, (b) visual strength and (c) word concreteness. Vocabulary size is constrained to deciles, whereas in the statistical analysis it contained more values within the current range. \emph{n} = number of participants contained between decile values.}\label{fig:semanticdecision-interactions-with-vocabulary-size}
\end{figure}

The present analysis uses a continuous measure of word concreteness. In contrast, Pexman and Yap (2018) analysed the same data set after dividing the stimulus words into abstract and concrete subsets, which they analysed separately. Pexman and Yap found that high-vocabulary participants were more sensitive to the relative abstractness of words. Specifically, these participants were faster to classify very abstract words than mid-abstract ones, thus presenting a reverse concreteness effect. Such a reverse effect might stem from the bimodal distributions of concreteness ratings (Brysbaert et al., 2014) and semantic decisions (Pexman \& Yap, 2018). The reverse effect has also been found in semantic dementia patients (Connell \& Lynott, 2012). Since the reverse effect contrasted with the long-established concreteness effect, the former has sometimes been regarded as an inconsistency.

Notwithstanding the aforementioned bimodal distributions, Troche et al. (2017) suggested that a continuous analysis remains necessary to study word concreteness (also see Cohen, 1983). Consistent with this, our present findings demonstrated the sensitivity of a continuous word-concreteness variable to patterns such as the greater role of task-relevant variables in high-vocabulary participants. In conclusion, the literature and our findings suggest that the split-data approach and the continuous approach to word concreteness are both useful. Where feasible, the application of both approaches would provide the most information.

\hypertarget{visualising-the-estimates-1}{%
\subsubsection{Visualising the estimates}\label{visualising-the-estimates-1}}

Figure \ref{fig:semanticdecision-confidence-intervals-plot} presents the means and 95\% confidence intervals for the effects of interest.\footnote{Bayesian estimates not shown as they were not valid. They are nonetheless available in \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}.}

\begin{figure}

{\centering \includegraphics[width=0.92\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/plots/semanticdecision_confidence_intervals_plot}

}

\caption{Means and 95\% confidence intervals for the effects of interest in the semantic decision model.}\label{fig:semanticdecision-confidence-intervals-plot}
\end{figure}

\hypertarget{statistical-power-analysis-1}{%
\subsubsection{Statistical power analysis}\label{statistical-power-analysis-1}}

Figures \ref{fig:semanticdecision-powercurve-plots-1-2-3} and \ref{fig:semanticdecision-powercurve-plots-4-5-6-7} show the estimated power available for main effects and interactions of interest, respectively.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/power_analysis/plots/semanticdecision_powercurve_plots_1_2_3}

}

\caption{Power curves for some main effects in the semantic decision study.}\label{fig:semanticdecision-powercurve-plots-1-2-3}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/power_analysis/plots/semanticdecision_powercurve_plots_4_5_6_7}

}

\caption{Power curves for some interactions in the semantic decision study.}\label{fig:semanticdecision-powercurve-plots-4-5-6-7}
\end{figure}

\_\_\_\_\_\_\_ interpret \_\_\_\_\_\_\_\_\_\_\_\_

\hypertarget{discussion-1}{%
\subsection{Discussion}\label{discussion-1}}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\clearpage

\hypertarget{study-3-lexical-decision}{%
\section{Study 3: Lexical decision}\label{study-3-lexical-decision}}

The core data set in this study was the lexical decision subset of the English Lexicon Project---ELP (Balota et al., 2007). The lexical decision task differs from semantic priming and semantic decision in two important aspects.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Less semantic processing.} The lexical decision paradigm is likely to involve less semantic processing than the other paradigms. \_\_\_\_\_\_\_\_\_\_\_\_
\item
  \textbf{Single-word measures.} Compared to semantic priming and semantic decision, it is more difficult in the lexical decision paradigm to create word-to-word distance measures to capture language-based and vision-based information. The possibility of calculating the distance between words in consecutive trials is hindered by the need to skip trials, owing to the high prevalence of nonword trials in the lexical decision paradigm. Therefore, the measures must be based on each word alone. Accordingly, vision-based information can be operationalised as the visual strength of each word. Language-based information could be operationalised as any of several lexical variables. In the present study, word frequency was chosen as it had the most explanatory power out of 5 candidates---the other candidates being number of letters, number of syllables, orthographic Levenshtein distance and phonological Levenshtein distance (see \protect\hyperlink{appendix-A-lexical-covariates}{\underline{Appendix A}}). It should also be noted that word frequency has been found to be more closely related to semantic variables than to lexical ones, such as word length, orthography, phonology (see Table 4 in Yap et al., 2012).
\end{enumerate}

Word frequency is also of interest due to its varying relationship to vocabulary size across different paradigms. Yap et al. (2012) found that higher-vocabulary participants in the ELP were more strongly influenced by word frequency than lower-vocabulary participants. The same finding also appeared in a lexical decision study in Chinese (Lim et al., 2020). In contrast, deeper semantic tasks, such as semantic priming (Yap et al., 2017) and semantic decision (Pexman \& Yap, 2018), have yielded the opposite pattern, with the effect of word frequency decreasing in higher-vocabulary participants.

\hypertarget{effects-of-interest-2}{%
\subsection{Effects of interest}\label{effects-of-interest-2}}

\begin{itemize}
\item
  Z-scored vocabulary age {[}\texttt{z\_vocabulary\_age}; calculated from \texttt{vocabAge} in Balota et al. (2007){]}
\item
  Z-scored, recoded participant's gender {[}\texttt{z\_recoded\_participant\_gender}; calculated from \texttt{Gender} in Balota et al. (2007){]}
\item
  Z-scored word frequency {[}\texttt{z\_word\_frequency}; calculated from \texttt{LgSUBTLWF} in Balota et al. (2007){]}
\item
  Z-scored vision-based information in words {[}\texttt{z\_visual\_rating}; calculated from \texttt{Visual.mean} in Lynott et al. (2020){]}
\end{itemize}

The final data set contained 795 participants, 12,636 words, and a total of 19,828 RTs. On average, there were 25 words per participant (\(SD\) = 36.04), and conversely, 2 participants per word (\(SD\) = 0.86).

Figure \ref{fig:lexicaldecision-correlations} shows the zero-order correlations among the predictors and the dependent variable.

\begin{figure}

{\centering \includegraphics[width=0.5\linewidth]{manuscript_files/figure-latex/lexicaldecision-correlations-1}

}

\caption{Zero-order correlations in the lexical decision study.}\label{fig:lexicaldecision-correlations}
\end{figure}

\hypertarget{covariates-2}{%
\subsection{Covariates}\label{covariates-2}}

The following lexical covariates were included in the model to allow a rigorous analysis of the effects of interest.

\begin{itemize}
\item
  Lexical (see \protect\hyperlink{appendix-A-lexical-covariates}{\underline{Appendix A}}): Z-scored orthographic Levenshtein distance (Balota et al., 2007)
\item
  Semantic: z-scored word concreteness (Brysbaert et al., 2014), used as a covariate of visual rating.
\end{itemize}

\hypertarget{diagnostics-for-the-frequentist-model-3}{%
\subsubsection{Diagnostics for the frequentist model}\label{diagnostics-for-the-frequentist-model-3}}

The model presented convergence warnings. To avoid removing important random slopes, which could increase the Type I error (Brauer \& Curtin, 2018; Singmann \& Kellen, 2019), we examined the model after refitting it using seven optimization algorithms through the `allFit' function of the `lme4' package (Bates et al., 2021). The results showed that all optimizers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential {[}Bates et al. (2021); see \protect\hyperlink{appendix-B-frequentist-analysis-diagnostics}{\underline{Appendix B}}{]}.

The residual errors were not normally distributed, and attempts to mitigate this deviation proved unsuccessful (see \protect\hyperlink{appendix-B-frequentist-analysis-diagnostics}{\underline{Appendix B}}). However, this is not likely to have posed a major problem, as mixed-effects models are fairly robust to deviations from normality (Knief \& Forstmeier, 2021; Schielzeth et al., 2020).

The model did not present multicollinearity problems, all VIFs being smaller than 2 (Dormann et al., 2013; Harrison et al., 2018).

\hypertarget{diagnostics-for-the-bayesian-model-2}{%
\subsubsection{Diagnostics for the Bayesian model}\label{diagnostics-for-the-bayesian-model-2}}

Three Bayesian models were run that were respectively characterised by informative, weakly-informative and diffuse priors. In each model, 5 chains were used. In each chain, 2,000 warmup iterations were run, followed by 18,000 post-warmup iterations. Thus, a total of 90,000 post-warmup draws were produced over all the chains.

The maximum \(\widehat R\) value for the fixed effects across the three models was 1.00, suggesting that these effects converged (Schoot et al., 2021; Vehtari et al., 2021). For the random effects, the maximum \(\widehat R\) value was 1.02, barely exceeding the 1.01 threshold (Vehtari et al., 2021).

The posterior predictive checks were sound (see \protect\hyperlink{appendix-C-Bayesian-analysis-diagnostics}{\underline{Appendix C}}). Furthermore, in the prior sensitivity analysis, the results were virtually identical with the three priors that were considered (to recall the priors, see Figure \ref{fig:bayesian-priors} above; to view the results in detail, see \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}).

\hypertarget{results-2}{%
\subsection{Results}\label{results-2}}

Table \ref{tab:lexicaldecision-frequentist-model} presents the results of the mixed-effects model.

\begin{table}[H]

\caption{\label{tab:lexicaldecision-frequentist-model}Frequentist model for the lexical decision study.}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lrrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{$\upbeta$} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$}\\
\midrule
(Intercept) & 0.00 & 0.01 & {}[-0.01, 0.01] & -0.02 & .983\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Individual differences}}\\
\hspace{1em}Vocabulary age $^{\text{a}}$ & 0.00 & 0.01 & {}[-0.01, 0.01] & -0.06 & .950\\
\hspace{1em}Gender $^{\text{a}}$ & 0.00 & 0.01 & {}[-0.01, 0.01] & 0.01 & .995\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Lexical covariate}}\\
\cellcolor{gray!6}{\hspace{1em}Orthographic Levenshtein distance} & \cellcolor{gray!6}{0.11} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[0.09, 0.12]} & \cellcolor{gray!6}{13.41} & \cellcolor{gray!6}{<.001}\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Semantic variables}}\\
\cellcolor{gray!6}{\hspace{1em}Word concreteness} & \cellcolor{gray!6}{-0.02} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[-0.04, -0.01]} & \cellcolor{gray!6}{-2.79} & \cellcolor{gray!6}{.005}\\
\hspace{1em}Word frequency $^{\text{b}}$ & -0.16 & 0.01 & {}[-0.18, -0.14] & -13.01 & <.001\\
\hspace{1em}Visual strength $^{\text{b}}$ & -0.01 & 0.01 & {}[-0.03, 0.01] & -1.36 & .175\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Interactions}}\\
\cellcolor{gray!6}{\hspace{1em}Word concreteness  $\times$  Vocabulary age} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[-0.01, 0.03]} & \cellcolor{gray!6}{1.16} & \cellcolor{gray!6}{.244}\\
\cellcolor{gray!6}{\hspace{1em}Word concreteness  $\times$  Gender} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[-0.02, 0.02]} & \cellcolor{gray!6}{0.16} & \cellcolor{gray!6}{.876}\\
\hspace{1em}Word frequency  $\times$  Vocabulary age & -0.02 & 0.01 & {}[-0.04, 0.01] & -1.31 & .191\\
\hspace{1em}Visual strength  $\times$  Vocabulary age & 0.00 & 0.01 & {}[-0.02, 0.02] & 0.05 & .962\\
\hspace{1em}Word frequency  $\times$  Gender & -0.02 & 0.01 & {}[-0.04, 0.00] & -1.75 & .080\\
\hspace{1em}Visual strength  $\times$  Gender & -0.01 & 0.01 & {}[-0.03, 0.01] & -0.86 & .390\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \textit{\linebreak} 
\item \textit{Note}. $\upbeta$ = Estimate based on z-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CI = confidence interval. Shaded rows contain covariates. \linebreak \linebreak \phantom{.}$^{\text{a}}$ By-word random slopes were included for this effect. \linebreak \phantom{.}$^{\text{b}}$ By-participant random slopes were included for this effect.
\end{tablenotes}
\end{threeparttable}
\end{table}

The fixed effects of this model explained 5.61\% of the variance, and the random effects explained 10.25\% (Nakagawa et al., 2017).

\hypertarget{visualising-the-estimates-2}{%
\subsubsection{Visualising the estimates}\label{visualising-the-estimates-2}}

Figure \ref{fig:lexicaldecision-frequentist-bayesian-plot-weaklyinformativepriors-exgaussian} presents the posterior distribution of each effect, based on the informative prior model (for the models with the other priors, see \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}). The frequentist estimates are also shown to facilitate the comparison with them.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_bayesian_plots/plots/lexicaldecision_frequentist_bayesian_plot_weaklyinformativepriors_exgaussian}

}

\caption{Estimates from the frequentist analysis (in red) and from the Bayesian analysis (in blue) for the lexical decision study. The frequentist means (represented by points) are flanked by 95\% confidence intervals. The Bayesian means (represented by vertical lines) are flanked by 95\% credible intervals, in light blue (in some cases, the interval is covered up by the bar of the mean).}\label{fig:lexicaldecision-frequentist-bayesian-plot-weaklyinformativepriors-exgaussian}
\end{figure}

\hypertarget{statistical-power-analysis-2}{%
\subsubsection{Statistical power analysis}\label{statistical-power-analysis-2}}

Figures \ref{fig:lexicaldecision-powercurve-plots-1-2-3} and \ref{fig:lexicaldecision-powercurve-plots-4-5-6-7} show the estimated power available for main effects and interactions of interest, respectively.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/power_analysis/plots/lexicaldecision_powercurve_plots_1_2_3}

}

\caption{Power curves for some main effects in the lexical decision study.}\label{fig:lexicaldecision-powercurve-plots-1-2-3}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/power_analysis/plots/lexicaldecision_powercurve_plots_4_5_6_7}

}

\caption{Power curves for some interactions in the lexical decision study.}\label{fig:lexicaldecision-powercurve-plots-4-5-6-7}
\end{figure}

\_\_\_\_\_\_\_ interpret \_\_\_\_\_\_\_\_\_\_\_\_

\hypertarget{discussion-2}{%
\subsection{Discussion}\label{discussion-2}}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{general-discussion}{%
\section{General discussion}\label{general-discussion}}

In all three studies, the main effects and the interactions of language-based information were larger than those of vision-based information, consistent with previous research {[}\ldots{]}. Beyond that, the results revealed a dynamic process influenced by three levels of variation: participants, words and tasks. The associations that appeared across these levels revealed the roles of language-based and vision-based mechanisms in conceptual processing.

The RTs of higher-vocabulary participants were influenced by a smaller number of variables than those of lower-vocabulary participants. This converges with previous findings suggesting that higher and lower-vocabulary participants are affected by different variables. Potentially, the variables affecting higher-vocabulary participants are more relevant to the task (Lim et al., 2020; Pexman \& Yap, 2018; Yap et al., 2012, 2017).

\hypertarget{differences-between-measurement-instruments-and-the-associated-risks}{%
\subsection{Differences between measurement instruments and the associated risks}\label{differences-between-measurement-instruments-and-the-associated-risks}}

We also compared two measures of visual priming. The first measure was operationalised as the difference in visual strength (Lynott et al., 2020) between the prime and the target word in each trial. The second measure, created by (Petilli et al., 2021), was based on vector representations trained on images. The results revealed that the visual strength measure was significantly superior in explaining RTs. This difference was not due to an excessive collinearity between these measures (\(r\) = .02). Also importantly, both measures appeared to be valid based on their correlations with language-based similarity and with word concreteness.

If we indeed accept that both the above measures were valid, we must reflect on the possibility that measurement instruments create confounds when different systems are compared. That is, in the case of linguistic and embodied processing, the large difference between the effect sizes of these systems---found in the three current studies and in the previous literature {[}\ldots{]}---would not be trustworthy if the instruments that were used to measure the language system were far more precise than the instruments used to measure the embodiment system. In this sense, consider how variables are refined in research: it is done by comparing the performance of different variables. Critically, the literature seems to contain many comparisons of text-based variables, some dating from the 1990s (De Deyne et al., 2016, 2013; Günther et al., 2016a, 2016b; Jones et al., 2006; Lund \& Burgess, 1996; Mikolov et al., 2013; Wingfield \& Connell, 2022). In contrast, the work on embodiment variables began more than a decade afterwards, and this work has been more concerned with comparisons of different \emph{modalities}---e.g., valence, visual strength, auditory strength, etc. (Lynott et al., 2020; Lynott \& Connell, 2009; Newcombe et al., 2012). Thus, this historical discrepancy might in part (only in part) account for the superiority of linguistic information over embodied information, as found in the present study and in previous studies (Banks et al., 2021; Kiela \& Bottou, 2014; Lam et al., 2015; Louwerse et al., 2015; Pecher et al., 1998; Petilli et al., 2021).

The case of different measurement instruments is one of several factors that can exert a great influence in analyses. In the medium term, it may pay dividends to devote more work to comparing different instruments and, more generally, different analyses (see Barsalou, 2019; Botvinik-Nezer et al., 2020; Wagenmakers et al., 2022).

\hypertarget{statistical-power}{%
\subsection{Statistical power}\label{statistical-power}}

Power analyses were performed to \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_. \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_. The sample sizes required for some of the effects are not easily feasible with the usual distribution of funding in psychological research projects.

\clearpage

\hypertarget{references}{%
\section{References}\label{references}}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-albersWhenPowerAnalyses2018}{}}%
Albers, C., \& Lakens, D. (2018). When power analyses based on pilot data are biased: {Inaccurate} effect size estimators and follow-up bias. \emph{Journal of Experimental Social Psychology}, \emph{74}, 187--195. \url{https://doi.org/10.1016/j.jesp.2017.09.004}

\leavevmode\vadjust pre{\hypertarget{ref-amselTrackingRealtimeNeural2011}{}}%
Amsel, B. D. (2011). Tracking real-time neural activation of conceptual knowledge using single-trial event-related potentials. \emph{Neuropsychologia}, \emph{49}(5), 970--983. \url{https://doi.org/10.1016/j.neuropsychologia.2011.01.003}

\leavevmode\vadjust pre{\hypertarget{ref-amselEmpiricallyGroundingGrounded2014}{}}%
Amsel, B. D., Urbach, T. P., \& Kutas, M. (2014). Empirically grounding grounded cognition: {The} case of color. \emph{NeuroImage}, \emph{99}, 149--157. \url{https://doi.org/10.1016/j.neuroimage.2014.05.025}

\leavevmode\vadjust pre{\hypertarget{ref-andersonResponseCommentEstimating2016}{}}%
Anderson, C. J., Bahník, Š., Barnett-Cowan, M., Bosco, F. A., Chandler, J., Chartier, C. R., Cheung, F., Christopherson, C. D., Cordes, A., Cremata, E. J., Della Penna, N., Estel, V., Fedor, A., Fitneva, S. A., Frank, M. C., Grange, J. A., Hartshorne, J. K., Hasselman, F., Henninger, F., \ldots{} Zuni, K. (2016). Response to {Comment} on {``{Estimating} the reproducibility of psychological science.''} \emph{Science}, \emph{351}(6277), 1037--1037. \url{https://doi.org/10.1126/science.aad9163}

\leavevmode\vadjust pre{\hypertarget{ref-andrewsIntegratingExperientialDistributional2009}{}}%
Andrews, M., Vigliocco, G., \& Vinson, D. (2009). Integrating experiential and distributional data to learn semantic representations. \emph{Psychological Review}, \emph{116}(3), 463--498. \url{https://doi.org/10.1037/a0016261}

\leavevmode\vadjust pre{\hypertarget{ref-aujlaLanguageExperiencePredicts2021}{}}%
Aujla, H. (2021). Language experience predicts semantic priming of lexical decision. \emph{Canadian Journal of Experimental Psychology/Revue Canadienne de Psychologie Expérimentale}, \emph{75}(3), 235. \url{https://doi.org/10.1037/cep0000255}

\leavevmode\vadjust pre{\hypertarget{ref-balotaDepthAutomaticSpreading1986}{}}%
Balota, D. A., \& Lorch, R. F. (1986). Depth of automatic spreading activation: {Mediated} priming effects in pronunciation but not in lexical decision. \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{12}(3), 336--345. \url{https://doi.org/10.1037/0278-7393.12.3.336}

\leavevmode\vadjust pre{\hypertarget{ref-balotaMeanResponseLatency2008}{}}%
Balota, D. A., Yap, M. J., Cortese, M. J., \& Watson, J. M. (2008). Beyond mean response latency: {Response} time distributional analyses of semantic priming. \emph{Journal of Memory and Language}, \emph{59}(4), 495--523. \url{https://doi.org/10.1016/j.jml.2007.10.004}

\leavevmode\vadjust pre{\hypertarget{ref-balota2007a}{}}%
Balota, D. A., Yap, M. J., Hutchison, K. A., Cortese, M. J., Kessler, B., Loftis, B., Neely, J. H., Nelson, D. L., Simpson, G. B., \& Treiman, R. (2007). The {English Lexicon Project}. \emph{Behavior Research Methods}, \emph{39}, 445--459. \url{https://doi.org/10.3758/BF03193014}

\leavevmode\vadjust pre{\hypertarget{ref-banksLinguisticDistributionalKnowledge2021}{}}%
Banks, B., Wingfield, C., \& Connell, L. (2021). Linguistic distributional knowledge and sensorimotor grounding both contribute to semantic category production. \emph{Cognitive Science}, \emph{45}(10), e13055. \url{https://doi.org/10.1111/cogs.13055}

\leavevmode\vadjust pre{\hypertarget{ref-barca2020a}{}}%
Barca, L., Mazzuca, C., \& Borghi, A. (2020). Overusing the pacifier during infancy sets a footprint on abstract words processing. \emph{Journal of Child Language}, \emph{47}(5), 1084--1099. \url{https://doi.org/10.1017/S0305000920000070}

\leavevmode\vadjust pre{\hypertarget{ref-barrRandomEffectsStructure2013}{}}%
Barr, D. J., Levy, R., Scheepers, C., \& Tily, H. J. (2013). Random effects structure for confirmatory hypothesis testing: {Keep} it maximal. \emph{Journal of Memory and Language}, \emph{68}(3), 255--278. \url{https://doi.org/10.1016/j.jml.2012.11.001}

\leavevmode\vadjust pre{\hypertarget{ref-barsalouEstablishingGeneralizableMechanisms2019}{}}%
Barsalou, L. W. (2019). Establishing generalizable mechanisms. \emph{Psychological Inquiry}, \emph{30}(4), 220--230. \url{https://doi.org/10.1080/1047840X.2019.1693857}

\leavevmode\vadjust pre{\hypertarget{ref-barsalouPerceptualSymbolSystems1999}{}}%
Barsalou, L. W. (1999). Perceptual symbol systems. \emph{Behavioral and Brain Sciences}, \emph{22}(4), 577--660. \url{https://doi.org/10.1017/S0140525X99002149}

\leavevmode\vadjust pre{\hypertarget{ref-barsalouLanguageSimulationConceptual2008}{}}%
Barsalou, L. W., Santos, A., Simmons, W. K., \& Wilson, C. D. (2008). Language and simulation in conceptual processing. In \emph{Symbols and {Embodiment}}. {Oxford University Press}. \url{https://doi.org/10.1093/acprof:oso/9780199217274.003.0013}

\leavevmode\vadjust pre{\hypertarget{ref-bartonWordlengthEffectReading2014}{}}%
Barton, J. J. S., Hanif, H. M., Eklinder Björnström, L., \& Hills, C. (2014). The word-length effect in reading: {A} review. \emph{Cognitive Neuropsychology}, \emph{31}(5-6), 378--412. \url{https://doi.org/10.1080/02643294.2014.895314}

\leavevmode\vadjust pre{\hypertarget{ref-batesFittingLinearMixedeffects2015}{}}%
Bates, D., Mächler, M., Bolker, B., \& Walker, S. (2015). Fitting linear mixed-effects models using {lme4}. \emph{Journal of Statistical Software}, \emph{67}, 1--48. \url{https://doi.org/10.18637/jss.v067.i01}

\leavevmode\vadjust pre{\hypertarget{ref-batesPackageLme42021}{}}%
Bates, D., Maechler, M., Bolker, B., Walker, S., Christensen, R. H. B., Singmann, H., Dai, B., Scheipl, F., Grothendieck, G., Green, P., Fox, J., Brauer, A., \& Krivitsky, P. N. (2021). \emph{Package '{lme4}'}. {CRAN}. \url{https://cran.r-project.org/web/packages/lme4/lme4.pdf}

\leavevmode\vadjust pre{\hypertarget{ref-beckerLongtermSemanticPriming1997}{}}%
Becker, S., Moscovitch, M., Behrmann, M., \& Joordens, S. (1997). Long-term semantic priming: {A} computational account and empirical evidence. \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{23}(5), 1059--1082. \url{https://doi.org/10.1037/0278-7393.23.5.1059}

\leavevmode\vadjust pre{\hypertarget{ref-bernabeu2021a}{}}%
Bernabeu, P., Lynott, D., \& Connell, L. (2021). \emph{Preregistration: {The} interplay between linguistic and embodied systems in conceptual processing}. {OSF}. \url{https://osf.io/ftydw/}

\leavevmode\vadjust pre{\hypertarget{ref-bernabeu2017a}{}}%
Bernabeu, P., Willems, R. M., \& Louwerse, M. M. (2017). Modality switch effects emerge early and increase throughout conceptual processing: {Evidence} from {ERPs}. In G. Gunzelmann, A. Howes, T. Tenbrink, \& E. J. Davelaar (Eds.), \emph{Proceedings of the 39th {Annual Conference} of the {Cognitive Science Society}} (pp. 1629--1634). {Cognitive Science Society}. \url{https://mindmodeling.org/cogsci2017/papers/0318}

\leavevmode\vadjust pre{\hypertarget{ref-beyersmannEvidenceEmbeddedWord2020}{}}%
Beyersmann, E., Grainger, J., \& Taft, M. (2020). Evidence for embedded word length effects in complex nonwords. \emph{Language, Cognition and Neuroscience}, \emph{35}(2), 235--245. \url{https://doi.org/10.1080/23273798.2019.1659989}

\leavevmode\vadjust pre{\hypertarget{ref-borghiWordsSocialTools2019}{}}%
Borghi, A. M., Barca, L., Binkofski, F., Castelfranchi, C., Pezzulo, G., \& Tummolini, L. (2019). Words as social tools: {Language}, sociality and inner grounding in abstract concepts. \emph{Physics of Life Reviews}, \emph{29}, 120--153. \url{https://doi.org/10.1016/j.plrev.2018.12.001}

\leavevmode\vadjust pre{\hypertarget{ref-bottiniConcretenessAdvantageLexical2021}{}}%
Bottini, R., Morucci, P., D'Urso, A., Collignon, O., \& Crepaldi, D. (2021). The concreteness advantage in lexical decision does not depend on perceptual simulations. \emph{Journal of Experimental Psychology: General}. \url{https://doi.org/10.1037/xge0001090}

\leavevmode\vadjust pre{\hypertarget{ref-botvinik-nezerVariabilityAnalysisSingle2020}{}}%
Botvinik-Nezer, R., Holzmeister, F., Camerer, C. F., Dreber, A., Huber, J., Johannesson, M., Kirchler, M., Iwanir, R., Mumford, J. A., Adcock, R. A., Avesani, P., Baczkowski, B. M., Bajracharya, A., Bakst, L., Ball, S., Barilari, M., Bault, N., Beaton, D., Beitner, J., \ldots{} Schonberg, T. (2020). Variability in the analysis of a single neuroimaging dataset by many teams. \emph{Nature}, \emph{582}(7810, 7810), 84--88. \url{https://doi.org/10.1038/s41586-020-2314-9}

\leavevmode\vadjust pre{\hypertarget{ref-brauer2018a}{}}%
Brauer, M., \& Curtin, J. J. (2018). Linear mixed-effects models and the analysis of nonindependent data: {A} unified framework to analyze categorical and continuous independent variables that vary within-subjects and/or within-items. \emph{Psychological Methods}, \emph{23}(3), 389--411. \url{https://doi.org/10.1037/met0000159}

\leavevmode\vadjust pre{\hypertarget{ref-brysbaertHowManyParticipants2019}{}}%
Brysbaert, M. (2019). How many participants do we have to include in properly powered experiments? {A} tutorial of power analysis with reference tables. \emph{Journal of Cognition}, \emph{2}(1, 1), 16. \url{https://doi.org/10.5334/joc.72}

\leavevmode\vadjust pre{\hypertarget{ref-brysbaertWordRecognitionII2022}{}}%
Brysbaert, M. (2022). Word recognition {II}. In M. J. Snowling, C. Hulme, \& K. Nation, \emph{The science of reading} (pp. 79--101). {John Wiley \& Sons, Ltd}. \url{https://doi.org/10.1002/9781119705116.ch4}

\leavevmode\vadjust pre{\hypertarget{ref-brysbaertWordFrequencyEffect2018a}{}}%
Brysbaert, M., Mandera, P., \& Keuleers, E. (2018). The word frequency effect in word processing: {An} updated review. \emph{Current Directions in Psychological Science}, \emph{27}(1), 45--50. \url{https://doi.org/10.1177/0963721417727521}

\leavevmode\vadjust pre{\hypertarget{ref-brysbaertPowerAnalysisEffect2018}{}}%
Brysbaert, M., \& Stevens, M. (2018). Power analysis and effect size in mixed effects models: A tutorial. \emph{Journal of Cognition}, \emph{1}(1), 9. \url{https://doi.org/10.5334/joc.10}

\leavevmode\vadjust pre{\hypertarget{ref-brysbaertImpactWordPrevalence2016}{}}%
Brysbaert, M., Stevens, M., Mandera, P., \& Keuleers, E. (2016). The impact of word prevalence on lexical decision times: {Evidence} from the {Dutch Lexicon Project} 2. \emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{42}(3), 441--458. \url{https://doi.org/10.1037/xhp0000159}

\leavevmode\vadjust pre{\hypertarget{ref-brysbaert2014a}{}}%
Brysbaert, M., Warriner, A. B., \& Kuperman, V. (2014). Concreteness ratings for 40 thousand generally known {English} word lemmas. \emph{Behavior Research Methods}, \emph{46}, 904--911. \url{https://doi.org/10.3758/s13428-013-0403-5}

\leavevmode\vadjust pre{\hypertarget{ref-bullinariaExtractingSemanticRepresentations2007}{}}%
Bullinaria, J. A., \& Levy, J. P. (2007). Extracting semantic representations from word co-occurrence statistics: {A} computational study. \emph{Behavior Research Methods}, \emph{39}(3), 510--526. \url{https://doi.org/10.3758/BF03193020}

\leavevmode\vadjust pre{\hypertarget{ref-burknerAdvancedBayesianMultilevel2018}{}}%
Bürkner, P.-C. (2018). Advanced {Bayesian} multilevel modeling with the {R} package {brms}. \emph{The R Journal}, \emph{10}(1), 395--411. \url{https://journal.r-project.org/archive/2018/RJ-2018-017/index.html}

\leavevmode\vadjust pre{\hypertarget{ref-burknerPackageBrms2022}{}}%
Bürkner, P.-C., Gabry, J., Weber, S., Johnson, A., Modrak, M., Badr, H. S., Weber, F., Ben-Shachar, M. S., \& Rabel, H. (2022). \emph{Package '{brms}'}. {CRAN}. \url{https://cran.r-project.org/web/packages/brms/brms.pdf}

\leavevmode\vadjust pre{\hypertarget{ref-burman2008a}{}}%
Burman, D., Bitan, T., \& Both, J. (2008). Sex differences in neural processing of language among children. \emph{Neuropsychologia}, \emph{46, 5}, 1349--1362. \url{https://doi.org/10.1016/j.neuropsychologia.2007.12.021}

\leavevmode\vadjust pre{\hypertarget{ref-buttonPowerFailureWhy2013}{}}%
Button, K. S., Ioannidis, J. P. A., Mokrysz, C., Nosek, B. A., Flint, J., Robinson, E. S. J., \& Munafò, M. R. (2013). Power failure: {Why} small sample size undermines the reliability of neuroscience. \emph{Nature Reviews Neuroscience}, \emph{14}(5, 5), 365--376. \url{https://doi.org/10.1038/nrn3475}

\leavevmode\vadjust pre{\hypertarget{ref-cerniMotorExpertiseTyping2016}{}}%
Cerni, T., Velay, J.-L., Alario, F.-X., Vaugoyeau, M., \& Longcamp, M. (2016). Motor expertise for typing impacts lexical decision performance. \emph{Trends in Neuroscience and Education}, \emph{5}(3), 130--138. \url{https://doi.org/10.1016/j.tine.2016.07.007}

\leavevmode\vadjust pre{\hypertarget{ref-charbonnierPredictingConcretenessGerman2020}{}}%
Charbonnier, J., \& Wartena, C. (2020). Predicting the concreteness of {German} words. \emph{Proceedings of the 5th {Swiss Text Analytics Conference} ({SwissText})}, \emph{2624}. \url{https://doi.org/10.25968/opus-2075}

\leavevmode\vadjust pre{\hypertarget{ref-charbonnierPredictingWordConcreteness2019}{}}%
Charbonnier, J., \& Wartena, C. (2019). Predicting word concreteness and imagery. \emph{Proceedings of the 13th {International Conference} on {Computational Semantics} - {Long Papers}}, 176--187. \url{https://doi.org/10.18653/v1/W19-0415}

\leavevmode\vadjust pre{\hypertarget{ref-cohenCostDichotomization1983}{}}%
Cohen, J. (1983). The cost of dichotomization. \emph{Applied Psychological Measurement}, \emph{7}(3), 249--253. \url{https://doi.org/10.1177/014662168300700301}

\leavevmode\vadjust pre{\hypertarget{ref-collinsModalitySwitchingProperty2011}{}}%
Collins, J., Pecher, D., Zeelenberg, R., \& Coulson, S. (2011). Modality switching in a property verification task: {An} erp study of what happens when candles flicker after high heels click. \emph{Frontiers in Psychology}, \emph{2}. \url{https://www.frontiersin.org/article/10.3389/fpsyg.2011.00010}

\leavevmode\vadjust pre{\hypertarget{ref-concaSearchDifferentCategories2021}{}}%
Conca, F., Catricalà, E., Canini, M., Petrini, A., Vigliocco, G., Cappa, S. F., \& Della Rosa, P. A. (2021). In search of different categories of abstract concepts: A {fMRI} adaptation study. \emph{Scientific Reports}, \emph{11}(1, 1), 22587. \url{https://doi.org/10.1038/s41598-021-02013-8}

\leavevmode\vadjust pre{\hypertarget{ref-connell2019a}{}}%
Connell, L. (2019). What have labels ever done for us? {The} linguistic shortcut in conceptual processing. \emph{Language, Cognition and Neuroscience}, \emph{34}(10), 1308--1318. \url{https://doi.org/10.1080/23273798.2018.1471512}

\leavevmode\vadjust pre{\hypertarget{ref-connellStrengthPerceptualExperience2012}{}}%
Connell, L., \& Lynott, D. (2012). Strength of perceptual experience predicts word processing performance better than concreteness or imageability. \emph{Cognition}, \emph{125}(3), 452--465. \url{https://doi.org/10.1016/j.cognition.2012.07.010}

\leavevmode\vadjust pre{\hypertarget{ref-connell2013a}{}}%
Connell, L., \& Lynott, D. (2013). Flexible and fast: {Linguistic} shortcut affects both shallow and deep conceptual processing. \emph{Psychonomic Bulletin \& Review}, \emph{20, 3}, 542--550. \url{https://doi.org/10.3758/s13423-012-0368-x}

\leavevmode\vadjust pre{\hypertarget{ref-connellSeeHearWhat2014}{}}%
Connell, L., \& Lynott, D. (2014). I see/hear what you mean: {Semantic} activation in visual word recognition depends on perceptual attention. \emph{Journal of Experimental Psychology: General}, \emph{143}(2), 527--533. \url{https://doi.org/10.1037/a0034626}

\leavevmode\vadjust pre{\hypertarget{ref-connellWeKnowWhat2016}{}}%
Connell, L., \& Lynott, D. (2016). Do we know what we're simulating? {Information} loss on transferring unconscious perceptual simulation to conscious imagery. \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{42}(8), 1218--1232. \url{https://doi.org/10.1037/xlm0000245}

\leavevmode\vadjust pre{\hypertarget{ref-connellInteroceptionForgottenModality2018}{}}%
Connell, L., Lynott, D., \& Banks, B. (2018). Interoception: The forgotten modality in perceptual grounding of abstract and concrete concepts. \emph{Philosophical Transactions of the Royal Society B: Biological Sciences}, \emph{373}(1752), 20170143. \url{https://doi.org/10.1098/rstb.2017.0143}

\leavevmode\vadjust pre{\hypertarget{ref-contreraskallensQuantifyingInterdisciplinarityCognitive2022}{}}%
Contreras Kallens, P., Dale, R., \& Christiansen, M. H. (2022). Quantifying interdisciplinarity in cognitive science and beyond. \emph{Topics in Cognitive Science}. \url{https://doi.org/10.1111/tops.12609}

\leavevmode\vadjust pre{\hypertarget{ref-corkerHighQualityDirect2014}{}}%
Corker, K. S., Lynott, D., Wortman, J., Connell, L., Donnellan, M. B., Lucas, R. E., \& O'Brien, K. (2014). High quality direct replications matter: {Response} to {Williams} (2014). \emph{Social Psychology}, \emph{45}(4), 324--326.

\leavevmode\vadjust pre{\hypertarget{ref-cummingNewStatisticsWhy2014}{}}%
Cumming, G. (2014). The new statistics: {Why} and how. \emph{Psychological Science}, \emph{25}(1), 7--29. \url{https://doi.org/10.1177/0956797613504966}

\leavevmode\vadjust pre{\hypertarget{ref-davies2017a}{}}%
Davies, R. A., Arnell, R., Birchenough, J. M., Grimmond, D., \& Houlson, S. (2017). Reading through the life span: {Individual} differences in psycholinguistic effects. \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{43}(8), 1298. \url{https://doi.org/10.1037/xlm0000366}

\leavevmode\vadjust pre{\hypertarget{ref-dedeyneVisualAffectiveMultimodal2021}{}}%
De Deyne, S., Navarro, D. J., Collell, G., \& Perfors, A. (2021). Visual and affective multimodal models of word meaning in language and mind. \emph{Cognitive Science}, \emph{45}(1), e12922. \url{https://doi.org/10.1111/cogs.12922}

\leavevmode\vadjust pre{\hypertarget{ref-de2019a}{}}%
De Deyne, S., Navarro, D. J., Perfors, A., Brysbaert, M., \& Storms, G. (2019). The {``{Small World} of {Words}''} {English} word association norms for over 12,000 cue words. \emph{Behavior Research Methods}, \emph{51}, 987--1006. \url{https://doi.org/10.3758/s13428-018-1115-7}

\leavevmode\vadjust pre{\hypertarget{ref-dedeyneBetterExplanationsLexical2013}{}}%
De Deyne, S., Navarro, D. J., \& Storms, G. (2013). Better explanations of lexical and semantic cognition using networks derived from continued rather than single-word associations. \emph{Behavior Research Methods}, \emph{45}(2), 480--498. \url{https://doi.org/10.3758/s13428-012-0260-7}

\leavevmode\vadjust pre{\hypertarget{ref-de2016a}{}}%
De Deyne, S., Perfors, A., \& Navarro, D. (2016). Predicting human similarity judgments with distributional models: {The} value of word associations. \emph{Proceedings of {COLING} 2016, the 26th International Conference on Computational Linguistics: {Technical} Papers}, 1861--1870.

\leavevmode\vadjust pre{\hypertarget{ref-dewitMaskedSemanticPriming2015}{}}%
de Wit, B., \& Kinoshita, S. (2015). The masked semantic priming effect is task dependent: {Reconsidering} the automatic spreading activation process. \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{41}(4), 1062--1075. \url{https://doi.org/10.1037/xlm0000074}

\leavevmode\vadjust pre{\hypertarget{ref-dilolloDecouplingStimulusDuration2004}{}}%
Di Lollo, V., Mühlenen, A. von, Enns, J. T., \& Bridgeman, B. (2004). Decoupling stimulus duration from brightness in metacontrast masking: {Data} and models. \emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{30}(4), 733--745. \url{https://doi.org/10.1037/0096-1523.30.4.733}

\leavevmode\vadjust pre{\hypertarget{ref-diazNeuralSensitivityPhonological2021}{}}%
Diaz, M. T., Karimi, H., Troutman, S. B. W., Gertel, V. H., Cosgrove, A. L., \& Zhang, H. (2021). Neural sensitivity to phonological characteristics is stable across the lifespan. \emph{NeuroImage}, \emph{225}, 117511. \url{https://doi.org/10.1016/j.neuroimage.2020.117511}

\leavevmode\vadjust pre{\hypertarget{ref-dijkstraMultilinkComputationalModel2019}{}}%
Dijkstra, T., Wahl, A., Buytenhuijs, F., Halem, N. V., Al-Jibouri, Z., Korte, M. D., \& Rekké, S. (2019). Multilink: {A} computational model for bilingual word recognition and word translation. \emph{Bilingualism: Language and Cognition}, \emph{22}(4), 657--679. \url{https://doi.org/10.1017/S1366728918000287}

\leavevmode\vadjust pre{\hypertarget{ref-dils2010a}{}}%
Dils, A. T., \& Boroditsky, L. (2010). Visual motion aftereffect from understanding motion language. \emph{Proceedings of the National Academy of Sciences}, \emph{107}(37), 16396--16400. \url{https://doi.org/10.1073/pnas.1009438107}

\leavevmode\vadjust pre{\hypertarget{ref-diveicaQuantifyingSocialSemantics2022}{}}%
Diveica, V., Pexman, P. M., \& Binney, R. J. (2022). Quantifying social semantics: {An} inclusive definition of socialness and ratings for 8388 {English} words. \emph{Behavior Research Methods}. \url{https://doi.org/10.3758/s13428-022-01810-x}

\leavevmode\vadjust pre{\hypertarget{ref-dormannCollinearityReviewMethods2013}{}}%
Dormann, C. F., Elith, J., Bacher, S., Buchmann, C., Carl, G., Carré, G., Marquéz, J. R. G., Gruber, B., Lafourcade, B., Leitão, P. J., Münkemüller, T., McClean, C., Osborne, P. E., Reineking, B., Schröder, B., Skidmore, A. K., Zurell, D., \& Lautenbach, S. (2013). Collinearity: A review of methods to deal with it and a simulation study evaluating their performance. \emph{Ecography}, \emph{36}(1), 27--46. \url{https://doi.org/10.1111/j.1600-0587.2012.07348.x}

\leavevmode\vadjust pre{\hypertarget{ref-dove2020a}{}}%
Dove, G. (2020). More than a scaffold: {Language} is a neuroenhancement. \emph{Cognitive Neuropsychology}, \emph{37}(5-6), 288--311. \url{https://doi.org/10.1080/02643294.2019.1637338}

\leavevmode\vadjust pre{\hypertarget{ref-dunabeitiaQualitativeDifferencesRepresentation2009}{}}%
Duñabeitia, J. A., Avilés, A., Afonso, O., Scheepers, C., \& Carreiras, M. (2009). Qualitative differences in the representation of abstract versus concrete words: {Evidence} from the visual-world paradigm. \emph{Cognition}, \emph{110}(2), 284--292. \url{https://doi.org/10.1016/j.cognition.2008.11.012}

\leavevmode\vadjust pre{\hypertarget{ref-faust1999a}{}}%
Faust, M. E., Balota, D. A., Spieler, D. H., \& Ferraro, F. R. (1999). Individual differences in information-processing rate and amount: {Implications} for group differences in response latency. \emph{Psychological Bulletin}, \emph{125}, 777--799. \url{https://doi.org/10.1037/0033-2909.125.6.777}

\leavevmode\vadjust pre{\hypertarget{ref-fernandinoDecodingInformationStructure2022}{}}%
Fernandino, L., Tong, J.-Q., Conant, L. L., Humphries, C. J., \& Binder, J. R. (2022). Decoding the information structure underlying the neural representation of concepts. \emph{Proceedings of the National Academy of Sciences}, \emph{119}(6). \url{https://doi.org/10.1073/pnas.2108091119}

\leavevmode\vadjust pre{\hypertarget{ref-fettermanFeelingWarmBeing2018}{}}%
Fetterman, A. K., Wilkowski, B. M., \& Robinson, M. D. (2018). On feeling warm and being warm: {Daily} perceptions of physical warmth fluctuate with interpersonal warmth. \emph{Social Psychological and Personality Science}, \emph{9}(5), 560--567. \url{https://doi.org/10.1177/1948550617712032}

\leavevmode\vadjust pre{\hypertarget{ref-fleurDefinitelySawIt2020}{}}%
Fleur, D. S., Flecken, M., Rommers, J., \& Nieuwland, M. S. (2020). Definitely saw it coming? {The} dual nature of the pre-nominal prediction effect. \emph{Cognition}, \emph{204}, 104335. \url{https://doi.org/10.1016/j.cognition.2020.104335}

\leavevmode\vadjust pre{\hypertarget{ref-floresdarcaisSemanticActivationRecognition1985}{}}%
Flores d'Arcais, G. B., Schreuder, R., \& Glazenborg, G. (1985). Semantic activation during recognition of referential words. \emph{Psychological Research}, \emph{47}(1), 39--49. \url{https://doi.org/10.1007/BF00309217}

\leavevmode\vadjust pre{\hypertarget{ref-foxGeneralizedLinearModels2016}{}}%
Fox, J. (2016). Generalized linear models. In \emph{Applied regression analysis and generalized linear models} (Third Edition, pp. 418--472). {SAGE}.

\leavevmode\vadjust pre{\hypertarget{ref-gagneProcessingEnglishCompounds2016}{}}%
Gagné, C. L., Spalding, T. L., \& Nisbet, K. A. (2016). Processing english compounds: {Investigating} semantic transparency. \emph{SKASE Journal of Theoretical Linguistics}, \emph{13}(2), 2--22. \url{https://link.gale.com/apps/doc/A469757337/LitRC?u=anon~b6a332f4\&xid=9960afc7}

\leavevmode\vadjust pre{\hypertarget{ref-galleseBrainConceptsRole2005}{}}%
Gallese, V., \& Lakoff, G. (2005). The {Brain}'s concepts: The role of the {Sensory-motor} system in conceptual knowledge. \emph{Cognitive Neuropsychology}, \emph{22}(3-4), 455--479. \url{https://doi.org/10.1080/02643290442000310}

\leavevmode\vadjust pre{\hypertarget{ref-garceaPreservedToolKnowledge2013}{}}%
Garcea, F., Dombovy, M., \& Mahon, B. Z. (2013). Preserved {Tool Knowledge} in the {Context} of {Impaired Action Knowledge}: {Implications} for {Models} of {Semantic Memory}. \emph{Frontiers in Human Neuroscience}, \emph{7}, 120. \url{https://doi.org/10.3389/fnhum.2013.00120}

\leavevmode\vadjust pre{\hypertarget{ref-garciaTimeFaceLanguage2020}{}}%
García, A. M., Hesse, E., Birba, A., Adolfi, F., Mikulan, E., Caro, M. M., Petroni, A., Bekinschtein, T. A., del Carmen García, M., Silva, W., Ciraolo, C., Vaucheret, E., Sedeño, L., \& Ibáñez, A. (2020). Time to face language: Embodied mechanisms underpin the inception of face-related meanings in the human brain. \emph{Cerebral Cortex}, \emph{30}(11), 6051--6068. \url{https://doi.org/10.1093/cercor/bhaa178}

\leavevmode\vadjust pre{\hypertarget{ref-gelmanPowerCalculationsAssessing2014}{}}%
Gelman, A., \& Carlin, J. (2014). Beyond power calculations: Assessing type s (sign) and type m (magnitude) errors. \emph{Perspectives on Psychological Science}, \emph{9}(6), 641--651. \url{https://doi.org/10.1177/1745691614551642}

\leavevmode\vadjust pre{\hypertarget{ref-gelmanPosteriorPredictiveAssessment1996}{}}%
Gelman, A., Meng, X., \& Stern, H. (1996). Posterior predictive assessment of model fitness via realized discrepancies. \emph{Statistica Sinica}, 733--807.

\leavevmode\vadjust pre{\hypertarget{ref-gilbertCommentEstimatingReproducibility2016}{}}%
Gilbert, D. T., King, G., Pettigrew, S., \& Wilson, T. D. (2016). Comment on {``{Estimating} the reproducibility of psychological science.''} \emph{Science}, \emph{351}(6277), 1037--1037. \url{https://doi.org/10.1126/science.aad7243}

\leavevmode\vadjust pre{\hypertarget{ref-greenSIMRPackagePower2016}{}}%
Green, P., \& MacLeod, C. J. (2016). {SIMR}: {An R} package for power analysis of generalized linear mixed models by simulation. \emph{Methods in Ecology and Evolution}, \emph{7}(4), 493--498. \url{https://doi.org/10.1111/2041-210X.12504}

\leavevmode\vadjust pre{\hypertarget{ref-guntherLatentSemanticAnalysis2016}{}}%
Günther, F., Dudschig, C., \& Kaup, B. (2016a). Latent semantic analysis cosines as a cognitive similarity measure: {Evidence} from priming studies. \emph{Quarterly Journal of Experimental Psychology}, \emph{69}(4), 626--653. \url{https://doi.org/10.1080/17470218.2015.1038280}

\leavevmode\vadjust pre{\hypertarget{ref-guenther2016a}{}}%
Günther, F., Dudschig, C., \& Kaup, B. (2016b). Predicting lexical priming effects from distributional semantic similarities: {A} replication with extension. \emph{Frontiers in Psychology}, \emph{7}. \url{https://doi.org/10.3389/fpsyg.2016.01646}

\leavevmode\vadjust pre{\hypertarget{ref-guntherSymbolGroundingDirect2018}{}}%
Günther, F., Dudschig, C., \& Kaup, B. (2018). Symbol grounding without direct experience: Do words inherit sensorimotor activation from purely linguistic context? \emph{Cognitive Science}, \emph{42}(S2), 336--374. \url{https://doi.org/10.1111/cogs.12549}

\leavevmode\vadjust pre{\hypertarget{ref-guntherLimitsAutomaticSensorimotor2021}{}}%
Günther, F., Press, S. A., Dudschig, C., \& Kaup, B. (2021). The limits of automatic sensorimotor processing during word processing: Investigations with repeated linguistic experience, memory consolidation during sleep, and rich linguistic learning contexts. \emph{Psychological Research}. \url{https://doi.org/10.1007/s00426-021-01620-4}

\leavevmode\vadjust pre{\hypertarget{ref-haldEEGThetaGamma2006}{}}%
Hald, L. A., Bastiaansen, M. C. M., \& Hagoort, P. (2006). {EEG} theta and gamma responses to semantic violations in online sentence processing. \emph{Brain and Language}, \emph{96}(1), 90--105. \url{https://doi.org/10.1016/j.bandl.2005.06.007}

\leavevmode\vadjust pre{\hypertarget{ref-hald2013a}{}}%
Hald, L. A., Hocking, I., Vernon, D., Marshall, J. A., \& Garnham, A. (2013). Exploring modality switching effects in negated sentences: {Further} evidence for grounded representations. \emph{Frontiers in Psychology}, \emph{4}, 93. \url{https://doi.org/10.3389/fpsyg.2013.00093}

\leavevmode\vadjust pre{\hypertarget{ref-hald2011a}{}}%
Hald, L. A., Marshall, J. A., Janssen, D. P., \& Garnham, A. (2011). Switching modalities in a sentence verification task: {ERP} evidence for embodied language processing. \emph{Frontiers in Psychology}, \emph{2}, 45. \url{https://doi.org/10.3389/fpsyg.2011.00045}

\leavevmode\vadjust pre{\hypertarget{ref-harnadSymbolGroundingProblem1990}{}}%
Harnad, S. (1990). The symbol grounding problem. \emph{Physica D: Nonlinear Phenomena}, \emph{42}(1), 335--346. \url{https://doi.org/10.1016/0167-2789(90)90087-6}

\leavevmode\vadjust pre{\hypertarget{ref-harrison2018a}{}}%
Harrison, X. A., Donaldson, L., Correa-Cano, M. E., Evans, J., Fisher, D. N., Goodwin, C., Robinson, B. S., Hodgson, D. J., \& Inger, R. (2018). A brief introduction to mixed effects modelling and multi-model inference in ecology. \emph{PeerJ}, \emph{6}, 4794. \url{https://doi.org/10.7717/peerj.4794}

\leavevmode\vadjust pre{\hypertarget{ref-haukOnlyTimeWill2016}{}}%
Hauk, O. (2016). Only time will tell -- why temporal information is essential for our neuroscientific understanding of semantics. \emph{Psychonomic Bulletin \& Review}, \emph{23}(4), 1072--1079. \url{https://doi.org/10.3758/s13423-015-0873-9}

\leavevmode\vadjust pre{\hypertarget{ref-hedge2018a}{}}%
Hedge, C., Powell, G., \& Sumner, P. (2018). The reliability paradox: {Why} robust cognitive tasks do not produce reliable individual differences. \emph{Behavior Research Methods}, \emph{50}(3), 1166--1186. \url{https://doi.org/10.3758/s13428-017-0935-1}

\leavevmode\vadjust pre{\hypertarget{ref-henrich2010a}{}}%
Henrich, J., Heine, S. J., \& Norenzayan, A. (2010). The weirdest people in the world? \emph{Behavioral and Brain Sciences}, \emph{33}(2-3), 61--135. \url{https://doi.org/10.1017/S0140525X0999152X}

\leavevmode\vadjust pre{\hypertarget{ref-hoedemakerItTakesTime2014}{}}%
Hoedemaker, R. S., \& Gordon, P. C. (2014). It takes time to prime: {Semantic} priming in the ocular lexical decision task. \emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{40}(6), 2179--2197. \url{https://doi.org/10.1037/a0037677}

\leavevmode\vadjust pre{\hypertarget{ref-hoenigAbusePower2001}{}}%
Hoenig, J. M., \& Heisey, D. M. (2001). The {Abuse} of {Power}. \emph{The American Statistician}, \emph{55}(1), 19--24. \url{https://doi.org/10.1198/000313001300339897}

\leavevmode\vadjust pre{\hypertarget{ref-holt2006a}{}}%
Holt, L. E., \& Beilock, S. L. (2006). Expertise and its embodiment: {Examining} the impact of sensorimotor skill expertise on the representation of action-related text. \emph{Psychonomic Bulletin \& Review}, \emph{13}(4), 694--701. \url{https://doi.org/10.3758/BF03193983}

\leavevmode\vadjust pre{\hypertarget{ref-hultenNeuralRepresentationAbstract2021}{}}%
Hultén, A., Vliet, M. van, Kivisaari, S., Lammi, L., Lindh-Knuutila, T., Faisal, A., \& Salmelin, R. (2021). The neural representation of abstract words may arise through grounding word meaning in language itself. \emph{Human Brain Mapping}, \emph{42}(15), 4973--4984. \url{https://onlinelibrary.wiley.com/doi/abs/10.1002/hbm.25593}

\leavevmode\vadjust pre{\hypertarget{ref-hutchinson2013a}{}}%
Hutchinson, S., \& Louwerse, M. M. (2013). Language statistics and individual differences in processing primary metaphors. \emph{Cognitive Linguistics}, \emph{24}(4), 667--687. \url{https://doi.org/10.1515/cog-2013-0023}

\leavevmode\vadjust pre{\hypertarget{ref-hutchisonSemanticPrimingDue2003}{}}%
Hutchison, K. A. (2003). Is semantic priming due to association strength or feature overlap? {A} microanalytic review. \emph{Psychonomic Bulletin \& Review}, \emph{10}(4), 785--813. \url{https://doi.org/10.3758/BF03196544}

\leavevmode\vadjust pre{\hypertarget{ref-hutchisonPredictingSemanticPriming2008}{}}%
Hutchison, K. A., Balota, D. A., Cortese, M. J., \& Watson, J. M. (2008). Predicting semantic priming at the item level. \emph{Quarterly Journal of Experimental Psychology}, \emph{61}(7), 1036--1066. \url{https://doi.org/10.1080/17470210701438111}

\leavevmode\vadjust pre{\hypertarget{ref-hutchison2013a}{}}%
Hutchison, K. A., Balota, D. A., Neely, J. H., Cortese, M. J., Cohen-Shikora, E. R., Tse, C.-S., Yap, M. J., Bengson, J. J., Niemeyer, D., \& Buchanan, E. (2013). The semantic priming project. \emph{Behavior Research Methods}, \emph{45}, 1099--1114. \url{https://doi.org/10.3758/s13428-012-0304-z}

\leavevmode\vadjust pre{\hypertarget{ref-james2018a}{}}%
James, A. N., Fraundorf, S. H., Lee, E. K., \& Watson, D. G. (2018). Individual differences in syntactic processing: {Is} there evidence for reader-text interactions? \emph{Journal of Memory and Language}, \emph{102}, 155--181. \url{https://doi.org/10.1016/j.jml.2018.05.006}

\leavevmode\vadjust pre{\hypertarget{ref-jones2006a}{}}%
Jones, M. N., Kintsch, W., \& Mewhort, D. J. (2006). High-dimensional semantic space accounts of priming. \emph{Journal of Memory and Language}, \emph{55}(4), 534--552. \url{https://doi.org/10.1016/j.jml.2006.07.003}

\leavevmode\vadjust pre{\hypertarget{ref-joordensLongShortSemantic1997}{}}%
Joordens, S., \& Becker, S. (1997). The long and short of semantic priming effects in lexical decision. \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{23}(5), 1083--1105. \url{https://doi.org/10.1037/0278-7393.23.5.1083}

\leavevmode\vadjust pre{\hypertarget{ref-jung2019a}{}}%
Jung, M., Mody, M., Fujioka, T., Kimura, Y., Okazawa, H., \& Kosaka, H. (2019). Sex differences in white matter pathways related to language ability. \emph{Frontiers in Human Neuroscience}, \emph{13}, 898. \url{https://doi.org/10.3389/fnins.2019.00898}

\leavevmode\vadjust pre{\hypertarget{ref-kieferDifferentialTemporospatialPattern2022}{}}%
Kiefer, M., Pielke, L., \& Trumpp, N. M. (2022). Differential temporo-spatial pattern of electrical brain activity during the processing of abstract concepts related to mental states and verbal associations. \emph{NeuroImage}, \emph{252}, 119036. \url{https://doi.org/10.1016/j.neuroimage.2022.119036}

\leavevmode\vadjust pre{\hypertarget{ref-kiela2014a}{}}%
Kiela, D., \& Bottou, L. (2014). Learning image embeddings using convolutional neural networks for improved multi-modal semantics. \emph{Proceedings of the 2014 Conference on Empirical Methods in Natural Language Processing ({EMNLP}}, 36--45. \url{https://doi.org/10.3115/v1/D14-1005}

\leavevmode\vadjust pre{\hypertarget{ref-kimEffectsLexicalFeatures2018}{}}%
Kim, M., Crossley, S. A., \& Skalicky, S. (2018). Effects of lexical features, textual properties, and individual differences on word processing times during second language reading comprehension. \emph{Reading and Writing}, \emph{31}(5), 1155--1180. \url{https://doi.org/10.1007/s11145-018-9833-x}

\leavevmode\vadjust pre{\hypertarget{ref-kniefViolatingNormalityAssumption2021}{}}%
Knief, U., \& Forstmeier, W. (2021). Violating the normality assumption may be the lesser of two evils. \emph{Behavior Research Methods}. \url{https://doi.org/10.3758/s13428-021-01587-5}

\leavevmode\vadjust pre{\hypertarget{ref-R-robustlmm}{}}%
Koller, M. (2016). {robustlmm}: An {R} package for robust estimation of linear mixed-effects models. \emph{Journal of Statistical Software}, \emph{75}(6), 1--24. \url{https://doi.org/10.18637/jss.v075.i06}

\leavevmode\vadjust pre{\hypertarget{ref-kosIndividualVariationLate2012}{}}%
Kos, M., Van den Brink, D., \& Hagoort, P. (2012). Individual {Variation} in the {Late Positive Complex} to {Semantic Anomalies}. \emph{Frontiers in Psychology}, \emph{3}. \url{https://www.frontiersin.org/article/10.3389/fpsyg.2012.00318}

\leavevmode\vadjust pre{\hypertarget{ref-kousta2011a}{}}%
Kousta, S.-T., Vigliocco, G., Vinson, D. P., Andrews, M., \& Del Campo, E. (2011). The representation of abstract words: {Why} emotion matters. \emph{Journal of Experimental Psychology: General}, \emph{140}, 14--34. \url{https://doi.org/10.1037/a0021446}

\leavevmode\vadjust pre{\hypertarget{ref-kruschkeBayesianNewStatistics2018}{}}%
Kruschke, J. K., \& Liddell, T. M. (2018). The {Bayesian New Statistics}: {Hypothesis} testing, estimation, meta-analysis, and power analysis from a {Bayesian} perspective. \emph{Psychonomic Bulletin \& Review}, \emph{25}(1), 178--206. \url{https://doi.org/10.3758/s13423-016-1221-4}

\leavevmode\vadjust pre{\hypertarget{ref-kumar2021a}{}}%
Kumar, A. A. (2021). Semantic memory: {A} review of methods, models, and current challenges. \emph{Psychonomic Bulletin \& Review}, \emph{28}(1), 40--80. \url{https://doi.org/10.3758/s13423-020-01792-x}

\leavevmode\vadjust pre{\hypertarget{ref-kumarDistantConnectivityMultiplestep2020}{}}%
Kumar, A. A., Balota, D. A., \& Steyvers, M. (2020). Distant connectivity and multiple-step priming in large-scale semantic networks. \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{46}(12), 2261--2276. \url{https://doi.org/10.1037/xlm0000793}

\leavevmode\vadjust pre{\hypertarget{ref-kumleEstimatingPowerGeneralized2021}{}}%
Kumle, L., Võ, M. L.-H., \& Draschkow, D. (2021). Estimating power in (generalized) linear mixed models: {An} open introduction and tutorial in {R}. \emph{Behavior Research Methods}. \url{https://doi.org/10.3758/s13428-021-01546-0}

\leavevmode\vadjust pre{\hypertarget{ref-R-lmerTest}{}}%
Kuznetsova, A., Brockhoff, P. B., \& Christensen, R. H. B. (2017). {lmerTest} package: Tests in linear mixed effects models. \emph{Journal of Statistical Software}, \emph{82}(13), 1--26. \url{https://doi.org/10.18637/jss.v082.i13}

\leavevmode\vadjust pre{\hypertarget{ref-lam2015a}{}}%
Lam, K. J., Dijkstra, T., \& Rueschemeyer, S. A. (2015). Feature activation during word recognition: Action, visual, and associative-semantic priming effects. \emph{Frontiers in Psychology}, \emph{6}, 659. \url{https://doi.org/10.3389/fpsyg.2015.00659}

\leavevmode\vadjust pre{\hypertarget{ref-lamiellStatisticalThinkingPsychology2019}{}}%
Lamiell, J. T. (2019). Statistical thinking in psychology: Some needed critical perspective on what {``everyone knows.''} In J. T. Lamiell (Ed.), \emph{Psychology's {Misuse} of {Statistics} and {Persistent Dismissal} of its {Critics}} (pp. 99--121). {Springer International Publishing}. \url{https://doi.org/10.1007/978-3-030-12131-0_5}

\leavevmode\vadjust pre{\hypertarget{ref-landauerIntroductionLatentSemantic1998}{}}%
Landauer, T. K., Foltz, P. W., \& Laham, D. (1998). An introduction to latent semantic analysis. \emph{Discourse Processes}, \emph{25}(2-3), 259--284. \url{https://doi.org/10.1080/01638539809545028}

\leavevmode\vadjust pre{\hypertarget{ref-leboisAreAutomaticConceptual2015}{}}%
Lebois, L. A. M., Wilson-Mendenhall, C. D., \& Barsalou, L. W. (2015). Are automatic conceptual cores the gold standard of semantic processing? {The} context-dependence of spatial meaning in grounded congruency effects. \emph{Cognitive Science}, \emph{39}(8), 1764--1801. \url{https://doi.org/10.1111/cogs.12174}

\leavevmode\vadjust pre{\hypertarget{ref-leeBayesianCognitiveModeling2014}{}}%
Lee, M. D., \& Wagenmakers, E.-J. (2014). \emph{Bayesian cognitive modeling: {A} practical course}. {Cambridge University Press}. \url{https://doi.org/10.1017/CBO9781139087759}

\leavevmode\vadjust pre{\hypertarget{ref-lieversLinguisticDimensionsConcrete2021}{}}%
Lievers, F. S., Bolognesi, M., \& Winter, B. (2021). The linguistic dimensions of concrete and abstract concepts: Lexical category, morphological structure, countability, and etymology. \emph{Cognitive Linguistics}, \emph{32}(4), 641--670. \url{https://doi.org/10.1515/cog-2021-0007}

\leavevmode\vadjust pre{\hypertarget{ref-lim2020a}{}}%
Lim, R. Y., Yap, M. J., \& Tse, C.-S. (2020). Individual differences in cantonese chinese word recognition: {Insights} from the chinese lexicon project. \emph{Quarterly Journal of Experimental Psychology}, \emph{73}(4), 504--518. \url{https://doi.org/10.1177/1747021820906566}

\leavevmode\vadjust pre{\hypertarget{ref-loTransformNotTransform2015}{}}%
Lo, S., \& Andrews, S. (2015). To transform or not to transform: Using generalized linear mixed models to analyse reaction time data. \emph{Frontiers in Psychology}, \emph{6}. \url{https://doi.org/10.3389/fpsyg.2015.01171}

\leavevmode\vadjust pre{\hypertarget{ref-lokenMeasurementErrorReplication2017}{}}%
Loken, E., \& Gelman, A. (2017). Measurement error and the replication crisis. \emph{Science}, \emph{355}(6325), 584--585. \url{https://doi.org/10.1126/science.aal3618}

\leavevmode\vadjust pre{\hypertarget{ref-louwerseSymbolInterdependencySymbolic2011}{}}%
Louwerse, M. M. (2011). Symbol {Interdependency} in {Symbolic} and {Embodied Cognition}. \emph{Topics in Cognitive Science}, \emph{3}(2), 273--302. \url{https://doi.org/10.1111/j.1756-8765.2010.01106.x}

\leavevmode\vadjust pre{\hypertarget{ref-louwerseTasteWordsLinguistic2011}{}}%
Louwerse, M. M., \& Connell, L. (2011). A taste of words: Linguistic context and perceptual simulation predict the modality of words. \emph{Cognitive Science}, \emph{35}(2), 381--398. \url{https://doi.org/10.1111/j.1551-6709.2010.01157.x}

\leavevmode\vadjust pre{\hypertarget{ref-louwerse2015a}{}}%
Louwerse, M. M., Hutchinson, S., Tillman, R., \& Recchia, G. (2015). Effect size matters: {The} role of language statistics and perceptual simulation in conceptual processing. \emph{Language, Cognition and Neuroscience}, \emph{30}(4), 430--447. \url{https://doi.org/10.1080/23273798.2014.981552}

\leavevmode\vadjust pre{\hypertarget{ref-louwerseLanguageEncodesGeographical2009}{}}%
Louwerse, M. M., \& Zwaan, R. A. (2009). Language encodes geographical information. \emph{Cognitive Science}, \emph{33}(1), 51--73. \url{https://doi.org/10.1111/j.1551-6709.2008.01003.x}

\leavevmode\vadjust pre{\hypertarget{ref-luke2017a}{}}%
Luke, S. G. (2017). Evaluating significance in linear mixed-effects models in {R}. \emph{Behavior Research Methods}, \emph{49}(4), 1494--1502. \url{https://doi.org/10.3758/s13428-016-0809-y}

\leavevmode\vadjust pre{\hypertarget{ref-lund1996a}{}}%
Lund, K., \& Burgess, C. (1996). Producing high-dimensional semantic spaces from lexical co-occurrence. \emph{Behavior Research Methods, Instruments, \& Computers}, \emph{28}(2), 203--208. \url{https://doi.org/10.3758/BF03204766}

\leavevmode\vadjust pre{\hypertarget{ref-lund1995a}{}}%
Lund, K., Burgess, C., \& Atchley, R. A. (1995). Semantic and associative priming in high-dimensional semantic space. \emph{Proceedings of the Cognitive Science Society}, 660--665.

\leavevmode\vadjust pre{\hypertarget{ref-lynottModalityExclusivityNorms2009}{}}%
Lynott, D., \& Connell, L. (2009). Modality exclusivity norms for 423 object properties. \emph{Behavior Research Methods}, \emph{41}(2), 558--564. \url{https://doi.org/10.3758/BRM.41.2.558}

\leavevmode\vadjust pre{\hypertarget{ref-lynott2020a}{}}%
Lynott, D., Connell, L., Brysbaert, M., Brand, J., \& Carney, J. (2020). The {Lancaster Sensorimotor Norms}: {Multidimensional} measures of perceptual and action strength for 40,000 {English} words. \emph{Behavior Research Methods}, \emph{52}, 1271--1291. \url{https://doi.org/10.3758/s13428-019-01316-z}

\leavevmode\vadjust pre{\hypertarget{ref-lynottReplicationExperiencingPhysical2014}{}}%
Lynott, D., Corker, K. S., Wortman, J., Connell, L., Donnellan, M. B., Lucas, R. E., \& O'Brien, K. (2014). Replication of {``{Experiencing} physical warmth promotes interpersonal warmth''} by {Williams} and {Bargh} (2008). \emph{Social Psychology}, \emph{45}(3), 216--222. \url{https://doi.org/10.1027/1864-9335/a000187}

\leavevmode\vadjust pre{\hypertarget{ref-mahonCriticalLookEmbodied2008}{}}%
Mahon, B. Z., \& Caramazza, A. (2008). A critical look at the embodied cognition hypothesis and a new proposal for grounding conceptual content. \emph{Journal of Physiology-Paris}, \emph{102}(1), 59--70. \url{https://doi.org/10.1016/j.jphysparis.2008.03.004}

\leavevmode\vadjust pre{\hypertarget{ref-mahon2016a}{}}%
Mahon, B. Z., \& Hickok, G. (2016). Arguments about the nature of concepts: {Symbols}, embodiment, and beyond. \emph{Psychonomic Bulletin \& Review}, \emph{23}(4), 941--958. \url{https://doi.org/10.3758/s13423-016-1045-2}

\leavevmode\vadjust pre{\hypertarget{ref-majidOdorsAreExpressible2014}{}}%
Majid, A., \& Burenhult, N. (2014). Odors are expressible in language, as long as you speak the right language. \emph{Cognition}, \emph{130}(2), 266--270. \url{https://doi.org/10.1016/j.cognition.2013.11.004}

\leavevmode\vadjust pre{\hypertarget{ref-majidSensesLanguageCulture2011}{}}%
Majid, A., \& Levinson, S. C. (2011). The senses in language and culture. \emph{The Senses and Society}, \emph{6}(1), 5--18. \url{https://doi.org/10.2752/174589311X12893982233551}

\leavevmode\vadjust pre{\hypertarget{ref-majidCanNomenclatureBody2015}{}}%
Majid, A., \& van Staden, M. (2015). Can nomenclature for the body be explained by embodiment theories? \emph{Topics in Cognitive Science}, \emph{7}(4), 570--594. \url{https://doi.org/10.1111/tops.12159}

\leavevmode\vadjust pre{\hypertarget{ref-mak2019a}{}}%
Mak, M., \& Willems, R. M. (2019). Mental simulation during literary reading: {Individual} differences revealed with eye-tracking. \emph{Language, Cognition and Neuroscience}, \emph{34}(4), 511--535. \url{https://doi.org/10.1080/23273798.2018.1552007}

\leavevmode\vadjust pre{\hypertarget{ref-mandera2017a}{}}%
Mandera, P., Keuleers, E., \& Brysbaert, M. (2017). Explaining human performance in psycholinguistic tasks with models of semantic similarity based on prediction and counting: {A} review and empirical validation. \emph{Journal of Memory and Language}, \emph{92}, 57--78. \url{https://doi.org/10.1016/j.jml.2016.04.001}

\leavevmode\vadjust pre{\hypertarget{ref-marekReproducibleBrainwideAssociation2022}{}}%
Marek, S., Tervo-Clemmens, B., Calabro, F. J., Montez, D. F., Kay, B. P., Hatoum, A. S., Donohue, M. R., Foran, W., Miller, R. L., Hendrickson, T. J., Malone, S. M., Kandala, S., Feczko, E., Miranda-Dominguez, O., Graham, A. M., Earl, E. A., Perrone, A. J., Cordova, M., Doyle, O., \ldots{} Dosenbach, N. U. F. (2022). Reproducible brain-wide association studies require thousands of individuals. \emph{Nature}, 1--7. \url{https://doi.org/10.1038/s41586-022-04492-9}

\leavevmode\vadjust pre{\hypertarget{ref-matuschekBalancingTypeError2017}{}}%
Matuschek, H., Kliegl, R., Vasishth, S., Baayen, H., \& Bates, D. (2017). Balancing {Type I} error and power in linear mixed models. \emph{Journal of Memory and Language}, \emph{94}, 305--315. \url{https://doi.org/10.1016/j.jml.2017.01.001}

\leavevmode\vadjust pre{\hypertarget{ref-matzkePsychologicalInterpretationExGaussian2009}{}}%
Matzke, D., \& Wagenmakers, E.-J. (2009). Psychological interpretation of the ex-{Gaussian} and shifted {Wald} parameters: {A} diffusion model analysis. \emph{Psychonomic Bulletin \& Review}, \emph{16}(5), 798--817. \url{https://doi.org/10.3758/PBR.16.5.798}

\leavevmode\vadjust pre{\hypertarget{ref-mcdonald2002a}{}}%
McDonald, S., \& Brew, C. (2002). A distributional model of semantic context effects in lexical processing. \emph{Proceedings of the 42nd Annual Meeting on Association for Computational Linguistics}, 17--24. \url{http://dblp.uni-trier.de/db/conf/acl/acl2004.html\#McDonaldB04}

\leavevmode\vadjust pre{\hypertarget{ref-mendesPervasiveEffectWord2021}{}}%
Mendes, P. S., \& Undorf, M. (2021). On the pervasive effect of word frequency in metamemory. \emph{Quarterly Journal of Experimental Psychology}, 17470218211053329. \url{https://doi.org/10.1177/17470218211053329}

\leavevmode\vadjust pre{\hypertarget{ref-miceliDifferencesRelatedAging2022}{}}%
Miceli, A., Wauthia, E., Lefebvre, L., Vallet, G. T., Ris, L., \& Loureiro, I. S. (2022). Differences related to aging in sensorimotor knowledge: {Investigation} of perceptual strength and body object interaction. \emph{Archives of Gerontology and Geriatrics}, \emph{102}, 104715. \url{https://doi.org/10.1016/j.archger.2022.104715}

\leavevmode\vadjust pre{\hypertarget{ref-mikolovEfficientEstimationWord2013}{}}%
Mikolov, T., Chen, K., Corrado, G., \& Dean, J. (2013). \emph{Efficient estimation of word representations in vector space} (Version 3). {arXiv}. \url{https://doi.org/10.48550/arXiv.1301.3781}

\leavevmode\vadjust pre{\hypertarget{ref-milekEavesdroppingHappinessRevisited2018}{}}%
Milek, A., Butler, E. A., Tackman, A. M., Kaplan, D. M., Raison, C. L., Sbarra, D. A., Vazire, S., \& Mehl, M. R. (2018). {``{Eavesdropping} on happiness''} revisited: {A} pooled, multisample replication of the association between life satisfaction and observed daily conversation quantity and quality. \emph{Psychological Science}, \emph{29}(9), 1451--1462. \url{https://doi.org/10.1177/0956797618774252}

\leavevmode\vadjust pre{\hypertarget{ref-milton2021a}{}}%
Milton, F., Fulford, J., Dance, C., Gaddum, J., Heuerman-Williamson, B., Jones, K., Knight, K. F., MacKisack, M., Winlove, C., \& Zeman, A. (2021). Behavioral and neural signatures of visual imagery vividness extremes: Aphantasia versus hyperphantasia. \emph{Cerebral Cortex Communications}, \emph{2}(2), 035. \url{https://doi.org/10.1093/texcom/tgab035}

\leavevmode\vadjust pre{\hypertarget{ref-montero-melisConsistencyMotionEvent2021}{}}%
Montero-Melis, G. (2021). Consistency in motion event encoding across languages. \emph{Frontiers in Psychology}, \emph{12}(625153). \url{https://doi.org/10.3389/fpsyg.2021.625153}

\leavevmode\vadjust pre{\hypertarget{ref-montero-melisSatelliteVsVerbframing2017}{}}%
Montero-Melis, G., Eisenbeiss, S., Narasimhan, B., Ibarretxe-Antuñano, I., Kita, S., Kopecka, A., Lüpke, F., Nikitina, T., Tragel, I., Jaeger, T. F., \& Bohnemeyer, J. (2017). Satellite- vs. Verb-framing underpredicts nonverbal motion categorization: Insights from a large language sample and simulations. \emph{Cognitive Semantics}, \emph{3}(1), 36--61. \url{https://doi.org/10.1163/23526416-00301002}

\leavevmode\vadjust pre{\hypertarget{ref-montero-melisNoEvidenceEmbodiment2022}{}}%
Montero-Melis, G., van Paridon, J., Ostarek, M., \& Bylund, E. (2022). No evidence for embodiment: {The} motor system is not needed to keep action verbs in working memory. \emph{Cortex}, \emph{150}, 108--125. \url{https://doi.org/10.1016/j.cortex.2022.02.006}

\leavevmode\vadjust pre{\hypertarget{ref-moranPosteriorPredictiveNull2021}{}}%
Moran, G. E., Cunningham, J. P., \& Blei, D. M. (2021). \emph{Posterior predictive null checks} (No. arXiv:2112.03333). {arXiv}. \url{https://doi.org/10.48550/arXiv.2112.03333}

\leavevmode\vadjust pre{\hypertarget{ref-nakagawaCoefficientDeterminationR22017}{}}%
Nakagawa, S., Johnson, P. C. D., \& Schielzeth, H. (2017). The coefficient of determination {\emph{R}}{\textsuperscript{2}} and intra-class correlation coefficient from generalized linear mixed-effects models revisited and expanded. \emph{Journal of The Royal Society Interface}, \emph{14}(134), 20170213. \url{https://doi.org/10.1098/rsif.2017.0213}

\leavevmode\vadjust pre{\hypertarget{ref-negriWhatRoleMotor2007}{}}%
Negri, G. A. L., Rumiati, R. I., Zadini, A., Ukmar, M., Mahon, B. Z., \& Caramazza, A. (2007). What is the role of motor simulation in action and object recognition? {Evidence} from apraxia. \emph{Cognitive Neuropsychology}, \emph{24}(8), 795--816. \url{https://doi.org/10.1080/02643290701707412}

\leavevmode\vadjust pre{\hypertarget{ref-newcombeEffectsEmotionalSensorimotor2012}{}}%
Newcombe, P., Campbell, C., Siakaluk, P., \& Pexman, P. (2012). Effects of emotional and sensorimotor knowledge in semantic processing of concrete and abstract nouns. \emph{Frontiers in Human Neuroscience}, \emph{6}. \url{https://www.frontiersin.org/article/10.3389/fnhum.2012.00275}

\leavevmode\vadjust pre{\hypertarget{ref-opensciencecollaborationEstimatingReproducibilityPsychological2015}{}}%
Open Science Collaboration. (2015). Estimating the reproducibility of psychological science. \emph{Science}, \emph{349}(6251), aac4716. \url{https://doi.org/10.1126/science.aac4716}

\leavevmode\vadjust pre{\hypertarget{ref-ostarekStrongInferenceResearch2021}{}}%
Ostarek, M., \& Bottini, R. (2021). Towards strong inference in research on embodiment -- {Possibilities} and limitations of causal paradigms. \emph{Journal of Cognition}, \emph{4}(1), 5. \url{https://doi.org/10.5334/joc.139}

\leavevmode\vadjust pre{\hypertarget{ref-ostarekTaskdependentCausalRole2017}{}}%
Ostarek, M., \& Huettig, F. (2017). A task-dependent causal role for low-level visual processes in spoken word comprehension. \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{43}(8), 1215--1224. \url{https://doi.org/10.1037/xlm0000375}

\leavevmode\vadjust pre{\hypertarget{ref-ostarekSixChallengesEmbodiment2019}{}}%
Ostarek, M., \& Huettig, F. (2019). Six challenges for embodiment research. \emph{Current Directions in Psychological Science}, \emph{28}(6), 593--599. \url{https://doi.org/10.1177/0963721419866441}

\leavevmode\vadjust pre{\hypertarget{ref-paciniExocentricCodingMapping2021}{}}%
Pacini, A. M., \& Barnard, P. J. (2021). Exocentric coding of the mapping between valence and regions of space: {Implications} for embodied cognition. \emph{Acta Psychologica}, \emph{214}, 103264. \url{https://doi.org/10.1016/j.actpsy.2021.103264}

\leavevmode\vadjust pre{\hypertarget{ref-pad2007a}{}}%
Padó, S., \& Lapata, M. (2007). Dependency-based construction of semantic space models. \emph{Computational Linguistics}, \emph{33}(2), 161--199. \url{https://doi.org/10.1162/coli.2007.33.2.161}

\leavevmode\vadjust pre{\hypertarget{ref-paivioMentalRepresentationsDual1990}{}}%
Paivio, A. (1990). \emph{Mental representations: A dual coding approach}. {Oxford University Press}. \url{https://doi.org/10.1093/acprof:oso/9780195066661.001.0001}

\leavevmode\vadjust pre{\hypertarget{ref-papeoActionPerformanceActionword2010}{}}%
Papeo, L., Negri, G. A. L., Zadini, A., \& Ida Rumiati, R. (2010). Action performance and action-word understanding: {Evidence} of double dissociations in left-damaged patients. \emph{Cognitive Neuropsychology}, \emph{27}(5), 428--461. \url{https://doi.org/10.1080/02643294.2011.570326}

\leavevmode\vadjust pre{\hypertarget{ref-pearsonHeterogeneityMentalRepresentation2015}{}}%
Pearson, J., \& Kosslyn, S. M. (2015). The heterogeneity of mental representation: {Ending} the imagery debate. \emph{Proceedings of the National Academy of Sciences}, \emph{112}(33), 10089--10092. \url{https://doi.org/10.1073/pnas.1504933112}

\leavevmode\vadjust pre{\hypertarget{ref-pecherVerifyingDifferentmodalityProperties2003}{}}%
Pecher, D., Zeelenberg, R., \& Barsalou, L. W. (2003). Verifying different-modality properties for concepts produces switching costs. \emph{Psychological Science}, \emph{14}(2), 119--124. \url{https://doi.org/10.1111/1467-9280.t01-1-01429}

\leavevmode\vadjust pre{\hypertarget{ref-pecherDoesPizzaPrime1998}{}}%
Pecher, D., Zeelenberg, R., \& Raaijmakers, J. G. W. (1998). Does pizza prime coin? {Perceptual} priming in lexical decision and pronunciation. \emph{Journal of Memory and Language}, \emph{38}(4), 401--418. \url{https://doi.org/10.1006/jmla.1997.2557}

\leavevmode\vadjust pre{\hypertarget{ref-petilli2021a}{}}%
Petilli, M. A., Günther, F., Vergallito, A., Ciapparelli, M., \& Marelli, M. (2021). Data-driven computational models reveal perceptual simulation in word processing. \emph{Journal of Memory and Language}, \emph{117}, 104194. \url{https://doi.org/10.1016/j.jml.2020.104194}

\leavevmode\vadjust pre{\hypertarget{ref-pexman2017a}{}}%
Pexman, P. M., Heard, A., Lloyd, E., \& Yap, M. J. (2017). The {Calgary} semantic decision project: {Concrete}/abstract decision data for 10,000 {English} words. \emph{Behavior Research Methods}, \emph{49}(2), 407--417. \url{https://doi.org/10.3758/s13428-016-0720-6}

\leavevmode\vadjust pre{\hypertarget{ref-pexman2018a}{}}%
Pexman, P. M., \& Yap, M. J. (2018). Individual differences in semantic processing: {Insights} from the {Calgary} semantic decision project. \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{44}(7), 1091--1112. \url{https://doi.org/10.1037/xlm0000499}

\leavevmode\vadjust pre{\hypertarget{ref-ponari2018a}{}}%
Ponari, M., Norbury, C. F., Rotaru, A., Lenci, A., \& Vigliocco, G. (2018). Learning abstract words and concepts: {Insights} from developmental language disorder. \emph{Philosophical Transactions of the Royal Society B: Biological Sciences}, \emph{373}, 20170140. \url{https://doi.org/10.1098/rstb.2017.0140}

\leavevmode\vadjust pre{\hypertarget{ref-ponariRoleEmotionalValence2020}{}}%
Ponari, M., Norbury, C. F., \& Vigliocco, G. (2020). The role of emotional valence in learning novel abstract concepts. \emph{Developmental Psychology}, \emph{56}(10), 1855--1865. \url{https://doi.org/10.1037/dev0001091}

\leavevmode\vadjust pre{\hypertarget{ref-ponari2018b}{}}%
Ponari, M., Norbury, C. F., \& Vigliocco, G. (2018). Acquisition of abstract concepts is influenced by emotional valence. \emph{Developmental Science}, \emph{21}(2), 12549. \url{https://doi.org/10.1111/desc.12549}

\leavevmode\vadjust pre{\hypertarget{ref-preglaVariabilitySentenceComprehension2021}{}}%
Pregla, D., Lissón, P., Vasishth, S., Burchert, F., \& Stadie, N. (2021). Variability in sentence comprehension in aphasia in {German}. \emph{Brain and Language}, \emph{222}, 105008. \url{https://doi.org/10.1016/j.bandl.2021.105008}

\leavevmode\vadjust pre{\hypertarget{ref-pulvermullerHowNeuronsMake2013}{}}%
Pulvermüller, F. (2013). How neurons make meaning: {Brain} mechanisms for embodied and abstract-symbolic semantics. \emph{Trends in Cognitive Sciences}, \emph{17}(9), 458--470. \url{https://doi.org/10.1016/j.tics.2013.06.004}

\leavevmode\vadjust pre{\hypertarget{ref-pylyshynWhatMindEye1973}{}}%
Pylyshyn, Z. W. (1973). What the mind's eye tells the mind's brain: {A} critique of mental imagery. \emph{Psychological Bulletin}, \emph{80}(1), 1--24. \url{https://doi.org/10.1037/h0034650}

\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
R Core Team. (2021). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}

\leavevmode\vadjust pre{\hypertarget{ref-rajanandaRandomdotKinematogramWebbased2018}{}}%
Rajananda, S., Lau, H., \& Odegaard, B. (2018). A random-dot kinematogram for web-based vision research. \emph{Journal of Open Research Software}, \emph{6}(1, 1), 6. \url{https://doi.org/10.5334/jors.194}

\leavevmode\vadjust pre{\hypertarget{ref-ratcliff2010a}{}}%
Ratcliff, R., Thapar, A., \& McKoon, G. (2010). Individual differences, aging, and {IQ} in two-choice tasks. \emph{Cognitive Psychology}, \emph{60}, 127--157. \url{https://doi.org/10.1016/j.cogpsych.2009.09.001}

\leavevmode\vadjust pre{\hypertarget{ref-regginDevelopmentAbstractWord2021}{}}%
Reggin, L. D., Muraki, E. J., \& Pexman, P. M. (2021). Development of abstract word knowledge. \emph{Frontiers in Psychology}, \emph{12}, 2115. \url{https://doi.org/10.3389/fpsyg.2021.686478}

\leavevmode\vadjust pre{\hypertarget{ref-reillyEnglishLexiconMirrors2020}{}}%
Reilly, J., Flurie, M., \& Peelle, J. E. (2020). The {English} lexicon mirrors functional brain activation for a sensory hierarchy dominated by vision and audition: {Point-counterpoint}. \emph{Journal of Neurolinguistics}, \emph{55}, 100895. \url{https://doi.org/10.1016/j.jneuroling.2020.100895}

\leavevmode\vadjust pre{\hypertarget{ref-riccardiDissociatingActionAbstract2019}{}}%
Riccardi, N., Yourganov, G., Rorden, C., Fridriksson, J., \& Desai, R. H. (2019). Dissociating action and abstract verb comprehension post-stroke. \emph{Cortex}, \emph{120}, 131--146. \url{https://doi.org/10.1016/j.cortex.2019.05.013}

\leavevmode\vadjust pre{\hypertarget{ref-rodriguez-ferreiroSemanticPrimingSchizotypal2020}{}}%
Rodríguez-Ferreiro, J., Aguilera, M., \& Davies, R. (2020). Semantic priming and schizotypal personality: Reassessing the link between thought disorder and enhanced spreading of semantic activation. \emph{PeerJ}, \emph{8}, e9511. \url{https://doi.org/10.7717/peerj.9511}

\leavevmode\vadjust pre{\hypertarget{ref-rouderPsychometricsIndividualDifferences2019}{}}%
Rouder, J. N., \& Haaf, J. M. (2019). A psychometrics of individual differences in experimental tasks. \emph{Psychonomic Bulletin \& Review}, \emph{26}(2), 452--467. \url{https://doi.org/10.3758/s13423-018-1558-y}

\leavevmode\vadjust pre{\hypertarget{ref-rouderBayesianInferencePsychology2018}{}}%
Rouder, J. N., Haaf, J. M., \& Vandekerckhove, J. (2018). Bayesian inference for psychology, part {IV}: {Parameter} estimation and {Bayes} factors. \emph{Psychonomic Bulletin \& Review}, \emph{25}(1), 102--113. \url{https://doi.org/10.3758/s13423-017-1420-7}

\leavevmode\vadjust pre{\hypertarget{ref-santosPropertyGenerationReflects2011}{}}%
Santos, A., Chaigneau, S. E., Simmons, W. K., \& Barsalou, L. W. (2011). Property generation reflects word association and situated simulation. \emph{Language and Cognition}, \emph{3}(1), 83--119. \url{https://doi.org/10.1515/langcog.2011.004}

\leavevmode\vadjust pre{\hypertarget{ref-sassenhagenCommonMisapplicationStatistical2016}{}}%
Sassenhagen, J., \& Alday, P. M. (2016). A common misapplication of statistical inference: {Nuisance} control with null-hypothesis significance tests. \emph{Brain and Language}, \emph{162}, 42--45. \url{https://doi.org/10.1016/j.bandl.2016.08.001}

\leavevmode\vadjust pre{\hypertarget{ref-satoTaskRelatedModulation2008}{}}%
Sato, M., Mengarelli, M., Riggio, L., Gallese, V., \& Buccino, G. (2008). Task related modulation of the motor system during language processing. \emph{Brain and Language}, \emph{105}(2), 83--90. \url{https://doi.org/10.1016/j.bandl.2007.10.001}

\leavevmode\vadjust pre{\hypertarget{ref-schielzethRobustnessLinearMixed2020}{}}%
Schielzeth, H., Dingemanse, N. J., Nakagawa, S., Westneat, D. F., Allegue, H., Teplitsky, C., Réale, D., Dochtermann, N. A., Garamszegi, L. Z., \& Araya‐Ajoy, Y. G. (2020). Robustness of linear mixed‐effects models to violations of distributional assumptions. \emph{Methods in Ecology and Evolution}, \emph{11}(9), 1141--1152. \url{https://doi.org/10.1111/2041-210X.13434}

\leavevmode\vadjust pre{\hypertarget{ref-schmalzWhatBayesFactor2021}{}}%
Schmalz, X., Biurrun Manresa, J., \& Zhang, L. (2021). What is a {Bayes} factor? \emph{Psychological Methods}. \url{https://doi.org/10.1037/met0000421}

\leavevmode\vadjust pre{\hypertarget{ref-schmidtke2018a}{}}%
Schmidtke, D., Van Dyke, J. A., \& Kuperman, V. (2018). Individual variability in the semantic processing of {English} compound words. \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{44}(3), 421--439. \url{https://doi.org/10.1037/xlm0000442}

\leavevmode\vadjust pre{\hypertarget{ref-schootBayesianStatisticsModelling2021}{}}%
Schoot, R. van de, Depaoli, S., Gelman, A., King, R., Kramer, B., Märtens, K., Tadesse, M. G., Vannucci, M., Willemsen, J., \& Yau, C. (2021). Bayesian statistics and modelling. \emph{Nature Reviews Methods Primers}, \emph{1}, 3. \url{https://doi.org/10.1038/s43586-020-00003-0}

\leavevmode\vadjust pre{\hypertarget{ref-schreuderEffectsPerceptualConceptual1984}{}}%
Schreuder, R., Flores d'Arcais, G. B., \& Glazenborg, G. (1984). Effects of perceptual and conceptual similarity in semantic priming. \emph{Psychological Research}, \emph{45}(4), 339--354. \url{https://doi.org/10.1007/BF00309710}

\leavevmode\vadjust pre{\hypertarget{ref-shebaniWhatImpairedSpatial2021}{}}%
Shebani, Z., Nestor, P. J., \& Pulvermüller, F. (2021). What's {``up''}? {Impaired} spatial preposition processing in posterior cortical atrophy. \emph{Frontiers in Human Neuroscience}, \emph{15}, 718. \url{https://doi.org/10.3389/fnhum.2021.731104}

\leavevmode\vadjust pre{\hypertarget{ref-shebaniFlexibilityLanguageAction2018}{}}%
Shebani, Z., \& Pulvermüller, F. (2018). Flexibility in {Language Action Interaction}: {The Influence} of {Movement Type}. \emph{Frontiers in Human Neuroscience}, \emph{12}. \url{https://www.frontiersin.org/article/10.3389/fnhum.2018.00252}

\leavevmode\vadjust pre{\hypertarget{ref-R-afex}{}}%
Singmann, H., Bolker, B., Westfall, J., Aust, F., \& Ben-Shachar, M. S. (2021). \emph{{afex}: Analysis of factorial experiments}. \url{https://CRAN.R-project.org/package=afex}

\leavevmode\vadjust pre{\hypertarget{ref-singmann2019a}{}}%
Singmann, H., \& Kellen, D. (2019). An introduction to mixed models for experimental psychology. In D. H. Spieler \& E. Schumacher (Eds.), \emph{New methods in cognitive psychology} (pp. 4--31). {Psychology Press}.

\leavevmode\vadjust pre{\hypertarget{ref-sleegersPupillometryHindsightBias2021}{}}%
Sleegers, W. W. A., Proulx, T., \& van Beest, I. (2021). Pupillometry and hindsight bias: Physiological arousal predicts compensatory behavior. \emph{Social Psychological and Personality Science}, \emph{12}(7), 1146--1154. \url{https://doi.org/10.1177/1948550620966153}

\leavevmode\vadjust pre{\hypertarget{ref-snefjella2020a}{}}%
Snefjella, B., \& Blank, I. (2020). \emph{Semantic norm extrapolation is a missing data problem}. {PsyArXiv}. \url{https://doi.org/10.31234/osf.io/y2gav}

\leavevmode\vadjust pre{\hypertarget{ref-solovyevConcretenessAbstractnessConcept2021}{}}%
Solovyev, V. (2021). Concreteness/abstractness concept: State of the art. In B. M. Velichkovsky, P. M. Balaban, \& V. L. Ushakov (Eds.), \emph{Advances in {Cognitive Research}, {Artificial Intelligence} and {Neuroinformatics}} (pp. 275--283). {Springer International Publishing}. \url{https://doi.org/10.1007/978-3-030-71637-0_33}

\leavevmode\vadjust pre{\hypertarget{ref-speedImpairedComprehensionSpeed2017}{}}%
Speed, L. J., van Dam, W. O., Hirath, P., Vigliocco, G., \& Desai, R. H. (2017). Impaired comprehension of speed verbs in parkinson's disease. \emph{Journal of the International Neuropsychological Society}, \emph{23}(5), 412--420. \url{https://doi.org/10.1017/S1355617717000248}

\leavevmode\vadjust pre{\hypertarget{ref-stasenkoWhenConceptsLose2014}{}}%
Stasenko, A., Garcea, F. E., Dombovy, M., \& Mahon, B. Z. (2014). When concepts lose their color: {A} case of object-color knowledge impairment. \emph{Cortex}, \emph{58}, 217--238. \url{https://doi.org/10.1016/j.cortex.2014.05.013}

\leavevmode\vadjust pre{\hypertarget{ref-stoneEffectDecayLexical2020}{}}%
Stone, K., Malsburg, T. von der, \& Vasishth, S. (2020). The effect of decay and lexical uncertainty on processing long-distance dependencies in reading. \emph{PeerJ}, \emph{8}, e10438. \url{https://doi.org/10.7717/peerj.10438}

\leavevmode\vadjust pre{\hypertarget{ref-stoneInteractionGrammaticallyDistinct2021}{}}%
Stone, K., Veríssimo, J., Schad, D. J., Oltrogge, E., Vasishth, S., \& Lago, S. (2021). The interaction of grammatically distinct agreement dependencies in predictive processing. \emph{Language, Cognition and Neuroscience}, \emph{36}(9), 1159--1179. \url{https://doi.org/10.1080/23273798.2021.1921816}

\leavevmode\vadjust pre{\hypertarget{ref-suarezObservingNeighborhoodEffects2011}{}}%
Suárez, L., Tan, S. H., Yap, M. J., \& Goh, W. D. (2011). Observing neighborhood effects without neighbors. \emph{Psychonomic Bulletin \& Review}, \emph{18}(3), 605--611. \url{https://doi.org/10.3758/s13423-011-0078-9}

\leavevmode\vadjust pre{\hypertarget{ref-tendeiroReviewIssuesNull2019}{}}%
Tendeiro, J. N., \& Kiers, H. A. L. (2019). A review of issues about null hypothesis {Bayesian} testing. \emph{Psychological Methods}, \emph{24}(6), 774--795. \url{https://doi.org/10.1037/met0000221}

\leavevmode\vadjust pre{\hypertarget{ref-tendeiroOnTheWhite2022}{}}%
Tendeiro, J. N., \& Kiers, H. A. L. (in press). On the white, the black, and the many shades of gray in between: {Our} reply to van {Ravenzwaaij} and {Wagenmakers} (2021). \emph{Psychological Methods}.

\leavevmode\vadjust pre{\hypertarget{ref-tillmanHowSharpOccam2015}{}}%
Tillman, R., Hutchinson, S., \& Louwerse, M. M. (2015). How sharp is {Occam}'s razor? {Language} statistics in cognitive processing. In D. C. Noelle, R. Dale, A. S. Warlaumont, J. Yoshimi, T. Matlock, C. D. Jennings, \& P. P. Maglio (Eds.), \emph{Proceedings of the 37th {Annual Conference} of the {Cognitive Science Society}} (pp. 2404--2409). {Cognitive Science Society}. \url{https://cogsci.mindmodeling.org/2015/papers/0413/paper0413.pdf}

\leavevmode\vadjust pre{\hypertarget{ref-trocheDefiningConceptualTopography2017}{}}%
Troche, J., Crutch, S. J., \& Reilly, J. (2017). Defining a conceptual topography of word concreteness: {Clustering} properties of emotion, sensation, and magnitude among 750 english words. \emph{Frontiers in Psychology}, \emph{8}, 1787. \url{https://doi.org/10.3389/fpsyg.2017.01787}

\leavevmode\vadjust pre{\hypertarget{ref-trumppMaskedPrimingConceptual2013}{}}%
Trumpp, N. M., Traub, F., \& Kiefer, M. (2013). Masked priming of conceptual features reveals differential brain activation during unconscious access to conceptual action and sound information. \emph{PLOS ONE}, \emph{8}(5), e65910. \url{https://doi.org/10.1371/journal.pone.0065910}

\leavevmode\vadjust pre{\hypertarget{ref-tverskyBeliefLawSmall1971}{}}%
Tversky, A., \& Kahneman, D. (1971). Belief in the law of small numbers. \emph{Psychological Bulletin}, \emph{76}(2), 105--110. \url{https://doi.org/10.1037/h0031322}

\leavevmode\vadjust pre{\hypertarget{ref-ullman2008a}{}}%
Ullman, M. T., Miranda, R. A., \& Travers, M. L. (2008). Sex differences in the neurocognition of language. In J. B. Becker, K. J. Berkley, N. Geary, E. Hampson, J. Herman, \& E. Young (Eds.), \emph{Sex on the brain: {From} genes to behavior} (pp. 291--309). {Oxford University Press}.

\leavevmode\vadjust pre{\hypertarget{ref-uttlNorthAmericanAdult2002}{}}%
Uttl, B. (2002). North {American Adult Reading Test}: {Age} norms, reliability, and validity. \emph{Journal of Clinical and Experimental Neuropsychology}, \emph{24}(8), 1123--1137. \url{https://doi.org/10.1076/jcen.24.8.1123.8375}

\leavevmode\vadjust pre{\hypertarget{ref-vanravenzwaaijAdvantagesMasqueradingIssues2021}{}}%
van Ravenzwaaij, D., \& Wagenmakers, E.-J. (2021). Advantages masquerading as {``issues''} in {Bayesian} hypothesis testing: {A} commentary on {Tendeiro} and {Kiers} (2019). \emph{Psychological Methods}. \url{https://doi.org/10.1037/met0000415}

\leavevmode\vadjust pre{\hypertarget{ref-vannuscorpsPersistentSparingAction2016}{}}%
Vannuscorps, G., Dricot, L., \& Pillon, A. (2016). Persistent sparing of action conceptual processing in spite of increasing disorders of action production: {A} case against motor embodiment of action concepts. \emph{Cognitive Neuropsychology}, \emph{33}(3-4), 191--219. \url{https://doi.org/10.1080/02643294.2016.1186615}

\leavevmode\vadjust pre{\hypertarget{ref-vasishthHowEmbraceVariation2021}{}}%
Vasishth, S., \& Gelman, A. (2021). How to embrace variation and accept uncertainty in linguistic and psycholinguistic data analysis. \emph{Linguistics}, \emph{59}(5), 1311--1342. \url{https://doi.org/10.1515/ling-2019-0051}

\leavevmode\vadjust pre{\hypertarget{ref-vasishthStatisticalSignificanceFilter2018}{}}%
Vasishth, S., Mertzen, D., Jäger, L. A., \& Gelman, A. (2018). The statistical significance filter leads to overoptimistic expectations of replicability. \emph{Journal of Memory and Language}, \emph{103}, 151--175. \url{https://doi.org/10.1016/j.jml.2018.07.004}

\leavevmode\vadjust pre{\hypertarget{ref-vehtariRanknormalizationFoldingLocalization2021}{}}%
Vehtari, A., Gelman, A., Simpson, D., Carpenter, B., \& Burkner, P.-C. (2021). Rank-normalization, folding, and localization: {An} improved {R-hat} for assessing convergence of {MCMC}. \emph{Bayesian Analysis}, \emph{16}(2), 667--718. \url{https://doi.org/10.1214/20-BA1221}

\leavevmode\vadjust pre{\hypertarget{ref-versaceImpactEmbodiedSimulation2021}{}}%
Versace, R., Bailloud, N., Magnan, A., \& Ecalle, J. (2021). The impact of embodied simulation in vocabulary learning. \emph{The Mental Lexicon}, \emph{16}(1), 2--22. \url{https://doi.org/10.1075/ml.20011.ver}

\leavevmode\vadjust pre{\hypertarget{ref-vigliocco2014a}{}}%
Vigliocco, G., Kousta, S.-T., Della Rosa, P. A., Vinson, D. P., Tettamanti, M., Devlin, J. T., \& Cappa, S. F. (2014). The neural representation of abstract words: The role of emotion. \emph{Cerebral Cortex}, \emph{7}(24), 1767--1777. \url{https://doi.org/10.1093/cercor/bht025}

\leavevmode\vadjust pre{\hypertarget{ref-villalongaPerceptualTimingPrecision2021}{}}%
Villalonga, M. B., Sussman, R. F., \& Sekuler, R. (2021). Perceptual timing precision with vibrotactile, auditory, and multisensory stimuli. \emph{Attention, Perception, \& Psychophysics}, \emph{83}(5), 2267--2280. \url{https://doi.org/10.3758/s13414-021-02254-9}

\leavevmode\vadjust pre{\hypertarget{ref-vitaleNeuralInhibitionNetwork2021}{}}%
Vitale, F., Monti, I., Padrón, I., Avenanti, A., \& de Vega, M. (2021). The neural inhibition network is causally involved in the disembodiment effect of linguistic negation. \emph{Cortex}. \url{https://doi.org/10.1016/j.cortex.2021.11.015}

\leavevmode\vadjust pre{\hypertarget{ref-vondermalsburgFalsePositivesOther2017}{}}%
von der Malsburg, T., \& Angele, B. (2017). False positives and other statistical errors in standard analyses of eye movements in reading. \emph{Journal of Memory and Language}, \emph{94}, 119--133. \url{https://doi.org/10.1016/j.jml.2016.10.003}

\leavevmode\vadjust pre{\hypertarget{ref-vukovicPrimaryMotorCortex2017}{}}%
Vukovic, N., Feurra, M., Shpektor, A., Myachykov, A., \& Shtyrov, Y. (2017). Primary motor cortex functionally contributes to language comprehension: {An} online {rTMS} study. \emph{Neuropsychologia}, \emph{96}, 222--229. \url{https://doi.org/10.1016/j.neuropsychologia.2017.01.025}

\leavevmode\vadjust pre{\hypertarget{ref-vukovic2015a}{}}%
Vukovic, N., \& Williams, J. N. (2015). Individual differences in spatial cognition influence mental simulation of language. \emph{Cognition}, \emph{142}, 110--122. \url{https://doi.org/10.1016/j.cognition.2015.05.017}

\leavevmode\vadjust pre{\hypertarget{ref-wagenmakersOneStatisticalAnalysis2022}{}}%
Wagenmakers, E.-J., Sarafoglou, A., \& Aczel, B. (2022). One statistical analysis must not rule them all. \emph{Nature}, \emph{605}(7910), 423--425. \url{https://doi.org/10.1038/d41586-022-01332-8}

\leavevmode\vadjust pre{\hypertarget{ref-wallentinChapterGenderDifferences2020}{}}%
Wallentin, M. (2020). Chapter 6 - {Gender} differences in language are small but matter for disorders. In R. Lanzenberger, G. S. Kranz, \& I. Savic (Eds.), \emph{Handbook of {Clinical Neurology}} (Vol. 175, pp. 81--102). {Elsevier}. \url{https://doi.org/10.1016/B978-0-444-64123-6.00007-2}

\leavevmode\vadjust pre{\hypertarget{ref-wangNeuralRepresentationAbstract2010}{}}%
Wang, J., Conder, J. A., Blitzer, D. N., \& Shinkareva, S. V. (2010). Neural representation of abstract and concrete concepts: {A} meta-analysis of neuroimaging studies. \emph{Human Brain Mapping}, \emph{31}(10), 1459--1468. \url{https://doi.org/10.1002/hbm.20950}

\leavevmode\vadjust pre{\hypertarget{ref-wangSocialEmotionDimensional2021}{}}%
Wang, X., Li, G., Zhao, G., Li, Y., Wang, B., Lin, C.-P., Liu, X., \& Bi, Y. (2021). Social and emotion dimensional organizations in the abstract semantic space: The neuropsychological evidence. \emph{Scientific Reports}, \emph{11}(1, 1), 23572. \url{https://doi.org/10.1038/s41598-021-02824-9}

\leavevmode\vadjust pre{\hypertarget{ref-willemsFlexibilityEmbodiedLanguage2011}{}}%
Willems, R. M., \& Casasanto, D. (2011). Flexibility in {Embodied Language Understanding}. \emph{Frontiers in Psychology}, \emph{0}. \url{https://doi.org/10.3389/fpsyg.2011.00116}

\leavevmode\vadjust pre{\hypertarget{ref-williamsImprovingPsychologicalScience2014}{}}%
Williams, L. E. (2014). Improving psychological science requires theory, data, and caution: {Reflections} on {Lynott} et al. (2014). \emph{Social Psychology}, \emph{45}(4), 321--323.

\leavevmode\vadjust pre{\hypertarget{ref-wingfieldUnderstandingRoleLinguistic2022}{}}%
Wingfield, C., \& Connell, L. (2022). Understanding the role of linguistic distributional knowledge in cognition. \emph{Language, Cognition and Neuroscience}, 1--51. \url{https://doi.org/10.1080/23273798.2022.2069278}

\leavevmode\vadjust pre{\hypertarget{ref-winterVisionDominatesPerceptual2018}{}}%
Winter, B., Perlman, M., \& Majid, A. (2018). Vision dominates in perceptual language: {English} sensory vocabulary is optimized for usage. \emph{Cognition}, \emph{179}, 213--220. \url{https://doi.org/10.1016/j.cognition.2018.05.008}

\leavevmode\vadjust pre{\hypertarget{ref-woodcockWoodcockJohnsonIII2001}{}}%
Woodcock, R. W., McGrew, K. S., \& Mather, N. (2001). \emph{Woodcock {Johnson III} tests of cognitive abilities}. {Riverside Publishing}.

\leavevmode\vadjust pre{\hypertarget{ref-yap2012a}{}}%
Yap, M. J., Balota, D. A., Sibley, D. E., \& Ratcliff, R. (2012). Individual differences in visual word recognition: {Insights} from the {English Lexicon Project}. \emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{38, 1}, 53--79. \url{https://doi.org/10.1037/a0024177}

\leavevmode\vadjust pre{\hypertarget{ref-yapAdditiveInteractiveEffects2013}{}}%
Yap, M. J., Balota, D. A., \& Tan, S. E. (2013). Additive and interactive effects in semantic priming: {Isolating} lexical and decision processes in the lexical decision task. \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{39}(1), 140--158. \url{https://doi.org/10.1037/a0028520}

\leavevmode\vadjust pre{\hypertarget{ref-yap2017a}{}}%
Yap, M. J., Hutchison, K. A., \& Tan, L. C. (2017). Individual differences in semantic priming performance: {Insights} from the semantic priming project. In M. N. Jones (Ed.), \emph{Frontiers of cognitive psychology. {Big} data in cognitive science} (pp. 203--226). {Routledge/Taylor \& Francis Group}.

\leavevmode\vadjust pre{\hypertarget{ref-yapIndividualDifferencesJoint2009}{}}%
Yap, M. J., Tse, C.-S., \& Balota, D. A. (2009). Individual differences in the joint effects of semantic priming and word frequency revealed by {RT} distributional analyses: {The} role of lexical integrity. \emph{Journal of Memory and Language}, \emph{61}(3), 303--325. \url{https://doi.org/10.1016/j.jml.2009.07.001}

\leavevmode\vadjust pre{\hypertarget{ref-yarkoniMovingColtheartNew2008}{}}%
Yarkoni, T., Balota, D., \& Yap, M. (2008). Moving beyond {Coltheart}'s {N}: {A} new measure of orthographic similarity. \emph{Psychonomic Bulletin \& Review}, \emph{15}(5), 971--979. \url{https://doi.org/10.3758/PBR.15.5.971}

\leavevmode\vadjust pre{\hypertarget{ref-yeeColorlessGreenIdeas2012}{}}%
Yee, E., Ahmed, S. Z., \& Thompson-Schill, S. L. (2012). Colorless green ideas (can) prime furiously. \emph{Psychological Science}, \emph{23}(4), 364--369. \url{https://doi.org/10.1177/0956797611430691}

\leavevmode\vadjust pre{\hypertarget{ref-yeeFunctionFollowsForm2011}{}}%
Yee, E., Huffstetler, S., \& Thompson-Schill, S. L. (2011). Function follows form: {Activation} of shape and function features during object identification. \emph{Journal of Experimental Psychology: General}, \emph{140}(3), 348--363. \url{https://doi.org/10.1037/a0022840}

\leavevmode\vadjust pre{\hypertarget{ref-zeman2020a}{}}%
Zeman, A., Milton, F., Della Sala, S., Dewar, M., Frayling, T., Gaddum, J., Hattersley, A., Heuerman-Williamson, B., Jones, K., \& MacKisack, M. (2020). Phantasia---the psychological significance of lifelong visual imagery vividness extremes. \emph{Cortex}, \emph{130}, 426--440. \url{https://doi.org/10.1016/j.cortex.2020.04.003}

\end{CSLReferences}

\newpage

\hypertarget{appendix-appendix}{%
\appendix}

\renewcommand{\thefigure}{A\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{A\arabic{table}} \setcounter{table}{0}

\hypertarget{appendix-A-lexical-covariates}{%
\section{Appendix A: Selection of lexical covariates}\label{appendix-A-lexical-covariates}}

Lexical covariates are usually used in conceptual processing studies due to the widespread connections among lexical and semantic variables. Including these covariates---or nuisance variables---in the model allows a more rigorous analysis of the predictors of interest (Sassenhagen \& Alday, 2016).

In each study, the covariates were selected out of a group of 5 variables that had been used as covariates in Wingfield and Connell (2022), and are widely used (e.g., Petilli et al., 2021). Some of these covariates were highly intercorrelated (\(r\) \textgreater{} .70), as shown below. To avoid the problem of multicollinearity, the maximum zero-order correlation allowed between any two covariates was of \(r\) = \(\pm\).70 (Dormann et al., 2013; Harrison et al., 2018). In cases of higher correlations, the covariate with the largest effect in the model, based on the estimate (\(\upbeta\)), was selected.

In Studies 1 (semantic priming) and 2 (semantic decision), the lexical covariates were selected out of five variables, which mirrored those used by Wingfield and Connell (2022): namely, number of letters (i.e., orthographic length, which we computed in R), word frequency, number of syllables (both the latter from Balota et al., 2007), orthographic Levenshtein distance (Yarkoni et al., 2008) and phonological Levenshtein distance (Suárez et al., 2011). In Study 3 (lexical decision), the procedure was identical except that word frequency could not be selected as a covariate because it constituted a predictor of interest, specifically corresponding to linguistic information (for details, see Study 3 in the main article).

All the models included by-participant and by-word random intercepts, as well as by-participant random slopes for every predictor. Below, the correlations and the selection model are shown for each study.

\hypertarget{study-1-semantic-priming-1}{%
\subsection{Study 1: Semantic priming}\label{study-1-semantic-priming-1}}

All lexical covariates considered in the semantic priming study were based on the target words. Figure \ref{fig:semanticpriming-lexical-covariates-correlations} shows the zero-order correlations among the lexical covariates considered in the selection.

\begin{figure}

{\centering \includegraphics[width=0.5\linewidth]{manuscript_files/figure-latex/semanticpriming-lexical-covariates-correlations-1}

}

\caption{Zero-order correlations among lexical covariates pretested in the semantic priming study.}\label{fig:semanticpriming-lexical-covariates-correlations}
\end{figure}

Table \ref{tab:semanticpriming-lexical-covariates-selection} shows the results of the selection model.

\begin{table}[H]

\caption{\label{tab:semanticpriming-lexical-covariates-selection}Mixed-effects model for the selection of lexical covariates in the semantic priming study.}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lrrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{$\upbeta$} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$}\\
\midrule
(Intercept) & 0.01 & 0.00 & {}[0.00, 0.02] & 1.19 & .236\\
Word frequency & -0.14 & 0.01 & {}[-0.15, -0.13] & -24.19 & <.001\\
Number of letters & 0.00 & 0.01 & {}[-0.02, 0.02] & 0.12 & .903\\
Number of syllables & 0.04 & 0.01 & {}[0.02, 0.06] & 4.02 & <.001\\
Orthographic Levenshtein distance & 0.03 & 0.01 & {}[0.00, 0.05] & 2.19 & .029\\
Phonological Levenshtein distance & 0.02 & 0.01 & {}[-0.01, 0.04] & 1.28 & .199\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \textit{\linebreak} 
\item \textit{Note}. $\upbeta$ = Estimate based on z-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CI = confidence interval. By-participant random slopes were included for \linebreak \phantom{.}every effect.
\end{tablenotes}
\end{threeparttable}
\end{table}

Considering the maximum correlation allowed (\(r\) = \(\pm\).70) and the results of the model, the variables that will be included as covariates in the main analysis are word frequency and number of syllables.

\hypertarget{study-2-semantic-decision-1}{%
\subsection{Study 2: Semantic decision}\label{study-2-semantic-decision-1}}

Figure \ref{fig:semanticdecision-lexical-covariates-correlations} shows the zero-order correlations among the lexical covariates considered in the selection.

\begin{figure}

{\centering \includegraphics[width=0.5\linewidth]{manuscript_files/figure-latex/semanticdecision-lexical-covariates-correlations-1}

}

\caption{Zero-order correlations for the lexical covariates pretested in the semantic decision study.}\label{fig:semanticdecision-lexical-covariates-correlations}
\end{figure}

Table \ref{tab:semanticdecision-lexical-covariates-selection} shows the results of the selection model.

\begin{table}[H]

\caption{\label{tab:semanticdecision-lexical-covariates-selection}Mixed-effects model for the selection of lexical covariates in the semantic decision study.}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lrrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{$\upbeta$} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$}\\
\midrule
(Intercept) & 0.05 & 0.00 & {}[0.05, 0.06] & 12.35 & <.001\\
Word frequency & -0.13 & 0.01 & {}[-0.14, -0.11] & -20.01 & <.001\\
Number of letters & 0.05 & 0.01 & {}[0.03, 0.07] & 5.20 & <.001\\
Number of syllables & 0.08 & 0.01 & {}[0.07, 0.10] & 10.80 & <.001\\
Orthographic Levenshtein distance & -0.13 & 0.01 & {}[-0.15, -0.10] & -10.23 & <.001\\
Phonological Levenshtein distance & 0.01 & 0.01 & {}[-0.01, 0.03] & 0.91 & .361\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \textit{\linebreak} 
\item \textit{Note}. $\upbeta$ = Estimate based on z-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CI = confidence interval. By-participant random slopes were included for \linebreak \phantom{.}every effect.
\end{tablenotes}
\end{threeparttable}
\end{table}

Considering the maximum correlation allowed (\(r\) = \(\pm\).70) and the results of the model, the variables that will be included as covariates in the main analysis are word frequency and orthographic Levenshtein distance.

\hypertarget{study-3-lexical-decision-1}{%
\subsection{Study 3: Lexical decision}\label{study-3-lexical-decision-1}}

Figure \ref{fig:lexicaldecision-lexical-covariates-correlations} shows the zero-order correlations among the lexical covariates considered in the selection.

\begin{figure}

{\centering \includegraphics[width=0.5\linewidth]{manuscript_files/figure-latex/lexicaldecision-lexical-covariates-correlations-1}

}

\caption{Zero-order correlations for the lexical covariates pretested in the lexical decision study.}\label{fig:lexicaldecision-lexical-covariates-correlations}
\end{figure}

Table \ref{tab:lexicaldecision-lexical-covariates-selection} shows the results of the selection model.

\begin{table}[H]

\caption{\label{tab:lexicaldecision-lexical-covariates-selection}Mixed-effects model for the selection of lexical covariates in the lexical decision study.}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lrrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{$\upbeta$} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$}\\
\midrule
(Intercept) & 0.00 & 0.01 & {}[-0.01, 0.01] & -0.02 & .981\\
Word frequency & -0.12 & 0.01 & {}[-0.15, -0.10] & -11.60 & <.001\\
Number of letters & 0.05 & 0.02 & {}[0.01, 0.09] & 2.73 & .006\\
Number of syllables & 0.06 & 0.01 & {}[0.03, 0.09] & 4.43 & <.001\\
Orthographic Levenshtein distance & 0.10 & 0.02 & {}[0.05, 0.14] & 4.52 & <.001\\
Phonological Levenshtein distance & -0.02 & 0.02 & {}[-0.06, 0.02] & -1.18 & .238\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \textit{\linebreak} 
\item \textit{Note}. $\upbeta$ = Estimate based on z-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CI = confidence interval. By-participant random slopes were included for \linebreak \phantom{.}every effect.
\end{tablenotes}
\end{threeparttable}
\end{table}

Considering the maximum correlation allowed (\(r\) = \(\pm\).70), the results of the model, and the use of word frequency as a predictor of interest in the model, the variable that will be included as a covariate in the main analysis is orthographic Levenshtein distance.

\hypertarget{conclusion}{%
\subsection{Conclusion}\label{conclusion}}

Word frequency presented the largest effect in the three models. Orthographic Levenshtein distance was the second largest effect in the semantic decision and the lexical decision studies, whereas its phonological counterpart was not significant in any of the studies. The latter difference makes sense, as participants read the stimulus words in the three studies (Brysbaert, 2022).

\clearpage

\renewcommand{\thefigure}{B\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{B\arabic{table}} \setcounter{table}{0}

\hypertarget{appendix-B-frequentist-analysis-diagnostics}{%
\section{Appendix B: Diagnostics for the frequentist analyses}\label{appendix-B-frequentist-analysis-diagnostics}}

Below, the convergence warnings and the non-normal residuals are first addressed generally, and then in more detail in the context of each study.

\hypertarget{lack-of-convergence}{%
\subsection{Lack of convergence}\label{lack-of-convergence}}

The challenge of convergence is well known in the area of mixed-effects models. The solutions proposed range from the removal of random slopes under certain conditions (Matuschek et al., 2017) to the maintenance of random slopes in spite of convergence warnings, which seeks to avoid an inflation of the Type I error caused by non-independence in the data (Brauer \& Curtin, 2018; Singmann \& Kellen, 2019).

\hypertarget{the-multiple-optimizers-sanity-check-from-lme4allfit}{%
\subsubsection{\texorpdfstring{The multiple-optimizers sanity check from \texttt{lme4::allFit()}}{The multiple-optimizers sanity check from lme4::allFit()}}\label{the-multiple-optimizers-sanity-check-from-lme4allfit}}

Framed within the drive to maintain random slopes wherever possible, the developers of the `lme4' package propose a sanity check that uses a part of the `lme4' \emph{engine} called `optimizer'. Every model has a default optimizer, unless a specific one is chosen through \texttt{control\ =\ lmerControl(optimizer\ =\ \textquotesingle{}...\textquotesingle{})} (in \texttt{lmer} models) or \texttt{control\ =\ glmerControl(optimizer\ =\ \textquotesingle{}...\textquotesingle{})} (in \texttt{glmer} models). The 7 widely-available optimizers are:

\begin{itemize}
\tightlist
\item
  bobyqa
\item
  Nelder\_Mead
\item
  nlminbwrap
\item
  nmkbw
\item
  optimx.L-BFGS-B
\item
  nloptwrap.NLOPT\_LN\_NELDERMEAD
\item
  nloptwrap.NLOPT\_LN\_BOBYQA
\end{itemize}

To assess whether convergence warnings render the results invalid, or on the contrary, the results can be deemed valid in spite of the warnings, Bates et al. (2021) suggest refitting models affected by convergence warnings with a variety of optimizers. The authors argue that if the different optimizers produce practically-equivalent results, the results are valid. For this purpose, the `allFit' function from the `lme4' package allows the refitting of models using a number of optimizers. To use the 7 optimizers listed above, two extra packages were installed: `dfoptim' and `optimx' (see \href{https://cran.r-project.org/web/packages/lme4/lme4.pdf}{lme4 manual}). The output from `allFit' contains several statistics on the fixed and the random effects fitted by each optimizer (see \href{https://github.com/lme4/lme4/issues/512\#issue-425198940}{example}).

The severity of convergence problems in each study will be examined below using the `allFit' function from the `lme4' package.

\hypertarget{residual-errors-not-normally-distributed}{%
\subsection{Residual errors not normally distributed}\label{residual-errors-not-normally-distributed}}

The residuals of the linear mixed-effects models in all three studies violated the assumption of normality. Even though linear mixed-effects models tend to be quite robust to deviations from normality (Knief \& Forstmeier, 2021; Schielzeth et al., 2020), we sought to verify our results. To this end, two robust models were performed in each study, as described below.

\hypertarget{method-a-robustlmm-model}{%
\subsubsection{\texorpdfstring{Method A: \emph{robustlmm} model}{Method A: robustlmm model}}\label{method-a-robustlmm-model}}

The first method uses the R package `robustlmm' v2.4-4 (Koller, 2016). To calculate the p values, we followed the procedure of Sleegers et al. (2021), but used the Kenward-Roger method instead of Satterthwaite (see Luke, 2017).

\hypertarget{method-b-inverse-gaussian-model-with-identity-link-function}{%
\subsubsection{Method B: Inverse Gaussian model with identity link function}\label{method-b-inverse-gaussian-model-with-identity-link-function}}

We followed a method proposed by Lo and Andrews (2015), based on generalized linear mixed-effects models (GLMM) implementing an identity link function. According to Lo and Andrews (2015), the link function helps avoid directly transforming the dependent variable, which can hinder the interpretability of the results (also see Knief \& Forstmeier, 2021).

GLMMs require the use of families of distributions. Lo and Andrews (2015) tested the Gaussian, Gamma and Inverse Gaussian families, with either an identity or an inverse link function. The authors found that the Inverse Gaussian family with an identity link yielded the most normal residuals. The Inverse Gaussian and the Gamma families only accept positive values in the outcome variable (see Table 15.2 in Fox, 2016). Due to this restriction, the dependent variable in the present model is raw RT, unlike the standardised RT that was used in the main analysis.

\emph{P} values were to be calculated through parametric bootstrapping, which is the most robust method for GLMMs, as the Kenward-Roger and Satterthwaite methods are not available for these models (Luke, 2017; Singmann et al., 2021).

Neither Method A nor Method B could finally be used, as the code produced errors. These errors are shown in the corresponding scripts inside the `model\_diagnostics' folder in each study. Nonetheless, the residuals are shown below.

\hypertarget{study-1-semantic-priming-2}{%
\subsection{Study 1: Semantic priming}\label{study-1-semantic-priming-2}}

\hypertarget{lack-of-convergence-1}{%
\subsubsection{Lack of convergence}\label{lack-of-convergence-1}}

In the initial model, the optimizer used (the default one in `lmerTest') was `nloptwrap', and the convergence warning read: `boundary (singular) fit: see ?isSingular'.

Based on the reanalysis using 7 optimizers, Figure \ref{fig:main-effects-semanticpriming-allFit-convergence} shows the fixed, main effects, and Figure \ref{fig:interactions-semanticpriming-allFit-convergence} shows the fixed interactions.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/model_diagnostics/plots/main_effects_semanticpriming_allFit_convergence}

}

\caption{Fixed, main effects from the semantic priming study fitted by 7 optimizers.}\label{fig:main-effects-semanticpriming-allFit-convergence}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/model_diagnostics/plots/interactions_semanticpriming_allFit_convergence}

}

\caption{Fixed interaction effects from the semantic priming study fitted by 7 optimizers.}\label{fig:interactions-semanticpriming-allFit-convergence}
\end{figure}

\hypertarget{residual-errors-not-normally-distributed-1}{%
\subsubsection{Residual errors not normally distributed}\label{residual-errors-not-normally-distributed-1}}

Figure \ref{fig:semanticpriming-residuals} shows the deviation from normality of the residuals of the linear mixed-effects model.

\begin{figure}

{\centering \includegraphics[width=0.65\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/model_diagnostics/plots/semanticpriming_residuals}

}

\caption{Residuals of the linear mixed-effects model from the semantic priming study. \linebreak KS = Kolmogorov-Smirnov test; TS = tail-sensitive confidence bands.}\label{fig:semanticpriming-residuals}
\end{figure}

\hypertarget{semantic-priming-model-including-visual-similarity}{%
\subsubsection{Semantic priming model including visual similarity}\label{semantic-priming-model-including-visual-similarity}}

\hypertarget{convergence}{%
\paragraph{Convergence}\label{convergence}}

In the initial model, the optimizer used (the default one in `lmerTest') was `nloptwrap', and the convergence warning read: `boundary (singular) fit: see ?isSingular'.

Based on the reanalysis using 7 optimizers, Figure \ref{fig:main-effects-semanticpriming-with-visualsimilarity-allFit-convergence} shows the fixed, main effects, and Figure \ref{fig:interactions-semanticpriming-with-visualsimilarity-allFit-convergence} shows the fixed interactions.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/analysis_with_visualsimilarity/model_diagnostics/plots/main_effects_semanticpriming_with_visualsimilarity_allFit_convergence}

}

\caption{Fixed, main effects from the semantic priming study fitted by 7 optimizers.}\label{fig:main-effects-semanticpriming-with-visualsimilarity-allFit-convergence}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/analysis_with_visualsimilarity/model_diagnostics/plots/interactions_semanticpriming_with_visualsimilarity_allFit_convergence}

}

\caption{Fixed interaction effects from the semantic priming study fitted by 7 optimizers.}\label{fig:interactions-semanticpriming-with-visualsimilarity-allFit-convergence}
\end{figure}

\hypertarget{residual-errors-not-normally-distributed-2}{%
\paragraph{Residual errors not normally distributed}\label{residual-errors-not-normally-distributed-2}}

Figure \ref{fig:semanticpriming-with-visualsimilarity-residuals} shows the deviation from normality of the residuals of the linear mixed-effects model.

\begin{figure}

{\centering \includegraphics[width=0.65\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/analysis_with_visualsimilarity/model_diagnostics/plots/semanticpriming_with_visualsimilarity_residuals}

}

\caption{Residuals of the linear mixed-effects model from the semantic priming study. \linebreak KS = Kolmogorov-Smirnov test; TS = tail-sensitive confidence bands.}\label{fig:semanticpriming-with-visualsimilarity-residuals}
\end{figure}

\hypertarget{study-2-semantic-decision-2}{%
\subsection{Study 2: Semantic decision}\label{study-2-semantic-decision-2}}

\hypertarget{convergence-1}{%
\subsubsection{Convergence}\label{convergence-1}}

In the initial model, the optimizer used (the default one in `lmerTest') was `nloptwrap', and the convergence warning read: `boundary (singular) fit: see ?isSingular'.

Based on the reanalysis using 7 optimizers, Figure \ref{fig:main-effects-semanticdecision-allFit-convergence} shows the fixed, main effects, and Figure \ref{fig:interactions-semanticdecision-allFit-convergence} shows the fixed interactions.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/model_diagnostics/plots/main_effects_semanticdecision_allFit_convergence}

}

\caption{Fixed, main effects from the semantic decision study fitted by 7 optimizers.}\label{fig:main-effects-semanticdecision-allFit-convergence}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/model_diagnostics/plots/interactions_semanticdecision_allFit_convergence}

}

\caption{Fixed interaction effects from the semantic decision study fitted by 7 optimizers.}\label{fig:interactions-semanticdecision-allFit-convergence}
\end{figure}

\hypertarget{residual-errors-not-normally-distributed-3}{%
\subsubsection{Residual errors not normally distributed}\label{residual-errors-not-normally-distributed-3}}

Figure \ref{fig:semanticdecision-residuals} shows the deviation from normality of the residuals.

\begin{figure}

{\centering \includegraphics[width=0.65\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/model_diagnostics/plots/semanticdecision_residuals}

}

\caption{Residuals of the linear mixed-effects model from the semantic decision study. \linebreak KS = Kolmogorov-Smirnov test; TS = tail-sensitive confidence bands.}\label{fig:semanticdecision-residuals}
\end{figure}

\hypertarget{study-3-lexical-decision-2}{%
\subsection{Study 3: Lexical decision}\label{study-3-lexical-decision-2}}

\hypertarget{convergence-2}{%
\subsubsection{Convergence}\label{convergence-2}}

In the initial model, the optimizer used (the default one in `lmerTest') was `nloptwrap', and the convergence warning read: `boundary (singular) fit: see ?isSingular'.

Based on the reanalysis using 7 optimizers, Figure \ref{fig:main-effects-lexicaldecision-allFit-convergence} shows the fixed, main effects, and Figure \ref{fig:interactions-lexicaldecision-allFit-convergence} shows the fixed interactions.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/model_diagnostics/plots/main_effects_lexicaldecision_allFit_convergence}

}

\caption{Fixed, main effects from the lexical decision study fitted by 7 optimizers.}\label{fig:main-effects-lexicaldecision-allFit-convergence}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/model_diagnostics/plots/interactions_lexicaldecision_allFit_convergence}

}

\caption{Fixed interaction effects from the lexical decision study fitted by 7 optimizers.}\label{fig:interactions-lexicaldecision-allFit-convergence}
\end{figure}

\hypertarget{residual-errors-not-normally-distributed-4}{%
\subsubsection{Residual errors not normally distributed}\label{residual-errors-not-normally-distributed-4}}

Figure \ref{fig:lexicaldecision-residuals} shows the deviation from normality of the residuals.

\begin{figure}

{\centering \includegraphics[width=0.65\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/model_diagnostics/plots/lexicaldecision_residuals}

}

\caption{Residuals of the linear mixed-effects model from the lexical decision study. The outliers in the residuals deviate from the coloured areas indicating an acceptable normality. \linebreak KS = Kolmogorov-Smirnov test; TS = tail-sensitive confidence bands.}\label{fig:lexicaldecision-residuals}
\end{figure}

\clearpage

\renewcommand{\thefigure}{C\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{C\arabic{table}} \setcounter{table}{0}

\hypertarget{appendix-C-Bayesian-analysis-diagnostics}{%
\section{Appendix C: Diagnostics for the Bayesian analyses}\label{appendix-C-Bayesian-analysis-diagnostics}}

This appendix presents diagnostics for the Bayesian analyses. In each study, prior predictive checks are presented before posterior predictive checks. Furthermore, in each of these checks, the models presented first have the default Gaussian distribution, whereas the next series have an exponentially modified Gaussian (dubbed `ex-Gaussian') distribution with an identity link function (for details, see the section titled `Distributions and prior predictive checks' in the main article). Eyeball estimation is used to assess the outcomes of these checks (for background on predictive checks and for alternative estimation procedures, see Gelman et al., 1996; Moran et al., 2021; Schoot et al., 2021). One diagnostic not shown in this appendix is the \(\widehat R\), which is shown in \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}} instead.

\hypertarget{study1-bayesian-diagnostics}{%
\subsection{Study 1: Semantic priming}\label{study1-bayesian-diagnostics}}

\hypertarget{prior-predictive-checks}{%
\subsubsection{Prior predictive checks}\label{prior-predictive-checks}}

Figures \ref{fig:semanticpriming-priorpredictivecheck-informativepriors}, \ref{fig:semanticpriming-priorpredictivecheck-weaklyinformativepriors} and \ref{fig:semanticpriming-priorpredictivecheck-diffusepriors} show the prior predictive checks for the Gaussian models. These plots show the maximum, mean and minimum values of the observed data (\(y\)) and those of the predicted distribution (\(y_{rep}\), which stands for \emph{rep}lications of the outcome). The way of interpreting these plots is by comparing the observed data to the predicted distribution. The specifics of this vary across the three plots in the series. Firstly, in the upper plot, which shows the maximum values, the ideal scenario would have the observed (\(y\)) value overlapping with the maximum value of the predicted distribution (\(y_{rep}\)). Secondly, in the middle plot, showing the mean values, the ideal scenario would show the observed (\(y\)) value overlapping with the mean value of the predicted distribution (\(y_{rep}\)). Lastly, in the lower plot, which shows the minimum values, the ideal scenario would have the observed (\(y\)) value overlapping with the minimum value of the predicted distribution (\(y_{rep}\)). The overlap need not be absolute but the closer the observed and the predicted values on the X axis, the better. As such, the three predictive checks below---corresponding to models that used the default Gaussian distribution---show that the priors fitted the data acceptably but not very well.

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_informativepriors}

}

\caption{Prior predictive checks for the Gaussian, informative prior model from the semantic priming study. \(y\) = observed data; \(y_{rep}\) = predicted data.}\label{fig:semanticpriming-priorpredictivecheck-informativepriors}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_weaklyinformativepriors}

}

\caption{Prior predictive checks for the Gaussian, weakly-informative prior model from the semantic priming study. \(y\) = observed data; \(y_{rep}\) = predicted data.}\label{fig:semanticpriming-priorpredictivecheck-weaklyinformativepriors}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_diffusepriors}

}

\caption{Prior predictive checks for the Gaussian, diffuse prior model from the semantic priming study. \(y\) = observed data; \(y_{rep}\) = predicted data.}\label{fig:semanticpriming-priorpredictivecheck-diffusepriors}
\end{figure}

In contrast to the above results, Figures \ref{fig:semanticpriming-priorpredictivecheck-informativepriors-exgaussian}, \ref{fig:semanticpriming-priorpredictivecheck-weaklyinformativepriors-exgaussian} and \ref{fig:semanticpriming-priorpredictivecheck-diffusepriors-exgaussian} demonstrate that, when an ex-Gaussian distribution was used, the priors fitted the data far better, which converged with the results of a similar comparison performed by Rodríguez-Ferreiro et al. (2020) (see supplementary materials of the latter study).

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_informativepriors_exgaussian}

}

\caption{Prior predictive checks for the ex-Gaussian, informative prior model from the semantic priming study. \(y\) = observed data; \(y_{rep}\) = predicted data.}\label{fig:semanticpriming-priorpredictivecheck-informativepriors-exgaussian}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_weaklyinformativepriors_exgaussian}

}

\caption{Prior predictive checks for the ex-Gaussian, weakly-informative prior model from the semantic priming study. \(y\) = observed data; \(y_{rep}\) = predicted data.}\label{fig:semanticpriming-priorpredictivecheck-weaklyinformativepriors-exgaussian}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_diffusepriors_exgaussian}

}

\caption{Prior predictive checks for the ex-Gaussian, diffuse prior model from the semantic priming study. \(y\) = observed data; \(y_{rep}\) = predicted data.}\label{fig:semanticpriming-priorpredictivecheck-diffusepriors-exgaussian}
\end{figure}

\hypertarget{posterior-predictive-checks}{%
\subsubsection{Posterior predictive checks}\label{posterior-predictive-checks}}

Based on the above results, the ex-Gaussian distribution was used in the final models. Figure \ref{fig:semanticpriming-posteriorpredictivechecks-allpriors-exgaussian} presents the posterior predictive checks the latter models. The interpretation of these plots is simple: the distributions of the observed (\(y\)) and the predicted data (\(y_{rep}\)) should be as similar as possible. As such, the plots below suggest that the results are trustworthy.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/posterior_predictive_checks/plots/semanticpriming_posteriorpredictivechecks_allpriors_exgaussian}

}

\caption{Posterior predictive checks for the (ex-Gaussian) models from the semantic priming study. \(y\) = observed data; \(y_{rep}\) = predicted data.}\label{fig:semanticpriming-posteriorpredictivechecks-allpriors-exgaussian}
\end{figure}

\hypertarget{study-2-semantic-decision-3}{%
\subsection{Study 2: Semantic decision}\label{study-2-semantic-decision-3}}

\hypertarget{prior-predictive-checks-1}{%
\subsubsection{Prior predictive checks}\label{prior-predictive-checks-1}}

Figures \ref{fig:semanticdecision-priorpredictivecheck-informativepriors}, \ref{fig:semanticdecision-priorpredictivecheck-weaklyinformativepriors} and \ref{fig:semanticdecision-priorpredictivecheck-diffusepriors} show the prior predictive checks for the Gaussian models (for background on these checks, see \protect\hyperlink{study1-bayesian-diagnostics}{\underline{Study 1 above}}). The three plots---corresponding to models that used the default Gaussian distribution---show that the priors fitted the data acceptably but not very well.

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_informativepriors}

}

\caption{Prior predictive checks for the Gaussian, informative prior model from the semantic decision study. \(y\) = observed data; \(y_{rep}\) = predicted data.}\label{fig:semanticdecision-priorpredictivecheck-informativepriors}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_weaklyinformativepriors}

}

\caption{Prior predictive checks for the Gaussian, weakly-informative prior model from the semantic decision study. \(y\) = observed data; \(y_{rep}\) = predicted data.}\label{fig:semanticdecision-priorpredictivecheck-weaklyinformativepriors}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_diffusepriors}

}

\caption{Prior predictive checks for the Gaussian, diffuse prior model from the semantic decision study. \(y\) = observed data; \(y_{rep}\) = predicted data.}\label{fig:semanticdecision-priorpredictivecheck-diffusepriors}
\end{figure}

In contrast to the results from the Gaussian models, Figures \ref{fig:semanticdecision-priorpredictivecheck-informativepriors-exgaussian}, \ref{fig:semanticdecision-priorpredictivecheck-weaklyinformativepriors-exgaussian} and \ref{fig:semanticdecision-priorpredictivecheck-diffusepriors-exgaussian} demonstrate that, when an ex-Gaussian distribution was used, the priors fitted the data far better, which converged with the results found in Study 1.

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_informativepriors_exgaussian}

}

\caption{Prior predictive checks for the ex-Gaussian, informative prior model from the semantic decision study. \(y\) = observed data; \(y_{rep}\) = predicted data.}\label{fig:semanticdecision-priorpredictivecheck-informativepriors-exgaussian}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_weaklyinformativepriors_exgaussian}

}

\caption{Prior predictive checks for the ex-Gaussian, weakly-informative prior model from the semantic decision study. \(y\) = observed data; \(y_{rep}\) = predicted data.}\label{fig:semanticdecision-priorpredictivecheck-weaklyinformativepriors-exgaussian}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_diffusepriors_exgaussian}

}

\caption{Prior predictive checks for the ex-Gaussian, diffuse prior model from the semantic decision study. \(y\) = observed data; \(y_{rep}\) = predicted data.}\label{fig:semanticdecision-priorpredictivecheck-diffusepriors-exgaussian}
\end{figure}

\hypertarget{posterior-predictive-checks-1}{%
\subsubsection{Posterior predictive checks}\label{posterior-predictive-checks-1}}

Based on the above results, the ex-Gaussian distribution was used in the final models. Figure \ref{fig:semanticdecision-posteriorpredictivechecks-allpriors-exgaussian} presents the posterior predictive checks for the latter models. The interpretation of these plots is simple: the distributions of the observed (\(y\)) and the predicted data (\(y_{rep}\)) should be as similar as possible. As such, the plots below suggest that the results are not entirely trustworthy. Indeed, the results themselves (\protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}) are clearly not valid.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/posterior_predictive_checks/plots/semanticdecision_posteriorpredictivechecks_allpriors_exgaussian}

}

\caption{Posterior predictive checks for the (ex-Gaussian) models from the semantic decision study. \(y\) = observed data; \(y_{rep}\) = predicted data.}\label{fig:semanticdecision-posteriorpredictivechecks-allpriors-exgaussian}
\end{figure}

\hypertarget{study-3-lexical-decision-3}{%
\subsection{Study 3: Lexical decision}\label{study-3-lexical-decision-3}}

\hypertarget{prior-predictive-checks-2}{%
\subsubsection{Prior predictive checks}\label{prior-predictive-checks-2}}

Figures \ref{fig:lexicaldecision-priorpredictivecheck-informativepriors}, \ref{fig:lexicaldecision-priorpredictivecheck-weaklyinformativepriors} and \ref{fig:lexicaldecision-priorpredictivecheck-diffusepriors} show the prior predictive checks for the Gaussian models (for background on these checks, see \protect\hyperlink{study1-bayesian-diagnostics}{\underline{Study 1 above}}). The three plots---corresponding to models that used the default Gaussian distribution---show that the priors fitted the data acceptably but not very well.

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_informativepriors}

}

\caption{Prior predictive checks for the Gaussian, informative prior model from the lexical decision study. \(y\) = observed data; \(y_{rep}\) = predicted data.}\label{fig:lexicaldecision-priorpredictivecheck-informativepriors}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_weaklyinformativepriors}

}

\caption{Prior predictive checks for the Gaussian, weakly-informative prior model from the lexical decision study. \(y\) = observed data; \(y_{rep}\) = predicted data.}\label{fig:lexicaldecision-priorpredictivecheck-weaklyinformativepriors}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_diffusepriors}

}

\caption{Prior predictive checks for the Gaussian, diffuse prior model from the lexical decision study. \(y\) = observed data; \(y_{rep}\) = predicted data.}\label{fig:lexicaldecision-priorpredictivecheck-diffusepriors}
\end{figure}

In contrast to the results from the Gaussian models, Figures \ref{fig:lexicaldecision-priorpredictivecheck-informativepriors-exgaussian}, \ref{fig:lexicaldecision-priorpredictivecheck-weaklyinformativepriors-exgaussian} and \ref{fig:lexicaldecision-priorpredictivecheck-diffusepriors-exgaussian} demonstrate that, when an ex-Gaussian distribution was used, the priors fitted the data far better, which converged with the results found in Studies 1 and 2.

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_informativepriors_exgaussian}

}

\caption{Prior predictive checks for the ex-Gaussian, informative prior model from the lexical decision study. \(y\) = observed data; \(y_{rep}\) = predicted data.}\label{fig:lexicaldecision-priorpredictivecheck-informativepriors-exgaussian}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_weaklyinformativepriors_exgaussian}

}

\caption{Prior predictive checks for the ex-Gaussian, weakly-informative prior model from the lexical decision study. \(y\) = observed data; \(y_{rep}\) = predicted data.}\label{fig:lexicaldecision-priorpredictivecheck-weaklyinformativepriors-exgaussian}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_diffusepriors_exgaussian}

}

\caption{Prior predictive checks for the ex-Gaussian, diffuse prior model from the lexical decision study. \(y\) = observed data; \(y_{rep}\) = predicted data.}\label{fig:lexicaldecision-priorpredictivecheck-diffusepriors-exgaussian}
\end{figure}

\hypertarget{posterior-predictive-checks-2}{%
\subsubsection{Posterior predictive checks}\label{posterior-predictive-checks-2}}

Based on the above results, the ex-Gaussian distribution was used in the final models. Figure \ref{fig:lexicaldecision-posteriorpredictivechecks-allpriors-exgaussian} presents the posterior predictive checks for the latter models. The interpretation of these plots is simple: the distributions of the observed (\(y\)) and the predicted data (\(y_{rep}\)) should be as similar as possible. As such, the plots below suggest that the results are trustworthy.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/posterior_predictive_checks/plots/lexicaldecision_posteriorpredictivechecks_allpriors_exgaussian}

}

\caption{Posterior predictive checks for the (ex-Gaussian) models from the lexical decision study. \(y\) = observed data; \(y_{rep}\) = predicted data.}\label{fig:lexicaldecision-posteriorpredictivechecks-allpriors-exgaussian}
\end{figure}

\clearpage

\renewcommand{\thefigure}{D\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{D\arabic{table}} \setcounter{table}{0}

\hypertarget{appendix-D-interaction-plots}{%
\section{Appendix D: Further plots of interactions}\label{appendix-D-interaction-plots}}

This appendix presents plots of interactions that did not fit in the main text.

\hypertarget{study-1-semantic-priming-3}{%
\subsection{Study 1: Semantic priming}\label{study-1-semantic-priming-3}}

\begin{figure}

{\centering \includegraphics[width=1\linewidth,height=0.7\textheight]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-gender}

}

\caption{Interactions with gender in the semantic priming study.}\label{fig:semanticpriming-interactions-with-gender}
\end{figure}

\ldots{} TBC

\hypertarget{study-2-semantic-decision-4}{%
\subsection{Study 2: Semantic decision}\label{study-2-semantic-decision-4}}

\ldots{}

\hypertarget{study-3-lexical-decision-4}{%
\subsection{Study 3: Lexical decision}\label{study-3-lexical-decision-4}}

\ldots{}

\clearpage

\renewcommand{\thefigure}{E\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{E\arabic{table}} \setcounter{table}{0}

\hypertarget{appendix-E-Bayesian-analysis-results}{%
\section{Appendix E: Results from the Bayesian analyses}\label{appendix-E-Bayesian-analysis-results}}

This appendix presents extended results from the Bayesian analyses, containing a prior sensitivity analysis (Schoot et al., 2021). For each study, three tables are presented that contain the results from the informative prior model (\(SD\) = 0.1), the weakly-informative prior model (\(SD\) = 0.2) and the diffuse prior model (\(SD\) = 0.3). All models had an exponentially modified Gaussian (dubbed `ex-Gaussian') distribution with an identity link function (for background, see main article and \protect\hyperlink{appendix-C-Bayesian-analysis-diagnostics}{\underline{Appendix C}}). The \(\widehat R\) value is a convergence diagnostic that should ideally be smaller than 1.01 (Vehtari et al., 2021).

The approach used in this Bayesian analysis is that of estimation (Tendeiro \& Kiers, 2019; also see Schmalz et al., 2021). Thus, the estimates were interpreted by considering the position of their credible intervals in relation to the predicted value of RT (\(z\)). That is, the closer an interval is to a value of 0 on the predicted RT (\(z\)), the smaller the effect of that predictor. For instance, an interval that is symmetrically centred on 0 indicates a very small effect, whereas---in comparison---an interval that does not include 0 indicates a far larger effect (for examples of this approach, see Milek et al., 2018; Rodríguez-Ferreiro et al., 2020).

\hypertarget{study-1-semantic-priming-4}{%
\subsection{Study 1: Semantic priming}\label{study-1-semantic-priming-4}}

Table \ref{tab:semanticpriming-informativepriors-model} presents the results of the informative prior model, and Table \ref{tab:semanticpriming-diffusepriors-model} presents those of the diffuse prior model (further to this, the weakly-informative prior model will be added when it finishes running).

\begin{table}[H]

\caption{\label{tab:semanticpriming-informativepriors-model}Informative prior model for the semantic priming study.}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{$\upbeta$} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{95\% CrI} & \multicolumn{1}{c}{$\widehat R$}\\
\midrule
(Intercept) & 0.00 & 0.00 & {}[0.00, 0.01] & 1.00\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Individual differences}}\\
\cellcolor{gray!6}{\hspace{1em}Attentional control} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.00, 0.01]} & \cellcolor{gray!6}{1.00}\\
\hspace{1em}Vocabulary size $^{\text{a}}$ & -0.01 & 0.00 & {}[-0.01, 0.00] & 1.00\\
\hspace{1em}Gender $^{\text{a}}$ & 0.00 & 0.00 & {}[0.00, 0.01] & 1.00\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Target-word lexical covariates}}\\
\cellcolor{gray!6}{\hspace{1em}Word frequency} & \cellcolor{gray!6}{-0.11} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[-0.12, -0.11]} & \cellcolor{gray!6}{1.00}\\
\cellcolor{gray!6}{\hspace{1em}Number of syllables} & \cellcolor{gray!6}{0.07} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.06, 0.07]} & \cellcolor{gray!6}{1.00}\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Prime-target semantic relationship}}\\
\cellcolor{gray!6}{\hspace{1em}Word-concreteness difference} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.00, 0.01]} & \cellcolor{gray!6}{1.00}\\
\hspace{1em}Language-based similarity $^{\text{b}}$ & -0.06 & 0.00 & {}[-0.07, -0.06] & 1.00\\
\hspace{1em}Visual-strength difference $^{\text{b}}$ & 0.01 & 0.00 & {}[0.01, 0.02] & 1.00\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Task condition}}\\
\hspace{1em}Stimulus-onset asynchrony (SOA) $^{\text{b}}$ & 0.03 & 0.01 & {}[0.02, 0.04] & 1.00\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Interactions}}\\
\cellcolor{gray!6}{\hspace{1em}\makecell[l]{Word-concreteness difference  $\times$ \\ \hspace{0.3cm} Vocabulary size}} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.00, 0.00]} & \cellcolor{gray!6}{1.00}\\
\cellcolor{gray!6}{\hspace{1em}Word-concreteness difference  $\times$  SOA} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.00, 0.00]} & \cellcolor{gray!6}{1.00}\\
\cellcolor{gray!6}{\hspace{1em}Word-concreteness difference  $\times$  Gender} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.00, 0.00]} & \cellcolor{gray!6}{1.00}\\
\cellcolor{gray!6}{\hspace{1em}\makecell[l]{Language-based similarity  $\times$ \\ \hspace{0.3cm} Attentional control}} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[-0.01, 0.00]} & \cellcolor{gray!6}{1.00}\\
\cellcolor{gray!6}{\hspace{1em}\makecell[l]{Visual-strength difference  $\times$ \\ \hspace{0.3cm} Attentional control}} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.00, 0.00]} & \cellcolor{gray!6}{1.00}\\
\hspace{1em}\makecell[l]{Language-based similarity  $\times$ \\ \hspace{0.3cm} Vocabulary size} & 0.00 & 0.00 & {}[-0.01, 0.00] & 1.00\\
\hspace{1em}\makecell[l]{Visual-strength difference  $\times$ \\ \hspace{0.3cm} Vocabulary size} & 0.00 & 0.00 & {}[0.00, 0.00] & 1.00\\
\hspace{1em}Language-based similarity  $\times$  Gender & 0.00 & 0.00 & {}[-0.01, 0.00] & 1.00\\
\hspace{1em}Visual-strength difference  $\times$  Gender & 0.00 & 0.00 & {}[0.00, 0.00] & 1.00\\
\hspace{1em}Language-based similarity  $\times$  SOA $^{\text{b}}$ & 0.00 & 0.00 & {}[0.00, 0.00] & 1.00\\
\hspace{1em}Visual-strength difference  $\times$  SOA $^{\text{b}}$ & 0.00 & 0.00 & {}[0.00, 0.00] & 1.00\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \textit{\linebreak} 
\item \textit{Note}. $\upbeta$ = Estimate based on z-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CrI = credible interval. Shaded rows contain covariates. Some interactions \linebreak \phantom{.}are split over two lines, with the second line indented. \linebreak \linebreak \phantom{.}$^{\text{a}}$ By-word random slopes were included for this effect. \linebreak \phantom{.}$^{\text{b}}$ By-participant random slopes were included for this effect.
\end{tablenotes}
\end{threeparttable}
\end{table}

\begin{table}[H]

\caption{\label{tab:semanticpriming-diffusepriors-model}Diffuse prior model for the semantic priming study.}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{$\upbeta$} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{95\% CrI} & \multicolumn{1}{c}{$\widehat R$}\\
\midrule
(Intercept) & 0.00 & 0.00 & {}[0.00, 0.01] & 1.00\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Individual differences}}\\
\cellcolor{gray!6}{\hspace{1em}Attentional control} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.00, 0.01]} & \cellcolor{gray!6}{1.00}\\
\hspace{1em}Vocabulary size $^{\text{a}}$ & -0.01 & 0.00 & {}[-0.01, 0.00] & 1.00\\
\hspace{1em}Gender $^{\text{a}}$ & 0.00 & 0.00 & {}[0.00, 0.01] & 1.00\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Target-word lexical covariates}}\\
\cellcolor{gray!6}{\hspace{1em}Word frequency} & \cellcolor{gray!6}{-0.11} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[-0.12, -0.11]} & \cellcolor{gray!6}{1.00}\\
\cellcolor{gray!6}{\hspace{1em}Number of syllables} & \cellcolor{gray!6}{0.07} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.06, 0.07]} & \cellcolor{gray!6}{1.00}\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Prime-target semantic relationship}}\\
\cellcolor{gray!6}{\hspace{1em}Word-concreteness difference} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.00, 0.01]} & \cellcolor{gray!6}{1.00}\\
\hspace{1em}Language-based similarity $^{\text{b}}$ & -0.06 & 0.00 & {}[-0.07, -0.06] & 1.00\\
\hspace{1em}Visual-strength difference $^{\text{b}}$ & 0.01 & 0.00 & {}[0.01, 0.01] & 1.00\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Task condition}}\\
\hspace{1em}Stimulus-onset asynchrony (SOA) $^{\text{b}}$ & 0.03 & 0.01 & {}[0.02, 0.04] & 1.00\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Interactions}}\\
\cellcolor{gray!6}{\hspace{1em}\makecell[l]{Word-concreteness difference  $\times$ \\ \hspace{0.3cm} Vocabulary size}} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.00, 0.00]} & \cellcolor{gray!6}{1.00}\\
\cellcolor{gray!6}{\hspace{1em}Word-concreteness difference  $\times$  SOA} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.00, 0.00]} & \cellcolor{gray!6}{1.00}\\
\cellcolor{gray!6}{\hspace{1em}Word-concreteness difference  $\times$  Gender} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.00, 0.00]} & \cellcolor{gray!6}{1.00}\\
\cellcolor{gray!6}{\hspace{1em}\makecell[l]{Language-based similarity  $\times$ \\ \hspace{0.3cm} Attentional control}} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[-0.01, 0.00]} & \cellcolor{gray!6}{1.00}\\
\cellcolor{gray!6}{\hspace{1em}\makecell[l]{Visual-strength difference  $\times$ \\ \hspace{0.3cm} Attentional control}} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.00, 0.00]} & \cellcolor{gray!6}{1.00}\\
\hspace{1em}\makecell[l]{Language-based similarity  $\times$ \\ \hspace{0.3cm} Vocabulary size} & 0.00 & 0.00 & {}[-0.01, 0.00] & 1.00\\
\hspace{1em}\makecell[l]{Visual-strength difference  $\times$ \\ \hspace{0.3cm} Vocabulary size} & 0.00 & 0.00 & {}[0.00, 0.00] & 1.00\\
\hspace{1em}Language-based similarity  $\times$  Gender & 0.00 & 0.00 & {}[-0.01, 0.00] & 1.00\\
\hspace{1em}Visual-strength difference  $\times$  Gender & 0.00 & 0.00 & {}[0.00, 0.00] & 1.00\\
\hspace{1em}Language-based similarity  $\times$  SOA $^{\text{b}}$ & 0.00 & 0.00 & {}[0.00, 0.00] & 1.00\\
\hspace{1em}Visual-strength difference  $\times$  SOA $^{\text{b}}$ & 0.00 & 0.00 & {}[0.00, 0.00] & 1.00\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \textit{\linebreak} 
\item \textit{Note}. $\upbeta$ = Estimate based on z-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CrI = credible interval. Shaded rows contain covariates. Some interactions \linebreak \phantom{.}are split over two lines, with the second line indented. \linebreak \linebreak \phantom{.}$^{\text{a}}$ By-word random slopes were included for this effect. \linebreak \phantom{.}$^{\text{b}}$ By-participant random slopes were included for this effect.
\end{tablenotes}
\end{threeparttable}
\end{table}

Figure \ref{fig:semanticpriming-frequentist-bayesian-plot-allpriors-exgaussian} presents the posterior distribution of each effect in each model. The frequentist estimates are also shown to facilitate the comparison with them.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_bayesian_plots/plots/semanticpriming_frequentist_bayesian_plot_allpriors_exgaussian}

}

\caption{Estimates from the frequentist analysis (in red) and from the Bayesian analysis (in blue) for the semantic priming study, in each model. The frequentist means (represented by points) are flanked by 95\% confidence intervals. The Bayesian means (represented by vertical lines) are flanked by 95\% credible intervals, in light blue (in some cases, the interval is covered up by the bar of the mean).}\label{fig:semanticpriming-frequentist-bayesian-plot-allpriors-exgaussian}
\end{figure}

\hypertarget{study-2-semantic-decision-5}{%
\subsection{Study 2: Semantic decision}\label{study-2-semantic-decision-5}}

Table \ref{tab:semanticdecision-informativepriors-model} presents the results of the informative prior model, Table \ref{tab:semanticdecision-weaklyinformativepriors-model} presents those of the weakly-informative prior model and Table \ref{tab:semanticdecision-diffusepriors-model} presents those of the diffuse prior model.

\begin{table}[H]

\caption{\label{tab:semanticdecision-informativepriors-model}Informative prior model for the semantic decision study.}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{$\upbeta$} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{95\% CrI} & \multicolumn{1}{c}{$\widehat R$}\\
\midrule
(Intercept) & 0.14 & 0.42 & {}[0.00, 1.72] & 1.31\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Individual differences}}\\
\cellcolor{gray!6}{\hspace{1em}Information uptake} & \cellcolor{gray!6}{0.03} & \cellcolor{gray!6}{0.08} & \cellcolor{gray!6}{{}[-0.01, 0.31]} & \cellcolor{gray!6}{1.31}\\
\hspace{1em}Vocabulary size $^{\text{a}}$ & 0.18 & 0.46 & {}[0.00, 1.44] & 1.31\\
\hspace{1em}Gender $^{\text{a}}$ & -0.12 & 0.39 & {}[-1.56, 0.02] & 1.31\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Lexical covariates}}\\
\cellcolor{gray!6}{\hspace{1em}Word frequency} & \cellcolor{gray!6}{-0.18} & \cellcolor{gray!6}{0.31} & \cellcolor{gray!6}{{}[-1.34, -0.07]} & \cellcolor{gray!6}{1.30}\\
\cellcolor{gray!6}{\hspace{1em}Orthographic Levenshtein distance} & \cellcolor{gray!6}{0.06} & \cellcolor{gray!6}{0.56} & \cellcolor{gray!6}{{}[-1.14, 1.94]} & \cellcolor{gray!6}{1.41}\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Semantic variables}}\\
\cellcolor{gray!6}{\hspace{1em}Word concreteness} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.26} & \cellcolor{gray!6}{{}[-0.08, 1.01]} & \cellcolor{gray!6}{1.30}\\
\hspace{1em}Distance to word 'abstract' $^{\text{b}}$ & -0.05 & 0.23 & {}[-0.87, 0.40] & 1.41\\
\hspace{1em}Visual strength $^{\text{b}}$ & -0.20 & 0.49 & {}[-1.52, -0.01] & 1.31\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Interactions}}\\
\cellcolor{gray!6}{\hspace{1em}Word concreteness  $\times$  Gender} & \cellcolor{gray!6}{0.07} & \cellcolor{gray!6}{0.40} & \cellcolor{gray!6}{{}[-0.31, 1.58]} & \cellcolor{gray!6}{1.42}\\
\cellcolor{gray!6}{\hspace{1em}Visual strength  $\times$  Information uptake} & \cellcolor{gray!6}{-0.15} & \cellcolor{gray!6}{0.46} & \cellcolor{gray!6}{{}[-1.79, 0.02]} & \cellcolor{gray!6}{1.30}\\
\hspace{1em}\makecell[l]{Distance to word 'abstract'  $\times$ \\ \hspace{0.3cm} Vocabulary size} & -0.04 & 0.55 & {}[-1.92, 1.11] & 1.42\\
\hspace{1em}Visual strength  $\times$  Vocabulary size & 0.15 & 0.38 & {}[0.00, 1.27] & 1.30\\
\hspace{1em}Distance to word 'abstract'  $\times$  Gender & 0.00 & 0.26 & {}[-0.78, 0.68] & 1.41\\
\hspace{1em}Visual strength  $\times$  Gender & 0.18 & 0.49 & {}[-0.01, 1.66] & 1.30\\
\hspace{1em}Word concreteness  $\times$  Vocabulary size & 0.02 & 0.55 & {}[-1.24, 1.83] & 1.42\\
\hspace{1em}\makecell[l]{Information uptake  $\times$ \\ \hspace{0.3cm} Distance to word 'abstract'} & -0.06 & 0.19 & {}[-0.70, 0.02] & 1.31\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \textit{\linebreak} 
\item \textit{Note}. $\upbeta$ = Estimate based on z-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CrI = credible interval. Shaded rows contain covariates. Some interactions \linebreak \phantom{.}are split over two lines, with the second line indented. \linebreak \linebreak \phantom{.}$^{\text{a}}$ By-word random slopes were included for this effect. \linebreak \phantom{.}$^{\text{b}}$ By-participant random slopes were included for this effect.
\end{tablenotes}
\end{threeparttable}
\end{table}

\begin{table}[H]

\caption{\label{tab:semanticdecision-weaklyinformativepriors-model}Weakly-informative prior model for the semantic decision study.}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{$\upbeta$} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{95\% CrI} & \multicolumn{1}{c}{$\widehat R$}\\
\midrule
(Intercept) & 0.14 & 0.42 & {}[0.00, 1.72] & 1.31\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Individual differences}}\\
\cellcolor{gray!6}{\hspace{1em}Information uptake} & \cellcolor{gray!6}{0.03} & \cellcolor{gray!6}{0.08} & \cellcolor{gray!6}{{}[-0.01, 0.31]} & \cellcolor{gray!6}{1.31}\\
\hspace{1em}Vocabulary size $^{\text{a}}$ & 0.18 & 0.46 & {}[0.00, 1.44] & 1.31\\
\hspace{1em}Gender $^{\text{a}}$ & -0.12 & 0.39 & {}[-1.56, 0.02] & 1.30\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Lexical covariates}}\\
\cellcolor{gray!6}{\hspace{1em}Word frequency} & \cellcolor{gray!6}{-0.18} & \cellcolor{gray!6}{0.31} & \cellcolor{gray!6}{{}[-1.34, -0.07]} & \cellcolor{gray!6}{1.31}\\
\cellcolor{gray!6}{\hspace{1em}Orthographic Levenshtein distance} & \cellcolor{gray!6}{0.06} & \cellcolor{gray!6}{0.56} & \cellcolor{gray!6}{{}[-1.14, 1.94]} & \cellcolor{gray!6}{1.40}\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Semantic variables}}\\
\cellcolor{gray!6}{\hspace{1em}Word concreteness} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.26} & \cellcolor{gray!6}{{}[-0.08, 1.01]} & \cellcolor{gray!6}{1.30}\\
\hspace{1em}Distance to word 'abstract' $^{\text{b}}$ & -0.05 & 0.23 & {}[-0.87, 0.40] & 1.41\\
\hspace{1em}Visual strength $^{\text{b}}$ & -0.20 & 0.49 & {}[-1.52, -0.01] & 1.31\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Interactions}}\\
\cellcolor{gray!6}{\hspace{1em}Word concreteness  $\times$  Gender} & \cellcolor{gray!6}{0.07} & \cellcolor{gray!6}{0.40} & \cellcolor{gray!6}{{}[-0.31, 1.58]} & \cellcolor{gray!6}{1.42}\\
\cellcolor{gray!6}{\hspace{1em}Visual strength  $\times$  Information uptake} & \cellcolor{gray!6}{-0.15} & \cellcolor{gray!6}{0.46} & \cellcolor{gray!6}{{}[-1.79, 0.02]} & \cellcolor{gray!6}{1.31}\\
\hspace{1em}\makecell[l]{Distance to word 'abstract'  $\times$ \\ \hspace{0.3cm} Vocabulary size} & -0.04 & 0.55 & {}[-1.92, 1.11] & 1.42\\
\hspace{1em}Visual strength  $\times$  Vocabulary size & 0.15 & 0.38 & {}[0.00, 1.28] & 1.30\\
\hspace{1em}Distance to word 'abstract'  $\times$  Gender & 0.00 & 0.26 & {}[-0.78, 0.68] & 1.41\\
\hspace{1em}Visual strength  $\times$  Gender & 0.18 & 0.49 & {}[-0.01, 1.66] & 1.31\\
\hspace{1em}Word concreteness  $\times$  Vocabulary size & 0.02 & 0.55 & {}[-1.24, 1.83] & 1.41\\
\hspace{1em}\makecell[l]{Information uptake  $\times$ \\ \hspace{0.3cm} Distance to word 'abstract'} & -0.06 & 0.19 & {}[-0.70, 0.02] & 1.31\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \textit{\linebreak} 
\item \textit{Note}. $\upbeta$ = Estimate based on z-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CrI = credible interval. Shaded rows contain covariates. Some interactions \linebreak \phantom{.}are split over two lines, with the second line indented. \linebreak \linebreak \phantom{.}$^{\text{a}}$ By-word random slopes were included for this effect. \linebreak \phantom{.}$^{\text{b}}$ By-participant random slopes were included for this effect.
\end{tablenotes}
\end{threeparttable}
\end{table}

\begin{table}[H]

\caption{\label{tab:semanticdecision-diffusepriors-model}Diffuse prior model for the semantic decision study.}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{$\upbeta$} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{95\% CrI} & \multicolumn{1}{c}{$\widehat R$}\\
\midrule
(Intercept) & 0.14 & 0.42 & {}[0.00, 1.72] & 1.31\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Individual differences}}\\
\cellcolor{gray!6}{\hspace{1em}Information uptake} & \cellcolor{gray!6}{0.03} & \cellcolor{gray!6}{0.08} & \cellcolor{gray!6}{{}[-0.01, 0.31]} & \cellcolor{gray!6}{1.30}\\
\hspace{1em}Vocabulary size $^{\text{a}}$ & 0.18 & 0.46 & {}[0.00, 1.44] & 1.30\\
\hspace{1em}Gender $^{\text{a}}$ & -0.12 & 0.39 & {}[-1.56, 0.02] & 1.31\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Lexical covariates}}\\
\cellcolor{gray!6}{\hspace{1em}Word frequency} & \cellcolor{gray!6}{-0.18} & \cellcolor{gray!6}{0.31} & \cellcolor{gray!6}{{}[-1.34, -0.07]} & \cellcolor{gray!6}{1.30}\\
\cellcolor{gray!6}{\hspace{1em}Orthographic Levenshtein distance} & \cellcolor{gray!6}{0.06} & \cellcolor{gray!6}{0.56} & \cellcolor{gray!6}{{}[-1.14, 1.94]} & \cellcolor{gray!6}{1.41}\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Semantic variables}}\\
\cellcolor{gray!6}{\hspace{1em}Word concreteness} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.26} & \cellcolor{gray!6}{{}[-0.08, 1.01]} & \cellcolor{gray!6}{1.30}\\
\hspace{1em}Distance to word 'abstract' $^{\text{b}}$ & -0.05 & 0.23 & {}[-0.87, 0.40] & 1.41\\
\hspace{1em}Visual strength $^{\text{b}}$ & -0.20 & 0.49 & {}[-1.52, -0.01] & 1.31\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Interactions}}\\
\cellcolor{gray!6}{\hspace{1em}Word concreteness  $\times$  Gender} & \cellcolor{gray!6}{0.07} & \cellcolor{gray!6}{0.40} & \cellcolor{gray!6}{{}[-0.31, 1.58]} & \cellcolor{gray!6}{1.41}\\
\cellcolor{gray!6}{\hspace{1em}Visual strength  $\times$  Information uptake} & \cellcolor{gray!6}{-0.15} & \cellcolor{gray!6}{0.46} & \cellcolor{gray!6}{{}[-1.79, 0.02]} & \cellcolor{gray!6}{1.30}\\
\hspace{1em}\makecell[l]{Distance to word 'abstract'  $\times$ \\ \hspace{0.3cm} Vocabulary size} & -0.04 & 0.55 & {}[-1.92, 1.11] & 1.41\\
\hspace{1em}Visual strength  $\times$  Vocabulary size & 0.15 & 0.38 & {}[0.00, 1.27] & 1.30\\
\hspace{1em}Distance to word 'abstract'  $\times$  Gender & 0.00 & 0.26 & {}[-0.78, 0.68] & 1.42\\
\hspace{1em}Visual strength  $\times$  Gender & 0.18 & 0.49 & {}[-0.01, 1.66] & 1.30\\
\hspace{1em}Word concreteness  $\times$  Vocabulary size & 0.02 & 0.55 & {}[-1.24, 1.83] & 1.41\\
\hspace{1em}\makecell[l]{Information uptake  $\times$ \\ \hspace{0.3cm} Distance to word 'abstract'} & -0.06 & 0.19 & {}[-0.70, 0.02] & 1.31\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \textit{\linebreak} 
\item \textit{Note}. $\upbeta$ = Estimate based on z-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CrI = credible interval. Shaded rows contain covariates. Some interactions \linebreak \phantom{.}are split over two lines, with the second line indented. \linebreak \linebreak \phantom{.}$^{\text{a}}$ By-word random slopes were included for this effect. \linebreak \phantom{.}$^{\text{b}}$ By-participant random slopes were included for this effect.
\end{tablenotes}
\end{threeparttable}
\end{table}

Figure \ref{fig:semanticdecision-frequentist-bayesian-plot-allpriors-exgaussian} presents the posterior distribution of each effect in each model. The frequentist estimates are also shown to facilitate the comparison with them.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_bayesian_plots/plots/semanticdecision_frequentist_bayesian_plot_allpriors_exgaussian}

}

\caption{Estimates from the frequentist analysis (in red) and from the Bayesian analysis (in blue) for the semantic decision study, in each model. The frequentist means (represented by points) are flanked by 95\% confidence intervals. The Bayesian means (represented by vertical lines) are flanked by 95\% credible intervals, in light blue (in some cases, the interval is covered up by the bar of the mean).}\label{fig:semanticdecision-frequentist-bayesian-plot-allpriors-exgaussian}
\end{figure}

\hypertarget{study-3-lexical-decision-5}{%
\subsection{Study 3: Lexical decision}\label{study-3-lexical-decision-5}}

Table \ref{tab:lexicaldecision-informativepriors-model} presents the results of the informative prior model, Table \ref{tab:lexicaldecision-weaklyinformativepriors-model} presents those of the weakly-informative prior model and Table \ref{tab:lexicaldecision-diffusepriors-model} presents those of the diffuse prior model.

\begin{table}[H]

\caption{\label{tab:lexicaldecision-informativepriors-model}Informative prior model for the lexical decision study.}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{$\upbeta$} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{95\% CrI} & \multicolumn{1}{c}{$\widehat R$}\\
\midrule
(Intercept) & 0.00 & 0.01 & {}[-0.01, 0.01] & 1.00\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Individual differences}}\\
\hspace{1em}Vocabulary age $^{\text{a}}$ & 0.00 & 0.01 & {}[-0.01, 0.02] & 1.00\\
\hspace{1em}Gender $^{\text{a}}$ & 0.00 & 0.01 & {}[-0.01, 0.01] & 1.00\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Lexical covariate}}\\
\cellcolor{gray!6}{\hspace{1em}Orthographic Levenshtein distance $^{\text{b}}$} & \cellcolor{gray!6}{0.15} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[0.13, 0.17]} & \cellcolor{gray!6}{1.00}\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Semantic variables}}\\
\cellcolor{gray!6}{\hspace{1em}Word concreteness $^{\text{b}}$} & \cellcolor{gray!6}{-0.03} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[-0.05, -0.02]} & \cellcolor{gray!6}{1.00}\\
\hspace{1em}Word frequency $^{\text{b}}$ & -0.14 & 0.01 & {}[-0.16, -0.12] & 1.00\\
\hspace{1em}Visual strength $^{\text{b}}$ & -0.01 & 0.01 & {}[-0.02, 0.01] & 1.00\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Interactions}}\\
\cellcolor{gray!6}{\hspace{1em}Word concreteness  $\times$  Vocabulary age} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[-0.01, 0.03]} & \cellcolor{gray!6}{1.00}\\
\cellcolor{gray!6}{\hspace{1em}Word concreteness  $\times$  Gender} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[-0.01, 0.03]} & \cellcolor{gray!6}{1.00}\\
\hspace{1em}Word frequency  $\times$  Vocabulary age & 0.00 & 0.01 & {}[-0.02, 0.02] & 1.00\\
\hspace{1em}Visual strength  $\times$  Vocabulary age & 0.00 & 0.01 & {}[-0.02, 0.01] & 1.00\\
\hspace{1em}Word frequency  $\times$  Gender & -0.01 & 0.01 & {}[-0.03, 0.01] & 1.00\\
\hspace{1em}Visual strength  $\times$  Gender & -0.01 & 0.01 & {}[-0.02, 0.01] & 1.00\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \textit{\linebreak} 
\item \textit{Note}. $\upbeta$ = Estimate based on z-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CrI = credible interval. Shaded rows contain covariates. \linebreak \linebreak \phantom{.}$^{\text{a}}$ By-word random slopes were included for this effect. \linebreak \phantom{.}$^{\text{b}}$ By-participant random slopes were included for this effect.
\end{tablenotes}
\end{threeparttable}
\end{table}

\begin{table}[H]

\caption{\label{tab:lexicaldecision-weaklyinformativepriors-model}Weakly-informative prior model for the lexical decision study.}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{$\upbeta$} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{95\% CrI} & \multicolumn{1}{c}{$\widehat R$}\\
\midrule
(Intercept) & 0.00 & 0.01 & {}[-0.01, 0.01] & 1.00\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Individual differences}}\\
\hspace{1em}Vocabulary age $^{\text{a}}$ & 0.00 & 0.01 & {}[-0.01, 0.02] & 1.00\\
\hspace{1em}Gender $^{\text{a}}$ & 0.00 & 0.01 & {}[-0.01, 0.01] & 1.00\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Lexical covariate}}\\
\cellcolor{gray!6}{\hspace{1em}Orthographic Levenshtein distance $^{\text{b}}$} & \cellcolor{gray!6}{0.15} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[0.13, 0.17]} & \cellcolor{gray!6}{1.00}\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Semantic variables}}\\
\cellcolor{gray!6}{\hspace{1em}Word concreteness $^{\text{b}}$} & \cellcolor{gray!6}{-0.03} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[-0.05, -0.02]} & \cellcolor{gray!6}{1.00}\\
\hspace{1em}Word frequency $^{\text{b}}$ & -0.14 & 0.01 & {}[-0.16, -0.12] & 1.00\\
\hspace{1em}Visual strength $^{\text{b}}$ & -0.01 & 0.01 & {}[-0.02, 0.01] & 1.00\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Interactions}}\\
\cellcolor{gray!6}{\hspace{1em}Word concreteness  $\times$  Vocabulary age} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[-0.01, 0.03]} & \cellcolor{gray!6}{1.00}\\
\cellcolor{gray!6}{\hspace{1em}Word concreteness  $\times$  Gender} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[-0.01, 0.03]} & \cellcolor{gray!6}{1.00}\\
\hspace{1em}Word frequency  $\times$  Vocabulary age & 0.00 & 0.01 & {}[-0.02, 0.02] & 1.00\\
\hspace{1em}Visual strength  $\times$  Vocabulary age & 0.00 & 0.01 & {}[-0.02, 0.01] & 1.00\\
\hspace{1em}Word frequency  $\times$  Gender & -0.01 & 0.01 & {}[-0.03, 0.01] & 1.00\\
\hspace{1em}Visual strength  $\times$  Gender & -0.01 & 0.01 & {}[-0.02, 0.01] & 1.00\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \textit{\linebreak} 
\item \textit{Note}. $\upbeta$ = Estimate based on z-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CrI = credible interval. Shaded rows contain covariates. \linebreak \linebreak \phantom{.}$^{\text{a}}$ By-word random slopes were included for this effect. \linebreak \phantom{.}$^{\text{b}}$ By-participant random slopes were included for this effect.
\end{tablenotes}
\end{threeparttable}
\end{table}

\begin{table}[H]

\caption{\label{tab:lexicaldecision-diffusepriors-model}Diffuse prior model for the lexical decision study.}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{$\upbeta$} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{95\% CrI} & \multicolumn{1}{c}{$\widehat R$}\\
\midrule
(Intercept) & 0.00 & 0.01 & {}[-0.01, 0.01] & 1.00\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Individual differences}}\\
\hspace{1em}Vocabulary age $^{\text{a}}$ & 0.00 & 0.01 & {}[-0.01, 0.02] & 1.00\\
\hspace{1em}Gender $^{\text{a}}$ & 0.00 & 0.01 & {}[-0.01, 0.01] & 1.00\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Lexical covariate}}\\
\cellcolor{gray!6}{\hspace{1em}Orthographic Levenshtein distance $^{\text{b}}$} & \cellcolor{gray!6}{0.15} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[0.13, 0.17]} & \cellcolor{gray!6}{1.00}\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Semantic variables}}\\
\cellcolor{gray!6}{\hspace{1em}Word concreteness $^{\text{b}}$} & \cellcolor{gray!6}{-0.03} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[-0.05, -0.02]} & \cellcolor{gray!6}{1.00}\\
\hspace{1em}Word frequency $^{\text{b}}$ & -0.14 & 0.01 & {}[-0.16, -0.12] & 1.00\\
\hspace{1em}Visual strength $^{\text{b}}$ & -0.01 & 0.01 & {}[-0.02, 0.01] & 1.00\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Interactions}}\\
\cellcolor{gray!6}{\hspace{1em}Word concreteness  $\times$  Vocabulary age} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[-0.01, 0.03]} & \cellcolor{gray!6}{1.00}\\
\cellcolor{gray!6}{\hspace{1em}Word concreteness  $\times$  Gender} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[-0.01, 0.03]} & \cellcolor{gray!6}{1.00}\\
\hspace{1em}Word frequency  $\times$  Vocabulary age & 0.00 & 0.01 & {}[-0.02, 0.02] & 1.00\\
\hspace{1em}Visual strength  $\times$  Vocabulary age & 0.00 & 0.01 & {}[-0.02, 0.01] & 1.00\\
\hspace{1em}Word frequency  $\times$  Gender & -0.01 & 0.01 & {}[-0.03, 0.01] & 1.00\\
\hspace{1em}Visual strength  $\times$  Gender & -0.01 & 0.01 & {}[-0.02, 0.01] & 1.00\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \textit{\linebreak} 
\item \textit{Note}. $\upbeta$ = Estimate based on z-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CrI = credible interval. Shaded rows contain covariates. \linebreak \linebreak \phantom{.}$^{\text{a}}$ By-word random slopes were included for this effect. \linebreak \phantom{.}$^{\text{b}}$ By-participant random slopes were included for this effect.
\end{tablenotes}
\end{threeparttable}
\end{table}

Figure \ref{fig:lexicaldecision-frequentist-bayesian-plot-allpriors-exgaussian} presents the posterior distribution of each effect in each model. The frequentist estimates are also shown to facilitate the comparison with them.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_bayesian_plots/plots/lexicaldecision_frequentist_bayesian_plot_allpriors_exgaussian}

}

\caption{Estimates from the frequentist analysis (in red) and from the Bayesian analysis (in blue) for the lexical decision study, in each model. The frequentist means (represented by points) are flanked by 95\% confidence intervals. The Bayesian means (represented by vertical lines) are flanked by 95\% credible intervals, in light blue (in some cases, the interval is covered up by the bar of the mean).}\label{fig:lexicaldecision-frequentist-bayesian-plot-allpriors-exgaussian}
\end{figure}

\clearpage

\end{document}

### 2022-06-24 R_functions/alias_interaction_plot.R

@@ -1,0 +1,173 @@
+
+
+# Function for plotting interaction effect by presenting one of the variables 
+# (namely, the variable passed to the `fill` argument) as an alias variable 
+# (`fill_alias`). The main purpose is facilitating the visualisation of
+# interactions involving a categorical factor that was z-scored in the 
+# statistical model. The function draws on `sjPlot::plot_model()`. Note that 
+# all arguments except `model`, `dataset` and `legend_ncol` must be enclosed 
+# in quotation marks. 
+
+# Usage example:
+
+# alias_interaction_plot(
+#   model = semanticpriming_lmerTest,
+#   dataset = semanticpriming,
+#   x = 'z_cosine_similarity',
+#   fill = 'z_recoded_participant_gender',
+#   fill_alias = 'participant_gender',
+#   fill_nesting_factor = 'Participant',
+#   x_title = 'Language-based similarity (*z*)',
+#   y_title = 'Predicted target-word RT (*z*)',
+#   fill_title = 'Gender'
+# )
+
+# Note: if you wished to verify the accuracy of these involved plots, 
+# you could use sjPlot::plot_model() to obtain more basic versions.
+
+#################################
+
+
+alias_interaction_plot = 
+  
+  function(model, dataset, x, fill, fill_alias, fill_nesting_factor = NULL, 
+           x_title = NULL, y_title = NULL, fill_title = NULL, legend_ncol = 1) {
+    
+    require(rlang)  # needed for `!!parse_expr()`
+    require(dplyr)
+    require(ggplot2)
+    require(sjPlot)
+    require(RColorBrewer)
+    require(ggtext)
+    require(Cairo)
+    
+    # Import fill_alias into the model by finding the match with
+    # the `fill` in the model and the `fill` in the data set.
+    model@frame[,fill_alias] = 
+      dataset[,fill_alias][match(model@frame[,fill], dataset[,fill])]
+    
+    # Save model in a new data frame, which will only be used 
+    # to create the fill_labels.
+    model_df = as.data.frame(model@frame)
+    
+    # If appropriate, try appending sample size of 
+    # `fill_nesting_factor` to `fill_alias`
+    if(!is.null(fill_nesting_factor)) {
+      
+      # Proceed only if the `fill` and the `fill_alias` variables contain 
+      # the same number of unique values.
+      if(identical(n_distinct(model_df[,fill]), 
+                   n_distinct(model_df[,fill_alias]))) {
+        
[…]

### 2022-06-24 R_functions/deciles_interaction_plot.R

@@ -1,0 +1,201 @@
+
+
+# Function for plotting interaction effect by splitting one of the variables 
+# (namely, the one passed to the `fill` argument) into ten deciles. The 
+# function draws on sjPlot::plot_model. Note that all arguments except 
+# `model` and `legend_ncol` must be enclosed in quotation marks. 
+
+# Usage example:
+
+# deciles_interaction_plot(
+#   model = semanticdecision_lmerTest,
+#   x = 'z_word_cooccurrence',
+#   fill = 'z_vocabulary_size',
+#   fill_nesting_factor = 'Participant',
+#   x_title = "Distance to word 'abstract' (*z*)",
+#   y_title = 'Predicted RT (*z*)',
+#   fill_title = 'Vocabulary size<br>(*z*, deciles)',
+#   legend_ncol = 2
+# )
+
+# Note: if you wished to verify the accuracy of these involved plots, 
+# you could use sjPlot::plot_model() to obtain more basic versions.
+
+#################################
+
+
+deciles_interaction_plot = 
+  
+  function(model, x, fill, fill_nesting_factor = NULL, x_title = NULL,
+           y_title = NULL, fill_title = NULL, legend_ncol = 1) {
+    
+    require(dplyr)
+    require(ggplot2)
+    require(sjPlot)
+    require(RColorBrewer)
+    require(ggtext)
+    require(Cairo)
+    
+    # Save decile values
+    deciles = quantile(model@frame[,fill], prob = seq(0, 1, length = 11), 
+                       names = FALSE)
+    
+    # Create fill argument name, to be passed into the `terms` argument of 
+    # the plot. This name includes a [list] of the values to be shown.
+    fill_name = paste0(fill, ' [', 
+                       deciles[1], ', ', 
+                       deciles[2], ', ', 
+                       deciles[3], ', ',
+                       deciles[4], ', ',
+                       deciles[5], ', ', 
+                       deciles[6], ', ', 
+                       deciles[7], ', ', 
+                       deciles[8], ', ', 
+                       deciles[9], ', ', 
+                       deciles[10], ', ', 
+                       deciles[11], 
+                       ']')
+    
+    # Wrap number-processing functions into a single one
+    process_labels = function(x) {
+      # First, round to two decimal places 
+      # while keeping any trailing zeros
+      sprintf('%.2f', x) %>% 
+        # Now, remove minus sign from any -0.00 
+        sub('-0.00', '0.00', .)
+    }
+    
[…]

### 2022-06-24 R_functions/powercurvePlot.R

@@ -1,0 +1,80 @@
+
+
+# Plot power curve. This function plots the output from simr::powerCurve()
+# or from combine_powercurve_chunks()
+
+powercurvePlot = function( powercurve, 
+                           
+                           # Format interactions
+                           interaction_symbol_x = TRUE,
+                           
+                           # Value(s) to which the X axis should be expanded
+                           x_axis_expand = NULL,
+                           
+                           # Approximate number of X-axis levels
+                           number_x_axis_levels = NULL ) {
+  
+  # Load required packages
+  require(dplyr)    # data wrangling
+  require(simr)     # used for summary()
+  require(ggplot2)  # plotting
+  require(ggtext)   # enable more formats and HTML code in plot title (&times;)
+  require(Cairo)    # plot format
+  
+  plot =
+    data.frame(summary(powercurve)) %>%
+    ggplot(aes(y = mean, x = nlevels, ymin = lower, ymax = upper, label = nlevels)) +
+    geom_ribbon(fill = 'grey94') + geom_errorbar(colour = 'grey40') + geom_point() + 
+    # Print sample size by each point
+    # geom_label(colour = 'grey30', fill = 'white', alpha = .5, 
+    #            nudge_x = 5, nudge_y = -0.03, label.size = NA) +
+    # Draw 80% threshold
+    geom_hline(yintercept = 0.8, color = 'gray70', lty = 2) +
+    scale_y_continuous(name = 'Power', limits = c(0, 1), 
+                       breaks = c(0, .2, .4, .6, .8, 1),
+                       labels = c('0%', '20%', '40%', '60%', '80%', '100%')) +
+    scale_x_continuous(n.breaks = number_x_axis_levels) + 
+    expand_limits(x = x_axis_expand) + labs(x = 'Number of participants') + 
+    theme_bw() + 
+    theme(axis.title.x = element_text(size = 10, margin = margin(t = 8)), 
+          axis.title.y = element_text(size = 10, margin = margin(r = 8)), 
+          axis.text = element_text(size = 9), 
+          axis.ticks = element_line(colour = 'grey50'),
+          plot.title = element_textbox_simple(size = 9, width = unit(1, 'npc'), 
+                                              halign = 0.5, lineheight = 1.6, 
+                                              padding = margin(6, 6, 6, 6),
+                                              r = grid::unit(8, 'pt'), 
+                                              fill = 'grey96'),
+          axis.line = element_line(colour = 'black'),
[…]

### 2022-06-24 bayesian_priors/bayesian_priors.R

@@ -1,0 +1,223 @@
+
+
+# Priors used in the Bayesian analyses
+
+
+library(dplyr)
+library(ggplot2)
+library(ggridges)
+library(ggtext)
+
+# Set seed number to ensure exact reproducibility 
+# of the random distributions
+set.seed(123)
+
+
+# Background
+
+# The priors below were established by inspecting the effect sizes obtained
+# in previous studies as well as the effect sizes obtained in our 
+# frequentist analyses of the present studies, which are contained in the 
+# present project. These sources revealed highly-similar ranges. The 
+# previous studies that were considered were selected because they 
+# implemented experimental experimental paradigms and analytical procedures 
+# similar to those used in the current studies. The paradigms were lexical 
+# decision, semantic decision or semantic priming with a lexical decision 
+# task. The analytical procedures consisted of the z-scoring of the 
+# dependent and the independent variables. Two studies matched these 
+# characteristics:
+# -- Pexman and Yap (2018, Tables 6 and 7, https://doi.org/10.1037/xlm0000499s)
+# -- Lim et al. (2020, Table 5, https://doi.org/10.1177/1747021820906566)
+# These studies and the frequentist analyses contained in the present 
+# project yielded effect sizes smaller than ±0.30. The bounds of this 
+# range were determined by determined by the results from Pexman and Yap 
+# (2018), who found a word-concreteness effect of β = 0.41 in the 
+# concrete-words analysis, and an effect of β = 0.20 in the abstract-words 
+# analysis. Since we did not separate abstract from concrete words, we 
+# averaged the former values, and set -0.30 as the lower bound, and 0.30 
+# as the upper bound.
+
+# Direction of effects
+
+# The sources used to determine the effect size range also revealed that 
+# some effects consistently presented a negative direction (e.g., word 
+# frequency), whereas some other effects were consistently positive 
+# (e.g., number of letters and interstimulus interval). We incorporated 
+# direction information into the priors in cases of very consistent 
+# patterns, whereas most priors were non-directional. For instance, we 
[…]

### 2022-06-24 lexicaldecision/bayesian_analysis/divergent_models/lexicaldecision_brms_diffusepriors_exgaussian.R

@@ -1,0 +1,115 @@
+
+
+# Part of Study 3: Lexical decision
+
+# Part of Bayesian analysis
+
+# Model with diffuse priors (SD = 0.3)
+
+
+library(dplyr)
+library(brms)  # Version 2.17.0
+
+# Read in data
+lexicaldecision = read.csv('lexicaldecision/data/final_dataset/lexicaldecision.csv')
+
+# Define priors
+
+# In the function `set_prior` used below, the argument `class` often represents
+# groups of parameters. For instance, class 'b' refers to fixed effects.
+
+# Since most priors do not specify the negative/positive direction of effects,
+# distributions are first specified for entire classes, and those are
+# overridden wherever a direction is specified.
+
+diffuse_priors =
+  c(set_prior('normal(0, 0.3)', class = 'Intercept'),
+    set_prior('normal(0, 0.3)', class = 'b'),
+    set_prior('normal(0.1, 0.3)', class = 'b',
+              coef = 'z_orthographic_Levenshtein_distance'),
+    set_prior('normal(-0.1, 0.3)', class = 'b',
+              coef = 'z_word_frequency'),
+    set_prior('normal(0, 0.3)', class = 'sd'),  # automatically truncated to keep positive values only
+    set_prior('normal(0, 0.3)', class = 'sigma'),  # automatically truncated to keep positive values only
+    set_prior('lkj(2)', class = 'cor')  # standard, regularising prior on random-effects covariance to aid convergence
+  )
+
+# Model
+
+lexicaldecision_brms_diffusepriors_exgaussian =
+  
+  brm(
+    
+    # Dependent variable
+    z_RT ~
+      
+      # FIXED EFFECTS
+      
+      # Controlled lexical variable
+      z_orthographic_Levenshtein_distance +
+      
+      # Controlled semantic variable
+      z_word_concreteness +
+      
+      # Control interactions with word concreteness to allow a rigorous analysis of
+      # the interactions with visual rating specified futher below.
+      z_word_concreteness : z_vocabulary_age +
+      z_word_concreteness : z_recoded_participant_gender +
+      
+      # No covariate of vocabulary age (e.g., information uptake) was controlled for
+      # because the online materials from the English Lexicon Project did not contain
+      # such a covariate (materials hosted at https://elexicon.wustl.edu/ and
+      # https://osf.io/n63s2/, accessed in June 2021).
+      
+      # Main effects of interest
[…]

### 2022-06-24 lexicaldecision/bayesian_analysis/lexicaldecision_brms_diffusepriors_exgaussian.R

@@ -1,0 +1,130 @@
+
+
+# Part of Study 3: Lexical decision
+
+# Part of Bayesian analysis
+
+# Model with diffuse priors (SD = 0.3)
+
+
+library(dplyr)
+library(brms)  # Version 2.17.0
+
+# Read in data
+lexicaldecision = read.csv('lexicaldecision/data/final_dataset/lexicaldecision.csv')
+
+# Define priors
+
+# In the function `set_prior` used below, the argument `class` often represents
+# groups of parameters. For instance, class 'b' refers to fixed effects.
+
+# Since most priors do not specify the negative/positive direction of effects,
+# distributions are first specified for entire classes, and those are
+# overridden wherever a direction is specified.
+
+diffuse_priors =
+  c(set_prior('normal(0, 0.3)', class = 'Intercept'),
+    set_prior('normal(0, 0.3)', class = 'b'),
+    set_prior('normal(0.1, 0.3)', class = 'b',
+              coef = 'z_orthographic_Levenshtein_distance'),
+    set_prior('normal(-0.1, 0.3)', class = 'b',
+              coef = 'z_word_frequency'),
+    set_prior('normal(0, 0.3)', class = 'sd'),  # automatically truncated to keep positive values only
+    set_prior('normal(0, 0.3)', class = 'sigma'),  # automatically truncated to keep positive values only
+    set_prior('lkj(2)', class = 'cor')  # standard, regularising prior on random-effects covariance to aid convergence
+  )
+
+# Model
+
+lexicaldecision_brms_diffusepriors_exgaussian =
+  
+  brm(
+    
+    # Dependent variable
+    z_RT ~
+      
+      # FIXED EFFECTS
+      
+      # Controlled lexical variable
+      z_orthographic_Levenshtein_distance +
+      
+      # Controlled semantic variable
+      z_word_concreteness +
+      
+      # Control interactions with word concreteness to allow a rigorous analysis of
+      # the interactions with visual rating specified futher below.
+      z_word_concreteness : z_vocabulary_age +
+      z_word_concreteness : z_recoded_participant_gender +
+      
+      # No covariate of vocabulary age (e.g., information uptake) was controlled for
+      # because the online materials from the English Lexicon Project did not contain
+      # such a covariate (materials hosted at https://elexicon.wustl.edu/ and
+      # https://osf.io/n63s2/, accessed in June 2021).
+      
[…]

### 2022-06-24 lexicaldecision/bayesian_analysis/lexicaldecision_brms_informativepriors_exgaussian.R

@@ -1,0 +1,130 @@
+
+
+# Part of Study 3: Lexical decision
+
+# Part of Bayesian analysis
+
+# Model with informative priors (SD = 0.1)
+
+
+library(dplyr)
+library(brms)  # Version 2.17.0
+
+# Read in data
+lexicaldecision = read.csv('lexicaldecision/data/final_dataset/lexicaldecision.csv')
+
+# Define priors
+
+# In the function `set_prior` used below, the argument `class` often represents
+# groups of parameters. For instance, class 'b' refers to fixed effects.
+
+# Since most priors do not specify the negative/positive direction of effects,
+# distributions are first specified for entire classes, and those are
+# overridden wherever a direction is specified.
+
+informative_priors =
+  c(set_prior('normal(0, 0.1)', class = 'Intercept'),
+    set_prior('normal(0, 0.1)', class = 'b'),
+    set_prior('normal(0.1, 0.1)', class = 'b',
+              coef = 'z_orthographic_Levenshtein_distance'),
+    set_prior('normal(-0.1, 0.1)', class = 'b',
+              coef = 'z_word_frequency'),
+    set_prior('normal(0, 0.1)', class = 'sd'),  # automatically truncated to keep positive values only
+    set_prior('normal(0, 0.1)', class = 'sigma'),  # automatically truncated to keep positive values only
+    set_prior('lkj(2)', class = 'cor')  # standard, regularising prior on random-effects covariance to aid convergence
+  )
+
+# Model
+
+lexicaldecision_brms_informativepriors_exgaussian =
+  
+  brm(
+    
+    # Dependent variable
+    z_RT ~
+      
+      # FIXED EFFECTS
+      
+      # Controlled lexical variable
+      z_orthographic_Levenshtein_distance +
+      
+      # Controlled semantic variable
+      z_word_concreteness +
+      
+      # Control interactions with word concreteness to allow a rigorous analysis of
+      # the interactions with visual rating specified futher below.
+      z_word_concreteness : z_vocabulary_age +
+      z_word_concreteness : z_recoded_participant_gender +
+      
+      # No covariate of vocabulary age (e.g., information uptake) was controlled for
+      # because the online materials from the English Lexicon Project did not contain
+      # such a covariate (materials hosted at https://elexicon.wustl.edu/ and
+      # https://osf.io/n63s2/, accessed in June 2021).
+      
[…]

### 2022-06-24 lexicaldecision/bayesian_analysis/prior_predictive_checks/lexicaldecision_priorpredictivecheck_diffusepriors_exgaussian.R

@@ -1,0 +1,235 @@
+
+
+# Part of Study 3: Lexical decision
+
+# Part of Bayesian analysis
+
+# Prior predictive checks are performed to verify the adequacy of the priors
+# (Nicenboim et al., 2022, https://vasishth.github.io/bayescogsci). For this 
+# purpose, the results from three priors are compared below. These priors 
+# differ in their standard deviations, which are—respectively—0.1 (priors 
+# labelled 'informative'), 0.2 ('weakly-informative') and 0.3 ('diffuse'). 
+# The rationale for these priors is provided in the 'bayesian_priors' 
+# folder, located in the root directory of this project. An ex-gaussian 
+# distribution is tested in this script (Rodríguez-Ferreiro et al., 2020; 
+# see supplementary materials via https://doi.org/10.7717/peerj.9511).
+# Due to computational constraints, the random-effects structures of these
+# models are slightly smaller than those of the final models, and the
+# number of iterations is lower.
+
+
+library(dplyr)
+library(brms)  # Version 2.17.0
+library(ggplot2)
+library(ggtext)
+library(patchwork)
+
+
+# Begin by checking what parameters of the model can be assigned priors
+
+# Read in data
+lexicaldecision = read.csv('lexicaldecision/data/final_dataset/lexicaldecision.csv')
+
+
+get_prior(
+  
+  # Dependent variable
+  z_RT ~
+    
+    # FIXED EFFECTS
+    
+    # Controlled lexical variable
+    z_orthographic_Levenshtein_distance +
+    
+    # Controlled semantic variable
+    z_word_concreteness +
+    
+    # Control interactions with word concreteness to allow a rigorous analysis of
+    # the interactions with visual rating specified futher below.
+    z_word_concreteness : z_vocabulary_age +
+    z_word_concreteness : z_recoded_participant_gender +
+    
+    # No covariate of vocabulary age (e.g., information uptake) was controlled for
+    # because the online materials from the English Lexicon Project did not contain
+    # such a covariate (materials hosted at https://elexicon.wustl.edu/ and
+    # https://osf.io/n63s2/, accessed in June 2021).
+    
+    # Main effects of interest
+    z_vocabulary_age + z_recoded_participant_gender +
+    z_word_frequency + z_visual_rating +
+    
+    # Interactions of interest
+    z_word_frequency : z_vocabulary_age +
[…]

### 2022-06-24 lexicaldecision/bayesian_analysis/prior_predictive_checks/lexicaldecision_priorpredictivecheck_informativepriors.R

@@ -1,0 +1,215 @@
+
+
+# Part of Study 3: Lexical decision
+
+# Part of Bayesian analysis
+
+# Prior predictive checks are performed to verify the adequacy of the priors
+# (Nicenboim et al., 2022, https://vasishth.github.io/bayescogsci). For this 
+# purpose, the results from three priors are compared below. These priors 
+# differ in their standard deviations, which are—respectively—0.1 (priors 
+# labelled 'informative'), 0.2 ('weakly-informative') and 0.3 ('diffuse'). 
+# The rationale for these priors is provided in the 'bayesian_priors' 
+# folder, located in the root directory of this project. A gaussian 
+# distribution is tested in this script (Rodríguez-Ferreiro et al., 2020; 
+# see supplementary materials via https://doi.org/10.7717/peerj.9511).
+# Due to computational constraints, the random-effects structures of these
+# models are slightly smaller than those of the final models, and the
+# number of iterations is lower.
+
+
+library(dplyr)
+library(brms)  # Version 2.17.0
+library(ggplot2)
+library(ggtext)
+library(patchwork)
+
+
+# Begin by checking what parameters of the model can be assigned priors
+
+# Read in data
+lexicaldecision = read.csv('lexicaldecision/data/final_dataset/lexicaldecision.csv')
+
+
+get_prior(
+  
+  # Dependent variable
+  z_RT ~
+    
+    # FIXED EFFECTS
+    
+    # Controlled lexical variable
+    z_orthographic_Levenshtein_distance +
+    
+    # Controlled semantic variable
+    z_word_concreteness +
+    
+    # Control interactions with word concreteness to allow a rigorous analysis of
+    # the interactions with visual rating specified futher below.
+    z_word_concreteness : z_vocabulary_age +
+    z_word_concreteness : z_recoded_participant_gender +
+    
+    # No covariate of vocabulary age (e.g., information uptake) was controlled for
+    # because the online materials from the English Lexicon Project did not contain
+    # such a covariate (materials hosted at https://elexicon.wustl.edu/ and
+    # https://osf.io/n63s2/, accessed in June 2021).
+    
+    # Main effects of interest
+    z_vocabulary_age + z_recoded_participant_gender +
+    z_word_frequency + z_visual_rating +
+    
+    # Interactions of interest
+    z_word_frequency : z_vocabulary_age +
[…]

### 2022-06-24 lexicaldecision/bayesian_analysis/prior_predictive_checks/lexicaldecision_priorpredictivecheck_informativepriors_exgaussian.R

@@ -1,0 +1,235 @@
+
+
+# Part of Study 3: Lexical decision
+
+# Part of Bayesian analysis
+
+# Prior predictive checks are performed to verify the adequacy of the priors
+# (Nicenboim et al., 2022, https://vasishth.github.io/bayescogsci). For this 
+# purpose, the results from three priors are compared below. These priors 
+# differ in their standard deviations, which are—respectively—0.1 (priors 
+# labelled 'informative'), 0.2 ('weakly-informative') and 0.3 ('diffuse'). 
+# The rationale for these priors is provided in the 'bayesian_priors' 
+# folder, located in the root directory of this project. An ex-gaussian 
+# distribution is tested in this script (Rodríguez-Ferreiro et al., 2020; 
+# see supplementary materials via https://doi.org/10.7717/peerj.9511).
+# Due to computational constraints, the random-effects structures of these
+# models are slightly smaller than those of the final models, and the
+# number of iterations is lower.
+
+
+library(dplyr)
+library(brms)  # Version 2.17.0
+library(ggplot2)
+library(ggtext)
+library(patchwork)
+
+
+# Begin by checking what parameters of the model can be assigned priors
+
+# Read in data
+lexicaldecision = read.csv('lexicaldecision/data/final_dataset/lexicaldecision.csv')
+
+
+get_prior(
+  
+  # Dependent variable
+  z_RT ~
+    
+    # FIXED EFFECTS
+    
+    # Controlled lexical variable
+    z_orthographic_Levenshtein_distance +
+    
+    # Controlled semantic variable
+    z_word_concreteness +
+    
+    # Control interactions with word concreteness to allow a rigorous analysis of
+    # the interactions with visual rating specified futher below.
+    z_word_concreteness : z_vocabulary_age +
+    z_word_concreteness : z_recoded_participant_gender +
+    
+    # No covariate of vocabulary age (e.g., information uptake) was controlled for
+    # because the online materials from the English Lexicon Project did not contain
+    # such a covariate (materials hosted at https://elexicon.wustl.edu/ and
+    # https://osf.io/n63s2/, accessed in June 2021).
+    
+    # Main effects of interest
+    z_vocabulary_age + z_recoded_participant_gender +
+    z_word_frequency + z_visual_rating +
+    
+    # Interactions of interest
+    z_word_frequency : z_vocabulary_age +
[…]

### 2022-06-24 lexicaldecision/data/lexicaldecision_data_preparation.R

@@ -1,0 +1,426 @@
+
+
+# Part of Study 3: Lexical decision
+
+# Preparation of final data set by merging several data sets from previous studies.
+
+# All primary data sets were last downloaded on 3 January 2022.
+
+
+# install.packages('curl')          # Data download
+# install.packages('httr')          # Data download
+# install.packages('readxl')        # Data reading
+# install.packages('readr')         # Data reading
+# install.packages('purrr')         # Data wrangling
+# install.packages('dplyr')         # Data wrangling
+# install.packages('stringr')       # Text processing
+# install.packages('standardize')   # Used to cluster-mean center within-participants variables 
+
+library(curl)
+library(httr)
+library(readxl)
+library(readr)
+library(purrr)
+library(dplyr)
+library(stringr)
+library(standardize)
+
+
+# DATA SET 1. English Lexicon Project (Balota et al., 2007; https://doi.org/10.3758/BF03193014)
+
+# Download zip from https://osf.io/eu5ca/?version=1. There is one file for each of the 820 participants. 
+# Inside note: The link below provides the first version of the file, which was used in the present 
+# script in June 2021. Even though a second version was later added, in November 2021, to correct some 
+# problems with the files (mentioned below in the current script), the first version is still used in 
+# the current script, thanks to the version-specific link below.
+
+# Note on reproducibility
+# The code below was used to download and save the data set in the folder 'lexicaldecision/data/primary_datasets'. 
+# Such a folder was used because this data set was used in more than one study. To prevent any influence from future 
+# changes to the original data set online, the code below was protected (i.e., commented out) by inserting the snippet 
+# `# Protected code # ` at the beginning of each line. If desired, the code can be run by removing the protective 
+# snippet from every line.
+
+# Protected code # curl_download('https://osf.io/eu5ca/download?version=1',
+# Protected code #               destfile = 'lexicaldecision/data/primary_datasets/ldt.zip')
+
+# Unzip
+unzip('lexicaldecision/data/primary_datasets/ldt.zip', 
+      exdir = 'lexicaldecision/data/primary_datasets/ldt_unzipped')
+
+# List all files
+files = list.files(path = 'lexicaldecision/data/primary_datasets/ldt_unzipped')
+
+# Read in every file, saving each filename (`cbind` function 
[…]

### 2022-06-24 lexicaldecision/frequentist_analysis/lexicaldecision_confidence_intervals_plot.R

@@ -1,0 +1,84 @@
+
+
+# Part of Study 3: Lexical decision
+
+# Plot mean and 95% confidence interval for each effect
+
+library(dplyr)
+library(stringr)
+library(ggplot2)
+
+# Load custom function
+source('R_functions/plot_95_confidence_intervals.R')
+
+# Model below created in the script 'lexicaldecision_lmerTest.R',
+# which is stored in the folder 'lexicaldecision/frequentist_analysis'
+
+KR_summary_lexicaldecision_lmerTest =   # Model summary with Kenward-Roger p values
+  readRDS('lexicaldecision/frequentist_analysis/results/KR_summary_lexicaldecision_lmerTest.rds')
+
+confint_lexicaldecision_lmerTest =   # Confidence intervals
+  readRDS('lexicaldecision/frequentist_analysis/results/confint_lexicaldecision_lmerTest.rds')
+
+# Change labels of effects into plain language
+
+rownames(KR_summary_lexicaldecision_lmerTest$coefficients) =
+  rownames(KR_summary_lexicaldecision_lmerTest$coefficients) %>%
+  
+  # First, adjust names of variables (both in main effects and in interactions)
+  str_replace(pattern = 'z_orthographic_Levenshtein_distance',
+              replacement = 'Orthographic Levenshtein distance') %>%
+  str_replace(pattern = 'z_word_concreteness',
+              replacement = 'Word concreteness') %>%
+  str_replace(pattern = 'z_word_frequency',
+              replacement = 'Word frequency') %>%
+  str_replace(pattern = 'z_visual_rating',
+              replacement = 'Visual strength') %>%
+  str_replace(pattern = 'z_vocabulary_age',
+              replacement = 'Vocabulary age') %>%
+  str_replace(pattern = 'z_recoded_participant_gender',
+              replacement = 'Gender') %>%
+  
+  # Second, adjust order of effects in interactions. In the output from the model, 
+  # the word-level variables of interest (i.e., 'z_word_frequency' and 
+  # 'z_visual_rating') sometimes appeared second in their interactions. For 
+  # better consistency, the code below moves those word-level variables (with 
+  # their new names) to the first position in their interactions. Note that the 
+  # order does not affect the results in any way.
+  sub("(\\w+.*):(Word frequency|Visual strength)", '\\2:\\1', .)
+
+rownames(confint_lexicaldecision_lmerTest) =
[…]

### 2022-06-24 lexicaldecision/frequentist_analysis/lexicaldecision_lmerTest.R

@@ -1,0 +1,122 @@
+
+
+# Part of Study 3: Lexical decision
+
+library(dplyr)  # data wrangling
+# The following lme4-relevant package was installed before lme4 to avoid a conflict 
+# noted at https://cran.r-project.org/web/packages/lme4/lme4.pdf
+library(RcppEigen)
+library(lme4)   # Mixed-effects models (package version 1.1-26)
+library(lmerTest)  # Compute p values (package version 3.1-3)
+library(MuMIn)   # R^2
+
+# Read in data
+lexicaldecision = 
+  read.csv('lexicaldecision/data/final_dataset/lexicaldecision.csv')
+
+# MODEL
+# Measure running time
+system.time({
+  
+  # Model name
+  lexicaldecision_lmerTest =
+    
+    lmerTest::lmer( 
+      
+      # Dependent variable
+      z_RT ~
+        
+        # FIXED EFFECTS
+        
+        # Controlled lexical variable
+        z_orthographic_Levenshtein_distance +
+        
+        # Controlled semantic variable
+        z_word_concreteness +
+        
+        # Control interactions with word concreteness to allow a rigorous analysis of
+        # the interactions with visual rating specified futher below.
+        z_word_concreteness : z_vocabulary_age + 
+        z_word_concreteness : z_recoded_participant_gender + 
+        
+        # No covariate of vocabulary age (e.g., information uptake) was controlled for 
+        # because the online materials from the English Lexicon Project did not contain 
+        # such a covariate (materials hosted at https://elexicon.wustl.edu/ and 
+        # https://osf.io/n63s2/, accessed in June 2021).
+        
+        # Main effects of interest
+        z_vocabulary_age + z_recoded_participant_gender + 
+        z_word_frequency + z_visual_rating + 
+        
+        # Interactions of interest
+        z_word_frequency : z_vocabulary_age +
+        z_visual_rating : z_vocabulary_age +
+        z_word_frequency : z_recoded_participant_gender +
+        z_visual_rating : z_recoded_participant_gender +
+        
+        # RANDOM EFFECTS: maximal structure constructed following the guidelines of Brauer and Curtin (2018;
+        # https://psych.wisc.edu/Brauer/BrauerLab/wp-content/uploads/2014/04/Brauer-Curtin-2018-on-LMEMs.pdf).
+        # Interactions only require random slopes if all variables involved vary within the same units.
[…]

### 2022-06-24 lexicaldecision/frequentist_analysis/model_diagnostics/lexicaldecision_GLMM.R

@@ -1,0 +1,125 @@
+
+
+# Part of Study 3: Lexical decision
+
+# Generalized linear mixed-effects model motivated by the non-normal distribution of the residuals 
+# from the linear mixed-effects model (Lo & Andrews, 2015). The dependent variable used in this 
+# model was raw RT, rather than standardized, RT, as none of the families of distributions tested 
+# by Lo and Andrews (2015) allow values below zero (see Table 15.2 in Fox, 2015). We used the 
+# Inverse Gaussian family with an identity link, which was the family that yielded the most normal 
+# residuals in the analysis by Lo and Andrews.
+# 
+# P values were calculated through parametric bootstrapping, which is the most robust method for 
+# a GLMM, as the Kenward-Roger and Satterthwaite methods are not possible for these models (Luke, 
+# 2017; Singmann et al., 2021).
+
+# Further background:
+# Knief and Forstmeier (2021), https://doi.org/10.1101/498931
+# Schielzeth et al. (2020), https://doi.org/10.1111/2041-210X.13434
+# 
+# References
+# 
+# Fox, J. (2016). Generalized Linear Models. In Applied regression analysis and generalized 
+# linear models (Third Edition, pp. 418–472). SAGE.
+# 
+# Lo, S, & Andrews, S. (2015). To transform or not to transform: Using generalized linear mixed 
+# models to analyse reaction time data. Frontiers in Psychology, 6, 1171. 
+# https://doi.org/10.3389/fpsyg.2015.01171
+# 
+# Luke, S. G. (2017). Evaluating significance in linear mixed-effects models in R. Behavior 
+# Research Methods, 49(4), 1494--1502. https://doi.org/10.3758/s13428-016-0809-y
+# 
+# Singmann, H., Bolker, B., Westfall, J., Aust, F., &  Ben-Sachar, M. S. (2021). Package 'afex'. 
+# CRAN. https://cran.r-project.org/web/packages/afex/afex.pdf
+
+
+# install.packages('afex', repos = 'https://www.stats.bris.ac.uk/R/')
+library(afex)  # Compute p values (package version 3.1-3) using parametric bootstrapping (see information below)
+library(parallel)  # Parallel processing for a faster computation (included in base R)
+
+# Read in data
+lexicaldecision = read.csv('lexicaldecision/data/final_dataset/lexicaldecision.csv')
+
+# Enable parallel clusters, which allows faster processing if several cores available.
[…]

### 2022-06-24 semanticdecision/bayesian_analysis/divergent_models/semanticdecision_brms_diffusepriors_exgaussian.R

@@ -1,0 +1,140 @@
+
+
+# Part of Study 2: Semantic decision
+
+# Part of Bayesian analysis
+
+# Model with diffuse priors (SD = 0.3)
+
+
+library(dplyr)
+library(brms)  # Version 2.17.0
+
+# Read in data
+semanticdecision = read.csv('semanticdecision/data/final_dataset/semanticdecision.csv')
+
+# Define priors
+
+# In the function `set_prior` used below, the argument `class` often represents
+# groups of parameters. For instance, class 'b' refers to fixed effects.
+
+# Since most priors do not specify the negative/positive direction of effects,
+# distributions are first specified for entire classes, and those are
+# overridden wherever a direction is specified.
+
+diffuse_priors =
+  c(set_prior('normal(0, 0.3)', class = 'Intercept'),
+    set_prior('normal(0, 0.3)', class = 'b'),
+    set_prior('normal(0.1, 0.3)', class = 'b',
+              coef = 'z_orthographic_Levenshtein_distance'),
+    set_prior('normal(-0.1, 0.3)', class = 'b',
+              coef = 'z_word_frequency'),
+    set_prior('normal(0, 0.3)', class = 'sd'),  # automatically truncated to keep positive values only
+    set_prior('normal(0, 0.3)', class = 'sigma'),  # automatically truncated to keep positive values only
+    set_prior('lkj(2)', class = 'cor')  # standard, regularising prior on random-effects covariance to aid convergence
+  )
+
+# Model
+
+semanticdecision_brms_diffusepriors_exgaussian =
+  
+  brm(
+    
+    # Dependent variable
+    z_RTclean ~
+      
+      # FIXED EFFECTS
+      
+      # Controlled lexical variables
+      z_word_frequency + z_orthographic_Levenshtein_distance +
+      
+      # Controlled word concreteness, important because the task is a word concreteness assessment.
+      z_word_concreteness +
+      
+      # Control interaction between word concreteness and vocabulary size to allow a rigorous analysis of the
+      # interaction between word co-occurrence and vocabulary size, and the interaction between word visual
+      # rating and vocabulary size.
+      z_word_concreteness : z_vocabulary_size +
+      
+      # Control interaction between word concreteness and participant gender to allow a rigorous analysis
+      # of the interaction between visual rating and participant gender.
+      z_word_concreteness : z_recoded_participant_gender +
+      
+      # Important control due to the relationship between this variable and vocabulary size (Pexman & Yap, 2018;
[…]

### 2022-06-24 semanticdecision/bayesian_analysis/divergent_models/semanticdecision_brms_informativepriors_exgaussian.R

@@ -1,0 +1,140 @@
+
+
+# Part of Study 2: Semantic decision
+
+# Part of Bayesian analysis
+
+# Model with informative priors (SD = 0.1)
+
+
+library(dplyr)
+library(brms)  # Version 2.17.0
+
+# Read in data
+semanticdecision = read.csv('semanticdecision/data/final_dataset/semanticdecision.csv')
+
+# Define priors
+
+# In the function `set_prior` used below, the argument `class` often represents
+# groups of parameters. For instance, class 'b' refers to fixed effects.
+
+# Since most priors do not specify the negative/positive direction of effects,
+# distributions are first specified for entire classes, and those are
+# overridden wherever a direction is specified.
+
+informative_priors =
+  c(set_prior('normal(0, 0.1)', class = 'Intercept'),
+    set_prior('normal(0, 0.1)', class = 'b'),
+    set_prior('normal(0.1, 0.1)', class = 'b',
+              coef = 'z_orthographic_Levenshtein_distance'),
+    set_prior('normal(-0.1, 0.1)', class = 'b',
+              coef = 'z_word_frequency'),
+    set_prior('normal(0, 0.1)', class = 'sd'),  # automatically truncated to keep positive values only
+    set_prior('normal(0, 0.1)', class = 'sigma'),  # automatically truncated to keep positive values only
+    set_prior('lkj(2)', class = 'cor')  # standard, regularising prior on random-effects covariance to aid convergence
+  )
+
+# Model
+
+semanticdecision_brms_informativepriors_exgaussian =
+  
+  brm(
+    
+    # Dependent variable
+    z_RTclean ~
+      
+      # FIXED EFFECTS
+      
+      # Controlled lexical variables
+      z_word_frequency + z_orthographic_Levenshtein_distance +
+      
+      # Controlled word concreteness, important because the task is a word concreteness assessment.
+      z_word_concreteness +
+      
+      # Control interaction between word concreteness and vocabulary size to allow a rigorous analysis of the
+      # interaction between word co-occurrence and vocabulary size, and the interaction between word visual
+      # rating and vocabulary size.
+      z_word_concreteness : z_vocabulary_size +
+      
+      # Control interaction between word concreteness and participant gender to allow a rigorous analysis
+      # of the interaction between visual rating and participant gender.
+      z_word_concreteness : z_recoded_participant_gender +
+      
+      # Important control due to the relationship between this variable and vocabulary size (Pexman & Yap, 2018;
[…]

### 2022-06-24 semanticdecision/bayesian_analysis/prior_predictive_checks/semanticdecision_priorpredictivecheck_diffusepriors.R

@@ -1,0 +1,240 @@
+
+
+# Part of Study 2: Semantic decision
+
+# Part of Bayesian analysis
+
+# Prior predictive checks are performed to verify the adequacy of the priors
+# (Nicenboim et al., 2022, https://vasishth.github.io/bayescogsci). For this 
+# purpose, the results from three priors are compared below. These priors 
+# differ in their standard deviations, which are—respectively—0.1 (priors 
+# labelled 'informative'), 0.2 ('weakly-informative') and 0.3 ('diffuse'). 
+# The rationale for these priors is provided in the 'bayesian_priors' 
+# folder, located in the root directory of this project. A gaussian 
+# distribution is tested in this script (Rodríguez-Ferreiro et al., 2020; 
+# see supplementary materials via https://doi.org/10.7717/peerj.9511).
+# Due to computational constraints, the random-effects structures of these
+# models are slightly smaller than those of the final models, and the
+# number of iterations is lower.
+
+
+library(dplyr)
+library(brms)  # Version 2.17.0
+library(ggplot2)
+library(ggtext)
+library(patchwork)
+
+
+# Begin by checking what parameters of the model can be assigned priors
+
+# Read in data
+semanticdecision = read.csv('semanticdecision/data/final_dataset/semanticdecision.csv')
+
+
+get_prior(
+  
+  # Dependent variable
+  z_RTclean ~
+    
+    # FIXED EFFECTS
+    
+    # Controlled lexical variables
+    z_word_frequency + z_orthographic_Levenshtein_distance +
+    
+    # Controlled word concreteness, important because the task is a word concreteness assessment.
+    z_word_concreteness +
+    
+    # Control interaction between word concreteness and vocabulary size to allow a rigorous analysis of the
+    # interaction between word co-occurrence and vocabulary size, and the interaction between word visual
+    # rating and vocabulary size.
+    z_word_concreteness : z_vocabulary_size +
+    
+    # Control interaction between word concreteness and participant gender to allow a rigorous analysis
+    # of the interaction between visual rating and participant gender.
+    z_word_concreteness : z_recoded_participant_gender +
+    
+    # Important control due to the relationship between this variable and vocabulary size (Pexman & Yap, 2018;
[…]

### 2022-06-24 semanticdecision/bayesian_analysis/prior_predictive_checks/semanticdecision_priorpredictivecheck_diffusepriors_exgaussian.R

@@ -1,0 +1,260 @@
+
+
+# Part of Study 2: Semantic decision
+
+# Part of Bayesian analysis
+
+# Prior predictive checks are performed to verify the adequacy of the priors
+# (Nicenboim et al., 2022, https://vasishth.github.io/bayescogsci). For this 
+# purpose, the results from three priors are compared below. These priors 
+# differ in their standard deviations, which are—respectively—0.1 (priors 
+# labelled 'informative'), 0.2 ('weakly-informative') and 0.3 ('diffuse'). 
+# The rationale for these priors is provided in the 'bayesian_priors' 
+# folder, located in the root directory of this project. An ex-gaussian 
+# distribution is tested in this script (Rodríguez-Ferreiro et al., 2020; 
+# see supplementary materials via https://doi.org/10.7717/peerj.9511).
+# Due to computational constraints, the random-effects structures of these
+# models are slightly smaller than those of the final models, and the
+# number of iterations is lower.
+
+
+library(dplyr)
+library(brms)  # Version 2.17.0
+library(ggplot2)
+library(ggtext)
+library(patchwork)
+
+
+# Begin by checking what parameters of the model can be assigned priors
+
+# Read in data
+semanticdecision = read.csv('semanticdecision/data/final_dataset/semanticdecision.csv')
+
+
+get_prior(
+  
+  # Dependent variable
+  z_RTclean ~
+    
+    # FIXED EFFECTS
+    
+    # Controlled lexical variables
+    z_word_frequency + z_orthographic_Levenshtein_distance +
+    
+    # Controlled word concreteness, important because the task is a word concreteness assessment.
+    z_word_concreteness +
+    
+    # Control interaction between word concreteness and vocabulary size to allow a rigorous analysis of the
+    # interaction between word co-occurrence and vocabulary size, and the interaction between word visual
+    # rating and vocabulary size.
+    z_word_concreteness : z_vocabulary_size +
+    
+    # Control interaction between word concreteness and participant gender to allow a rigorous analysis
+    # of the interaction between visual rating and participant gender.
+    z_word_concreteness : z_recoded_participant_gender +
+    
+    # Important control due to the relationship between this variable and vocabulary size (Pexman & Yap, 2018;
[…]

### 2022-06-24 semanticdecision/bayesian_analysis/prior_predictive_checks/semanticdecision_priorpredictivecheck_weaklyinformativepriors.R

@@ -1,0 +1,239 @@
+
+
+# Part of Study 2: Semantic decision
+
+# Part of Bayesian analysis
+
+# Prior predictive checks are performed to verify the adequacy of the priors
+# (Nicenboim et al., 2022, https://vasishth.github.io/bayescogsci). For this 
+# purpose, the results from three priors are compared below. These priors 
+# differ in their standard deviations, which are—respectively—0.1 (priors 
+# labelled 'informative'), 0.2 ('weakly-informative') and 0.3 ('diffuse'). 
+# The rationale for these priors is provided in the 'bayesian_priors' 
+# folder, located in the root directory of this project. A gaussian 
+# distribution is tested in this script (Rodríguez-Ferreiro et al., 2020; 
+# see supplementary materials via https://doi.org/10.7717/peerj.9511).
+# Due to computational constraints, the random-effects structures of these
+# models are slightly smaller than those of the final models, and the
+# number of iterations is lower.
+
+
+library(dplyr)
+library(brms)  # Version 2.17.0
+library(ggplot2)
+library(ggtext)
+library(patchwork)
+
+
+# Begin by checking what parameters of the model can be assigned priors
+
+# Read in data
+semanticdecision = read.csv('semanticdecision/data/final_dataset/semanticdecision.csv')
+
+
+get_prior(
+  
+  # Dependent variable
+  z_RTclean ~
+    
+    # FIXED EFFECTS
+    
+    # Controlled lexical variables
+    z_word_frequency + z_orthographic_Levenshtein_distance +
+    
+    # Controlled word concreteness, important because the task is a word concreteness assessment.
+    z_word_concreteness +
+    
+    # Control interaction between word concreteness and vocabulary size to allow a rigorous analysis of the
+    # interaction between word co-occurrence and vocabulary size, and the interaction between word visual
+    # rating and vocabulary size.
+    z_word_concreteness : z_vocabulary_size +
+    
+    # Control interaction between word concreteness and participant gender to allow a rigorous analysis
+    # of the interaction between visual rating and participant gender.
+    z_word_concreteness : z_recoded_participant_gender +
+    
+    # Important control due to the relationship between this variable and vocabulary size (Pexman & Yap, 2018;
[…]

### 2022-06-24 semanticdecision/bayesian_analysis/semanticdecision_brms_diffusepriors_exgaussian.R

@@ -1,0 +1,156 @@
+
+
+# Part of Study 2: Semantic decision
+
+# Part of Bayesian analysis
+
+# Model with diffuse priors (SD = 0.3)
+
+
+library(dplyr)
+library(brms)  # Version 2.17.0
+
+# Read in data
+semanticdecision = read.csv('semanticdecision/data/final_dataset/semanticdecision.csv')
+
+# Define priors
+
+# In the function `set_prior` used below, the argument `class` often represents
+# groups of parameters. For instance, class 'b' refers to fixed effects.
+
+# Since most priors do not specify the negative/positive direction of effects,
+# distributions are first specified for entire classes, and those are
+# overridden wherever a direction is specified.
+
+diffuse_priors =
+  c(set_prior('normal(0, 0.3)', class = 'Intercept'),
+    set_prior('normal(0, 0.3)', class = 'b'),
+    set_prior('normal(0.1, 0.3)', class = 'b',
+              coef = 'z_orthographic_Levenshtein_distance'),
+    set_prior('normal(-0.1, 0.3)', class = 'b',
+              coef = 'z_word_frequency'),
+    set_prior('normal(0, 0.3)', class = 'sd'),  # automatically truncated to keep positive values only
+    set_prior('normal(0, 0.3)', class = 'sigma'),  # automatically truncated to keep positive values only
+    set_prior('lkj(2)', class = 'cor')  # standard, regularising prior on random-effects covariance to aid convergence
+  )
+
+# Model
+
+semanticdecision_brms_diffusepriors_exgaussian =
+  
+  brm(
+    
+    # Dependent variable
+    z_RTclean ~
+      
+      # FIXED EFFECTS
+      
+      # Controlled lexical variables
+      z_word_frequency + z_orthographic_Levenshtein_distance +
+      
+      # Controlled word concreteness, important because the task is a word concreteness assessment.
+      z_word_concreteness +
+      
+      # Control interaction between word concreteness and vocabulary size to allow a rigorous analysis of the
+      # interaction between word co-occurrence and vocabulary size, and the interaction between word visual
+      # rating and vocabulary size.
+      z_word_concreteness : z_vocabulary_size +
+      
+      # Control interaction between word concreteness and participant gender to allow a rigorous analysis
+      # of the interaction between visual rating and participant gender.
+      z_word_concreteness : z_recoded_participant_gender +
+      
[…]

### 2022-06-24 semanticdecision/correlations/semanticdecision_correlations.R

@@ -1,0 +1,49 @@
+
+
+# Part of Study 2: Semantic decision
+
+# Zero-order correlations between continuous variables
+
+
+# install.packages('dplyr', repos = 'https://www.stats.bris.ac.uk/R/')
+library(dplyr)    # Data wrangling
+
+# install.packages('Cairo', repos = 'https://www.stats.bris.ac.uk/R/')
+library(Cairo)    # Allows use of special characters such as dashes in plots
+
+# install.packages('ggplot2', repos = 'https://www.stats.bris.ac.uk/R/')
+library(ggplot2)    # ggsave()
+
+
+# Read in data
+semanticdecision = read.csv('semanticdecision/data/final_dataset/semanticdecision.csv')
+
+# Load correlation matrix function
+source('R_functions/correlation_matrix.R')
+
+# Using the following variables...
+(semanticdecision[, c('z_RTclean', 'z_vocabulary_size', 
+                      'z_information_uptake', 'z_word_cooccurrence', 
+                      'z_visual_rating', 'z_word_concreteness', 
+                      'z_word_frequency', 
+                      'z_orthographic_Levenshtein_distance')] %>%
+    
+    # renamed for the sake of clarity
+    rename('RT' = z_RTclean, 
+           'Vocabulary size' = z_vocabulary_size,
+           'Information uptake' = z_information_uptake,
+           "Distance to word 'abstract'" = z_word_cooccurrence,
+           'Visual strength' = z_visual_rating,
+           'Word concreteness' = z_word_concreteness,
+           'Word frequency' = z_word_frequency,
+           'OLD20' = z_orthographic_Levenshtein_distance) %>%
+    
+    # make correlation matrix (custom function from 'R_functions' folder)
+    correlation_matrix() + 
+    
+    theme(plot.margin = unit(c(0.1, 0.6, 0.1, -1.76), 'in'))) %>%
+  
+  # Save
+  ggsave(filename = 'semanticdecision/correlations/plots/semanticdecision_correlations.pdf',
+         device = cairo_pdf, width = 8, height = 6, units = 'in', dpi = 500)
+

### 2022-06-24 semanticdecision/data/semanticdecision_data_preparation.R

@@ -1,0 +1,459 @@
+
+
+# Part of Study 2: Semantic decision
+
+# Preparation of final data set by merging several data sets from previous studies.
+
+# All primary data sets were last downloaded on 2 January 2022.
+
+
+# install.packages('dplyr')         # Data wrangling
+# install.packages('httr')          # Data download
+# install.packages('readxl')        # Data reading
+# install.packages('standardize')   # Used to cluster-mean center within-participants variables 
+
+library(httr)
+library(readxl)
+library(dplyr)
+library(standardize)
+
+
+# DATA SET 1. Calgary Semantic Decision data (Pexman et al., 2017), downloaded from 'Electronic supplementary material' 
+# at https://doi.org/10.3758/s13428-016-0720-6. Download URL:
+# https://static-content.springer.com/esm/art%3A10.3758%2Fs13428-016-0720-6/MediaObjects/13428_2016_720_MOESM3_ESM.xlsx
+
+# Note on reproducibility
+# The code below was used to download and save the data set in the folder 'semanticdecision/data/primary_datasets'. 
+# To prevent any influence from future changes to the original data set online, the code below was protected (i.e., 
+# commented out) by inserting the snippet `# Protected code # ` at the beginning of each line. If desired, the code
+# can be run by removing the protective snippet from every line.
+
+# Protected code # GET('https://static-content.springer.com/esm/art%3A10.3758%2Fs13428-016-0720-6/MediaObjects/13428_2016_720_MOESM3_ESM.xlsx', 
+# Protected code #     write_disk(tf <- tempfile(fileext = ".xlsx")))
+# Protected code # read_excel(tf) %>%
+# Protected code #   write.csv('semanticdecision/data/primary_datasets/Pexman_etal_2017_semanticdecision.csv', 
+# Protected code #             row.names = FALSE)
+
+# Read in data set
+semanticdecision =
+  read.csv('semanticdecision/data/primary_datasets/Pexman_etal_2017_semanticdecision.csv')
+
+str(semanticdecision)
+semanticdecision$RTclean = 
+  as.numeric(as.character(semanticdecision$RTclean))
+
+# Descriptives
+head(semanticdecision)
+nrow(semanticdecision)
+length(unique(semanticdecision$Participant))
+length(unique(semanticdecision$Word))
+
+# Rename vocabulary size
+semanticdecision = semanticdecision %>% rename(vocabulary_size = NAART)
+
[…]

### 2022-06-24 semanticdecision/frequentist_analysis/model_diagnostics/semanticdecision_allFit_convergence.R

@@ -1,0 +1,128 @@
+
+
+# Part of Study 2: Semantic decision
+
+# Convergence diagnostics
+
+# Following Brauer and Curtin (2018), avoid removing random slopes to prevent an inflation of the Type I error rate.
+# As a sanity check, refit mixed-effects model with several optimizers. This check is done by comparing the results 
+# from these optimizers. If they are similar, especially for the fixed effects, then the results are likely valid,
+# even in the presence of convergence warnings (see https://cran.r-project.org/web/packages/lme4/lme4.pdf).
+
+
+library(tidyverse)  # Data wrangling, text processing and plotting
+library(dfoptim)  # Refit model with various optimizers using lme4::allFit()
+library(optimx)  # Refit model with various optimizers using lme4::allFit()
+library(lme4)   # Main analysis and adjustment of effect labels
+library(parallel)   # Allow parallel processing using several cores
+
+
+# Data set below created in the script 'semanticdecision_data_preparation.R',
+# which is stored in the folder 'semanticdecision/data'
+semanticdecision = 
+  read.csv('semanticdecision/data/final_dataset/semanticdecision.csv')
+
+# Model below created in the script 'semanticdecision_lmerTest.R',
+# which is stored in the folder 'semanticdecision/frequentist_analysis'
+semanticdecision_lmerTest = 
+  readRDS('semanticdecision/frequentist_analysis/results/semanticdecision_lmerTest.rds')
+
+# Fit model using the seven available optimizers
+semanticdecision_allFit_convergence = 
+  allFit(semanticdecision_lmerTest, 
+         # Set maximum iterations to 1m to facilitate convergence 
+         # (Brauer & Curtin, 2018; Singmann & Kellen, 2019)
+         maxfun = 1e6,
+         # Use 7 cores in parallel for faster computation
+         ncpus = 7)
+
+# Save
+saveRDS(semanticdecision_allFit_convergence,
+        'semanticdecision/frequentist_analysis/model_diagnostics/results/semanticdecision_allFit_convergence.rds')
+
+# Load the result back in, if needed later
+# semanticdecision_allFit_convergence =
+#   readRDS('semanticdecision/frequentist_analysis/model_diagnostics/results/semanticdecision_allFit_convergence.rds')
+
+################################################################################
+
+
+# PLOT fixed effects from all the optimizers
+
[…]

### 2022-06-24 semanticdecision/frequentist_analysis/model_diagnostics/semanticdecision_robustlmm.R

@@ -1,0 +1,126 @@
+
+
+# Part of Study 2: Semantic decision
+
+# This {robustlmm} model is used to validate the results of the standard mixed-effects model, 
+# in which the residuals were not normally distributed. The robustlmm package detects and 
+# removes outliers that hinder the normality of the residuals.
+
+# Package paper: Koller (2016), http://dx.doi.org/10.18637/jss.v075.i06
+
+# Use case: Sleegers et al. (2020), https://doi.org/10.1177/1948550620966153
+
+# Further background:
+# Knief and Forstmeier (2021), https://doi.org/10.1101/498931
+# Schielzeth et al. (2020), https://doi.org/10.1111/2041-210X.13434
+
+
+# install.packages('robustlmm', repos = 'https://www.stats.bris.ac.uk/R/')
+library(robustlmm)
+
+# Read in data
+semanticdecision = read.csv('semanticdecision/data/final_dataset/semanticdecision.csv')
+
+# Model
+semanticdecision_robustlmm =
+  
+  robustlmm::rlmer(z_RTclean ~
+                     
+                     # FIXED EFFECTS
+                     
+                     # Controlled lexical variables
+                     z_word_frequency + z_orthographic_Levenshtein_distance +
+                     
+                     # Controlled word concreteness, important because the task is a word concreteness assessment.
+                     z_word_concreteness +
+                     
+                     # Important control due to the relationship between this variable and vocabulary size (Pexman & Yap, 2018; 
+                     # http://germel.dyndns.org/psyling/pdf/2018_PexmanYap_SemCat_IndividualDifferences.pdf)
+                     z_information_uptake +
+                     
+                     # Control interactions with information uptake to allow a rigorous analysis of the interactions with 
+                     # vocabulary size specified below.
+                     z_word_cooccurrence : z_information_uptake +
+                     z_visual_rating : z_information_uptake +
+                     
+                     # Control interaction between word concreteness and vocabulary size to allow a rigorous analysis of the
+                     # interaction between word co-occurrence and vocabulary size, and the interaction between word visual 
+                     # rating and vocabulary size).
+                     z_word_concreteness : z_vocabulary_size + 
+                     
+                     # Main effects of interest
+                     z_vocabulary_size + z_recoded_participant_gender + 
+                     z_word_cooccurrence + z_visual_rating +
+                     
[…]

### 2022-06-24 semanticdecision/frequentist_analysis/semanticdecision-interactions-with-gender.R

@@ -1,0 +1,119 @@
+
+
+# Part of Study 2: Semantic decision
+
+# Combination of plots:
+# 1. Interaction between gender and distance to word 'abstract'
+# 2. Interaction between gender and visual strength
+# 3. Interaction between gender and word concreteness
+
+library(dplyr)
+library(ggplot2)
+library(patchwork)
+
+# Data set below created in the script 'semanticdecision_data_preparation.R',
+# which is stored in the folder 'semanticdecision/data'
+semanticdecision = 
+  read.csv('semanticdecision/data/final_dataset/semanticdecision.csv')
+
+# Set plain-language labels
+semanticdecision$participant_gender = 
+  ifelse(semanticdecision$participant_gender == 'F', 'Female',
+         ifelse(semanticdecision$participant_gender == 'M', 'Male', NA))
+
+# Model below created in the script 'semanticdecision_lmerTest.R',
+# which is stored in the folder 'semanticdecision/frequentist_analysis'
+semanticdecision_lmerTest = 
+  readRDS('semanticdecision/frequentist_analysis/results/semanticdecision_lmerTest.rds')
+
+# Load custom function
+source('R_functions/alias_interaction_plot.R')
+
+plot1 =
+  alias_interaction_plot(
+    model = semanticdecision_lmerTest,
+    dataset = semanticdecision,
+    x = 'z_word_cooccurrence',
+    fill = 'z_recoded_participant_gender',
+    fill_alias = 'participant_gender',
+    fill_nesting_factor = 'Participant',
+    x_title = "Distance to word 'abstract' (*z*)",
+    y_title = 'Predicted RT (*z*)',
+    fill_title = 'Gender'
+  ) +
+  guides(color = 'none',
+         fill = guide_legend(title = 'Gender', 
+                             # In each key of the legend, replace the 
+                             # default line with a full square.
+                             override.aes = list(linetype = c(0, 0), 
+                                                 alpha = 1), 
+                             # Reverse default order of categories 
+                             # in legend (else, Male would appear 
+                             # first as it was coded as -0.5).
+                             reverse = TRUE)) +
+  theme(plot.tag.position = c(0, 1), 
+        legend.key.width = unit(1.2, 'cm'),
+        legend.margin = margin(t = 21),
+        legend.background = element_blank())
+
+plot2 =
+  alias_interaction_plot(
+    model = semanticdecision_lmerTest,
+    dataset = semanticdecision,
+    x = 'z_visual_rating',
+    fill = 'z_recoded_participant_gender',
[…]

### 2022-06-24 semanticdecision/frequentist_analysis/semanticdecision-interactions-with-vocabulary-size.R

@@ -1,0 +1,78 @@
+
+
+# Part of Study 2: Semantic decision
+
+# Combination of plots:
+# 1. Interaction between vocabulary size and distance to word 'abstract'
+# 2. Interaction between vocabulary size and visual strength
+# 3. Interaction between vocabulary size and word concreteness
+
+library(dplyr)
+library(ggplot2)
+library(patchwork)
+
+# Data set below created in the script 'semanticdecision_data_preparation.R',
+# which is stored in the folder 'semanticdecision/data'
+semanticdecision = 
+  read.csv('semanticdecision/data/final_dataset/semanticdecision.csv')
+
+# Model below created in the script 'semanticdecision_lmerTest.R',
+# which is stored in the folder 'semanticdecision/frequentist_analysis'
+semanticdecision_lmerTest = 
+  readRDS('semanticdecision/frequentist_analysis/results/semanticdecision_lmerTest.rds')
+
+# Load custom function
+source('R_functions/deciles_interaction_plot.R')
+
+plot1 =
+  deciles_interaction_plot(
+    model = semanticdecision_lmerTest,
+    x = 'z_word_cooccurrence',
+    fill = 'z_vocabulary_size',
+    fill_nesting_factor = 'Participant',
+    x_title = "Distance to word 'abstract' (*z*)",
+    y_title = 'Predicted RT (*z*)',
+    fill_title = 'Vocabulary size (*z*, deciles)'
+  ) +
+  theme(plot.tag.position = c(0, 1), 
+        legend.key.width = unit(1.2, 'cm'),
+        legend.margin = margin(t = 21),
+        legend.background = element_blank())
+
+plot2 =
+  deciles_interaction_plot(
+    model = semanticdecision_lmerTest,
+    x = 'z_visual_rating',
+    fill = 'z_vocabulary_size',
+    fill_nesting_factor = 'Participant',
+    x_title = 'Visual strength (*z*)',
+    y_title = 'Predicted RT (*z*)',
+    fill_title = 'Vocabulary size (*z*, deciles)'
+  ) +
+  theme(axis.title.y = element_blank(), 
+        legend.key.width = unit(1.2, 'cm'),
+        legend.margin = margin(t = 21),
+        legend.background = element_blank())
+
+plot3 =
+  deciles_interaction_plot(
+    model = semanticdecision_lmerTest,
+    x = 'z_word_concreteness',
[…]

### 2022-06-24 semanticdecision/frequentist_analysis/semanticdecision_confidence_intervals_plot.R

@@ -1,0 +1,96 @@
+
+
+# Part of Study 2: Semantic decision
+
+# Plot mean and 95% confidence interval for each effect
+
+library(dplyr)
+library(stringr)
+library(ggplot2)
+
+# Load custom function
+source('R_functions/plot_95_confidence_intervals.R')
+
+# Model below created in the script 'semanticdecision_lmerTest.R',
+# which is stored in the folder 'semanticdecision/frequentist_analysis'
+
+KR_summary_semanticdecision_lmerTest =   # Model summary with Kenward-Roger p values
+  readRDS('semanticdecision/frequentist_analysis/results/KR_summary_semanticdecision_lmerTest.rds')
+
+confint_semanticdecision_lmerTest =   # Confidence intervals
+  readRDS('semanticdecision/frequentist_analysis/results/confint_semanticdecision_lmerTest.rds')
+
+# Change labels of effects into plain language
+
+rownames(KR_summary_semanticdecision_lmerTest$coefficients) =
+  rownames(KR_summary_semanticdecision_lmerTest$coefficients) %>%
+  
+  # First, adjust names of variables (both in main effects and in interactions)
+  str_replace(pattern = 'z_word_frequency',
+              replacement = 'Word frequency') %>%
+  str_replace(pattern = 'z_orthographic_Levenshtein_distance',
+              replacement = 'Orthographic Levenshtein distance') %>%
+  str_replace(pattern = 'z_word_concreteness',
+              replacement = 'Word concreteness') %>%
+  str_replace(pattern = 'z_word_cooccurrence',
+              replacement = "Distance to word \'abstract\'") %>%
+  str_replace(pattern = 'z_visual_rating',
+              replacement = 'Visual strength') %>%
+  str_replace(pattern = 'z_information_uptake',
+              replacement = 'Information uptake') %>%
+  str_replace(pattern = 'z_vocabulary_size',
+              replacement = 'Vocabulary size') %>%
+  str_replace(pattern = 'z_recoded_participant_gender',
+              replacement = 'Gender') %>%
+  
+  # Second, adjust order of effects in interactions. In the output from the model, 
+  # the word-level variables of interest (i.e., 'z_word_cooccurrence' and 
+  # 'z_visual_rating') sometimes appeared second in their interactions. For 
+  # better consistency, the code below moves those word-level variables (with 
+  # their new names) to the first position in their interactions. Note that the 
[…]

### 2022-06-24 semanticdecision/frequentist_bayesian_plots/semanticdecision_frequentist_bayesian_plots.R

@@ -1,0 +1,152 @@
+
+
+# Part of Study 2: Semantic decision
+
+# Presenting the frequentist and the Bayesian estimates in the same plot. 
+# For this purpose, the frequentist results are merged into a plot from 
+# brms::mcmc_plot()
+
+
+library(tidyverse)
+library(ggtext)
+library(patchwork)
+library(Cairo)
+
+# Load custom function to present the frequentist and 
+# the Bayesian estimates in the same plot
+source('R_functions/frequentist_bayesian_plot.R')
+
+# Load frequentist coefficients (estimates and confidence intervals)
+
+KR_summary_semanticdecision_lmerTest = 
+  readRDS('semanticdecision/frequentist_analysis/results/KR_summary_semanticdecision_lmerTest.rds')
+
+confint_semanticdecision_lmerTest = 
+  readRDS('semanticdecision/frequentist_analysis/results/confint_semanticdecision_lmerTest.rds')
+
+# Below are the default names of the effects
+rownames(KR_summary_semanticdecision_lmerTest$coefficients)
+rownames(confint_semanticdecision_lmerTest)
+
+# Load Bayesian posterior distributions
+
+semanticdecision_posteriordistributions_informativepriors_exgaussian = 
+  readRDS('semanticdecision/bayesian_analysis/results/semanticdecision_posteriordistributions_informativepriors_exgaussian.rds')
+
+semanticdecision_posteriordistributions_weaklyinformativepriors_exgaussian =
+  readRDS('semanticdecision/bayesian_analysis/results/semanticdecision_posteriordistributions_weaklyinformativepriors_exgaussian.rds')
+
+semanticdecision_posteriordistributions_diffusepriors_exgaussian = 
+  readRDS('semanticdecision/bayesian_analysis/results/semanticdecision_posteriordistributions_diffusepriors_exgaussian.rds')
+
+# Below are the default names of the effects
+levels(semanticdecision_posteriordistributions_diffusepriors_exgaussian$data$parameter)
+
+
+# Create a vector containing the names of the effects. This vector will be passed 
+# to the plotting function.
+
+new_labels = 
+  
+  semanticdecision_posteriordistributions_diffusepriors_exgaussian$data$parameter %>% 
+  unique %>%
+  
+  # Remove the default 'b_' from the beginning of each effect
+  str_remove('^b_') %>%
+  
+  # Put Intercept in parentheses
+  str_replace(pattern = 'Intercept', replacement = '(Intercept)') %>%
+  
[…]

### 2022-06-24 semanticpriming/analysis_with_visualsimilarity/semanticpriming_with_visualsimilarity_confidence_intervals_plot.R

@@ -1,0 +1,139 @@
+
+
+# Part of Study 1: Semantic priming
+
+# Plot mean and 95% confidence interval for each effect
+
+library(dplyr)
+library(stringr)
+library(ggplot2)
+
+# Load custom function
+source('R_functions/plot_95_confidence_intervals.R')
+
+# Model below created in the script 'semanticpriming_with_visualsimilarity_lmerTest.R',
+# which is stored in the folder 'semanticpriming/analysis_with_visualsimilarity'
+
+KR_summary_semanticpriming_with_visualsimilarity_lmerTest =   # Model summary with Kenward-Roger p values
+  readRDS('semanticpriming/analysis_with_visualsimilarity/results/KR_summary_semanticpriming_with_visualsimilarity_lmerTest.rds')
+
+confint_semanticpriming_with_visualsimilarity_lmerTest =   # Confidence intervals
+  readRDS('semanticpriming/analysis_with_visualsimilarity/results/confint_semanticpriming_with_visualsimilarity_lmerTest.rds')
+
+# Change labels of effects into plain language
+
+rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) =
+  rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) %>%
+  
+  # First, adjust names of variables (both in main effects and in interactions)
+  str_replace(pattern = 'z_target_word_frequency',
+              replacement = 'Target-word frequency') %>%
+  str_replace(pattern = 'z_target_number_syllables',
+              replacement = 'Number of target-word syllables') %>%
+  str_replace(pattern = 'z_word_concreteness_diff',
+              replacement = 'Word-concreteness difference') %>%
+  str_replace(pattern = 'z_cosine_similarity',
+              replacement = 'Language-based similarity') %>%
+  str_replace(pattern = 'z_visual_rating_diff',
+              replacement = 'Visual-strength difference') %>%
+  str_replace(pattern = 'z_visual_similarity',
+              replacement = 'Vision-based similarity') %>%
+  str_replace(pattern = 'z_attentional_control',
+              replacement = 'Attentional control') %>%
+  str_replace(pattern = 'z_vocabulary_size',
+              replacement = 'Vocabulary size') %>%
+  str_replace(pattern = 'z_recoded_participant_gender',
+              replacement = 'Gender') %>%
+  str_replace(pattern = 'z_recoded_interstimulus_interval',
+              replacement = 'SOA') %>%
[…]

### 2022-06-24 semanticpriming/analysis_with_visualsimilarity/semanticpriming_with_visualsimilarity_lmerTest.R

@@ -1,0 +1,145 @@
+
+
+# Part of Study 1: Semantic priming
+
+library(dplyr)  # data wrangling
+# The following lme4-relevant package was installed before lme4 to avoid a conflict 
+# noted at https://cran.r-project.org/web/packages/lme4/lme4.pdf
+library(RcppEigen)
+library(lme4)   # Mixed-effects models (package version 1.1-26)
+library(lmerTest)  # Compute p values (package version 3.1-3)
+library(MuMIn)   # R^2
+
+# Read in data
+semanticpriming_with_visualsimilarity = 
+  read.csv('semanticpriming/data/subset_with_visualsimilarity/semanticpriming_with_visualsimilarity.csv')
+
+# MODEL
+# Measure running time
+system.time({
+  
+  # Model name
+  semanticpriming_with_visualsimilarity_lmerTest =
+    
+    lmerTest::lmer( 
+      
+      # Dependent variable
+      z_target.RT ~
+        
+        # FIXED EFFECTS
+        
+        # Controlled lexical variables
+        z_target_word_frequency + z_target_number_syllables +
+        
+        # Controlled semantic variable
+        z_word_concreteness_diff +
+        
+        # Control interactions with word concreteness to allow a rigorous analysis of the 
+        # interactions with visual-strength difference and with visual similarity, which 
+        # are specified further below.
+        z_word_concreteness_diff : z_vocabulary_size + 
+        z_word_concreteness_diff : z_recoded_interstimulus_interval + 
+        z_word_concreteness_diff : z_recoded_participant_gender + 
+        
+        # Important control due to the relationship between this variable and vocabulary size 
+        # (Yap et al., 2017; https://www.montana.edu/khutchison/documents/YHT%20in%20press.pdf)
+        z_attentional_control +
+        
+        # Control interactions with attentional control to allow a rigorous analysis of
+        # the interactions with vocabulary size specified further below.
+        z_cosine_similarity : z_attentional_control +
+        z_visual_rating_diff : z_attentional_control +
+        z_visual_similarity : z_attentional_control +
+        
+        # Main effects of interest
+        z_vocabulary_size + z_recoded_participant_gender + 
+        z_cosine_similarity + z_visual_rating_diff + 
+        z_visual_similarity + z_recoded_interstimulus_interval +
+        
+        # Interactions of interest
+        z_cosine_similarity : z_vocabulary_size +
[…]

### 2022-06-24 semanticpriming/bayesian_analysis/divergent_models/semanticpriming_brms_diffusepriors_exgaussian.R

@@ -1,0 +1,125 @@
+
+
+# Part of Study 1: Semantic priming
+
+# Part of Bayesian analysis
+
+# Model with diffuse priors (SD = 0.3)
+
+
+library(dplyr)
+library(brms)  # Version 2.17.0
+
+# Read in data
+semanticpriming = read.csv('semanticpriming/data/final_dataset/semanticpriming.csv')
+
+# Define priors
+
+# In the function `set_prior` used below, the argument `class` often represents
+# groups of parameters. For instance, class 'b' refers to fixed effects.
+
+# Since most priors do not specify the negative/positive direction of effects,
+# distributions are first specified for entire classes, and those are
+# overridden wherever a direction is specified.
+
+diffuse_priors =
+  c(set_prior('normal(0, 0.3)', class = 'Intercept'),
+    set_prior('normal(0, 0.3)', class = 'b'),
+    set_prior('normal(0.1, 0.3)', class = 'b',
+              coef = 'z_target_number_syllables'),
+    set_prior('normal(-0.1, 0.3)', class = 'b',
+              coef = 'z_target_word_frequency'),
+    set_prior('normal(0, 0.3)', class = 'sd'),  # automatically truncated to keep positive values only
+    set_prior('normal(0, 0.3)', class = 'sigma'),  # automatically truncated to keep positive values only
+    set_prior('lkj(2)', class = 'cor')  # standard, regularising prior on random-effects covariance to aid convergence
+  )
+
+# Model
+
+semanticpriming_brms_diffusepriors_exgaussian =
+  
+  brm(
+    
+    # Dependent variable
+    z_target.RT ~
+      
+      # FIXED EFFECTS
+      
+      # Controlled lexical variables
+      z_target_word_frequency + z_target_number_syllables +
+      
+      # Controlled semantic variable
+      z_word_concreteness_diff +
+      
+      # Control interactions with word concreteness to allow a rigorous analysis of the
+      # interactions with visual-strength difference that are specified further below.
+      z_word_concreteness_diff : z_vocabulary_size +
+      z_word_concreteness_diff : z_recoded_interstimulus_interval +
+      z_word_concreteness_diff : z_recoded_participant_gender +
+      
+      # Important control due to the relationship between this variable and vocabulary size
+      # (Yap et al., 2017; https://www.montana.edu/khutchison/documents/YHT%20in%20press.pdf)
+      z_attentional_control +
+      
[…]

### 2022-06-24 semanticpriming/bayesian_analysis/divergent_models/semanticpriming_brms_weaklyinformativepriors_exgaussian.R

@@ -1,0 +1,125 @@
+
+
+# Part of Study 1: Semantic priming
+
+# Part of Bayesian analysis
+
+# Model with weakly-informative priors (SD = 0.2)
+
+
+library(dplyr)
+library(brms)  # Version 2.17.0
+
+# Read in data
+semanticpriming = read.csv('semanticpriming/data/final_dataset/semanticpriming.csv')
+
+# Define priors
+
+# In the function `set_prior` used below, the argument `class` often represents
+# groups of parameters. For instance, class 'b' refers to fixed effects.
+
+# Since most priors do not specify the negative/positive direction of effects,
+# distributions are first specified for entire classes, and those are
+# overridden wherever a direction is specified.
+
+weaklyinformative_priors =
+  c(set_prior('normal(0, 0.2)', class = 'Intercept'),
+    set_prior('normal(0, 0.2)', class = 'b'),
+    set_prior('normal(0.1, 0.2)', class = 'b',
+              coef = 'z_target_number_syllables'),
+    set_prior('normal(-0.1, 0.2)', class = 'b',
+              coef = 'z_target_word_frequency'),
+    set_prior('normal(0, 0.2)', class = 'sd'),  # automatically truncated to keep positive values only
+    set_prior('normal(0, 0.2)', class = 'sigma'),  # automatically truncated to keep positive values only
+    set_prior('lkj(2)', class = 'cor')  # standard, regularising prior on random-effects covariance to aid convergence
+  )
+
+# Model
+
+semanticpriming_brms_weaklyinformativepriors_exgaussian =
+  
+  brm(
+    
+    # Dependent variable
+    z_target.RT ~
+      
+      # FIXED EFFECTS
+      
+      # Controlled lexical variables
+      z_target_word_frequency + z_target_number_syllables +
+      
+      # Controlled semantic variable
+      z_word_concreteness_diff +
+      
+      # Control interactions with word concreteness to allow a rigorous analysis of the
+      # interactions with visual-strength difference that are specified further below.
+      z_word_concreteness_diff : z_vocabulary_size +
+      z_word_concreteness_diff : z_recoded_interstimulus_interval +
+      z_word_concreteness_diff : z_recoded_participant_gender +
+      
+      # Important control due to the relationship between this variable and vocabulary size
+      # (Yap et al., 2017; https://www.montana.edu/khutchison/documents/YHT%20in%20press.pdf)
+      z_attentional_control +
+      
[…]

### 2022-06-24 semanticpriming/bayesian_analysis/posterior_predictive_checks/semanticpriming_posteriorpredictivechecks.R

@@ -1,0 +1,68 @@
+
+
+# Part of Study 1: Semantic priming
+
+# Plots of the posterior predictive checks
+
+# Note. Only the plots are created in this script. The posterior predictive 
+# checks themselves were created in the script of each model--e.g., in
+# 'semanticpriming/bayesian_analysis/semanticpriming_brms_informativepriors_exgaussian.R'
+
+
+library(dplyr)
+library(ggplot2)
+library(patchwork)
+library(Cairo)
+
+# Load custom plotting function
+source('R_functions/plot_posteriorpredictivecheck.R')
+
+# Load posterior predictive checks
+
+semanticpriming_posteriorpredictivecheck_informativepriors_exgaussian =
+  readRDS('semanticpriming/bayesian_analysis/posterior_predictive_checks/results/semanticpriming_posteriorpredictivecheck_informativepriors_exgaussian.rds')
+
+# semanticpriming_posteriorpredictivecheck_weaklyinformativepriors_exgaussian =
+#   readRDS('semanticpriming/bayesian_analysis/posterior_predictive_checks/results/semanticpriming_posteriorpredictivecheck_weaklyinformativepriors_exgaussian.rds')
+
+semanticpriming_posteriorpredictivecheck_diffusepriors_exgaussian =
+  readRDS('semanticpriming/bayesian_analysis/posterior_predictive_checks/results/semanticpriming_posteriorpredictivecheck_diffusepriors_exgaussian.rds')
+
+
+# Create plots, beginning with the informative-prior model
+
+semanticpriming_posteriorpredictivecheck_informativepriors_exgaussian =
+  semanticpriming_posteriorpredictivecheck_informativepriors_exgaussian %>%
+  plot_posteriorpredictivecheck() + 
+  ggtitle('Prior *SD* = 0.1') + xlab('RT (*z*)') + 
+  theme(legend.position = 'none')
+
+# Weakly-informative-prior model
+semanticpriming_posteriorpredictivecheck_weaklyinformativepriors_exgaussian =
+  semanticpriming_posteriorpredictivecheck_weaklyinformativepriors_exgaussian %>%
+  plot_posteriorpredictivecheck() + 
+  ggtitle('Prior *SD* = 0.2') + xlab('RT (*z*)') + 
+  theme(legend.position = 'none', axis.title.y = element_blank())
+
+# Diffuse-prior model
[…]

### 2022-06-24 semanticpriming/bayesian_analysis/prior_predictive_checks/semanticpriming_priorpredictivecheck_diffusepriors_exgaussian.R

@@ -1,0 +1,264 @@
+
+
+# Part of Study 1: Semantic priming
+
+# Part of Bayesian analysis
+
+# Prior predictive checks are performed to verify the adequacy of the priors
+# (Nicenboim et al., 2022, https://vasishth.github.io/bayescogsci). For this 
+# purpose, the results from three priors are compared below. These priors 
+# differ in their standard deviations, which are—respectively—0.1 (priors 
+# labelled 'informative'), 0.2 ('weakly-informative') and 0.3 ('diffuse'). 
+# The rationale for these priors is provided in the 'bayesian_priors' 
+# folder, located in the root directory of this project. An ex-gaussian 
+# distribution is tested in this script (Rodríguez-Ferreiro et al., 2020; 
+# see supplementary materials via https://doi.org/10.7717/peerj.9511).
+# Due to computational constraints, the random-effects structures of these
+# models are slightly smaller than those of the final models, and the
+# number of iterations is lower.
+
+
+library(dplyr)
+library(brms)  # Version 2.17.0
+library(ggplot2)
+library(ggtext)
+library(patchwork)
+
+
+# Begin by checking what parameters of the model can be assigned priors
+
+# Read in data
+semanticpriming = read.csv('semanticpriming/data/final_dataset/semanticpriming.csv')
+
+
+get_prior(
+  
+  # Dependent variable
+  z_target.RT ~
+    
+    # FIXED EFFECTS
+    
+    # Controlled lexical variables
+    z_target_word_frequency + z_target_number_syllables +
+    
+    # Controlled semantic variable
+    z_word_concreteness_diff +
+    
+    # Control interactions with word concreteness to allow a rigorous analysis of the
+    # interactions with visual-strength difference that are specified further below.
+    z_word_concreteness_diff : z_vocabulary_size +
+    z_word_concreteness_diff : z_recoded_interstimulus_interval +
+    z_word_concreteness_diff : z_recoded_participant_gender +
+    
+    # Important control due to the relationship between this variable and vocabulary size
+    # (Yap et al., 2017; https://www.montana.edu/khutchison/documents/YHT%20in%20press.pdf)
+    z_attentional_control +
+    
+    # Control interactions with attentional control to allow a rigorous analysis of
+    # the interactions with vocabulary size specified further below.
[…]

### 2022-06-24 semanticpriming/bayesian_analysis/prior_predictive_checks/semanticpriming_priorpredictivecheck_informativepriors.R

@@ -1,0 +1,244 @@
+
+
+# Part of Study 1: Semantic priming
+
+# Part of Bayesian analysis
+
+# Prior predictive checks are performed to verify the adequacy of the priors
+# (Nicenboim et al., 2022, https://vasishth.github.io/bayescogsci). For this 
+# purpose, the results from three priors are compared below. These priors 
+# differ in their standard deviations, which are—respectively—0.1 (priors 
+# labelled 'informative'), 0.2 ('weakly-informative') and 0.3 ('diffuse'). 
+# The rationale for these priors is provided in the 'bayesian_priors' 
+# folder, located in the root directory of this project. A gaussian 
+# distribution is tested in this script (Rodríguez-Ferreiro et al., 2020; 
+# see supplementary materials via https://doi.org/10.7717/peerj.9511).
+# Due to computational constraints, the random-effects structures of these
+# models are slightly smaller than those of the final models, and the
+# number of iterations is lower.
+
+
+library(dplyr)
+library(brms)  # Version 2.17.0
+library(ggplot2)
+library(ggtext)
+library(patchwork)
+
+
+# Begin by checking what parameters of the model can be assigned priors
+
+# Read in data
+semanticpriming = read.csv('semanticpriming/data/final_dataset/semanticpriming.csv')
+
+
+get_prior(
+  
+  # Dependent variable
+  z_target.RT ~
+    
+    # FIXED EFFECTS
+    
+    # Controlled lexical variables
+    z_target_word_frequency + z_target_number_syllables +
+    
+    # Controlled semantic variable
+    z_word_concreteness_diff +
+    
+    # Control interactions with word concreteness to allow a rigorous analysis of the
+    # interactions with visual-strength difference that are specified further below.
+    z_word_concreteness_diff : z_vocabulary_size +
+    z_word_concreteness_diff : z_recoded_interstimulus_interval +
+    z_word_concreteness_diff : z_recoded_participant_gender +
+    
+    # Important control due to the relationship between this variable and vocabulary size
+    # (Yap et al., 2017; https://www.montana.edu/khutchison/documents/YHT%20in%20press.pdf)
+    z_attentional_control +
+    
+    # Control interactions with attentional control to allow a rigorous analysis of
+    # the interactions with vocabulary size specified further below.
+    z_cosine_similarity : z_attentional_control +
[…]

### 2022-06-24 semanticpriming/bayesian_analysis/prior_predictive_checks/semanticpriming_priorpredictivecheck_informativepriors_exgaussian.R

@@ -1,0 +1,263 @@
+
+
+# Part of Study 1: Semantic priming
+
+# Part of Bayesian analysis
+
+# Prior predictive checks are performed to verify the adequacy of the priors
+# (Nicenboim et al., 2022, https://vasishth.github.io/bayescogsci). For this 
+# purpose, the results from three priors are compared below. These priors 
+# differ in their standard deviations, which are—respectively—0.1 (priors 
+# labelled 'informative'), 0.2 ('weakly-informative') and 0.3 ('diffuse'). 
+# The rationale for these priors is provided in the 'bayesian_priors' 
+# folder, located in the root directory of this project. An ex-gaussian 
+# distribution is tested in this script (Rodríguez-Ferreiro et al., 2020; 
+# see supplementary materials via https://doi.org/10.7717/peerj.9511).
+# Due to computational constraints, the random-effects structures of these
+# models are slightly smaller than those of the final models, and the
+# number of iterations is lower.
+
+
+library(dplyr)
+library(brms)  # Version 2.17.0
+library(ggplot2)
+library(ggtext)
+library(patchwork)
+
+
+# Begin by checking what parameters of the model can be assigned priors
+
+# Read in data
+semanticpriming = read.csv('semanticpriming/data/final_dataset/semanticpriming.csv')
+
+
+get_prior(
+  
+  # Dependent variable
+  z_target.RT ~
+    
+    # FIXED EFFECTS
+    
+    # Controlled lexical variables
+    z_target_word_frequency + z_target_number_syllables +
+    
+    # Controlled semantic variable
+    z_word_concreteness_diff +
+    
+    # Control interactions with word concreteness to allow a rigorous analysis of the
+    # interactions with visual-strength difference that are specified further below.
+    z_word_concreteness_diff : z_vocabulary_size +
+    z_word_concreteness_diff : z_recoded_interstimulus_interval +
+    z_word_concreteness_diff : z_recoded_participant_gender +
+    
+    # Important control due to the relationship between this variable and vocabulary size
+    # (Yap et al., 2017; https://www.montana.edu/khutchison/documents/YHT%20in%20press.pdf)
+    z_attentional_control +
+    
+    # Control interactions with attentional control to allow a rigorous analysis of
+    # the interactions with vocabulary size specified further below.
+    z_cosine_similarity : z_attentional_control +
[…]

### 2022-06-24 semanticpriming/bayesian_analysis/prior_predictive_checks/semanticpriming_priorpredictivecheck_weaklyinformativepriors.R

@@ -1,0 +1,244 @@
+
+
+# Part of Study 1: Semantic priming
+
+# Part of Bayesian analysis
+
+# Prior predictive checks are performed to verify the adequacy of the priors
+# (Nicenboim et al., 2022, https://vasishth.github.io/bayescogsci). For this 
+# purpose, the results from three priors are compared below. These priors 
+# differ in their standard deviations, which are—respectively—0.1 (priors 
+# labelled 'informative'), 0.2 ('weakly-informative') and 0.3 ('diffuse'). 
+# The rationale for these priors is provided in the 'bayesian_priors' 
+# folder, located in the root directory of this project. A gaussian 
+# distribution is tested in this script (Rodríguez-Ferreiro et al., 2020; 
+# see supplementary materials via https://doi.org/10.7717/peerj.9511).
+# Due to computational constraints, the random-effects structures of these
+# models are slightly smaller than those of the final models, and the
+# number of iterations is lower.
+
+
+library(dplyr)
+library(brms)  # Version 2.17.0
+library(ggplot2)
+library(ggtext)
+library(patchwork)
+
+
+# Begin by checking what parameters of the model can be assigned priors
+
+# Read in data
+semanticpriming = read.csv('semanticpriming/data/final_dataset/semanticpriming.csv')
+
+
+get_prior(
+  
+  # Dependent variable
+  z_target.RT ~
+    
+    # FIXED EFFECTS
+    
+    # Controlled lexical variables
+    z_target_word_frequency + z_target_number_syllables +
+    
+    # Controlled semantic variable
+    z_word_concreteness_diff +
+    
+    # Control interactions with word concreteness to allow a rigorous analysis of the
+    # interactions with visual-strength difference that are specified further below.
+    z_word_concreteness_diff : z_vocabulary_size +
+    z_word_concreteness_diff : z_recoded_interstimulus_interval +
+    z_word_concreteness_diff : z_recoded_participant_gender +
+    
+    # Important control due to the relationship between this variable and vocabulary size
+    # (Yap et al., 2017; https://www.montana.edu/khutchison/documents/YHT%20in%20press.pdf)
+    z_attentional_control +
+    
+    # Control interactions with attentional control to allow a rigorous analysis of
+    # the interactions with vocabulary size specified further below.
+    z_cosine_similarity : z_attentional_control +
[…]

### 2022-06-24 semanticpriming/bayesian_analysis/prior_predictive_checks/semanticpriming_priorpredictivecheck_weaklyinformativepriors_exgaussian.R

@@ -1,0 +1,264 @@
+
+
+# Part of Study 1: Semantic priming
+
+# Part of Bayesian analysis
+
+# Prior predictive checks are performed to verify the adequacy of the priors
+# (Nicenboim et al., 2022, https://vasishth.github.io/bayescogsci). For this 
+# purpose, the results from three priors are compared below. These priors 
+# differ in their standard deviations, which are—respectively—0.1 (priors 
+# labelled 'informative'), 0.2 ('weakly-informative') and 0.3 ('diffuse'). 
+# The rationale for these priors is provided in the 'bayesian_priors' 
+# folder, located in the root directory of this project. An ex-gaussian 
+# distribution is tested in this script (Rodríguez-Ferreiro et al., 2020; 
+# see supplementary materials via https://doi.org/10.7717/peerj.9511).
+# Due to computational constraints, the random-effects structures of these
+# models are slightly smaller than those of the final models, and the
+# number of iterations is lower.
+
+
+library(dplyr)
+library(brms)  # Version 2.17.0
+library(ggplot2)
+library(ggtext)
+library(patchwork)
+
+
+# Begin by checking what parameters of the model can be assigned priors
+
+# Read in data
+semanticpriming = read.csv('semanticpriming/data/final_dataset/semanticpriming.csv')
+
+
+get_prior(
+  
+  # Dependent variable
+  z_target.RT ~
+    
+    # FIXED EFFECTS
+    
+    # Controlled lexical variables
+    z_target_word_frequency + z_target_number_syllables +
+    
+    # Controlled semantic variable
+    z_word_concreteness_diff +
+    
+    # Control interactions with word concreteness to allow a rigorous analysis of the
+    # interactions with visual-strength difference that are specified further below.
+    z_word_concreteness_diff : z_vocabulary_size +
+    z_word_concreteness_diff : z_recoded_interstimulus_interval +
+    z_word_concreteness_diff : z_recoded_participant_gender +
+    
+    # Important control due to the relationship between this variable and vocabulary size
+    # (Yap et al., 2017; https://www.montana.edu/khutchison/documents/YHT%20in%20press.pdf)
+    z_attentional_control +
+    
+    # Control interactions with attentional control to allow a rigorous analysis of
+    # the interactions with vocabulary size specified further below.
[…]

### 2022-06-24 semanticpriming/bayesian_analysis/semanticpriming_brms_weaklyinformativepriors_exgaussian.R

@@ -1,0 +1,156 @@
+
+
+# Part of Study 1: Semantic priming
+
+# Part of Bayesian analysis
+
+# Model with weakly-informative priors (SD = 0.2)
+
+
+library(dplyr)
+library(brms)  # Version 2.17.0
+
+# Read in data
+semanticpriming = read.csv('semanticpriming/data/final_dataset/semanticpriming.csv')
+
+# Define priors
+
+# In the function `set_prior` used below, the argument `class` often represents
+# groups of parameters. For instance, class 'b' refers to fixed effects.
+
+# Since most priors do not specify the negative/positive direction of effects,
+# distributions are first specified for entire classes, and those are
+# overridden wherever a direction is specified.
+
+weaklyinformative_priors =
+  c(set_prior('normal(0, 0.2)', class = 'Intercept'),
+    set_prior('normal(0, 0.2)', class = 'b'),
+    set_prior('normal(0.1, 0.2)', class = 'b',
+              coef = 'z_target_number_syllables'),
+    set_prior('normal(-0.1, 0.2)', class = 'b',
+              coef = 'z_target_word_frequency'),
+    set_prior('normal(0, 0.2)', class = 'sd'),  # automatically truncated to keep positive values only
+    set_prior('normal(0, 0.2)', class = 'sigma'),  # automatically truncated to keep positive values only
+    set_prior('lkj(2)', class = 'cor')  # standard, regularising prior on random-effects covariance to aid convergence
+  )
+
+# Model
+
+semanticpriming_brms_weaklyinformativepriors_exgaussian =
+  
+  brm(
+    
+    # Dependent variable
+    z_target.RT ~
+      
+      # FIXED EFFECTS
+      
+      # Controlled lexical variables
+      z_target_word_frequency + z_target_number_syllables +
+      
+      # Controlled semantic variable
+      z_word_concreteness_diff +
+      
+      # Control interactions with word concreteness to allow a rigorous analysis of the
+      # interactions with visual-strength difference that are specified further below.
+      z_word_concreteness_diff : z_vocabulary_size +
+      z_word_concreteness_diff : z_recoded_interstimulus_interval +
+      z_word_concreteness_diff : z_recoded_participant_gender +
+      
+      # Important control due to the relationship between this variable and vocabulary size
+      # (Yap et al., 2017; https://www.montana.edu/khutchison/documents/YHT%20in%20press.pdf)
+      z_attentional_control +
+      
[…]

### 2022-06-24 semanticpriming/data/semanticpriming_data_preparation.R

@@ -1,0 +1,535 @@
+
+
+# Part of Study 1: Semantic priming
+
+# Preparation of final data set by merging several data sets from previous studies.
+
+# All primary data sets were last downloaded on 3 January 2022.
+
+
+# install.packages('httr')          # Data download
+# install.packages('readxl')        # Data reading
+# install.packages('readr')         # Data reading
+# install.packages('dplyr')         # Data wrangling
+# install.packages('purrr')         # Data wrangling
+# install.packages('Matrix')        # Data wrangling
+# install.packages('LSAfun')        # Computation of cosine similarity (not using the LSA space but one described below)
+# install.packages('standardize')   # Used to cluster-mean center within-participants variables 
+
+library(httr)
+library(readxl)
+library(readr)
+library(dplyr)
+library(purrr)
+library(Matrix)
+library(LSAfun)
+library(standardize)
+
+
+# DATA SET 1. Lexical decision task from the Semantic Priming Project (Hutchison et al., 2013; 
+# https://doi.org/10.3758/s13428-012-0304-z), downloaded from 
+# https://www.montana.edu/attmemlab/documents/all%20ldt%20subs_all%20trials3.xlsx
+
+# Note on reproducibility
+# The code below was used to download and save the data set in the folder 'semanticpriming/data/primary_datasets'. 
+# To prevent any influence from future changes to the original data set online, the code below was protected (i.e., 
+# commented out) by inserting the snippet `# Protected code # ` at the beginning of each line. If desired, the code
+# can be run by removing the protective snippet from every line.
+
+# Protected code # GET('https://www.montana.edu/attmemlab/documents/all%20ldt%20subs_all%20trials3.xlsx', 
+# Protected code #     write_disk(tf <- tempfile(fileext = ".xlsx")))
+# Protected code # read_excel(tf) %>%
+# Protected code #   write.csv('semanticpriming/data/primary_datasets/Hutchison_etal_2013_semanticpriming_lexicaldecision.csv', 
+# Protected code #             row.names = FALSE)
+
+# Read in data set
+semanticpriming = 
+  read.csv('semanticpriming/data/primary_datasets/Hutchison_etal_2013_semanticpriming_lexicaldecision.csv')
+
+# Rename columns
+semanticpriming = 
+  semanticpriming %>%
+  rename(Participant = Subject, target_word = target,
+         prime_word = prime, interstimulus_interval = isi)
+
[…]

### 2022-06-24 semanticpriming/frequentist_analysis/model_diagnostics/semanticpriming_GLMM.R

@@ -1,0 +1,153 @@
+
+
+# Part of Study 1: Semantic priming
+
+# Generalized linear mixed-effects model motivated by the non-normal distribution of the residuals 
+# from the linear mixed-effects model (Lo & Andrews, 2015). The dependent variable used in this 
+# model was raw RT, rather than standardized, RT, as none of the families of distributions tested 
+# by Lo and Andrews (2015) allow values below zero (see Table 15.2 in Fox, 2015). We used the 
+# Inverse Gaussian family with an identity link, which was the family that yielded the most normal 
+# residuals in the analysis by Lo and Andrews.
+# 
+# P values were calculated through parametric bootstrapping, which is the most robust method for 
+# a GLMM, as the Kenward-Roger and Satterthwaite methods are not possible for these models (Luke, 
+# 2017; Singmann et al., 2021).
+
+# Further background:
+# Knief and Forstmeier (2021), https://doi.org/10.1101/498931
+# Schielzeth et al. (2020), https://doi.org/10.1111/2041-210X.13434
+# 
+# References
+# 
+# Fox, J. (2016). Generalized Linear Models. In Applied regression analysis and generalized 
+# linear models (Third Edition, pp. 418–472). SAGE.
+# 
+# Lo, S, & Andrews, S. (2015). To transform or not to transform: Using generalized linear mixed 
+# models to analyse reaction time data. Frontiers in Psychology, 6, 1171. 
+# https://doi.org/10.3389/fpsyg.2015.01171
+# 
+# Luke, S. G. (2017). Evaluating significance in linear mixed-effects models in R. Behavior 
+# Research Methods, 49(4), 1494--1502. https://doi.org/10.3758/s13428-016-0809-y
+# 
+# Singmann, H., Bolker, B., Westfall, J., Aust, F., &  Ben-Sachar, M. S. (2021). Package 'afex'. 
+# CRAN. https://cran.r-project.org/web/packages/afex/afex.pdf
+
+
+# install.packages('afex', repos = 'https://www.stats.bris.ac.uk/R/')
+library(afex)  # Compute p values (package version 3.1-3) using parametric bootstrapping (see information below)
+library(parallel)  # Parallel processing for a faster computation (included in base R)
+
+# Read in data
+semanticpriming = read.csv('semanticpriming/data/final_dataset/semanticpriming.csv')
+
+# Enable parallel clusters, which allows faster processing if several cores available.
[…]

### 2022-06-24 semanticpriming/frequentist_analysis/model_diagnostics/semanticpriming_robustlmm.R

@@ -1,0 +1,136 @@
+
+
+# Part of Study 1: Semantic priming
+
+# This {robustlmm} model is used to validate the results of the standard mixed-effects model, 
+# in which the residuals were not normally distributed. The robustlmm package detects and 
+# removes outliers that hinder the normality of the residuals.
+
+# Package paper: Koller (2016), http://dx.doi.org/10.18637/jss.v075.i06
+
+# Use case: Sleegers et al. (2020), https://doi.org/10.1177/1948550620966153
+
+# Further background:
+# Knief and Forstmeier (2021), https://doi.org/10.1101/498931
+# Schielzeth et al. (2020), https://doi.org/10.1111/2041-210X.13434
+
+
+# install.packages('robustlmm', repos = 'https://www.stats.bris.ac.uk/R/')
+library(robustlmm)
+
+# Read in data
+semanticpriming = read.csv('semanticpriming/data/final_dataset/semanticpriming.csv')
+
+# Model
+semanticpriming_robustlmm = 
+  
+  robustlmm::rlmer(
+    
+    # Dependent variable
+    z_target.RT ~
+      
+      # FIXED EFFECTS
+      
+      # Controlled lexical variables
+      z_target_word_frequency + z_target_number_syllables +
+      
+      # Controlled semantic variable
+      z_word_concreteness_diff +
+      
+      # Control interactions with word concreteness to allow a rigorous analysis of the 
+      # interactions with visual-strength difference that are specified further below.
+      z_word_concreteness_diff : z_vocabulary_size + 
+      z_word_concreteness_diff : z_recoded_interstimulus_interval + 
+      z_word_concreteness_diff : z_recoded_participant_gender + 
+      
+      # Important control due to the relationship between this variable and vocabulary size 
+      # (Yap et al., 2017; https://www.montana.edu/khutchison/documents/YHT%20in%20press.pdf)
+      z_attentional_control +
+      
+      # Control interactions with attentional control to allow a rigorous analysis of
+      # the interactions with vocabulary size specified further below.
+      z_cosine_similarity : z_attentional_control +
+      z_visual_rating_diff : z_attentional_control +
+      
+      # Main effects of interest
+      z_vocabulary_size + z_recoded_participant_gender + z_cosine_similarity + 
+      z_visual_rating_diff + z_recoded_interstimulus_interval +
+      
[…]

### 2022-06-24 semanticpriming/frequentist_analysis/semanticpriming-interactions-with-gender.R

@@ -1,0 +1,89 @@
+
+
+# Part of Study 1: Semantic priming
+
+# Combination of plots:
+# 1. Interaction between gender and cosine similarity
+# 2. Interaction between gender and visual rating difference
+
+library(dplyr)
+library(patchwork)
+library(ggplot2)
+
+# Data set below created in the script 'semanticpriming_data_preparation.R',
+# which is stored in the folder 'semanticpriming/data'
+semanticpriming = 
+  read.csv('semanticpriming/data/final_dataset/semanticpriming.csv')
+
+# Consolidate gender labels
+semanticpriming$participant_gender = 
+  ifelse(semanticpriming$participant_gender == 'f', 'Female',
+         ifelse(semanticpriming$participant_gender == 'F', 'Female',
+                ifelse(semanticpriming$participant_gender == 'wf', 'Female',
+                       ifelse(semanticpriming$participant_gender == 'm', 'Male',
+                              ifelse(semanticpriming$participant_gender == 'M', 'Male',
+                                     semanticpriming$participant_gender)))))
+
+# Model below created in the script 'semanticpriming_lmerTest.R',
+# which is stored in the folder 'semanticpriming/frequentist_analysis'
+semanticpriming_lmerTest = 
+  readRDS('semanticpriming/frequentist_analysis/results/semanticpriming_lmerTest.rds')
+
+# Load custom function
+source('R_functions/alias_interaction_plot.R')
+
+plot1 =
+  alias_interaction_plot(
+    model = semanticpriming_lmerTest,
+    dataset = semanticpriming,
+    x = 'z_cosine_similarity',
+    fill = 'z_recoded_participant_gender',
+    fill_alias = 'participant_gender',
+    fill_nesting_factor = 'Participant',
+    x_title = 'Language-based similarity (*z*)',
+    y_title = 'Predicted RT (*z*)',
+    fill_title = 'Gender'
+  ) +
+  guides(color = 'none',
+         fill = guide_legend(title = 'Gender', 
+                             # In each key of the legend, replace the 
+                             # default line with a full square.
+                             override.aes = list(linetype = c(0, 0), 
+                                                 alpha = 1), 
+                             # Reverse default order of categories 
+                             # in legend (else, Male would appear 
+                             # first as it was coded as -0.5).
+                             reverse = TRUE)) +
+  theme(plot.tag.position = c(0, 1), legend.position = c(.85, .81))
+
+plot2 = 
[…]

### 2022-06-24 semanticpriming/frequentist_analysis/semanticpriming_lmerTest.R

@@ -1,0 +1,136 @@
+
+
+# Part of Study 1: Semantic priming
+
+library(dplyr)  # data wrangling
+# The following lme4-relevant package was installed before lme4 to avoid a conflict 
+# noted at https://cran.r-project.org/web/packages/lme4/lme4.pdf
+library(RcppEigen)
+library(lme4)   # Mixed-effects models (package version 1.1-26)
+library(lmerTest)  # Compute p values (package version 3.1-3)
+library(MuMIn)   # R^2
+
+# Read in data
+semanticpriming = read.csv('semanticpriming/data/final_dataset/semanticpriming.csv')
+
+# MODEL
+# Measure running time
+system.time({
+  
+  # Model name
+  semanticpriming_lmerTest =
+    
+    lmerTest::lmer( 
+      
+      # Dependent variable
+      z_target.RT ~
+        
+        # FIXED EFFECTS
+        
+        # Controlled lexical variables
+        z_target_word_frequency + z_target_number_syllables +
+        
+        # Controlled semantic variable
+        z_word_concreteness_diff +
+        
+        # Control interactions with word concreteness to allow a rigorous analysis of the
+        # interactions with visual-strength difference that are specified further below.
+        z_word_concreteness_diff : z_vocabulary_size +
+        z_word_concreteness_diff : z_recoded_interstimulus_interval +
+        z_word_concreteness_diff : z_recoded_participant_gender +
+        
+        # Important control due to the relationship between this variable and vocabulary size
+        # (Yap et al., 2017; https://www.montana.edu/khutchison/documents/YHT%20in%20press.pdf)
+        z_attentional_control +
+        
+        # Control interactions with attentional control to allow a rigorous analysis of
+        # the interactions with vocabulary size specified further below.
+        z_cosine_similarity : z_attentional_control +
+        z_visual_rating_diff : z_attentional_control +
+        
+        # Main effects of interest
+        z_vocabulary_size + z_recoded_participant_gender + z_cosine_similarity +
+        z_visual_rating_diff + z_recoded_interstimulus_interval +
+        
+        # Interactions of interest
+        z_cosine_similarity : z_vocabulary_size +
+        z_visual_rating_diff : z_vocabulary_size +
+        z_cosine_similarity : z_recoded_participant_gender +
+        z_visual_rating_diff : z_recoded_participant_gender +
+        z_cosine_similarity : z_recoded_interstimulus_interval +
[…]

### 2022-06-24 semanticpriming/frequentist_bayesian_plots/semanticpriming_frequentist_bayesian_plots.R

@@ -1,0 +1,175 @@
+
+
+# Part of Study 1: Semantic priming
+
+# Presenting the frequentist and the Bayesian estimates in the same plot. 
+# For this purpose, the frequentist results are merged into a plot from 
+# brms::mcmc_plot()
+
+
+library(tidyverse)
+library(ggtext)
+library(patchwork)
+library(Cairo)
+
+# Load custom function to present the frequentist and 
+# the Bayesian estimates in the same plot
+source('R_functions/frequentist_bayesian_plot.R')
+
+# Load frequentist coefficients (estimates and confidence intervals)
+
+KR_summary_semanticpriming_lmerTest = 
+  readRDS('semanticpriming/frequentist_analysis/results/KR_summary_semanticpriming_lmerTest.rds')
+
+confint_semanticpriming_lmerTest = 
+  readRDS('semanticpriming/frequentist_analysis/results/confint_semanticpriming_lmerTest.rds')
+
+# Below are the default names of the effects
+rownames(KR_summary_semanticpriming_lmerTest$coefficients)
+rownames(confint_semanticpriming_lmerTest)
+
+# Load Bayesian posterior distributions
+
+semanticpriming_posteriordistributions_informativepriors_exgaussian = 
+  readRDS('semanticpriming/bayesian_analysis/results/semanticpriming_posteriordistributions_informativepriors_exgaussian.rds')
+
+# semanticpriming_posteriordistributions_weaklyinformativepriors_exgaussian = 
+#   readRDS('semanticpriming/bayesian_analysis/results/semanticpriming_posteriordistributions_weaklyinformativepriors_exgaussian.rds')
+
+semanticpriming_posteriordistributions_diffusepriors_exgaussian = 
+  readRDS('semanticpriming/bayesian_analysis/results/semanticpriming_posteriordistributions_diffusepriors_exgaussian.rds')
+
+# Below are the default names of the effects
+levels(semanticpriming_posteriordistributions_diffusepriors_exgaussian$data$parameter)
+
+
+# Reorder the components of interactions in the frequentist results to match 
+# with the order present in the Bayesian results.
+
+rownames(KR_summary_semanticpriming_lmerTest$coefficients) =
+  rownames(KR_summary_semanticpriming_lmerTest$coefficients) %>%
+  str_replace(pattern = 'z_recoded_interstimulus_interval:z_cosine_similarity', 
+              replacement = 'z_cosine_similarity:z_recoded_interstimulus_interval') %>%
[…]

### 2022-06-24 semanticpriming/power_analysis/reduced_randomeffects_model/semanticpriming-interactions-with-gender.R

@@ -1,0 +1,85 @@
+
+
+# Part of Study 1: Semantic priming
+
+# Combination of plots:
+# 1. Interaction between gender and cosine similarity
+# 2. Interaction between gender and visual rating difference
+
+library(dplyr)
+library(patchwork)
+library(ggplot2)
+
+# Data set below created in the script 'semanticpriming_data_preparation.R',
+# which is stored in the folder 'semanticpriming/data'
+semanticpriming = 
+  read.csv('semanticpriming/data/final_dataset/semanticpriming.csv')
+
+# Consolidate gender labels
+semanticpriming$participant_gender = 
+  ifelse(semanticpriming$participant_gender == 'wf', 'Female',
+         ifelse(semanticpriming$participant_gender == 'F', 'Female',
+                ifelse(semanticpriming$participant_gender == 'f', 'Female',
+                       ifelse(semanticpriming$participant_gender == 'M', 'Male',
+                              ifelse(semanticpriming$participant_gender == 'm', 'Male',
+                                     semanticpriming$participant_gender)))))
+
+# Model below created in the script 'semanticpriming_lmerTest.R', which
+# is stored in the folder 'semanticpriming/power_analysis/model'
+semanticpriming_lmerTest = 
+  readRDS('semanticpriming/power_analysis/model/results/semanticpriming_lmerTest.rds')
+
+# Load custom function
+source('R_functions/alias_interaction_plot.R')
+
+plot1 =
+  alias_interaction_plot(
+    model = semanticpriming_lmerTest,
+    dataset = semanticpriming,
+    x = 'z_cosine_similarity',
+    fill = 'z_recoded_participant_gender',
+    fill_alias = 'participant_gender',
+    fill_nesting_factor = 'Participant',
+    x_title = 'Language-based similarity (*z*)',
+    y_title = 'Predicted RT (*z*)',
+    fill_title = 'Gender'
+  ) +
+  guides(color = 'none',
+         fill = guide_legend(title = 'Gender', 
+                             # In each key of the legend, replace the 
+                             # default line with a full square.
+                             override.aes = list(linetype = c(0, 0), 
+                                                 alpha = 1), 
+                             # In the legend, place labels in 
+                             # alphabetical order.
+                             reverse = TRUE)) +
+  labs(tag = '(a)')
+
+plot2 = 
+  alias_interaction_plot(
+    model = semanticpriming_lmerTest,
+    dataset = semanticpriming,
+    x = 'z_visual_rating_diff',
[…]

### 2022-06-24 semanticpriming/power_analysis/reduced_randomeffects_model/semanticpriming-interactions-with-interstimulus-interval.R

@@ -1,0 +1,56 @@
+
+
+# Part of Study 1: Semantic priming
+
+# Combination of plots:
+# 1. Interaction between cosine similarity and interstimulus interval
+# 2. Interaction between visual rating difference and interstimulus interval
+
+library(dplyr)
+library(ggplot2)
+library(patchwork)
+
+# Data set below created in the script 'semanticpriming_data_preparation.R',
+# which is stored in the folder 'semanticpriming/data'
+semanticpriming = 
+  read.csv('semanticpriming/data/final_dataset/semanticpriming.csv')
+
+# Model below created in the script 'semanticpriming_lmerTest.R', which
+# is stored in the folder 'semanticpriming/power_analysis/model'
+semanticpriming_lmerTest = 
+  readRDS('semanticpriming/power_analysis/model/results/semanticpriming_lmerTest.rds')
+
+# Load custom function
+source('R_functions/alias_interaction_plot.R')
+
+plot1 =
+  alias_interaction_plot(
+    model = semanticpriming_lmerTest,
+    dataset = semanticpriming,
+    x = 'z_cosine_similarity',
+    fill = 'z_recoded_interstimulus_interval',
+    fill_alias = 'interstimulus_interval',
+    x_title = 'Language-based similarity (*z*)',
+    y_title = 'Predicted RT (*z*)',
+    fill_title = 'Interstimulus<br>interval (ms)'
+  ) +
+  labs(tag = '(a)')
+
+plot2 = 
+  alias_interaction_plot(
+    model = semanticpriming_lmerTest,
+    dataset = semanticpriming,
+    x = 'z_visual_rating_diff',
+    fill = 'z_recoded_interstimulus_interval',
+    fill_alias = 'interstimulus_interval',
+    x_title = 'Visual-strength difference (*z*)',
+    y_title = 'Predicted RT (*z*)',
+    fill_title = 'Interstimulus<br>interval (ms)'
+  ) +
+  labs(tag = '(b)')
+
+# Combine plots using {patchwork}
+(plot1 + plot2 + plot_layout(ncol = 1, guides = 'collect')) %>%
+  ggsave(filename = 'semanticpriming/power_analysis/model/plots/semanticpriming-interactions-with-interstimulus-interval.pdf',
+         device = cairo_pdf, width = 6.5, height = 7, dpi = 900)
+

### 2022-06-24 semanticpriming/power_analysis/reduced_randomeffects_model/semanticpriming-interactions-with-vocabulary-size.R

@@ -1,0 +1,54 @@
+
+
+# Part of Study 1: Semantic priming
+
+# Combination of plots:
+# 1. Interaction between vocabulary size and language-based similarity
+# 2. Interaction between vocabulary size and visual-strength difference
+
+library(dplyr)
+library(ggplot2)
+library(patchwork)
+
+# Data set below created in the script 'semanticpriming_data_preparation.R',
+# which is stored in the folder 'semanticpriming/data'
+semanticpriming = 
+  read.csv('semanticpriming/data/final_dataset/semanticpriming.csv')
+
+# Model below created in the script 'semanticpriming_lmerTest.R', which
+# is stored in the folder 'semanticpriming/power_analysis/model'
+semanticpriming_lmerTest = 
+  readRDS('semanticpriming/power_analysis/model/results/semanticpriming_lmerTest.rds')
+
+# Load custom function
+source('R_functions/deciles_interaction_plot.R')
+
+plot1 =
+  deciles_interaction_plot(
+    model = semanticpriming_lmerTest,
+    x = 'z_cosine_similarity',
+    fill = 'z_vocabulary_size',
+    fill_nesting_factor = 'Participant',
+    x_title = 'Language-based similarity (*z*)',
+    y_title = 'Predicted RT (*z*)',
+    fill_title = 'Vocabulary size<br>(*z*, deciles)'
+  ) +
+  labs(tag = '(a)')
+
+plot2 =
+  deciles_interaction_plot(
+    model = semanticpriming_lmerTest,
+    x = 'z_visual_rating_diff',
+    fill = 'z_vocabulary_size',
+    fill_nesting_factor = 'Participant',
+    x_title = 'Visual-strength difference (*z*)',
+    y_title = 'Predicted RT (*z*)',
+    fill_title = 'Vocabulary size<br>(*z*, deciles)'
+  ) +
+  labs(tag = '(b)')
+
+# Combine plots using {patchwork}
+(plot1 + plot2 + plot_layout(ncol = 1, guides = 'collect')) %>%
+  ggsave(filename = 'semanticpriming/power_analysis/model/plots/semanticpriming-interactions-with-vocabulary-size.pdf',
+         device = cairo_pdf, width = 6.5, height = 7, dpi = 900)
+

### 2022-06-24 semanticpriming/power_analysis/reduced_randomeffects_model/semanticpriming_lmerTest.R

@@ -1,0 +1,128 @@
+
+
+# Part of Study 1: Semantic priming
+
+# This model was run 
+
+library(dplyr)  # data wrangling
+# The following lme4-relevant package was installed before lme4 to avoid a conflict 
+# noted at https://cran.r-project.org/web/packages/lme4/lme4.pdf
+library(RcppEigen)
+library(lme4)   # Mixed-effects models (package version 1.1-26)
+library(lmerTest)  # Compute p values (package version 3.1-3)
+library(MuMIn)   # R^2
+
+# Read in data
+semanticpriming = read.csv('semanticpriming/data/final_dataset/semanticpriming.csv')
+
+# MODEL
+# Measure running time
+system.time({
+  
+  # Model name
+  semanticpriming_lmerTest =
+    
+    lmerTest::lmer( 
+      
+      # Dependent variable
+      z_target.RT ~
+        
+        # FIXED EFFECTS
+        
+        # Controlled lexical variables
+        z_target_word_frequency + z_target_number_syllables +
+        
+        # Controlled semantic variable
+        z_word_concreteness_diff +
+        
+        # Control interactions with word concreteness to allow a rigorous analysis of the 
+        # interactions with visual-strength difference that are specified further below.
+        z_word_concreteness_diff : z_vocabulary_size + 
+        z_word_concreteness_diff : z_recoded_interstimulus_interval + 
+        z_word_concreteness_diff : z_recoded_participant_gender + 
+        
+        # Important control due to the relationship between this variable and vocabulary size 
+        # (Yap et al., 2017; https://www.montana.edu/khutchison/documents/YHT%20in%20press.pdf)
+        z_attentional_control +
+        
+        # Control interactions with attentional control to allow a rigorous analysis of
+        # the interactions with vocabulary size specified further below.
+        z_cosine_similarity : z_attentional_control +
+        z_visual_rating_diff : z_attentional_control +
+        
+        # Main effects of interest
+        z_vocabulary_size + z_recoded_participant_gender + z_cosine_similarity + 
+        z_visual_rating_diff + z_recoded_interstimulus_interval +
+        
+        # Interactions of interest
+        z_cosine_similarity : z_vocabulary_size +
+        z_visual_rating_diff : z_vocabulary_size +
+        z_cosine_similarity : z_recoded_participant_gender +
[…]

### 2022-06-29 manuscript/appendix-A-lexical-covariates.Rmd
29062022

@@
 
-# This appendix inherits the libraries, the working directory and the
-# data sets loaded in manuscript.Rmd, when the latter is knitted.
+# This appendix is rendered by the main manuscript. It inherits the 
+# working directory and all the objects loaded in the main manuscript.
 
@@
   footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
-           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on z-scored variables; \\\\textit{SE} = standard error;',
+           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored variables; \\\\textit{SE} = standard error;',
                            'CI = confidence interval. By-participant random slopes were included for',

### 2022-06-29 manuscript/appendix-B-frequentist-analysis-diagnostics.Rmd
29062022

@@
 
-## Lack of convergence
+## Convergence
 
 The challenge of convergence is well known in the area of mixed-effects models.
-The solutions proposed range from the removal of random slopes under certain conditions [@matuschekBalancingTypeError2017] to the maintenance of random slopes in spite of convergence warnings, which seeks to avoid an inflation of the Type I error caused by non-independence in the data [@brauer2018a; @singmann2019a].
+These models often struggle to reach reliable-enough estimates due to an insufficiency of data relative to the complexity of the model [@batesFittingLinearMixedeffects2015; @baayenMixedeffectsModelingCrossed2008; @brauer2018a].
+The solutions proposed range from the removal of random slopes under certain conditions [@matuschekBalancingTypeError2017] to the maintenance of random slopes in spite of convergence warnings, which seeks to avoid an inflation of the Type I error due to dependencies in the data [@brauer2018a; @singmann2019a].
 
@@
 
-### Lack of convergence
+### Convergence
 

### 2022-06-29 manuscript/appendix-D-interaction-plots.Rmd
29062022

@@
-# Appendix D: Further plots of interactions {#appendix-D-interaction-plots}
+# Appendix D: Further interaction plots {#appendix-D-interaction-plots}
 
@@
 
-This appendix presents plots of interactions that did not fit in the main text.
+This appendix presents plots of interactions that were not shown in the main text.
 
@@
 
-```{r semanticpriming-interactions-with-gender, fig.cap = 'Interactions with gender in the semantic priming study.', out.height = '70%'}
+(ref:semanticpriming-interactions-with-attentional-control) Interactions of attentional control with language-based similarity and visual-strength difference.
+Attentional control is constrained to deciles (ten sections) in this plot, whereas in the statistical analysis it contained more values within the current range.
+*n* = number of participants contained between decile values.
+
+```{r semanticpriming-interactions-with-attentional-control, fig.cap = '(ref:semanticpriming-interactions-with-attentional-control)', out.width = '85%'}
 
@@
 
-source('semanticpriming/frequentist_analysis/semanticpriming-interactions-with-gender.R', 
+source('semanticpriming/frequentist_analysis/semanticpriming-interactions-with-attentional-control.R', 
        local = TRUE)
@@
     getwd(),  # Circumvent illegal characters in file path
-    '/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-gender.pdf'
+    '/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-attentional-control.pdf'
   ))
@@
 
-... TBC
+```{r semanticpriming-interaction-word-concreteness-difference-SOA, fig.cap = 'Interaction of stimulus-onset asynchrony (SOA) with word-concreteness difference.
+SOA was analysed using $z$-scores, but for clarity, the variable is shown in its basic form here.', out.width = '65%'}
+
+# Run plot through source() rather than directly in this R Markdown document 
+# to preserve the italicised text.
+
+source('semanticpriming/frequentist_analysis/semanticpriming-interactions-with-word-concreteness-difference.R', 
+       local = TRUE)
+
+include_graphics(
+  paste0(
+    getwd(),  # Circumvent illegal characters in file path
+    '/semanticpriming/frequentist_analysis/plots/semanticpriming-interaction-word-concreteness-difference-SOA.pdf'
+  ))
+
+```
+
+(ref:semanticpriming-interaction-word-concreteness-difference-vocabulary-size) Interaction of word-concreteness difference with vocabulary size.
+Vocabulary size is constrained to deciles in this plot, whereas in the statistical analysis it contained more values within the current range.
+*n* = number of participants contained between decile values.
+
+```{r semanticpriming-interaction-word-concreteness-difference-vocabulary-size, fig.cap = '(ref:semanticpriming-interaction-word-concreteness-difference-vocabulary-size)', out.width = '85%'}
+
+include_graphics(
+  paste0(
+    getwd(),  # Circumvent illegal characters in file path
+    '/semanticpriming/frequentist_analysis/plots/semanticpriming-interaction-word-concreteness-difference-vocabulary-size.pdf'
+  ))
+
+```
+
+(ref:semanticpriming-interaction-word-concreteness-difference-gender) Interaction of word-concreteness difference with gender.
+Gender was analysed using $z$-scores, but for clarity, the variable is shown in its basic form here.
+*n* = number of participants contained between decile values.
+
+```{r semanticpriming-interaction-word-concreteness-difference-gender, fig.cap = '(ref:semanticpriming-interaction-word-concreteness-difference-gender)', out.width = '65%'}
+
+include_graphics(
+  paste0(
+    getwd(),  # Circumvent illegal characters in file path
+    '/semanticpriming/frequentist_analysis/plots/semanticpriming-interaction-word-concreteness-difference-gender.pdf'
+  ))
+
+```
+
+\clearpage
 
@@
 
-...
+(ref:semanticdecision-interactions-with-information-uptake) Interactions of information uptake with language-based similarity and visual-strength difference.
+Information uptake is constrained to deciles in this plot, whereas in the statistical analysis it contained more values within the current range.
+*n* = number of participants contained between decile values.
+
+```{r semanticdecision-interactions-with-information-uptake, fig.cap = '(ref:semanticdecision-interactions-with-information-uptake)', out.width = '90%'}
+
+# Run plot through source() rather than directly in this R Markdown document 
+# to preserve the italicised text.
+
+source('semanticdecision/frequentist_analysis/semanticdecision-interactions-with-information-uptake.R', 
+       local = TRUE)
+
+include_graphics(
+  paste0(
+    getwd(),  # Circumvent illegal characters in file path
+    '/semanticdecision/frequentist_analysis/plots/semanticdecision-interactions-with-information-uptake.pdf'
+  ))
+
+```
+
+\clearpage
 
@@
 
-...
+(ref:lexicaldecision-interaction-word-concreteness-vocabulary-age) Interaction of word concreteness with vocabulary age.
+Vocabulary age is constrained to sextiles (six sections) in this plot, whereas in the statistical analysis it contained more values within the current range.
+*n* = number of participants contained between sextile values.
+
+```{r lexicaldecision-interaction-word-concreteness-vocabulary-age, fig.cap = '(ref:lexicaldecision-interaction-word-concreteness-vocabulary-age)', out.width = '85%'}
+
+# Run plot through source() rather than directly in this R Markdown document 
+# to preserve the italicised text.
+
+source('lexicaldecision/frequentist_analysis/lexicaldecision-interactions-with-word-concreteness.R', 
+       local = TRUE)
+
+include_graphics(
+  paste0(
+    getwd(),  # Circumvent illegal characters in file path
+    '/lexicaldecision/frequentist_analysis/plots/lexicaldecision-interaction-word-concreteness-vocabulary-age.pdf'
+  ))
+
+```
+
+(ref:lexicaldecision-interaction-word-concreteness-gender) Interaction of word concreteness with gender.
+Gender was analysed using $z$-scores, but for clarity, the variable is shown in its basic form here.
+*n* = number of participants contained between sextile values.
+
+```{r lexicaldecision-interaction-word-concreteness-gender, fig.cap = '(ref:lexicaldecision-interaction-word-concreteness-gender)', out.width = '65%'}
+
+include_graphics(
+  paste0(
+    getwd(),  # Circumvent illegal characters in file path
+    '/lexicaldecision/frequentist_analysis/plots/lexicaldecision-interaction-word-concreteness-gender.pdf'
+  ))
+
+```

### 2022-06-29 manuscript/appendix-E-Bayesian-analysis-results.Rmd
29062022

@@
   footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
-           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on z-scored variables; \\\\textit{SE} = standard error;',
+           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored variables; \\\\textit{SE} = standard error;',
                            'CrI = credible interval. Shaded rows contain covariates. Some interactions',
@@
   rownames(semanticdecision_summary_informativepriors_exgaussian$fixed) == 
-    'z_word_cooccurrence'] = "Distance to word 'abstract' $^{\\text{b}}$"
+    'z_word_cooccurrence'] = "Word co-occurrence $^{\\text{b}}$"
 
@@
     'z_information_uptake:z_word_cooccurrence'] = 
-  "Information uptake :: Distance to word 'abstract'"
+  "Word co-occurrence : Information uptake"
 
@@
     'z_vocabulary_size:z_word_cooccurrence'] = 
-  "Distance to word 'abstract' :: Vocabulary size"
+  "Word co-occurrence : Vocabulary size"
 
@@
     'z_recoded_participant_gender:z_word_cooccurrence'] = 
-  "Distance to word 'abstract' : Gender"
+  "Word co-occurrence : Gender"
 
@@
                     'Word concreteness',
-                    "Distance to word 'abstract' $^{\\text{b}}$",
+                    "Word co-occurrence $^{\\text{b}}$",
                     'Visual strength $^{\\text{b}}$',
-                    'Vocabulary size : Word concreteness',
+                    'Word concreteness : Vocabulary size',
                     'Word concreteness : Gender',
-                    "Distance to word 'abstract' :: Information uptake",
+                    "Word co-occurrence : Information uptake",
                     'Visual strength : Information uptake',
-                    "Distance to word 'abstract' :: Vocabulary size",
+                    "Word co-occurrence : Vocabulary size",
                     'Visual strength : Vocabulary size',
-                    "Distance to word 'abstract' : Gender",
+                    "Word co-occurrence : Gender",
                     'Visual strength : Gender'),
@@
   kable_styling(latex_options = c('HOLD_position', 'striped'), 
-                stripe_index = c(2, 5:7, 10:11)) %>%
+                stripe_index = c(2, 5:7, 10:13)) %>%
 
@@
   rownames(semanticdecision_summary_weaklyinformativepriors_exgaussian$fixed) == 
-    'z_word_cooccurrence'] = "Distance to word 'abstract' $^{\\text{b}}$"
+    'z_word_cooccurrence'] = "Word co-occurrence $^{\\text{b}}$"
 
@@
   rownames(semanticdecision_summary_diffusepriors_exgaussian$fixed) == 
-    'z_word_cooccurrence'] = "Distance to word 'abstract' $^{\\text{b}}$"
+    'z_word_cooccurrence'] = "Word co-occurrence $^{\\text{b}}$"
 
@@
   footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
-           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on z-scored variables; \\\\textit{SE} = standard error;',
+           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored variables; \\\\textit{SE} = standard error;',
                            'CrI = credible interval. Shaded rows contain covariates. \\\\linebreak', 

### 2022-06-29 manuscript/manuscript.Rmd
29062022

@@
    Research over the past two decades has suggested that conceptual processing depends on both language-based and vision-based information.
-We tested this interplay at three levels of the data: individual differences, words and tasks.
+We tested this interplay at three levels of the data: individuals, words and tasks.
 To this aim, we drew on three existing data sets that were composed of large samples, and implemented the paradigms of semantic priming, semantic decision and lexical decision.
@@
 In addition, higher-vocabulary participants presented a greater effect of language-based similarity than lower-vocabulary participants.
-Conversely, lower-vocabulary participants presented a greater effect of vision-based information, which was less relevant to the task.
-This 'relevance advantage' for higher-vocabulary participants also appeared in the semantic decision study, whose task required distinguishing between concrete and abstract words.
-Specifically, higher-vocabulary participants were more strongly influenced by word concreteness than lower-vocabulary participants.
-Furthermore, we compared the effects of different measures of visual information.
+In contrast, this pattern did not hold for vision-based information, which was less relevant to the task.
+The 'relevance advantage' in higher-vocabulary participants also appeared in the semantic decision and the lexical decision studies.
+Furthermore, we compare the effects of two visual information measures, and discuss the role of measurement instruments in this research topic.
 Lastly, we estimated the sample size required to reliably examine each effect of interest.
-We found that 300 participants would suffice to examine language-based information contained in words, whereas more than 1,000 participants would be necessary to examine vision-based information as well as the interactions between both the former variables and vocabulary size, gender and presentation speed.
-
-keywords: semantic, conceptual processing, vocabulary size, statistical power
+We found that 300 participants suffice to examine language-based information contained in words, whereas more than 1,000 participants are necessary to examine vision-based information as well as the interactions between both the former variables and vocabulary size, gender and presentation speed.
+
+keywords: conceptual processing, semantic priming, semantic decision, lexical decision, language, vision, vocabulary size, statistical power
 
@@
   - \usepackage{xcolor}                     # Dependency for R package 'kableExtra' (table formatting)
-  - \renewcommand\appendix{}                # Remove redundant label
+  - \renewcommand\appendix{}                # Remove redundant 'Appendix' label
 ---
@@
 
-Research over the past two decades has suggested that conceptual processing involves both 'linguistic' and 'embodied' systems of the brain.
-The language system is characterised by associations across networks of words [@landauerIntroductionLatentSemantic1998; @pylyshynWhatMindEye1973], whereas the embodiment system is characterised by associations within perceptual, motor, affective and social domains [@barsalouPerceptualSymbolSystems1999; @diveicaQuantifyingSocialSemantics2022].
-Both systems have strengths and limitations [@connell2019a; @dove2020a; @kumar2021a; @louwerse2015a; @mahon2016a].
-As a result, conceptual processing flexibly draws on these systems following the demands of the context [@satoTaskRelatedModulation2008; @shebaniFlexibilityLanguageAction2018; @willemsFlexibilityEmbodiedLanguage2011].
-
-The language system is involved in the representation of both abstract and concrete concepts [@ponari2018a; @regginDevelopmentAbstractWord2021].
-For instance, measures of distributional semantic distance---solely based on texts---have been shown to capture aspects of the real world with considerable accuracy [@contreraskallensQuantifyingInterdisciplinarityCognitive2022; @dedeyneBetterExplanationsLexical2013; @kumarDistantConnectivityMultiplestep2020; @louwerseLanguageEncodesGeographical2009].
-Although the language system is likely more important for the processing of abstract---rather than concrete---concepts [@barca2020a; @dunabeitiaQualitativeDifferencesRepresentation2009; @hultenNeuralRepresentationAbstract2021], although the degree of this difference could be small [@dedeyneBetterExplanationsLexical2013].
-Language-based regularities may even allow distinguishing between concrete and abstract words, as word concreteness is consistently related to linguistic characteristics such as part of speech, morphological structure, countability and etymology [@lieversLinguisticDimensionsConcrete2021].
-
-Regarding the time course, the language system is activated more quickly in semantically-deep tasks [@connell2013a; @louwerseTasteWordsLinguistic2011], whereas both systems are similarly fast in semantically-shallow tasks [@petilli2021a].
-As a result of these characteristics, the language system is equipped to support a major part of conceptual processing [@connell2019a; @connellSeeHearWhat2014].
-However, the language system is hindered by the symbol grounding problem, which refers to the impossibility of obtaining meaning---or 'grounding' lexical content in reality---on the sole basis of word-to-word associations [@guntherLimitsAutomaticSensorimotor2021; @guntherSymbolGroundingDirect2018; @louwerseSymbolInterdependencySymbolic2011; @harnadSymbolGroundingProblem1990].
-Another limitation is caused by the finite vocabularies of languages, which sometimes fall short of the richness of sensorimotor experience [@guntherLimitsAutomaticSensorimotor2021; @dedeyneVisualAffectiveMultimodal2021; @majidOdorsAreExpressible2014; @majidSensesLanguageCulture2011; @majidCanNomenclatureBody2015].
-In conclusion, word-to-word associations appear to be necessary but not sufficient for conceptual processing.
-
-The embodiment system is best suited for the representation of concrete concepts, such as those involving perceptual features [@pecherDoesPizzaPrime1998; @yeeColorlessGreenIdeas2012; @ostarekTaskdependentCausalRole2017] and actions [@riccardiDissociatingActionAbstract2019].
-Some research has suggested that embodied simulation plays an integral role in conceptual processing [@pulvermullerHowNeuronsMake2013], at least in the context of relatively-semantic tasks and stimuli [@leboisAreAutomaticConceptual2015; @pecherDoesPizzaPrime1998; @yeeColorlessGreenIdeas2012; @ostarekTaskdependentCausalRole2017; @connellWeKnowWhat2016; @garciaTimeFaceLanguage2020; @shebaniWhatImpairedSpatial2021; @vitaleNeuralInhibitionNetwork2021; @vukovicPrimaryMotorCortex2017; @wangSocialEmotionDimensional2021].
-For instance, @riccardiDissociatingActionAbstract2019 investigated the comprehension of action verbs and abstract verbs in left-hemisphere stroke patients, and found that the processing of action concepts relied more heavily on sensory-motor areas.
-Furthermore, studies have suggested that even abstract concepts may be partially grounded in modality-specific domains such as emotion, sociality and interoception [@concaSearchDifferentCategories2021; @connellInteroceptionForgottenModality2018; @diveicaQuantifyingSocialSemantics2022; @kousta2011a; @vigliocco2014a; @wangSocialEmotionDimensional2021].
-
-However, other research has curtailed the importance of this system [@mahonCriticalLookEmbodied2008; @bottiniConcretenessAdvantageLexical2021; @garceaPreservedToolKnowledge2013; @guntherSymbolGroundingDirect2018; @guntherLimitsAutomaticSensorimotor2021; @montero-melisNoEvidenceEmbodiment2022; @vannuscorpsPersistentSparingAction2016].
-For instance, studies have found that lesions to motor brain areas did not systematically impair the processing of action concepts in language [@papeoActionPerformanceActionword2010; @negriWhatRoleMotor2007].
-
-## Interplay between language and embodiment systems
-
-The above characteristics make the language and the embodiment systems complementary to each other [@andrewsIntegratingExperientialDistributional2009; @dedeyneVisualAffectiveMultimodal2021; @wangNeuralRepresentationAbstract2010].
+Over the past decades, research in psycholinguistics has suggested that conceptual processing depends on both language and embodiment systems [@barsalouLanguageSimulationConceptual2008; @louwerseSymbolInterdependencySymbolic2011; @connell2013a].
 A comprehensive approach to both these systems requires a direct comparison of them.
@@
 
-# The present study
-
-There is considerable evidence supporting the 'hybrid' theory positing that conceptual processing depends on both language and embodiment systems [@barsalouLanguageSimulationConceptual2008; @louwerseSymbolInterdependencySymbolic2011; @connell2013a].
-Nonetheless, there are also reasons to continue testing this theory.
+In spite of the amount of evidence favouring the interplay between language and embodiment, there are at least 2 reasons to continue testing the interplay theory.
 Firstly, the coexistence of several systems in a scientific theory must be thoroughly justified, due to the value of simplicity, as epitomised by Occam's razor [@galleseBrainConceptsRole2005; @tillmanHowSharpOccam2015].
 This point is particularly pressing because the language system has consistently produced larger effect sizes than the embodiment system [@lam2015a; @pecherDoesPizzaPrime1998; @petilli2021a; @banksLinguisticDistributionalKnowledge2021; @kiela2014a; @louwerse2015a].
+Consequently, in this research question, we examine whether the interplay between linguistic and visual processing holds in the expected directions and at multiple levels of the experimental structure.
+
 Secondly, mixed evidence has appeared regarding some aspects of the interplay.
-For instance, whereas some studies have suggested that the language system becomes relevant before the embodiment system [@lam2015a; @louwerseTasteWordsLinguistic2011], a recent study found the opposite pattern [@petilli2021a].
-Similarly, whereas some evidence has suggested that female participants might draw on the language system more prominently than males [@hutchinson2013a], other research has suggested that this difference could be negligible [@wallentinChapterGenderDifferences2020].
-Thirdly, the role of individual differences has not been examined in most of the studies addressing the language--embodiment interplay.
-Fourthly and last, the scarcity of statistical power that has ailed some studies in cognitive psychology and neuroscience [@vasishthHowEmbraceVariation2021; @marekReproducibleBrainwideAssociation2022] is likely to have affected some studies in the present topic area, too [see @lynottReplicationExperiencingPhysical2014; @montero-melisNoEvidenceEmbodiment2022].
-
-The above open questions were addressed in the present study.
-These questions were overarched by the main research question, which examined whether the interplay between linguistic and visual processing held in the expected direction and at multiple levels of the experimental structure.
-To study this question, we drew on the data sets from three previous studies whose samples of participants were larger than average.
-These studies implemented the paradigms of semantic priming [@hutchison2013a], semantic decision [@pexman2017a] and lexical decision [@balota2007a].
-Importantly, we extended these data sets with
+For instance, whereas some studies have suggested that the language system is activated before the embodiment system [@lam2015a; @louwerseTasteWordsLinguistic2011], a recent study found the opposite pattern in a lexical decision task [@petilli2021a].
+Similarly, some evidence has suggested that high-vocabulary participants are more sensitive to linguistic features [@yap2017a], whereas other evidence has suggested the opposite [@yapIndividualDifferencesJoint2009; @yap2012a].
+Another case of mixed evidence regards gender: whereas some evidence has suggested that female participants draw on the language system more prominently than males [@hutchinson2013a], other research has suggested that this difference is negligible in the general population [@wallentinChapterGenderDifferences2020].
+Presumably, the scarcity of statistical power that has ailed some studies in cognitive psychology and neuroscience [@vasishthHowEmbraceVariation2021; @marekReproducibleBrainwideAssociation2022] may have affected some studies in the present topic area as well [see @lynottReplicationExperiencingPhysical2014; @montero-melisNoEvidenceEmbodiment2022].
+Therefore, in this study, we re-examine longstanding questions using larger-than-average data sets, and calculate the sample size required to reliably detect a range of effects.
+
+## Language and vision
+
+To retest the interplay theory, we revisit previous studies that contained larger-than-average samples of participants.
+Each of our three studies is organised around one *hub* study.
+In Study 1, the hub is @hutchison2013a, which implements a semantic priming paradigm.
+In Study 2, the hub is @pexman2017a, which implements a lexical decision paradigm.
+In Study 3, the hub is @balota2007a, which implements a lexical decision paradigm.
+Upon this basis, we added word-level variables from other studies to tap into language [@mandera2017a; @wingfieldUnderstandingRoleLinguistic2022] and vision [@lynott2020a; @petilli2021a].
+Additionally, we included several covariates---or nuisance variables---to allow a rigorous analysis of the effects of interest [@sassenhagenCommonMisapplicationStatistical2016].
+These covariates comprised participant-specific variables (e.g., attentional control), lexical variables (e.g., word frequency) and word concreteness.
 
@@
 Experimental data in psycholinguistics often consists of various levels, such as participants, words and tasks.
-A simultaneous examination of these levels should improve our understanding of the evidence collected [@ostarekStrongInferenceResearch2021].
-For instance, this cross-examination can help increase our certainty on the attribution of explanatory power to each level, as well as allowing a comparison of the explanatory power across levels.
-This multilevel approach is complementary to another approach in the field which seeks to test the causal contribution of different sources of information to conceptual processing---e.g., language [@ponari2018a], perception [@stasenkoWhenConceptsLose2014] and action [@speedImpairedComprehensionSpeed2017].
+A simultaneous examination of these levels should enhance our understanding of the evidence collected [@ostarekStrongInferenceResearch2021]---for instance, by shedding light on the distribution of explanatory power within and across levels.
+This multilevel approach is complementary to another approach in the field that seeks to test the causal contribution of different sources of information to conceptual processing---e.g., language [@ponari2018a], perception [@stasenkoWhenConceptsLose2014] and action [@speedImpairedComprehensionSpeed2017].
 
@@
 
-## Participant level
-
-*** to be edited *** Individual differences in domains such as language, perception, mental imagery and physical experience [e.g., @davies2017a; @dils2010a; @fettermanFeelingWarmBeing2018; @holt2006a; @mak2019a; @miceliDifferencesRelatedAging2022; @pexman2018a; @vukovic2015a; @yap2012a; @yap2017a].^[According to @lamiellStatisticalThinkingPsychology2019, 'individual differences' is a misnomer in that the methods used to analyse individual differences (e.g, regression) are not participant-specific.
+## Individual level
+
+Variation  The role of individual differences in domains such as language, perception, mental imagery and physical experience [e.g., @davies2017a; @dils2010a; @fettermanFeelingWarmBeing2018; @holt2006a; @mak2019a; @miceliDifferencesRelatedAging2022; @pexman2018a; @vukovic2015a; @yap2012a; @yap2017a].^[According to @lamiellStatisticalThinkingPsychology2019, 'individual differences' is a misnomer in that the methods used to analyse individual differences (e.g, regression) are not participant-specific.
 We think that this observation is mitigated in the context of mixed-effects models (as used in our current study), which incorporate by-participant random intercepts and random slopes.] Furthermore, in some topic areas in which individual differences have not featured as prominently, the data have revealed a non-trivial role of individual differences [@montero-melisConsistencyMotionEvent2021; @kosIndividualVariationLate2012].
@@
 Some previous studies have found that the effect of vocabulary size was moderated by variables related to general intelligence, such as processing speed [@ratcliff2010a; @yap2012a].
-Owing to those findings, and the recommendations from other studies [@james2018a; @pexman2018a; @sassenhagenCommonMisapplicationStatistical2016], the present studies included covariates of vocabulary size, where available.These covariates were measures of intelligence that were not vocabulary-based, namely, attentional control in Study 1 and information uptake in Study 2 (such a variable was not available for Study 3).
+Owing to those findings, and the recommendations from other studies [@james2018a; @pexman2018a; @sassenhagenCommonMisapplicationStatistical2016], the present studies included covariates of vocabulary size, where available.
+These covariates were measures of intelligence that were not vocabulary-based, namely, attentional control in Study 1 and information uptake in Study 2 (such a variable was not available for Study 3).
 
@@
 
-*** to be edited *** Semantic or lexical information in words [e.g., @dedeyneVisualAffectiveMultimodal2021; @lam2015a; @lund1995a; @lund1996a; @lynott2020a; @mandera2017a; @pexman2017a; @santosPropertyGenerationReflects2011; @wingfieldUnderstandingRoleLinguistic2022]
-
-- *Variables in this study:* degree of association between words, degree of vision-based information in single words
-
-- Covariates: lexical variables and word concreteness.
+*** to be edited *** Semantic or lexical information in words [e.g., @dedeyneVisualAffectiveMultimodal2021; @lam2015a; @lund1995a; @lund1996a; @lynott2020a; @mandera2017a; @petilli2021a; @pexman2017a; @santosPropertyGenerationReflects2011; @wingfieldUnderstandingRoleLinguistic2022]
+
+- Variables in this study: language-based and vision-based information;
+
+- Covariates: lexical variables and word concreteness;
 
@@
 For instance, @yap2017a observed a larger semantic priming effect in higher-vocabulary participants from [@hutchinson2013a].
-The second hypothesis, in contrast, states that higher-vocabulary participants would be *less* sensitive to linguistic features, thanks to a more automatic process.
+The second hypothesis, in contrast, states that higher-vocabulary participants would be *less* sensitive to linguistic features, thanks to a more automatic process [@perfettiLexicalQualityHypothesis2002].
 For instance, @yapIndividualDifferencesJoint2009 observed a smaller semantic priming effect in higher-vocabulary participants.
@@
 
-Statistical power depends on the following factors: (1) sample size---comprising the number of participants, items, trials, etc.---, (2) effect size, (3) measurement variability and (4) number of comparisons being performed [@kumleEstimatingPowerGeneralized2021].
+Statistical power depends on the following factors: (1) sample size---comprising the number of participants, items, trials, etc.---, (2) effect size, (3) measurement variability and (4) number of comparisons being performed.
 Out of these, sample size is the factor that can best be controlled by researchers [@kumleEstimatingPowerGeneralized2021].
@@
 
-## General method for statistical analyses {#general-statistical-analyses}
+## General method for statistical analysis {#general-statistical-analyses}
 
@@
 
-Several covariates---or nuisance variables---were included, as detailed in each study, to allow a rigorous analysis of the effects of interest [@sassenhagenCommonMisapplicationStatistical2016].
+Several covariates---or nuisance variables---were included in each study, to allow a rigorous analysis of the effects of interest [@sassenhagenCommonMisapplicationStatistical2016].
 Unlike the effects of interest, these covariates were not critical to the research question.
-They comprised lexical variables (e.g., word frequency) and participant-specific variables (e.g., attentional control).
-The lexical covariates were selected in every study out of the same 5 variables, which had been used as covariates in @wingfieldUnderstandingRoleLinguistic2022, and are widely used [e.g., @petilli2021a].
+They comprised participant-specific variables (e.g., attentional control), lexical variables (e.g., word frequency) and word concreteness.
+
+The lexical covariates were selected in every study out of the same 5 variables, which had been used as covariates in @wingfieldUnderstandingRoleLinguistic2022 [also see @petilli2021a].
 They comprised: number of letters (i.e., orthographic length), word frequency, number of syllables [both the latter from @balota2007a], orthographic Levenshtein distance [@yarkoniMovingColtheartNew2008] and phonological Levenshtein distance [@suarezObservingNeighborhoodEffects2011].
@@
 The correlations and the selection models are available in [\underline{Appendix A}](#appendix-A-lexical-covariates).
+
+Word concreteness was included due to its correlation with visual strength, as shown in each study below.
+A recent study suggested that the psycholinguistic import of concreteness is fundamentally lexical, and does not involve perceptual simulation [@bottiniConcretenessAdvantageLexical2021].
+
+The participant-specific covariates were measures akin to fluid intelligence, and were included due to their relationship with vocabulary size, as previous studies have expressed the desirability of including such covariates [@james2018a; @pexman2018a].
+As described in each study, these covariates were used in Studies 1 and 2, but not in Study 3, as such a variable was not available.
 
@@
 Therefore, linear mixed-effects models were implemented.
-These models included a maximal random-effects structure, with by-participant and by-word random intercepts, and the appropriate random slopes for all effects of interest [@barrRandomEffectsStructure2013].
-In the case of interactions, random slopes were included only when the variables interacting varied within the same unit [@brauer2018a]---e.g., an interaction of two variables varying within participants (only present in Study 1).
-Owing to convergence warnings, random slopes for controlled covariates were removed, inspired by Remedy 11 from @brauer2018a.
-Exceptionally, in the Bayesian models for the lexical decision study, the random slopes for the covariates did not have to be removed.
-
-To avoid inflating the Type I error rate (false positives), the random slopes for the effects of interest were never removed [see Table 17 in @brauer2018a; for an example of this approach, see @diazNeuralSensitivityPhonological2021].
-This approach provides a better protection against false positives [@barrRandomEffectsStructure2013; @brauer2018a; @singmann2019a] than the practice of removing random slopes when they do not significantly improve the fit [e.g., @bernabeu2017a; @pexman2018a; see @batesFittingLinearMixedeffects2015].
+These models included a maximal random-effects structure, with by-participant and by-item random intercepts, and the appropriate random slopes for all effects of interest [@barrRandomEffectsStructure2013].
+In the semantic priming study, the items were prime-target pairs, whereas in the semantic decision and lexical decision studies, the items were individual words.
+In the case of interactions, random slopes were included only when the interacting variables varied within the same unit [@brauer2018a]---e.g., an interaction of two variables varying within participants (only present in Study 1).
+Where required due to convergence warnings, random slopes for covariates were removed, as inspired by Remedy 11 from @brauer2018a.
+In this regard, whereas @brauer2018a contemplate the removal of random slopes for covariates only when the covariates are not interacting with any effects of interest, we removed random slopes for covariates even if they interacted with effects of interest because these interactions were covariates themselves (covariates are indicated in the results tables).
+
+To avoid inflating the Type I error rate (false positives), the random slopes for the effects of interest (indicated by non-shaded rows in the results tables below) were never removed [see Table 17 in @brauer2018a; for an example of this approach, see @diazNeuralSensitivityPhonological2021].
+This approach arguably provides a better protection against false positives [@barrRandomEffectsStructure2013; @brauer2018a; @singmann2019a] than the practice of removing random slopes when they do not significantly improve the fit [e.g., @bernabeu2017a; @pexman2018a; @batesFittingLinearMixedeffects2015; @baayenMixedeffectsModelingCrossed2008; but also see @matuschekBalancingTypeError2017].
 
@@
 
-*P* values were calculated with the Kenward-Roger approximation for degrees of freedom [@luke2017a], using the 'lmerTest' package, Version 3.1-3 [@R-lmerTest].
+$P$ values were calculated using the Kenward-Roger approximation for degrees of freedom [@luke2017a], in the R package 'lmerTest', Version 3.1-3 [@R-lmerTest].
 The latter package in turn used 'lme4', Version 1.1-26 [@batesPackageLme42021; @batesFittingLinearMixedeffects2015].
+To facilitate the convergence of the models, the maximum number of iterations was set to 1 million.
 Diagnostics regarding convergence and normality are provided in [\underline{Appendix B}](#appendix-B-frequentist-analysis-diagnostics).
+Effects that were non-significant or very small are best interpreted by considering their 95% confidence intervals [@cummingNewStatisticsWhy2014], which are shown in the results tables as well as in plots.
 
@@
 
-In addition to the frequentist analysis, a Bayesian analysis was performed for two purposes: firstly, to enhance the interpretation of the smaller effects (which were identified as low-powered), and secondly, to complement the estimates obtained in the frequentist analysis.
+A Bayesian analysis was performed to complement the estimates that had been obtained in the frequentist analysis.
+Whereas the focus of the frequentist analysis had been hypothesis testing, using $p$ values, the purpose of the Bayesian analysis was parameter estimation.
+Accordingly, we estimated the posterior distribution of every effect, without calculating Bayes factors [for other examples of this approach, see @milekEavesdroppingHappinessRevisited2018; @preglaVariabilitySentenceComprehension2021; @rodriguez-ferreiroSemanticPrimingSchizotypal2020; for comparisons between estimation and hypothesis testing, see @cummingNewStatisticsWhy2014; @kruschkeBayesianNewStatistics2018; @schmalzWhatBayesFactor2021; @tendeiroReviewIssuesNull2019; @tendeiroOnTheWhite2022; @rouderBayesianInferencePsychology2018; @vanravenzwaaijAdvantagesMasqueradingIssues2021].
+In the estimation approach, the estimates are interpreted by considering the position of their credible intervals in relation to the expected effect size.
+That is, the closer an interval is to an effect size of 0, the smaller the effect of that predictor.
+For instance, an interval that is symmetrically centred on 0 indicates a very small effect, whereas---in comparison---an interval that does not include 0 at all indicates a far larger effect.
+
+This analysis served two purposes: firstly, to ascertain the interpretation of the smaller effects---which were identified as unreliable in the power analyses---, and secondly, to complement the estimates obtained in the frequentist analysis.
 The latter purpose was pertinent because the frequentist models presented convergence warnings---even though it must be noted that a previous study found that frequentist and Bayesian estimates were similar despite convergence warnings appearing in the frequentist analysis [@rodriguez-ferreiroSemanticPrimingSchizotypal2020].
 Furthermore, the complementary analysis was pertinent because the frequentist models presented residual errors that deviated from normality---even though mixed-effects models are fairly robust to such a deviation [@kniefViolatingNormalityAssumption2021; @schielzethRobustnessLinearMixed2020].
-Owing to these precedents, we expected to find broadly similar estimates in the two approaches.
-
-Each frequentist model in the three studies has a Bayesian counterpart, with the exception of a sub-analysis performed in the first study (semantic priming), which included 'visual similarity' as a predictor.
-Due to time constraints, this analysis did not include a Bayesian model.
-Furthermore, it must be noted that the Bayesian models in the semantic decision study did not produce valid results.
-Therefore, the estimates produced by these models are not shown in the main text, but they are instead in [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results).
-
-Just as the frequentist estimates include 95% confidence intervals (CI), the Bayesian estimates include 95% credible intervals (CrI).
-These two types differ at a theoretical level, in that frequentist statistics are designed for the long run of testing, whereas Bayesian statistics are specific to each study [@schootBayesianStatisticsModelling2021; @vasishthStatisticalSignificanceFilter2018].
-
-The random effects included in these models were largely the same as those included in the frequentist models.
-The only exception regarded the lexical decision models.
-In the frequentist models for lexical decision, the covariates did not carry random slopes due to the presence of convergence warnings [see Remedy 11 in @brauer2018a], whereas in the Bayesian analysis, covariates did carry random slopes because the models converged.
-
-This Bayesian analysis was not aimed at hypothesis testing.
-Instead, it was designed to complement and verify the estimates that had been obtained in the frequentist analysis.
-Accordingly, we estimated the posterior distribution of every effect, without calculating Bayes factors [for other examples of this approach, see @milekEavesdroppingHappinessRevisited2018; @preglaVariabilitySentenceComprehension2021; @rodriguez-ferreiroSemanticPrimingSchizotypal2020; for comparisons between estimation and hypothesis testing, see @cummingNewStatisticsWhy2014; @kruschkeBayesianNewStatistics2018; @schmalzWhatBayesFactor2021; @tendeiroReviewIssuesNull2019; @tendeiroOnTheWhite2022; @rouderBayesianInferencePsychology2018; @vanravenzwaaijAdvantagesMasqueradingIssues2021].
-In the estimation approach, the estimates are interpreted by considering the position of their credible intervals in relation to the predicted value of RT ($z$).
-That is, the closer an interval is to a value of 0 on the predicted RT ($z$), the smaller the effect of that predictor.
-For instance, an interval that is symmetrically centred on 0 indicates a very small effect, whereas---in comparison---an interval that does not include 0 at all indicates a far larger effect.
+Owing to these precedents, we expected to find broadly similar estimates in the frequentist and the Bayesian analyses.
+Each frequentist model in the three studies has a Bayesian counterpart, with the exception of a sub-analysis performed in the first study (semantic priming), which included 'vision-based similarity' as a predictor.
 
@@
 These studies and the frequentist analyses reported below yielded effect sizes smaller than ±0.30.
-The bounds of this range were determined by the results from @pexman2018a, who found a word-concreteness effect of $\upbeta$ = 0.41 in the concrete-words analysis, and an effect of $\upbeta$ = 0.20 in the abstract-words analysis.
+The bounds of this range were determined by the results from @pexman2018a, who found a word concreteness effect of $\upbeta$ = 0.41 in the concrete-words analysis, and an effect of $\upbeta$ = 0.20 in the abstract-words analysis.
 Since we did not separate abstract from concrete words, we averaged the former values, and set -0.30 as the lower bound, and 0.30 as the upper bound.
@@
 
-Prior predictive checks revealed that the priors were adequate, and that the ex-Gaussian distribution was more appropriate than the Gaussian one, converging with @rodriguez-ferreiroSemanticPrimingSchizotypal2020 (see the corresponding plots in [\underline{Appendix D}](#appendix-D-interaction-plots)).
+Prior predictive checks revealed that the priors were adequate, and that the ex-Gaussian distribution was more appropriate than the Gaussian one, converging with @rodriguez-ferreiroSemanticPrimingSchizotypal2020 (see the corresponding plots in [\underline{Appendix C}](#appendix-C-Bayesian-analysis-diagnostics)).
 Therefore, the ex-Gaussian distribution was used in the final models.
@@
 
-As a last diagnostic, posterior predictive checks were performed to assess the fit between the observed data and new data predicted by the posterior [@schootBayesianStatisticsModelling2021].
+Posterior predictive checks were performed to assess the fit between the observed data and new data predicted by the posterior [@schootBayesianStatisticsModelling2021].
 These checks are available in [\underline{Appendix C}](#appendix-C-Bayesian-analysis-diagnostics).
 
-## General method for statistical power analyses
+#### Convergence
+
+Where convergence was not reached in a model, as indicated by $\widehat R$ > 1.01 [@schootBayesianStatisticsModelling2021; @vehtariRanknormalizationFoldingLocalization2021], the number of iterations was increased.
+Furthermore, where necessary, the random slopes for covariates were removed [@brauer2018a].
+The resulting random effects in these models were largely the same as those present in the frequentist models.
+The only exception regarded the lexical decision models.
+In the frequentist model for lexical decision, the random slopes for covariates were removed due to convergence warnings, whereas in the Bayesian analysis, these random slopes did not have to be removed as the models converged.
+
+The Bayesian models in the semantic decision study could not be made to converge, and the results were not valid.
+Therefore, those estimates are not shown in the main text but in [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results).
+
+## General method for statistical power analysis
 
@@
 Thus, each of the power curves we present assume the same number of words that existed in each of our studies (these numbers are detailed in each study below).
-*P* values were calculated using the Satterthwaite approximation for degrees of freedom, which is faster than Kenward-Roger but similarly accurate [@luke2017a].
+$P$ values were calculated using the Satterthwaite approximation for degrees of freedom [@luke2017a].
 
@@
 Specifically, we used the same primary data set [@hutchison2013a], and a language-based similarity measure that was very similar to that used by @petilli2021a [both our measure and theirs originated from @mandera2017a].
-In contrast, in the domain of vision, the operationalisation of visual-strength difference in our study---based one variable from [@lynott2020a]---was simpler than that of Petilli et al.'s visual similarity---which involved convolutional neural networks.
-As a counterpoint, Petilli et al.'s measure was superior in that it was independent from human ratings, thus precluding the problem of circularity between the independent and the dependent variables.
-At [\underline{the end of the Results section}](#comparing-two-measures-of-vision-based-information), we compare the performance of these two measures.
+In contrast, our predictors in the domain of vision differed.
+Whereas Petilli et al.
+used a human-independent measure based on images from the Internet (see description above), we drew on visual strength---from the modality ratings of @lynott2020a---and calculated the difference in visual strength between the prime and the target word in each trial.^[These measures are compared at [\underline{the end of the Results section}](#comparing-two-measures-of-vision-based-information).]
 
@@
 
-- $Z$-scored, recoded participant's gender [`z_recoded_participant_gender`; calculated from `gender` in @hutchison2013a]
+- $Z$-scored, recoded participants' gender [`z_recoded_participant_gender`; calculated from `gender` in @hutchison2013a]
 
@@
 
-- $Z$-scored vision-based information in words [`z_visual_rating`; calculated from `Visual.mean` in @lynott2020a]
+- $Z$-scored vision-based information in words [`z_visual_rating_diff`; calculated from `Visual.mean` in @lynott2020a]
 
@@
 
-The final data set contained `r semanticpriming_number_participants` participants, `r semanticpriming_number_primetarget_pairs %>% formattable::comma(digits = 0)` prime-target pairs, and a total of `r length(semanticpriming$z_target.RT) %>% formattable::comma(digits = 0)` RTs.
+The final data set contained `r semanticpriming_number_participants` participants, `r semanticpriming_number_primetarget_pairs %>% formattable::comma(digits = 0)` prime-target pairs, and `r length(semanticpriming$z_target.RT) %>% formattable::comma(digits = 0)` RTs.
 On average, there were `r semanticpriming_mean_primetarget_pairs_per_participant` prime-target pairs per participant ($SD$ = `r semanticpriming_SD_primetarget_pairs_per_participant`), and conversely, `r semanticpriming_mean_participants_per_primetarget_pair` participants per prime-target pair ($SD$ = `r semanticpriming_SD_participants_per_primetarget_pair`).
@@
 - Individual differences: $z$-scored attentional control [@hutchison2013a].
-This covariate is related to vocabulary size [@ratcliff2010a], and previous studies have pointed out the desirability of including these kinds of covariates in analyses [@james2018a; @pexman2018a].
-Attentional control was operationalised as the average score across three attention-demanding tasks: namely, operation span, Stroop, antisaccade.
+This covariate is related to vocabulary size [@ratcliff2010a], and previous studies have expressed the desirability of including such covariates [@james2018a; @pexman2018a].
+Attentional control was operationalised as the average score across three tasks of @hutchison2013a---namely, operation span, Stroop and antisaccade.
 
@@
 The model presented convergence warnings.
-To avoid removing important random slopes, which could increase the Type I error [@brauer2018a; @singmann2019a], we examined the model after refitting it using seven optimization algorithms through the 'allFit' function of the 'lme4' package [@batesPackageLme42021].
+To avoid removing important random slopes, which could increase the Type I error [@brauer2018a; @singmann2019a], we examined the model after refitting it using seven optimization algorithms through the 'allFit' function of the R package 'lme4' [@batesPackageLme42021].
 The results showed that all optimizers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential (Bates et al., 2021; see [\underline{Appendix B}](#appendix-B-frequentist-analysis-diagnostics)).
@@
 
-Three Bayesian models were run that were respectively characterised by informative, weakly-informative and diffuse priors.
+Three Bayesian models were run that were respectively characterised by informative, weakly-informative and diffuse priors (note that the weakly-informative prior model has not yet finished running).
 In each model, `r semanticpriming_summary_informativepriors_exgaussian$chains` chains were used.
@@
 
-The maximum $\widehat R$ value for the fixed effects across the three models was `r semanticpriming_fixedeffects_max_Rhat`, suggesting that these parameters had converged [@schootBayesianStatisticsModelling2021; @vehtariRanknormalizationFoldingLocalization2021].
+The maximum $\widehat R$ value for the fixed effects in both models was `r semanticpriming_fixedeffects_max_Rhat`, suggesting that these parameters had converged [@schootBayesianStatisticsModelling2021; @vehtariRanknormalizationFoldingLocalization2021].
 In contrast, the maximum $\widehat R$ value for the random effects was `r semanticpriming_randomeffects_max_Rhat`, exceeding the 1.01 threshold [@vehtariRanknormalizationFoldingLocalization2021].
@@
 
-Table \@ref(tab:semanticpriming-frequentist-model) presents the results of the mixed-effects model.
+```{r}
+
+# Calculate R^2. This coefficient must be interpreted with caution 
+# (Nakagawa et al., 2017; https://doi.org/10.1098/rsif.2017.0213). 
+# Also, transform coefficient to rounded percentage.
+
+Nakagawa2017_fixedeffects_R2_semanticpriming_lmerTest = 
+  paste0(
+    (MuMIn::r.squaredGLMM(semanticpriming_lmerTest)[1, 'R2m'][[1]] * 100) %>% 
+      sprintf('%.2f', .), '%'
+  )
+
+Nakagawa2017_randomeffects_R2_semanticpriming_lmerTest = 
+  paste0(
+    (MuMIn::r.squaredGLMM(semanticpriming_lmerTest)[1, 'R2c'][[1]] * 100) %>% 
+      sprintf('%.2f', .), '%'
+  )
+
+```
+
+Table \@ref(tab:semanticpriming-frequentist-model) presents the results of the frequentist model.
+The fixed effects explained `r Nakagawa2017_fixedeffects_R2_semanticpriming_lmerTest` of the variance, and the random effects `r Nakagawa2017_randomeffects_R2_semanticpriming_lmerTest` [@nakagawaCoefficientDeterminationR22017].
+It is to be expected that random effects explain more variance, as they involve a far larger number of coefficients for each effect.
+For instance, the by-item random slopes (specifically, by prime-target pair) for a single individual-level variable (e.g., vocabulary size) involve as many coefficients as the number of items.
+Conversely, the by-participant random slopes for a single item-level variable (e.g., language-based similarity) involve as many coefficients as the number of participants.
+In contrast, each fixed effect involves 1 coefficient only.
 
@@
   # Place table close to designated position and highlight covariates
-  kable_styling(latex_options = c('hold_position', 'striped'), 
+  kable_styling(latex_options = c('HOLD_position', 'striped'), 
                 stripe_index = c(2, 5:7, 11:15)) %>%
@@
 
-# Calculate R^2. This coefficient must be interpreted with caution 
-# (Nakagawa et al., 2017; https://doi.org/10.1098/rsif.2017.0213). 
-# Also, transform coefficient to rounded percentage.
-
-Nakagawa2017_fixedeffects_R2_semanticpriming_lmerTest = 
+```
+
+Figure \@ref(fig:semanticpriming-frequentist-bayesian-plot-informativepriors-exgaussian) displays the frequentist estimates alongside the Bayesian estimates.
+The latter are from the informative prior model.
+The estimates of the diffuse prior model were virtually identical to these (see [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results)).
+
+```{r semanticpriming-frequentist-bayesian-plot-informativepriors-exgaussian, fig.cap = 'Estimates from the frequentist analysis (in red) and from the Bayesian analysis (in blue) for the semantic priming study.
+The frequentist means (represented by points) are flanked by 95\\% confidence intervals.
+The Bayesian means (represented by vertical lines) are flanked by 95\\% credible intervals, in light blue (in some cases, the interval is covered up by the bar of the mean).'}
+
+# Run plot through source() rather than directly in this R Markdown document
+# to preserve the format.
+
+source('semanticpriming/frequentist_bayesian_plots/semanticpriming_frequentist_bayesian_plots.R', 
+       local = TRUE)
+
+include_graphics(
   paste0(
-    (MuMIn::r.squaredGLMM(semanticpriming_lmerTest)[1, 'R2m'][[1]] * 100) %>% 
-      sprintf('%.2f', .), '%'
-  )
-
-Nakagawa2017_randomeffects_R2_semanticpriming_lmerTest = 
-  paste0(
-    (MuMIn::r.squaredGLMM(semanticpriming_lmerTest)[1, 'R2c'][[1]] * 100) %>% 
-      sprintf('%.2f', .), '%'
-  )
-
-```
-
-The fixed effects of this model explained `r Nakagawa2017_fixedeffects_R2_semanticpriming_lmerTest` of the variance, and the random effects explained `r Nakagawa2017_randomeffects_R2_semanticpriming_lmerTest` [@nakagawaCoefficientDeterminationR22017].
-It is to be expected that random effects explain more variance, as they involve a far larger number of coefficients for each effect.
-For instance, the by-word random slopes for a single individual-level variable (e.g., vocabulary size) involve as many coefficients as the number of words.
-Similarly, the by-participant random slopes for a single word-level variable (e.g., language-based similarity) involve as many coefficients as the number of participants.
-In contrast, a fixed effect involves 1 coefficient only.
+    getwd(),  # Circumvent illegal characters in file path
+    '/semanticpriming/frequentist_bayesian_plots/plots/semanticpriming_frequentist_bayesian_plot_informativepriors_exgaussian.pdf'
+  ))
+
+```
 
@@
 
-Figure \@ref(fig:semanticpriming-interactions-with-vocabulary-size)-b presents the interaction between vocabulary size and vision-based similarity.
-Albeit a non-significant interaction, it is noteworthy that the effect of vision-based information is larger in lower-vocabulary participants.
-
-(ref:semanticpriming-interactions-with-vocabulary-size) Interactions of vocabulary size with language- and vision-based similarity.
-Vocabulary size is constrained to deciles, whereas in the statistical analysis it contained more values within the current range.
-*n* = number of participants contained between decile values.
+Figure \@ref(fig:semanticpriming-interactions-with-vocabulary-size)-b presents the interaction between vocabulary size and visual-strength difference.^[All interaction plots across the three studies are based on the frequentist models.] Albeit a non-significant interaction, it is noteworthy that the effect of visual-strength difference is larger in lower-vocabulary participants.
+
+(ref:semanticpriming-interactions-with-vocabulary-size) Interactions of vocabulary size with language-based similarity and visual-strength difference.
+Vocabulary size is constrained to deciles (ten sections) in this plot, whereas in the statistical analysis it contained more values within the current range.
+*n* = number of participants contained between deciles.
 
@@
 
-```{r semanticpriming-interactions-with-SOA, fig.cap = 'Interactions of SOA with language-based similarity and visual strength.
-SOA was analysed using $z$-scores, but for clarity, the variable is shown in its simpler form here.', out.width = '80%'}
+```{r semanticpriming-interactions-with-SOA, fig.cap = 'Interactions of stimulus-onset asynchrony (SOA) with language-based similarity and visual strength.
+SOA was analysed using $z$-scores, but for clarity, the variable is shown in its basic form here.', out.width = '80%'}
 
@@
 
-#### The importance of outliers
-
-The interaction in Figure \@ref(fig:semanticpriming-interactions-with-vocabulary-size) is patent in all deciles of vocabulary size but most notably in the participants who lie more than 1 standard deviation away from the mean.
-Outliers in individual differences have played important roles in other areas of cognition as well, such as in the domains of aphantasia and hyperphantasia---traits characterised, respectively, by a diminished and an extraordinary ability to mentally visualise objects [@milton2021a; @zeman2020a].
-Furthermore, if we consider the difficulty of detecting effects involving individual differences [@diazNeuralSensitivityPhonological2021; @hedge2018a; @rodriguez-ferreiroSemanticPrimingSchizotypal2020], and the limited representativeness of most samples of participants [@henrich2010a], it may be fruitful to study more varied samples, where possible.
-
-### Visualising the estimates
-
-Figure \@ref(fig:semanticpriming-frequentist-bayesian-plot-informativepriors-exgaussian) presents the posterior distribution of each effect, based on the informative prior model.
-The models with the other priors produced virtually identical results (see [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results)).
-The figure also shows the frequentist estimates from Table \@ref(tab:semanticpriming-frequentist-model), to facilitate the comparison.
-
-```{r semanticpriming-frequentist-bayesian-plot-informativepriors-exgaussian, fig.cap = 'Estimates from the frequentist analysis (in red) and from the Bayesian analysis (in blue) for the semantic priming study.
-The frequentist means (represented by points) are flanked by 95\\% confidence intervals.
-The Bayesian means (represented by vertical lines) are flanked by 95\\% credible intervals, in light blue (in some cases, the interval is covered up by the bar of the mean).'}
+Figure \@ref(fig:semanticpriming-interactions-with-gender) shows the interactions of gender with language-based similarity and visual-strength difference, albeit non-significant.^[Plots of other interactions are available in [\underline{Appendix D}](#appendix-D-interaction-plots).]
+
+```{r semanticpriming-interactions-with-gender, fig.cap = 'Interactions with gender in the semantic priming study.
+Gender was analysed using $z$-scores, but for clarity, the variable is shown in its basic form here.', out.width = '80%'}
 
 # Run plot through source() rather than directly in this R Markdown document 
-# to preserve the format.
-
-source('semanticpriming/frequentist_bayesian_plots/semanticpriming_frequentist_bayesian_plots.R', 
+# to preserve the italicised text.
+
+source('semanticpriming/frequentist_analysis/semanticpriming-interactions-with-gender.R', 
        local = TRUE)
@@
     getwd(),  # Circumvent illegal characters in file path
-    '/semanticpriming/frequentist_bayesian_plots/plots/semanticpriming_frequentist_bayesian_plot_informativepriors_exgaussian.pdf'
+    '/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-gender.pdf'
   ))
@@
 ```
+
+#### The importance of outliers
+
+The interaction shown in Figure \@ref(fig:semanticpriming-interactions-with-vocabulary-size) was patent in all deciles of vocabulary size but most notably in the participants who lie more than 1 standard deviation away from the mean.
+Outliers in individual differences have played important roles in other areas of cognition as well, such as in the domains of aphantasia and hyperphantasia---traits characterised, respectively, by a diminished and an extraordinary ability to mentally visualise objects [@milton2021a; @zeman2020a].
+Furthermore, if we consider the difficulty of detecting effects involving individual differences [@diazNeuralSensitivityPhonological2021; @hedge2018a; @rodriguez-ferreiroSemanticPrimingSchizotypal2020], and the limited representativeness of most samples of participants [@henrich2010a], it may be fruitful to study more varied samples, where possible.
 
@@
 in the creation of the visual-similarity measure (e.g., both the target and the prime word had to be associated to at least 100 pictures in ImageNet).
-As a result, our data set in this analysis contained `r semanticpriming_with_visualsimilarity_number_participants` participants, `r semanticpriming_with_visualsimilarity_number_primetarget_pairs %>% formattable::comma(digits = 0)` prime-target pairs, and a total of `r length(semanticpriming_with_visualsimilarity$z_target.RT) %>% formattable::comma(digits = 0)` RTs.
+As a result, our data set in this analysis contained `r semanticpriming_with_visualsimilarity_number_participants` participants, `r semanticpriming_with_visualsimilarity_number_primetarget_pairs %>% formattable::comma(digits = 0)` prime-target pairs, and `r length(semanticpriming_with_visualsimilarity$z_target.RT) %>% formattable::comma(digits = 0)` RTs.
 On average, there were `r semanticpriming_with_visualsimilarity_mean_primetarget_pairs_per_participant` prime-target pairs per participant ($SD$ = `r semanticpriming_with_visualsimilarity_SD_primetarget_pairs_per_participant`), and conversely, `r semanticpriming_with_visualsimilarity_mean_participants_per_primetarget_pair` participants per prime-target pair ($SD$ = `r semanticpriming_with_visualsimilarity_SD_participants_per_primetarget_pair`).
@@
 
-Table \@ref(tab:semanticpriming-with-visualsimilarity-frequentist-model) presents the results of the mixed-effects model.
+```{r}
+
+# Calculate R^2. This coefficient must be interpreted with caution 
+# (Nakagawa et al., 2017; https://doi.org/10.1098/rsif.2017.0213). 
+# Also, transform coefficient to rounded percentage.
+
+Nakagawa2017_fixedeffects_R2_semanticpriming_with_visualsimilarity_lmerTest = 
+  paste0(
+    (MuMIn::r.squaredGLMM(semanticpriming_with_visualsimilarity_lmerTest)[1, 'R2m'][[1]] * 100) %>% 
+      sprintf('%.2f', .), '%'
+  )
+
+Nakagawa2017_randomeffects_R2_semanticpriming_with_visualsimilarity_lmerTest = 
+  paste0(
+    (MuMIn::r.squaredGLMM(semanticpriming_with_visualsimilarity_lmerTest)[1, 'R2c'][[1]] * 100) %>% 
+      sprintf('%.2f', .), '%'
+  )
+
+```
+
+Table \@ref(tab:semanticpriming-with-visualsimilarity-frequentist-model) presents the results of the frequentist model.
 Due to space, the covariates are shown in Table \@ref(tab:semanticpriming-with-visualsimilarity-frequentist-model-covariates).
-
-```{r semanticpriming-with-visualsimilarity-frequentist-model, results = 'asis'}
+The fixed effects explained `r Nakagawa2017_fixedeffects_R2_semanticpriming_with_visualsimilarity_lmerTest` of the variance, and the random effects `r Nakagawa2017_randomeffects_R2_semanticpriming_with_visualsimilarity_lmerTest` (Nakagawa et al., 2017; for an explanation of this difference, see [\underline{above}](#semanticpriming-results)).
+Figure \@ref(fig:semanticpriming-with-visualsimilarity-confidence-intervals-plot) displays the estimates for the effects of interest.
+
+```{r semanticpriming-with-visualsimilarity-frequentist-model, results = 'asis', out.width = '90%'}
 
@@
   # Place table close to designated position
-  kable_styling(latex_options = c('hold_position')) %>%
+  kable_styling(latex_options = c('HOLD_position')) %>%
 
@@
 
-# Calculate R^2. This coefficient must be interpreted with caution 
-# (Nakagawa et al., 2017; https://doi.org/10.1098/rsif.2017.0213). 
-# Also, transform coefficient to rounded percentage.
-
-Nakagawa2017_fixedeffects_R2_semanticpriming_with_visualsimilarity_lmerTest = 
-  paste0(
-    (MuMIn::r.squaredGLMM(semanticpriming_with_visualsimilarity_lmerTest)[1, 'R2m'][[1]] * 100) %>% 
-      sprintf('%.2f', .), '%'
-  )
-
-Nakagawa2017_randomeffects_R2_semanticpriming_with_visualsimilarity_lmerTest = 
-  paste0(
-    (MuMIn::r.squaredGLMM(semanticpriming_with_visualsimilarity_lmerTest)[1, 'R2c'][[1]] * 100) %>% 
-      sprintf('%.2f', .), '%'
-  )
-
-```
-
-The fixed effects of this model explained `r Nakagawa2017_fixedeffects_R2_semanticpriming_with_visualsimilarity_lmerTest` of the variance, and the random effects explained `r Nakagawa2017_randomeffects_R2_semanticpriming_with_visualsimilarity_lmerTest` (Nakagawa et al., 2017; for background on why random effects explain more variance, see [Results in Study 1](#semanticpriming-results)).
-
-Figure \@ref(fig:semanticpriming-with-visualsimilarity-confidence-intervals-plot) presents the means and 95% confidence intervals for the effects of interest.
+```
 
@@
 @wingfieldUnderstandingRoleLinguistic2022 reanalysed the data from @pexman2017a using language-based variables that are more related to the language system than to the visual system.
-The authors found that the variables that best explained RTs were word co-occurrence measures.
-Specifically, the measures corresponded to the distance from each stimulus word to two labels that were central to the task, namely, the words ‘abstract’ and ‘concrete’.
+The task used by Pexman et al.
+had been semantic decision, in which participants assessed whether words were abstract or concrete.
+Wingfield and Connell found that the variables that best explained RTs were word co-occurrence measures.
+Specifically, one of these variables was the correlation distance between each stimulus word and the word 'abstract'.
+The other variable was the correlation distance between each stimulus word and the word 'concrete'.
 Wingfield and Connell studied these distance measures in various forms, and found that cosine and correlation distance yielded the best results.
-We used the correlation distance following the advice of [@kiela2014a].
-Furthermore, we sought to avoid the collinearity between these variables ($r$ = .99) and to facilitate the analysis of interactions with other variables.
-For this purpose, we created a difference score by subtracting distance to 'abstract' from the distance to 'concrete'.
-The resulting variable was practically equivalent to the distance to 'abstract', as attested by its large correlation with word concreteness ($r$ = `r cor(semanticdecision$word_cooccurrence, semanticdecision$information_uptake) %>% sprintf('%.2f', .)`).
-Last, it should be noted that this difference score may not be affected by the reduced sensitivity of other ones [see @rodriguez-ferreiroSemanticPrimingSchizotypal2020], as this difference score did not entail an aggregation of data points over any third variables.
+We used the correlation distance, following the advice of @kiela2014a (see details below).
 
@@
 
-- $Z$-scored vocabulary size [`z_vocabulary_size`; calculated from `NAART` in @pexman2017a].
+#### Vocabulary size
+
+[`z_vocabulary_size`; calculated from `NAART` in @pexman2017a].
 In the test used by @pexman2018a, participants were presented with 35 rare words, whose pronunciations are not regular (e.g., *gaoled*, *ennui*), and they were asked to read the words aloud.
@@
 
-- $Z$-scored, recoded participant's gender [`z_recoded_participant_gender`; calculated from `Gender` in @pexman2018a]
-
-- $Z$-scored distance to word 'abstract': a distributional semantic distance measure obtained from @wingfieldUnderstandingRoleLinguistic2022 that reflects the correlation distance between each stimulus word and the word 'abstract'.^[Specifically, this measure is a difference score that merges both the distance to the word 'abstract' and the distance to the word 'concrete'.
-We drew on both variables because @wingfieldUnderstandingRoleLinguistic2022 found them to be similarly important.
-Yet, we had to create a difference score because these variables were highly correlated ($r$ = .99), we created a difference score by subtracting the distance to 'abstract' from the distance to 'concrete'.
-The resulting difference score was practically equivalent to the distance to the word 'abstract', as attested by its correlation with word concreteness (see Figure \@ref(fig:semanticdecision-correlations)).
-Our difference score in practice  The variable `Conditional_probability_BNC_r5_correlation_abstract_distance` was subtracted from `Conditional_probability_BNC_r5_correlation_concrete_distance`.]
-
-- $Z$-scored vision-based information in words [`z_visual_rating`; calculated from `Visual.mean` in @lynott2020a]
+#### Participant's gender
+
+[`z_recoded_participant_gender`; calculated from `Gender` in @pexman2018a]
+
+#### Word co-occurrence
+
+The zero-order correlation between Wingfield and Connell's (2022) distance to 'abstract' and distance to 'concrete' was $r$ = `r cor(semanticdecision$Conditional_probability_BNC_r5_correlation_abstract_distance, semanticdecision$Conditional_probability_BNC_r5_correlation_concrete_distance) %>% sprintf('%.2f', .)`.
+To avoid the collinearity between these variables in the model [@dormannCollinearityReviewMethods2013; @harrison2018a], and to facilitate the analysis of interactions with other variables, we created a difference score by subtracting the distance to 'abstract' from the distance to 'concrete'.
+This new variable was named 'word co-occurrence'.
+As Figure \@ref(fig:semanticdecision-cooccurrence-correlations) demonstrates, the difference score captured the explanatory power of the two original variables, resulting in an increase of the correlation with word concreteness.
+
+```{r semanticdecision-cooccurrence-correlations, fig.cap = "Zero-order correlations among Wingfield and Connell's (2022) distances, the difference score (word co-occurrence) and word concreteness (Brysbaert et al., 2014).", fig.width = 7, fig.height = 2.2, out.width = '58%'}
+
+# Using the following variables...
+semanticdecision[, c('word_concreteness', 'word_cooccurrence',
+                     'Conditional_probability_BNC_r5_correlation_concrete_distance',
+                     'Conditional_probability_BNC_r5_correlation_abstract_distance')] %>%
+
+  # renamed for the sake of clarity
+  rename('Word concreteness' = word_concreteness, 
+         'Word co-occurrence' = word_cooccurrence,
+         "Distance to 'concrete'" = Conditional_probability_BNC_r5_correlation_concrete_distance,
+         "Distance to 'abstract'" = Conditional_probability_BNC_r5_correlation_abstract_distance) %>%
+
+  # make correlation matrix (custom function from the 'R_functions' folder)
+  correlation_matrix() + 
+  theme(plot.margin = unit(c(0, -0.5, 0.05, -3.78), 'in'))
+
+```
+
+#### Visual strength
+
+[`z_visual_rating`; calculated from `Visual.mean` in @lynott2020a]
 
@@
 
-The final data set contained `r semanticdecision_number_participants` participants, `r semanticdecision_number_words %>% formattable::comma(digits = 0)` words, and a total of `r length(semanticdecision$z_RTclean) %>% formattable::comma(digits = 0)` RTs.
+The final data set contained `r semanticdecision_number_participants` participants, `r semanticdecision_number_words %>% formattable::comma(digits = 0)` words, and `r length(semanticdecision$z_RTclean) %>% formattable::comma(digits = 0)` RTs.
 On average, there were `r semanticdecision_mean_words_per_participant` words per participant ($SD$ = `r semanticdecision_SD_words_per_participant`), and conversely, `r semanticdecision_mean_participants_per_word` participants per word ($SD$ = `r semanticdecision_SD_participants_per_word`).
@@
          'Information uptake' = z_information_uptake,
-         "Distance to word 'abstract'" = z_word_cooccurrence,
+         "Word co-occurrence" = z_word_cooccurrence,
          'Visual strength' = z_visual_rating,
@@
 Furthermore, the posterior predictive checks revealed major divergences between the observed data and the predicted outcome (see [\underline{Appendix C}](#appendix-C-Bayesian-analysis-diagnostics)).
-Since the results were not valid, they are not shown in the main text but instead in [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results).
+Since the results were not valid, they are not shown in the main text but in [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results).
 
@@
 
-Table \@ref(tab:semanticdecision-frequentist-model) presents the results of the mixed-effects model.
+```{r}
+
+# Calculate R^2. This coefficient must be interpreted with caution 
+# (Nakagawa et al., 2017; https://doi.org/10.1098/rsif.2017.0213). 
+# Also, transform coefficient to rounded percentage.
+
+Nakagawa2017_fixedeffects_R2_semanticdecision_lmerTest = 
+  paste0(
+    (MuMIn::r.squaredGLMM(semanticdecision_lmerTest)[1, 'R2m'][[1]] * 100) %>% 
+      sprintf('%.2f', .), '%'
+  )
+
+Nakagawa2017_randomeffects_R2_semanticdecision_lmerTest = 
+  paste0(
+    (MuMIn::r.squaredGLMM(semanticdecision_lmerTest)[1, 'R2c'][[1]] * 100) %>% 
+      sprintf('%.2f', .), '%'
+  )
+
+```
+
+Table \@ref(tab:semanticdecision-frequentist-model) presents the results of the frequentist model.
+The fixed effects explained `r Nakagawa2017_fixedeffects_R2_semanticdecision_lmerTest` of the variance, and the random effects `r Nakagawa2017_randomeffects_R2_semanticdecision_lmerTest` [@nakagawaCoefficientDeterminationR22017; for an explanation of this difference, see [\underline{Results of Study 1}](#semanticpriming-results)).
+Figure \@ref(fig:semanticdecision-confidence-intervals-plot) displays these estimates.^[Bayesian estimates not shown as they were not valid.
+They are nonetheless available in [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results).]
 
@@
   rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
-    'z_word_cooccurrence'] = "Distance to word 'abstract' $^{\\text{b}}$"
+    'z_word_cooccurrence'] = "Word co-occurrence $^{\\text{b}}$"
 
@@
   rownames(confint_semanticdecision_lmerTest) == 
-    'z_word_cooccurrence'] = "Distance to word 'abstract' $^{\\text{b}}$"
+    'z_word_cooccurrence'] = "Word co-occurrence $^{\\text{b}}$"
 
@@
   # Place table close to designated position and highlight covariates
-  kable_styling(latex_options = c('hold_position', 'striped'), 
-                stripe_index = c(2, 5:7, 10:11)) %>%
+  kable_styling(latex_options = c('HOLD_position', 'striped'), 
+                stripe_index = c(2, 5:7, 10:13)) %>%
 
@@
 
-# Calculate R^2. This coefficient must be interpreted with caution 
-# (Nakagawa et al., 2017; https://doi.org/10.1098/rsif.2017.0213). 
-# Also, transform coefficient to rounded percentage.
-
-Nakagawa2017_fixedeffects_R2_semanticdecision_lmerTest = 
+```
+
+```{r semanticdecision-confidence-intervals-plot, fig.cap = 'Means and 95\\% confidence intervals for the effects of interest in the semantic decision study.'}
+
+# Run plot through source() rather than directly in this R Markdown document
+# to preserve the format.
+
+source('semanticdecision/frequentist_analysis/semanticdecision_confidence_intervals_plot.R', 
+       local = TRUE)
+
+include_graphics(
   paste0(
-    (MuMIn::r.squaredGLMM(semanticdecision_lmerTest)[1, 'R2m'][[1]] * 100) %>% 
-      sprintf('%.2f', .), '%'
-  )
-
-Nakagawa2017_randomeffects_R2_semanticdecision_lmerTest = 
-  paste0(
-    (MuMIn::r.squaredGLMM(semanticdecision_lmerTest)[1, 'R2c'][[1]] * 100) %>% 
-      sprintf('%.2f', .), '%'
-  )
-
-```
-
-The fixed effects of this model explained `r Nakagawa2017_fixedeffects_R2_semanticdecision_lmerTest` of the variance, and the random effects explained `r Nakagawa2017_randomeffects_R2_semanticdecision_lmerTest` [@nakagawaCoefficientDeterminationR22017].
+    getwd(),  # Circumvent illegal characters in file path
+    '/semanticdecision/frequentist_analysis/plots/semanticdecision_confidence_intervals_plot.pdf'
+  ))
+
+```
 
@@
 In contrast, Figure \@ref(fig:semanticdecision-interactions-with-vocabulary-size)-c shows that higher-vocabulary participants benefitted more strongly from word concreteness.
-Since the variable that is most relevant to the semantic decision task is word concreteness, the present interactions suggest that higher-vocabulary participants were better able to focus on the most relevant information, whereas lower-vocabulary participants were sensitive to a greater breadth of information [@lim2020a; @pexman2018a; @yap2012a; @yap2017a].
+Since the variable that is most relevant to the semantic decision task is word concreteness, the present interactions suggest that higher-vocabulary participants were better able to focus on the most relevant information, whereas lower-vocabulary participants were sensitive to a greater breadth of information [@lim2020a; @pexman2018a; @yap2012a; @yap2017a; @yapIndividualDifferencesJoint2009].
 
 (ref:semanticdecision-interactions-with-vocabulary-size) Interactions of vocabulary size with (a) language-based information, (b) visual strength and (c) word concreteness.
-Vocabulary size is constrained to deciles, whereas in the statistical analysis it contained more values within the current range.
-*n* = number of participants contained between decile values.
-
-```{r semanticdecision-interactions-with-vocabulary-size, fig.cap = '(ref:semanticdecision-interactions-with-vocabulary-size)', out.height = '95%'}
+Vocabulary size is constrained to deciles in this plot, whereas in the statistical analysis it contained more values within the current range.
+*n* = number of participants contained between deciles.
+
+```{r semanticdecision-interactions-with-vocabulary-size, fig.cap = '(ref:semanticdecision-interactions-with-vocabulary-size)', out.width = '90%'}
 
@@
 
-The present analysis uses a continuous measure of word concreteness.
+The present analysis used a continuous measure of word concreteness.
 In contrast, @pexman2018a analysed the same data set after dividing the stimulus words into abstract and concrete subsets, which they analysed separately.
@@
 Notwithstanding the aforementioned bimodal distributions, @trocheDefiningConceptualTopography2017 suggested that a continuous analysis remains necessary to study word concreteness [also see @cohenCostDichotomization1983].
-Consistent with this, our present findings demonstrated the sensitivity of a continuous word-concreteness variable to patterns such as the greater role of task-relevant variables in high-vocabulary participants.
+Consistent with this, our present findings demonstrated the sensitivity of a continuous word concreteness variable to patterns such as the greater role of task-relevant variables in high-vocabulary participants.
 In conclusion, the literature and our findings suggest that the split-data approach and the continuous approach to word concreteness are both useful.
@@
 
-### Visualising the estimates
-
-Figure \@ref(fig:semanticdecision-confidence-intervals-plot) presents the means and 95% confidence intervals for the effects of interest.^[Bayesian estimates not shown as they were not valid.
-They are nonetheless available in [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results).]
-
-```{r semanticdecision-confidence-intervals-plot, fig.cap = 'Means and 95\\% confidence intervals for the effects of interest in the semantic decision model.', out.width = '110%'}
+Figure \@ref(fig:semanticdecision-interactions-with-gender) shows the interactions of gender with language-based similarity and visual-strength difference, albeit non-significant.^[Plots of other interactions are available in [\underline{Appendix D}](#appendix-D-interaction-plots).]
+
+```{r semanticdecision-interactions-with-gender, fig.cap = 'Interactions with gender in the semantic decision study.
+Gender was analysed using $z$-scores, but for clarity, the variable is shown in its basic form here.', out.width = '90%'}
 
 # Run plot through source() rather than directly in this R Markdown document 
-# to preserve the format.
-
-source('semanticdecision/frequentist_analysis/semanticdecision_confidence_intervals_plot.R', 
+# to preserve the italicised text.
+
+source('semanticdecision/frequentist_analysis/semanticdecision-interactions-with-gender.R', 
        local = TRUE)
@@
     getwd(),  # Circumvent illegal characters in file path
-    '/semanticdecision/frequentist_analysis/plots/semanticdecision_confidence_intervals_plot.pdf'
+    '/semanticdecision/frequentist_analysis/plots/semanticdecision-interactions-with-gender.pdf'
   ))
@@
 
-The final data set contained `r lexicaldecision_number_participants` participants, `r lexicaldecision_number_words %>% formattable::comma(digits = 0)` words, and a total of `r length(lexicaldecision$z_RT) %>% formattable::comma(digits = 0)` RTs.
+The final data set contained `r lexicaldecision_number_participants` participants, `r lexicaldecision_number_words %>% formattable::comma(digits = 0)` words, and `r length(lexicaldecision$z_RT) %>% formattable::comma(digits = 0)` RTs.
 On average, there were `r lexicaldecision_mean_words_per_participant` words per participant ($SD$ = `r lexicaldecision_SD_words_per_participant`), and conversely, `r lexicaldecision_mean_participants_per_word` participants per word ($SD$ = `r lexicaldecision_SD_participants_per_word`).
@@
 
-Table \@ref(tab:lexicaldecision-frequentist-model) presents the results of the mixed-effects model.
+```{r}
+
+# Calculate R^2. This coefficient must be interpreted with caution 
+# (Nakagawa et al., 2017; https://doi.org/10.1098/rsif.2017.0213). 
+# Also, transform coefficient to rounded percentage.
+
+Nakagawa2017_fixedeffects_R2_lexicaldecision_lmerTest = 
+  paste0(
+    (MuMIn::r.squaredGLMM(lexicaldecision_lmerTest)[1, 'R2m'][[1]] * 100) %>% 
+      sprintf('%.2f', .), '%'
+  )
+
+Nakagawa2017_randomeffects_R2_lexicaldecision_lmerTest = 
+  paste0(
+    (MuMIn::r.squaredGLMM(lexicaldecision_lmerTest)[1, 'R2c'][[1]] * 100) %>% 
+      sprintf('%.2f', .), '%'
+  )
+
+```
+
+Table \@ref(tab:lexicaldecision-frequentist-model) presents the results of the frequentist model.
+The fixed effects explained `r Nakagawa2017_fixedeffects_R2_lexicaldecision_lmerTest` of the variance, and the random effects `r Nakagawa2017_randomeffects_R2_lexicaldecision_lmerTest` [@nakagawaCoefficientDeterminationR22017; for an explanation of this difference, see [\underline{Results of Study 1}](#semanticpriming-results)).
+Figure \@ref(fig:lexicaldecision-frequentist-bayesian-plot-weaklyinformativepriors-exgaussian) displays the frequentist estimates alongside the Bayesian estimates.
+The latter are from the weakly-informative prior model.
+The estimates of the two other models (i.e., with informative and diffuse priors, respectively) were virtually identical to these (see [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results)).
 
@@
 
-# Calculate R^2. This coefficient must be interpreted with caution 
-# (Nakagawa et al., 2017; https://doi.org/10.1098/rsif.2017.0213). 
-# Also, transform coefficient to rounded percentage.
-
-Nakagawa2017_fixedeffects_R2_lexicaldecision_lmerTest = 
-  paste0(
-    (MuMIn::r.squaredGLMM(lexicaldecision_lmerTest)[1, 'R2m'][[1]] * 100) %>% 
-      sprintf('%.2f', .), '%'
-  )
-
-Nakagawa2017_randomeffects_R2_lexicaldecision_lmerTest = 
-  paste0(
-    (MuMIn::r.squaredGLMM(lexicaldecision_lmerTest)[1, 'R2c'][[1]] * 100) %>% 
-      sprintf('%.2f', .), '%'
-  )
-
-```
-
-The fixed effects of this model explained `r Nakagawa2017_fixedeffects_R2_lexicaldecision_lmerTest` of the variance, and the random effects explained `r Nakagawa2017_randomeffects_R2_lexicaldecision_lmerTest` [@nakagawaCoefficientDeterminationR22017].
-
-### Visualising the estimates
-
-Figure \@ref(fig:lexicaldecision-frequentist-bayesian-plot-weaklyinformativepriors-exgaussian) presents the posterior distribution of each effect, based on the informative prior model.
-The models with the other priors produced virtually identical results (see [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results)).
-The figure also shows the frequentist estimates from Table \@ref(tab:lexicaldecision-frequentist-model), to facilitate the comparison.
+```
 
@@
     '/lexicaldecision/frequentist_bayesian_plots/plots/lexicaldecision_frequentist_bayesian_plot_weaklyinformativepriors_exgaussian.pdf'
+  ))
+
+```
+
+Figure \@ref(fig:lexicaldecision-interactions-with-vocabulary-age) presents the interactions of vocabulary age with word frequency and with visual strength, albeit non-significant.
+
+(ref:lexicaldecision-interactions-with-vocabulary-age) Interactions of vocabulary age with word frequency and visual strength.
+Vocabulary age is constrained to sextiles (six sections) in this plot, whereas in the statistical analysis it contained more values within the current range.
+*n* = number of participants contained between sextiles.
+
+```{r lexicaldecision-interactions-with-vocabulary-age, fig.cap = '(ref:lexicaldecision-interactions-with-vocabulary-age)', out.width = '80%'}
+
+# Run plot through source() rather than directly in this R Markdown document 
+# to preserve the italicised text.
+
+source('lexicaldecision/frequentist_analysis/lexicaldecision-interactions-with-vocabulary-age.R', 
+       local = TRUE)
+
+include_graphics(
+  paste0(
+    getwd(),  # Circumvent illegal characters in file path
+    '/lexicaldecision/frequentist_analysis/plots/lexicaldecision-interactions-with-vocabulary-age.pdf'
+  ))
+
+```
+
+Figure \@ref(fig:lexicaldecision-interactions-with-gender) shows the interactions of gender with language-based similarity and visual-strength difference, albeit non-significant.^[Plots of other interactions are available in [\underline{Appendix D}](#appendix-D-interaction-plots).]
+
+```{r lexicaldecision-interactions-with-gender, fig.cap = 'Interactions with gender in the lexical decision study.
+Gender was analysed using $z$-scores, but for clarity, the variable is shown in its basic form here.', out.width = '80%'}
+
+# Run plot through source() rather than directly in this R Markdown document 
+# to preserve the italicised text.
+
+source('lexicaldecision/frequentist_analysis/lexicaldecision-interactions-with-gender.R', 
+       local = TRUE)
+
+include_graphics(
+  paste0(
+    getwd(),  # Circumvent illegal characters in file path
+    '/lexicaldecision/frequentist_analysis/plots/lexicaldecision-interactions-with-gender.pdf'
   ))

### 2022-06-29 manuscript/manuscript.tex
29062022

@@
   pdflang={en-EN},
-  pdfkeywords={semantic, conceptual processing, vocabulary size, statistical power},
+  pdfkeywords={conceptual processing, semantic priming, semantic decision, lexical decision, language, vision, vocabulary size, statistical power},
   hidelinks,
@@
 {}{\PatchFailed}
-\keywords{semantic, conceptual processing, vocabulary size, statistical power}
+\keywords{conceptual processing, semantic priming, semantic decision, lexical decision, language, vision, vocabulary size, statistical power}
 \usepackage{csquotes}
@@
 Research over the past two decades has suggested that conceptual processing depends on both language-based and vision-based information.
-We tested this interplay at three levels of the data: individual differences, words and tasks.
+We tested this interplay at three levels of the data: individuals, words and tasks.
 To this aim, we drew on three existing data sets that were composed of large samples, and implemented the paradigms of semantic priming, semantic decision and lexical decision.
@@
 In addition, higher-vocabulary participants presented a greater effect of language-based similarity than lower-vocabulary participants.
-Conversely, lower-vocabulary participants presented a greater effect of vision-based information, which was less relevant to the task.
-This `relevance advantage' for higher-vocabulary participants also appeared in the semantic decision study, whose task required distinguishing between concrete and abstract words.
-Specifically, higher-vocabulary participants were more strongly influenced by word concreteness than lower-vocabulary participants.
-Furthermore, we compared the effects of different measures of visual information.
+In contrast, this pattern did not hold for vision-based information, which was less relevant to the task.
+The `relevance advantage' in higher-vocabulary participants also appeared in the semantic decision and the lexical decision studies.
+Furthermore, we compare the effects of two visual information measures, and discuss the role of measurement instruments in this research topic.
 Lastly, we estimated the sample size required to reliably examine each effect of interest.
-We found that 300 participants would suffice to examine language-based information contained in words, whereas more than 1,000 participants would be necessary to examine vision-based information as well as the interactions between both the former variables and vocabulary size, gender and presentation speed.
+We found that 300 participants suffice to examine language-based information contained in words, whereas more than 1,000 participants are necessary to examine vision-based information as well as the interactions between both the former variables and vocabulary size, gender and presentation speed.
 }
@@
 
-Research over the past two decades has suggested that conceptual processing involves both `linguistic' and `embodied' systems of the brain.
-The language system is characterised by associations across networks of words (Landauer et al., 1998; Pylyshyn, 1973), whereas the embodiment system is characterised by associations within perceptual, motor, affective and social domains (Barsalou, 1999; Diveica et al., 2022).
-Both systems have strengths and limitations (Connell, 2019; Dove, 2020; Kumar, 2021; Louwerse et al., 2015; Mahon \& Hickok, 2016).
-As a result, conceptual processing flexibly draws on these systems following the demands of the context (Sato et al., 2008; Shebani \& Pulvermüller, 2018; Willems \& Casasanto, 2011).
-
-The language system is involved in the representation of both abstract and concrete concepts (Ponari, Norbury, Rotaru, et al., 2018; Reggin et al., 2021).
-For instance, measures of distributional semantic distance---solely based on texts---have been shown to capture aspects of the real world with considerable accuracy (Contreras Kallens et al., 2022; De Deyne et al., 2013; Kumar et al., 2020; Louwerse \& Zwaan, 2009).
-Although the language system is likely more important for the processing of abstract---rather than concrete---concepts (Barca et al., 2020; Duñabeitia et al., 2009; Hultén et al., 2021), although the degree of this difference could be small (De Deyne et al., 2013).
-Language-based regularities may even allow distinguishing between concrete and abstract words, as word concreteness is consistently related to linguistic characteristics such as part of speech, morphological structure, countability and etymology (Lievers et al., 2021).
-
-Regarding the time course, the language system is activated more quickly in semantically-deep tasks (Connell \& Lynott, 2013; Louwerse \& Connell, 2011), whereas both systems are similarly fast in semantically-shallow tasks (Petilli et al., 2021).
-As a result of these characteristics, the language system is equipped to support a major part of conceptual processing (Connell, 2019; Connell \& Lynott, 2014).
-However, the language system is hindered by the symbol grounding problem, which refers to the impossibility of obtaining meaning---or `grounding' lexical content in reality---on the sole basis of word-to-word associations (Günther et al., 2021, 2018; Harnad, 1990; Louwerse, 2011).
-Another limitation is caused by the finite vocabularies of languages, which sometimes fall short of the richness of sensorimotor experience (De Deyne et al., 2021; Günther et al., 2021; Majid \& Burenhult, 2014; Majid \& Levinson, 2011; Majid \& van Staden, 2015).
-In conclusion, word-to-word associations appear to be necessary but not sufficient for conceptual processing.
-
-The embodiment system is best suited for the representation of concrete concepts, such as those involving perceptual features (Ostarek \& Huettig, 2017; Pecher et al., 1998; Yee et al., 2012) and actions (Riccardi et al., 2019).
-Some research has suggested that embodied simulation plays an integral role in conceptual processing (Pulvermüller, 2013), at least in the context of relatively-semantic tasks and stimuli (Connell \& Lynott, 2016; García et al., 2020; Lebois et al., 2015; Ostarek \& Huettig, 2017; Pecher et al., 1998; Shebani et al., 2021; Vitale et al., 2021; Vukovic et al., 2017; X.
-Wang et al., 2021; Yee et al., 2012).
-For instance, Riccardi et al.
-(2019) investigated the comprehension of action verbs and abstract verbs in left-hemisphere stroke patients, and found that the processing of action concepts relied more heavily on sensory-motor areas.
-Furthermore, studies have suggested that even abstract concepts may be partially grounded in modality-specific domains such as emotion, sociality and interoception (Conca et al., 2021; Connell et al., 2018; Diveica et al., 2022; Kousta et al., 2011; Vigliocco et al., 2014; X.
-Wang et al., 2021).
-
-However, other research has curtailed the importance of this system (Bottini et al., 2021; Garcea et al., 2013; Günther et al., 2021, 2018; Mahon \& Caramazza, 2008; Montero-Melis et al., 2022; Vannuscorps et al., 2016).
-For instance, studies have found that lesions to motor brain areas did not systematically impair the processing of action concepts in language (Negri et al., 2007; Papeo et al., 2010).
-
-\hypertarget{interplay-between-language-and-embodiment-systems}{%
-\subsection{Interplay between language and embodiment systems}\label{interplay-between-language-and-embodiment-systems}}
-
-The above characteristics make the language and the embodiment systems complementary to each other (Andrews et al., 2009; De Deyne et al., 2021; J.
-Wang et al., 2010).
+Over the past decades, research in psycholinguistics has suggested that conceptual processing depends on both language and embodiment systems (Barsalou et al., 2008; Connell \& Lynott, 2013; Louwerse, 2011).
 A comprehensive approach to both these systems requires a direct comparison of them.
@@
 
-\hypertarget{the-present-study}{%
-\section{The present study}\label{the-present-study}}
-
-There is considerable evidence supporting the `hybrid' theory positing that conceptual processing depends on both language and embodiment systems (Barsalou et al., 2008; Connell \& Lynott, 2013; Louwerse, 2011).
-Nonetheless, there are also reasons to continue testing this theory.
+In spite of the amount of evidence favouring the interplay between language and embodiment, there are at least 2 reasons to continue testing the interplay theory.
 Firstly, the coexistence of several systems in a scientific theory must be thoroughly justified, due to the value of simplicity, as epitomised by Occam's razor (Gallese \& Lakoff, 2005; Tillman et al., 2015).
 This point is particularly pressing because the language system has consistently produced larger effect sizes than the embodiment system (Banks et al., 2021; Kiela \& Bottou, 2014; Lam et al., 2015; Louwerse et al., 2015; Pecher et al., 1998; Petilli et al., 2021).
+Consequently, in this research question, we examine whether the interplay between linguistic and visual processing holds in the expected directions and at multiple levels of the experimental structure.
+
 Secondly, mixed evidence has appeared regarding some aspects of the interplay.
-For instance, whereas some studies have suggested that the language system becomes relevant before the embodiment system (Lam et al., 2015; Louwerse \& Connell, 2011), a recent study found the opposite pattern (Petilli et al., 2021).
-Similarly, whereas some evidence has suggested that female participants might draw on the language system more prominently than males (Hutchinson \& Louwerse, 2013), other research has suggested that this difference could be negligible (Wallentin, 2020).
-Thirdly, the role of individual differences has not been examined in most of the studies addressing the language--embodiment interplay.
-Fourthly and last, the scarcity of statistical power that has ailed some studies in cognitive psychology and neuroscience (Marek et al., 2022; Vasishth \& Gelman, 2021) is likely to have affected some studies in the present topic area, too (see Lynott et al., 2014; Montero-Melis et al., 2022).
-
-The above open questions were addressed in the present study.
-These questions were overarched by the main research question, which examined whether the interplay between linguistic and visual processing held in the expected direction and at multiple levels of the experimental structure.
-To study this question, we drew on the data sets from three previous studies whose samples of participants were larger than average.
-These studies implemented the paradigms of semantic priming (Hutchison et al., 2013), semantic decision (Pexman et al., 2017) and lexical decision (Balota et al., 2007).
-Importantly, we extended these data sets with
+For instance, whereas some studies have suggested that the language system is activated before the embodiment system (Lam et al., 2015; Louwerse \& Connell, 2011), a recent study found the opposite pattern in a lexical decision task (Petilli et al., 2021).
+Similarly, some evidence has suggested that high-vocabulary participants are more sensitive to linguistic features (Yap et al., 2017), whereas other evidence has suggested the opposite (Yap et al., 2009, 2012).
+Another case of mixed evidence regards gender: whereas some evidence has suggested that female participants draw on the language system more prominently than males (Hutchinson \& Louwerse, 2013), other research has suggested that this difference is negligible in the general population (Wallentin, 2020).
+Presumably, the scarcity of statistical power that has ailed some studies in cognitive psychology and neuroscience (Marek et al., 2022; Vasishth \& Gelman, 2021) may have affected some studies in the present topic area as well (see Lynott et al., 2014; Montero-Melis et al., 2022).
+Therefore, in this study, we re-examine longstanding questions using larger-than-average data sets, and calculate the sample size required to reliably detect a range of effects.
+
+\hypertarget{language-and-vision}{%
+\subsection{Language and vision}\label{language-and-vision}}
+
+To retest the interplay theory, we revisit previous studies that contained larger-than-average samples of participants.
+Each of our three studies is organised around one \emph{hub} study.
+In Study 1, the hub is Hutchison et al.
+(2013), which implements a semantic priming paradigm.
+In Study 2, the hub is Pexman et al.
+(2017), which implements a lexical decision paradigm.
+In Study 3, the hub is Balota et al.
+(2007), which implements a lexical decision paradigm.
+Upon this basis, we added word-level variables from other studies to tap into language (Mandera et al., 2017; Wingfield \& Connell, 2022) and vision (Lynott et al., 2020; Petilli et al., 2021).
+Additionally, we included several covariates---or nuisance variables---to allow a rigorous analysis of the effects of interest (Sassenhagen \& Alday, 2016).
+These covariates comprised participant-specific variables (e.g., attentional control), lexical variables (e.g., word frequency) and word concreteness.
 
@@
 Experimental data in psycholinguistics often consists of various levels, such as participants, words and tasks.
-A simultaneous examination of these levels should improve our understanding of the evidence collected (Ostarek \& Bottini, 2021).
-For instance, this cross-examination can help increase our certainty on the attribution of explanatory power to each level, as well as allowing a comparison of the explanatory power across levels.
-This multilevel approach is complementary to another approach in the field which seeks to test the causal contribution of different sources of information to conceptual processing---e.g., language (Ponari, Norbury, Rotaru, et al., 2018), perception (Stasenko et al., 2014) and action (Speed et al., 2017).
+A simultaneous examination of these levels should enhance our understanding of the evidence collected (Ostarek \& Bottini, 2021)---for instance, by shedding light on the distribution of explanatory power within and across levels.
+This multilevel approach is complementary to another approach in the field that seeks to test the causal contribution of different sources of information to conceptual processing---e.g., language (Ponari, Norbury, Rotaru, et al., 2018), perception (Stasenko et al., 2014) and action (Speed et al., 2017).
 
@@
 
-\hypertarget{participant-level}{%
-\subsection{Participant level}\label{participant-level}}
-
-*** to be edited *** Individual differences in domains such as language, perception, mental imagery and physical experience (e.g., Davies et al., 2017; Dils \& Boroditsky, 2010; Fetterman et al., 2018; Holt \& Beilock, 2006; Mak \& Willems, 2019; Miceli et al., 2022; Pexman \& Yap, 2018; Vukovic \& Williams, 2015; Yap et al., 2012, 2017).\footnote{According to Lamiell (2019), `individual differences' is a misnomer in that the methods used to analyse individual differences (e.g, regression) are not participant-specific.
+\hypertarget{individual-level}{%
+\subsection{Individual level}\label{individual-level}}
+
+Variation The role of individual differences in domains such as language, perception, mental imagery and physical experience (e.g., Davies et al., 2017; Dils \& Boroditsky, 2010; Fetterman et al., 2018; Holt \& Beilock, 2006; Mak \& Willems, 2019; Miceli et al., 2022; Pexman \& Yap, 2018; Vukovic \& Williams, 2015; Yap et al., 2012, 2017).\footnote{According to Lamiell (2019), `individual differences' is a misnomer in that the methods used to analyse individual differences (e.g, regression) are not participant-specific.
 We think that this observation is mitigated in the context of mixed-effects models (as used in our current study), which incorporate by-participant random intercepts and random slopes.} Furthermore, in some topic areas in which individual differences have not featured as prominently, the data have revealed a non-trivial role of individual differences (Kos et al., 2012; Montero-Melis, 2021).
@@
 Some previous studies have found that the effect of vocabulary size was moderated by variables related to general intelligence, such as processing speed (Ratcliff et al., 2010; Yap et al., 2012).
-Owing to those findings, and the recommendations from other studies (James et al., 2018; Pexman \& Yap, 2018; Sassenhagen \& Alday, 2016), the present studies included covariates of vocabulary size, where available.These covariates were measures of intelligence that were not vocabulary-based, namely, attentional control in Study 1 and information uptake in Study 2 (such a variable was not available for Study 3).
+Owing to those findings, and the recommendations from other studies (James et al., 2018; Pexman \& Yap, 2018; Sassenhagen \& Alday, 2016), the present studies included covariates of vocabulary size, where available.
+These covariates were measures of intelligence that were not vocabulary-based, namely, attentional control in Study 1 and information uptake in Study 2 (such a variable was not available for Study 3).
 
@@
 
-*** to be edited *** Semantic or lexical information in words (e.g., De Deyne et al., 2021; Lam et al., 2015; Lund et al., 1995; Lund \& Burgess, 1996; Lynott et al., 2020; Mandera et al., 2017; Pexman et al., 2017; Santos et al., 2011; Wingfield \& Connell, 2022)
+*** to be edited *** Semantic or lexical information in words (e.g., De Deyne et al., 2021; Lam et al., 2015; Lund et al., 1995; Lund \& Burgess, 1996; Lynott et al., 2020; Mandera et al., 2017; Petilli et al., 2021; Pexman et al., 2017; Santos et al., 2011; Wingfield \& Connell, 2022)
 
@@
 \item
-  \emph{Variables in this study:} degree of association between words, degree of vision-based information in single words
+  Variables in this study: language-based and vision-based information;
 \item
-  Covariates: lexical variables and word concreteness.
+  Covariates: lexical variables and word concreteness;
+
+  \begin{itemize}
   \item
-  Lexical variables: The lexical covariates were selected in each study out of the same 5 variables, which have been identified as important in previous research {[}Wingfield and Connell (2022); see \protect\hyperlink{general-statistical-analyses}{\underline{General statistical analysis}} for details{]}.
+    Lexical variables: The lexical covariates were selected in each study out of the same 5 variables, which have been identified as important in previous research (Wingfield \& Connell, 2022; see \protect\hyperlink{general-statistical-analyses}{\underline{General statistical analysis}} for details).
   \item
@@
 Furthermore, it has been recently suggested that the effect of word concreteness does not stem from perceptual simulation, but instead from modality-independent properties of words (Bottini et al., 2021).
+  \end{itemize}
 \end{itemize}
@@
 We use the formula of the `stimulus-onset asynchrony' (SOA) in this paper, instead of the `interstimulus interval' (ISI), as the SOA has been more commonly used in previous papers (e.g., Hutchison et al., 2013; Pecher et al., 1998; Petilli et al., 2021; Yap et al., 2017).
-The difference between these formulas is that the ISI does not count the presentation of the prime word (example equivalences between ISI and SOA are available in Lam et al.
-(2015), and in Figure 1A of Di Lollo et al.
-(2004)).
+The difference between these formulas is that the ISI does not count the presentation of the prime word Di Lollo et al.
+(2004).
 In the current study, the presentation of the prime word lasts 150 ms.
 Thus, the 200-ms SOA is equivalent to an ISI of 50 ms, and the 1,200-ms SOA corresponds to an ISI of 1,050 ms (Hutchison et al., 2013).
-The use of either formula in the analysis would not change our results, as we recoded the levels of the factor as -0.5 and +0.5, and then z-scored those, following the advice of Brauer and Curtin (2018).
+The use of either formula in the analysis would not change our results, as we recoded the levels of the factor as -0.5 and +0.5, and then \(z\)-scored those, following the advice of Brauer and Curtin (2018).
 In our analyses (\url{https://osf.io/ueryq}), we used the ISI formula as it was the one present in the data set of Hutchison et al.
@@
 
-The three levels are strongly intertwined, and studies have probed into more than one level at once: for instance, word level and individual level (Aujla, 2021; Lim et al., 2020; Pexman \& Yap, 2018; Yap et al., 2009), or word level and task level (Connell \& Lynott, 2013; Ostarek \& Huettig, 2019; Petilli et al., 2021).
+The three levels are strongly intertwined, and studies have probed into more than one level at once: for instance, word level and individual level (Aujla, 2021; Lim et al., 2020; Pexman \& Yap, 2018; Yap et al., 2009), or word level and task level (Al-Azary et al., 2022; Connell \& Lynott, 2013; Ostarek \& Huettig, 2019; Petilli et al., 2021).
 Thus, hypotheses are available regarding interactions across levels, as addressed below.
@@
 (2017) observed a larger semantic priming effect in higher-vocabulary participants from (Hutchinson \& Louwerse, 2013).
-The second hypothesis, in contrast, states that higher-vocabulary participants would be \emph{less} sensitive to linguistic features, thanks to a more automatic process.
+The second hypothesis, in contrast, states that higher-vocabulary participants would be \emph{less} sensitive to linguistic features, thanks to a more automatic process (Perfetti \& Hart, 2002).
 For instance, Yap et al.
@@
 
-Statistical power depends on the following factors: (1) sample size---comprising the number of participants, items, trials, etc.---, (2) effect size, (3) measurement variability and (4) number of comparisons being performed (Kumle et al., 2021).
+Statistical power depends on the following factors: (1) sample size---comprising the number of participants, items, trials, etc.---, (2) effect size, (3) measurement variability and (4) number of comparisons being performed.
 Out of these, sample size is the factor that can best be controlled by researchers (Kumle et al., 2021).
@@
 Insufficient statistical power lowers the reliability of effect sizes, and increases the likelihood of false positive results---i.e., Type I error---and of false negative results---i.e., Type II error (Gelman \& Carlin, 2014; Loken \& Gelman, 2017; Tversky \& Kahneman, 1971; von der Malsburg \& Angele, 2017).
-For instance, Vasishth and Gelman (2021) illustrate how, in low-powered studies, effect sizes associated with significant results tend to be overestimated (also see Vasishth et al., 2018).
-
-Over the past decade, replication studies and power analyses have uncovered insufficient sample sizes in psychology (Brysbaert, 2019; Lynott et al., 2014; Montero-Melis et al., 2017, 2022; Rodríguez-Ferreiro et al., 2020; Vasishth et al., 2018).
+For instance, Vasishth and Gelman (2021) illustrate how, in low-powered studies, effect sizes associated with significant results tend to be overestimated (also see Vasishth, Mertzen, et al., 2018).
+
+Over the past decade, replication studies and power analyses have uncovered insufficient sample sizes in psychology (Brysbaert, 2019; Lynott et al., 2014; Montero-Melis et al., 2017, 2022; Rodríguez-Ferreiro et al., 2020; Vasishth, Mertzen, et al., 2018).
 In the neighbouring field of neuroscience, Marek et al.
@@
 \hypertarget{general-statistical-analyses}{%
-\subsection{General method for statistical analyses}\label{general-statistical-analyses}}
+\subsection{General method for statistical analysis}\label{general-statistical-analyses}}
 
 The statistical analysis was designed to examine the unique contribution of each effect of interest.
-In all three studies, the dependent variable---response time (RT)---was z-scored around each participant's mean to curb the influence of each participant's baseline speed (Balota et al., 2007; Kumar et al., 2020; Lim et al., 2020; Pexman et al., 2017; Pexman \& Yap, 2018; Yap et al., 2012, 2017).
+In all three studies, the dependent variable---response time (RT)---was \(z\)-scored around each participant's mean to curb the influence of each participant's baseline speed (Balota et al., 2007; Kumar et al., 2020; Lim et al., 2020; Pexman et al., 2017; Pexman \& Yap, 2018; Yap et al., 2012, 2017).
 This was important because the size of experimental effects is known to increase with longer RTs (Faust et al., 1999).
@@
 The SOAs in Study 1 were recoded as follows: 150 ms = -0.5; 1,200 ms = 0.5.
-Finally, following Brauer and Curtin (2018), all predictors were z-scored (i.e., \(M \approx\) 0, \(SD \approx\) 1).
-
-Several covariates---or nuisance variables---were included, as detailed in each study, to allow a rigorous analysis of the effects of interest (Sassenhagen \& Alday, 2016).
+Finally, following Brauer and Curtin (2018), all predictors were \(z\)-scored (i.e., \(M \approx\) 0, \(SD \approx\) 1).
+
+Several covariates---or nuisance variables---were included in each study, to allow a rigorous analysis of the effects of interest (Sassenhagen \& Alday, 2016).
 Unlike the effects of interest, these covariates were not critical to the research question.
-They comprised lexical variables (e.g., word frequency) and participant-specific variables (e.g., attentional control).
-The lexical covariates were selected in every study out of the same 5 variables, which had been used as covariates in Wingfield and Connell (2022), and are widely used (e.g., Petilli et al., 2021).
+They comprised participant-specific variables (e.g., attentional control), lexical variables (e.g., word frequency) and word concreteness.
+
+The lexical covariates were selected in every study out of the same 5 variables, which had been used as covariates in Wingfield and Connell (2022; also see Petilli et al., 2021).
 They comprised: number of letters (i.e., orthographic length), word frequency, number of syllables (both the latter from Balota et al., 2007), orthographic Levenshtein distance (Yarkoni et al., 2008) and phonological Levenshtein distance (Suárez et al., 2011).
@@
 The correlations and the selection models are available in \protect\hyperlink{appendix-A-lexical-covariates}{\underline{Appendix A}}.
+
+Word concreteness was included due to its correlation with visual strength, as shown in each study below.
+A recent study suggested that the psycholinguistic import of concreteness is fundamentally lexical, and does not involve perceptual simulation (Bottini et al., 2021).
+
+The participant-specific covariates were measures akin to fluid intelligence, and were included due to their relationship with vocabulary size, as previous studies have expressed the desirability of including such covariates (James et al., 2018; Pexman \& Yap, 2018).
+As described in each study, these covariates were used in Studies 1 and 2, but not in Study 3, as such a variable was not available.
 
@@
 Therefore, linear mixed-effects models were implemented.
-These models included a maximal random-effects structure, with by-participant and by-word random intercepts, and the appropriate random slopes for all effects of interest (Barr et al., 2013).
-In the case of interactions, random slopes were included only when the variables interacting varied within the same unit (Brauer \& Curtin, 2018)---e.g., an interaction of two variables varying within participants (only present in Study 1).
-Owing to convergence warnings, random slopes for controlled covariates were removed, inspired by Remedy 11 from Brauer and Curtin (2018).
-Exceptionally, in the Bayesian models for the lexical decision study, the random slopes for the covariates did not have to be removed.
-
-To avoid inflating the Type I error rate (false positives), the random slopes for the effects of interest were never removed (see Table 17 in Brauer \& Curtin, 2018; for an example of this approach, see Diaz et al., 2021).
-This approach provides a better protection against false positives (Barr et al., 2013; Brauer \& Curtin, 2018; Singmann \& Kellen, 2019) than the practice of removing random slopes when they do not significantly improve the fit (e.g., Bernabeu et al., 2017; Pexman \& Yap, 2018; see Bates et al., 2015).
+These models included a maximal random-effects structure, with by-participant and by-item random intercepts, and the appropriate random slopes for all effects of interest (Barr et al., 2013).
+In the semantic priming study, the items were prime-target pairs, whereas in the semantic decision and lexical decision studies, the items were individual words.
+In the case of interactions, random slopes were included only when the interacting variables varied within the same unit (Brauer \& Curtin, 2018)---e.g., an interaction of two variables varying within participants (only present in Study 1).
+Where required due to convergence warnings, random slopes for covariates were removed, as inspired by Remedy 11 from Brauer and Curtin (2018).
+In this regard, whereas Brauer and Curtin (2018) contemplate the removal of random slopes for covariates only when the covariates are not interacting with any effects of interest, we removed random slopes for covariates even if they interacted with effects of interest because these interactions were covariates themselves (covariates are indicated in the results tables).
+
+To avoid inflating the Type I error rate (false positives), the random slopes for the effects of interest (indicated by non-shaded rows in the results tables below) were never removed (see Table 17 in Brauer \& Curtin, 2018; for an example of this approach, see Diaz et al., 2021).
+This approach arguably provides a better protection against false positives (Barr et al., 2013; Brauer \& Curtin, 2018; Singmann \& Kellen, 2019) than the practice of removing random slopes when they do not significantly improve the fit (Baayen et al., 2008; Bates et al., 2015; e.g., Bernabeu et al., 2017; Pexman \& Yap, 2018; but also see Matuschek et al., 2017).
 
@@
 
-\emph{P} values were calculated with the Kenward-Roger approximation for degrees of freedom (Luke, 2017), using the `lmerTest' package, Version 3.1-3 (Kuznetsova et al., 2017).
+\(P\) values were calculated using the Kenward-Roger approximation for degrees of freedom (Luke, 2017), in the R package `lmerTest', Version 3.1-3 (Kuznetsova et al., 2017).
 The latter package in turn used `lme4', Version 1.1-26 (Bates et al., 2015; Bates et al., 2021).
+To facilitate the convergence of the models, the maximum number of iterations was set to 1 million.
 Diagnostics regarding convergence and normality are provided in \protect\hyperlink{appendix-B-frequentist-analysis-diagnostics}{\underline{Appendix B}}.
+Effects that were non-significant or very small are best interpreted by considering their 95\% confidence intervals (Cumming, 2014), which are shown in the results tables as well as in plots.
 
@@
 
-In addition to the frequentist analysis, a Bayesian analysis was performed for two purposes: firstly, to enhance the interpretation of the smaller effects (which were identified as low-powered), and secondly, to complement the estimates obtained in the frequentist analysis.
+A Bayesian analysis was performed to complement the estimates that had been obtained in the frequentist analysis.
+Whereas the focus of the frequentist analysis had been hypothesis testing, using \(p\) values, the purpose of the Bayesian analysis was parameter estimation.
+Accordingly, we estimated the posterior distribution of every effect, without calculating Bayes factors (for other examples of this approach, see Milek et al., 2018; Pregla et al., 2021; Rodríguez-Ferreiro et al., 2020; for comparisons between estimation and hypothesis testing, see Cumming, 2014; Kruschke \& Liddell, 2018; Rouder et al., 2018; Schmalz et al., 2021; Tendeiro \& Kiers, 2019, in press; van Ravenzwaaij \& Wagenmakers, 2021).
+In the estimation approach, the estimates are interpreted by considering the position of their credible intervals in relation to the expected effect size.
+That is, the closer an interval is to an effect size of 0, the smaller the effect of that predictor.
+For instance, an interval that is symmetrically centred on 0 indicates a very small effect, whereas---in comparison---an interval that does not include 0 at all indicates a far larger effect.
+
+This analysis served two purposes: firstly, to ascertain the interpretation of the smaller effects---which were identified as unreliable in the power analyses---, and secondly, to complement the estimates obtained in the frequentist analysis.
 The latter purpose was pertinent because the frequentist models presented convergence warnings---even though it must be noted that a previous study found that frequentist and Bayesian estimates were similar despite convergence warnings appearing in the frequentist analysis (Rodríguez-Ferreiro et al., 2020).
 Furthermore, the complementary analysis was pertinent because the frequentist models presented residual errors that deviated from normality---even though mixed-effects models are fairly robust to such a deviation (Knief \& Forstmeier, 2021; Schielzeth et al., 2020).
-Owing to these precedents, we expected to find broadly similar estimates in the two approaches.
-
-Each frequentist model in the three studies has a Bayesian counterpart, with the exception of a sub-analysis performed in the first study (semantic priming), which included `visual similarity' as a predictor.
-Due to time constraints, this analysis did not include a Bayesian model.
-Furthermore, it must be noted that the Bayesian models in the semantic decision study did not produce valid results.
-Therefore, the estimates produced by these models are not shown in the main text, but they are instead in \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}.
-
-Just as the frequentist estimates include 95\% confidence intervals (CI), the Bayesian estimates include 95\% credible intervals (CrI).
-These two types differ at a theoretical level, in that frequentist statistics are designed for the long run of testing, whereas Bayesian statistics are specific to each study (Schoot et al., 2021; Vasishth et al., 2018).
-
-The random effects included in these models were largely the same as those included in the frequentist models.
-The only exception regarded the lexical decision models.
-In the frequentist models for lexical decision, the covariates did not carry random slopes due to the presence of convergence warnings (see Remedy 11 in Brauer \& Curtin, 2018), whereas in the Bayesian analysis, covariates did carry random slopes because the models converged.
-
-This Bayesian analysis was not aimed at hypothesis testing.
-Instead, it was designed to complement and verify the estimates that had been obtained in the frequentist analysis.
-Accordingly, we estimated the posterior distribution of every effect, without calculating Bayes factors (for examples of this approach, see Milek et al., 2018; Rodríguez-Ferreiro et al., 2020; for comparisons between estimation and hypothesis testing, see Cumming, 2014; Kruschke \& Liddell, 2018; Rouder et al., 2018; Schmalz et al., 2021; Tendeiro \& Kiers, 2019, in press; van Ravenzwaaij \& Wagenmakers, 2021).
-In the estimation approach, the estimates are interpreted by considering the position of their credible intervals in relation to the predicted value of RT (\(z\)).
-That is, the closer an interval is to a value of 0 on the predicted RT (\(z\)), the smaller the effect of that predictor.
-For instance, an interval that is symmetrically centred on 0 indicates a very small effect, whereas---in comparison---an interval that does not include 0 at all indicates a far larger effect.
+Owing to these precedents, we expected to find broadly similar estimates in the frequentist and the Bayesian analyses.
+Each frequentist model in the three studies has a Bayesian counterpart, with the exception of a sub-analysis performed in the first study (semantic priming), which included `vision-based similarity' as a predictor.
 
@@
 
-The priors were established by inspecting the effect sizes obtained in previous studies as well as the effect sizes obtained in our frequentist analyses of the present studies, reported below.
-These sources revealed highly-similar ranges.
-The previous studies that were considered were selected because they implemented experimental experimental paradigms and analytical procedures similar to those used in the current studies.
-The paradigms were lexical decision, semantic decision or semantic priming with a lexical decision task.
+The priors were established by inspecting the effect sizes obtained in previous studies as well as the effect sizes obtained in our frequentist analyses of Studies 1, 2 and 3.
+
+The previous studies that were considered for determining the priors were selected because they had used experimental paradigms and analytical procedures similar to those used in the current studies.
+Specifically, the paradigms were (I) semantic priming with a lexical decision task---as in Study 1---, (II) semantic decision---as in Study 2---,and (III) lexical decision---as in Study 3.
 The analytical procedures consisted of the z-scoring of the dependent and the independent variables.
-Two studies matched these characteristics: Lim et al.
+We found two studies that matched these characteristics: Lim et al.
 (2020) (see Table 5 therein) and Pexman and Yap (2018) (see Tables 6 and 7 therein).
 These studies and the frequentist analyses reported below yielded effect sizes smaller than ±0.30.
-The bounds of this range were determined by the results from Pexman and Yap (2018), who found a word-concreteness effect of \(\upbeta\) = 0.41 in the concrete-words analysis, and an effect of \(\upbeta\) = 0.20 in the abstract-words analysis.
+The bounds of this range were determined by the results from Pexman and Yap (2018), who found a word concreteness effect of \(\upbeta\) = 0.41 in the concrete-words analysis, and an effect of \(\upbeta\) = 0.20 in the abstract-words analysis.
 Since we did not separate abstract from concrete words, we averaged the former values, and set -0.30 as the lower bound, and 0.30 as the upper bound.
-
-The sources used to determine the effect size range also revealed that some effects consistently presented a negative direction, whereas some other effects were consistently positive.
-We only incorporated the direction of effects into the priors of those variables that had produced large effects with consistent directions in previous studies and in our frequentist analyses.
-These variables were: word frequency---with a negative direction, as higher word frequency leads to shorter RTs (Brysbaert et al., 2018; Brysbaert et al., 2016; Lim et al., 2020; Mendes \& Undorf, 2021; Pexman \& Yap, 2018)---, number of letters and number of syllables---both with positive directions (Barton et al., 2014; Beyersmann et al., 2020; Pexman \& Yap, 2018)---, and orthographic Levenshtein distance---with a positive direction (Cerni et al., 2016; Dijkstra et al., 2019; Kim et al., 2018; Yarkoni et al., 2008).
+This provided the basis for informative priors.
+Specifically, in these informative priors, 95\% of values would fall within the range {[}-0.30, 0.30{]}.
+
+Next, we considered the direction of effects.
+In the results of Lim et al.
+(2020) and Pexman and Yap (2018), and in our frequentist results, some effects consistently presented a negative direction---i.e., an inhibitory effect on RT---, whereas some other effects were consistently positive.
+We only incorporated the direction of effects into the priors in cases of large effects that had presented consistent directions in previous studies and in our frequentist analyses.
+These criteria were matched by the following variables: word frequency---with a negative direction, as higher word frequency leads to shorter RTs (Brysbaert et al., 2018; Brysbaert et al., 2016; Lim et al., 2020; Mendes \& Undorf, 2021; Pexman \& Yap, 2018)---, number of letters and number of syllables---both with positive directions (Barton et al., 2014; Beyersmann et al., 2020; Pexman \& Yap, 2018)---, and orthographic Levenshtein distance---with a positive direction (Cerni et al., 2016; Dijkstra et al., 2019; Kim et al., 2018; Yarkoni et al., 2008).
 We did not incorporate information about the direction of the word concreteness effect as this effect can follow different directions in abstract and concrete words (Pexman \& Yap, 2018), and we analysed both sets of words together.
 Last, it is noteworthy that some previous studies have integrated effect direction in some priors (e.g., Stone et al., 2021), but most have not (e.g., Pregla et al., 2021; Rodríguez-Ferreiro et al., 2020; Stone et al., 2020).
-
-\hypertarget{distributions-and-prior-predictive-checks}{%
-\subparagraph{Distributions and prior predictive checks}\label{distributions-and-prior-predictive-checks}}
+In conclusion, the four predictors that had directional priors were covariates (also known as nuisance variables).
+All the other predictors had priors centred on 0.
+
+These priors were used on the fixed effects and on the corresponding standard deviation parameters.
+The correlation among the random effects had a weakly-informative prior, LKJ(2) (Lewandowski et al., 2009), which assumes that high correlations among the random effects are rare (also used in Rodríguez-Ferreiro et al., 2020; Stone et al., 2021; Stone et al., 2020; Vasishth, Nicenboim, et al., 2018).
+
+\hypertarget{prior-distributions-and-prior-predictive-checks}{%
+\subparagraph{Prior distributions and prior predictive checks}\label{prior-distributions-and-prior-predictive-checks}}
+
+We aimed to perform prior sensitivity analyses of our results.
+Prior sensitivity analyses are checks that assess the influence of different priors on the results (Lee \& Wagenmakers, 2014; Schoot et al., 2021; Stone et al., 2020).
+The range of priors established for this purpose varied in their standard deviations.
+Their means were the same, most being centred on 0, as explained above.
 
@@
 (2020) used the following priors: \(Normal\)(0, 0.1), \(Normal\)(0, 0.3) and \(Normal\)(0, 1).
-The range of standard deviations we used---i.e., 0.1, 0.2 and 0.3---was narrower than those of previous studies because our dependent variable and our predictors were z-scored, resulting in small estimates and small \(SD\)s (see Lim et al., 2020; Pexman \& Yap, 2018).
+The range of standard deviations we used---i.e., 0.1, 0.2 and 0.3---was narrower than those of previous studies because our dependent variable and our predictors were \(z\)-scored, resulting in small estimates and small \(SD\)s (see Lim et al., 2020; Pexman \& Yap, 2018).
 
@@
 
-\caption{Priors used in the three studies.
-The green vertical rectangle shows the range of plausible effect sizes based on relevant previous studies and on our frequentist analyses.}\label{fig:bayesian-priors}
+\caption{Priors used in the three studies. The green vertical rectangle shows the range of plausible effect sizes based on previous studies and on our frequentist analyses.}\label{fig:bayesian-priors}
 \end{figure}
@@
 Prior predictive checks revealed that the priors were adequate, and that the ex-Gaussian distribution was more appropriate than the Gaussian one, converging with Rodríguez-Ferreiro et al.
-(2020) (see the corresponding plots in \protect\hyperlink{appendix-D-interaction-plots}{\underline{Appendix D}}).
+(2020) (see the corresponding plots in \protect\hyperlink{appendix-C-Bayesian-analysis-diagnostics}{\underline{Appendix C}}).
 Therefore, the ex-Gaussian distribution was used in the final models.
@@
 
-The priors were used in the main analyses within separate models.
-In other words, in each model, all priors had the same degree of informativeness (for similar approaches, see Pregla et al., 2021; Rodríguez-Ferreiro et al., 2020; Stone et al., 2021; Stone et al., 2020).
+In the main analyses, the informative, weakly-informative and diffuse priors were used in separate models.
+In other words, in each model, all priors had the same degree of informativeness (as done in Pregla et al., 2021; Rodríguez-Ferreiro et al., 2020; Stone et al., 2021; Stone et al., 2020).
 In this way, a prior sensitivity analysis was performed to acknowledge the likely influence of the priors on the posterior distributions---that is, on the results (Lee \& Wagenmakers, 2014; Schoot et al., 2021; Stone et al., 2020).
@@
 
-As a last diagnostic, posterior predictive checks were performed to assess the fit between the observed data and new data predicted by the posterior (Schoot et al., 2021).
+Posterior predictive checks were performed to assess the fit between the observed data and new data predicted by the posterior (Schoot et al., 2021).
 These checks are available in \protect\hyperlink{appendix-C-Bayesian-analysis-diagnostics}{\underline{Appendix C}}.
 
-\hypertarget{general-method-for-statistical-power-analyses}{%
-\subsection{General method for statistical power analyses}\label{general-method-for-statistical-power-analyses}}
+\hypertarget{convergence}{%
+\paragraph{Convergence}\label{convergence}}
+
+Where convergence was not reached in a model, as indicated by \(\widehat R\) \textgreater{} 1.01 (Schoot et al., 2021; Vehtari et al., 2021), the number of iterations was increased.
+Furthermore, where necessary, the random slopes for covariates were removed (Brauer \& Curtin, 2018).
+The resulting random effects in these models were largely the same as those present in the frequentist models.
+The only exception regarded the lexical decision models.
+In the frequentist model for lexical decision, the random slopes for covariates were removed due to convergence warnings, whereas in the Bayesian analysis, these random slopes did not have to be removed as the models converged.
+
+The Bayesian models in the semantic decision study could not be made to converge, and the results were not valid.
+Therefore, those estimates are not shown in the main text but in \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}.
+
+\hypertarget{general-method-for-statistical-power-analysis}{%
+\subsection{General method for statistical power analysis}\label{general-method-for-statistical-power-analysis}}
 
@@
 Thus, each of the power curves we present assume the same number of words that existed in each of our studies (these numbers are detailed in each study below).
-\emph{P} values were calculated using the Satterthwaite approximation for degrees of freedom, which is faster than Kenward-Roger but similarly accurate (Luke, 2017).
+\(P\) values were calculated using the Satterthwaite approximation for degrees of freedom (Luke, 2017).
 
@@
 In contrast, some authors have opted to reduce the previous effect sizes to account for factors that can influence the effect size of the planned study.
-First, publication bias and low-powered studies cause published effect sizes to be inflated (Brysbaert, 2019; Loken \& Gelman, 2017; Open Science Collaboration, 2015; Vasishth et al., 2018; Vasishth \& Gelman, 2021).
+First, publication bias and low-powered studies cause published effect sizes to be inflated (Brysbaert, 2019; Loken \& Gelman, 2017; Open Science Collaboration, 2015; Vasishth, Mertzen, et al., 2018; Vasishth \& Gelman, 2021).
 Second, there might be differences between the studies used in the power analysis and the study to be conducted.
@@
 (2021; both our measure and theirs originated from Mandera et al., 2017).
-In contrast, in the domain of vision, the operationalisation of visual-strength difference in our study---based one variable from (Lynott et al., 2020)---was simpler than that of Petilli et al.'s visual similarity---which involved convolutional neural networks.
-As a counterpoint, Petilli et al.'s measure was superior in that it was independent from human ratings, thus precluding the problem of circularity between the independent and the dependent variables.
-At \protect\hyperlink{comparing-two-measures-of-vision-based-information}{\underline{the end of the Results section}}, we compare the performance of these two measures.
+In contrast, our predictors in the domain of vision differed.
+Whereas Petilli et al.~used a human-independent measure based on images from the Internet (see description above), we drew on visual strength---from the modality ratings of Lynott et al.
+(2020)---and calculated the difference in visual strength between the prime and the target word in each trial.\footnote{These measures are compared at \protect\hyperlink{comparing-two-measures-of-vision-based-information}{\underline{the end of the Results section}}.}
 
@@
 \item
-  Z-scored vocabulary size {[}\texttt{z\_vocabulary\_size}; calculated from average of \texttt{vocaba}, \texttt{vocabb} and \texttt{vocabc} in Hutchison et al.
+  \(Z\)-scored vocabulary size {[}\texttt{z\_vocabulary\_size}; calculated from average of \texttt{vocaba}, \texttt{vocabb} and \texttt{vocabc} in Hutchison et al.
 (2013){]}.
@@
 \item
-  Z-scored, recoded participant's gender {[}\texttt{z\_recoded\_participant\_gender}; calculated from \texttt{gender} in Hutchison et al. (2013){]}
+  \(Z\)-scored, recoded participants' gender {[}\texttt{z\_recoded\_participant\_gender}; calculated from \texttt{gender} in Hutchison et al. (2013){]}
 \item
-  Z-scored language-based similarity between prime and target words {[}\texttt{z\_cosine\_similarity}{]}.
+  \(Z\)-scored language-based similarity between prime and target words {[}\texttt{z\_cosine\_similarity}{]}.
 This measure was calculated using a semantic space from Mandera et al.
@@
 \item
-  Z-scored vision-based information in words {[}\texttt{z\_visual\_rating}; calculated from \texttt{Visual.mean} in Lynott et al. (2020){]}
+  \(Z\)-scored vision-based information in words {[}\texttt{z\_visual\_rating\_diff}; calculated from \texttt{Visual.mean} in Lynott et al. (2020){]}
 \item
-  Z-scored, recoded SOA {[}\texttt{z\_recoded\_interstimulus\_interval}; calculated from \texttt{isi} in Hutchison et al. (2013){]}
+  \(Z\)-scored, recoded SOA {[}\texttt{z\_recoded\_interstimulus\_interval}; calculated from \texttt{isi} in Hutchison et al. (2013){]}
 \end{itemize}
 
-The final data set contained 496 participants, 5,943 prime-target pairs, and a total of 345,666 RTs.
+The final data set contained 496 participants, 5,943 prime-target pairs, and 345,666 RTs.
 On average, there were 697 prime-target pairs per participant (\(SD\) = 33.34), and conversely, 58 participants per prime-target pair (\(SD\) = 4.25).
@@
 \item
-  Lexical (see \protect\hyperlink{appendix-A-lexical-covariates}{\underline{Appendix A}}): z-scored word frequency and orthographic Levenshtein distance (Balota et al., 2007)
+  Lexical (see \protect\hyperlink{appendix-A-lexical-covariates}{\underline{Appendix A}}): \(z\)-scored word frequency and orthographic Levenshtein distance (Balota et al., 2007)
 \item
-  Semantic: z-scored word concreteness (Brysbaert et al., 2014), used as a covariate of visual rating.
+  Semantic: \(z\)-scored word concreteness (Brysbaert et al., 2014), used as a covariate of visual rating.
 \item
-  Individual differences: z-scored attentional control (Hutchison et al., 2013).
-This covariate is related to vocabulary size (Ratcliff et al., 2010), and previous studies have pointed out the desirability of including these kinds of covariates in analyses (James et al., 2018; Pexman \& Yap, 2018).
-Attentional control was operationalised as the average score across three attention-demanding tasks: namely, operation span, Stroop, antisaccade.
+  Individual differences: \(z\)-scored attentional control (Hutchison et al., 2013).
+This covariate is related to vocabulary size (Ratcliff et al., 2010), and previous studies have expressed the desirability of including such covariates (James et al., 2018; Pexman \& Yap, 2018).
+Attentional control was operationalised as the average score across three tasks of Hutchison et al.
+(2013)---namely, operation span, Stroop and antisaccade.
 \end{itemize}
@@
 The model presented convergence warnings.
-To avoid removing important random slopes, which could increase the Type I error (Brauer \& Curtin, 2018; Singmann \& Kellen, 2019), we examined the model after refitting it using seven optimization algorithms through the `allFit' function of the `lme4' package (Bates et al., 2021).
-The results showed that all optimizers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential (Bates et al., 2021) (see \protect\hyperlink{appendix-B-frequentist-analysis-diagnostics}{\underline{Appendix B}}).
+To avoid removing important random slopes, which could increase the Type I error (Brauer \& Curtin, 2018; Singmann \& Kellen, 2019), we examined the model after refitting it using seven optimization algorithms through the `allFit' function of the R package `lme4' (Bates et al., 2021).
+The results showed that all optimizers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential (Bates et al., 2021; see \protect\hyperlink{appendix-B-frequentist-analysis-diagnostics}{\underline{Appendix B}}).
 
@@
 
-Three Bayesian models were run that were respectively characterised by informative, weakly-informative and diffuse priors.
+Three Bayesian models were run that were respectively characterised by informative, weakly-informative and diffuse priors (note that the weakly-informative prior model has not yet finished running).
 In each model, 16 chains were used.
@@
 
-The maximum \(\widehat R\) value for the fixed effects across the three models was 1.00, suggesting that these parameters had converged (Schoot et al., 2021; Vehtari et al., 2021).
+The maximum \(\widehat R\) value for the fixed effects in both models was 1.00, suggesting that these parameters had converged (Schoot et al., 2021; Vehtari et al., 2021).
 In contrast, the maximum \(\widehat R\) value for the random effects was 1.13, exceeding the 1.01 threshold (Vehtari et al., 2021).
@@
 
-Table \ref{tab:semanticpriming-frequentist-model} presents the results of the mixed-effects model.
-
-\begin{table}[!h]
+Table \ref{tab:semanticpriming-frequentist-model} presents the results of the frequentist model.
+The fixed effects explained 4.22\% of the variance, and the random effects 11.01\% (Nakagawa et al., 2017).
+It is to be expected that random effects explain more variance, as they involve a far larger number of coefficients for each effect.
+For instance, the by-item random slopes (specifically, by prime-target pair) for a single individual-level variable (e.g., vocabulary size) involve as many coefficients as the number of items.
+Conversely, the by-participant random slopes for a single item-level variable (e.g., language-based similarity) involve as many coefficients as the number of participants.
+In contrast, each fixed effect involves 1 coefficient only.
+
+\begin{table}[H]
 
@@
 \item \textit{Note}.
-$\upbeta$ = Estimate based on z-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CI = confidence interval.
+$\upbeta$ = Estimate based on $z$-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CI = confidence interval.
 Shaded rows contain covariates.
@@
 
-The fixed effects of this model explained 4.22\% of the variance, and the random effects explained 11.01\% (Nakagawa et al., 2017).
-It is to be expected that random effects explain more variance, as they involve a far larger number of coefficients for each effect.
-For instance, the by-word random slopes for a single individual-level variable (e.g., vocabulary size) involve as many coefficients as the number of words.
-Similarly, the by-participant random slopes for a single word-level variable (e.g., language-based similarity) involve as many coefficients as the number of participants.
-In contrast, a fixed effect involves 1 coefficient only.
+Figure \ref{fig:semanticpriming-frequentist-bayesian-plot-informativepriors-exgaussian} displays the frequentist estimates alongside the Bayesian estimates.
+The latter are from the informative prior model.
+The estimates of the diffuse prior model were virtually identical to these (see \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}).
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_bayesian_plots/plots/semanticpriming_frequentist_bayesian_plot_informativepriors_exgaussian}
+
+}
+
+\caption{Estimates from the frequentist analysis (in red) and from the Bayesian analysis (in blue) for the semantic priming study.
+The frequentist means (represented by points) are flanked by 95\% confidence intervals.
+The Bayesian means (represented by vertical lines) are flanked by 95\% credible intervals, in light blue (in some cases, the interval is covered up by the bar of the mean).}\label{fig:semanticpriming-frequentist-bayesian-plot-informativepriors-exgaussian}
+\end{figure}
 
@@
 
-Figure \ref{fig:semanticpriming-interactions-with-vocabulary-size}-b presents the interaction between vocabulary size and vision-based similarity.
-Albeit a non-significant interaction, it is noteworthy that the effect of vision-based information is larger in lower-vocabulary participants.
+Figure \ref{fig:semanticpriming-interactions-with-vocabulary-size}-b presents the interaction between vocabulary size and visual-strength difference.\footnote{All interaction plots across the three studies are based on the frequentist models.} Albeit a non-significant interaction, it is noteworthy that the effect of visual-strength difference is larger in lower-vocabulary participants.
 
@@
 
-\caption{Interactions of vocabulary size with language- and vision-based similarity.
-Vocabulary size is constrained to deciles, whereas in the statistical analysis it contained more values within the current range.
-\emph{n} = number of participants contained between decile values.}\label{fig:semanticpriming-interactions-with-vocabulary-size}
+\caption{Interactions of vocabulary size with language-based similarity and visual-strength difference.
+Vocabulary size is constrained to deciles (ten sections) in this plot, whereas in the statistical analysis it contained more values within the current range.
+\emph{n} = number of participants contained between deciles.}\label{fig:semanticpriming-interactions-with-vocabulary-size}
 \end{figure}
@@
 
-\caption{Interactions of SOA with language-based similarity and visual strength.
-SOA was analysed using z-scores, but for clarity, the variable is shown in its simpler form here.}\label{fig:semanticpriming-interactions-with-SOA}
+\caption{Interactions of stimulus-onset asynchrony (SOA) with language-based similarity and visual strength.
+SOA was analysed using $z$-scores, but for clarity, the variable is shown in its basic form here.}\label{fig:semanticpriming-interactions-with-SOA}
+\end{figure}
+
+Figure \ref{fig:semanticpriming-interactions-with-gender} shows the interactions of gender with language-based similarity and visual-strength difference, albeit non-significant.\footnote{Plots of other interactions are available in \protect\hyperlink{appendix-D-interaction-plots}{\underline{Appendix D}}.}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-gender}
+
+}
+
+\caption{Interactions with gender in the semantic priming study.
+Gender was analysed using $z$-scores, but for clarity, the variable is shown in its basic form here.}\label{fig:semanticpriming-interactions-with-gender}
 \end{figure}
@@
 
-The interaction in Figure \ref{fig:semanticpriming-interactions-with-vocabulary-size} is patent in all deciles of vocabulary size but most notably in the participants who lie more than 1 standard deviation away from the mean.
+The interaction shown in Figure \ref{fig:semanticpriming-interactions-with-vocabulary-size} was patent in all deciles of vocabulary size but most notably in the participants who lie more than 1 standard deviation away from the mean.
 Outliers in individual differences have played important roles in other areas of cognition as well, such as in the domains of aphantasia and hyperphantasia---traits characterised, respectively, by a diminished and an extraordinary ability to mentally visualise objects (Milton et al., 2021; Zeman et al., 2020).
-Furthermore, if we consider the difficulty of detecting effects involving individual differences (Diaz et al., 2021; Hedge et al., 2018; Rodríguez-Ferreiro et al., 2020), and the limited representativeness of most participant samples (Henrich et al., 2010), it seems recommendable to examine more varied samples in future studies, where possible.
-
-\hypertarget{visualising-the-estimates}{%
-\subsubsection{Visualising the estimates}\label{visualising-the-estimates}}
-
-Figure \ref{fig:semanticpriming-frequentist-bayesian-plot-informativepriors-exgaussian} presents the posterior distribution of each effect, based on the informative prior model (for the models with the other priors, see \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}).
-The frequentist estimates are also shown to facilitate the comparison with them.
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_bayesian_plots/plots/semanticpriming_frequentist_bayesian_plot_informativepriors_exgaussian}
-
-}
-
-\caption{Estimates from the frequentist analysis (in red) and from the Bayesian analysis (in blue) for the semantic priming study.
-The frequentist means (represented by points) are flanked by 95\% confidence intervals.
-The Bayesian means (represented by vertical lines) are flanked by 95\% credible intervals, in light blue (in some cases, the interval is covered up by the bar of the mean).}\label{fig:semanticpriming-frequentist-bayesian-plot-informativepriors-exgaussian}
-\end{figure}
+Furthermore, if we consider the difficulty of detecting effects involving individual differences (Diaz et al., 2021; Hedge et al., 2018; Rodríguez-Ferreiro et al., 2020), and the limited representativeness of most samples of participants (Henrich et al., 2010), it may be fruitful to study more varied samples, where possible.
 
@@
 We created a subset of our data set in which we ensured that all the trials contained data from all the relevant variables---i.e., from all the existing variables and from the newly-added visual similarity from Petilli et al.~This subsetting resulted in the loss of 83\% of trials, owing to the strict selection criteria applied by Petilli et al.~in the creation of the visual-similarity measure (e.g., both the target and the prime word had to be associated to at least 100 pictures in ImageNet).
-As a result, our data set in this analysis contained 496 participants, 1,091 prime-target pairs, and a total of 254,140 RTs.
+As a result, our data set in this analysis contained 496 participants, 1,091 prime-target pairs, and 254,140 RTs.
 On average, there were 128 prime-target pairs per participant (\(SD\) = 10.37), and conversely, 58 participants per prime-target pair (\(SD\) = 4.90).
@@
 To avoid removing important random slopes, which could increase the Type I error (Brauer \& Curtin, 2018; Singmann \& Kellen, 2019), we examined the model after refitting it using seven optimization algorithms through the `allFit' function of the `lme4' package (Bates et al., 2021).
-The results showed that all optimizers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential {[}Bates et al.
-(2021); see \protect\hyperlink{appendix-B-frequentist-analysis-diagnostics}{\underline{Appendix B}}{]}.
+The results showed that all optimizers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential (Bates et al., 2021; see \protect\hyperlink{appendix-B-frequentist-analysis-diagnostics}{\underline{Appendix B}}).
 
@@
 
-Table \ref{tab:semanticpriming-with-visualsimilarity-frequentist-model} presents the results of the mixed-effects model.
+Table \ref{tab:semanticpriming-with-visualsimilarity-frequentist-model} presents the results of the frequentist model.
 Due to space, the covariates are shown in Table \ref{tab:semanticpriming-with-visualsimilarity-frequentist-model-covariates}.
-
-\begin{table}[!h]
+The fixed effects explained 3.53\% of the variance, and the random effects 18.47\% (Nakagawa et al., 2017; for an explanation of this difference, see \protect\hyperlink{semanticpriming-results}{\underline{above}}).
+Figure \ref{fig:semanticpriming-with-visualsimilarity-confidence-intervals-plot} displays the estimates for the effects of interest.
+
+\begin{table}[H]
 
@@
 \item \textit{Note}.
-$\upbeta$ = Estimate based on z-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CI = confidence interval.
+$\upbeta$ = Estimate based on $z$-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CI = confidence interval.
 Covariates shown in next table due to space.
@@
 
-\begin{table}[!h]
+\begin{table}[H]
 
@@
 \item \textit{Note}.
-$\upbeta$ = Estimate based on z-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CI = confidence interval.
+$\upbeta$ = Estimate based on $z$-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CI = confidence interval.
 Some interactions are split over two lines, with the \linebreak \phantom{.}second line indented.
@@
 
-The fixed effects of this model explained 3.53\% of the variance, and the random effects explained 18.47\% {[}Nakagawa et al.
-(2017); for background on why random effects explain more variance, see \protect\hyperlink{semanticpriming-results}{Results in Study 1}{]}.
-
-Figure \ref{fig:semanticpriming-with-visualsimilarity-confidence-intervals-plot} presents the means and 95\% confidence intervals for the effects of interest.
-
 \begin{figure}
@@
 
-{\centering \includegraphics[width=0.9\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/power_analysis/plots/semanticpriming_powercurve_plots_4_5_6_7_8_9}
+{\centering \includegraphics[width=0.92\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/power_analysis/plots/semanticpriming_powercurve_plots_4_5_6_7_8_9}
 
@@
 (2017) using language-based variables that are more related to the language system than to the visual system.
-The authors found that the variables that best explained RTs were word co-occurrence measures.
-Specifically, the measures corresponded to the distance from each stimulus word to two labels that were central to the task, namely, the words `abstract' and `concrete'.
+The task used by Pexman et al.~had been semantic decision, in which participants assessed whether words were abstract or concrete.
+Wingfield and Connell found that the variables that best explained RTs were word co-occurrence measures.
+Specifically, one of these variables was the correlation distance between each stimulus word and the word `abstract'.
+The other variable was the correlation distance between each stimulus word and the word `concrete'.
 Wingfield and Connell studied these distance measures in various forms, and found that cosine and correlation distance yielded the best results.
-We used the correlation distance following the advice of (Kiela \& Bottou, 2014).
-Furthermore, we sought to avoid the collinearity between these variables (\(r\) = .99) and to facilitate the analysis of interactions with other variables.
-For this purpose, we created a difference score by subtracting distance to `abstract' from the distance to `concrete'.
-The resulting variable was practically equivalent to the distance to `abstract', as attested by its large correlation with word concreteness (\(r\) = 0.02).
-Last, it should be noted that this difference score may not be affected by the reduced sensitivity of other ones (see Rodríguez-Ferreiro et al., 2020), as this difference score did not entail an aggregation of data points over any third variables.
+We used the correlation distance, following the advice of Kiela and Bottou (2014) (see details below).
 
@@
 
-\begin{itemize}
-\item
-  Z-scored vocabulary size {[}\texttt{z\_vocabulary\_size}; calculated from \texttt{NAART} in Pexman et al.
+\hypertarget{vocabulary-size-1}{%
+\paragraph{Vocabulary size}\label{vocabulary-size-1}}
+
+{[}\texttt{z\_vocabulary\_size}; calculated from \texttt{NAART} in Pexman et al.
 (2017){]}.
@@
 This test was based on NAART35, a short version of the North American Adult Reading Test (Uttl, 2002).
-\item
-  Z-scored, recoded participant's gender {[}\texttt{z\_recoded\_participant\_gender}; calculated from \texttt{Gender} in Pexman and Yap (2018){]}
-\item
-  Z-scored distance to word `abstract': a distributional semantic distance measure obtained from Wingfield and Connell (2022) that reflects the correlation distance between each stimulus word and the word `abstract'.\footnote{Specifically, this measure is a difference score that merges both the distance to the word `abstract' and the distance to the word `concrete'.
-We drew on both variables because Wingfield and Connell (2022) found them to be similarly important.
-Yet, we had to create a difference score because these variables were highly correlated (\(r\) = .99), we created a difference score by subtracting the distance to `abstract' from the distance to `concrete'.
-The resulting difference score was practically equivalent to the distance to the word `abstract', as attested by its correlation with word concreteness (see Figure \ref{fig:semanticdecision-correlations}).
-Our difference score in practice The variable \texttt{Conditional\_probability\_BNC\_r5\_correlation\_abstract\_distance} was subtracted from \texttt{Conditional\_probability\_BNC\_r5\_correlation\_concrete\_distance}.}
-\item
-  Z-scored vision-based information in words {[}\texttt{z\_visual\_rating}; calculated from \texttt{Visual.mean} in Lynott et al. (2020){]}
-\end{itemize}
-
-The final data set contained 306 participants, 8,927 words, and a total of 246,432 RTs.
+
+\hypertarget{participants-gender}{%
+\paragraph{Participant's gender}\label{participants-gender}}
+
+{[}\texttt{z\_recoded\_participant\_gender}; calculated from \texttt{Gender} in Pexman and Yap (2018){]}
+
+\hypertarget{word-co-occurrence-1}{%
+\paragraph{Word co-occurrence}\label{word-co-occurrence-1}}
+
+The zero-order correlation between Wingfield and Connell's (2022) distance to `abstract' and distance to `concrete' was \(r\) = 0.98.
+To avoid the collinearity between these variables in the model (Dormann et al., 2013; Harrison et al., 2018), and to facilitate the analysis of interactions with other variables, we created a difference score by subtracting the distance to `abstract' from the distance to `concrete'.
+This new variable was named `word co-occurrence'.
+As Figure \ref{fig:semanticdecision-cooccurrence-correlations} demonstrates, the difference score captured the explanatory power of the two original variables, resulting in an increase of the correlation with word concreteness.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.58\linewidth]{manuscript_files/figure-latex/semanticdecision-cooccurrence-correlations-1}
+
+}
+
+\caption{Zero-order correlations among Wingfield and Connell's (2022) distances, the difference score (word co-occurrence) and word concreteness (Brysbaert et al., 2014).}\label{fig:semanticdecision-cooccurrence-correlations}
+\end{figure}
+
+\hypertarget{visual-strength}{%
+\paragraph{Visual strength}\label{visual-strength}}
+
+{[}\texttt{z\_visual\_rating}; calculated from \texttt{Visual.mean} in Lynott et al. (2020){]}
+
+The final data set contained 306 participants, 8,927 words, and 246,432 RTs.
 On average, there were 755 words per participant (\(SD\) = 42.05), and conversely, 26 participants per word (\(SD\) = 4.80).
@@
 \item
-  Lexical (see \protect\hyperlink{appendix-A-lexical-covariates}{\underline{Appendix A}}): z-scored word frequency and orthographic Levenshtein distance (Balota et al., 2007)
+  Lexical (see \protect\hyperlink{appendix-A-lexical-covariates}{\underline{Appendix A}}): \(z\)-scored word frequency and orthographic Levenshtein distance (Balota et al., 2007)
 \item
-  Semantic: z-scored word concreteness (Brysbaert et al., 2014).
+  Semantic: \(z\)-scored word concreteness (Brysbaert et al., 2014).
 This variable is used as a covariate of visual strength, and it is especially fundamental in the semantic decision task, in which participants judge whether words are concrete or abstract (for a more general consideration of concreteness, see Bottini et al., 2021).
@@
 \item
-  Individual differences: z-scored information uptake (Pexman \& Yap, 2018). This covariate is related to vocabulary size (Ratcliff et al., 2010; also see James et al., 2018; Pexman \& Yap, 2018).
+  Individual differences: \(z\)-scored information uptake (Pexman \& Yap, 2018). This covariate is related to vocabulary size (Ratcliff et al., 2010; also see James et al., 2018; Pexman \& Yap, 2018).
 \end{itemize}
@@
 Furthermore, the posterior predictive checks revealed major divergences between the observed data and the predicted outcome (see \protect\hyperlink{appendix-C-Bayesian-analysis-diagnostics}{\underline{Appendix C}}).
-Since the results were not valid, they are not shown in the main text but instead in \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}.
+Since the results were not valid, they are not shown in the main text but in \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}.
 
@@
 
-Table \ref{tab:semanticdecision-frequentist-model} presents the results of the mixed-effects model.
-
-\begin{table}[!h]
+Table \ref{tab:semanticdecision-frequentist-model} presents the results of the frequentist model.
+The fixed effects explained 4.11\% of the variance, and the random effects 17.48\% {[}Nakagawa et al.
+(2017); for an explanation of this difference, see \protect\hyperlink{semanticpriming-results}{\underline{Results of Study 1}}).
+Figure \ref{fig:semanticdecision-confidence-intervals-plot} displays these estimates.\footnote{Bayesian estimates not shown as they were not valid.
+They are nonetheless available in \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}.}
+
+\begin{table}[H]
 
@@
 \cellcolor{gray!6}{\hspace{1em}Word concreteness} & \cellcolor{gray!6}{-0.13} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[-0.14, -0.11]} & \cellcolor{gray!6}{-21.39} & \cellcolor{gray!6}{<.001}\\
-\hspace{1em}Distance to word 'abstract' $^{\text{b}}$ & -0.03 & 0.01 & {}[-0.04, -0.02] & -4.48 & <.001\\
+\hspace{1em}Word co-occurrence $^{\text{b}}$ & -0.03 & 0.01 & {}[-0.04, -0.02] & -4.48 & <.001\\
 \hspace{1em}Visual strength $^{\text{b}}$ & -0.02 & 0.01 & {}[-0.03, -0.01] & -2.91 & .004\\
@@
 \multicolumn{6}{l}{\textbf{Interactions}}\\
+\cellcolor{gray!6}{\hspace{1em}Word concreteness  $\times$  Vocabulary size} & \cellcolor{gray!6}{-0.02} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[-0.03, -0.02]} & \cellcolor{gray!6}{-7.66} & \cellcolor{gray!6}{<.001}\\
 \cellcolor{gray!6}{\hspace{1em}Word concreteness  $\times$  Gender} & \cellcolor{gray!6}{-0.01} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[-0.02, 0.00]} & \cellcolor{gray!6}{-3.50} & \cellcolor{gray!6}{<.001}\\
+\cellcolor{gray!6}{\hspace{1em}Word co-occurrence  $\times$  Information uptake} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[0.00, 0.02]} & \cellcolor{gray!6}{1.48} & \cellcolor{gray!6}{.141}\\
 \cellcolor{gray!6}{\hspace{1em}Visual strength  $\times$  Information uptake} & \cellcolor{gray!6}{0.02} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[0.01, 0.03]} & \cellcolor{gray!6}{3.05} & \cellcolor{gray!6}{.003}\\
-\hspace{1em}\makecell[l]{Distance to word 'abstract'  $\times$ \\ \hspace{0.3cm} Vocabulary size} & 0.01 & 0.01 & {}[0.00, 0.02] & 1.66 & .098\\
+\hspace{1em}Word co-occurrence  $\times$  Vocabulary size & 0.01 & 0.01 & {}[0.00, 0.02] & 1.66 & .098\\
 \hspace{1em}Visual strength  $\times$  Vocabulary size & 0.01 & 0.01 & {}[0.00, 0.02] & 2.03 & .043\\
-\hspace{1em}Distance to word 'abstract'  $\times$  Gender & 0.00 & 0.00 & {}[-0.01, 0.01] & 0.86 & .393\\
+\hspace{1em}Word co-occurrence  $\times$  Gender & 0.00 & 0.00 & {}[-0.01, 0.01] & 0.86 & .393\\
 \hspace{1em}Visual strength  $\times$  Gender & 0.00 & 0.00 & {}[-0.01, 0.01] & -0.08 & .940\\
-\hspace{1em}Word concreteness  $\times$  Vocabulary size & -0.02 & 0.00 & {}[-0.03, -0.02] & -7.66 & <.001\\
-\hspace{1em}\makecell[l]{Information uptake  $\times$ \\ \hspace{0.3cm} Distance to word 'abstract'} & 0.01 & 0.01 & {}[0.00, 0.02] & 1.48 & .141\\
 \bottomrule
@@
 
-The fixed effects of this model explained 4.11\% of the variance, and the random effects explained 17.48\% (Nakagawa et al., 2017).
-
-Figures \ref{fig:semanticdecision-interactions-with-vocabulary-size}-a and \ref{fig:semanticdecision-interactions-with-vocabulary-size}-b show that lower-vocabulary participants benefited more strongly than higher-vocabulary participants from both language- and vision-based similarity.
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/plots/semanticdecision_confidence_intervals_plot}
+
+}
+
+\caption{Means and 95\% confidence intervals for the effects of interest in the semantic decision study.}\label{fig:semanticdecision-confidence-intervals-plot}
+\end{figure}
+
+Figures \ref{fig:semanticdecision-interactions-with-vocabulary-size}-a and \ref{fig:semanticdecision-interactions-with-vocabulary-size}-b demonstrate how lower-vocabulary participants (compared to higher-vocabulary participants) were more strongly influenced by both language- and vision-based similarity.
 In contrast, Figure \ref{fig:semanticdecision-interactions-with-vocabulary-size}-c shows that higher-vocabulary participants benefitted more strongly from word concreteness.
-Since the variable that is most relevant to the semantic decision task is word concreteness, the present interactions may suggest that higher-vocabulary participants were better able to focus on the most relevant information, whereas lower-vocabulary participants were sensitive to a greater breadth of information (Lim et al., 2020; Pexman \& Yap, 2018; Yap et al., 2012, 2017).
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth,height=0.95\textheight]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/plots/semanticdecision-interactions-with-vocabulary-size}
+Since the variable that is most relevant to the semantic decision task is word concreteness, the present interactions suggest that higher-vocabulary participants were better able to focus on the most relevant information, whereas lower-vocabulary participants were sensitive to a greater breadth of information (Lim et al., 2020; Pexman \& Yap, 2018; Yap et al., 2009, 2012, 2017).
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.9\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/plots/semanticdecision-interactions-with-vocabulary-size}
 
@@
 \caption{Interactions of vocabulary size with (a) language-based information, (b) visual strength and (c) word concreteness.
-Vocabulary size is constrained to deciles, whereas in the statistical analysis it contained more values within the current range.
-\emph{n} = number of participants contained between decile values.}\label{fig:semanticdecision-interactions-with-vocabulary-size}
-\end{figure}
-
-The present analysis uses a continuous measure of word concreteness.
+Vocabulary size is constrained to deciles in this plot, whereas in the statistical analysis it contained more values within the current range.
+\emph{n} = number of participants contained between deciles.}\label{fig:semanticdecision-interactions-with-vocabulary-size}
+\end{figure}
+
+The present analysis used a continuous measure of word concreteness.
 In contrast, Pexman and Yap (2018) analysed the same data set after dividing the stimulus words into abstract and concrete subsets, which they analysed separately.
@@
 (2017) suggested that a continuous analysis remains necessary to study word concreteness (also see Cohen, 1983).
-Consistent with this, our present findings demonstrated the sensitivity of a continuous word-concreteness variable to patterns such as the greater role of task-relevant variables in high-vocabulary participants.
+Consistent with this, our present findings demonstrated the sensitivity of a continuous word concreteness variable to patterns such as the greater role of task-relevant variables in high-vocabulary participants.
 In conclusion, the literature and our findings suggest that the split-data approach and the continuous approach to word concreteness are both useful.
@@
 
-\hypertarget{visualising-the-estimates-1}{%
-\subsubsection{Visualising the estimates}\label{visualising-the-estimates-1}}
-
-Figure \ref{fig:semanticdecision-confidence-intervals-plot} presents the means and 95\% confidence intervals for the effects of interest.\footnote{Bayesian estimates not shown as they were not valid.
-They are nonetheless available in \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}.}
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.92\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/plots/semanticdecision_confidence_intervals_plot}
-
-}
-
-\caption{Means and 95\% confidence intervals for the effects of interest in the semantic decision model.}\label{fig:semanticdecision-confidence-intervals-plot}
+Figure \ref{fig:semanticdecision-interactions-with-gender} shows the interactions of gender with language-based similarity and visual-strength difference, albeit non-significant.\footnote{Plots of other interactions are available in \protect\hyperlink{appendix-D-interaction-plots}{\underline{Appendix D}}.}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.9\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/plots/semanticdecision-interactions-with-gender}
+
+}
+
+\caption{Interactions with gender in the semantic decision study.
+Gender was analysed using $z$-scores, but for clarity, the variable is shown in its basic form here.}\label{fig:semanticdecision-interactions-with-gender}
 \end{figure}
@@
 \item
-  Z-scored vocabulary age {[}\texttt{z\_vocabulary\_age}; calculated from \texttt{vocabAge} in Balota et al. (2007){]}
+  \(Z\)-scored vocabulary age {[}\texttt{z\_vocabulary\_age}; calculated from \texttt{vocabAge} in Balota et al. (2007){]}
 \item
-  Z-scored, recoded participant's gender {[}\texttt{z\_recoded\_participant\_gender}; calculated from \texttt{Gender} in Balota et al. (2007){]}
+  \(Z\)-scored, recoded participant's gender {[}\texttt{z\_recoded\_participant\_gender}; calculated from \texttt{Gender} in Balota et al. (2007){]}
 \item
-  Z-scored word frequency {[}\texttt{z\_word\_frequency}; calculated from \texttt{LgSUBTLWF} in Balota et al. (2007){]}
+  \(Z\)-scored word frequency {[}\texttt{z\_word\_frequency}; calculated from \texttt{LgSUBTLWF} in Balota et al. (2007){]}
 \item
-  Z-scored vision-based information in words {[}\texttt{z\_visual\_rating}; calculated from \texttt{Visual.mean} in Lynott et al. (2020){]}
+  \(Z\)-scored vision-based information in words {[}\texttt{z\_visual\_rating}; calculated from \texttt{Visual.mean} in Lynott et al. (2020){]}
 \end{itemize}
 
-The final data set contained 795 participants, 12,636 words, and a total of 19,828 RTs.
-On average, there were 25 words per participant (\(SD\) = 36.04), and conversely, 2 participants per word (\(SD\) = 0.86).
+The final data set contained 795 participants, 12,636 words, and 19,828 RTs. On average, there were 25 words per participant (\(SD\) = 36.04), and conversely, 2 participants per word (\(SD\) = 0.86).
 
@@
 \item
-  Lexical (see \protect\hyperlink{appendix-A-lexical-covariates}{\underline{Appendix A}}): Z-scored orthographic Levenshtein distance (Balota et al., 2007)
+  Lexical (see \protect\hyperlink{appendix-A-lexical-covariates}{\underline{Appendix A}}): \(Z\)-scored orthographic Levenshtein distance (Balota et al., 2007)
 \item
-  Semantic: z-scored word concreteness (Brysbaert et al., 2014), used as a covariate of visual rating.
+  Semantic: \(z\)-scored word concreteness (Brysbaert et al., 2014), used as a covariate of visual rating.
 \end{itemize}
@@
 
-Table \ref{tab:lexicaldecision-frequentist-model} presents the results of the mixed-effects model.
+Table \ref{tab:lexicaldecision-frequentist-model} presents the results of the frequentist model.
+The fixed effects explained 5.61\% of the variance, and the random effects 10.25\% {[}Nakagawa et al.
+(2017); for an explanation of this difference, see \protect\hyperlink{semanticpriming-results}{\underline{Results of Study 1}}).
+Figure \ref{fig:lexicaldecision-frequentist-bayesian-plot-weaklyinformativepriors-exgaussian} displays the frequentist estimates alongside the Bayesian estimates.
+The latter are from the weakly-informative prior model.
+The estimates of the two other models (i.e., with informative and diffuse priors, respectively) were virtually identical to these (see \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}).
 
@@
 
-The fixed effects of this model explained 5.61\% of the variance, and the random effects explained 10.25\% (Nakagawa et al., 2017).
-
-\hypertarget{visualising-the-estimates-2}{%
-\subsubsection{Visualising the estimates}\label{visualising-the-estimates-2}}
-
-Figure \ref{fig:lexicaldecision-frequentist-bayesian-plot-weaklyinformativepriors-exgaussian} presents the posterior distribution of each effect, based on the informative prior model (for the models with the other priors, see \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}).
-The frequentist estimates are also shown to facilitate the comparison with them.
-
 \begin{figure}
@@
 The Bayesian means (represented by vertical lines) are flanked by 95\% credible intervals, in light blue (in some cases, the interval is covered up by the bar of the mean).}\label{fig:lexicaldecision-frequentist-bayesian-plot-weaklyinformativepriors-exgaussian}
+\end{figure}
+
+Figure \ref{fig:lexicaldecision-interactions-with-vocabulary-age} presents the interactions of vocabulary age with word frequency and with visual strength, albeit non-significant.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/plots/lexicaldecision-interactions-with-vocabulary-age}
+
+}
+
+\caption{Interactions of vocabulary age with word frequency and visual strength.
+Vocabulary age is constrained to sextiles (six sections) in this plot, whereas in the statistical analysis it contained more values within the current range.
+\emph{n} = number of participants contained between sextiles.}\label{fig:lexicaldecision-interactions-with-vocabulary-age}
+\end{figure}
+
+Figure \ref{fig:lexicaldecision-interactions-with-gender} shows the interactions of gender with language-based similarity and visual-strength difference, albeit non-significant.\footnote{Plots of other interactions are available in \protect\hyperlink{appendix-D-interaction-plots}{\underline{Appendix D}}.}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/plots/lexicaldecision-interactions-with-gender}
+
+}
+
+\caption{Interactions with gender in the lexical decision study.
+Gender was analysed using $z$-scores, but for clarity, the variable is shown in its basic form here.}\label{fig:lexicaldecision-interactions-with-gender}
 \end{figure}
@@
 (Lynott et al., 2020; Lynott \& Connell, 2009; Newcombe et al., 2012).
-Thus, this historical discrepancy might in part (only in part) account for the superiority of linguistic information over embodied information, as found in the present study and in previous studies (Banks et al., 2021; Kiela \& Bottou, 2014; Lam et al., 2015; Louwerse et al., 2015; Pecher et al., 1998; Petilli et al., 2021).
+Thus, this historical accident could account for a portion of the superiority of linguistic information over embodied information (Banks et al., 2021; Kiela \& Bottou, 2014; as found in Lam et al., 2015; Louwerse et al., 2015; Pecher et al., 1998; Petilli et al., 2021).
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-al-azaryCanYouTouch2022}{}}%
+Al-Azary, H., Yu, T., \& McRae, K.
+(2022).
+Can you touch the {N400}?
+{The} interactive effects of body-object interaction and task demands on {N400} amplitudes and decision latencies.
+\emph{Brain and Language}, \emph{231}, 105147.
+\url{https://doi.org/10.1016/j.bandl.2022.105147}
+
 \leavevmode\vadjust pre{\hypertarget{ref-albersWhenPowerAnalyses2018}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-andrewsIntegratingExperientialDistributional2009}{}}%
-Andrews, M., Vigliocco, G., \& Vinson, D.
-(2009).
-Integrating experiential and distributional data to learn semantic representations.
-\emph{Psychological Review}, \emph{116}(3), 463--498.
-\url{https://doi.org/10.1037/a0016261}
-
 \leavevmode\vadjust pre{\hypertarget{ref-aujlaLanguageExperiencePredicts2021}{}}%
@@
 \url{https://doi.org/10.1037/cep0000255}
+
+\leavevmode\vadjust pre{\hypertarget{ref-baayenMixedeffectsModelingCrossed2008}{}}%
+Baayen, R.
+H., Davidson, D.
+J., \& Bates, D.
+M.
+(2008).
+Mixed-effects modeling with crossed random effects for subjects and items.
+\emph{Journal of Memory and Language}, \emph{59}(4), 390--412.
+\url{https://doi.org/10.1016/j.jml.2007.12.005}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-barsalouPerceptualSymbolSystems1999}{}}%
-Barsalou, L. W. (1999). Perceptual symbol systems. \emph{Behavioral and Brain Sciences}, \emph{22}(4), 577--660. \url{https://doi.org/10.1017/S0140525X99002149}
-
 \leavevmode\vadjust pre{\hypertarget{ref-barsalouLanguageSimulationConceptual2008}{}}%
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bernabeu2021a}{}}%
-Bernabeu, P., Lynott, D., \& Connell, L. (2021). \emph{Preregistration: {The} interplay between linguistic and embodied systems in conceptual processing}. {OSF}. \url{https://osf.io/ftydw/}
+Bernabeu, P., Lynott, D., \& Connell, L. (2021). \emph{Preregistration: {The} interplay between linguistic and embodied systems in conceptual processing}. {OSF}. \url{https://osf.io/ftydw}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-concaSearchDifferentCategories2021}{}}%
-Conca, F., Catricalà, E., Canini, M., Petrini, A., Vigliocco, G., Cappa, S.
-F., \& Della Rosa, P.
-A.
-(2021).
-In search of different categories of abstract concepts: A {fMRI} adaptation study.
-\emph{Scientific Reports}, \emph{11}(1, 1), 22587.
-\url{https://doi.org/10.1038/s41598-021-02013-8}
-
 \leavevmode\vadjust pre{\hypertarget{ref-connell2019a}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-connellWeKnowWhat2016}{}}%
-Connell, L., \& Lynott, D.
-(2016).
-Do we know what we're simulating?
-{Information} loss on transferring unconscious perceptual simulation to conscious imagery.
-\emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{42}(8), 1218--1232.
-\url{https://doi.org/10.1037/xlm0000245}
-
 \leavevmode\vadjust pre{\hypertarget{ref-connellInteroceptionForgottenModality2018}{}}%
@@
 \url{https://doi.org/10.1098/rstb.2017.0143}
-
-\leavevmode\vadjust pre{\hypertarget{ref-contreraskallensQuantifyingInterdisciplinarityCognitive2022}{}}%
-Contreras Kallens, P., Dale, R., \& Christiansen, M.
-H.
-(2022).
-Quantifying interdisciplinarity in cognitive science and beyond.
-\emph{Topics in Cognitive Science}.
-\url{https://doi.org/10.1111/tops.12609}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-dove2020a}{}}%
-Dove, G. (2020). More than a scaffold: {Language} is a neuroenhancement. \emph{Cognitive Neuropsychology}, \emph{37}(5-6), 288--311. \url{https://doi.org/10.1080/02643294.2019.1637338}
-
 \leavevmode\vadjust pre{\hypertarget{ref-dunabeitiaQualitativeDifferencesRepresentation2009}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-garceaPreservedToolKnowledge2013}{}}%
-Garcea, F., Dombovy, M., \& Mahon, B.
-Z.
-(2013).
-Preserved {Tool Knowledge} in the {Context} of {Impaired Action Knowledge}: {Implications} for {Models} of {Semantic Memory}.
-\emph{Frontiers in Human Neuroscience}, \emph{7}, 120.
-\url{https://doi.org/10.3389/fnhum.2013.00120}
-
-\leavevmode\vadjust pre{\hypertarget{ref-garciaTimeFaceLanguage2020}{}}%
-García, A.
-M., Hesse, E., Birba, A., Adolfi, F., Mikulan, E., Caro, M.
-M., Petroni, A., Bekinschtein, T.
-A., del Carmen García, M., Silva, W., Ciraolo, C., Vaucheret, E., Sedeño, L., \& Ibáñez, A.
-(2020).
-Time to face language: Embodied mechanisms underpin the inception of face-related meanings in the human brain.
-\emph{Cerebral Cortex}, \emph{30}(11), 6051--6068.
-\url{https://doi.org/10.1093/cercor/bhaa178}
-
 \leavevmode\vadjust pre{\hypertarget{ref-gelmanPowerCalculationsAssessing2014}{}}%
@@
 \url{https://doi.org/10.3389/fpsyg.2016.01646}
-
-\leavevmode\vadjust pre{\hypertarget{ref-guntherSymbolGroundingDirect2018}{}}%
-Günther, F., Dudschig, C., \& Kaup, B.
-(2018).
-Symbol grounding without direct experience: Do words inherit sensorimotor activation from purely linguistic context?
-\emph{Cognitive Science}, \emph{42}(S2), 336--374.
-\url{https://doi.org/10.1111/cogs.12549}
-
-\leavevmode\vadjust pre{\hypertarget{ref-guntherLimitsAutomaticSensorimotor2021}{}}%
-Günther, F., Press, S.
-A., Dudschig, C., \& Kaup, B.
-(2021).
-The limits of automatic sensorimotor processing during word processing: Investigations with repeated linguistic experience, memory consolidation during sleep, and rich linguistic learning contexts.
-\emph{Psychological Research}.
-\url{https://doi.org/10.1007/s00426-021-01620-4}
 
@@
 \url{https://doi.org/10.3389/fpsyg.2011.00045}
-
-\leavevmode\vadjust pre{\hypertarget{ref-harnadSymbolGroundingProblem1990}{}}%
-Harnad, S. (1990). The symbol grounding problem. \emph{Physica D: Nonlinear Phenomena}, \emph{42}(1), 335--346. \url{https://doi.org/10.1016/0167-2789(90)90087-6}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-kumar2021a}{}}%
-Kumar, A.
-A.
-(2021).
-Semantic memory: {A} review of methods, models, and current challenges.
-\emph{Psychonomic Bulletin \& Review}, \emph{28}(1), 40--80.
-\url{https://doi.org/10.3758/s13423-020-01792-x}
-
 \leavevmode\vadjust pre{\hypertarget{ref-kumarDistantConnectivityMultiplestep2020}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-leboisAreAutomaticConceptual2015}{}}%
-Lebois, L.
-A.
-M., Wilson-Mendenhall, C.
-D., \& Barsalou, L.
-W.
-(2015).
-Are automatic conceptual cores the gold standard of semantic processing?
-{The} context-dependence of spatial meaning in grounded congruency effects.
-\emph{Cognitive Science}, \emph{39}(8), 1764--1801.
-\url{https://doi.org/10.1111/cogs.12174}
-
 \leavevmode\vadjust pre{\hypertarget{ref-leeBayesianCognitiveModeling2014}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-lieversLinguisticDimensionsConcrete2021}{}}%
-Lievers, F.
-S., Bolognesi, M., \& Winter, B.
-(2021).
-The linguistic dimensions of concrete and abstract concepts: Lexical category, morphological structure, countability, and etymology.
-\emph{Cognitive Linguistics}, \emph{32}(4), 641--670.
-\url{https://doi.org/10.1515/cog-2021-0007}
+\leavevmode\vadjust pre{\hypertarget{ref-lewandowskiGeneratingRandomCorrelation2009}{}}%
+Lewandowski, D., Kurowicka, D., \& Joe, H.
+(2009).
+Generating random correlation matrices based on vines and extended onion method.
+\emph{Journal of Multivariate Analysis}, \emph{100}(9), 1989--2001.
+\url{https://doi.org/10.1016/j.jmva.2009.04.008}
 
@@
 \url{https://doi.org/10.1080/23273798.2014.981552}
-
-\leavevmode\vadjust pre{\hypertarget{ref-louwerseLanguageEncodesGeographical2009}{}}%
-Louwerse, M. M., \& Zwaan, R. A. (2009). Language encodes geographical information. \emph{Cognitive Science}, \emph{33}(1), 51--73. \url{https://doi.org/10.1111/j.1551-6709.2008.01003.x}
 
@@
 \url{https://doi.org/10.1027/1864-9335/a000187}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mahonCriticalLookEmbodied2008}{}}%
-Mahon, B.
-Z., \& Caramazza, A.
-(2008).
-A critical look at the embodied cognition hypothesis and a new proposal for grounding conceptual content.
-\emph{Journal of Physiology-Paris}, \emph{102}(1), 59--70.
-\url{https://doi.org/10.1016/j.jphysparis.2008.03.004}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mahon2016a}{}}%
-Mahon, B.
-Z., \& Hickok, G.
-(2016).
-Arguments about the nature of concepts: {Symbols}, embodiment, and beyond.
-\emph{Psychonomic Bulletin \& Review}, \emph{23}(4), 941--958.
-\url{https://doi.org/10.3758/s13423-016-1045-2}
-
-\leavevmode\vadjust pre{\hypertarget{ref-majidOdorsAreExpressible2014}{}}%
-Majid, A., \& Burenhult, N.
-(2014).
-Odors are expressible in language, as long as you speak the right language.
-\emph{Cognition}, \emph{130}(2), 266--270.
-\url{https://doi.org/10.1016/j.cognition.2013.11.004}
-
-\leavevmode\vadjust pre{\hypertarget{ref-majidSensesLanguageCulture2011}{}}%
-Majid, A., \& Levinson, S. C. (2011). The senses in language and culture. \emph{The Senses and Society}, \emph{6}(1), 5--18. \url{https://doi.org/10.2752/174589311X12893982233551}
-
-\leavevmode\vadjust pre{\hypertarget{ref-majidCanNomenclatureBody2015}{}}%
-Majid, A., \& van Staden, M.
-(2015).
-Can nomenclature for the body be explained by embodiment theories?
-\emph{Topics in Cognitive Science}, \emph{7}(4), 570--594.
-\url{https://doi.org/10.1111/tops.12159}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-negriWhatRoleMotor2007}{}}%
-Negri, G.
-A.
-L., Rumiati, R.
-I., Zadini, A., Ukmar, M., Mahon, B.
-Z., \& Caramazza, A.
-(2007).
-What is the role of motor simulation in action and object recognition?
-{Evidence} from apraxia.
-\emph{Cognitive Neuropsychology}, \emph{24}(8), 795--816.
-\url{https://doi.org/10.1080/02643290701707412}
-
 \leavevmode\vadjust pre{\hypertarget{ref-newcombeEffectsEmotionalSensorimotor2012}{}}%
@@
 Paivio, A. (1990). \emph{Mental representations: A dual coding approach}. {Oxford University Press}. \url{https://doi.org/10.1093/acprof:oso/9780195066661.001.0001}
-
-\leavevmode\vadjust pre{\hypertarget{ref-papeoActionPerformanceActionword2010}{}}%
-Papeo, L., Negri, G.
-A.
-L., Zadini, A., \& Ida Rumiati, R.
-(2010).
-Action performance and action-word understanding: {Evidence} of double dissociations in left-damaged patients.
-\emph{Cognitive Neuropsychology}, \emph{27}(5), 428--461.
-\url{https://doi.org/10.1080/02643294.2011.570326}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-perfettiLexicalQualityHypothesis2002}{}}%
+Perfetti, C.
+A., \& Hart, L.
+(2002).
+The lexical quality hypothesis.
+In L.
+Verhoeven, C.
+Elbro, \& P.
+Reitsma (Eds.), \emph{Studies in {Written Language} and {Literacy}} (Vol.
+11, pp.
+189--213).
+{John Benjamins Publishing Company}.
+\url{https://doi.org/10.1075/swll.11.14per}
+
 \leavevmode\vadjust pre{\hypertarget{ref-petilli2021a}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-pulvermullerHowNeuronsMake2013}{}}%
-Pulvermüller, F.
-(2013).
-How neurons make meaning: {Brain} mechanisms for embodied and abstract-symbolic semantics.
-\emph{Trends in Cognitive Sciences}, \emph{17}(9), 458--470.
-\url{https://doi.org/10.1016/j.tics.2013.06.004}
-
 \leavevmode\vadjust pre{\hypertarget{ref-pylyshynWhatMindEye1973}{}}%
@@
 \url{https://doi.org/10.1016/j.cogpsych.2009.09.001}
-
-\leavevmode\vadjust pre{\hypertarget{ref-regginDevelopmentAbstractWord2021}{}}%
-Reggin, L. D., Muraki, E. J., \& Pexman, P. M. (2021). Development of abstract word knowledge. \emph{Frontiers in Psychology}, \emph{12}, 2115. \url{https://doi.org/10.3389/fpsyg.2021.686478}
 
@@
 \url{https://doi.org/10.1016/j.jneuroling.2020.100895}
-
-\leavevmode\vadjust pre{\hypertarget{ref-riccardiDissociatingActionAbstract2019}{}}%
-Riccardi, N., Yourganov, G., Rorden, C., Fridriksson, J., \& Desai, R.
-H.
-(2019).
-Dissociating action and abstract verb comprehension post-stroke.
-\emph{Cortex}, \emph{120}, 131--146.
-\url{https://doi.org/10.1016/j.cortex.2019.05.013}
 
@@
 \url{https://doi.org/10.1016/j.bandl.2016.08.001}
-
-\leavevmode\vadjust pre{\hypertarget{ref-satoTaskRelatedModulation2008}{}}%
-Sato, M., Mengarelli, M., Riggio, L., Gallese, V., \& Buccino, G.
-(2008).
-Task related modulation of the motor system during language processing.
-\emph{Brain and Language}, \emph{105}(2), 83--90.
-\url{https://doi.org/10.1016/j.bandl.2007.10.001}
 
@@
 \url{https://doi.org/10.1007/BF00309710}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shebaniWhatImpairedSpatial2021}{}}%
-Shebani, Z., Nestor, P.
-J., \& Pulvermüller, F.
-(2021).
-What's {``up''}?
-{Impaired} spatial preposition processing in posterior cortical atrophy.
-\emph{Frontiers in Human Neuroscience}, \emph{15}, 718.
-\url{https://doi.org/10.3389/fnhum.2021.731104}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shebaniFlexibilityLanguageAction2018}{}}%
-Shebani, Z., \& Pulvermüller, F.
-(2018).
-Flexibility in {Language Action Interaction}: {The Influence} of {Movement Type}.
-\emph{Frontiers in Human Neuroscience}, \emph{12}.
-\url{https://www.frontiersin.org/article/10.3389/fnhum.2018.00252}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-vannuscorpsPersistentSparingAction2016}{}}%
-Vannuscorps, G., Dricot, L., \& Pillon, A.
-(2016).
-Persistent sparing of action conceptual processing in spite of increasing disorders of action production: {A} case against motor embodiment of action concepts.
-\emph{Cognitive Neuropsychology}, \emph{33}(3-4), 191--219.
-\url{https://doi.org/10.1080/02643294.2016.1186615}
-
 \leavevmode\vadjust pre{\hypertarget{ref-vasishthHowEmbraceVariation2021}{}}%
@@
 \url{https://doi.org/10.1016/j.jml.2018.07.004}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vasishthBayesianDataAnalysis2018}{}}%
+Vasishth, S., Nicenboim, B., Beckman, M.
+E., Li, F., \& Kong, E.
+J.
+(2018).
+Bayesian data analysis in the phonetic sciences: {A} tutorial introduction.
+\emph{Journal of Phonetics}, \emph{71}, 147--161.
+\url{https://doi.org/10.1016/j.wocn.2018.07.008}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-vitaleNeuralInhibitionNetwork2021}{}}%
-Vitale, F., Monti, I., Padrón, I., Avenanti, A., \& de Vega, M.
-(2021).
-The neural inhibition network is causally involved in the disembodiment effect of linguistic negation.
-\emph{Cortex}.
-\url{https://doi.org/10.1016/j.cortex.2021.11.015}
-
 \leavevmode\vadjust pre{\hypertarget{ref-vondermalsburgFalsePositivesOther2017}{}}%
@@
 \url{https://doi.org/10.1016/j.jml.2016.10.003}
-
-\leavevmode\vadjust pre{\hypertarget{ref-vukovicPrimaryMotorCortex2017}{}}%
-Vukovic, N., Feurra, M., Shpektor, A., Myachykov, A., \& Shtyrov, Y.
-(2017).
-Primary motor cortex functionally contributes to language comprehension: {An} online {rTMS} study.
-\emph{Neuropsychologia}, \emph{96}, 222--229.
-\url{https://doi.org/10.1016/j.neuropsychologia.2017.01.025}
 
@@
 \url{https://doi.org/10.1016/B978-0-444-64123-6.00007-2}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wangNeuralRepresentationAbstract2010}{}}%
-Wang, J., Conder, J.
-A., Blitzer, D.
-N., \& Shinkareva, S.
-V.
-(2010).
-Neural representation of abstract and concrete concepts: {A} meta-analysis of neuroimaging studies.
-\emph{Human Brain Mapping}, \emph{31}(10), 1459--1468.
-\url{https://doi.org/10.1002/hbm.20950}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wangSocialEmotionDimensional2021}{}}%
-Wang, X., Li, G., Zhao, G., Li, Y., Wang, B., Lin, C.-P., Liu, X., \& Bi, Y.
-(2021).
-Social and emotion dimensional organizations in the abstract semantic space: The neuropsychological evidence.
-\emph{Scientific Reports}, \emph{11}(1, 1), 23572.
-\url{https://doi.org/10.1038/s41598-021-02824-9}
-
-\leavevmode\vadjust pre{\hypertarget{ref-willemsFlexibilityEmbodiedLanguage2011}{}}%
-Willems, R. M., \& Casasanto, D. (2011). Flexibility in {Embodied Language Understanding}. \emph{Frontiers in Psychology}, \emph{0}. \url{https://doi.org/10.3389/fpsyg.2011.00116}
 
@@
 \item \textit{Note}.
-$\upbeta$ = Estimate based on z-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CI = confidence interval.
+$\upbeta$ = Estimate based on $z$-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CI = confidence interval.
 By-participant random slopes were included for \linebreak \phantom{.}every effect.
@@
 
-\hypertarget{lack-of-convergence}{%
-\subsection{Lack of convergence}\label{lack-of-convergence}}
+\hypertarget{convergence-1}{%
+\subsection{Convergence}\label{convergence-1}}
 
 The challenge of convergence is well known in the area of mixed-effects models.
-The solutions proposed range from the removal of random slopes under certain conditions (Matuschek et al., 2017) to the maintenance of random slopes in spite of convergence warnings, which seeks to avoid an inflation of the Type I error caused by non-independence in the data (Brauer \& Curtin, 2018; Singmann \& Kellen, 2019).
+These models often struggle to reach reliable-enough estimates due to an insufficiency of data relative to the complexity of the model (Baayen et al., 2008; Bates et al., 2015; Brauer \& Curtin, 2018).
+The solutions proposed range from the removal of random slopes under certain conditions (Matuschek et al., 2017) to the maintenance of random slopes in spite of convergence warnings, which seeks to avoid an inflation of the Type I error due to dependencies in the data (Brauer \& Curtin, 2018; Singmann \& Kellen, 2019).
 
@@
 
-\hypertarget{lack-of-convergence-1}{%
-\subsubsection{Lack of convergence}\label{lack-of-convergence-1}}
+\hypertarget{convergence-2}{%
+\subsubsection{Convergence}\label{convergence-2}}
 
@@
 
-\hypertarget{convergence}{%
-\paragraph{Convergence}\label{convergence}}
+\hypertarget{convergence-3}{%
+\paragraph{Convergence}\label{convergence-3}}
 
@@
 
-\hypertarget{convergence-1}{%
-\subsubsection{Convergence}\label{convergence-1}}
+\hypertarget{convergence-4}{%
+\subsubsection{Convergence}\label{convergence-4}}
 
@@
 
-\hypertarget{convergence-2}{%
-\subsubsection{Convergence}\label{convergence-2}}
+\hypertarget{convergence-5}{%
+\subsubsection{Convergence}\label{convergence-5}}
 
@@
 \hypertarget{appendix-D-interaction-plots}{%
-\section{Appendix D: Further plots of interactions}\label{appendix-D-interaction-plots}}
-
-This appendix presents plots of interactions that did not fit in the main text.
+\section{Appendix D: Further interaction plots}\label{appendix-D-interaction-plots}}
+
+This appendix presents plots of interactions that were not shown in the main text.
 
@@
 
-{\centering \includegraphics[width=1\linewidth,height=0.7\textheight]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-gender}
-
-}
-
-\caption{Interactions with gender in the semantic priming study.}\label{fig:semanticpriming-interactions-with-gender}
-\end{figure}
-
-\ldots{} TBC
+{\centering \includegraphics[width=0.85\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-attentional-control}
+
+}
+
+\caption{Interactions of attentional control with language-based similarity and visual-strength difference.
+Attentional control is constrained to deciles (ten sections) in this plot, whereas in the statistical analysis it contained more values within the current range.
+\emph{n} = number of participants contained between decile values.}\label{fig:semanticpriming-interactions-with-attentional-control}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.65\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interaction-word-concreteness-difference-SOA}
+
+}
+
+\caption{Interaction of stimulus-onset asynchrony (SOA) with word-concreteness difference.
+SOA was analysed using $z$-scores, but for clarity, the variable is shown in its basic form here.}\label{fig:semanticpriming-interaction-word-concreteness-difference-SOA}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.85\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interaction-word-concreteness-difference-vocabulary-size}
+
+}
+
+\caption{Interaction of word-concreteness difference with vocabulary size.
+Vocabulary size is constrained to deciles in this plot, whereas in the statistical analysis it contained more values within the current range.
+\emph{n} = number of participants contained between decile values.}\label{fig:semanticpriming-interaction-word-concreteness-difference-vocabulary-size}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.65\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interaction-word-concreteness-difference-gender}
+
+}
+
+\caption{Interaction of word-concreteness difference with gender.
+Gender was analysed using \(z\)-scores, but for clarity, the variable is shown in its basic form here.
+\emph{n} = number of participants contained between decile values.}\label{fig:semanticpriming-interaction-word-concreteness-difference-gender}
+\end{figure}
+
+\clearpage
 
@@
 
-\ldots{}
+\begin{figure}
+
+{\centering \includegraphics[width=0.9\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/plots/semanticdecision-interactions-with-information-uptake}
+
+}
+
+\caption{Interactions of information uptake with language-based similarity and visual-strength difference.
+Information uptake is constrained to deciles in this plot, whereas in the statistical analysis it contained more values within the current range.
+\emph{n} = number of participants contained between decile values.}\label{fig:semanticdecision-interactions-with-information-uptake}
+\end{figure}
+
+\clearpage
 
@@
 
-\ldots{}
+\begin{figure}
+
+{\centering \includegraphics[width=0.85\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/plots/lexicaldecision-interaction-word-concreteness-vocabulary-age}
+
+}
+
+\caption{Interaction of word concreteness with vocabulary age.
+Vocabulary age is constrained to sextiles (six sections) in this plot, whereas in the statistical analysis it contained more values within the current range.
+\emph{n} = number of participants contained between sextile values.}\label{fig:lexicaldecision-interaction-word-concreteness-vocabulary-age}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.65\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/plots/lexicaldecision-interaction-word-concreteness-gender}
+
+}
+
+\caption{Interaction of word concreteness with gender.
+Gender was analysed using \(z\)-scores, but for clarity, the variable is shown in its basic form here.
+\emph{n} = number of participants contained between sextile values.}\label{fig:lexicaldecision-interaction-word-concreteness-gender}
+\end{figure}
 
@@
 That is, the closer an interval is to a value of 0 on the predicted RT (\(z\)), the smaller the effect of that predictor.
-For instance, an interval that is symmetrically centred on 0 indicates a very small effect, whereas---in comparison---an interval that does not include 0 indicates a far larger effect (for examples of this approach, see Milek et al., 2018; Rodríguez-Ferreiro et al., 2020).
+For instance, an interval that is symmetrically centred on 0 indicates a very small effect, whereas---in comparison---an interval that does not include 0 indicates a far larger effect (for other examples of this approach, see Milek et al., 2018; Pregla et al., 2021; Rodríguez-Ferreiro et al., 2020).
 
@@
 \item \textit{Note}.
-$\upbeta$ = Estimate based on z-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CrI = credible interval.
+$\upbeta$ = Estimate based on $z$-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CrI = credible interval.
 Shaded rows contain covariates.
@@
 Figure \ref{fig:semanticpriming-frequentist-bayesian-plot-allpriors-exgaussian} presents the posterior distribution of each effect in each model.
-The frequentist estimates are also shown to facilitate the comparison with them.
+The frequentist estimates are also shown to facilitate the comparison.
 
@@
 \cellcolor{gray!6}{\hspace{1em}Word concreteness} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.26} & \cellcolor{gray!6}{{}[-0.08, 1.01]} & \cellcolor{gray!6}{1.30}\\
-\hspace{1em}Distance to word 'abstract' $^{\text{b}}$ & -0.05 & 0.23 & {}[-0.87, 0.40] & 1.41\\
+\hspace{1em}Word co-occurrence $^{\text{b}}$ & -0.05 & 0.23 & {}[-0.87, 0.40] & 1.41\\
 \hspace{1em}Visual strength $^{\text{b}}$ & -0.20 & 0.49 & {}[-1.52, -0.01] & 1.31\\
@@
 \multicolumn{5}{l}{\textbf{Interactions}}\\
+\cellcolor{gray!6}{\hspace{1em}Word concreteness  $\times$  Vocabulary size} & \cellcolor{gray!6}{0.02} & \cellcolor{gray!6}{0.55} & \cellcolor{gray!6}{{}[-1.24, 1.83]} & \cellcolor{gray!6}{1.42}\\
 \cellcolor{gray!6}{\hspace{1em}Word concreteness  $\times$  Gender} & \cellcolor{gray!6}{0.07} & \cellcolor{gray!6}{0.40} & \cellcolor{gray!6}{{}[-0.31, 1.58]} & \cellcolor{gray!6}{1.42}\\
+\cellcolor{gray!6}{\hspace{1em}Word co-occurrence  $\times$  Information uptake} & \cellcolor{gray!6}{-0.06} & \cellcolor{gray!6}{0.19} & \cellcolor{gray!6}{{}[-0.70, 0.02]} & \cellcolor{gray!6}{1.31}\\
 \cellcolor{gray!6}{\hspace{1em}Visual strength  $\times$  Information uptake} & \cellcolor{gray!6}{-0.15} & \cellcolor{gray!6}{0.46} & \cellcolor{gray!6}{{}[-1.79, 0.02]} & \cellcolor{gray!6}{1.30}\\
-\hspace{1em}\makecell[l]{Distance to word 'abstract'  $\times$ \\ \hspace{0.3cm} Vocabulary size} & -0.04 & 0.55 & {}[-1.92, 1.11] & 1.42\\
+\hspace{1em}Word co-occurrence  $\times$  Vocabulary size & -0.04 & 0.55 & {}[-1.92, 1.11] & 1.42\\
 \hspace{1em}Visual strength  $\times$  Vocabulary size & 0.15 & 0.38 & {}[0.00, 1.27] & 1.30\\
-\hspace{1em}Distance to word 'abstract'  $\times$  Gender & 0.00 & 0.26 & {}[-0.78, 0.68] & 1.41\\
+\hspace{1em}Word co-occurrence  $\times$  Gender & 0.00 & 0.26 & {}[-0.78, 0.68] & 1.41\\
 \hspace{1em}Visual strength  $\times$  Gender & 0.18 & 0.49 & {}[-0.01, 1.66] & 1.30\\
-\hspace{1em}Word concreteness  $\times$  Vocabulary size & 0.02 & 0.55 & {}[-1.24, 1.83] & 1.42\\
-\hspace{1em}\makecell[l]{Information uptake  $\times$ \\ \hspace{0.3cm} Distance to word 'abstract'} & -0.06 & 0.19 & {}[-0.70, 0.02] & 1.31\\
 \bottomrule
@@
 \multicolumn{5}{l}{\textbf{Interactions}}\\
+\cellcolor{gray!6}{\hspace{1em}Word concreteness  $\times$  Vocabulary size} & \cellcolor{gray!6}{0.02} & \cellcolor{gray!6}{0.55} & \cellcolor{gray!6}{{}[-1.24, 1.83]} & \cellcolor{gray!6}{1.41}\\
 \cellcolor{gray!6}{\hspace{1em}Word concreteness  $\times$  Gender} & \cellcolor{gray!6}{0.07} & \cellcolor{gray!6}{0.40} & \cellcolor{gray!6}{{}[-0.31, 1.58]} & \cellcolor{gray!6}{1.42}\\
+\cellcolor{gray!6}{\hspace{1em}Word co-occurrence  $\times$  Information uptake} & \cellcolor{gray!6}{-0.06} & \cellcolor{gray!6}{0.19} & \cellcolor{gray!6}{{}[-0.70, 0.02]} & \cellcolor{gray!6}{1.31}\\
 \cellcolor{gray!6}{\hspace{1em}Visual strength  $\times$  Information uptake} & \cellcolor{gray!6}{-0.15} & \cellcolor{gray!6}{0.46} & \cellcolor{gray!6}{{}[-1.79, 0.02]} & \cellcolor{gray!6}{1.31}\\
-\hspace{1em}\makecell[l]{Distance to word 'abstract'  $\times$ \\ \hspace{0.3cm} Vocabulary size} & -0.04 & 0.55 & {}[-1.92, 1.11] & 1.42\\
+\hspace{1em}Word co-occurrence  $\times$  Vocabulary size & -0.04 & 0.55 & {}[-1.92, 1.11] & 1.42\\
 \hspace{1em}Visual strength  $\times$  Vocabulary size & 0.15 & 0.38 & {}[0.00, 1.28] & 1.30\\
-\hspace{1em}Distance to word 'abstract'  $\times$  Gender & 0.00 & 0.26 & {}[-0.78, 0.68] & 1.41\\
+\hspace{1em}Word co-occurrence  $\times$  Gender & 0.00 & 0.26 & {}[-0.78, 0.68] & 1.41\\
 \hspace{1em}Visual strength  $\times$  Gender & 0.18 & 0.49 & {}[-0.01, 1.66] & 1.31\\
-\hspace{1em}Word concreteness  $\times$  Vocabulary size & 0.02 & 0.55 & {}[-1.24, 1.83] & 1.41\\
-\hspace{1em}\makecell[l]{Information uptake  $\times$ \\ \hspace{0.3cm} Distance to word 'abstract'} & -0.06 & 0.19 & {}[-0.70, 0.02] & 1.31\\
 \bottomrule
@@
 \multicolumn{5}{l}{\textbf{Interactions}}\\
+\cellcolor{gray!6}{\hspace{1em}Word concreteness  $\times$  Vocabulary size} & \cellcolor{gray!6}{0.02} & \cellcolor{gray!6}{0.55} & \cellcolor{gray!6}{{}[-1.24, 1.83]} & \cellcolor{gray!6}{1.41}\\
 \cellcolor{gray!6}{\hspace{1em}Word concreteness  $\times$  Gender} & \cellcolor{gray!6}{0.07} & \cellcolor{gray!6}{0.40} & \cellcolor{gray!6}{{}[-0.31, 1.58]} & \cellcolor{gray!6}{1.41}\\
+\cellcolor{gray!6}{\hspace{1em}Word co-occurrence  $\times$  Information uptake} & \cellcolor{gray!6}{-0.06} & \cellcolor{gray!6}{0.19} & \cellcolor{gray!6}{{}[-0.70, 0.02]} & \cellcolor{gray!6}{1.31}\\
 \cellcolor{gray!6}{\hspace{1em}Visual strength  $\times$  Information uptake} & \cellcolor{gray!6}{-0.15} & \cellcolor{gray!6}{0.46} & \cellcolor{gray!6}{{}[-1.79, 0.02]} & \cellcolor{gray!6}{1.30}\\
-\hspace{1em}\makecell[l]{Distance to word 'abstract'  $\times$ \\ \hspace{0.3cm} Vocabulary size} & -0.04 & 0.55 & {}[-1.92, 1.11] & 1.41\\
+\hspace{1em}Word co-occurrence  $\times$  Vocabulary size & -0.04 & 0.55 & {}[-1.92, 1.11] & 1.41\\
 \hspace{1em}Visual strength  $\times$  Vocabulary size & 0.15 & 0.38 & {}[0.00, 1.27] & 1.30\\
-\hspace{1em}Distance to word 'abstract'  $\times$  Gender & 0.00 & 0.26 & {}[-0.78, 0.68] & 1.42\\
+\hspace{1em}Word co-occurrence  $\times$  Gender & 0.00 & 0.26 & {}[-0.78, 0.68] & 1.42\\
 \hspace{1em}Visual strength  $\times$  Gender & 0.18 & 0.49 & {}[-0.01, 1.66] & 1.30\\
-\hspace{1em}Word concreteness  $\times$  Vocabulary size & 0.02 & 0.55 & {}[-1.24, 1.83] & 1.41\\
-\hspace{1em}\makecell[l]{Information uptake  $\times$ \\ \hspace{0.3cm} Distance to word 'abstract'} & -0.06 & 0.19 & {}[-0.70, 0.02] & 1.31\\
 \bottomrule
@@
 Figure \ref{fig:semanticdecision-frequentist-bayesian-plot-allpriors-exgaussian} presents the posterior distribution of each effect in each model.
-The frequentist estimates are also shown to facilitate the comparison with them.
+The frequentist estimates are also shown to facilitate the comparison.
 
@@
 Figure \ref{fig:lexicaldecision-frequentist-bayesian-plot-allpriors-exgaussian} presents the posterior distribution of each effect in each model.
-The frequentist estimates are also shown to facilitate the comparison with them.
+The frequentist estimates are also shown to facilitate the comparison.
 

### 2022-06-29 slides/slides.Rmd
29062022

---
title: "<img src='img/LU logo.jpg' alt='Lancaster University logo' width='130px' style='float:right; margin-top:-5%;'/><br>Language and vision in conceptual processing: Multilevel analysis and statistical power"
subtitle: 'Pablo Bernabeu'
author: 'Supervisors: &nbsp;Dermot Lynott and Louise Connell<br><br>Materials: http://doi.org/10.17605/OSF.IO/UERYQ'
institute: 'Lancaster University'
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      titleSlideClass: [middle, center]
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

---

class: middle, left
layout: true

---

<!-- Load Bootstrap styles -->
<link href="https://cdn.jsdelivr.net/npm/bootstrap@5.0.2/dist/css/bootstrap.min.css" rel="stylesheet" integrity="sha384-EVSTQN3/azprG1Anm3QDgpJLIm9Nao0Yz1ztcQTwFspd3yD65VohhpuuCOmLASjC" crossorigin="anonymous">

<!-- Define CSS styles -->
<style>

.title-slide {
  background-color: #FAFAFC;
}
.title-slide h1,
.title-slide h2,
.title-slide h3,
.title-slide h4 {
  color: black;
  text-shadow: none;
}

/* Disable default striping in tables */
.remark-slide thead, 
.remark-slide tfoot, 
.remark-slide tr:nth-child(even) {
  background: none;
}

</style>

```{r setup, include = FALSE}

options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(cache = FALSE, message = FALSE, warning = FALSE, error = FALSE, 
                      echo = FALSE, knitr.duplicate.label = 'allow', 
                      fig.align = 'center')

library(dplyr)        # data wrangling
library(formattable)  # number formatting
library(kableExtra)   # table formatting

# Move working directory to the project root
knitr::opts_knit$set(root.dir = '../')

```

```{r xaringanExtra, include = FALSE}

xaringanExtra::use_xaringan_extra(c('tile_view', 'share_again', 'scribble',
                                    'logo', 'search', 'fit_screen'))

```

```{r load-functions-data-models, include = FALSE}

# Read in custom functions. Working directory has to be changed, but at the end 
# of this chunk, it is automatically reset to the manuscript.
setwd('R_functions')
sapply(list.files(), source, echo = FALSE)
setwd('../')

# Load main data sets and models. These objects are loaded directly, rather than 
# being run on the go, to keep the knitting of the manuscript reasonably fast. 
# Crucially, however, all the objects can be reproduced from the appropriate R 
# scripts in the current project.

# Study 1: Semantic priming
# Code for data set below in 'semanticpriming/data/data_preparation' folder
semanticpriming = read.csv('semanticpriming/data/final_dataset/semanticpriming.csv')
# Code for models below in 'analysis' folder
semanticpriming_lmerTest =   # Primary model object
  readRDS('semanticpriming/frequentist_analysis/results/semanticpriming_lmerTest.rds')
KR_summary_semanticpriming_lmerTest =   # Model with Kenward-Roger p values
  readRDS('semanticpriming/frequentist_analysis/results/KR_summary_semanticpriming_lmerTest.rds')
confint_semanticpriming_lmerTest =   # Confidence intervals
  readRDS('semanticpriming/frequentist_analysis/results/confint_semanticpriming_lmerTest.rds')

# Study 2: Semantic decision
# Code for data set below in 'semanticdecision/data/data_preparation' folder
semanticdecision = read.csv('semanticdecision/data/final_dataset/semanticdecision.csv')
# Code for models below in 'semanticdecision/frequentist_analysis' folder
semanticdecision_lmerTest =   # Primary model object
  readRDS('semanticdecision/frequentist_analysis/results/semanticdecision_lmerTest.rds')
KR_summary_semanticdecision_lmerTest =   # Model with Kenward-Roger p values
  readRDS('semanticdecision/frequentist_analysis/results/KR_summary_semanticdecision_lmerTest.rds')
confint_semanticdecision_lmerTest =   # Confidence intervals
  readRDS('semanticdecision/frequentist_analysis/results/confint_semanticdecision_lmerTest.rds')

# Study 3: Lexical decision
# Code for data set below in 'lexicaldecision/data/data_preparation' folder
lexicaldecision = read.csv('lexicaldecision/data/final_dataset/lexicaldecision.csv')
# Code for models below in 'lexicaldecision/frequentist_analysis' folder
lexicaldecision_lmerTest =   # Primary model object
  readRDS('lexicaldecision/frequentist_analysis/results/lexicaldecision_lmerTest.rds')
KR_summary_lexicaldecision_lmerTest =   # Model with Kenward-Roger p values
  readRDS('lexicaldecision/frequentist_analysis/results/KR_summary_lexicaldecision_lmerTest.rds')
confint_lexicaldecision_lmerTest =   # Confidence intervals
  readRDS('lexicaldecision/frequentist_analysis/results/confint_lexicaldecision_lmerTest.rds')

```

## Understanding the meaning of words

- Linguistic systems:

--

  - word co-occurrence

  - word association

--

- Embodied systems:

--

  - perceptual

  - motor

  - emotional

  - social

---

## Research question

How are the linguistic and the visual bases of conceptual processing manifested at the levels of participants, words and tasks?

--

- Three studies with large samples

  - semantic priming (Hutchison et al., 2013)

  - semantic decision (Pexman et al., 2017)

  - lexical decision (Balota et al., 2007)

--

- A-priori power analysis for each study

---

#### Main individual differences

  - vocabulary size

--

#### Main word-level variables

  - corpus-based linguistic measure in each study

  - visual strength (Lynott et al., 2020)

---

### Why vision?

Other studies have considered more perceptual modalities, such as hearing, touch, taste and smell (e.g., Bernabeu et al., 2017).

Vision most prominent in the brain (Reilly et al., 2020) and in language (Lynott et al., 2020; Winter et al., 2018).

Individual differences in vision easiest to measure (not present in these studies but planned for next study).

---

### Statistical analysis

#### Lexical covariates

- All possible lexical covariates out of 5 typical candidates:

  - Largest contributors without multicollinearity (*r* < .70) selected

#### Other important covariates for participant-level and word-level variables

- Word concreteness, fluid intelligence

---

## Semantic priming

### Primary data set: Hutchison et al. (2013)

```{r}

# Save number of participants and target_words
semanticpriming_number_participants = length(unique(semanticpriming$Participant))
semanticpriming_number_target_words = length(unique(semanticpriming$target_word))

# Number of target_words per participant
# Save mean as integer and SD rounded while keeping trailing zeros
semanticpriming_mean_target_words_per_participant = 
  semanticpriming %>% group_by(Participant) %>% 
  summarise(length(unique(target_word))) %>% 
  select(2) %>% unlist %>% mean %>% round(0)

semanticpriming_SD_target_words_per_participant = 
  semanticpriming %>% group_by(Participant) %>% 
  summarise(length(unique(target_word))) %>% 
  select(2) %>% unlist %>% sd %>% sprintf('%.2f', .)

# Number of participants per target_word
# Save mean as integer and SD rounded while keeping trailing zeros
semanticpriming_mean_participants_per_target_word = 
  semanticpriming %>% group_by(target_word) %>% 
  summarise(length(unique(Participant))) %>% 
  select(2) %>% unlist %>% mean %>% round(0)

semanticpriming_SD_participants_per_target_word = 
  semanticpriming %>% group_by(target_word) %>% 
  summarise(length(unique(Participant))) %>% 
  select(2) %>% unlist %>% sd %>% sprintf('%.2f', .)

```

- `r semanticpriming_number_participants` participants

- `r semanticpriming_number_target_words` target words

- `r nrow(semanticpriming) %>% formattable::comma(digits = 0)` observations

- `r semanticpriming_mean_target_words_per_participant` target words per participant (*SD* = `r semanticpriming_SD_target_words_per_participant`)

- `r semanticpriming_mean_participants_per_target_word` participants per target word (*SD* = `r semanticpriming_SD_participants_per_target_word`)

---

- Lexical decision = overt task

Over multiple trials, do the characters form a real word?

--

- Semantic priming = covert experimental design

>  <span style='color:blue;'> PRIME WORD  &nbsp; &nbsp;  target word</span>

>  &nbsp; &nbsp; &nbsp; &nbsp; PIKE  &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp;  prack

---

- Primes always real words; targets sometimes nonwords

  - Lexical decision on the target word (i.e., word or nonword?)

- Prime word: 150 ms

--

Interstimulus interval: 50 or 1,050 ms

Target word: until response or 3,000 ms

--

Linguistic information usually more influential than visual information

<div class='p-3 mb-2 bg-light text-dark' style='background-image: var(--bs-gradient);'>(Lam et al., 2015; Petilli et al., 2021)</div>

---

```{r rename-semanticpriming-effects, results = 'asis'}

# Rename effects using plain language and specify the random 
# slopes that were included. This is first done with the 
# main summary of the model (KR_summary...) and then with 
# the confidence intervals (confint...).

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_attentional_control'] =
  'Attentional control'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_vocabulary_size'] =
  'Vocabulary size <sup>a</sup>'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_recoded_participant_gender'] =
  'Gender <sup>a</sup>'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_target_word_frequency'] =
  'Word frequency'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_target_number_syllables'] =
  'Number of syllables'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_word_concreteness_diff'] =
  'Word-concreteness difference'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_cosine_similarity'] =
  'Cosine similarity <sup>a</sup>'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_visual_rating_diff'] =
  'Visual-strength difference <sup>a</sup>'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_recoded_interstimulus_interval'] =
  'Interstimulus interval <sup>a</sup>'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_word_concreteness_diff:z_vocabulary_size'] =
  'Word-concreteness difference : Vocabulary size'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_word_concreteness_diff:z_recoded_interstimulus_interval'] =
  'Word-concreteness difference : Interstimulus interval'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_word_concreteness_diff:z_recoded_participant_gender'] =
  'Word-concreteness difference : Gender'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_attentional_control:z_cosine_similarity'] =
  'Attentional control : Cosine similarity'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_attentional_control:z_visual_rating_diff'] =
  'Attentional control : Visual-strength difference'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_vocabulary_size:z_cosine_similarity'] =
  'Vocabulary size : Cosine similarity'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_vocabulary_size:z_visual_rating_diff'] =
  'Vocabulary size : Visual-strength difference'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_recoded_participant_gender:z_cosine_similarity'] =
  'Gender : Cosine similarity'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_recoded_participant_gender:z_visual_rating_diff'] =
  'Gender : Visual-strength difference'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_recoded_interstimulus_interval:z_cosine_similarity'] =
  'Interstimulus interval : Cosine similarity <sup>a</sup>'

rownames(KR_summary_semanticpriming_lmerTest$coefficients)[
  rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
    'z_recoded_interstimulus_interval:z_visual_rating_diff'] =
  'Interstimulus interval : Visual-strength difference <sup>a</sup>'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_attentional_control'] =
  'Attentional control'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_vocabulary_size'] =
  'Vocabulary size <sup>a</sup>'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_recoded_participant_gender'] =
  'Gender <sup>a</sup>'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_target_word_frequency'] =
  'Word frequency'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_target_number_syllables'] =
  'Number of syllables'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_word_concreteness_diff'] =
  'Word-concreteness difference'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_cosine_similarity'] =
  'Cosine similarity <sup>a</sup>'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_visual_rating_diff'] =
  'Visual-strength difference <sup>a</sup>'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_recoded_interstimulus_interval'] =
  'Interstimulus interval <sup>a</sup>'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_word_concreteness_diff:z_vocabulary_size'] =
  'Word-concreteness difference : Vocabulary size'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_word_concreteness_diff:z_recoded_interstimulus_interval'] =
  'Word-concreteness difference : Interstimulus interval'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_word_concreteness_diff:z_recoded_participant_gender'] =
  'Word-concreteness difference : Gender'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_attentional_control:z_cosine_similarity'] =
  'Attentional control : Cosine similarity'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_attentional_control:z_visual_rating_diff'] =
  'Attentional control : Visual-strength difference'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_vocabulary_size:z_cosine_similarity'] =
  'Vocabulary size : Cosine similarity'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_vocabulary_size:z_visual_rating_diff'] =
  'Vocabulary size : Visual-strength difference'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_recoded_participant_gender:z_cosine_similarity'] =
  'Gender : Cosine similarity'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_recoded_participant_gender:z_visual_rating_diff'] =
  'Gender : Visual-strength difference'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_recoded_interstimulus_interval:z_cosine_similarity'] =
  'Interstimulus interval : Cosine similarity <sup>a</sup>'

rownames(confint_semanticpriming_lmerTest)[
  rownames(confint_semanticpriming_lmerTest) == 
    'z_recoded_interstimulus_interval:z_visual_rating_diff'] =
  'Interstimulus interval : Visual-strength difference <sup>a</sup>'

# Main effects (2/2)

# model_table() is a custom function from the 'R_functions' folder
semanticpriming_maineffects_2 =

  # model_table() is a custom function from the 'R_functions' folder
  model_table(KR_summary_semanticpriming_lmerTest,
              confidence_intervals = confint_semanticpriming_lmerTest,
              select_effects = c('Word-concreteness difference',
                                 'Cosine similarity <sup>a</sup>',
                                 'Visual-strength difference <sup>a</sup>',
                                 'Interstimulus interval <sup>a</sup>'),
              caption = '') %>%

  # Group predictors under headings
  pack_rows('Semantic variables', 1, 3) %>% 
  pack_rows('Task condition', 4, 4) %>%

  # Highlight covariates
  row_spec(1, background = '#EFEFEF') %>%

  footnote(general_title = 'Note. ', 
           general = "Shaded rows contain covariates. Variables involving 'difference' or 'similarity' are based on the comparison of the prime and the target words in each trial.",
           alphabet = c('By-participant random slopes were included for this effect.'),
           footnote_as_chunk = TRUE) %>%

  kable_classic(full_width = F, html_font = 'Cambria')

# Interactions (1/2)

# model_table() is a custom function from the 'R_functions' folder
semanticpriming_interactions_1 =

  # model_table() is a custom function from the 'R_functions' folder
  model_table(KR_summary_semanticpriming_lmerTest, 
              confidence_intervals = confint_semanticpriming_lmerTest,
              select_effects = c('Word-concreteness difference : Vocabulary size',
                                 'Word-concreteness difference : Interstimulus interval',
                                 'Word-concreteness difference : Gender',
                                 'Attentional control : Cosine similarity',
                                 'Attentional control : Visual-strength difference'),
              interaction_symbol_x = TRUE,
              caption = '') %>%

  # Highlight covariates
  row_spec(1:5, background = '#EFEFEF') %>%

  footnote(general_title = 'Note. ', 
           general = "All these interactions are covariates. Variables involving 'difference' or 'similarity' are based on the comparison of the prime and the target words in each trial.",
           footnote_as_chunk = TRUE) %>%

  kable_classic(full_width = F, html_font = 'Cambria')

# Interactions (2/2)

# model_table() is a custom function from the 'R_functions' folder
semanticpriming_interactions_2 =

  # model_table() is a custom function from the 'R_functions' folder
  model_table(KR_summary_semanticpriming_lmerTest, 
              confidence_intervals = confint_semanticpriming_lmerTest,
              select_effects = c('Vocabulary size : Cosine similarity',
                                 'Vocabulary size : Visual-strength difference',
                                 'Gender : Cosine similarity',
                                 'Gender : Visual-strength difference',
                                 'Interstimulus interval : Cosine similarity <sup>a</sup>',
                                 'Interstimulus interval : Visual-strength difference <sup>a</sup>'),
              interaction_symbol_x = TRUE,
              caption = '') %>%

  footnote(general_title = 'Note. ', 
           general = "Variables involving 'difference' or 'similarity' are based on the comparison of the prime and the target words in each trial.",
           alphabet = c('By-participant random slopes were included for this effect.'),
           footnote_as_chunk = TRUE) %>%

  kable_classic(full_width = F, html_font = 'Cambria')

# Calculate R^2. This coefficient must be interpreted with caution 
# (Nakagawa et al., 2017; https://doi.org/10.1098/rsif.2017.0213). 
# Also, transform coefficient to rounded percentage.

Nakagawa2017_fixedeffects_R2_semanticpriming_lmerTest = 
  paste0(
    (MuMIn::r.squaredGLMM(semanticpriming_lmerTest)[1, 'R2m'][[1]] * 100) %>% 
      sprintf('%.2f', .),
    '%')

Nakagawa2017_randomeffects_R2_semanticpriming_lmerTest = 
  paste0(
    (MuMIn::r.squaredGLMM(semanticpriming_lmerTest)[1, 'R2c'][[1]] * 100) %>% 
      sprintf('%.2f', .),
    '%')

```

#### Predictors

.pull-left[

```{r semanticpriming-predictors-1, results = 'asis'}

# model_table() is a custom function from the 'R_functions' folder
model_table(KR_summary_semanticpriming_lmerTest,
            confidence_intervals = confint_semanticpriming_lmerTest,
            select_effects = c('Attentional control',
                               'Vocabulary size <sup>a</sup>',
                               'Gender <sup>a</sup>',
                               'Word frequency',
                               'Number of syllables'),
            caption = '') %>%

  # Display the names of the effects only
  remove_column(2:6) %>%

  # Group predictors under headings
  pack_rows('Individual differences', 2, 4) %>% 
  pack_rows('Lexical covariates', 5, 6) %>%

  # Highlight covariates
  row_spec(c(2, 5:6), background = '#EFEFEF') %>%

  footnote(general_title = 'Note. ', general = "Shaded rows contain covariates.",
           alphabet = c('By-item random slopes were included for this effect.'),
           footnote_as_chunk = TRUE) %>%

  kable_classic(full_width = F, html_font = 'Cambria')

```

]

.pull-right[

```{r semanticpriming-predictors-2, results = 'asis'}

semanticpriming_maineffects_2 %>%
  remove_column(2:6)

```

]

---

<img src='img/Screenshot 2022-02-10 at 08.11.24.png' height='580px'/>

---

#### Results: Main effects (1/2)

```{r semanticpriming-maineffects-1, results = 'asis'}

# model_table() is a custom function from the 'R_functions' folder
model_table(KR_summary_semanticpriming_lmerTest,
            confidence_intervals = confint_semanticpriming_lmerTest,
            select_effects = c('(Intercept)',
                               'Attentional control',
                               'Vocabulary size <sup>a</sup>',
                               'Gender <sup>a</sup>',
                               'Word frequency',
                               'Number of syllables'),
            caption = '') %>%

  # Group predictors under headings
  pack_rows('Individual differences', 2, 4) %>% 
  pack_rows('Lexical covariates', 5, 6) %>%

  # Highlight covariates
  row_spec(c(2, 5:6), background = '#EFEFEF') %>%

  footnote(general_title = 'Note. ', general = "Shaded rows contain covariates.",
           alphabet = c('By-item random slopes were included for this effect.'),
           footnote_as_chunk = TRUE) %>%

  kable_classic(full_width = F, html_font = 'Cambria')

```

---

#### Results: Main effects (2/2)

---

#### Results: Interactions (1/2)

---

#### Results: Interactions (2/2)

---

### Variance explained (Nakagawa et al., 2017)

- the fixed effects explained `r Nakagawa2017_fixedeffects_R2_semanticpriming_lmerTest`

- the random effects explained `r Nakagawa2017_randomeffects_R2_semanticpriming_lmerTest`

---

### Power analysis

---

## Semantic decision

### Primary data set: Pexman et al. (2017)

```{r}

# Save number of participants and words
semanticdecision_number_participants = length(unique(semanticdecision$Participant))
semanticdecision_number_words = length(unique(semanticdecision$Word))

# Number of words per participant
# Save mean as integer and SD rounded while keeping trailing zeros
semanticdecision_mean_words_per_participant = 
  semanticdecision %>% group_by(Participant) %>% 
  summarise(length(unique(Word))) %>% 
  select(2) %>% unlist %>% mean %>% round(0)

semanticdecision_SD_words_per_participant = 
  semanticdecision %>% group_by(Participant) %>% 
  summarise(length(unique(Word))) %>% 
  select(2) %>% unlist %>% sd %>% sprintf('%.2f', .)

# Number of participants per word
# Save mean as integer and SD rounded while keeping trailing zeros
semanticdecision_mean_participants_per_word = 
  semanticdecision %>% group_by(Word) %>% 
  summarise(length(unique(Participant))) %>% 
  select(2) %>% unlist %>% mean %>% round(0)

semanticdecision_SD_participants_per_word = 
  semanticdecision %>% group_by(Word) %>% 
  summarise(length(unique(Participant))) %>% 
  select(2) %>% unlist %>% sd %>% sprintf('%.2f', .)

```

- `r semanticdecision_number_participants` participants

- `r semanticdecision_number_words` words

- `r nrow(semanticdecision) %>% formattable::comma(digits = 0)` observations

- `r semanticdecision_mean_words_per_participant` words per participant (*SD* = `r semanticdecision_SD_words_per_participant`)

- `r semanticdecision_mean_participants_per_word` participants per word (*SD* = `r semanticdecision_SD_participants_per_word`)

---

#### Predictors

<img src='img/Screenshot 2022-02-10 at 08.11.48.png' height='300px'/>

---

<img src='img/Screenshot 2022-02-10 at 08.12.05.png' height='430px'/>

---

#### Results: Main effects (1/2)

```{r semanticdecision-maineffects-1, results = 'asis'}

# Rename effects using plain language and specify the random 
# slopes that were included.

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_information_uptake'] = 
  'Information uptake'

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_vocabulary_size'] = 
  'Vocabulary size <sup>a</sup>'

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_recoded_participant_gender'] =
  'Gender <sup>a</sup>'

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_information_uptake'] = 
  'Information uptake'

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_vocabulary_size'] = 
  'Vocabulary size <sup>a</sup>'

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_recoded_participant_gender'] =
  'Gender <sup>a</sup>'

# model_table() is a custom function from the 'R_functions' folder
model_table(KR_summary_semanticdecision_lmerTest, 
            confidence_intervals = confint_semanticdecision_lmerTest,
            select_effects = c('(Intercept)',
                               'Information uptake',
                               'Vocabulary size <sup>a</sup>',
                               'Gender <sup>a</sup>'),
            caption = '') %>%

  # Group predictors under headings
  pack_rows('Individual differences', 2, 4) %>%

  # Highlight covariates
  row_spec(2, background = '#EFEFEF') %>%

  footnote(general_title = 'Note. ', general = 'Shaded rows contain covariates.',
           alphabet = c('By-item random slopes were included for this effect. '),
           footnote_as_chunk = TRUE) %>%

  kable_classic(full_width = F, html_font = 'Cambria')

```

---

#### Results: Main effects (2/2)

```{r semanticdecision-maineffects-2, results = 'asis'}

# Rename effects using plain language and specify the random 
# slopes that were included.

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_word_frequency'] = 
  'Word frequency'

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_orthographic_Levenshtein_distance'] = 
  'OLD20'

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_word_concreteness'] = 
  'Word concreteness'

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_word_cooccurrence'] = 
  'Word co-occurrence <sup>a</sup>'

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_visual_rating'] =
  'Visual strength <sup>a</sup>'

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_word_frequency'] = 
  'Word frequency'

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_orthographic_Levenshtein_distance'] = 
  'OLD20'

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_word_concreteness'] = 
  'Word concreteness'

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_word_cooccurrence'] = 
  'Word co-occurrence <sup>a</sup>'

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_visual_rating'] =
  'Visual strength <sup>a</sup>'

# model_table() is a custom function from the 'R_functions' folder
model_table(KR_summary_semanticdecision_lmerTest, 
            confidence_intervals = confint_semanticdecision_lmerTest,
            select_effects = c('Word frequency',
                               'OLD20',
                               'Word concreteness',
                               'Word co-occurrence <sup>a</sup>',
                               'Visual strength <sup>a</sup>'),
            caption = '') %>%

  # Group predictors under headings
  pack_rows('Lexical covariates', 1, 2) %>% 
  pack_rows('Semantic variables', 3, 5) %>%

  # Highlight covariates
  row_spec(1:3, background = '#EFEFEF') %>%

  footnote(general_title = 'Note. ', 
           general = 'Shaded rows contain covariates. OLD = Orthographic Levenshtein distance.',
           alphabet = c('By-participant random slopes were included for this effect.'),
           footnote_as_chunk = TRUE) %>%

  kable_classic(full_width = F, html_font = 'Cambria')

```

---

#### Results: Interactions (1/2)

```{r semanticdecision-interactions-1, results = 'asis'}

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_word_concreteness:z_vocabulary_size'] =
  'Word concreteness : Vocabulary size'

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_word_concreteness:z_recoded_participant_gender'] =
  'Word concreteness : Gender'

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_information_uptake:z_word_cooccurrence'] =
  'Information uptake : Word co-occurrence'

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_information_uptake:z_visual_rating'] =
  'Information uptake : Visual strength'

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_word_concreteness:z_vocabulary_size'] =
  'Word concreteness : Vocabulary size'

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_word_concreteness:z_recoded_participant_gender'] =
  'Word concreteness : Gender'

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_information_uptake:z_word_cooccurrence'] =
  'Information uptake : Word co-occurrence'

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_information_uptake:z_visual_rating'] =
  'Information uptake : Visual strength'

# model_table() is a custom function from the 'R_functions' folder
model_table(KR_summary_semanticdecision_lmerTest, 
            confidence_intervals = confint_semanticdecision_lmerTest,
            select_effects = c('Word concreteness : Vocabulary size',
                               'Word concreteness : Gender',
                               'Information uptake : Word co-occurrence',
                               'Information uptake : Visual strength'),
            interaction_symbol_x = TRUE,
            caption = '') %>%

  footnote(general_title = 'Note. ', 
           general = 'All these interactions are covariates.',
           footnote_as_chunk = TRUE) %>%

  # Highlight covariates
  row_spec(1:4, background = '#EFEFEF') %>%

  kable_classic(full_width = F, html_font = 'Cambria')

```

---

#### Results: Interactions (2/2)

```{r semanticdecision-interactions-2, results = 'asis'}

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_vocabulary_size:z_word_cooccurrence'] =
  'Vocabulary size : Word co-occurrence'

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_vocabulary_size:z_visual_rating'] =
  'Vocabulary size : Visual strength'

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_recoded_participant_gender:z_word_cooccurrence'] =
  'Gender : Word co-occurrence'

rownames(KR_summary_semanticdecision_lmerTest$coefficients)[
  rownames(KR_summary_semanticdecision_lmerTest$coefficients) == 
    'z_recoded_participant_gender:z_visual_rating'] =
  'Gender : Visual strength'

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_vocabulary_size:z_word_cooccurrence'] =
  'Vocabulary size : Word co-occurrence'

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_vocabulary_size:z_visual_rating'] =
  'Vocabulary size : Visual strength'

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_recoded_participant_gender:z_word_cooccurrence'] =
  'Gender : Word co-occurrence'

rownames(confint_semanticdecision_lmerTest)[
  rownames(confint_semanticdecision_lmerTest) == 
    'z_recoded_participant_gender:z_visual_rating'] =
  'Gender : Visual strength'

# model_table() is a custom function from the 'R_functions' folder
model_table(KR_summary_semanticdecision_lmerTest, 
            confidence_intervals = confint_semanticdecision_lmerTest,
            select_effects = c('Vocabulary size : Word co-occurrence',
                               'Vocabulary size : Visual strength',
                               'Gender : Word co-occurrence',
                               'Gender : Visual strength'),
            interaction_symbol_x = TRUE, 
            caption = '') %>%

  kable_classic(full_width = F, html_font = 'Cambria')

# Calculate R^2. This coefficient must be interpreted with caution 
# (Nakagawa et al., 2017; https://doi.org/10.1098/rsif.2017.0213). 
# Also, transform coefficient to rounded percentage.

Nakagawa2017_fixedeffects_R2_semanticdecision_lmerTest = 
  paste0(
    (MuMIn::r.squaredGLMM(semanticdecision_lmerTest)[1, 'R2m'][[1]] * 100) %>% 
      sprintf('%.2f', .),
    '%')

Nakagawa2017_randomeffects_R2_semanticdecision_lmerTest = 
  paste0(
    (MuMIn::r.squaredGLMM(semanticdecision_lmerTest)[1, 'R2c'][[1]] * 100) %>% 
      sprintf('%.2f', .),
    '%')

```

---

### Variance explained (Nakagawa et al., 2017)

- the fixed effects explained `r Nakagawa2017_fixedeffects_R2_semanticdecision_lmerTest`

- the random effects explained `r Nakagawa2017_randomeffects_R2_semanticdecision_lmerTest`

---

### Interactions

```{r}

# Run plot through source() rather than directly in this R Markdown document 
# to preserve the italics in the legend.

source('semanticpriming/frequentist_analysis/semanticpriming-interaction-vocabulary-cosinesimilarity.R', 
       local = TRUE)

include_graphics(
  paste0(
    getwd(),  # Keeping illegal characters out of include_graphics()
    '/semanticpriming/frequentist_analysis/plots/semanticpriming-interaction-vocabulary-cosinesimilarity.pdf'
  ))

```

---

### Power analysis

---

## Lexical decision

### Primary data set: Balota et al. (2007)

```{r}

# Save number of participants and words
lexicaldecision_number_participants = length(unique(lexicaldecision$Participant))
lexicaldecision_number_words = length(unique(lexicaldecision$word))

# Number of words per participant
# Save mean as integer and SD rounded while keeping trailing zeros
lexicaldecision_mean_words_per_participant = 
  lexicaldecision %>% group_by(Participant) %>% 
  summarise(length(unique(word))) %>% 
  select(2) %>% unlist %>% mean %>% round(0)

lexicaldecision_SD_words_per_participant = 
  lexicaldecision %>% group_by(Participant) %>% 
  summarise(length(unique(word))) %>% 
  select(2) %>% unlist %>% sd %>% sprintf('%.2f', .)

# Number of participants per word
# Save mean as integer and SD rounded while keeping trailing zeros
lexicaldecision_mean_participants_per_word = 
  lexicaldecision %>% group_by(word) %>% 
  summarise(length(unique(Participant))) %>% 
  select(2) %>% unlist %>% mean %>% round(0)

lexicaldecision_SD_participants_per_word = 
  lexicaldecision %>% group_by(word) %>% 
  summarise(length(unique(Participant))) %>% 
  select(2) %>% unlist %>% sd %>% sprintf('%.2f', .)

```

- `r lexicaldecision_number_participants` participants

- `r lexicaldecision_number_words` words

- `r nrow(lexicaldecision) %>% formattable::comma(digits = 0)` observations

- `r lexicaldecision_mean_words_per_participant` words per participant (*SD* = `r lexicaldecision_SD_words_per_participant`)

- `r lexicaldecision_mean_participants_per_word` participants per word (*SD* = `r lexicaldecision_SD_participants_per_word`)

---

#### Predictors

<img src='img/Screenshot 2022-02-10 at 08.12.25.png' height='270px'/>

---

<img src='img/Screenshot 2022-02-10 at 08.12.37.png' height='400px'/>

---

#### Results: Main effects

```{r lexicaldecision-maineffects, results = 'asis'}

# Rename effects using plain language and specify the random 
# slopes that were included.

rownames(KR_summary_lexicaldecision_lmerTest$coefficients)[
  rownames(KR_summary_lexicaldecision_lmerTest$coefficients) == 
    'z_vocabulary_age'] =
  'Vocabulary age <sup>a</sup>'

rownames(KR_summary_lexicaldecision_lmerTest$coefficients)[
  rownames(KR_summary_lexicaldecision_lmerTest$coefficients) == 
    'z_recoded_participant_gender'] =
  'Gender <sup>a</sup>'

rownames(KR_summary_lexicaldecision_lmerTest$coefficients)[
  rownames(KR_summary_lexicaldecision_lmerTest$coefficients) == 
    'z_orthographic_Levenshtein_distance'] =
  'OLD20'

rownames(KR_summary_lexicaldecision_lmerTest$coefficients)[
  rownames(KR_summary_lexicaldecision_lmerTest$coefficients) == 
    'z_word_concreteness'] =
  'Word concreteness'

rownames(KR_summary_lexicaldecision_lmerTest$coefficients)[
  rownames(KR_summary_lexicaldecision_lmerTest$coefficients) == 
    'z_word_frequency'] =
  'Word frequency <sup>b</sup>'

rownames(KR_summary_lexicaldecision_lmerTest$coefficients)[
  rownames(KR_summary_lexicaldecision_lmerTest$coefficients) == 
    'z_visual_rating'] =
  'Visual strength <sup>b</sup>'

rownames(confint_lexicaldecision_lmerTest)[
  rownames(confint_lexicaldecision_lmerTest) == 
    'z_vocabulary_age'] =
  'Vocabulary age <sup>a</sup>'

rownames(confint_lexicaldecision_lmerTest)[
  rownames(confint_lexicaldecision_lmerTest) == 
    'z_recoded_participant_gender'] =
  'Gender <sup>a</sup>'

rownames(confint_lexicaldecision_lmerTest)[
  rownames(confint_lexicaldecision_lmerTest) == 
    'z_orthographic_Levenshtein_distance'] =
  'OLD20'

rownames(confint_lexicaldecision_lmerTest)[
  rownames(confint_lexicaldecision_lmerTest) == 
    'z_word_concreteness'] =
  'Word concreteness'

rownames(confint_lexicaldecision_lmerTest)[
  rownames(confint_lexicaldecision_lmerTest) == 
    'z_word_frequency'] =
  'Word frequency <sup>b</sup>'

rownames(confint_lexicaldecision_lmerTest)[
  rownames(confint_lexicaldecision_lmerTest) == 
    'z_visual_rating'] =
  'Visual strength <sup>b</sup>'

# model_table() is a custom function from the 'R_functions' folder
model_table(KR_summary_lexicaldecision_lmerTest, 
            confidence_intervals = confint_lexicaldecision_lmerTest,
            select_effects = c('(Intercept)',
                               'Vocabulary age <sup>a</sup>',
                               'Gender <sup>a</sup>',
                               'OLD20',
                               'Word concreteness',
                               'Word frequency <sup>b</sup>',
                               'Visual strength <sup>b</sup>'),
            caption = '') %>%

  # Group predictors under headings
  pack_rows('Individual differences', 2, 3) %>% 
  pack_rows('Lexical-semantic covariates', 4, 5) %>% 
  pack_rows('Lexical-semantic variables', 6, 7) %>%

  # Highlight covariates
  row_spec(4:5, background = '#EFEFEF') %>%

  footnote(general_title = 'Note. ', 
           general = 'Shaded rows contain covariates. OLD = Orthographic Levenshtein distance.',
           alphabet = c('By-item random slopes were included for this effect. ', 
                        'By-participant random slopes were included for this effect.'),
           footnote_as_chunk = TRUE) %>%

  kable_classic(full_width = F, html_font = 'Cambria')

```

---

#### Results: Interactions

```{r lexicaldecision-interactions, results = 'asis'}

rownames(KR_summary_lexicaldecision_lmerTest$coefficients)[
  rownames(KR_summary_lexicaldecision_lmerTest$coefficients) == 
    'z_word_concreteness:z_vocabulary_age'] =
  'Word concreteness : Vocabulary age'

rownames(KR_summary_lexicaldecision_lmerTest$coefficients)[
  rownames(KR_summary_lexicaldecision_lmerTest$coefficients) == 
    'z_word_concreteness:z_recoded_participant_gender'] =
  'Word concreteness : Gender'

rownames(KR_summary_lexicaldecision_lmerTest$coefficients)[
  rownames(KR_summary_lexicaldecision_lmerTest$coefficients) == 
    'z_vocabulary_age:z_word_frequency'] =
  'Vocabulary age : Word frequency'

rownames(KR_summary_lexicaldecision_lmerTest$coefficients)[
  rownames(KR_summary_lexicaldecision_lmerTest$coefficients) == 
    'z_vocabulary_age:z_visual_rating'] =
  'Vocabulary age : Visual strength'

rownames(KR_summary_lexicaldecision_lmerTest$coefficients)[
  rownames(KR_summary_lexicaldecision_lmerTest$coefficients) == 
    'z_recoded_participant_gender:z_word_frequency'] =
  'Gender : Word frequency'

rownames(KR_summary_lexicaldecision_lmerTest$coefficients)[
  rownames(KR_summary_lexicaldecision_lmerTest$coefficients) == 
    'z_recoded_participant_gender:z_visual_rating'] =
  'Gender : Visual strength'

rownames(confint_lexicaldecision_lmerTest)[
  rownames(confint_lexicaldecision_lmerTest) == 
    'z_word_concreteness:z_vocabulary_age'] =
  'Word concreteness : Vocabulary age'

rownames(confint_lexicaldecision_lmerTest)[
  rownames(confint_lexicaldecision_lmerTest) == 
    'z_word_concreteness:z_recoded_participant_gender'] =
  'Word concreteness : Gender'

rownames(confint_lexicaldecision_lmerTest)[
  rownames(confint_lexicaldecision_lmerTest) == 
    'z_vocabulary_age:z_word_frequency'] =
  'Vocabulary age : Word frequency'

rownames(confint_lexicaldecision_lmerTest)[
  rownames(confint_lexicaldecision_lmerTest) == 
    'z_vocabulary_age:z_visual_rating'] =
  'Vocabulary age : Visual strength'

rownames(confint_lexicaldecision_lmerTest)[
  rownames(confint_lexicaldecision_lmerTest) == 
    'z_recoded_participant_gender:z_word_frequency'] =
  'Gender : Word frequency'

rownames(confint_lexicaldecision_lmerTest)[
  rownames(confint_lexicaldecision_lmerTest) == 
    'z_recoded_participant_gender:z_visual_rating'] =
  'Gender : Visual strength'

model_table(KR_summary_lexicaldecision_lmerTest, 
            confidence_intervals = confint_lexicaldecision_lmerTest,
            select_effects = c('Word concreteness : Vocabulary age',
                              'Word concreteness : Gender',
                              'Vocabulary age : Word frequency',
                              'Vocabulary age : Visual strength',
                              'Gender : Word frequency',
                              'Gender : Visual strength'),
            interaction_symbol_x = TRUE,
            caption = '') %>%

  footnote(general_title = 'Note. ', 
           general = 'Shaded rows contain covariates.',
           footnote_as_chunk = TRUE) %>%

  # Highlight covariates
  row_spec(1:2, background = '#EFEFEF') %>%

  kable_classic(full_width = F, html_font = 'Cambria')

# Calculate R^2. This coefficient must be interpreted with caution 
# (Nakagawa et al., 2017; https://doi.org/10.1098/rsif.2017.0213). 
# Also, transform coefficient to rounded percentage.

Nakagawa2017_fixedeffects_R2_lexicaldecision_lmerTest = 
  paste0(
    (MuMIn::r.squaredGLMM(lexicaldecision_lmerTest)[1, 'R2m'][[1]] * 100) %>% 
      sprintf('%.2f', .),
    '%')

Nakagawa2017_randomeffects_R2_lexicaldecision_lmerTest = 
  paste0(
    (MuMIn::r.squaredGLMM(lexicaldecision_lmerTest)[1, 'R2c'][[1]] * 100) %>% 
      sprintf('%.2f', .),
    '%')

```

---

### Variance explained (Nakagawa et al., 2017)

- the fixed effects explained `r Nakagawa2017_fixedeffects_R2_lexicaldecision_lmerTest`

- the random effects explained `r Nakagawa2017_randomeffects_R2_lexicaldecision_lmerTest`

---

### Power analysis

---

# References

Albers, C., & Lakens, D. (2018). When power analyses based on pilot data are biased: Inaccurate effect size estimators and follow-up bias. *Journal of Experimental Social Psychology, 74*, 187–195. https://doi.org/10.1016/j.jesp.2017.09.004

Balota, D. A., Yap, M. J., Hutchison, K. A., Cortese, M. J., Kessler, B., Loftis, B., Neely, J. H., Nelson, D. L., Simpson, G. B., & Treiman, R. (2007). The English Lexicon Project. *Behavior Research Methods, 39*, 445–459. https://doi.org/10.3758/BF03193014

Bernabeu, P., Lynott, D., & Connell, L. (2021). Preregistration: *The interplay between linguistic and embodied systems in conceptual processing*. OSF. https://osf.io/ftydw/

Bernabeu, P., Willems, R. M., & Louwerse, M. M. (2017). Modality switch effects emerge early and increase throughout conceptual processing: Evidence from ERPs. In G. Gunzelmann, A. Howes, T. Tenbrink, & E. J. Davelaar (Eds.), *Proceedings of the 39th Annual Conference of the Cognitive Science Society* (pp. 1629-1634). Austin, TX: Cognitive Science Society. https://mindmodeling.org/cogsci2017/papers/0318

---

Brauer, M., & Curtin, J. J. (2018). Linear mixed-effects models and the analysis of nonindependent data: A unified framework to analyze categorical and continuous independent variables that vary within-subjects and/or within-items. *Psychological Methods, 23*(3), 389–411. https://doi.org/10.1037/met0000159

Hutchison, K. A., Balota, D. A., Neely, J. H., Cortese, M. J., Cohen-Shikora, E. R., Tse, C.-S., Yap, M. J., Bengson, J. J., Niemeyer, D., & Buchanan, E. (2013). The semantic priming project. *Behavior Research Methods, 45*, 1099–1114. https://doi.org/10.3758/s13428-012-0304-z

Lam, K. J., Dijkstra, T., & Rueschemeyer, S. A. (2015). Feature activation during word recognition: Action, visual, and associative-semantic priming effects. *Frontiers in Psychology, 6*, 659. https://doi.org/10.3389/fpsyg.2015.00659

Loken, E., & Gelman, A. (2017). Measurement error and the replication crisis. *Science, 355*(6325), 584-585. https://doi.org/10.1126/science.aal3618

Luke, S. G. (2017). Evaluating significance in linear mixed-effects models in R. *Behavior Research Methods, 49*(4), 1494–1502. https://doi.org/10.3758/s13428-016-0809-y

---

Lynott, D., Connell, L., Brysbaert, M., Brand, J., & Carney, J. (2020). The Lancaster Sensorimotor Norms: Multidimensional measures of perceptual and action strength for 40,000 English words. *Behavior Research Methods, 52*, 1271–1291. https://doi.org/10.3758/s13428-019-01316-z.

Petilli, M. A., Günther, F., Vergallito, A., Ciapparelli, M., & Marelli, M. (2021). Data-driven computational models reveal perceptual simulation in word processing. *Journal of Memory and Language, 117*, 104194. https://doi.org/10.1016/j.jml.2020.104194

Pexman, P. M., Heard, A., Lloyd, E., & Yap, M. J. (2017). The Calgary semantic decision project: Concrete/abstract decision data for 10,000 English words. *Behavior Research Methods, 49*(2), 407–417. https://doi.org/10.3758/s13428-016-0720-6

Pexman, P. M., & Yap, M. J. (2018). Individual differences in semantic processing: Insights from the Calgary semantic decision project. *Journal of Experimental Psychology: Learning, Memory, and Cognition, 44*(7), 1091–1112. https://doi.org/10.1037/xlm0000499

---

Reilly, J., Flurie, M., & Peelle, J. E. (2020). The English lexicon mirrors functional brain
activation for a sensory hierarchy dominated by vision and audition: Point-counterpoint. *Journal of Neurolinguistics, 55*, 100895. https://doi.org/10.1016/j.jneuroling.2020.100895

Singmann, H., & Kellen, D. (2019). *An Introduction to Mixed Models for Experimental Psychology*. In D. H. Spieler & E. Schumacher (Eds.), New Methods in Cognitive Psychology (pp. 4--31). Hove, UK: Psychology Press. http://singmann.org/download/publications/singmann_kellen-introduction-mixed-models.pdf

Tulving, E. (2007). Are There 256 Different Kinds of Memory? In J. S. Nairne (Ed.), *The foundations of remembering: Essays in honor of Henry L. Roediger, III* (p. 39–52). Psychology Press.

Wingfield, C., & Connell, L. (2019). *Understanding the role of linguistic distributional knowledge in cognition.* PsyArXiv. https://doi.org/10.31234/osf.io/hpm4z

---

Yap, M. J., Balota, D. A., Sibley, D. E., & Ratcliff, R. (2012). Individual differences in visual word recognition: Insights from the English Lexicon Project. *Journal of Experimental Psychology: Human Perception and Performance*, 38, 1, 53–79. https://doi.org/10.1037/a0024177

Yap, M. J., Hutchison, K. A., & Tan, L. C. (2017). Individual differences in semantic priming performance: Insights from the semantic priming project. In M. N. Jones (Ed.), *Frontiers of cognitive psychology. Big data in cognitive science* (p. 203–226). Routledge/Taylor & Francis Group.

Yap, M. J., Tse, C.-S., & Balota, D. A. (2009). Individual differences in the joint effects of semantic priming and word frequency revealed by RT distributional analyses: The role of lexical integrity. *Journal of Memory and Language, 61*(3), 303–325. https://doi.org/10.1016/j.jml.2009.07.001

Winter, B., Perlman, M., & Majid, A. (2018). Vision dominates in perceptual language: English sensory vocabulary is optimized for usage. *Cognition, 179*, 213–220. https://doi.org/10.1016/j.cognition.2018.05.008

### 2022-06-29 R_functions/alias_interaction_plot.R

@@ -22,8 +22,8 @@
 #   fill_title = 'Gender'
 # )
 
-# Note: if you wished to verify the accuracy of these involved plots, 
-# you could use sjPlot::plot_model() to obtain more basic versions.
+# Note: should you wish to verify the accuracy of these involved plots, 
+# you could use sjPlot::plot_model() to produce simpler versions.
 
 #################################
 
@@ -54,8 +54,8 @@ alias_interaction_plot =
     # `fill_nesting_factor` to `fill_alias`
     if(!is.null(fill_nesting_factor)) {
       
-      # Proceed only if the `fill` and the `fill_alias` variables contain 
-      # the same number of unique values.
+      # Proceed only if the `fill` and the `fill_alias` variables 
+      # contain the same number of unique values.
       if(identical(n_distinct(model_df[,fill]), 
                    n_distinct(model_df[,fill_alias]))) {
         
@@ -76,13 +76,13 @@ alias_interaction_plot =
         model_df = as.data.frame(model_df)
         
         # If the `fill` and the `fill_alias` variables do not contain the
-        # same number of unique values, warn that`fill_nesting_factor` will 
-        # be ignored.
+        # same number of unique values, warn that`fill_nesting_factor` 
+        # will be ignored.
       } else {
         message(
           paste('The argument `fill_nesting_factor` has been ignored, as it requires', 
-                'that the `fill` variable contain the same number of unique', 
-                'values as the `fill_alias` variable.',
+                'that the `fill` variable contain the same number of unique values', 
+                'as the `fill_alias` variable.',
                 sep = '\n')
         )
       }
@@ -112,8 +112,7 @@ alias_interaction_plot =
       # unique values, assign values of `fill_alias` to `fill`, format it 
       # as a factor, and create fill labels directly from its levels.
     } else {
-      model@frame[,fill] = model@frame[,fill_alias]
-      model@frame[,fill] = as.factor(model@frame[,fill])
+      model@frame[,fill] = as.factor(model@frame[,fill_alias])
       fill_labels = levels(model@frame[,fill])
     }
     
@@ -130,7 +129,9 @@ alias_interaction_plot =
     if(is.null(fill_title)) fill_title = fill
     
     # Plot
+    
     plot_model(model, type = 'pred', terms = c(x, fill), ci.lvl = .95) +
+      
       geom_point(show.legend = FALSE) + 
       scale_x_continuous(expand = expansion(mult = c(.01, .01))) + 
[…]

### 2022-06-29 R_functions/frequentist_bayesian_plot.R

@@ -17,7 +17,7 @@ frequentist_bayesian_plot =
             # Number of columns into which the legend labels (i.e., 
             # 'Frequentist analysis', 'Bayesian analysis') should 
             # be distributed.
-            legend_columns = 2,
+            legend_ncol = 2,
             
             # If note_frequentist_no_prior = TRUE, '(no prior)' is appended to the
             # label 'Frequentist analysis' in the legend. This is useful when
@@ -118,40 +118,44 @@ frequentist_bayesian_plot =
       
       theme_minimal() +
       theme(text = element_text(family = 'Arial'),  # <-- prevent R crashing (see https://discourse.mc-stan.org/t/error-code-when-using-pp-check-with-brms/27419/4) 
-            plot.title = element_markdown(colour = '#005b96', hjust = 0.5, vjust = 1),
+            plot.title = element_markdown(colour = '#005b96', hjust = 0.5, vjust = 1,
+                                          size = font_size * 1.2),
             axis.title.x = ggtext::element_markdown(size = font_size, 
                                                     margin = margin(t = font_size * 0.8)), 
             axis.text.x = element_text(size = font_size * 0.9, 
                                        margin = margin(t = font_size * 0.4)), 
             axis.title.y = element_blank(), 
-            axis.text.y = ggtext::element_markdown(size = font_size, vjust = 0),  # Place label at the foot of each band, to fit with format of plot.
+            # Use 'vjust' used to place each Y axis label at the foot of its respective segment
+            axis.text.y = ggtext::element_markdown(size = font_size, vjust = 0),  
             axis.ticks.x = element_line(), 
-            legend.text = element_text(lineheight = 1.2, size = font_size, 
-                                       margin = margin(r = 4)),
-            legend.key.height = unit(ifelse(legend_columns==1, 17, 25), 'pt'),
-            legend.background = element_rect(colour = 'grey82', fill = 'white'),
+            # Parameters are adjusted based on number of columns in legend using ifelse()
+            legend.text = element_text(size = font_size,
+                                       lineheight = ifelse(legend_ncol == 1, 0.3, 1.2), 
+                                       margin = margin(r = ifelse(legend_ncol == 1, 2, 4))),
+            legend.key.height = unit(ifelse(legend_ncol == 1, 15, 21), 'pt'),
+            legend.background = element_rect(colour = 'grey70', fill = 'white'),
             panel.grid.major.y = element_line(colour = 'grey90'),
             plot.margin = margin(9, 4, 14, 12))
     
[…]

### 2022-06-29 lexicaldecision/bayesian_analysis/divergent_models/lexicaldecision_brms_informativepriors_exgaussian.R

@@ -75,12 +75,12 @@ lexicaldecision_brms_informativepriors_exgaussian =
       # https://psych.wisc.edu/Brauer/BrauerLab/wp-content/uploads/2014/04/Brauer-Curtin-2018-on-LMEMs.pdf).
       # Interactions only require random slopes if all variables involved vary within the same units.
       
-      # By-subject random slopes
+      # By-participant random slopes
       (z_word_frequency + z_visual_rating + 
          z_orthographic_Levenshtein_distance + 
          z_word_concreteness | Participant) +
       
-      # By-item random slopes
+      # By-word random slopes
       (z_vocabulary_age + z_recoded_participant_gender | word),
     
     data = lexicaldecision, prior = informative_priors,

### 2022-06-29 lexicaldecision/bayesian_analysis/divergent_models/lexicaldecision_brms_weaklyinformativepriors_exgaussian.R

@@ -75,12 +75,12 @@ lexicaldecision_brms_weaklyinformativepriors_exgaussian =
       # https://psych.wisc.edu/Brauer/BrauerLab/wp-content/uploads/2014/04/Brauer-Curtin-2018-on-LMEMs.pdf).
       # Interactions only require random slopes if all variables involved vary within the same units.
       
-      # By-subject random slopes
+      # By-participant random slopes
       (z_word_frequency + z_visual_rating + 
          z_orthographic_Levenshtein_distance + 
          z_word_concreteness | Participant) +
       
-      # By-item random slopes
+      # By-word random slopes
       (z_vocabulary_age + z_recoded_participant_gender | word),
     
     data = lexicaldecision, prior = weaklyinformative_priors,

### 2022-06-29 lexicaldecision/bayesian_analysis/lexicaldecision_brms_diffusepriors_exgaussian.R

@@ -75,12 +75,12 @@ lexicaldecision_brms_diffusepriors_exgaussian =
       # https://psych.wisc.edu/Brauer/BrauerLab/wp-content/uploads/2014/04/Brauer-Curtin-2018-on-LMEMs.pdf).
       # Interactions only require random slopes if all variables involved vary within the same units.
       
-      # By-subject random slopes
+      # By-participant random slopes
       (z_word_frequency + z_visual_rating + 
          z_orthographic_Levenshtein_distance + 
          z_word_concreteness | Participant) +
       
-      # By-item random slopes
+      # By-word random slopes
       (z_vocabulary_age + z_recoded_participant_gender | word),
     
     data = lexicaldecision, prior = diffuse_priors,

### 2022-06-29 lexicaldecision/bayesian_analysis/prior_predictive_checks/lexicaldecision_priorpredictivecheck_diffusepriors.R

@@ -74,12 +74,12 @@ get_prior(
     # In the random slopes below, `0 +` helps avoid redundant random intercepts
     # (background: https://github.com/lme4/lme4/issues/625)
     
-    # By-subject random slopes
+    # By-participant random slopes
     (0 + z_word_frequency | Participant) + (0 + z_visual_rating | Participant) +
     (0 + z_orthographic_Levenshtein_distance | Participant) +
     (0 + z_word_concreteness | Participant) +
     
-    # By-item random slopes
+    # By-word random slopes
     (0 + z_vocabulary_age | word) + (0 + z_recoded_participant_gender | word),
   
   data = lexicaldecision
@@ -159,12 +159,12 @@ sampleonly_lexicaldecision_brms_diffusepriors =
       
       # In the random slopes below, `0 +` helps avoid redundant random intercepts.
       
-      # By-subject random slopes
+      # By-participant random slopes
       (0 + z_word_frequency | Participant) + (0 + z_visual_rating | Participant) +
       (0 + z_orthographic_Levenshtein_distance | Participant) +
       (0 + z_word_concreteness | Participant) +
       
-      # By-item random slopes
+      # By-word random slopes
       (0 + z_vocabulary_age | word) + (0 + z_recoded_participant_gender | word),
     
     data = lexicaldecision, prior = diffuse_priors,

### 2022-06-29 lexicaldecision/bayesian_analysis/prior_predictive_checks/lexicaldecision_priorpredictivecheck_diffusepriors_exgaussian.R

@@ -74,12 +74,12 @@ get_prior(
     # In the random slopes below, `0 +` helps avoid redundant random intercepts
     # (background: https://github.com/lme4/lme4/issues/625)
     
-    # By-subject random slopes
+    # By-participant random slopes
     (0 + z_word_frequency | Participant) + (0 + z_visual_rating | Participant) +
     (0 + z_orthographic_Levenshtein_distance | Participant) +
     (0 + z_word_concreteness | Participant) +
     
-    # By-item random slopes
+    # By-word random slopes
     (0 + z_vocabulary_age | word) + (0 + z_recoded_participant_gender | word),
   
   data = lexicaldecision,
@@ -169,12 +169,12 @@ sampleonly_lexicaldecision_brms_diffusepriors =
       
       # In the random slopes below, `0 +` helps avoid redundant random intercepts.
       
-      # By-subject random slopes
+      # By-participant random slopes
       (0 + z_word_frequency | Participant) + (0 + z_visual_rating | Participant) +
       (0 + z_orthographic_Levenshtein_distance | Participant) +
       (0 + z_word_concreteness | Participant) +
       
-      # By-item random slopes
+      # By-word random slopes
       (0 + z_vocabulary_age | word) + (0 + z_recoded_participant_gender | word),
     
     data = lexicaldecision, prior = diffuse_priors,

### 2022-06-29 lexicaldecision/bayesian_analysis/prior_predictive_checks/lexicaldecision_priorpredictivecheck_informativepriors.R

@@ -74,12 +74,12 @@ get_prior(
     # In the random slopes below, `0 +` helps avoid redundant random intercepts
     # (background: https://github.com/lme4/lme4/issues/625)
     
-    # By-subject random slopes
+    # By-participant random slopes
     (0 + z_word_frequency | Participant) + (0 + z_visual_rating | Participant) +
     (0 + z_orthographic_Levenshtein_distance | Participant) +
     (0 + z_word_concreteness | Participant) +
     
-    # By-item random slopes
+    # By-word random slopes
     (0 + z_vocabulary_age | word) + (0 + z_recoded_participant_gender | word),
   
   data = lexicaldecision
@@ -159,12 +159,12 @@ sampleonly_lexicaldecision_brms_informativepriors =
       
       # In the random slopes below, `0 +` helps avoid redundant random intercepts.
       
-      # By-subject random slopes
+      # By-participant random slopes
       (0 + z_word_frequency | Participant) + (0 + z_visual_rating | Participant) +
       (0 + z_orthographic_Levenshtein_distance | Participant) +
       (0 + z_word_concreteness | Participant) +
       
-      # By-item random slopes
+      # By-word random slopes
       (0 + z_vocabulary_age | word) + (0 + z_recoded_participant_gender | word),
     
     data = lexicaldecision, prior = informative_priors,

### 2022-06-29 lexicaldecision/bayesian_analysis/prior_predictive_checks/lexicaldecision_priorpredictivecheck_informativepriors_exgaussian.R

@@ -74,12 +74,12 @@ get_prior(
     # In the random slopes below, `0 +` helps avoid redundant random intercepts
     # (background: https://github.com/lme4/lme4/issues/625)
     
-    # By-subject random slopes
+    # By-participant random slopes
     (0 + z_word_frequency | Participant) + (0 + z_visual_rating | Participant) +
     (0 + z_orthographic_Levenshtein_distance | Participant) +
     (0 + z_word_concreteness | Participant) +
     
-    # By-item random slopes
+    # By-word random slopes
     (0 + z_vocabulary_age | word) + (0 + z_recoded_participant_gender | word),
   
   data = lexicaldecision,
@@ -169,12 +169,12 @@ sampleonly_lexicaldecision_brms_informativepriors =
       
       # In the random slopes below, `0 +` helps avoid redundant random intercepts.
       
-      # By-subject random slopes
+      # By-participant random slopes
       (0 + z_word_frequency | Participant) + (0 + z_visual_rating | Participant) +
       (0 + z_orthographic_Levenshtein_distance | Participant) +
       (0 + z_word_concreteness | Participant) +
       
-      # By-item random slopes
+      # By-word random slopes
       (0 + z_vocabulary_age | word) + (0 + z_recoded_participant_gender | word),
     
     data = lexicaldecision, prior = informative_priors,

### 2022-06-29 lexicaldecision/frequentist_bayesian_plots/lexicaldecision_frequentist_bayesian_plots.R

@@ -77,7 +77,7 @@ new_labels =
   # the code below moves those word-level variables (with their new names) to 
   # the first position in their interactions. Note that the order does not 
   # affect the results in any way.
-  sub("'(\\w+.*):(Word frequency|Visual strength)'", '\\2:\\1', .) %>%
+  sub('(\\w+.*):(Word frequency|Visual strength)', '\\2:\\1', .) %>%
   
   # Replace colons denoting interactions with times symbols
   str_replace(pattern = ':', replacement = ' &times; ')
@@ -90,7 +90,7 @@ plot_lexicaldecision_frequentist_bayesian_plot_informativepriors_exgaussian =
                             confint_lexicaldecision_lmerTest,
                             lexicaldecision_posteriordistributions_informativepriors_exgaussian,
                             labels = new_labels, interaction_symbol_x = TRUE,
-                            vertical_line_at_x = 0, x_title = 'Predicted RT (*z*)', 
+                            vertical_line_at_x = 0, x_title = 'Effect size (&beta;)', 
                             note_frequentist_no_prior = TRUE) +
   ggtitle('Prior *SD* = 0.1')
 
@@ -101,8 +101,8 @@ plot_lexicaldecision_frequentist_bayesian_plot_informativepriors_exgaussian =
                             confint_lexicaldecision_lmerTest,
                             lexicaldecision_posteriordistributions_weaklyinformativepriors_exgaussian,
                             labels = new_labels, interaction_symbol_x = TRUE,
-                            vertical_line_at_x = 0, x_title = 'Predicted RT (*z*)',
-                            legend_columns = 1) + 
+                            vertical_line_at_x = 0, x_title = 'Effect size (&beta;)',
+                            legend_ncol = 1) + 
     theme(legend.position = 'bottom') ) %>%
   ggsave(filename = 'lexicaldecision/frequentist_bayesian_plots/plots/lexicaldecision_frequentist_bayesian_plot_weaklyinformativepriors_exgaussian.pdf',
          device = cairo_pdf, width = 5.4, height = 6, dpi = 900)
@@ -113,7 +113,7 @@ plot_lexicaldecision_frequentist_bayesian_plot_weaklyinformativepriors_exgaussia
                             confint_lexicaldecision_lmerTest,
                             lexicaldecision_posteriordistributions_weaklyinformativepriors_exgaussian,
[…]

### 2022-06-29 semanticdecision/bayesian_analysis/divergent_models/semanticdecision_brms_weaklyinformativepriors_exgaussian.R

@@ -83,28 +83,28 @@ semanticdecision_brms_weaklyinformativepriors_exgaussian =
       # https://psych.wisc.edu/Brauer/BrauerLab/wp-content/uploads/2014/04/Brauer-Curtin-2018-on-LMEMs.pdf).
       # Interactions only require random slopes if all variables involved vary within the same units.
       
-      # By-subject random slopes
+      # By-participant random slopes
       
-      # Below, the random slopes for controlled covariates (i.e., 'z_word_frequency', 
+      # Below, the random slopes for control covariates (i.e., 'z_word_frequency', 
       # 'z_orthographic_Levenshtein_distance' and 'z_word_concreteness') were removed 
       # due to non-convergence, inspired by Remedy 11 from Table 17 in Brauer and 
       # Curtin (2018). However, whereas Brauer and Curtin constrain such a removal 
       # to cases in which the covariate does not interact with any effects of 
       # interest, the random slopes for 'z_word_concreteness' were removed below 
       # because the interactions between this covariate and the effects of interest 
-      # were controlled covariates, not interactions of interest. That is, they 
+      # were control covariates, not interactions of interest. That is, they 
       # were not critical to the research question.
     
     (z_word_cooccurrence + z_visual_rating | Participant) +
       
-      # By-item random slopes
+      # By-word random slopes
       
-      # Below, the random slopes for the controlled covariate (i.e., 'z_information_uptake') 
+      # Below, the random slopes for the control covariate (i.e., 'z_information_uptake') 
       # were removed due to non-convergence, inspired by Remedy 11 from Table 17 in Brauer 
       # and Curtin (2018). However, whereas Brauer and Curtin constrained such a removal to 
       # cases in which the covariate does not interact with any effects of interest, the 
       # random slopes for 'z_information_uptake' were removed below because the interactions 
-      # between this covariate and the effects of interest were controlled covariates, not 
+      # between this covariate and the effects of interest were control covariates, not 
       # interactions of interest. That is, they were not critical to the research question.
       
     (z_vocabulary_size + z_recoded_participant_gender | Word),

### 2022-06-29 semanticdecision/bayesian_analysis/prior_predictive_checks/semanticdecision_priorpredictivecheck_diffusepriors.R

@@ -82,14 +82,14 @@ get_prior(
     # In the random slopes below, `0 +` helps avoid redundant random intercepts
     # (background: https://github.com/lme4/lme4/issues/625)
     
-    # By-subject random slopes
+    # By-participant random slopes
     (0 + z_word_cooccurrence | Participant) +
     (0 + z_visual_rating | Participant) +
     (0 + z_word_frequency | Participant) +
     (0 + z_orthographic_Levenshtein_distance | Participant) +
     (0 + z_word_concreteness | Participant) +
     
-    # By-item random slopes
+    # By-word random slopes
     (0 + z_vocabulary_size | Word) +
     (0 + z_recoded_participant_gender | Word) +
     (0 + z_information_uptake | Word),
@@ -180,14 +180,14 @@ sampleonly_semanticdecision_brms_diffusepriors =
       # In the random slopes below, `0 +` helps avoid redundant random intercepts
       # (background: https://github.com/lme4/lme4/issues/625)
       
-      # By-subject random slopes
+      # By-participant random slopes
       (0 + z_word_cooccurrence | Participant) +
       (0 + z_visual_rating | Participant) +
       (0 + z_word_frequency | Participant) +
       (0 + z_orthographic_Levenshtein_distance | Participant) +
       (0 + z_word_concreteness | Participant) +
       
-      # By-item random slopes
+      # By-word random slopes
       (0 + z_vocabulary_size | Word) +
       (0 + z_recoded_participant_gender | Word) +
       (0 + z_information_uptake | Word),

### 2022-06-29 semanticdecision/bayesian_analysis/prior_predictive_checks/semanticdecision_priorpredictivecheck_informativepriors.R

@@ -82,14 +82,14 @@ get_prior(
     # In the random slopes below, `0 +` helps avoid redundant random intercepts
     # (background: https://github.com/lme4/lme4/issues/625)
     
-    # By-subject random slopes
+    # By-participant random slopes
     (0 + z_word_cooccurrence | Participant) +
     (0 + z_visual_rating | Participant) +
     (0 + z_word_frequency | Participant) +
     (0 + z_orthographic_Levenshtein_distance | Participant) +
     (0 + z_word_concreteness | Participant) +
     
-    # By-item random slopes
+    # By-word random slopes
     (0 + z_vocabulary_size | Word) +
     (0 + z_recoded_participant_gender | Word) +
     (0 + z_information_uptake | Word),
@@ -180,14 +180,14 @@ sampleonly_semanticdecision_brms_informativepriors =
       # In the random slopes below, `0 +` helps avoid redundant random intercepts 
       # (background: https://github.com/lme4/lme4/issues/625)
       
-      # By-subject random slopes
+      # By-participant random slopes
       (0 + z_word_cooccurrence | Participant) + 
       (0 + z_visual_rating | Participant) +
       (0 + z_word_frequency | Participant) +
       (0 + z_orthographic_Levenshtein_distance | Participant) +
       (0 + z_word_concreteness | Participant) +
       
-      # By-item random slopes
+      # By-word random slopes
       (0 + z_vocabulary_size | Word) + 
       (0 + z_recoded_participant_gender | Word) +
       (0 + z_information_uptake | Word),

### 2022-06-29 semanticdecision/bayesian_analysis/semanticdecision_brms_informativepriors_exgaussian.R

@@ -83,28 +83,28 @@ semanticdecision_brms_informativepriors_exgaussian =
       # https://psych.wisc.edu/Brauer/BrauerLab/wp-content/uploads/2014/04/Brauer-Curtin-2018-on-LMEMs.pdf).
       # Interactions only require random slopes if all variables involved vary within the same units.
       
-      # By-subject random slopes
+      # By-participant random slopes
       
-      # Below, the random slopes for controlled covariates (i.e., 'z_word_frequency', 
+      # Below, the random slopes for control covariates (i.e., 'z_word_frequency', 
       # 'z_orthographic_Levenshtein_distance' and 'z_word_concreteness') were removed 
       # due to non-convergence, inspired by Remedy 11 from Table 17 in Brauer and 
       # Curtin (2018). However, whereas Brauer and Curtin constrain such a removal 
       # to cases in which the covariate does not interact with any effects of 
       # interest, the random slopes for 'z_word_concreteness' were removed below 
       # because the interactions between this covariate and the effects of interest 
-      # were controlled covariates, not interactions of interest. That is, they 
+      # were control covariates, not interactions of interest. That is, they 
       # were not critical to the research question.
     
     (z_word_cooccurrence + z_visual_rating | Participant) +
       
-      # By-item random slopes
+      # By-word random slopes
       
-      # Below, the random slopes for the controlled covariate (i.e., 'z_information_uptake') 
+      # Below, the random slopes for the control covariate (i.e., 'z_information_uptake') 
       # were removed due to non-convergence, inspired by Remedy 11 from Table 17 in Brauer 
       # and Curtin (2018). However, whereas Brauer and Curtin constrained such a removal to 
       # cases in which the covariate does not interact with any effects of interest, the 
       # random slopes for 'z_information_uptake' were removed below because the interactions 
-      # between this covariate and the effects of interest were controlled covariates, not 
+      # between this covariate and the effects of interest were control covariates, not 
       # interactions of interest. That is, they were not critical to the research question.
       
     (z_vocabulary_size + z_recoded_participant_gender | Word),

### 2022-06-29 semanticdecision/correlations/semanticdecision_correlations.R

@@ -32,7 +32,7 @@ source('R_functions/correlation_matrix.R')
     rename('RT' = z_RTclean, 
            'Vocabulary size' = z_vocabulary_size,
            'Information uptake' = z_information_uptake,
-           "Distance to word 'abstract'" = z_word_cooccurrence,
+           "Word co-occurrence" = z_word_cooccurrence,
            'Visual strength' = z_visual_rating,
            'Word concreteness' = z_word_concreteness,
            'Word frequency' = z_word_frequency,

### 2022-06-29 semanticdecision/frequentist_analysis/model_diagnostics/semanticdecision_GLMM.R

@@ -91,7 +91,7 @@ afex::mixed( RTclean ~
                # In the random slopes below, `0 +` helps avoid redundant random intercepts 
                # (background: https://github.com/lme4/lme4/issues/625)
                
-               # By-subject random slopes
+               # By-participant random slopes
                (0 + z_word_cooccurrence || Participant) + 
                (0 + z_visual_rating || Participant) +
                # Random slopes below removed due to non-convergence, following 
@@ -100,7 +100,7 @@ afex::mixed( RTclean ~
                # (0 + z_orthographic_Levenshtein_distance || Participant) +
                # (0 + z_word_concreteness || Participant) +
                
-               # By-item random slopes
+               # By-word random slopes
                (0 + z_vocabulary_size || Word) + 
                (0 + z_recoded_participant_gender || Word),
              # Random slopes below removed due to non-convergence, following 

### 2022-06-29 semanticdecision/frequentist_analysis/semanticdecision-interactions-with-vocabulary-size.R

@@ -3,7 +3,7 @@
 # Part of Study 2: Semantic decision
 
 # Combination of plots:
-# 1. Interaction between vocabulary size and distance to word 'abstract'
+# 1. Interaction between vocabulary size and word co-occurrence
 # 2. Interaction between vocabulary size and visual strength
 # 3. Interaction between vocabulary size and word concreteness
 
@@ -13,8 +13,7 @@ library(patchwork)
 
 # Data set below created in the script 'semanticdecision_data_preparation.R',
 # which is stored in the folder 'semanticdecision/data'
-semanticdecision = 
-  read.csv('semanticdecision/data/final_dataset/semanticdecision.csv')
+semanticdecision = read.csv('semanticdecision/data/final_dataset/semanticdecision.csv')
 
 # Model below created in the script 'semanticdecision_lmerTest.R',
 # which is stored in the folder 'semanticdecision/frequentist_analysis'
@@ -30,14 +29,13 @@ plot1 =
     x = 'z_word_cooccurrence',
     fill = 'z_vocabulary_size',
     fill_nesting_factor = 'Participant',
-    x_title = "Distance to word 'abstract' (*z*)",
+    x_title = "Word co-occurrence (*z*)",
     y_title = 'Predicted RT (*z*)',
     fill_title = 'Vocabulary size (*z*, deciles)'
-  ) +
-  theme(plot.tag.position = c(0, 1), 
-        legend.key.width = unit(1.2, 'cm'),
-        legend.margin = margin(t = 21),
-        legend.background = element_blank())
+  ) + theme(plot.tag.position = c(0, 1), 
+            legend.key.width = unit(1.2, 'cm'),
+            legend.margin = margin(t = 21),
+            legend.background = element_blank())
 
 plot2 =
   deciles_interaction_plot(
@@ -48,11 +46,11 @@ plot2 =
     x_title = 'Visual strength (*z*)',
     y_title = 'Predicted RT (*z*)',
     fill_title = 'Vocabulary size (*z*, deciles)'
-  ) +
-  theme(axis.title.y = element_blank(), 
-        legend.key.width = unit(1.2, 'cm'),
-        legend.margin = margin(t = 21),
-        legend.background = element_blank())
+  ) + theme(plot.tag.position = c(0, 1), 
+            axis.title.y = element_blank(), 
+            legend.key.width = unit(1.2, 'cm'),
+            legend.margin = margin(t = 21),
[…]

### 2022-06-29 semanticdecision/frequentist_analysis/semanticdecision_lmerTest.R

@@ -74,7 +74,7 @@ system.time({
         # (see https://github.com/lme4/lme4/issues/625) and reduces the random-effects
         # structure (Brauer & Curtin, 2018).
         
-        # By-subject random slopes
+        # By-participant random slopes
         (0 + z_word_cooccurrence || Participant) + 
         (0 + z_visual_rating || Participant) +
         
@@ -82,13 +82,13 @@ system.time({
         # in Brauer and Curtin (2018). However, whereas Brauer and Curtin constrained such a 
         # removal to cases in which the covariate does not interact with any effects of interest,
         # the random slopes for 'z_word_concreteness' are removed below because the interactions 
-        # between this covariate and the effects of interest are controlled covariates per se, 
+        # between this covariate and the effects of interest are control covariates per se, 
         # not interactions of interest. That is, they are not critical to the research question.
         # (0 + z_word_frequency || Participant) + 
         # (0 + z_orthographic_Levenshtein_distance || Participant) +
         # (0 + z_word_concreteness || Participant) +
         
-      # By-item random slopes
+      # By-word random slopes
       (0 + z_vocabulary_size || Word) + 
         (0 + z_recoded_participant_gender || Word),
       
@@ -96,7 +96,7 @@ system.time({
       # in Brauer and Curtin (2018). However, whereas Brauer and Curtin constrained such a 
       # removal to cases in which the covariate does not interact with any effects of interest,
       # the random slopes for 'z_information_uptake' are removed below because the interactions 
-      # between this covariate and the effects of interest are controlled covariates per se, 
+      # between this covariate and the effects of interest are control covariates per se, 
       # not interactions of interest. That is, they are not critical to the research question.
       # (0 + z_information_uptake || Word),
       

### 2022-06-29 semanticdecision/frequentist_bayesian_plots/semanticdecision_frequentist_bayesian_plots.R

@@ -65,7 +65,7 @@ new_labels =
   str_replace(pattern = 'z_word_concreteness',
               replacement = 'Word concreteness') %>%
   str_replace(pattern = 'z_word_cooccurrence',
-              replacement = "Distance to word \'abstract\'") %>%
+              replacement = 'Word co-occurrence') %>%
   str_replace(pattern = 'z_visual_rating',
               replacement = 'Visual strength') %>%
   str_replace(pattern = 'z_information_uptake',
@@ -81,9 +81,7 @@ new_labels =
   # better consistency, the code below moves those word-level variables (with 
   # their new names) to the first position in their interactions. Note that the 
   # order does not affect the results in any way.
-  sub("(\\w+.*):(Distance to word \'abstract\'|Visual strength)", 
-      '\\2:\\1', 
-      .) %>%
+  sub('(\\w+.*):(Word co-occurrence|Visual strength)', '\\2:\\1', .) %>%
   
   # Replace colons denoting interactions with times symbols
   str_replace(pattern = ':', replacement = ' &times; ')
@@ -96,7 +94,7 @@ plot_semanticdecision_frequentist_bayesian_plot_informativepriors_exgaussian =
                             confint_semanticdecision_lmerTest,
                             semanticdecision_posteriordistributions_informativepriors_exgaussian,
                             labels = new_labels, interaction_symbol_x = TRUE,
-                            vertical_line_at_x = 0, x_title = 'Predicted RT (*z*)', 
+                            vertical_line_at_x = 0, x_title = 'Effect size (&beta;)', 
                             note_frequentist_no_prior = TRUE) +
   ggtitle('Prior *SD* = 0.1')
 
@@ -107,8 +105,8 @@ plot_semanticdecision_frequentist_bayesian_plot_informativepriors_exgaussian =
                             confint_semanticdecision_lmerTest,
                             semanticdecision_posteriordistributions_weaklyinformativepriors_exgaussian,
                             labels = new_labels, interaction_symbol_x = TRUE,
-                            vertical_line_at_x = 0, x_title = 'Predicted RT (*z*)',
-                            legend_columns = 1) + 
+                            vertical_line_at_x = 0, x_title = 'Effect size (&beta;)',
+                            legend_ncol = 1) + 
     theme(legend.position = 'bottom') ) %>%
[…]

### 2022-06-29 semanticpriming/analysis_with_visualsimilarity/semanticpriming_with_visualsimilarity_confidence_intervals_plot.R

@@ -56,7 +56,7 @@ rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients)
   # better consistency, the code below moves those word-level variables (with 
   # their new names) to the first position in their interactions. Note that the 
   # order does not affect the results in any way.
-  sub("(\\w+.*):(Language-based similarity|Visual-strength difference|Vision-based similarity)", 
+  sub('(\\w+.*):(Language-based similarity|Visual-strength difference|Vision-based similarity)', 
       '\\2:\\1', 
       .)
 
@@ -94,7 +94,7 @@ rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) =
   # better consistency, the code below moves those word-level variables (with 
   # their new names) to the first position in their interactions. Note that the 
   # order does not affect the results in any way.
-  sub("(\\w+.*):(Language-based similarity|Visual-strength difference|Vision-based similarity)", 
+  sub('(\\w+.*):(Language-based similarity|Visual-strength difference|Vision-based similarity)', 
       '\\2:\\1', 
       .)
 
@@ -102,7 +102,7 @@ rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) =
 ( plot_95_confidence_intervals(
   KR_summary_semanticpriming_with_visualsimilarity_lmerTest, 
   confint_semanticpriming_with_visualsimilarity_lmerTest, 
-  x_title = 'Predicted RT (*z*)', interaction_symbol_x = TRUE, 
+  x_title = 'Effect size (&beta;)', interaction_symbol_x = TRUE, 
   axis_text_size = 13, vertical_line_at_x = 0,
   # Intercept and covariates commented out below
   select_effects = c(
@@ -135,5 +135,5 @@ rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) =
 ) + theme(plot.margin = margin(9, 4, 14, 12)) ) %>%
   # Save plot
   ggsave(filename = 'semanticpriming/analysis_with_visualsimilarity/plots/semanticpriming_with_visualsimilarity_confidence_intervals_plot.pdf', 
-         device = cairo_pdf, width = 7, height = 6.2, dpi = 900)
+         device = cairo_pdf, width = 7, height = 7, dpi = 900)
 

### 2022-06-29 semanticpriming/analysis_with_visualsimilarity/semanticpriming_with_visualsimilarity_lmerTest.R

@@ -80,7 +80,7 @@ system.time({
         # (see https://github.com/lme4/lme4/issues/625) and reduces the random-effects
         # structure (Brauer & Curtin, 2018).
         
-        # By-subject random slopes
+        # By-participant random slopes
         (0 + z_cosine_similarity || Participant) + 
         (0 + z_visual_rating_diff || Participant) +
         (0 + z_visual_similarity || Participant) + 
@@ -93,13 +93,13 @@ system.time({
         # in Brauer and Curtin (2018). However, whereas Brauer and Curtin constrained such a 
         # removal to cases in which the covariate does not interact with any effects of interest,
         # the random slopes for 'z_word_concreteness_diff' are removed below because the interactions 
-        # between this covariate and the effects of interest are controlled covariates per se, 
+        # between this covariate and the effects of interest are control covariates per se, 
         # not interactions of interest. That is, they are not critical to the research question.
         # (0 + z_target_word_frequency || Participant) + 
         # (0 + z_target_number_syllables || Participant) +
         # (0 + z_word_concreteness_diff || Participant) +
         
-      # By-item random slopes
+      # Random slopes by prime-target pair
       (0 + z_vocabulary_size || primeword_targetword) + 
         (0 + z_recoded_participant_gender || primeword_targetword),
       
@@ -107,7 +107,7 @@ system.time({
       # in Brauer and Curtin (2018). However, whereas Brauer and Curtin constrained such a 
       # removal to cases in which the covariate does not interact with any effects of interest,
       # the random slopes for 'z_attentional_control' are removed below because the interactions 
-      # between this covariate and the effects of interest are controlled covariates per se, 
+      # between this covariate and the effects of interest are control covariates per se, 
       # not interactions of interest. That is, they are not critical to the research question.
       # (0 + z_attentional_control || primeword_targetword),
       

### 2022-06-29 semanticpriming/bayesian_analysis/divergent_models/semanticpriming_brms_weaklyinformativepriors_exgaussian.R

@@ -82,7 +82,7 @@ semanticpriming_brms_weaklyinformativepriors_exgaussian =
       # https://psych.wisc.edu/Brauer/BrauerLab/wp-content/uploads/2014/04/Brauer-Curtin-2018-on-LMEMs.pdf).
       # Interactions only require random slopes if all variables involved vary within the same units.
       
-      # By-subject random slopes
+      # By-participant random slopes
       (z_cosine_similarity + z_visual_rating_diff +
          z_recoded_interstimulus_interval + 
          z_cosine_similarity : z_recoded_interstimulus_interval +
@@ -90,7 +90,7 @@ semanticpriming_brms_weaklyinformativepriors_exgaussian =
          z_target_word_frequency + z_target_number_syllables + 
          z_word_concreteness_diff | Participant) +
       
-      # By-item random slopes
+      # Random slopes by prime-target pair
       (z_vocabulary_size + z_recoded_participant_gender +
          z_attentional_control | primeword_targetword),
     

### 2022-06-29 semanticpriming/bayesian_analysis/prior_predictive_checks/semanticpriming_priorpredictivecheck_informativepriors.R

@@ -81,7 +81,7 @@ get_prior(
     # In the random slopes below, `0 +` helps avoid redundant random intercepts
     # (background: https://github.com/lme4/lme4/issues/625)
     
-    # By-subject random slopes
+    # By-participant random slopes
     (0 + z_cosine_similarity | Participant) +
     (0 + z_visual_rating_diff | Participant) +
     (0 + z_recoded_interstimulus_interval | Participant) +
@@ -91,7 +91,7 @@ get_prior(
     (0 + z_target_number_syllables | Participant) +
     (0 + z_word_concreteness_diff | Participant) +
     
-    # By-item random slopes
+    # Random slopes by prime-target pair
     (0 + z_vocabulary_size | primeword_targetword) +
     (0 + z_recoded_participant_gender | primeword_targetword) +
     (0 + z_attentional_control | primeword_targetword),
@@ -181,7 +181,7 @@ sampleonly_semanticpriming_brms_informativepriors =
       # In the random slopes below, `0 +` helps avoid redundant random intercepts
       # (background: https://github.com/lme4/lme4/issues/625)
       
-      # By-subject random slopes
+      # By-participant random slopes
       (0 + z_cosine_similarity | Participant) +
       (0 + z_visual_rating_diff | Participant) +
       (0 + z_recoded_interstimulus_interval | Participant) +
@@ -191,7 +191,7 @@ sampleonly_semanticpriming_brms_informativepriors =
       (0 + z_target_number_syllables | Participant) +
       (0 + z_word_concreteness_diff | Participant) +
       
-      # By-item random slopes
+      # Random slopes by prime-target pair
       (0 + z_vocabulary_size | primeword_targetword) +
       (0 + z_recoded_participant_gender | primeword_targetword) +
       (0 + z_attentional_control | primeword_targetword),

### 2022-06-29 semanticpriming/bayesian_analysis/prior_predictive_checks/semanticpriming_priorpredictivecheck_weaklyinformativepriors.R

@@ -81,7 +81,7 @@ get_prior(
     # In the random slopes below, `0 +` helps avoid redundant random intercepts
     # (background: https://github.com/lme4/lme4/issues/625)
     
-    # By-subject random slopes
+    # By-participant random slopes
     (0 + z_cosine_similarity | Participant) +
     (0 + z_visual_rating_diff | Participant) +
     (0 + z_recoded_interstimulus_interval | Participant) +
@@ -91,7 +91,7 @@ get_prior(
     (0 + z_target_number_syllables | Participant) +
     (0 + z_word_concreteness_diff | Participant) +
     
-    # By-item random slopes
+    # Random slopes by prime-target pair
     (0 + z_vocabulary_size | primeword_targetword) +
     (0 + z_recoded_participant_gender | primeword_targetword) +
     (0 + z_attentional_control | primeword_targetword),
@@ -181,7 +181,7 @@ sampleonly_semanticpriming_brms_weaklyinformativepriors =
       # In the random slopes below, `0 +` helps avoid redundant random intercepts
       # (background: https://github.com/lme4/lme4/issues/625)
       
-      # By-subject random slopes
+      # By-participant random slopes
       (0 + z_cosine_similarity | Participant) +
       (0 + z_visual_rating_diff | Participant) +
       (0 + z_recoded_interstimulus_interval | Participant) +
@@ -191,7 +191,7 @@ sampleonly_semanticpriming_brms_weaklyinformativepriors =
       (0 + z_target_number_syllables | Participant) +
       (0 + z_word_concreteness_diff | Participant) +
       
-      # By-item random slopes
+      # Random slopes by prime-target pair
       (0 + z_vocabulary_size | primeword_targetword) +
       (0 + z_recoded_participant_gender | primeword_targetword) +
       (0 + z_attentional_control | primeword_targetword),

### 2022-06-29 semanticpriming/bayesian_analysis/prior_predictive_checks/semanticpriming_priorpredictivecheck_weaklyinformativepriors_exgaussian.R

@@ -81,7 +81,7 @@ get_prior(
     # In the random slopes below, `0 +` helps avoid redundant random intercepts
     # (background: https://github.com/lme4/lme4/issues/625)
     
-    # By-subject random slopes
+    # By-participant random slopes
     (0 + z_cosine_similarity | Participant) +
     (0 + z_visual_rating_diff | Participant) +
     (0 + z_recoded_interstimulus_interval | Participant) +
@@ -91,7 +91,7 @@ get_prior(
     (0 + z_target_number_syllables | Participant) +
     (0 + z_word_concreteness_diff | Participant) +
     
-    # By-item random slopes
+    # Random slopes by prime-target pair
     (0 + z_vocabulary_size | primeword_targetword) +
     (0 + z_recoded_participant_gender | primeword_targetword) +
     (0 + z_attentional_control | primeword_targetword),
@@ -191,7 +191,7 @@ sampleonly_semanticpriming_brms_weaklyinformativepriors =
       # In the random slopes below, `0 +` helps avoid redundant random intercepts
       # (background: https://github.com/lme4/lme4/issues/625)
       
-      # By-subject random slopes
+      # By-participant random slopes
       (0 + z_cosine_similarity | Participant) +
       (0 + z_visual_rating_diff | Participant) +
       (0 + z_recoded_interstimulus_interval | Participant) +
@@ -201,7 +201,7 @@ sampleonly_semanticpriming_brms_weaklyinformativepriors =
       (0 + z_target_number_syllables | Participant) +
       (0 + z_word_concreteness_diff | Participant) +
       
-      # By-item random slopes
+      # Random slopes by prime-target pair
       (0 + z_vocabulary_size | primeword_targetword) +
       (0 + z_recoded_participant_gender | primeword_targetword) +
       (0 + z_attentional_control | primeword_targetword),

### 2022-06-29 semanticpriming/frequentist_analysis/model_diagnostics/semanticpriming_GLMM.R

@@ -97,7 +97,7 @@ afex::mixed(
     # In the random slopes below, `0 +` helps avoid redundant random intercepts 
     # (background: https://github.com/lme4/lme4/issues/625)
     
-    # By-subject random slopes
+    # By-participant random slopes
     (0 + z_cosine_similarity || Participant) + 
     (0 + z_visual_rating_diff || Participant) +
     (0 + z_recoded_interstimulus_interval || Participant) +
@@ -109,7 +109,7 @@ afex::mixed(
     # (0 + z_target_number_syllables || Participant) +
     # (0 + z_word_concreteness_diff || Participant) +
     
-    # By-item random slopes
+    # Random slopes by prime-target pair
     (0 + z_vocabulary_size || target_word) + 
     (0 + z_recoded_participant_gender || target_word),
   # Random slopes below removed due to non-convergence, inspired by Remedy 11 from Table 17 

### 2022-06-29 semanticpriming/frequentist_analysis/semanticpriming-interactions-with-SOA.R

@@ -12,8 +12,7 @@ library(patchwork)
 
 # Data set below created in the script 'semanticpriming_data_preparation.R',
 # which is stored in the folder 'semanticpriming/data'
-semanticpriming = 
-  read.csv('semanticpriming/data/final_dataset/semanticpriming.csv')
+semanticpriming = read.csv('semanticpriming/data/final_dataset/semanticpriming.csv')
 
 
 ## Convert interstimulus interval to stimulus-onset asynchrony ##
@@ -36,12 +35,12 @@ semanticpriming =
 # et al., 1998; Petilli et al., 2021; Yap et al., 2017).
 
 # The 'SOA' column is created below by replacing ISI values of 50 with 
-# 200 and ISI values of 1050 (i.e., all other values) with 1200.
+# 200 and ISI values of 1050 with 1200.
 
 semanticpriming$SOA = 
-  ifelse(test = semanticpriming$interstimulus_interval == 50, 
-         yes = 200, 
-         no = 1200)
+  ifelse(semanticpriming$interstimulus_interval == 50, 200, 
+         ifelse(semanticpriming$interstimulus_interval == 1050, 1200, 
+                semanticpriming$interstimulus_interval))
 
 
 # Model below created in the script 'semanticpriming_lmerTest.R',
@@ -62,9 +61,8 @@ plot1 =
     x_title = 'Language-based similarity (*z*)',
     y_title = 'Predicted RT (*z*)',
     fill_title = 'SOA (ms)'
-  ) +
-  theme(plot.tag.position = c(0, 1), 
-        legend.position = c(.9, .82))
+  ) + theme(plot.tag.position = c(0, 1), 
+            legend.position = c(.9, .82))
 
 plot2 = 
   alias_interaction_plot(
@@ -76,14 +74,13 @@ plot2 =
     x_title = 'Visual-strength difference (*z*)',
     y_title = 'Predicted RT (*z*)',
     fill_title = 'SOA (ms)'
-  ) +
-  theme(plot.tag.position = c(0, 1), 
-        legend.position = 'none')
+  ) + theme(plot.tag.position = c(0, 1), 
+            legend.position = 'none')
 
 # Combine plots using {patchwork} and save the result to disk
 ( plot1 + plot2 + 
-    plot_annotation(tag_levels = list(c('(a)', '(b)', '(c)'))) + 
+    plot_annotation(tag_levels = list(c('(a)', '(b)'))) + 
[…]

### 2022-06-29 semanticpriming/frequentist_analysis/semanticpriming-interactions-with-gender.R

@@ -12,10 +12,9 @@ library(ggplot2)
 
 # Data set below created in the script 'semanticpriming_data_preparation.R',
 # which is stored in the folder 'semanticpriming/data'
-semanticpriming = 
-  read.csv('semanticpriming/data/final_dataset/semanticpriming.csv')
+semanticpriming = read.csv('semanticpriming/data/final_dataset/semanticpriming.csv')
 
-# Consolidate gender labels
+# Set plain language labels
 semanticpriming$participant_gender = 
   ifelse(semanticpriming$participant_gender == 'f', 'Female',
          ifelse(semanticpriming$participant_gender == 'F', 'Female',
@@ -54,7 +53,7 @@ plot1 =
                              # in legend (else, Male would appear 
                              # first as it was coded as -0.5).
                              reverse = TRUE)) +
-  theme(plot.tag.position = c(0, 1), legend.position = c(.85, .81))
+  theme(plot.tag.position = c(0, 1), legend.position = c(.78, .81))
 
 plot2 = 
   alias_interaction_plot(
@@ -85,5 +84,5 @@ plot2 =
     plot_annotation(tag_levels = list(c('(a)', '(b)', '(c)'))) + 
     plot_layout(ncol = 1) ) %>%
   ggsave(filename = 'semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-gender.pdf',
-         device = cairo_pdf, width = 6.5, height = 7, dpi = 900)
+         device = cairo_pdf, width = 6, height = 7, dpi = 900)
 

### 2022-06-29 semanticpriming/frequentist_analysis/semanticpriming-interactions-with-word-concreteness-difference.R

@@ -1,0 +1,127 @@
+
+
+# Part of Study 1: Semantic priming
+
+# 1. Interaction between word-concreteness difference and SOA
+# 2. Interaction between word-concreteness difference and vocabulary size
+# 3. Interaction between word-concreteness difference and gender
+
+library(dplyr)
+library(ggplot2)
+library(patchwork)
+
+# Data set below created in the script 'semanticpriming_data_preparation.R',
+# which is stored in the folder 'semanticpriming/data'
+semanticpriming = read.csv('semanticpriming/data/final_dataset/semanticpriming.csv')
+
+
+## Convert interstimulus interval to stimulus-onset asynchrony ##
+
+# The stimulus-onset asynchrony (SOA) has an alternative formula called the 
+# 'interstimulus interval' (ISI). The difference between these is that the 
+# ISI does not count the presentation of the prime word (example 
+# equivalences between ISI and SOA are available ISI and SOA in Lam et al., 
+# 2015, and in Figure 1A of Di Lollo et al., 2004). In the current study, 
+# the presentation of the prime word lasts 150 ms. Thus, the 200-ms SOA is 
+# equivalent to an ISI of 50 ms, and the 1,200-ms SOA corresponds to an 
+# ISI of 1,050 ms (Hutchison et al., 2013). The use of either formula in 
+# the analysis would not change our results, as we recoded the levels of 
+# the factor as -0.5 and +0.5, and then z-scored those, following the 
+# advice of Brauer and Curtin (2018). In our analyses (https://osf.io/ueryq), 
+# we used the ISI formula, as it was the one present in the data set of 
+# Hutchison et al. (2013; https://www.montana.edu/attmemlab/documents/all%20ldt%20subs_all%20trials3.xlsx). 
+# However, we use the SOA formula in this paper as it has been more 
+# commonly used in previous papers (e.g., Hutchison et al., 2013; Pecher
+# et al., 1998; Petilli et al., 2021; Yap et al., 2017).
+
+# The 'SOA' column is created below by replacing ISI values of 50 with 
+# 200 and ISI values of 1050 with 1200.
+
+semanticpriming$SOA = 
+  ifelse(semanticpriming$interstimulus_interval == 50, 200, 
+         ifelse(semanticpriming$interstimulus_interval == 1050, 1200, 
+                semanticpriming$interstimulus_interval))
+
+
+# Consolidate gender labels
+semanticpriming$participant_gender = 
[…]

### 2022-06-29 semanticpriming/frequentist_analysis/semanticpriming_confidence_intervals_plot.R

@@ -90,14 +90,14 @@ rownames(confint_semanticpriming_lmerTest) =
   # better consistency, the code below moves those word-level variables (with 
   # their new names) to the first position in their interactions. Note that the 
   # order does not affect the results in any way.
-  sub("(\\w+.*):(Language-based similarity|Visual-strength difference)", 
+  sub('(\\w+.*):(Language-based similarity|Visual-strength difference)', 
       '\\2:\\1', 
       .)
 
 
 ( plot_95_confidence_intervals(
   KR_summary_semanticpriming_lmerTest, confint_semanticpriming_lmerTest, 
-  x_title = 'Predicted RT (*z*)', interaction_symbol_x = TRUE,
+  x_title = 'Effect size (&beta;)', interaction_symbol_x = TRUE,
   vertical_line_at_x = 0
 ) + theme(plot.margin = margin(9, 4, 14, 12)) ) %>%
   # Save plot

### 2022-06-29 semanticpriming/power_analysis/reduced_randomeffects_model/model_diagnostics/semanticpriming_robustlmm.R

@@ -74,7 +74,7 @@ semanticpriming_robustlmm =
       # In the random slopes below, `0 +` helps avoid redundant random intercepts 
       # (background: https://github.com/lme4/lme4/issues/625)
       
-      # By-subject random slopes
+      # By-participant random slopes
       (0 + z_cosine_similarity || Participant) + 
       (0 + z_visual_rating_diff || Participant) +
       (0 + z_recoded_interstimulus_interval || Participant) +
@@ -86,7 +86,7 @@ semanticpriming_robustlmm =
       # (0 + z_target_number_syllables || Participant) +
       # (0 + z_word_concreteness_diff || Participant) +
       
-      # By-item random slopes
+      # Random slopes by prime-target pair
       (0 + z_vocabulary_size || target_word) + 
       (0 + z_recoded_participant_gender || target_word),
     # Random slopes below removed due to non-convergence, inspired by Remedy 11 from Table 17 

### 2022-06-29 semanticpriming/power_analysis/reduced_randomeffects_model/semanticpriming_lmerTest.R

@@ -75,7 +75,7 @@ system.time({
         # (see https://github.com/lme4/lme4/issues/625) and reduces the random-effects
         # structure (Brauer & Curtin, 2018).
         
-        # By-subject random slopes
+        # By-participant random slopes
         (0 + z_cosine_similarity || Participant) + 
         (0 + z_visual_rating_diff || Participant) +
         (0 + z_recoded_interstimulus_interval || Participant) +
@@ -87,7 +87,7 @@ system.time({
         # (0 + z_target_number_syllables || Participant) +
         # (0 + z_word_concreteness_diff || Participant) +
         
-        # By-item random slopes
+        # Random slopes by prime-target pair
         (0 + z_vocabulary_size || target_word) + 
         (0 + z_recoded_participant_gender || target_word),
       # Random slopes below removed due to non-convergence, following 

### 2022-09-26 manuscript/appendix-A-lexical-covariates.Rmd
26092022

@@
 
-# This appendix is rendered by the main manuscript. It inherits the 
-# working directory and all the objects loaded in the main manuscript.
+# This appendix is rendered by the main manuscript. It inherits all the 
+# parameters set in the main manuscript and the objects loaded therein.
 
@@
 
-Lexical covariates are usually used in conceptual processing studies due to the widespread connections among lexical and semantic variables.
+Lexical covariates are usually used in conceptual processing studies due to the widespread connections among lexical and semantic variables [e.g., @pexman2018a; @petilli2021a; @wingfieldUnderstandingRoleLinguistic2022].
 Including these covariates---or nuisance variables---in the model allows a more rigorous analysis of the predictors of interest [@sassenhagenCommonMisapplicationStatistical2016].
-
-In each study, the covariates were selected out of a group of 5 variables that had been used as covariates in @wingfieldUnderstandingRoleLinguistic2022, and are widely used [e.g., @petilli2021a].
+In each of the present studies, the covariates were selected out of a group of five variables that had been used as covariates in @wingfieldUnderstandingRoleLinguistic2022, and are widely used [e.g., @petilli2021a].
 Some of these covariates were highly intercorrelated ($r$ > .70), as shown below.
@@
 
-In Studies 1 (semantic priming) and 2 (semantic decision), the lexical covariates were selected out of five variables, which mirrored those used by @wingfieldUnderstandingRoleLinguistic2022: namely, number of letters (i.e., orthographic length, which we computed in R), word frequency, number of syllables  [both the latter from @balota2007a], orthographic Levenshtein distance [@yarkoniMovingColtheartNew2008] and phonological Levenshtein distance [@suarezObservingNeighborhoodEffects2011].
-In Study 3 (lexical decision), the procedure was identical except that word frequency could not be selected as a covariate because it constituted a predictor of interest, specifically corresponding to linguistic information (for details, see Study 3 in the main article).
+In Studies 1 (semantic priming) and 2 (semantic decision), the lexical covariates were selected out of five variables, which mirrored those used by @wingfieldUnderstandingRoleLinguistic2022: namely, number of letters (i.e., orthographic length, which we computed in R), word frequency, number of syllables  [both the latter from @balota2007a], orthographic Levenshtein distance [@yarkoniMovingColtheartNew2008] and phonological Levenshtein distance [@suarezObservingNeighborhoodEffects2011; @yapVisualWordRecognition2009].
+In Study 3 (lexical decision), the procedure was more particular, as it served two purposes.
+First, the variable that had the largest effect out of the five was selected as the language-based predictor of interest (see reason in [\underline{Study 3 in the main text}](#lexicaldecision)).
+Second, one variable was selected as a covariate among the remaining four.
 
@@
   # Place table close to designated position
-  kable_styling(latex_options = 'HOLD_position') %>%
+  kable_styling(latex_options = 'hold_position') %>%
 
@@
   footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
-           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored variables; \\\\textit{SE} = standard error;',
+           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored predictors; \\\\textit{SE} = standard error;',
                            'CI = confidence interval. By-participant random slopes were included for',
                            'every effect.', 
-                           # Begin lines after first one with a dot-sized indent
+                           # After first line in the footnote, begin next lines with a dot-sized indent to correct default error.
                            sep = ' \\\\linebreak \\\\phantom{.}'))
@@
 ## Study 3: Lexical decision
+
+The selection model for Study 3 served a twofold purpose.
+First, the variable that had the largest effect out of the five was selected as the language-based predictor of interest (see reason in [\underline{Study 3 in the main text}](#lexicaldecision)).
+Second, one variable was selected as a covariate among the remaining four.
 

### 2022-09-26 manuscript/appendix-B-frequentist-analysis-diagnostics.Rmd
26092022

@@
 
-### The multiple-optimizers sanity check from `lme4::allFit()`
+### The multiple-optimisers sanity check from `lme4::allFit()`
 
-Framed within the drive to maintain random slopes wherever possible, the developers of the 'lme4' package propose a sanity check that uses a part of the 'lme4' *engine* called 'optimizer'.
-Every model has a default optimizer, unless a specific one is chosen through `control = lmerControl(optimizer = '...')` (in `lmer` models) or `control = glmerControl(optimizer = '...')` (in `glmer` models).
-The 7 widely-available optimizers are:
+Framed within the drive to maintain random slopes wherever possible, the developers of the 'lme4' package propose a sanity check that uses a part of the 'lme4' *engine* called 'optimiser'.
+Every model has a default optimiser, unless a specific one is chosen through `control = lmerControl(optimiser = '...')` (in `lmer` models) or `control = glmerControl(optimiser = '...')` (in `glmer` models).
+The seven widely-available optimisers are:
 
@@
 
-To assess whether convergence warnings render the results invalid, or on the contrary, the results can be deemed valid in spite of the warnings, @batesPackageLme42021 suggest refitting models affected by convergence warnings with a variety of optimizers.
-The authors argue that if the different optimizers produce practically-equivalent results, the results are valid.
-For this purpose, the 'allFit' function from the 'lme4' package allows the refitting of models using a number of optimizers.
-To use the 7 optimizers listed above, two extra packages were installed: 'dfoptim' and 'optimx' (see [lme4 manual](https://cran.r-project.org/web/packages/lme4/lme4.pdf)).
-The output from 'allFit' contains several statistics on the fixed and the random effects fitted by each optimizer (see [example](https://github.com/lme4/lme4/issues/512#issue-425198940)).
+To assess whether convergence warnings render the results invalid, or on the contrary, the results can be deemed valid in spite of the warnings, @batesPackageLme42021 suggest refitting models affected by convergence warnings with a variety of optimisers.
+The authors argue that if the different optimisers produce practically-equivalent results, the results are valid.
+For this purpose, the 'allFit' function from the 'lme4' package allows the refitting of models using a number of optimisers.
+To use the seven optimisers listed above, two extra packages were installed: 'dfoptim' and 'optimx' (see [lme4 manual](https://cran.r-project.org/web/packages/lme4/lme4.pdf)).
+The output from 'allFit' contains several statistics on the fixed and the random effects fitted by each optimiser (see [example](https://github.com/lme4/lme4/issues/512#issue-425198940)).
 
@@
 
-The residuals of the linear mixed-effects models in all three studies violated the assumption of normality.
+The residuals of the linear mixed-effects models in the three studies violated the assumption of normality.
 Even though linear mixed-effects models tend to be quite robust to deviations from normality [@kniefViolatingNormalityAssumption2021; @schielzethRobustnessLinearMixed2020], we sought to verify our results.
@@
 
-In the initial model, the optimizer used (the default one in 'lmerTest') was '`r semanticpriming_lmerTest@optinfo$optimizer`', and the convergence warning read: '`r semanticpriming_lmerTest@optinfo$conv$lme4$messages`'.
+In the initial model, the optimiser used (the default one in 'lmerTest') was '`r semanticpriming_lmerTest@optinfo$optimiser`', and the convergence warning read: '`r semanticpriming_lmerTest@optinfo$conv$lme4$messages`'.
 
-Based on the reanalysis using 7 optimizers, Figure \@ref(fig:main-effects-semanticpriming-allFit-convergence) shows the fixed, main effects, and Figure \@ref(fig:interactions-semanticpriming-allFit-convergence) shows the fixed interactions.
+Based on the reanalysis using seven optimisers, Figure \@ref(fig:main-effects-semanticpriming-allFit-convergence) shows the fixed, main effects, and Figure \@ref(fig:interactions-semanticpriming-allFit-convergence) shows the fixed interactions.
 
-```{r main-effects-semanticpriming-allFit-convergence, fig.cap = 'Fixed, main effects from the semantic priming study fitted by 7 optimizers.'}
+```{r main-effects-semanticpriming-allFit-convergence, fig.cap = 'Fixed, main effects from the semantic priming study fitted by seven optimisers.'}
 
@@
 
-```{r interactions-semanticpriming-allFit-convergence, fig.cap = 'Fixed interaction effects from the semantic priming study fitted by 7 optimizers.'}
+```{r interactions-semanticpriming-allFit-convergence, fig.cap = 'Fixed interaction effects from the semantic priming study fitted by seven optimisers.'}
 
@@
 
-In the initial model, the optimizer used (the default one in 'lmerTest') was '`r semanticpriming_with_visualsimilarity_lmerTest@optinfo$optimizer`', and the convergence warning read: '`r semanticpriming_with_visualsimilarity_lmerTest@optinfo$conv$lme4$messages`'.
+In the initial model, the optimiser used (the default one in 'lmerTest') was '`r semanticpriming_with_visualsimilarity_lmerTest@optinfo$optimiser`', and the convergence warning read: '`r semanticpriming_with_visualsimilarity_lmerTest@optinfo$conv$lme4$messages`'.
 
-Based on the reanalysis using 7 optimizers, Figure \@ref(fig:main-effects-semanticpriming-with-visualsimilarity-allFit-convergence) shows the fixed, main effects, and Figure \@ref(fig:interactions-semanticpriming-with-visualsimilarity-allFit-convergence) shows the fixed interactions.
+Based on the reanalysis using seven optimisers, Figure \@ref(fig:main-effects-semanticpriming-with-visualsimilarity-allFit-convergence) shows the fixed, main effects, and Figure \@ref(fig:interactions-semanticpriming-with-visualsimilarity-allFit-convergence) shows the fixed interactions.
 
-```{r main-effects-semanticpriming-with-visualsimilarity-allFit-convergence, fig.cap = 'Fixed, main effects from the semantic priming study fitted by 7 optimizers.'}
+```{r main-effects-semanticpriming-with-visualsimilarity-allFit-convergence, fig.cap = 'Fixed, main effects from the semantic priming study fitted by seven optimisers.'}
 
@@
 
-```{r interactions-semanticpriming-with-visualsimilarity-allFit-convergence, fig.cap = 'Fixed interaction effects from the semantic priming study fitted by 7 optimizers.'}
+```{r interactions-semanticpriming-with-visualsimilarity-allFit-convergence, fig.cap = 'Fixed interaction effects from the semantic priming study fitted by seven optimisers.'}
 
@@
 
-In the initial model, the optimizer used (the default one in 'lmerTest') was '`r semanticdecision_lmerTest@optinfo$optimizer`', and the convergence warning read: '`r semanticdecision_lmerTest@optinfo$conv$lme4$messages`'.
+In the initial model, the optimiser used (the default one in 'lmerTest') was '`r semanticdecision_lmerTest@optinfo$optimiser`', and the convergence warning read: '`r semanticdecision_lmerTest@optinfo$conv$lme4$messages`'.
 
-Based on the reanalysis using 7 optimizers, Figure \@ref(fig:main-effects-semanticdecision-allFit-convergence) shows the fixed, main effects, and Figure \@ref(fig:interactions-semanticdecision-allFit-convergence) shows the fixed interactions.
+Based on the reanalysis using seven optimisers, Figure \@ref(fig:main-effects-semanticdecision-allFit-convergence) shows the fixed, main effects, and Figure \@ref(fig:interactions-semanticdecision-allFit-convergence) shows the fixed interactions.
 
-```{r main-effects-semanticdecision-allFit-convergence, fig.cap = 'Fixed, main effects from the semantic decision study fitted by 7 optimizers.'}
+```{r main-effects-semanticdecision-allFit-convergence, fig.cap = 'Fixed, main effects from the semantic decision study fitted by seven optimisers.'}
 
@@
 
-```{r interactions-semanticdecision-allFit-convergence, fig.cap = 'Fixed interaction effects from the semantic decision study fitted by 7 optimizers.'}
+```{r interactions-semanticdecision-allFit-convergence, fig.cap = 'Fixed interaction effects from the semantic decision study fitted by seven optimisers.'}
 
@@
 
-In the initial model, the optimizer used (the default one in 'lmerTest') was '`r lexicaldecision_lmerTest@optinfo$optimizer`', and the convergence warning read: '`r lexicaldecision_lmerTest@optinfo$conv$lme4$messages`'.
+In the initial model, the optimiser used (the default one in 'lmerTest') was '`r lexicaldecision_lmerTest@optinfo$optimiser`', and the convergence warning read: '`r lexicaldecision_lmerTest@optinfo$conv$lme4$messages`'.
 
-Based on the reanalysis using 7 optimizers, Figure \@ref(fig:main-effects-lexicaldecision-allFit-convergence) shows the fixed, main effects, and Figure \@ref(fig:interactions-lexicaldecision-allFit-convergence) shows the fixed interactions.
+Based on the reanalysis using seven optimisers, Figure \@ref(fig:main-effects-lexicaldecision-allFit-convergence) shows the fixed, main effects, and Figure \@ref(fig:interactions-lexicaldecision-allFit-convergence) shows the fixed interactions.
 
-```{r main-effects-lexicaldecision-allFit-convergence, fig.cap = 'Fixed, main effects from the lexical decision study fitted by 7 optimizers.'}
+```{r main-effects-lexicaldecision-allFit-convergence, fig.cap = 'Fixed, main effects from the lexical decision study fitted by seven optimisers.'}
 
@@
 
-```{r interactions-lexicaldecision-allFit-convergence, fig.cap = 'Fixed interaction effects from the lexical decision study fitted by 7 optimizers.'}
+```{r interactions-lexicaldecision-allFit-convergence, fig.cap = 'Fixed interaction effects from the lexical decision study fitted by seven optimisers.'}
 

### 2022-09-26 manuscript/appendix-C-Bayesian-analysis-diagnostics.Rmd
29062022
26092022

@@
 
-# This appendix inherits the libraries, the working directory and the
-# data sets loaded in manuscript.Rmd, when the latter is knitted.
+# This appendix is rendered by the main manuscript. It inherits all the 
+# parameters set in the main manuscript and the objects loaded therein.
 
@@
 In each study, prior predictive checks are presented before posterior predictive checks.
-Furthermore, in each of these checks, the models presented first have the default Gaussian distribution, whereas the next series have an exponentially modified Gaussian (dubbed 'ex-Gaussian') distribution with an identity link function (for details, see the section titled 'Distributions and prior predictive checks' in the main article).
+Furthermore, in each of these checks, the models presented first have the default Gaussian distribution, whereas the next series have an exponentially modified Gaussian (dubbed 'ex-Gaussian') distribution with an identity link function (for details, see the section titled 'Distributions and prior predictive checks' in the main text).
 Eyeball estimation is used to assess the outcomes of these checks [for background on predictive checks and for alternative estimation procedures, see @gelmanPosteriorPredictiveAssessment1996; @moranPosteriorPredictiveNull2021; @schootBayesianStatisticsModelling2021].
@@
 The way of interpreting these plots is by comparing the observed data to the predicted distribution.
-The specifics of this vary across the three plots in the series.
-Firstly, in the upper plot, which shows the maximum values, the ideal scenario would have the observed ($y$) value overlapping with the maximum value of the predicted distribution ($y_{rep}$).
-Secondly, in the middle plot, showing the mean values, the ideal scenario would show the observed ($y$) value overlapping with the mean value of the predicted distribution ($y_{rep}$).
-Lastly, in the lower plot, which shows the minimum values, the ideal scenario would have the observed ($y$) value overlapping with the minimum value of the predicted distribution ($y_{rep}$).
-The overlap need not be absolute but the closer the observed and the predicted values on the X axis, the better.
+The specifics of this comparison vary across the three plots.
+First, in the upper plot, which shows the maximum values, the ideal scenario would show the observed maximum value ($y$) overlapping with the maximum value of the predicted distribution ($y_{rep}$).
+Second, in the middle plot, showing the mean values, the ideal scenario would show the observed mean value ($y$) overlapping with the mean value of the predicted distribution ($y_{rep}$).
+Last, in the lower plot, which shows the minimum values, the ideal scenario would have the observed minimum value ($y$) overlapping with the minimum value of the predicted distribution ($y_{rep}$).
+While the overlap need not be absolute, the closer the observed and the predicted values are on the X axis, the better.
 As such, the three predictive checks below---corresponding to models that used the default Gaussian distribution---show that the priors fitted the data acceptably but not very well.
@@
 Based on the above results, the ex-Gaussian distribution was used in the final models.
-Figure \@ref(fig:semanticpriming-posteriorpredictivechecks-allpriors-exgaussian) presents the posterior predictive checks the latter models.
+Figure \@ref(fig:semanticpriming-posteriorpredictivechecks-allpriors-exgaussian) presents the posterior predictive checks for the latter models.
 The interpretation of these plots is simple: the distributions of the observed ($y$) and the predicted data ($y_{rep}$) should be as similar as possible.
@@
 (ref:semanticpriming-posteriorpredictivechecks-allpriors-exgaussian) Posterior predictive checks for the (ex-Gaussian) models from the semantic priming study.
-$y$ = observed data; $y_{rep}$ = predicted data.
+The observed data ($y$) and the predicted data ($y_{rep}$) almost entirely overlap with each other, demonstrating a very good fit.
 
@@
 
-Figures \@ref(fig:semanticdecision-priorpredictivecheck-informativepriors), \@ref(fig:semanticdecision-priorpredictivecheck-weaklyinformativepriors) and \@ref(fig:semanticdecision-priorpredictivecheck-diffusepriors) show the prior predictive checks for the Gaussian models (for background on these checks, see [\underline{Study 1 above}](#study1-bayesian-diagnostics)).
+Figures \@ref(fig:semanticdecision-priorpredictivecheck-informativepriors), \@ref(fig:semanticdecision-priorpredictivecheck-weaklyinformativepriors) and \@ref(fig:semanticdecision-priorpredictivecheck-diffusepriors) show the prior predictive checks for the Gaussian models (for background on these checks, see [\underline{Study 1}](#study1-bayesian-diagnostics)).
 The three plots---corresponding to models that used the default Gaussian distribution---show that the priors fitted the data acceptably but not very well.
@@
 
-Figures \@ref(fig:lexicaldecision-priorpredictivecheck-informativepriors), \@ref(fig:lexicaldecision-priorpredictivecheck-weaklyinformativepriors) and \@ref(fig:lexicaldecision-priorpredictivecheck-diffusepriors) show the prior predictive checks for the Gaussian models (for background on these checks, see [\underline{Study 1 above}](#study1-bayesian-diagnostics)).
+Figures \@ref(fig:lexicaldecision-priorpredictivecheck-informativepriors), \@ref(fig:lexicaldecision-priorpredictivecheck-weaklyinformativepriors) and \@ref(fig:lexicaldecision-priorpredictivecheck-diffusepriors) show the prior predictive checks for the Gaussian models (for background on these checks, see [\underline{Study 1}](#study1-bayesian-diagnostics)).
 The three plots---corresponding to models that used the default Gaussian distribution---show that the priors fitted the data acceptably but not very well.

### 2022-09-26 manuscript/appendix-D-interaction-plots.Rmd
26092022

@@
 
-This appendix presents plots of interactions that were not shown in the main text.
+Figures \@ref(fig:semanticpriming-interactions-with-attentional-control) -- \@ref(fig:lexicaldecision-interaction-word-concreteness-gender) present interactions that were not displayed in the main article.
+All interaction plots are based on the frequentist analysis.
 
@@
 
-(ref:semanticpriming-interactions-with-attentional-control) Interactions of attentional control with language-based similarity and visual-strength difference.
-Attentional control is constrained to deciles (ten sections) in this plot, whereas in the statistical analysis it contained more values within the current range.
-*n* = number of participants contained between decile values.
+(ref:semanticpriming-interactions-with-attentional-control) Interactions of attentional control with language-based similarity (panel a) and with visual-strength difference (panel b).
+Attentional control is constrained to deciles (10 sections) in this plot, whereas in the statistical analysis it contained more values within the current range.
+$n$ = number of participants contained between deciles.
 
@@
 
-```{r semanticpriming-interaction-word-concreteness-difference-SOA, fig.cap = 'Interaction of stimulus-onset asynchrony (SOA) with word-concreteness difference.
-SOA was analysed using $z$-scores, but for clarity, the variable is shown in its basic form here.', out.width = '65%'}
+```{r semanticpriming-interaction-word-concreteness-difference-SOA, fig.cap = 'Interaction between stimulus onset asynchrony (SOA) and word-concreteness difference.
+SOA was analysed using $z$-scores, but for clarity, the basic labels are used in the legend.', out.width = '70%'}
 
@@
 
-(ref:semanticpriming-interaction-word-concreteness-difference-vocabulary-size) Interaction of word-concreteness difference with vocabulary size.
+(ref:semanticpriming-interaction-word-concreteness-difference-vocabulary-size) Interaction between word-concreteness difference and vocabulary size.
 Vocabulary size is constrained to deciles in this plot, whereas in the statistical analysis it contained more values within the current range.
-*n* = number of participants contained between decile values.
+$n$ = number of participants contained between deciles.
 
-```{r semanticpriming-interaction-word-concreteness-difference-vocabulary-size, fig.cap = '(ref:semanticpriming-interaction-word-concreteness-difference-vocabulary-size)', out.width = '85%'}
+```{r semanticpriming-interaction-word-concreteness-difference-vocabulary-size, fig.cap = '(ref:semanticpriming-interaction-word-concreteness-difference-vocabulary-size)', out.width = '90%'}
 
@@
 
-(ref:semanticpriming-interaction-word-concreteness-difference-gender) Interaction of word-concreteness difference with gender.
-Gender was analysed using $z$-scores, but for clarity, the variable is shown in its basic form here.
-*n* = number of participants contained between decile values.
+(ref:semanticpriming-interaction-word-concreteness-difference-gender) Interaction between word-concreteness difference and gender.
+Gender was analysed using $z$-scores, but for clarity, the basic labels are used in the legend.
+$n$ = number of participants contained between deciles.
 
-```{r semanticpriming-interaction-word-concreteness-difference-gender, fig.cap = '(ref:semanticpriming-interaction-word-concreteness-difference-gender)', out.width = '65%'}
+```{r semanticpriming-interaction-word-concreteness-difference-gender, fig.cap = '(ref:semanticpriming-interaction-word-concreteness-difference-gender)', out.width = '70%'}
 
@@
 
-(ref:semanticdecision-interactions-with-information-uptake) Interactions of information uptake with language-based similarity and visual-strength difference.
+(ref:semanticdecision-interactions-with-information-uptake) Interactions of information uptake with word co-occurrence (panel a) and with visual strength (panel b).
 Information uptake is constrained to deciles in this plot, whereas in the statistical analysis it contained more values within the current range.
-*n* = number of participants contained between decile values.
+$n$ = number of participants contained between deciles.
 
-```{r semanticdecision-interactions-with-information-uptake, fig.cap = '(ref:semanticdecision-interactions-with-information-uptake)', out.width = '90%'}
+```{r semanticdecision-interactions-with-information-uptake, fig.cap = '(ref:semanticdecision-interactions-with-information-uptake)', out.width = '95%'}
 
@@
 
-(ref:lexicaldecision-interaction-word-concreteness-vocabulary-age) Interaction of word concreteness with vocabulary age.
-Vocabulary age is constrained to sextiles (six sections) in this plot, whereas in the statistical analysis it contained more values within the current range.
-*n* = number of participants contained between sextile values.
+(ref:lexicaldecision-interaction-word-concreteness-vocabulary-age) Interaction between word concreteness and vocabulary age.
+Vocabulary age is constrained to sextiles (6 sections) in this plot, whereas in the statistical analysis it contained more values within the current range.
+$n$ = number of participants contained between sextiles.
 
-```{r lexicaldecision-interaction-word-concreteness-vocabulary-age, fig.cap = '(ref:lexicaldecision-interaction-word-concreteness-vocabulary-age)', out.width = '85%'}
+```{r lexicaldecision-interaction-word-concreteness-vocabulary-age, fig.cap = '(ref:lexicaldecision-interaction-word-concreteness-vocabulary-age)', out.width = '90%'}
 
@@
 
-(ref:lexicaldecision-interaction-word-concreteness-gender) Interaction of word concreteness with gender.
-Gender was analysed using $z$-scores, but for clarity, the variable is shown in its basic form here.
-*n* = number of participants contained between sextile values.
+(ref:lexicaldecision-interaction-word-concreteness-gender) Interaction between word concreteness and gender.
+Gender was analysed using $z$-scores, but for clarity, the basic labels are used in the legend.
+$n$ = number of participants contained between sextiles.
 

### 2022-09-26 manuscript/appendix-E-Bayesian-analysis-results.Rmd
26092022

@@
 For each study, three tables are presented that contain the results from the informative prior model ($SD$ = 0.1), the weakly-informative prior model ($SD$ = 0.2) and the diffuse prior model ($SD$ = 0.3).
-All models had an exponentially modified Gaussian (dubbed ‘ex-Gaussian’) distribution with an identity link function (for background, see main article and [\underline{Appendix C}](#appendix-C-Bayesian-analysis-diagnostics)).
+All models had an exponentially modified Gaussian (dubbed ‘ex-Gaussian’) distribution with an identity link function (for background, see main text and [\underline{Appendix C}](#appendix-C-Bayesian-analysis-diagnostics)).
 The $\widehat R$ value is a convergence diagnostic that should ideally be smaller than 1.01 [@vehtariRanknormalizationFoldingLocalization2021].
@@
 
-Table \@ref(tab:semanticpriming-informativepriors-model) presents the results of the informative prior model, and Table \@ref(tab:semanticpriming-diffusepriors-model) presents those of the diffuse prior model (further to this, the weakly-informative prior model will be added when it finishes running).
+Table \@ref(tab:semanticpriming-informativepriors-model) presents the results of the informative prior model, Table \@ref(tab:semanticpriming-weaklyinformativepriors-model) those of the weakly-informative prior model, and Table \@ref(tab:semanticpriming-diffusepriors-model) those of the diffuse prior model.
 
@@
   rownames(semanticpriming_summary_informativepriors_exgaussian$fixed) == 
-    'z_recoded_interstimulus_interval'] = 'Stimulus-onset asynchrony (SOA) $^{\\text{b}}$'
+    'z_recoded_interstimulus_interval'] = 'Stimulus onset asynchrony (SOA) $^{\\text{b}}$'
 
@@
                     'Visual-strength difference $^{\\text{b}}$',
-                    'Stimulus-onset asynchrony (SOA) $^{\\text{b}}$',
+                    'Stimulus onset asynchrony (SOA) $^{\\text{b}}$',
                     'Word-concreteness difference :: Vocabulary size',
@@
   pack_rows('Target-word lexical covariates', 5, 6) %>% 
-  pack_rows('Prime-target semantic relationship', 7, 9) %>% 
+  pack_rows('Prime--target relationship', 7, 9) %>% 
   pack_rows('Task condition', 10, 10) %>% 
@@
   # Place table close to designated position and highlight covariates
-  kable_styling(latex_options = c('HOLD_position', 'striped'), 
+  kable_styling(latex_options = c('hold_position', 'striped'), 
                 stripe_index = c(2, 5:7, 11:15)) %>%
@@
   footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
-           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored variables; \\\\textit{SE} = standard error;',
+           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored predictors; \\\\textit{SE} = standard error;',
                            'CrI = credible interval. Shaded rows contain covariates. Some interactions',
@@
                            '$^{\\\\text{b}}$ By-participant random slopes were included for this effect.', 
-                           # Begin lines after first one with a dot-sized indent
+                           # After first line in the footnote, begin next lines with a dot-sized indent to correct default error.
                            sep = ' \\\\linebreak \\\\phantom{.}'))
@@
 
-```{r semanticpriming-diffusepriors-model, results = 'asis'}
+```{r semanticpriming-weaklyinformativepriors-model, results = 'asis'}
 
@@
 
-rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
-  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
+rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed) == 
     'z_attentional_control'] = 'Attentional control'
 
-rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
-  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
+rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed) == 
     'z_vocabulary_size'] = 'Vocabulary size $^{\\text{a}}$'
 
-rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
-  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
+rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed) == 
     'z_recoded_participant_gender'] = 'Gender $^{\\text{a}}$'
 
-rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
-  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
+rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed) == 
     'z_target_word_frequency'] = 'Word frequency'
 
-rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
-  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
+rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed) == 
     'z_target_number_syllables'] = 'Number of syllables'
 
-rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
-  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
+rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed) == 
     'z_word_concreteness_diff'] = 'Word-concreteness difference'
 
-rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
-  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
+rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed) == 
     'z_cosine_similarity'] = 'Language-based similarity $^{\\text{b}}$'
 
-rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
-  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
+rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed) == 
     'z_visual_rating_diff'] = 'Visual-strength difference $^{\\text{b}}$'
 
-rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
-  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
-    'z_recoded_interstimulus_interval'] = 'Stimulus-onset asynchrony (SOA) $^{\\text{b}}$'
+rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed) == 
+    'z_recoded_interstimulus_interval'] = 'Stimulus onset asynchrony (SOA) $^{\\text{b}}$'
+
+rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed) == 
+    'z_word_concreteness_diff:z_vocabulary_size'] = 
+  'Word-concreteness difference :: Vocabulary size'
+
+rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed) == 
+    'z_word_concreteness_diff:z_recoded_interstimulus_interval'] = 
+  'Word-concreteness difference : SOA'
+
+rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed) == 
+    'z_word_concreteness_diff:z_recoded_participant_gender'] = 
+  'Word-concreteness difference : Gender'
+
+rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed) == 
+    'z_attentional_control:z_cosine_similarity'] = 
+  'Language-based similarity :: Attentional control'
+
+rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed) == 
+    'z_attentional_control:z_visual_rating_diff'] = 
+  'Visual-strength difference :: Attentional control'
+
+rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed) == 
+    'z_vocabulary_size:z_cosine_similarity'] = 
+  'Language-based similarity :: Vocabulary size'
+
+rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed) == 
+    'z_vocabulary_size:z_visual_rating_diff'] = 
+  'Visual-strength difference :: Vocabulary size'
+
+rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed) == 
+    'z_recoded_participant_gender:z_cosine_similarity'] = 
+  'Language-based similarity : Gender'
+
+rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed) == 
+    'z_recoded_participant_gender:z_visual_rating_diff'] = 
+  'Visual-strength difference : Gender'
+
+rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed) == 
+    'z_cosine_similarity:z_recoded_interstimulus_interval'] = 
+  'Language-based similarity : SOA $^{\\text{b}}$'
+
+rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed) == 
+    'z_visual_rating_diff:z_recoded_interstimulus_interval'] = 
+  'Visual-strength difference : SOA $^{\\text{b}}$'
+
+# Create table (using custom function from the 'R_functions' folder)
+bayesian_model_table(
+  semanticpriming_summary_weaklyinformativepriors_exgaussian, 
+  order_effects = c('(Intercept)',
+                    'Attentional control',
+                    'Vocabulary size $^{\\text{a}}$',
+                    'Gender $^{\\text{a}}$',
+                    'Word frequency',
+                    'Number of syllables',
+                    'Word-concreteness difference',
+                    'Language-based similarity $^{\\text{b}}$',
+                    'Visual-strength difference $^{\\text{b}}$',
+                    'Stimulus onset asynchrony (SOA) $^{\\text{b}}$',
+                    'Word-concreteness difference :: Vocabulary size',
+                    'Word-concreteness difference : SOA',
+                    'Word-concreteness difference : Gender',
+                    'Language-based similarity :: Attentional control',
+                    'Visual-strength difference :: Attentional control',
+                    'Language-based similarity :: Vocabulary size',
+                    'Visual-strength difference :: Vocabulary size',
+                    'Language-based similarity : Gender',
+                    'Visual-strength difference : Gender',
+                    'Language-based similarity : SOA $^{\\text{b}}$',
+                    'Visual-strength difference : SOA $^{\\text{b}}$'),
+  interaction_symbol_x = TRUE,
+  caption = 'Weakly-informative prior model for the semantic priming study.') %>%
+  # kable_styling(latex_options = 'scale_down') %>%
+
+  # Group predictors under headings
+  pack_rows('Individual differences', 2, 4) %>% 
+  pack_rows('Target-word lexical covariates', 5, 6) %>% 
+  pack_rows('Prime--target relationship', 7, 9) %>% 
+  pack_rows('Task condition', 10, 10) %>% 
+  pack_rows('Interactions', 11, 21) %>%
+
+  # Place table close to designated position and highlight covariates
+  kable_styling(latex_options = c('hold_position', 'striped'), 
+                stripe_index = c(2, 5:7, 11:15)) %>%
+
+  # Footnote describing abbreviations, random slopes, etc. 
+  # LaTeX code used to format the text.
+  footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
+           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored predictors; \\\\textit{SE} = standard error;',
+                           'CrI = credible interval. Shaded rows contain covariates. Some interactions',
+                           'are split over two lines, with the second line indented. \\\\linebreak', 
+                           '$^{\\\\text{a}}$ By-word random slopes were included for this effect.',
+                           '$^{\\\\text{b}}$ By-participant random slopes were included for this effect.', 
+                           # After first line in the footnote, begin next lines with a dot-sized indent to correct default error.
+                           sep = ' \\\\linebreak \\\\phantom{.}'))
+
+```
+
+```{r semanticpriming-diffusepriors-model, results = 'asis'}
+
+# Rename effects in plain language and specify the random slopes
+# (if any) for each effect, in the footnote. For this purpose, 
+# superscripts are added to the names of the appropriate effects.
+# 
+# In the interactions below, word-level variables are presented 
+# first for the sake of consistency (the order does not affect 
+# the results in any way). Also in the interactions, double 
+# colons are used to inform the 'bayesian_model_table' function 
+# that the two terms in the interaction must be split into two 
+# lines.
+
+rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
+    'z_attentional_control'] = 'Attentional control'
+
+rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
+    'z_vocabulary_size'] = 'Vocabulary size $^{\\text{a}}$'
+
+rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
+    'z_recoded_participant_gender'] = 'Gender $^{\\text{a}}$'
+
+rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
+    'z_target_word_frequency'] = 'Word frequency'
+
+rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
+    'z_target_number_syllables'] = 'Number of syllables'
+
+rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
+    'z_word_concreteness_diff'] = 'Word-concreteness difference'
+
+rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
+    'z_cosine_similarity'] = 'Language-based similarity $^{\\text{b}}$'
+
+rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
+    'z_visual_rating_diff'] = 'Visual-strength difference $^{\\text{b}}$'
+
+rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed)[
+  rownames(semanticpriming_summary_diffusepriors_exgaussian$fixed) == 
+    'z_recoded_interstimulus_interval'] = 'Stimulus onset asynchrony (SOA) $^{\\text{b}}$'
 
@@
 ```
+
+\clearpage
 
@@
 The frequentist means (represented by points) are flanked by 95\\% confidence intervals.
-The Bayesian means (represented by vertical lines) are flanked by 95\\% credible intervals, in light blue (in some cases, the interval is covered up by the bar of the mean).'}
+The Bayesian means (represented by vertical lines) are flanked by 95\\% credible intervals in light blue (in some cases, the interval is occluded by the bar of the mean).'}
 
@@
 
+\clearpage
+
 ## Study 2: Semantic decision
 
-Table \@ref(tab:semanticdecision-informativepriors-model) presents the results of the informative prior model, Table \@ref(tab:semanticdecision-weaklyinformativepriors-model) presents those of the weakly-informative prior model and Table \@ref(tab:semanticdecision-diffusepriors-model) presents those of the diffuse prior model.
+Table \@ref(tab:semanticdecision-informativepriors-model) presents the results of the informative prior model, Table \@ref(tab:semanticdecision-weaklyinformativepriors-model) those of the weakly-informative prior model, and Table \@ref(tab:semanticdecision-diffusepriors-model) those of the diffuse prior model.
 
@@
   pack_rows('Individual differences', 2, 4) %>% 
-  pack_rows('Lexical covariates', 5, 6) %>% 
-  pack_rows('Semantic variables', 7, 9) %>% 
+  pack_rows('Lexicosemantic covariates', 5, 7) %>% 
+  pack_rows('Semantic variables', 8, 9) %>% 
   pack_rows('Interactions', 10, 17) %>%
@@
   # Place table close to designated position and highlight covariates
-  kable_styling(latex_options = c('HOLD_position', 'striped'), 
+  kable_styling(latex_options = c('hold_position', 'striped'), 
                 stripe_index = c(2, 5:7, 10:13)) %>%
@@
 
+\clearpage
+
 ## Study 3: Lexical decision
 
-Table \@ref(tab:lexicaldecision-informativepriors-model) presents the results of the informative prior model, Table \@ref(tab:lexicaldecision-weaklyinformativepriors-model) presents those of the weakly-informative prior model and Table \@ref(tab:lexicaldecision-diffusepriors-model) presents those of the diffuse prior model.
+Table \@ref(tab:lexicaldecision-informativepriors-model) presents the results of the informative prior model, Table \@ref(tab:lexicaldecision-weaklyinformativepriors-model) those of the weakly-informative prior model, and Table \@ref(tab:lexicaldecision-diffusepriors-model) those of the diffuse prior model.
 
@@
   pack_rows('Individual differences', 2, 3) %>% 
-  pack_rows('Lexical covariate', 4, 4) %>% 
-  pack_rows('Semantic variables', 5, 7) %>% 
+  pack_rows('Lexicosemantic covariates', 4, 5) %>% 
+  pack_rows('Semantic variables', 6, 7) %>% 
   pack_rows('Interactions', 8, 13) %>%
@@
   # Place table close to designated position and highlight covariates
-  kable_styling(latex_options = c('HOLD_position', 'striped'), 
+  kable_styling(latex_options = c('hold_position', 'striped'), 
                 stripe_index = c(4:5, 8:9)) %>%
@@
   footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
-           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored variables; \\\\textit{SE} = standard error;',
+           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored predictors; \\\\textit{SE} = standard error;',
                            'CrI = credible interval. Shaded rows contain covariates. \\\\linebreak', 

### 2022-09-26 manuscript/manuscript.tex
26092022

@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Language and vision in conceptual processing: Multilevel analysis and statistical power},
-  pdflang={en-EN},
-  pdfkeywords={conceptual processing, semantic priming, semantic decision, lexical decision, language, vision, vocabulary size, statistical power},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \setcounter{totalnumber}{4}
+\usepackage{placeins}
 \usepackage{amsmath}
@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Language and vision in conceptual processing: Multilevel analysis and statistical power},
+  pdflang={en-EN},
+  pdfkeywords={conceptual processing, semantic priming, semantic decision, lexical decision, language, vision, vocabulary size, statistical power},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
@@
 
-This manuscript is a draft and includes some appendices.
+This manuscript is a draft.
 Correspondence can be addressed to Pablo Bernabeu on \href{mailto:pcbernabeu@gmail.com}{\nolinkurl{pcbernabeu@gmail.com}}.
-All materials are available at \url{http://doi.org/10.17605/OSF.IO/UERYQ}.
+All materials needed to inspect and reproduce the present research---comprising documentation, data, analysis and results---are available at \url{http://doi.org/10.17605/OSF.IO/UERYQ}.
 
@@
 \abstract{%
-Research over the past two decades has suggested that conceptual processing depends on both language-based and vision-based information.
-We tested this interplay at three levels of the data: individuals, words and tasks.
-To this aim, we drew on three existing data sets that were composed of large samples, and implemented the paradigms of semantic priming, semantic decision and lexical decision.
-After extending these data sets with language-based and vision-based measures, we performed the analysis using mixed-effects models that included a comprehensive array of fixed effects---including covariates---and random effects.
-Overall, language-based information was found to be more important than vision-based information.
-Furthermore, in the semantic priming study---whose task required distinguishing between words and nonwords---, both language-based and vision-based information were more influential when words were presented faster.
-In addition, higher-vocabulary participants presented a greater effect of language-based similarity than lower-vocabulary participants.
-In contrast, this pattern did not hold for vision-based information, which was less relevant to the task.
-The `relevance advantage' in higher-vocabulary participants also appeared in the semantic decision and the lexical decision studies.
-Furthermore, we compare the effects of two visual information measures, and discuss the role of measurement instruments in this research topic.
-Lastly, we estimated the sample size required to reliably examine each effect of interest.
-We found that 300 participants suffice to examine language-based information contained in words, whereas more than 1,000 participants are necessary to examine vision-based information as well as the interactions between both the former variables and vocabulary size, gender and presentation speed.
+Research has suggested that conceptual processing depends on both language-based and vision-based information.
+We tested this interplay at three levels of the experimental structure: individuals, words and tasks.
+To this end, we drew on three existing data sets that were composed of large samples, and implemented the paradigms of semantic priming, semantic decision and lexical decision.
+We extended these data sets with language-based and vision-based measures, and analysed their interactions with participants' vocabulary size and gender, and with presentation speed in the semantic priming study.
+We performed the analysis using mixed-effects models that included a comprehensive array of fixed effects---including covariates---and random effects.
+First, language-based information was found to be more important than vision-based information.
+Second, in the semantic priming study---whose task required distinguishing between words and nonwords---, both language-based and vision-based information were more influential when words were presented faster.
+Third, a `task-relevance advantage' was identified in higher-vocabulary participants.
+Specifically, in lexical decision, higher-vocabulary participants were more sensitive than lower-vocabulary participants to language-based information.
+In contrast, in semantic decision, higher-vocabulary participants were more sensitive to word concreteness.
+Fourth, a human-based measure of visual information was found to be superior to a computational measure.
+These findings support the interplay between language and vision in conceptual processing, and demonstrate the influence of measurement instruments on the results.
+Last, we estimated the sample size required to reliably investigate various effects.
+We found that 300 participants were sufficient to examine the effect of language-based information contained in words, whereas more than 1,000 participants were necessary for the effect of vision-based information and for the interactions of both former variables with vocabulary size, gender and presentation speed.
+In conclusion, this power analysis reveals the need to increase sample sizes in research on perceptual simulation and individual differences.
 }
@@
 
-Over the past decades, research in psycholinguistics has suggested that conceptual processing depends on both language and embodiment systems (Barsalou et al., 2008; Connell \& Lynott, 2013; Louwerse, 2011).
-A comprehensive approach to both these systems requires a direct comparison of them.
-Studies tackling such a comparison have found that the systems are selectively engaged, following contextual demands (Connell \& Lynott, 2013; Louwerse \& Connell, 2011; Ostarek \& Huettig, 2017; Petilli et al., 2021).
-For instance, the role of perceptual simulation appears to be augmented in slower responses (Louwerse \& Connell, 2011), when words are presented more slowly (Lam et al., 2015), and in tasks prompting deeper semantic processing (Connell \& Lynott, 2013; Louwerse \& Connell, 2011; Ostarek \& Huettig, 2017; Petilli et al., 2021).
-
-In spite of the amount of evidence favouring the interplay between language and embodiment, there are at least 2 reasons to continue testing the interplay theory.
-Firstly, the coexistence of several systems in a scientific theory must be thoroughly justified, due to the value of simplicity, as epitomised by Occam's razor (Gallese \& Lakoff, 2005; Tillman et al., 2015).
-This point is particularly pressing because the language system has consistently produced larger effect sizes than the embodiment system (Banks et al., 2021; Kiela \& Bottou, 2014; Lam et al., 2015; Louwerse et al., 2015; Pecher et al., 1998; Petilli et al., 2021).
-Consequently, in this research question, we examine whether the interplay between linguistic and visual processing holds in the expected directions and at multiple levels of the experimental structure.
-
-Secondly, mixed evidence has appeared regarding some aspects of the interplay.
-For instance, whereas some studies have suggested that the language system is activated before the embodiment system (Lam et al., 2015; Louwerse \& Connell, 2011), a recent study found the opposite pattern in a lexical decision task (Petilli et al., 2021).
-Similarly, some evidence has suggested that high-vocabulary participants are more sensitive to linguistic features (Yap et al., 2017), whereas other evidence has suggested the opposite (Yap et al., 2009, 2012).
-Another case of mixed evidence regards gender: whereas some evidence has suggested that female participants draw on the language system more prominently than males (Hutchinson \& Louwerse, 2013), other research has suggested that this difference is negligible in the general population (Wallentin, 2020).
-Presumably, the scarcity of statistical power that has ailed some studies in cognitive psychology and neuroscience (Marek et al., 2022; Vasishth \& Gelman, 2021) may have affected some studies in the present topic area as well (see Lynott et al., 2014; Montero-Melis et al., 2022).
-Therefore, in this study, we re-examine longstanding questions using larger-than-average data sets, and calculate the sample size required to reliably detect a range of effects.
-
-\hypertarget{language-and-vision}{%
-\subsection{Language and vision}\label{language-and-vision}}
-
-To retest the interplay theory, we revisit previous studies that contained larger-than-average samples of participants.
-Each of our three studies is organised around one \emph{hub} study.
-In Study 1, the hub is Hutchison et al.
-(2013), which implements a semantic priming paradigm.
-In Study 2, the hub is Pexman et al.
-(2017), which implements a lexical decision paradigm.
-In Study 3, the hub is Balota et al.
-(2007), which implements a lexical decision paradigm.
-Upon this basis, we added word-level variables from other studies to tap into language (Mandera et al., 2017; Wingfield \& Connell, 2022) and vision (Lynott et al., 2020; Petilli et al., 2021).
-Additionally, we included several covariates---or nuisance variables---to allow a rigorous analysis of the effects of interest (Sassenhagen \& Alday, 2016).
-These covariates comprised participant-specific variables (e.g., attentional control), lexical variables (e.g., word frequency) and word concreteness.
+Over the last two decades, research in cognitive science has suggested that conceptual processing depends on both language and embodiment systems.
+That is, understanding words involves---on the one hand---lexical and semantic associations of an amodal kind, and---on the other hand---modality-specific associations within perceptual, motor, affective and social domains (Barsalou et al., 2008; Connell, 2019; Davis \& Yee, 2021; Khatin-Zadeh et al., 2021; Roads \& Love, 2020; Vigliocco et al., 2009).
+Studies addressing these systems have found that the language system is overall more prevalent in word processing, producing larger effect sizes (Banks et al., 2021; Kiela \& Bottou, 2014; Lam et al., 2015; Louwerse et al., 2015; Pecher et al., 1998; Petilli et al., 2021).
+More intricately, the roles of language and embodiment are modulated by the characteristics of individuals, words and tasks.
+For instance, people's individual experience with language is associated with differential effects relating to phonological, lexical and semantic features of words (Jared \& O'Donnell, 2017; Pexman \& Yap, 2018; Yap et al., 2009, 2012, 2017).
+Similarly, physical expertise and perceptual biases are associated with differences in the mental simulation of meaning (Beilock et al., 2008; Calvo-Merino et al., 2005; Vukovic \& Williams, 2015).
+Furthermore, the embodiment system is especially suited for the processing of concrete concepts---e.g., \emph{red}, \emph{building} (C.
+R.
+Jones et al., 2022; Kousta et al., 2011; Ponari, Norbury, Rotaru, et al., 2018; cf.
+Borghi et al., 2022).
+Embodied information also becomes more important in the following conditions: (I) later in the time courses of word recognition (Bernabeu et al., 2017; Louwerse \& Hutchinson, 2012; cf.
+Petilli et al., 2021) and property generation (Santos et al., 2011; Simmons et al., 2008), (II) when participants produce slower responses (Louwerse \& Connell, 2011), and (III) in tasks that elicit deeper semantic processing---e.g., semantic decision, as opposed to lexical decision (Ostarek \& Huettig, 2017; Petilli et al., 2021).
+
+In spite of the amount of evidence demonstrating the interplay between language and embodiment, there are four reasons to continue testing the interplay theory.
+First, the coexistence of several systems in a scientific theory must be thoroughly justified due to the value of simplicity (Gallese \& Lakoff, 2005; Tillman et al., 2015).
+This scrutiny is particularly necessary because the language system has consistently produced larger effect sizes than the embodiment system (Banks et al., 2021; Kiela \& Bottou, 2014; Lam et al., 2015; Louwerse et al., 2015; Pecher et al., 1998; Petilli et al., 2021).
+Therefore, it should be ruled out that the language system can suffice in all contexts.
+
+Second, it is important to examine both language and embodiment across various levels of the experimental structure---namely, individuals (i.e., due to individual differences such as vocabulary size), words (i.e., lexical and semantic variables) and tasks (i.e., experimental conditions affecting, for instance, processing speed).
+Some studies have approached this comprehensive structure but there is still room to widen the scope.
+One of the findings revealed by cross-level analyses is the influence of word processing tasks on the importance of modality-specific information.
+For instance, Connell and Lynott (2014) found that the vision-based information in words is important both for word identification (i.e., lexical decision) and for reading aloud (i.e., naming).
+In contrast, the auditory information in words is important for reading aloud but not so much for word identification.
+Another finding from cross-level research is a `task-relevance advantage' for individuals that have a greater linguistic experience.
+Specifically, Pexman and Yap (2018) found that higher-vocabulary individuals were more sensitive to task-relevant information, such as word concreteness in the semantic decision task.
+Furthermore, regarding embodiment, research has revealed that individuals who are briefly exposed to a certain sport develop neural activity that allows them to mentally simulate sport-specific actions during language processing (Beilock et al., 2008).
+While these works have covered a large swathe of the present topic, one question remains unanswered: how does an individual's linguistic experience relate to their sensivity to both linguistic and embodied information in words?
+
+Third, there is some inconclusive evidence.
+First, some findings have suggested that higher-vocabulary participants are more sensitive to language-based information---as reflected in greater semantic priming (Yap et al., 2017)---, whereas other findings have suggested the opposite (Yap et al., 2009).
+Second, some studies have suggested that the language system is activated before the embodiment system (Lam et al., 2015; Louwerse \& Connell, 2011), whereas a recent study suggested that this pattern does not hold in the lexical decision task (Petilli et al., 2021).
+Third, some evidence has suggested that female participants draw on the language system more prominently than males (Burman et al., 2008; Hutchinson \& Louwerse, 2013; Jung et al., 2019; Ullman et al., 2008), whereas other research has suggested that this difference is negligible in the general population (Wallentin, 2020).
+
+Fourth, some of the previous studies could have been affected by the scarcity of statistical power that has been identified in cognitive psychology and neuroscience (Lynott et al., 2014; Marek et al., 2022; Montero-Melis et al., 2022).
+Problematically, low-powered studies present more errors in the estimation of effect sizes and \(p\) values (Heyman et al., 2018; Loken \& Gelman, 2017; Vasishth, Mertzen, et al., 2018).
+The current studies address these four key issues.
+
+\hypertarget{present-studies}{%
+\section{The present studies}\label{present-studies}}
+
+We revisit three larger-than-average studies to investigate the interplay between language and embodiment in conceptual processing.
+We devote a study to each of the three original studies.
+Thus, Study 1 is centred on Hutchison et al.
+(2013) and uses the semantic priming paradigm.
+Study 2 is centred on Pexman et al.
+(2017) and uses the semantic decision paradigm.
+Study 3 is centred on Balota et al.
+(2007) and uses the lexical decision paradigm.
+Each of these central studies contained measures of participants' vocabulary size and gender.
+Furthermore, the core data sets were expanded by adding variables that captured the language-based information in words (Mandera et al., 2017; Wingfield \& Connell, 2022) and the vision-based information in words (Lynott et al., 2020; Petilli et al., 2021)---the latter being used to represent the embodiment system.
+One of the key questions we investigated using this array of variables was whether individual differences in vocabulary and gender modulated participants' sensivity to the language-based and vision-based information in words.
+Alongside the effects of interest, several covariates were included in the models to allow a rigorous analysis (Sassenhagen \& Alday, 2016).
+These covariates comprised measures of general cognition and lexical characteristics of the stimulus words.
+Last, in each study, we performed a statistical power analysis to help estimate the sample size needed to investigate a variety of effects in future studies.
+
+Below, we delve into the language and the embodiment components of these studies.
+
+\hypertarget{language}{%
+\subsection{Language}\label{language}}
+
+Studies have operationalised the language system at the word level using measures that capture the relationships among words without explicitly drawing on any sensory or affective modalities.
+Two main types of linguistic measures exist: those based on text corpora---dubbed \emph{word co-occurrence} measures (Bullinaria \& Levy, 2007; Petilli et al., 2021; Wingfield \& Connell, 2022)---and those based on associations collected from human participants---dubbed \emph{word association} measures (De Deyne et al., 2016, 2019).
+Notwithstanding the interrelation between word co-occurrence and word association (Planchuelo et al., 2022), co-occurrence is more purely linguistic, whereas association indirectly captures more of the sensory and affective meaning of words (De Deyne et al., 2021).
+
+\hypertarget{operationalisation-and-hypotheses}{%
+\subsubsection{Operationalisation and hypotheses}\label{operationalisation-and-hypotheses}}
+
+In Study 1 (semantic priming) and Study 2 (semantic decision), co-occurrence measures were used to represent the language system at the word level.
+Specifically, in Study 1, this measure was called \texttt{language-based\ similarity}, and it was based on the degree of text-based co-occurrence between the prime word and the target word in each trial (Mandera et al., 2017).
+In Study 2, the measure was called \texttt{word\ co-occurrence}, and it was based on the degree of text-based co-occurrence between each stimulus word and the words `abstract' and `concrete' (Wingfield \& Connell, 2022).
+In Study 3 (lexical decision), a co-occurrence measure could not be used, as the co-occurrence of words in consecutive trials could not be calculated due to the high frequency of nonword trials throughout the lexical decision task.
+Therefore, a single-word measure had to be used instead.
+Word frequency was used as it was the lexical variable, among five, that had the largest effect (see \protect\hyperlink{appendix-A-lexical-covariates}{\underline{Appendix A}}).
+
+At the individual level, language was represented by participants' vocabulary size in Studies 1 and 2, and by participants' vocabulary age in Study 3.
+Vocabulary \emph{size} and \emph{age} did not differ in any consequential way.
+They both captured the amount of vocabulary knowledge of each participant, by testing their knowledge of a small sample of pre-normed words, and thereby inferring their overall knowledge.
+
+We hypothesised that word co-occurrence, word frequency and vocabulary size would all have facilitatory effects on participants' performance, with higher values leading to shorter RTs (Pexman \& Yap, 2018; Wingfield \& Connell, 2022; Yap et al., 2009).
+
+\hypertarget{embodiment-represented-by-vision-based-information}{%
+\subsection{Embodiment represented by vision-based information}\label{embodiment-represented-by-vision-based-information}}
+
+In previous studies, the embodiment system has been represented at the word level by perceptual, motor, affective or social variables (Fernandino et al., 2022; Vigliocco et al., 2009; Wang et al., 2021).
+For instance, the perceptual modalities have often corresponded to the five Aristotelian senses---vision, hearing, touch, taste and smell (Bernabeu et al., 2017, 2021; Louwerse \& Connell, 2011)---and, less often, to interoception (Connell et al., 2018).
+Yet, out of all these senses, vision has been most frequently used in research (e.g., Bottini et al., 2021; De Deyne et al., 2021; Pearson \& Kosslyn, 2015; Petilli et al., 2021; Yee et al., 2012).
+The hegemony of vision is likely due to the central position of this sense in the human brain (Reilly et al., 2020) as well as in several languages (Bernabeu, 2018; Chen et al., 2019; Lynott et al., 2020; Miceli et al., 2021; Morucci et al., 2019; Roque et al., 2015; Speed \& Brybaert, 2021; Speed \& Majid, 2020; Vergallito et al., 2020; Winter et al., 2018; Zhong et al., 2022).
+In the present study, we focussed on vision alone both because of its prominence in cognition and because we had planned to use the present research to determine the sample size of a subsequent study that focusses on vision (indeed, the present study grew out of a statistical power analysis).
+
+\hypertarget{operationalisation-and-hypotheses-1}{%
+\subsubsection{Operationalisation and hypotheses}\label{operationalisation-and-hypotheses-1}}
+
+At the word level, we operationalised visual information using the visual strength variable from the Lancaster Sensorimotor Norms (Lynott et al., 2020).
+This variable measures the degree of visual experience associated with concepts.
+In Study 1, we created the variable \texttt{visual-strength\ difference} by subtracting the visual strength of the prime word from that of the target word, in each trial.
+Thus, visual-strength difference measured---in each trial---how much the prime word and the target word differed in their degrees of vision-based information.
+Even though we could not find any previous studies that reported the effect of visual strength (or visual-strength difference) on RT, we hypothesised a priming effect underpinned by this variable, consistent with related research (Petilli et al., 2021).
+Specifically, we hypothesised that visual-strength difference would have an inhibitory effect on participants' performance, with higher values leading to longer RTs.
+
+In Studies 2 and 3, we used the \texttt{visual\ strength} score per stimulus word.
+We hypothesised that this variable would have a facilitatory effect on participants' performance---i.e., higher values leading to shorter RTs---, consistent with related research (Petilli et al., 2021).
+
+Unlike language, vision was not examined at the individual level because the available variables were based on one self-reported value per participant (Balota et al., 2007; Hutchison et al., 2013), contrasting with the greater precision of the vocabulary measures, which consisted of multiple trials.
+Nonetheless, we recognise the need to investigate the role of perceptual experience (Muraki \& Pexman, 2021; Plaut \& Booth, 2000) alongside that of linguistic experience in the future.
 
 \hypertarget{levels-of-analysis}{%
-\section{Levels of analysis}\label{levels-of-analysis}}
-
-Experimental data in psycholinguistics often consists of various levels, such as participants, words and tasks.
-A simultaneous examination of these levels should enhance our understanding of the evidence collected (Ostarek \& Bottini, 2021)---for instance, by shedding light on the distribution of explanatory power within and across levels.
-This multilevel approach is complementary to another approach in the field that seeks to test the causal contribution of different sources of information to conceptual processing---e.g., language (Ponari, Norbury, Rotaru, et al., 2018), perception (Stasenko et al., 2014) and action (Speed et al., 2017).
-
-The three levels examined in this study are described below.
+\subsection{Levels of analysis}\label{levels-of-analysis}}
+
+Experimental data in psycholinguistics can be divided into various levels, such as individuals, words and tasks.
+The simultaneous examination of a theory across several levels is expected to enhance our understanding of the theory (Ostarek \& Bottini, 2021)---for instance, by revealing the distribution of explanatory power within and across these levels.
+Several studies have probed more than one level---for instance, word level and individual level (Aujla, 2021; Lim et al., 2020; Pexman \& Yap, 2018; Yap et al., 2009), or word level and task level (Al-Azary et al., 2022; Connell \& Lynott, 2013, 2014; Ostarek \& Huettig, 2019; Petilli et al., 2021).
+This multilevel approach is complementary to a different line of research that aims to test the causality of various sources of information in conceptual processing, such as language (Ponari, Norbury, Rotaru, et al., 2018), perception (Stasenko et al., 2014) and action (Speed et al., 2017).
+
+The three levels considered in this study---individual, word and task---are described below.
 
 \hypertarget{individual-level}{%
-\subsection{Individual level}\label{individual-level}}
-
-Variation The role of individual differences in domains such as language, perception, mental imagery and physical experience (e.g., Davies et al., 2017; Dils \& Boroditsky, 2010; Fetterman et al., 2018; Holt \& Beilock, 2006; Mak \& Willems, 2019; Miceli et al., 2022; Pexman \& Yap, 2018; Vukovic \& Williams, 2015; Yap et al., 2012, 2017).\footnote{According to Lamiell (2019), `individual differences' is a misnomer in that the methods used to analyse individual differences (e.g, regression) are not participant-specific.
-We think that this observation is mitigated in the context of mixed-effects models (as used in our current study), which incorporate by-participant random intercepts and random slopes.} Furthermore, in some topic areas in which individual differences have not featured as prominently, the data have revealed a non-trivial role of individual differences (Kos et al., 2012; Montero-Melis, 2021).
-
-\hypertarget{vocabulary-size}{%
-\subsubsection{Vocabulary size}\label{vocabulary-size}}
-
-Vocabulary size refers to the number of words a person can recognise out of a discrete set.
-Higher-vocabulary participants are expected to respond faster overall (Pexman \& Yap, 2018).
-Some previous studies have found that the effect of vocabulary size was moderated by variables related to general intelligence, such as processing speed (Ratcliff et al., 2010; Yap et al., 2012).
-Owing to those findings, and the recommendations from other studies (James et al., 2018; Pexman \& Yap, 2018; Sassenhagen \& Alday, 2016), the present studies included covariates of vocabulary size, where available.
-These covariates were measures of intelligence that were not vocabulary-based, namely, attentional control in Study 1 and information uptake in Study 2 (such a variable was not available for Study 3).
+\subsubsection{Individual level}\label{individual-level}}
+
+The individual level is concerned with the role of individual differences in domains such as language, perception, mental imagery and physical experience (e.g., Daidone \& Darcy, 2021; Davies et al., 2017; Dils \& Boroditsky, 2010; Fetterman et al., 2018; Holt \& Beilock, 2006; Mak \& Willems, 2019; Miceli et al., 2022; Pexman \& Yap, 2018; Vukovic \& Williams, 2015; Yap et al., 2009, 2012, 2017).\footnote{According to Lamiell (2019), `individual differences' is a misnomer in that the analyses used to examine those (e.g, regression) are not participant-specific.
+While this may partly hold for the current study too, the use of by-participant random effects increases the role of individuals in the analysis.} Recent studies have revealed important roles of participant-specific variables in topics where these variables have not traditionally been considered (DeLuca et al., 2019; Kos et al., 2012; Montero-Melis, 2021).
+
+Vocabulary size is used to represent the language system at the individual level.
+It measures the number of words a person can recognise out of a sample.
+Furthermore, covariates akin to general cognition---where available---were included the models (see \protect\hyperlink{covariates}{\underline{Covariates}} section below).
 
 \hypertarget{word-level}{%
-\subsection{Word level}\label{word-level}}
-
-*** to be edited *** Semantic or lexical information in words (e.g., De Deyne et al., 2021; Lam et al., 2015; Lund et al., 1995; Lund \& Burgess, 1996; Lynott et al., 2020; Mandera et al., 2017; Petilli et al., 2021; Pexman et al., 2017; Santos et al., 2011; Wingfield \& Connell, 2022)
-
-\begin{itemize}
-\item
-  Variables in this study: language-based and vision-based information;
-\item
-  Covariates: lexical variables and word concreteness;
-
-  \begin{itemize}
-  \item
-    Lexical variables: The lexical covariates were selected in each study out of the same 5 variables, which have been identified as important in previous research (Wingfield \& Connell, 2022; see \protect\hyperlink{general-statistical-analyses}{\underline{General statistical analysis}} for details).
-  \item
-    Word concreteness: Adjusting for word concreteness was deemed important due to the pervasive effect of this variable across lexical-semantic tasks (Brysbaert et al., 2014; Connell \& Lynott, 2012; Pexman \& Yap, 2018).
-Furthermore, it has been recently suggested that the effect of word concreteness does not stem from perceptual simulation, but instead from modality-independent properties of words (Bottini et al., 2021).
-  \end{itemize}
-\end{itemize}
-
-Studies have operationalised the \emph{language system} using measures that capture the relationships among words without explicitly drawing on any sensory or affective modalities.
-Two main types of linguistic measures exist: those based on text corpora---dubbed \emph{word co-occurrence} measures (Bullinaria \& Levy, 2007; Petilli et al., 2021; Wingfield \& Connell, 2022)---and those based on associations collected from human participants---dubbed \emph{word association} measures (De Deyne et al., 2016, 2019).
-Word co-occurrence is more purely linguistic, as word association captures more of the sensory and affective meaning of words (De Deyne et al., 2021).
-In Studies 1 and 2 below, word co-occurrence measures are used to represent the language system at the word level.
-In Study 3, however, such a measure could not be implemented.
-The measurement of priming across consecutive trials was not possible due to the high prevalence of nonword trials throughout the experiment.
-
-The embodiment system has been represented by measures that explicitly draw on perceptual, motor or affective modalities (Fernandino et al., 2022).
-The perceptual modalities used in studies have often matched the 5 prototypical senses---vision, hearing, touch, taste, smell (Bernabeu et al., 2017, 2021; Louwerse \& Connell, 2011)---and, less often, interoception (Connell et al., 2018).
-Yet, out of these senses, vision has been most frequently used in research (e.g., Bottini et al., 2021; De Deyne et al., 2021; Pearson \& Kosslyn, 2015; Petilli et al., 2021; Yee et al., 2012).
-The prevalence of vision in research could be due to the prevalence of this sense in the brain (Reilly et al., 2020) and in language (Lynott et al., 2020; Winter et al., 2018).
-Furthermore, for the purpose of examining individual differences along with word-level variables, vision is easier to tap into than other senses.
-For instance, the perception of visual motion can be measured using a standard computer screen (Rajananda et al., 2018).
-Owing to these reasons, the three studies reported below implement the visual modality to represent the embodiment system at the word level.
+\subsubsection{Word level}\label{word-level}}
+
+The word level is concerned with the lexical and semantic information in words (e.g., De Deyne et al., 2021; Lam et al., 2015; Lund et al., 1995; Lund \& Burgess, 1996; Lynott et al., 2020; Mandera et al., 2017; Petilli et al., 2021; Pexman et al., 2017; Santos et al., 2011; Wingfield \& Connell, 2022).
+The word-level variables of interest in this study are language-based and vision-based information (both described above).
+The covariates are lexical variables and word concreteness.
+The lexical covariates were selected in each study out of the same five variables (see \protect\hyperlink{covariates}{\underline{Covariates}} section below).
 
 \hypertarget{task-level}{%
-\subsection{Task level}\label{task-level}}
-
-*** to be edited ***
-
-\begin{itemize}
-\tightlist
-\item
-  \emph{Variable in this study:} stimulus-onset asynchrony (SOA), present in Study 1 only.\footnote{The names of all variables were slightly adjusted for this text to facilitate their understanding---for instance, by replacing underscores with spaces (see code scripts at \url{https://osf.io/ueryq}).
+\subsubsection{Task level}\label{task-level}}
+
+The task level is concerned with experimental conditions affecting, for instance, processing speed.
+In Study 1 (semantic priming), there is one task-level factor, namely, stimulus onset asynchrony (SOA), which measures the temporal interval between the onset of the prime word and the onset of the target word.\footnote{The names of all variables used in the analyses were slightly adjusted for this text to facilitate their understanding---for instance, by replacing underscores with spaces (conversions reflected in the scripts available at \url{http://doi.org/10.17605/OSF.IO/UERYQ}).
 One specific case deserves further comment.
-We use the formula of the `stimulus-onset asynchrony' (SOA) in this paper, instead of the `interstimulus interval' (ISI), as the SOA has been more commonly used in previous papers (e.g., Hutchison et al., 2013; Pecher et al., 1998; Petilli et al., 2021; Yap et al., 2017).
-The difference between these formulas is that the ISI does not count the presentation of the prime word Di Lollo et al.
-(2004).
-In the current study, the presentation of the prime word lasts 150 ms.
-Thus, the 200-ms SOA is equivalent to an ISI of 50 ms, and the 1,200-ms SOA corresponds to an ISI of 1,050 ms (Hutchison et al., 2013).
-The use of either formula in the analysis would not change our results, as we recoded the levels of the factor as -0.5 and +0.5, and then \(z\)-scored those, following the advice of Brauer and Curtin (2018).
-In our analyses (\url{https://osf.io/ueryq}), we used the ISI formula as it was the one present in the data set of Hutchison et al.
-(2013) (retrieved from \url{https://www.montana.edu/attmemlab/documents/all\%20ldt\%20subs_all\%20trials3.xlsx}}).
-\end{itemize}
-
-In addition, the different paradigms applied across the three studies can be compared, albeit cautiously as the studies differ in other influential ways, such as the number of participants and stimulus words.
-The three tasks examined in the present studies are likely to reflect different degrees of semantic depth, in the following order (for background, see Connell \& Lynott, 2013; Lam et al., 2015; Ostarek \& Huettig, 2017; Versace et al., 2021; Wingfield \& Connell, 2022).
+We use the formula of the SOA in this paper, instead of the `interstimulus interval' (ISI)---which we used in the analysis---, as the SOA has been more commonly used in previous papers (e.g., Hutchison et al., 2013; Pecher et al., 1998; Petilli et al., 2021; Yap et al., 2017).
+In our analysis, we used the ISI formula as it was the one present in the data set of Hutchison et al.
+(2013)---retrieved from \url{https://www.montana.edu/attmemlab/documents/all\%20ldt\%20subs_all\%20trials3.xlsx}.
+The only difference between these formulas is that the ISI does not count the presentation of the prime word.
+In the current study (Hutchison et al., 2013), the presentation of the prime word lasted 150 ms.
+Therefore, the 50 ms ISI is equivalent to a 200 ms SOA, and the 1,050 ms ISI is equivalent to a 1,200 ms SOA.
+The use of either formula in the analysis would not affect our results, as the ISI conditions were recoded as -0.5 and 0.5 (Brauer \& Curtin, 2018).} In Studies 2 and 3, there are no task-level variables.
+
+Beyond task-level variables, there is an additional source of task-related information across the three studies---namely, the experimental paradigm used in each study (i.e., semantic priming, semantic decision and lexical decision).
+Indeed, it is possible to examine how the effects vary across these paradigms (see Wingfield \& Connell, 2022).
+This comparison, however, must be considered cautiously due to the existence of other non-trivial differences across these studies, such as the numbers of observations.
+With this caveat noted, the tasks used across these studies likely elicit varying degrees of semantic depth, as ordered below (see Balota \& Lorch, 1986; Barsalou et al., 2008; Becker et al., 1997; de Wit \& Kinoshita, 2015; Joordens \& Becker, 1997; Lam et al., 2015; Muraki \& Pexman, 2021; Ostarek \& Huettig, 2017; Versace et al., 2021; Wingfield \& Connell, 2022).
 
@@
 \item
-  \textbf{Semantic decision} (Study 2) likely elicits the deepest semantic processing, as the instructions of this task ask for a concreteness judgement.
-In this task, participants are asked to classify words as abstract or concrete.
+  \emph{Semantic decision} (Study 2) likely elicits the deepest semantic processing, as the instructions of this task ask for a concreteness judgement.
+In this task, participants are asked to classify words as abstract or concrete, which elicits deeper semantic processing than the task of identifying word forms---i.e., lexical decision (de Wit \& Kinoshita, 2015).
 \item
-  \textbf{Semantic priming} (Study 1).
-The task in the semantic priming paradigm is often lexical decision, as in Study 1 herein.
-The fundamental characteristic of this paradigm is that, in each trial, a prime word is presented for a very short period before the target word.
-The prime word is not relevant to the task.
-Nonetheless, participants process both the prime word and the target word, and this combination allows researchers to analyse responses based on the relationship between those words.
-Therefore, this paradigm is more deeply semantic than the lexical decision paradigm.
-Indeed, slower responses in semantic priming studies---reflecting difficult lexical decisions---have been linked to larger priming effects (Balota et al., 2008; Hoedemaker \& Gordon, 2014; Yap et al., 2013), suggesting a degree of semantic association that does not appear in the standard lexical decision paradigm.
+  \emph{Semantic priming} (Study 1).
+The task administered to participants in semantic priming studies is often lexical decision, as in Study 1 below.
+The fundamental characteristic of semantic priming is that, in each trial, a prime word is briefly presented before the target word.
+The prime word is not directly relevant to the task, as participants respond to the target word.
+Nonetheless, participants normally process both the prime word and the target word in each trial, and this combination allows researchers to analyse responses based on the prime--target relationship.
+In this regard, this paradigm could be considered more deeply semantic than lexical decision.
+Indeed, slower responses in semantic priming studies---reflecting difficult lexical decisions---have been linked to larger priming effects (Balota et al., 2008; Hoedemaker \& Gordon, 2014; Yap et al., 2013), revealing a degree of semantic association that has not been identified in the lexical decision task.
 \item
-  \textbf{Lexical decision} (Study 3) is likely the semantically-shallowest task (see Balota \& Lorch, 1986; Becker et al., 1997; Connell \& Lynott, 2013; de Wit \& Kinoshita, 2015; Joordens \& Becker, 1997; Ostarek \& Huettig, 2017).
+  \emph{Lexical decision} (Study 3) is likely the semantically-shallowest task of these three, as it focusses solely on the identification of word forms.
 \end{enumerate}
 
-\hypertarget{interactions-across-levels}{%
-\subsection{Interactions across levels}\label{interactions-across-levels}}
-
-The three levels are strongly intertwined, and studies have probed into more than one level at once: for instance, word level and individual level (Aujla, 2021; Lim et al., 2020; Pexman \& Yap, 2018; Yap et al., 2009), or word level and task level (Al-Azary et al., 2022; Connell \& Lynott, 2013; Ostarek \& Huettig, 2019; Petilli et al., 2021).
-Thus, hypotheses are available regarding interactions across levels, as addressed below.
-
-\hypertarget{vocabulary-size-and-linguistic-features}{%
-\subsubsection{Vocabulary size and linguistic features}\label{vocabulary-size-and-linguistic-features}}
-
-Three hypotheses exist regarding the interaction between vocabulary size and lexical-semantic features.
-First, higher-vocabulary participants---compared to lower-vocabulary ones---might be more sensitive to linguistic features, thanks to a larger number of semantic associations (Connell, 2019; Landauer et al., 1998; Louwerse et al., 2015; Paivio, 1990; Pylyshyn, 1973).
+\hypertarget{hypotheses}{%
+\subsection{Hypotheses}\label{hypotheses}}
+
+The central objective of the present studies is the simultaneous investigation of language-based and vision-based information, along with the interactions between each of those and vocabulary size, gender and presentation speed (i.e., SOA).
+Previous studies have examined subsets of these effects using the same data sets we are using (Balota et al., 2007; Petilli et al., 2021; Pexman et al., 2017; Pexman \& Yap, 2018; Wingfield \& Connell, 2022; Yap et al., 2012, 2017).
+Out of these studies, only Petilli et al.
+(2021) investigated \emph{both} language and vision.
+However, in contrast to our present study, Petilli et al.~did not examine the role of vocabulary size or any other individual differences, instead collapsing the data across participants.
+
+In addition to main effects of the aforementioned variables, our three studies have four interactions in common: (1a) language-based information \(\times\) vocabulary size, (1b) vision-based information \(\times\) vocabulary size, (2a) language-based information \(\times\) participants' gender, and (2b) vision-based information \(\times\) participants' gender.
+In addition, Study 1 contained two further interactions: (3a) language-based information \(\times\) SOA, (3b) vision-based information \(\times\) SOA (note that the names of some predictors vary across studies, as detailed in the \protect\hyperlink{language}{\underline{present studies}} section above).
+Each interaction and the corresponding hypotheses are addressed below.
+
+\hypertarget{a.-language-based-information-times-vocabulary-size}{%
+\subsubsection{\texorpdfstring{1a.
+Language-based information \(\times\) vocabulary size}{1a.
+Language-based information \textbackslash times vocabulary size}}\label{a.-language-based-information-times-vocabulary-size}}
+
+We outline three hypotheses supported by literature regarding the interaction between language-based information and participants' vocabulary size.
+
+\begin{itemize}
+\item
+  \emph{Larger vocabulary, larger effects.} Higher-vocabulary participants might be more sensitive to linguistic features than lower-vocabulary participants, thanks to a larger number of semantic associations (Connell, 2019; Landauer et al., 1998; Louwerse et al., 2015; Paivio, 1990; Pylyshyn, 1973).
 For instance, Yap et al.
-(2017) observed a larger semantic priming effect in higher-vocabulary participants from (Hutchinson \& Louwerse, 2013).
-The second hypothesis, in contrast, states that higher-vocabulary participants would be \emph{less} sensitive to linguistic features, thanks to a more automatic process (Perfetti \& Hart, 2002).
-For instance, Yap et al.
-(2009) observed a smaller semantic priming effect in higher-vocabulary participants.
+(2017) revisited the semantic priming study of Hutchinson and Louwerse (2013) and observed a larger semantic priming effect in higher-vocabulary participants.
+\item
+  \emph{Larger vocabulary, smaller effects.} Higher-vocabulary participants might be less sensitive to linguistic features, thanks to a more automated language processing (Perfetti \& Hart, 2002).
+Some of the evidence aligned with this hypothesis was obtained by Yap et al.
+(2009), who observed a smaller semantic priming effect in higher-vocabulary participants.
 Similarly, Yap et al.
 (2012) found that higher-vocabulary participants in a lexical decision task (Balota et al., 2007) were less sensitive to a cluster of lexical and semantic features (i.e., word frequency, semantic neighborhood density and number of senses).
-Last, the third hypothesis proposes that higher-vocabulary participants might present a selective sensitivity, tailored to the task.
-For instance, Pexman and Yap (2018) analysed the semantic decision task of Pexman et al.
-(2017), in which participants assessed the concreteness of words.
-Pexman and Yap found that higher-vocabulary participants---compared to lower-vocabulary ones---were more sensitive to word concreteness and less sensitive to word frequency and age of acquisition, which were less relevant to the task (also see Lim et al., 2020).
-The three hypotheses herein were tested in the present study by revisiting some of the aforementioned studies (Balota et al., 2007; Hutchinson \& Louwerse, 2013; Pexman et al., 2017).
-
-\hypertarget{vocabulary-size-and-visual-strength}{%
-\subsubsection{Vocabulary size and visual strength}\label{vocabulary-size-and-visual-strength}}
-
-Research demonstrating the interplay between linguistic and embodied information (Connell, 2019; Louwerse et al., 2015; Paivio, 1990) affords the hypothesis that lower-vocabulary participants---compared to higher-vocabulary ones---might profit more from sensory, motor, affective and social associations of the words.
-
-\hypertarget{gender-and-linguistic-features}{%
-\subsubsection{Gender and linguistic features}\label{gender-and-linguistic-features}}
-
-In addition, the language system is expected to be more important in female than male participants (Burman et al., 2008; Hutchinson \& Louwerse, 2013; Jung et al., 2019; Ullman et al., 2008), provided that this interaction effect is not too small to be detected (Wallentin, 2020).
-
-In another study, Schmidtke et al.
-(2018) collected human ratings on the association between words that make up compounds.
-Some compounds were found to be relatively transparent---e.g., \emph{doorbell}---, and others relatively opaque---e.g., \emph{deadline}.
-Furthermore, Schmidtke et al.
-(2018) found an interaction between semantic transparency and participants' reading experience (the latter measure encompassing vocabulary size and exposure to printed materials): namely, more experienced readers processed transparent compounds more quickly than opaque ones, whereas less experienced readers processed opaque compounds more quickly than transparent ones.
-This interaction suggests \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_.
-Thus, \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_.
-
-\hypertarget{power-analysis}{%
-\subsection{Power analysis}\label{power-analysis}}
+\item
+  \emph{Larger vocabulary, more task-relevant effects.} Higher-vocabulary participants might present a greater sensitivity to task-relevant variables, borne out of their greater linguistic experience, relative to lower vocabulary participants.
+This would be consistent with the findings of Pexman and Yap (2018), who revisited the semantic decision study of Pexman et al.
+(2017).
+The semantic decision task of the Pexman et al.~consisted of classifying words as abstract or concrete.
+Pexman and Yap found that word concreteness---a very relevant source of information for this task---was more influential in higher-vocabulary participants than in lower-vocabulary ones.
+In contrast, word frequency and age of acquisition----not as relevant to the task--were more influential in lower-vocabulary participants (also see Lim et al., 2020).
+In our present studies, we set our hypotheses regarding the `task-relevance advantage' by working under the assumption that the language-based information in words---represented by one variable in each study---is important for the three tasks, given the large effects of language across tasks (Banks et al., 2021; Kiela \& Bottou, 2014; Lam et al., 2015; Louwerse et al., 2015; Pecher et al., 1998; Petilli et al., 2021).
+Therefore, the relevance hypothesis predicts that higher-vocabulary participants---compared to lower-vocabulary ones---will be more sensitive to language-based information (as represented by \texttt{language-based\ similarity} in Study 1, \texttt{word\ co-occurrence} in Study 2, and \texttt{word\ frequency} in Study 3).
+\end{itemize}
+
+\hypertarget{b.-vision-based-information-times-vocabulary-size}{%
+\subsubsection{\texorpdfstring{1b.
+Vision-based information \(\times\) vocabulary size}{1b.
+Vision-based information \textbackslash times vocabulary size}}\label{b.-vision-based-information-times-vocabulary-size}}
+
+To our knowledge, no previous studies have investigated the interaction between vision-based information and participants' vocabulary size.
+We entertained two hypotheses.
+First, lower-vocabulary participants might be more sensitive to visual strength than higher-vocabulary participants.
+In this way, lower-vocabulary participants might \emph{compensate} for the disadvantage on the language side.
+Second, we considered the possibility that there were no interaction effect.
+
+\hypertarget{a.-language-based-information-times-gender}{%
+\subsubsection{\texorpdfstring{2a. Language-based information \(\times\) gender}{2a. Language-based information \textbackslash times gender}}\label{a.-language-based-information-times-gender}}
+
+We entertained two hypothesis regarding the interaction between language-based information and participants' gender: (a) that the language system would be more important in female participants than in males (Burman et al., 2008; Hutchinson \& Louwerse, 2013; Jung et al., 2019; Ullman et al., 2008), and (b) that this interaction effect would be absent, as a recent review suggested that gender differences are negligible in the general population (Wallentin, 2020).
+
+\hypertarget{b.-vision-based-information-times-gender}{%
+\subsubsection{\texorpdfstring{2b. Vision-based information \(\times\) gender}{2b. Vision-based information \textbackslash times gender}}\label{b.-vision-based-information-times-gender}}
+
+To our knowledge, no previous studies have investigated the interaction between vision-based information and participants' gender.
+We entertained two hypothesis.
+Our first hypothesis was that this interaction would stand opposite to the interaction between language and gender.
+That is, if female participants were to present a greater role of language-based information, male participants would present a greater role of vision-based information, thereby compensating for the disadvantage on the language side.
+Our second hypothesis was the absence of this interaction effect (see Wallentin, 2020).
+
+\hypertarget{a.-language-based-information-times-soa}{%
+\subsubsection{\texorpdfstring{3a. Language-based information \(\times\) SOA}{3a. Language-based information \textbackslash times SOA}}\label{a.-language-based-information-times-soa}}
+
+Previous research predicts that language-based information will have a larger effect with the short SOA than with the long one (Lam et al., 2015; Petilli et al., 2021)), which also aligns with research demonstrating the fast activation of language-based information (Louwerse \& Connell, 2011; Santos et al., 2011; Simmons et al., 2008).
+
+\hypertarget{b.-vision-based-information-times-soa}{%
+\subsubsection{\texorpdfstring{3b. Vision-based information \(\times\) SOA}{3b. Vision-based information \textbackslash times SOA}}\label{b.-vision-based-information-times-soa}}
+
+The interaction between vision-based information and SOA allows three hypotheses.
+First, some previous research predicts that the role of vision-based information will be more prevalent with the long SOA than with the short one (Louwerse \& Connell, 2011; Santos et al., 2011; Simmons et al., 2008; also see Barsalou et al., 2008).
+Second, in contrast, other research (Petilli et al., 2021) based on the same data that we are analysing (Hutchison et al., 2013) predicts vision-based priming only with the short SOA (200 ms), and not with the long one (1,200 ms).
+Third, other research does not predict any vision-based priming effect (Hutchison, 2003; Ostarek \& Huettig, 2017; Pecher et al., 1998; Yee et al., 2012).
+In this regard, some studies have observed vision-based priming when the task was preceded by another task that required attention to visual features of concepts (Pecher et al., 1998; Yee et al., 2012), but the present data (Hutchison et al., 2013) does not contain such a prior task.
+
+\hypertarget{language-and-vision-across-studies}{%
+\subsubsection{Language and vision across studies}\label{language-and-vision-across-studies}}
+
+Next, we consider our hypotheses regarding the role of language and vision across studies.
+Yet, before addressing those, we reiterate that caution is required due to the existence of other differences across these studies, such as the number of observations.
+First, we hypothesise that language-based information will be relevant in the three studies due to the consistent importance of language observed in past studies (Banks et al., 2021; Kiela \& Bottou, 2014; Lam et al., 2015; Louwerse et al., 2015; Pecher et al., 1998; Petilli et al., 2021).
+Second, the extant evidence regarding vision-based information is less conclusive.
+Some studies have observed effects of vision-based information (Connell \& Lynott, 2014; Flores d'Arcais et al., 1985; Petilli et al., 2021; Schreuder et al., 1984), whereas others have not (Hutchison, 2003; Ostarek \& Huettig, 2017), and a third set of studies have only observed them when the critical task was preceded by a task that required attention to visual features of concepts (Pecher et al., 1998; Yee et al., 2012).
+Based on these precedents, we hypothesise that vision-based information will be relevant in semantic decision, whereas it might or might not be relevant in semantic priming and in lexical decision.
+
+\hypertarget{statistical-power-analysis}{%
+\subsection{Statistical power analysis}\label{statistical-power-analysis}}
 
@@
 Out of these, sample size is the factor that can best be controlled by researchers (Kumle et al., 2021).
-The three studies we present below, containing larger-than-average sample sizes, offer an opportunity to conduct an a-priori power analysis to help determine the sample size of future studies (Albers \& Lakens, 2018).
+The three studies we present below, containing larger-than-average sample sizes, offer an opportunity to perform an a-priori power analysis to help determine the sample size of future studies (Albers \& Lakens, 2018).
 
@@
 
-Insufficient statistical power lowers the reliability of effect sizes, and increases the likelihood of false positive results---i.e., Type I error---and of false negative results---i.e., Type II error (Gelman \& Carlin, 2014; Loken \& Gelman, 2017; Tversky \& Kahneman, 1971; von der Malsburg \& Angele, 2017).
+Insufficient statistical power lowers the reliability of effect sizes, and increases the likelihood of false positive results---i.e., Type I errors---as well as the likelihood of false negative results---i.e., Type II errors (Gelman \& Carlin, 2014; Loken \& Gelman, 2017; Tversky \& Kahneman, 1971; von der Malsburg \& Angele, 2017).
 For instance, Vasishth and Gelman (2021) illustrate how, in low-powered studies, effect sizes associated with significant results tend to be overestimated (also see Vasishth, Mertzen, et al., 2018).
 
-Over the past decade, replication studies and power analyses have uncovered insufficient sample sizes in psychology (Brysbaert, 2019; Lynott et al., 2014; Montero-Melis et al., 2017, 2022; Rodríguez-Ferreiro et al., 2020; Vasishth, Mertzen, et al., 2018).
-In the neighbouring field of neuroscience, Marek et al.
-(2022) recently estimated the sample size that is required to reliably study the mapping between individual differences, such as fluid intelligence, and brain structures.
-Marek et al.~found that the current median of 25 participants contributing to one of these studies contrasted with the thousands of participants---around 10,000---that would be needed for a well-powered study (also see Button et al., 2013).
-
-More topic-specific power analyses are necessary due to three reasons.
-Firstly, power analyses provide greater certainty on the reasons behind non-replications (e.g., Open Science Collaboration, 2015), and behind non-significant results.
-Indeed, insufficient power is one of the possible reasons, alongside procedural errors or subtler methodological differences, and publication bias (Anderson et al., 2016; Barsalou, 2019; Corker et al., 2014; Gilbert et al., 2016; Williams, 2014).
-Currently, if we consider---for instance---research on individual differences, we will find several non-significant results, both in behavioural studies (e.g., Hedge et al., 2018; Rodríguez-Ferreiro et al., 2020; for a Bayes factor analysis, see Rouder \& Haaf, 2019) and in neuroscientific studies (e.g., Diaz et al., 2021).
-A greater availability of power analyses in specific topics will at least shed light on the role of power in the results.
-Secondly, power analyses facilitate the identification of sensible sample sizes for future studies.
-Thirdly, power analyses help maximise the use of research funding in the long term by fostering studies that are more replicable (see Vasishth \& Gelman, 2021).
-
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
-The analytical method was largely similar across the three studies. Below, we present the commonalities in the statistical analyses and in the power analyses.
-
-\hypertarget{general-statistical-analyses}{%
-\subsection{General method for statistical analysis}\label{general-statistical-analyses}}
-
-The statistical analysis was designed to examine the unique contribution of each effect of interest.
-In all three studies, the dependent variable---response time (RT)---was \(z\)-scored around each participant's mean to curb the influence of each participant's baseline speed (Balota et al., 2007; Kumar et al., 2020; Lim et al., 2020; Pexman et al., 2017; Pexman \& Yap, 2018; Yap et al., 2012, 2017).
+Over the past decade, replication studies and power analyses have uncovered insufficient sample sizes in psychology (Brysbaert, 2019; Heyman et al., 2018; Lynott et al., 2014; Montero-Melis et al., 2017, 2022; Rodríguez-Ferreiro et al., 2020; Vasishth, Mertzen, et al., 2018).
+In one of these studies, Heyman et al.
+(2018) demonstrated that increasing the sample size resulted in an increase of the reliability of the estimates, which in turn lowered the Type I error rate and the Type II error rate---i.e., false negative and false positive results, respectively.
+Calls for larger sample sizes have also been voiced in the field of neuroscience.
+For instance, Marek et al.
+(2022) estimated the sample size that would be required to reliably study the mapping between individual differences---such as general cognition---and brain structures.
+The authors found that the current median of 25 participants in each of these studies contrasted with the thousands of participants---around 10,000---that would be needed for a well-powered study (also see Button et al., 2013).
+
+More topic-specific power analyses are necessary due to several reasons.
+First, power analyses provide greater certainty on the reasons behind non-replications (e.g., Open Science Collaboration, 2015), and behind non-significant results at large.
+Non-replications are not solely explained by methodological differences across studies, questionable research practices and publication bias (Anderson et al., 2016; Barsalou, 2019; Corker et al., 2014; Gilbert et al., 2016; Williams, 2014; Zwaan, 2014; also see Tiokhin et al., 2021).
+In addition to these factors, a lack of statistical power can cause non-replications and non-significant results (see Loken \& Gelman, 2017; Vasishth \& Gelman, 2021).
+
+Regarding non-significant results, it is worthwhile to consider some examples from research on individual differences.
+In this literature, there is a body of non-significant results, both in behavioural studies (Daidone \& Darcy, 2021; Hedge et al., 2018; Muraki \& Pexman, 2021; Ponari, Norbury, Rotaru, et al., 2018; Rodríguez-Ferreiro et al., 2020; for a Bayes factor analysis, see Rouder \& Haaf, 2019) and in neuroscientific studies (Diaz et al., 2021).
+A greater availability of power analyses within this topic area and others will at least shed light on the influence of statistical power on the results.
+Furthermore, power analyses facilitate the identification of sensible sample sizes for future studies.
+Last, it should be noted that although increasing the statistical power comes at a cost in the short term, power analyses will help maximise the use of research funding in the long term by fostering more replicable research (see Vasishth \& Gelman, 2021; remember Open Science Collaboration, 2015).
+
+\hypertarget{general-methods}{%
+\section{General methods}\label{general-methods}}
+
+The analytical method was broadly similar across the three studies. Below, we present the commonalities in the statistical analysis and in the power analysis.
+
+\hypertarget{covariates}{%
+\subsection{Covariates}\label{covariates}}
+
+Several covariates---or nuisance variables---were included in each study to allow a rigorous analysis of the effects of interest (Sassenhagen \& Alday, 2016).
+Unlike the effects of interest, these covariates were not critical to our research question (i.e., the interplay between language-based and vision-based information).
+They comprised participant-specific variables (e.g., attentional control), lexical variables (e.g., word frequency) and word concreteness.
+The covariates are distinguished from the effects of interest in the results table(s) in each study.
+The three kinds of covariates included were as follows.
+
+Participant-specific covariates were measures akin to general cognition, and were included because some studies have found that the effect of vocabulary size was moderated by general cognition variables such as processing speed (Ratcliff et al., 2010; Yap et al., 2012).
+Similarly, research has evidenced the role of attentional control (Hutchison et al., 2014; Yap et al., 2017), and authors have expressed the desirability of including such covariates in models (James et al., 2018; Pexman \& Yap, 2018).
+Therefore, we included in the analyses a individual measure of `general cognition', where available.
+These measures were available in the first two studies, and they indexed task performance abilities that were different from vocabulary knowledge.
+We refer to them by their more specific names in each study.\footnote{The general cognition measures could also be dubbed general or fluid intelligence, but we think that cognition is more appropriate in our present context.} In Study 1, the measure used was \texttt{attentional\ control} (Hutchison et al., 2013).
+In Study 2, it was \texttt{information\ uptake} (Pexman \& Yap, 2018).
+In Study 3, such a covariate was not used as it was not available in the data set of Balota et al.
+(2007).
+
+Lexical covariates were selected in every study out of the same five variables, which had been used as covariates in Wingfield and Connell (2022; also see Petilli et al., 2021).
+They comprised: number of letters (i.e., orthographic length), word frequency, number of syllables (both the latter from Balota et al., 2007), orthographic Levenshtein distance (Yarkoni et al., 2008) and phonological Levenshtein distance (Suárez et al., 2011; Yap \& Balota, 2009).
+The selection among these candidates was performed because some of them were highly intercorrelated---i.e., \(r\) \textgreater{} .70 (Dormann et al., 2013; Harrison et al., 2018).
+The correlations and the selection models are available in \protect\hyperlink{appendix-A-lexical-covariates}{\underline{Appendix A}}.
+
+Word concreteness was included due to the pervasive effect of this variable across lexical and semantic tasks (Brysbaert et al., 2014; Connell \& Lynott, 2012; Pexman \& Yap, 2018), and due to the sizable correlations (\(r\) \textgreater{} .30) between word concreteness and some other predictors, such as visual strength (see correlation figures in each study).
+Furthermore, the role of word concreteness has been contested, with some research suggesting that its effect stems from perceptual simulation (Connell \& Lynott, 2012) versus other research suggesting that the effect is amodal (Bottini et al., 2021).
+In passing, we will bring our results to bear on the role of word concreteness.
+
+\hypertarget{data-preprocessing-and-statistical-analysis}{%
+\subsection{Data preprocessing and statistical analysis}\label{data-preprocessing-and-statistical-analysis}}
+
+In the three studies, the statistical analysis was designed to investigate the contribution of each effect of interest.
+The following preprocessing steps were applied.
+First, incorrect responses were removed.
+Second, nonword trials were removed (only necessary in Studies 1 and 3).
+Third, too fast and too slow responses were removed.
+For the latter purpose, we applied the same thresholds that had been applied in each of the original studies.
+That is, in Study 1, we removed responses faster than 200 ms or slower than 3,000 ms (Hutchison et al., 2013).
+In Study 2, we removed responses faster than 250 ms or slower than 3,000 ms (Pexman \& Yap, 2018).
+In Study 3, we removed responses faster than 200 ms or slower than 4,000 ms (Balota et al., 2007).
+Next, the dependent variable---response time (RT)---was \(z\)-scored around each participant's mean to curb the influence of each participant's baseline speed (Balota et al., 2007; Kumar et al., 2020; Lim et al., 2020; Pexman et al., 2017; Pexman \& Yap, 2018; Yap et al., 2012, 2017).
 This was important because the size of experimental effects is known to increase with longer RTs (Faust et al., 1999).
 Next, binary predictors were recoded into continuous variables (Brauer \& Curtin, 2018).
-Specifically, participants' gender was recoded as follows: male = -0.5; female = 0.5; NA = 0.
-The SOAs in Study 1 were recoded as follows: 150 ms = -0.5; 1,200 ms = 0.5.
-Finally, following Brauer and Curtin (2018), all predictors were \(z\)-scored (i.e., \(M \approx\) 0, \(SD \approx\) 1).
-
-Several covariates---or nuisance variables---were included in each study, to allow a rigorous analysis of the effects of interest (Sassenhagen \& Alday, 2016).
-Unlike the effects of interest, these covariates were not critical to the research question.
-They comprised participant-specific variables (e.g., attentional control), lexical variables (e.g., word frequency) and word concreteness.
-
-The lexical covariates were selected in every study out of the same 5 variables, which had been used as covariates in Wingfield and Connell (2022; also see Petilli et al., 2021).
-They comprised: number of letters (i.e., orthographic length), word frequency, number of syllables (both the latter from Balota et al., 2007), orthographic Levenshtein distance (Yarkoni et al., 2008) and phonological Levenshtein distance (Suárez et al., 2011).
-The selection among these candidates was performed because some of them were highly intercorrelated---i.e., \(r\) \textgreater{} .70 (Dormann et al., 2013; Harrison et al., 2018).
-The correlations and the selection models are available in \protect\hyperlink{appendix-A-lexical-covariates}{\underline{Appendix A}}.
-
-Word concreteness was included due to its correlation with visual strength, as shown in each study below.
-A recent study suggested that the psycholinguistic import of concreteness is fundamentally lexical, and does not involve perceptual simulation (Bottini et al., 2021).
-
-The participant-specific covariates were measures akin to fluid intelligence, and were included due to their relationship with vocabulary size, as previous studies have expressed the desirability of including such covariates (James et al., 2018; Pexman \& Yap, 2018).
-As described in each study, these covariates were used in Studies 1 and 2, but not in Study 3, as such a variable was not available.
+Specifically, participants' gender was recoded as follows: Female = 0.5, X = 0, Male = -0.5.
+The SOAs in Study 1 were recoded as follows: 200 ms = -0.5; 1,200 ms = 0.5.
+Next, the data sets were trimmed by removing rows that lacked values on any variable, and by also removing RTs that were more than 3 standard deviations (\(SD\)) away from the mean (\(M\)).
+The nesting factors applied in the trimming are specified in each study.
+Finally, all predictors were \(z\)-scored, resulting in \(M \approx\) 0 and \(SD \approx\) 1 (values not exact as the variables were not normally distributed).
+More specifically, between-item predictors---i.e., word-level variables (e.g., language-based information) and task-level variables (e.g., SOA)---were \(z\)-scored around each participant's own mean (Brauer \& Curtin, 2018).
 
@@
 
-The participants and the stimulus items were crossed in the three studies.
-That is, each participant was presented with a subset of the stimulus words.
+With regard to random effects, participants and stimuli were \emph{crossed} in the three studies.
+That is, each participant was presented with a subset of the stimuli.
 Conversely, each word was presented to a subset of participants.
@@
 These models included a maximal random-effects structure, with by-participant and by-item random intercepts, and the appropriate random slopes for all effects of interest (Barr et al., 2013).
-In the semantic priming study, the items were prime-target pairs, whereas in the semantic decision and lexical decision studies, the items were individual words.
+In the semantic priming study, the items were prime--target pairs, whereas in the semantic decision and lexical decision studies, the items were individual words.
 In the case of interactions, random slopes were included only when the interacting variables varied within the same unit (Brauer \& Curtin, 2018)---e.g., an interaction of two variables varying within participants (only present in Study 1).
 Where required due to convergence warnings, random slopes for covariates were removed, as inspired by Remedy 11 from Brauer and Curtin (2018).
-In this regard, whereas Brauer and Curtin (2018) contemplate the removal of random slopes for covariates only when the covariates are not interacting with any effects of interest, we removed random slopes for covariates even if they interacted with effects of interest because these interactions were covariates themselves (covariates are indicated in the results tables).
-
-To avoid inflating the Type I error rate (false positives), the random slopes for the effects of interest (indicated by non-shaded rows in the results tables below) were never removed (see Table 17 in Brauer \& Curtin, 2018; for an example of this approach, see Diaz et al., 2021).
+In this regard, whereas Brauer and Curtin (2018) contemplate the removal of random slopes for covariates only when the covariates are not interacting with any effects of interest, we removed random slopes for covariates even if they interacted with effects of interest because these interactions were covariates themselves.
+
+To avoid an inflation of the Type I error rate---i.e., false positives---, the random slopes for the effects of interest (as indicated in each study) were never removed (see Table 17 in Brauer \& Curtin, 2018; for an example of this approach, see Diaz et al., 2021).
 This approach arguably provides a better protection against false positives (Barr et al., 2013; Brauer \& Curtin, 2018; Singmann \& Kellen, 2019) than the practice of removing random slopes when they do not significantly improve the fit (Baayen et al., 2008; Bates et al., 2015; e.g., Bernabeu et al., 2017; Pexman \& Yap, 2018; but also see Matuschek et al., 2017).
@@
 
-\(P\) values were calculated using the Kenward-Roger approximation for degrees of freedom (Luke, 2017), in the R package `lmerTest', Version 3.1-3 (Kuznetsova et al., 2017).
+\(P\) values were calculated using the Kenward-Roger approximation for degrees of freedom (Luke, 2017) in the R package `lmerTest', Version 3.1-3 (Kuznetsova et al., 2017).
 The latter package in turn used `lme4', Version 1.1-26 (Bates et al., 2015; Bates et al., 2021).
@@
 Diagnostics regarding convergence and normality are provided in \protect\hyperlink{appendix-B-frequentist-analysis-diagnostics}{\underline{Appendix B}}.
-Effects that were non-significant or very small are best interpreted by considering their 95\% confidence intervals (Cumming, 2014), which are shown in the results tables as well as in plots.
+Effects that were non-significant or very small are best interpreted by considering their 95\% confidence intervals, and the 95\% credible intervals (i.e., the Bayesian counterpart) where available (Cumming, 2014).
 
@@
 A Bayesian analysis was performed to complement the estimates that had been obtained in the frequentist analysis.
-Whereas the focus of the frequentist analysis had been hypothesis testing, using \(p\) values, the purpose of the Bayesian analysis was parameter estimation.
-Accordingly, we estimated the posterior distribution of every effect, without calculating Bayes factors (for other examples of this approach, see Milek et al., 2018; Pregla et al., 2021; Rodríguez-Ferreiro et al., 2020; for comparisons between estimation and hypothesis testing, see Cumming, 2014; Kruschke \& Liddell, 2018; Rouder et al., 2018; Schmalz et al., 2021; Tendeiro \& Kiers, 2019, in press; van Ravenzwaaij \& Wagenmakers, 2021).
+Whereas the goal of the frequentist analysis had been hypothesis testing, for which \(p\) values were used, the goal of the Bayesian analysis was parameter estimation.
+Accordingly, we estimated the posterior distribution of every effect, without calculating Bayes factors (for other examples of the same \emph{estimation approach}, see Milek et al., 2018; Pregla et al., 2021; Rodríguez-Ferreiro et al., 2020; for comparisons between estimation and hypothesis testing, see Cumming, 2014; Kruschke \& Liddell, 2018; Rouder et al., 2018; Schmalz et al., 2021; Tendeiro \& Kiers, 2019, in press; van Ravenzwaaij \& Wagenmakers, 2021).
 In the estimation approach, the estimates are interpreted by considering the position of their credible intervals in relation to the expected effect size.
@@
 
-This analysis served two purposes: firstly, to ascertain the interpretation of the smaller effects---which were identified as unreliable in the power analyses---, and secondly, to complement the estimates obtained in the frequentist analysis.
+This analysis served two purposes: first, to ascertain the interpretation of the smaller effects---which were identified as unreliable in the power analyses---, and second, to complement the estimates obtained in the frequentist analysis.
 The latter purpose was pertinent because the frequentist models presented convergence warnings---even though it must be noted that a previous study found that frequentist and Bayesian estimates were similar despite convergence warnings appearing in the frequentist analysis (Rodríguez-Ferreiro et al., 2020).
 Furthermore, the complementary analysis was pertinent because the frequentist models presented residual errors that deviated from normality---even though mixed-effects models are fairly robust to such a deviation (Knief \& Forstmeier, 2021; Schielzeth et al., 2020).
-Owing to these precedents, we expected to find broadly similar estimates in the frequentist and the Bayesian analyses.
-Each frequentist model in the three studies has a Bayesian counterpart, with the exception of a sub-analysis performed in the first study (semantic priming), which included `vision-based similarity' as a predictor.
-
-The R package `brms', Version 2.17.0, was used for this analysis (Bürkner, 2018; Bürkner et al., 2022).
+Owing to these precedents, we expected to find broadly similar estimates in the frequentist analyses and in the Bayesian ones.
+Across studies, each frequentist model has a Bayesian counterpart, with the exception of the secondary analysis performed in Study 1 (semantic priming) that included \texttt{vision-based\ similarity} as a predictor.
+The R package `brms', Version 2.17.0, was used for the Bayesian analysis (Bürkner, 2018; Bürkner et al., 2022).
 
@@
 
-The priors were established by inspecting the effect sizes obtained in previous studies as well as the effect sizes obtained in our frequentist analyses of Studies 1, 2 and 3.
-
-The previous studies that were considered for determining the priors were selected because they had used experimental paradigms and analytical procedures similar to those used in the current studies.
-Specifically, the paradigms were (I) semantic priming with a lexical decision task---as in Study 1---, (II) semantic decision---as in Study 2---,and (III) lexical decision---as in Study 3.
-The analytical procedures consisted of the z-scoring of the dependent and the independent variables.
-We found two studies that matched these characteristics: Lim et al.
+The priors were established by inspecting the effect sizes obtained in previous studies as well as the effect sizes obtained in our frequentist analyses of the present data (reported in Studies 1, 2 and 3 below).
+In the first regard, the previous studies that were considered were selected because the experimental paradigms, variables and analytical procedures they had used were similar to those used in our current studies.
+Specifically, regarding paradigms, we sought studies that implemented: (I) semantic priming with a lexical decision task---as in Study 1---, (II) semantic decision---as in Study 2---, or (III) lexical decision---as in Study 3.
+Regarding analytical procedures, we sought studies in which both the dependent and the independent variables were \(z\)-scored.
+We found two studies that broadly matched these criteria: Lim et al.
 (2020) (see Table 5 therein) and Pexman and Yap (2018) (see Tables 6 and 7 therein).
-These studies and the frequentist analyses reported below yielded effect sizes smaller than ±0.30.
-The bounds of this range were determined by the results from Pexman and Yap (2018), who found a word concreteness effect of \(\upbeta\) = 0.41 in the concrete-words analysis, and an effect of \(\upbeta\) = 0.20 in the abstract-words analysis.
-Since we did not separate abstract from concrete words, we averaged the former values, and set -0.30 as the lower bound, and 0.30 as the upper bound.
-This provided the basis for informative priors.
-Specifically, in these informative priors, 95\% of values would fall within the range {[}-0.30, 0.30{]}.
-
-Next, we considered the direction of effects.
+Out of these studies, Pexman and Yap (2018) contained the variables that were most similar to ours, which included vocabulary size (labelled `NAART') and word frequency.
+
+Based on both these studies and on the frequentist analyses reported below, a range of effect sizes was identified that spanned between \(\upbeta\) = -0.30 and \(\upbeta\) = 0.30.
+This range was centred around 0 as the variables were \(z\)-scored.
+The bounds of this range were determined by the largest effects, which appeared in Pexman and Yap (2018).
+Pexman et al.~conducted a semantic decision study, and split the data set into abstract and concrete words.
+The two largest effects they found were---first---a word concreteness effect in the concrete-words analysis of \(\upbeta\) = -0.41, and---second---a word concreteness effect in the abstract-words analysis of \(\upbeta\) = 0.20.
+Unlike Pexman et al., we did not split the data set into abstract and concrete words, but analysed these sets together.
+Therefore, we averaged between the aforementioned values, obtaining a range between \(\upbeta\) = -0.30 and \(\upbeta\) = 0.30.
+
 In the results of Lim et al.
-(2020) and Pexman and Yap (2018), and in our frequentist results, some effects consistently presented a negative direction---i.e., an inhibitory effect on RT---, whereas some other effects were consistently positive.
-We only incorporated the direction of effects into the priors in cases of large effects that had presented consistent directions in previous studies and in our frequentist analyses.
+(2020) and Pexman and Yap (2018), and in our frequentist results, some effects consistently presented a negative polarity (i.e., leading to shorter response times), whereas some other effects were consistently positive.
+We incorporated the direction of effects into the priors only in cases of large effects that had presented a consistent direction (either positive or negative) in previous studies and in our frequentist analyses in the present studies.
 These criteria were matched by the following variables: word frequency---with a negative direction, as higher word frequency leads to shorter RTs (Brysbaert et al., 2018; Brysbaert et al., 2016; Lim et al., 2020; Mendes \& Undorf, 2021; Pexman \& Yap, 2018)---, number of letters and number of syllables---both with positive directions (Barton et al., 2014; Beyersmann et al., 2020; Pexman \& Yap, 2018)---, and orthographic Levenshtein distance---with a positive direction (Cerni et al., 2016; Dijkstra et al., 2019; Kim et al., 2018; Yarkoni et al., 2008).
-We did not incorporate information about the direction of the word concreteness effect as this effect can follow different directions in abstract and concrete words (Pexman \& Yap, 2018), and we analysed both sets of words together.
-Last, it is noteworthy that some previous studies have integrated effect direction in some priors (e.g., Stone et al., 2021), but most have not (e.g., Pregla et al., 2021; Rodríguez-Ferreiro et al., 2020; Stone et al., 2020).
-In conclusion, the four predictors that had directional priors were covariates (also known as nuisance variables).
+We did not incorporate information about the direction of the word concreteness effect, as this effect can follow different directions in abstract and concrete words (Brysbaert et al., 2014; Pexman \& Yap, 2018), and we analysed both sets of words together.
+In conclusion, the four predictors that had directional priors were covariates.
 All the other predictors had priors centred on 0.
-
-These priors were used on the fixed effects and on the corresponding standard deviation parameters.
-The correlation among the random effects had a weakly-informative prior, LKJ(2) (Lewandowski et al., 2009), which assumes that high correlations among the random effects are rare (also used in Rodríguez-Ferreiro et al., 2020; Stone et al., 2021; Stone et al., 2020; Vasishth, Nicenboim, et al., 2018).
+Last, as a methodological matter, it is noteworthy that most of the psycholinguistic studies applying Bayesian analysis have not incorporated any directional information in priors (e.g., Pregla et al., 2021; Rodríguez-Ferreiro et al., 2020; Stone et al., 2020; cf.
+Stone et al., 2021).
 
@@
 
-We aimed to perform prior sensitivity analyses of our results.
-Prior sensitivity analyses are checks that assess the influence of different priors on the results (Lee \& Wagenmakers, 2014; Schoot et al., 2021; Stone et al., 2020).
-The range of priors established for this purpose varied in their standard deviations.
-Their means were the same, most being centred on 0, as explained above.
-
-The priors we settled upon---shown in Figure \ref{fig:bayesian-priors}---comprised an `informative' prior (\(SD\) = 0.1), a `weakly-informative' one (\(SD\) = 0.2) and a `diffuse' one (\(SD\) = 0.3).
+The choice of priors can influence the results in consequential ways.
+To assess the extent of this influence, \emph{prior sensitivity analyses} have been recommended.
+These analyses are performed by comparing the effect of more and less strict priors---or, in other words, priors varying in their degree of informativeness.
+The degree of variation is adjusted through the standard deviation, and the means are not varied (Lee \& Wagenmakers, 2014; Schoot et al., 2021; Stone et al., 2020).
+
+In this way, we compared the results obtained using `informative' priors (\(SD\) = 0.1), `weakly-informative' priors (\(SD\) = 0.2) and `diffuse' priors (\(SD\) = 0.3).
+These standard deviations were chosen so that around 95\% of values in the informative priors would fall within our initial range of effect sizes that spanned from -0.30 to 0.30.
+All priors are illustrated in Figure \ref{fig:bayesian-priors}.
 These priors resembled others from previous psycholinguistic studies (Pregla et al., 2021; Stone et al., 2021; Stone et al., 2020).
@@
 The range of standard deviations we used---i.e., 0.1, 0.2 and 0.3---was narrower than those of previous studies because our dependent variable and our predictors were \(z\)-scored, resulting in small estimates and small \(SD\)s (see Lim et al., 2020; Pexman \& Yap, 2018).
+These priors were used on the fixed effects and on the standard deviation parameters of the fixed effects.
+For the correlations among the random effects, an \(LKJ\)(2) prior was used (Lewandowski et al., 2009).
+This is a `regularising' prior, as it assumes that high correlations among random effects are rare (also used in Rodríguez-Ferreiro et al., 2020; Stone et al., 2021; Stone et al., 2020; Vasishth, Nicenboim, et al., 2018).
 
@@
 
-\caption{Priors used in the three studies. The green vertical rectangle shows the range of plausible effect sizes based on previous studies and on our frequentist analyses.}\label{fig:bayesian-priors}
-\end{figure}
-
-The adequacy of each of these priors was assessed with prior predictive checks, in which we compared the observed data to data predicted by the priors (Schoot et al., 2021).
-In these checks, we also tested the adequacy of two model-wide distributions: the traditional Gaussian distribution (default in most analyses) and an exponentially modified Gaussian---dubbed `ex-Gaussian'---distribution (Matzke \& Wagenmakers, 2009).
-The ex-Gaussian distribution was considered because the residual errors of the frequentist models were not normally distributed (Lo \& Andrews, 2015), and because this distribution was found to be more appropriate than the Gaussian one in a related, previous study (see supplementary materials of Rodríguez-Ferreiro et al., 2020).
+\caption{Priors used in the three studies.
+The green vertical rectangle shows the range of plausible effect sizes based on previous studies and on our frequentist analyses.
+In the informative priors, around 95\% of the values fall within the range.}\label{fig:bayesian-priors}
+\end{figure}
+
+The adequacy of each of these priors was assessed by performing prior predictive checks, in which we compared the observed data to the predictions of the model (Schoot et al., 2021).
+Furthermore, in these checks we also tested the adequacy of two model-wide distributions: the traditional Gaussian distribution (default in most analyses) and an exponentially modified Gaussian---dubbed `ex-Gaussian'---distribution (Matzke \& Wagenmakers, 2009).
+The ex-Gaussian distribution was considered because the residual errors of the frequentist models were not normally distributed (Lo \& Andrews, 2015), and because this distribution was found to be more appropriate than the Gaussian one in a previous, related study (see supplementary materials of Rodríguez-Ferreiro et al., 2020).
 The ex-Gaussian distribution had an identity link function, which preserves the interpretability of the coefficients, as opposed to a transformation applied directly to the dependent variable (Lo \& Andrews, 2015).
-
-Prior predictive checks revealed that the priors were adequate, and that the ex-Gaussian distribution was more appropriate than the Gaussian one, converging with Rodríguez-Ferreiro et al.
-(2020) (see the corresponding plots in \protect\hyperlink{appendix-C-Bayesian-analysis-diagnostics}{\underline{Appendix C}}).
+The results of these prior predictive checks revealed that the priors were adequate, and that the ex-Gaussian distribution was more appropriate than the Gaussian one (see \protect\hyperlink{appendix-C-Bayesian-analysis-diagnostics}{\underline{Appendix C}}), converging with Rodríguez-Ferreiro et al.
+(2020).
 Therefore, the ex-Gaussian distribution was used in the final models.
@@
 
-In the main analyses, the informative, weakly-informative and diffuse priors were used in separate models.
+In the main analysis, the informative, weakly-informative and diffuse priors were used in separate models.
 In other words, in each model, all priors had the same degree of informativeness (as done in Pregla et al., 2021; Rodríguez-Ferreiro et al., 2020; Stone et al., 2021; Stone et al., 2020).
@@
 
-Posterior predictive checks were performed to assess the fit between the observed data and new data predicted by the posterior (Schoot et al., 2021).
+Posterior predictive checks were performed to assess the consistency between the observed data and new data predicted by the posterior distributions (Schoot et al., 2021).
 These checks are available in \protect\hyperlink{appendix-C-Bayesian-analysis-diagnostics}{\underline{Appendix C}}.
@@
 
-Where convergence was not reached in a model, as indicated by \(\widehat R\) \textgreater{} 1.01 (Schoot et al., 2021; Vehtari et al., 2021), the number of iterations was increased.
-Furthermore, where necessary, the random slopes for covariates were removed (Brauer \& Curtin, 2018).
+When convergence was not reached in a model, as indicated by \(\widehat R\) \textgreater{} 1.01 (Schoot et al., 2021; Vehtari et al., 2021), the number of iterations was increased and the random slopes for covariates were removed (Brauer \& Curtin, 2018).
 The resulting random effects in these models were largely the same as those present in the frequentist models.
-The only exception regarded the lexical decision models.
-In the frequentist model for lexical decision, the random slopes for covariates were removed due to convergence warnings, whereas in the Bayesian analysis, these random slopes did not have to be removed as the models converged.
-
-The Bayesian models in the semantic decision study could not be made to converge, and the results were not valid.
-Therefore, those estimates are not shown in the main text but in \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}.
-
-\hypertarget{general-method-for-statistical-power-analysis}{%
-\subsection{General method for statistical power analysis}\label{general-method-for-statistical-power-analysis}}
-
-Power curves based on Monte Carlo simulations were performed for most of the effects of interest, using the R package `simr', Version 1.0.5 (Green \& MacLeod, 2016).
+The only exception concerned the models of the lexical decision study.
+In the frequentist model for the latter study, the random slopes for covariates were removed due to convergence warnings, whereas in the Bayesian analysis, these random slopes did not have to be removed as the models converged, thanks to the large number of iterations that were run.
+In the lexical decision study, it was possible to run a larger number of iterations than in the two other studies, as the lexical decision data set had fewer observations, resulting in faster running.
+
+The Bayesian models in the semantic decision study could not be made to converge, and the final results of these models were not valid.
+Therefore, those estimates are not shown in the main text, but are available in \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}.
+
+\hypertarget{statistical-power-analysis-1}{%
+\subsection{Statistical power analysis}\label{statistical-power-analysis-1}}
+
+Power curves based on Monte Carlo simulations were performed for most of the effects of interest using the R package `simr', Version 1.0.5 (Green \& MacLeod, 2016).
 Obtaining power curves for a range of effects in each study allows for a comprehensive assessment of the plausibility of the power estimated for each effect.
 
-Monte Carlo simulations are performed by running the statistical model a large number of times, under slight, random variations of the dependent variable (Green \& MacLeod, 2016; for a comparable approach, see Loken \& Gelman, 2017).
+In each study, the item-level sample size---i.e., the number of words---was not modified.
+Therefore, to plan the sample size for future studies, these results must be considered under the assumptions that the future study would apply a statistical method similar to ours---namely, a mixed-effects model with random intercepts and slopes---, and that the analysis would encompass at least as many stimuli as the corresponding study (numbers detailed in each study below).
+\(P\) values were calculated using the Satterthwaite approximation for degrees of freedom (Luke, 2017).
+
+Monte Carlo simulations consist of running the statistical model a large number of times, under slight, random variations of the dependent variable (Green \& MacLeod, 2016; for a comparable approach, see Loken \& Gelman, 2017).
 The power to detect each effect of interest is calculated by dividing the number of times that the effect is significant by the total number of simulations run.
@@
 Thus, for a power curve examining the power for an effect across 12 sample sizes, 2,400 simulations were run.
-In each study, the item-level sample size---i.e., the number of words---was not modified.
-Thus, each of the power curves we present assume the same number of words that existed in each of our studies (these numbers are detailed in each study below).
-\(P\) values were calculated using the Satterthwaite approximation for degrees of freedom (Luke, 2017).
-
-It is difficult to determine an effect size for each effect examined in a power analysis, as the amount and the scope of relevant research are usually finite and biased (Albers \& Lakens, 2018; Gelman \& Carlin, 2014; Kumle et al., 2021).
-Power analyses sometimes use the original effect sizes from previous studies (e.g., Pacini \& Barnard, 2021; Villalonga et al., 2021).
-In contrast, some authors have opted to reduce the previous effect sizes to account for factors that can influence the effect size of the planned study.
-First, publication bias and low-powered studies cause published effect sizes to be inflated (Brysbaert, 2019; Loken \& Gelman, 2017; Open Science Collaboration, 2015; Vasishth, Mertzen, et al., 2018; Vasishth \& Gelman, 2021).
-Second, there might be differences between the studies used in the power analysis and the study to be conducted.
-Some of these differences could be foreseeable---for instance, if they are due to a limitation in the literature available for the power analysis---, whereas other differences might arise from unexpected circumstances arising during the project or from random variation (Barsalou, 2019).
+
+Power analyses require setting an effect size for each effect.
+Often, it is difficult to determine the effect size, as the amount and the scope of relevant research are usually finite and biased (Albers \& Lakens, 2018; Gelman \& Carlin, 2014; Kumle et al., 2021).
+In some power analyses, the original effect sizes from previous studies have been adopted without any modification (e.g., Pacini \& Barnard, 2021; Villalonga et al., 2021).
+In contrast, some authors have opted to reduce the previous effect sizes to account for two intervening factors.
+First, publication bias and insufficient statistical power cause published effect sizes to be inflated (Brysbaert, 2019; Loken \& Gelman, 2017; Open Science Collaboration, 2015; Vasishth, Mertzen, et al., 2018; Vasishth \& Gelman, 2021).
+Second, over the course of the research, a variety of circumstances could create differences between the planned study and the studies that were used in the power analysis.
+Some of these differences could be foreseeable---for instance, if they are due to a limitation in the literature available for the power analysis---, whereas other differences might be unforeseeable and could go unnoticed (Barsalou, 2019).
 Reducing the effect size in the power analysis leads to an increase of the sample size of the planned study (Brysbaert \& Stevens, 2018; Green \& MacLeod, 2016; Hoenig \& Heisey, 2001).
-The reduced effect size---sometimes dubbed the smallest effect size of interest---is often set with a certain arbitrariness.
-For instance, Fleur et al.
+The reduced effect size---sometimes dubbed the smallest effect size of interest---is often set with a degree of arbitrariness.
+In previous studies, Fleur et al.
 (2020) applied a reduction of 1/8 (i.e., 12.5\%), whereas Kumle et al.
 (2021) applied a 15\% reduction.
-In the present study, a reduction of 20\% was applied to every effect examined in the power analysis.
-By comparison with the power analyses reviewed in this paragraph, the present reduction will lead to a relatively-conservative estimate of required sample sizes.
-Yet, it is intrinsically difficult to determine how conservative a power analysis is, once we consider the insufficient power of most studies in psychology, and the resulting overestimation of effect sizes.
+In the present study, a reduction of 20\% was applied to every effect in the power analysis.
+By comparison with the power analyses reviewed in this paragraph, the present reduction will lead to a more conservative estimate of required sample sizes.
+However, after considering the precedents of small samples and publication bias reviewed above, a 20\% reduction is arguably a reasonable safeguard.
+Indeed, a posteriori, the results of our power analyses suggested that the 20\% reduction had not been excessive, as some of the effects examined were detectable with small sample sizes.
 
 Both the primary analysis and the power analysis were performed in R (R Core Team, 2021).
-Version 4.0.2 was used for the frequentist analysis, Version 4.1.0 was used for the Bayesian analysis, and Version 4.1.2 was used for fast operations such as plotting.
-All the statistical and the power analyses were run on the High-End Computing facility at Lancaster University.\footnote{Information about this facility is available at \url{https://answers.lancaster.ac.uk/display/ISS/High+End+Computing+\%28HEC\%29+help}}
+Version 4.0.2 was used for the frequentist analysis, Version 4.1.0 was used for the Bayesian analysis, and Version 4.1.2 was used for fast operations such as data preprocessing and plotting.
+Given the complexity of these analyses, all the statistical and the power analyses were run on the High-End Computing facility at Lancaster University.\footnote{Information about this facility is available at \url{https://answers.lancaster.ac.uk/display/ISS/High+End+Computing+\%28HEC\%29+help}.
+Even though analysis jobs were run in parallel, some of the statistical analyses took four months to complete (specifically, one month for the final model to run, which was delayed due to three reasons: limited availability of machines, occasional cancellations of jobs to allow maintenance work on the machines, and lack of convergence of the models).
+Furthermore, the power analysis for the semantic priming study took six months (specifically, two months of running, with delays due to the limited availability of machines and occasional cancellations of jobs).}
 
@@
 The core data set in this study was that of the Semantic Priming Project (Hutchison et al., 2013; also see Yap et al., 2017).
-Out of the tasks delivered in the experiment, we used the lexical decision one because it was most relevant to our forthcoming research.
-In the lexical decision task, participants judged whether strings of letters constituted real words (e.g., `building') or nonwords (e.g., `gop').
-Crucially, in the experimental manipulation that characterises semantic priming, a prime word was presented before the target word in each trial.
-Since prime words facilitate the comprehension of target words, the participants' responses to the targets can be analysed as a function of the semantic relationship between primes and targets (Hoedemaker \& Gordon, 2014).
-
-In some studies, the association between prime and target words has been examined in terms of related versus unrelated pairs (Pecher et al., 1998; Trumpp et al., 2013), and in terms of first- and second-order relationships (Hutchison et al., 2013).
-In contrast to these categorical associations, other studies have measured the association between the prime and the target words using language-based similarity estimates (Günther et al., 2016a, 2016b; Hutchison et al., 2008; Jones et al., 2006; Lam et al., 2015; Lund et al., 1995; Lund \& Burgess, 1996; Mandera et al., 2017; McDonald \& Brew, 2002; Padó \& Lapata, 2007; Petilli et al., 2021; Wingfield \& Connell, 2022).
+The study of Hutchison et al.
+(2013) comprised two tasks: lexical decision and naming.
+We limited our analysis to the lexical decision task because it was more relevant to a subsequent study that we were planning.
+In the lexical decision task, participants judged whether strings of letters constituted real words (e.g., \emph{building}) or nonwords (e.g.~\emph{gop}).
+Importantly, in each trial, the target word that participants assessed was preceded by a prime word.
+Participants were only required to provide a response regarding the \emph{target} word.
+The characteristic feature of the semantic priming paradigm is the analysis of responses to the targets as a function of the semantic relationship between the primes and the targets (Brunellière et al., 2017; de Wit \& Kinoshita, 2015; Hoedemaker \& Gordon, 2014).
+
+In some studies, the association between prime and target words has been investigated in terms of related versus unrelated pairs (Lam et al., 2015; Pecher et al., 1998; Trumpp et al., 2013) and---in other studies---in terms of first- and second-order relationships (Hutchison et al., 2013).
+In contrast to these categorical associations, a third set of studies have measured the association between the prime and the target words using continuous estimates of text-based similarity (Günther et al., 2016a, 2016b; Hutchison et al., 2008; M.
+N.
+Jones et al., 2006; Lund et al., 1995; Lund \& Burgess, 1996; Mandera et al., 2017; McDonald \& Brew, 2002; Padó \& Lapata, 2007; Petilli et al., 2021; Wingfield \& Connell, 2022).
 In one of these studies, Mandera et al.
-(2017) found that the latter computational measures outperformed human-based associations at explaining the priming effect.
-
-Priming associations beyond the linguistic realm have also been examined, with early studies finding perceptual priming effects (Flores d'Arcais et al., 1985; Schreuder et al., 1984).
-Yet, the earliest findings were soon reframed by Pecher et al.
-(1998), who conducted a follow-up with an improved design, and observed the perceptual priming effect only when the word processing task was preceded by a visually-intensive task (Pecher et al., 1998).
-This moderating condition, replicated by Yee et al.
-(2012), is consistent with other conceptual-processing studies using a non-priming paradigm (Ostarek \& Huettig, 2017).
-However, a considerable number of studies have observed perceptual priming even in the absence of a preparatory perceptual task.
-A set of these studies used the Conceptual Modality Switch paradigm, in which the primes and the targets are presented in separate, consecutive trials (Bernabeu et al., 2017; Collins et al., 2011; Hald et al., 2011, 2013; Louwerse \& Connell, 2011; Lynott \& Connell, 2009; Pecher et al., 2003; Trumpp et al., 2013).
-The other set of studies, using the more standard priming intervals, are described below.
+(2017) found that computational measures of similarity outperformed human-based associations at explaining language-based priming.
+
+\hypertarget{language-vision-and-soa}{%
+\subsection{Language, vision and SOA}\label{language-vision-and-soa}}
+
+Priming associations beyond the linguistic realm have also been investigated, with early studies observing perceptual priming effects (Flores d'Arcais et al., 1985; Schreuder et al., 1984).
+Yet, those early findings were soon reframed by Pecher et al.
+(1998), who conducted a follow-up with an improved design, and observed vision-based priming only when the task was preceded by another task that required attention to visual features of concepts (Ostarek \& Huettig, 2017; also see Yee et al., 2012).
+Furthermore, two studies have failed to observe vision-based priming (Hutchison, 2003; Ostarek \& Huettig, 2017).
+
+Nonetheless, a considerable number of studies have observed perceptual priming, even in the absence of a pretask.
+A set of these studies used the Conceptual Modality Switch paradigm, in which the primes and the targets are presented in separate, consecutive trials---e.g., \emph{Loud Welcome} → \emph{Fine Selection} (Bernabeu et al., 2017; Collins et al., 2011; Hald et al., 2011, 2013; Louwerse \& Connell, 2011; Lynott \& Connell, 2009; Pecher et al., 2003; Trumpp et al., 2013).
+The other set of studies implemented the more classic priming manipulation, whereby a prime word is briefly presented before the target word in each trial---e.g., \emph{Welcome} → \emph{Selection}.
+This design is more relevant to our present study, as it was used in the study we are revisiting (Hutchison et al., 2013).
+Below, we review studies that have used the \emph{prime} → \emph{target} design.
 
 Lam et al.
-(2015) conducted a semantic priming experiment containing a lexical decision task.
-Participants were instructed to respond whether the prime word and the target word in each trial were both real words or pseudowords.
-The semantic-priming manipulation consisted of the following types of associations between the prime and the target words: (1) semantic association (e.g., bolt → screwdriver), (2) action association (e.g., housekey → screwdriver), (3) visual association (e.g., soldering iron → screwdriver), and (4) no association (e.g., charger → screwdriver).
-In addition, four conditions were present that consisted of SOAs of 500, 650, 800 and 1,400 ms.
-In the results, Lam et al.~firstly observed priming effects of the semantic-association type with all SOAs.
-Secondly, the authors observed motor-association priming effects with the SOAs of 500, 650 and 1,400 ms.
-Lastly, they observed visual-association priming effects only with the SOA of 1,400 ms.
-Overall, semantic-association priming---corresponding to language-based association---was more consistent than the priming based on visual and action associations.
-This greater influence of the language system converges with other studies on semantic priming (Lam et al., 2015; Pecher et al., 1998; Petilli et al., 2021) and with studies using other paradigms (Banks et al., 2021; Kiela \& Bottou, 2014; Louwerse et al., 2015).
+(2015) conducted a semantic priming experiment containing a lexical decision task, in which participants were instructed to assess whether the prime word and the target word in each trial were both real words.
+The semantic priming manipulation consisted of the following types of associations between the prime and the target words: (1) semantic association (e.g., bolt → screwdriver), (2) action association (e.g., housekey → screwdriver), (3) visual association (e.g., soldering iron → screwdriver), and (4) no association (e.g., charger → screwdriver).
+In addition, the following SOAs were compared: 500, 650, 800 and 1,400 ms.
+First, Lam et al.~observed priming effects of the semantic type with all SOAs.
+Second, the authors observed action-based priming with the SOAs of 500, 650 and 1,400 ms.
+Last, they observed vision-based priming only with the SOA of 1,400 ms.
+Overall, semantic---i.e., language-based---priming was more prevalent than visual and action priming.
+The greater role of language-based information converges with other semantic priming studies (Bottini et al., 2016; Lam et al., 2015; Pecher et al., 1998; Petilli et al., 2021), as well as with studies that used other paradigms (Banks et al., 2021; Kiela \& Bottou, 2014; Louwerse et al., 2015).
 
 Similarly, the results of Lam et al.
-(2015) regarding the time course of language-based and vision-based priming were consistent with a wealth of literature observing that perceptual systems, such as vision, are activated later than the language system (Barsalou et al., 2008; Connell \& Lynott, 2013; Louwerse \& Connell, 2011; Santos et al., 2011).
-For instance, studies using electroencephalography have found that perceptual priming effects emerged in the first 300 ms.
-Following the 300-ms stage, the perceptual priming increased in some studies (Amsel et al., 2014; Bernabeu et al., 2017), whereas other studies it stabilised (Kiefer et al., 2022), and in a third set of studies, the effect fluctuated (Amsel, 2011).
-Taken together, the most prevalent pattern is of a gradual accumulation of information throughout word processing (also see Hauk, 2016), which is consistent with the accummulation of information required for the integration of context in sentences (Hald et al., 2006).
-This progression invites two hypotheses regarding SOA in the current study: (1) that language-based information will be more prevalent than vision-based information in both the short and the long SOA, and (2) that vision-based information will be more prevalent in the long SOA than in the short one.
-Consistent with the first hypothesis, Petilli et al.
-(2021) observed that language-based information was more influential in both the short and the long SOA, within the data set of Hutchison et al.
-(2013).
-The second hypothesis, in contrast, is challenged by other findings.
-First, Hutchison (2003) concluded that the vision-based priming effect was negligible.
-Second, other studies have observed the effect only when the word processing task was preceded by a visually-intensive task (Pecher et al., 1998; Yee et al., 2012).
-Third, Petilli et al.~observed vision-based priming with the short SOA (150 ms) but not with the long one (1,200 ms).
-
-The findings of Petilli et al.
-(2021) were based on a novel analysis of the data set of Hutchison et al.
-(2013).
-The strengths of Petilli et al.'s study centred on the simultaneous analysis of language- and vision-based similarity using predictors that were continuous (see Cohen, 1983; Günther et al., 2016a; Mandera et al., 2017) and not based on human ratings (cf.
+(2015) regarding the time course of language-based and vision-based priming were consistent with a wealth of literature observing that the influence of perceptual systems, such as vision, peaks later than the influence of the language system (Barsalou et al., 2008; Louwerse \& Connell, 2011; Santos et al., 2011).
+For instance, studies using electroencephalography have observed perceptual priming effects within 300 ms from the word onset.
+Thereafter, the perceptual priming effect increased (Amsel et al., 2014; Bernabeu et al., 2017), or it stabilised (Kiefer et al., 2022), or fluctuated (Amsel, 2011).
+Overall, these patterns reveal a gradual accumulation of information throughout word processing (also see Hauk, 2016), which is consistent with the integration of contextual information (see Hald et al., 2006).
+
+In a more recent study, Petilli et al.
+(2021) revisited the data of Hutchison et al.
+(2013) using new variables that indexed language-based and vision-based associations between the prime and the target words.
+These variables had two important characteristics: (1) they were continuous rather than categorical (see Cohen, 1983; Günther et al., 2016a; Mandera et al., 2017), and (2) they were not dependent on human ratings (cf.
 Hutchison et al., 2008, 2013; Lam et al., 2015; Pecher et al., 1998).
-The authors used such measures to pursue a comprehensive analysis that was not affected by the problem of circularity between the independent and the dependent variables.
-The circularity problem obtains even though the participants who contributed to the ratings---or `norms'---are always different from those who participate in the main experiment.
-
-Petilli et al.~operationalised language-based similarity based on text-based co-occurrence, producing a continuous measure in contrast to the categorical factors used earlier.
-Next, Petilli et al.~created a visual-similarity measure by retrieving ImageNet images for each word, and training vector representations on those images using neural networks.
-Importantly, the authors compared the resulting visual-similarity measure to previous scores based on human ratings (Pecher et al., 1998), and found a comparable pattern.
-Using these materials, Petilli et al.~examined language-based and vision-based priming in two tasks---lexical decision and naming---and with both a short and a long SOA.
-In lexical decision, the largest effect observed by the authors was that of language-based priming with the short SOA (150 ms).
+By this means, Petilli et al.~avoided the circularity problem (rarely addressed in studies) that arises (or may arise) when human-based ratings are used to explain human behaviour.
+
+Petilli et al.
+(2021) operationalised word co-occurrence using text-based similarity (Mandera et al., 2017).
+Next, to operationalise vision-based similarity, the authors obtained images from ImageNet corresponding to each word (a minimum of 100 images per word), and trained vector representations on those images using neural networks (for related work, see Roads \& Love, 2020).
+The resulting computational measure of vision-based similarity was then validated against human-based ratings (Pecher et al., 1998), with a satisfactory result.
+In a concrete demonstration, Petilli et al.~show how vision-based similarity correctly concluded that drills were more visually similar to pistols than to screwdrivers, showing that the measure was not misled by functional similarity.
+In conclusion, using \texttt{language-based\ similarity} and \texttt{vision-based\ similarity}, Petilli et al.~investigated language-based and vision-based priming in two tasks---lexical decision and naming---and with both a short and a long SOA.
+
+In lexical decision, the largest effect observed by Petilli et al.
+(2021) was that of language-based priming with the short SOA (200 ms).
 The second largest effect was that of language-based priming with the long SOA (1,200 ms).
-Next, the weakest effect that was significant was that of vision-based priming with the short SOA.
+Next, the weakest, significant effect was that of vision-based priming with the short SOA.
 Last, there was no effect of vision-based priming with the long SOA.
-Petilli et al.
-(2021) explained the absence of vision-based priming with the long SOA in lexical decision by contending that visual activation had likely decayed before participants processed the target words (also see Yee et al., 2011), owing to the limited semantic processing required for lexical decision (also see Balota \& Lorch, 1986; Becker et al., 1997; Connell \& Lynott, 2013; de Wit \& Kinoshita, 2015; Joordens \& Becker, 1997; Ostarek \& Huettig, 2017).
-Therefore, the authors suggested that perceptual simulation does \emph{not} outlast language-based processing in lexical decision, in contrast to the longer latency found in other tasks (Barsalou et al., 2008; Louwerse \& Connell, 2011).
-
-In the naming task of Petilli et al.
-(2021), the largest effect was that of language-based priming with the long SOA.
+Petilli et al.~explained the absence of vision-based priming with the long SOA by contending that visual activation had likely decayed before participants processed the target words (also see Yee et al., 2011), owing to the limited semantic processing required for lexical decision (also see Balota \& Lorch, 1986; Becker et al., 1997; de Wit \& Kinoshita, 2015; Joordens \& Becker, 1997; Ostarek \& Huettig, 2017).
+Therefore, the authors suggested that perceptual simulation does \emph{not} peak before language-based processing in lexical decision, contrasting with the results of Lam et al.
+(2015) and with the results found in other tasks (Louwerse \& Connell, 2011; Santos et al., 2011; Simmons et al., 2008; also see Barsalou et al., 2008).
+
+In the naming task, the largest effect observed by Petilli et al.
+(2021) was that of language-based priming with the long SOA.
 The second largest effect was that of language-based priming with the short SOA.
 Last, there was no effect of vision-based priming with either SOA.
-This finding contrasted with Connell and Lynott (2014), who found facilitatory effects of visual strength in both lexical decision and naming.
-Petilli et al.~explained the lack of vision-based priming in the naming task by alluding to the lower semantic depth of this task---compared to lexical decision---, and the mixture of visual and auditory processing in the naming task (Connell \& Lynott, 2014).
-
-In the present study, we revisited the interplay between linguistic and perceptual simulation by conceptually replicating Petilli et al.
-(2021).
-Specifically, we used the same primary data set (Hutchison et al., 2013), and a language-based similarity measure that was very similar to that used by Petilli et al.
-(2021; both our measure and theirs originated from Mandera et al., 2017).
-In contrast, our predictors in the domain of vision differed.
-Whereas Petilli et al.~used a human-independent measure based on images from the Internet (see description above), we drew on visual strength---from the modality ratings of Lynott et al.
-(2020)---and calculated the difference in visual strength between the prime and the target word in each trial.\footnote{These measures are compared at \protect\hyperlink{comparing-two-measures-of-vision-based-information}{\underline{the end of the Results section}}.}
-
-\hypertarget{methods-1}{%
-\subsection{Methods}\label{methods-1}}
-
-\hypertarget{effects-of-interest}{%
-\subsubsection{Effects of interest}\label{effects-of-interest}}
+This finding contrasts with Connell and Lynott (2014), who found facilitatory effects of visual strength in both lexical decision and naming.
+Petilli et al.~explained the lack of vision-based priming in the naming task by alluding to the lower semantic depth of this task---compared to lexical decision---, and the mixture of visual and auditory processing in this task (also see Connell \& Lynott, 2014).
+
+In conclusion, there is mixed evidence regarding the time course of language-based and vision-based information in conceptual processing, and particularly in semantic priming.
+First, regarding language, previous research predicts that language-based priming will have a larger effect with the short SOA than with the long one (Lam et al., 2015; Petilli et al., 2021).
+Second, regarding vision, three hypotheses are available: (a) more vision-based priming with the long SOA (Louwerse \& Connell, 2011; Santos et al., 2011; Simmons et al., 2008; also see Barsalou et al., 2008), (b) vision-based priming only with the short SOA (Petilli et al., 2021), and (c) no vision-based priming (Hutchison, 2003; Ostarek \& Huettig, 2017; Pecher et al., 1998; Yee et al., 2012).
+
+\hypertarget{language-vision-and-vocabulary-size}{%
+\subsection{Language, vision and vocabulary size}\label{language-vision-and-vocabulary-size}}
+
+Next, we turn to considering the role of participants' vocabulary size with respect to language-based and vision-based information (this recaps the general \protect\hyperlink{hypotheses}{\underline{Hypotheses}} section).
+First, three hypotheses exist the interaction with language.
+On the one hand, some research predicts a larger effect of language-based priming in higher-vocabulary participants (Yap et al., 2017; also see Connell, 2019; Landauer et al., 1998; Louwerse et al., 2015; Paivio, 1990; Pylyshyn, 1973).
+On the other hand, other research has found the opposite pattern (Yap et al., 2009; also see Yap et al., 2012).
+Also relevant to these mixed findings is the notion that vocabulary knowledge is associated with increased attention to task-relevant variables (Pexman \& Yap, 2018).
+We hypothesised that language-based information---represented by \texttt{language-based\ similarity} in this study---was indeed important for present task, given its importance across the board (Banks et al., 2021; Kiela \& Bottou, 2014; Lam et al., 2015; Louwerse et al., 2015; Pecher et al., 1998; Petilli et al., 2021).
+Accordingly, the relevance hypothesis predicted that higher-vocabulary participants would present a larger priming effect.
+
+To our knowledge, no previous studies have investigated the interaction between vision-based information and participants' vocabulary size.
+We entertained two hypotheses: (a) that lower-vocabulary participants would be more sensitive to visual strength than higher-vocabulary participants, thereby compensating for the disadvantage on the language side, and (b) that this interaction effect would be absent.
+
+\hypertarget{the-present-study}{%
+\subsection{The present study}\label{the-present-study}}
+
+In the present study, we expanded on Petilli et al.
+(2021) by examining the role of participants' vocabulary size.
+In other regards, we used the same primary data set (Hutchison et al., 2013), and a language-based similarity measure that was very similar to that used by Petilli et al.
+(also created by Mandera et al., 2017).
+In contrast, our vision-based predictors differed.
+Whereas Petilli et al.~used a human-independent measure trained on images (see description above), we calculated the difference in visual strength (Lynott et al., 2020) between the prime and the target word in each trial.\footnote{These measures are compared at \protect\hyperlink{results-human-based-and-computational-measures-of-visual-information}{\underline{the end of the Results section}}.}
+
+\hypertarget{methods}{%
+\subsection{Methods}\label{methods}}
+
+\hypertarget{semanticpriming-dataset}{%
+\subsubsection{Data set}\label{semanticpriming-dataset}}
+
+The data set was trimmed by removing rows that lacked values on any variable, and by also removing RTs that were more than 3 standard deviations away from the mean.
+The standard deviation trimming was performed within participants, within sessions and within SOA conditions, as done in the Semantic Priming Project (Hutchison et al., 2013).
+The resulting data set contained 496 participants, 5,943 prime--target pairs and 345,666 RTs.
+On average, there were 697 prime--target pairs per participant (\(SD\) = 33.34), and conversely, 58 participants per prime--target pair (\(SD\) = 4.25).
+
+\hypertarget{variables}{%
+\subsubsection{Variables}\label{variables}}
+
+While the variables are generally described in the \protect\hyperlink{present-studies}{\underline{general introduction}}, a few further details are provided below regarding two of them.
 
@@
 \item
-  \(Z\)-scored vocabulary size {[}\texttt{z\_vocabulary\_size}; calculated from average of \texttt{vocaba}, \texttt{vocabb} and \texttt{vocabc} in Hutchison et al.
-(2013){]}.
+  \texttt{Vocabulary\ size}.
 The test used by Hutchison et al.
@@
 \item
-  \(Z\)-scored, recoded participants' gender {[}\texttt{z\_recoded\_participant\_gender}; calculated from \texttt{gender} in Hutchison et al. (2013){]}
-\item
-  \(Z\)-scored language-based similarity between prime and target words {[}\texttt{z\_cosine\_similarity}{]}.
+  \texttt{Language-based\ similarity}.
 This measure was calculated using a semantic space from Mandera et al.
@@
 (2013) (we could not use the best semantic space, \(R\)\textsuperscript{2} = .471, owing to computational limitations).
-The second-best semantic space (see first row in Table 5 of Mandera et al., 2017) was based on lemmas from a subtitle corpus, processed in a Continuous Bag Of Words model, and the space had 300 dimensions and a window size of 6.
+The second-best semantic space (see first row in Table 5 in Mandera et al., 2017) was based on lemmas from a subtitle corpus, and was processed using a Continuous Bag Of Words model.
+It had 300 dimensions and a window size of six words.
 \item
-  \(Z\)-scored vision-based information in words {[}\texttt{z\_visual\_rating\_diff}; calculated from \texttt{Visual.mean} in Lynott et al. (2020){]}
-\item
-  \(Z\)-scored, recoded SOA {[}\texttt{z\_recoded\_interstimulus\_interval}; calculated from \texttt{isi} in Hutchison et al. (2013){]}
+  \texttt{Stimulus\ onset\ asynchrony\ (SOA)}. Following Brauer and Curtin (2018), the categories of this factor were recoded as follows: 200 ms = -0.5, 1,200 ms = 0.5.
 \end{itemize}
 
-The final data set contained 496 participants, 5,943 prime-target pairs, and 345,666 RTs.
-On average, there were 697 prime-target pairs per participant (\(SD\) = 33.34), and conversely, 58 participants per prime-target pair (\(SD\) = 4.25).
-
-Figure \ref{fig:semanticpriming-correlations} shows the zero-order correlations among the predictors and the dependent variable.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.65\linewidth]{manuscript_files/figure-latex/semanticpriming-correlations-1}
-
-}
-
-\caption{Zero-order correlations in the semantic priming study.}\label{fig:semanticpriming-correlations}
-\end{figure}
-
-\hypertarget{covariates}{%
-\subsubsection{Covariates}\label{covariates}}
-
-The following covariates were included in the model to allow a rigorous analysis of the effects of interest.
+A few details regarding the covariates follow.
 
@@
 \item
-  Lexical (see \protect\hyperlink{appendix-A-lexical-covariates}{\underline{Appendix A}}): \(z\)-scored word frequency and orthographic Levenshtein distance (Balota et al., 2007)
+  \texttt{Attentional\ control} (Hutchison et al., 2013) was included as a measure akin to general cognition, and specifically as a covariate of vocabulary size (Ratcliff et al., 2010).
+The role of attentional control in semantic priming was evidenced by Yap et al.
+(2017).
+Attentional control comprised three attention-demanding tasks, namely, operation span, Stroop and antisaccade (Hutchison et al., 2013).
 \item
-  Semantic: \(z\)-scored word concreteness (Brysbaert et al., 2014), used as a covariate of visual rating.
+  Lexical covariates (see \protect\hyperlink{appendix-A-lexical-covariates}{\underline{Appendix A}}): \texttt{word\ frequency} and \texttt{orthographic\ Levenshtein\ distance} (Balota et al., 2007).
 \item
-  Individual differences: \(z\)-scored attentional control (Hutchison et al., 2013).
-This covariate is related to vocabulary size (Ratcliff et al., 2010), and previous studies have expressed the desirability of including such covariates (James et al., 2018; Pexman \& Yap, 2018).
-Attentional control was operationalised as the average score across three tasks of Hutchison et al.
-(2013)---namely, operation span, Stroop and antisaccade.
+  \texttt{Word\ concreteness} (Brysbaert et al., 2014), used as a covariate of visual strength.
 \end{itemize}
 
-\hypertarget{diagnostics-for-the-frequentist-model}{%
-\subsubsection{Diagnostics for the frequentist model}\label{diagnostics-for-the-frequentist-model}}
+Figure \ref{fig:semanticpriming-correlations} shows the correlations among the predictors and the dependent variable.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.65\linewidth]{manuscript_files/figure-latex/semanticpriming-correlations-1}
+
+}
+
+\caption{Zero-order correlations in the semantic priming study.}\label{fig:semanticpriming-correlations}
+\end{figure}
+
+\hypertarget{diagnostics-for-the-frequentist-analysis}{%
+\subsubsection{Diagnostics for the frequentist analysis}\label{diagnostics-for-the-frequentist-analysis}}
 
 The model presented convergence warnings.
-To avoid removing important random slopes, which could increase the Type I error (Brauer \& Curtin, 2018; Singmann \& Kellen, 2019), we examined the model after refitting it using seven optimization algorithms through the `allFit' function of the R package `lme4' (Bates et al., 2021).
-The results showed that all optimizers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential (Bates et al., 2021; see \protect\hyperlink{appendix-B-frequentist-analysis-diagnostics}{\underline{Appendix B}}).
+To avoid removing important random slopes, which could increase the Type I error rate---i.e., false positives (Brauer \& Curtin, 2018; Singmann \& Kellen, 2019), we examined the model after refitting it using seven optimisation algorithms through the `allFit' function of the R package `lme4' (Bates et al., 2021).
+The results showed that all optimisers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential (Bates et al., 2021; see \protect\hyperlink{appendix-B-frequentist-analysis-diagnostics}{\underline{Appendix B}}).
 
@@
 However, this is not likely to have posed a major problem, as mixed-effects models are fairly robust to deviations from normality (Knief \& Forstmeier, 2021; Schielzeth et al., 2020).
-
-The model did not present multicollinearity problems, all variance inflation factors (VIF) being smaller than 2 (Dormann et al., 2013; Harrison et al., 2018).
-
-\hypertarget{diagnostics-for-the-bayesian-model}{%
-\subsubsection{Diagnostics for the Bayesian model}\label{diagnostics-for-the-bayesian-model}}
-
-Three Bayesian models were run that were respectively characterised by informative, weakly-informative and diffuse priors (note that the weakly-informative prior model has not yet finished running).
+Last, the model did not present multicollinearity problems, with all variance inflation factors (VIF) below 2 (see Dormann et al., 2013; Harrison et al., 2018).
+
+\hypertarget{diagnostics-for-the-bayesian-analysis}{%
+\subsubsection{Diagnostics for the Bayesian analysis}\label{diagnostics-for-the-bayesian-analysis}}
+
+Three Bayesian models were run that were respectively characterised by informative, weakly-informative and diffuse priors.
 In each model, 16 chains were used.
@@
 
-The maximum \(\widehat R\) value for the fixed effects in both models was 1.00, suggesting that these parameters had converged (Schoot et al., 2021; Vehtari et al., 2021).
-In contrast, the maximum \(\widehat R\) value for the random effects was 1.13, exceeding the 1.01 threshold (Vehtari et al., 2021).
-Therefore, models with more iterations will be run, and once completed, they will be reported in this manuscript.
-
-The posterior predictive checks were sound (see \protect\hyperlink{appendix-C-Bayesian-analysis-diagnostics}{\underline{Appendix C}}).
+The maximum \(\widehat R\) value for the fixed effects across the three models was 1.00, suggesting that these parameters had converged (Schoot et al., 2021; Vehtari et al., 2021).
+In contrast, the maximum \(\widehat R\) value for the random effects was 1.13, slightly exceeding the 1.01 threshold (Vehtari et al., 2021).
+Since the interest of the present research is on the fixed effects, and the random effects were very close to convergence, the present model is valid.
+
+The results of the posterior predictive checks were sound (see \protect\hyperlink{appendix-C-Bayesian-analysis-diagnostics}{\underline{Appendix C}}), indicating that the posterior distributions were sufficiently consistent with the observed data.
 Furthermore, in the prior sensitivity analysis, the results were virtually identical with the three priors that were considered (to recall the priors, see Figure \ref{fig:bayesian-priors} above; to view the results in detail, see \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}).
@@
 \hypertarget{semanticpriming-results}{%
-\subsection{Results}\label{semanticpriming-results}}
-
-Table \ref{tab:semanticpriming-frequentist-model} presents the results of the frequentist model.
-The fixed effects explained 4.22\% of the variance, and the random effects 11.01\% (Nakagawa et al., 2017).
-It is to be expected that random effects explain more variance, as they involve a far larger number of coefficients for each effect.
-For instance, the by-item random slopes (specifically, by prime-target pair) for a single individual-level variable (e.g., vocabulary size) involve as many coefficients as the number of items.
-Conversely, the by-participant random slopes for a single item-level variable (e.g., language-based similarity) involve as many coefficients as the number of participants.
-In contrast, each fixed effect involves 1 coefficient only.
-
-\begin{table}[H]
+\subsection{Results of Study 1}\label{semanticpriming-results}}
+
+Table \ref{tab:semanticpriming-frequentist-model} presents the results.
+The fixed effects explained 4.22\% of the variance, and the random effects explained 11.01\% (Nakagawa et al., 2017).
+It is reasonable that random effects explain more variance, as they involve a far larger number of estimates for each effect.
+That is, whereas each fixed effect is formed of one estimate, the by-item random slopes for an individual difference variable---such as vocabulary size---comprise as many estimates as the number of stimulus items (in this study, the stimuli refer to the prime--target pairs).\footnote{For future reference, it should be noted that, in Studies 2 and 3, the \emph{stimuli} are the stimulus words, as there are no prime words in those studies.} Conversely, the by-participant random slopes for an item-level variable---such as language-based similarity---comprise as many estimates as the number of participants.
+
+\begin{table}[!h]
 
@@
 \addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{Prime-target semantic relationship}}\\
+\multicolumn{6}{l}{\textbf{Prime--target relationship}}\\
 \cellcolor{gray!6}{\hspace{1em}Word-concreteness difference} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.01, 0.02]} & \cellcolor{gray!6}{3.48} & \cellcolor{gray!6}{.001}\\
@@
 \multicolumn{6}{l}{\textbf{Task condition}}\\
-\hspace{1em}Stimulus-onset asynchrony (SOA) $^{\text{b}}$ & 0.06 & 0.01 & {}[0.04, 0.07] & 7.47 & <.001\\
+\hspace{1em}Stimulus onset asynchrony (SOA) $^{\text{b}}$ & 0.06 & 0.01 & {}[0.04, 0.07] & 7.47 & <.001\\
 \addlinespace[0.3em]
@@
 \item \textit{Note}.
-$\upbeta$ = Estimate based on $z$-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CI = confidence interval.
+$\upbeta$ = Estimate based on $z$-scored predictors; \textit{SE} = standard error; \linebreak \phantom{.}CI = confidence interval.
 Shaded rows contain covariates.
@@
 
-Figure \ref{fig:semanticpriming-frequentist-bayesian-plot-informativepriors-exgaussian} displays the frequentist estimates alongside the Bayesian estimates.
-The latter are from the informative prior model.
-The estimates of the diffuse prior model were virtually identical to these (see \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}).
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_bayesian_plots/plots/semanticpriming_frequentist_bayesian_plot_informativepriors_exgaussian}
-
-}
-
-\caption{Estimates from the frequentist analysis (in red) and from the Bayesian analysis (in blue) for the semantic priming study.
-The frequentist means (represented by points) are flanked by 95\% confidence intervals.
-The Bayesian means (represented by vertical lines) are flanked by 95\% credible intervals, in light blue (in some cases, the interval is covered up by the bar of the mean).}\label{fig:semanticpriming-frequentist-bayesian-plot-informativepriors-exgaussian}
-\end{figure}
-
-Figure \ref{fig:semanticpriming-interactions-with-vocabulary-size}-a shows the interaction between vocabulary size and language-based similarity, whereby higher-vocabulary participants presented a greater benefit from the language-based similarity between prime and target words.
-That is, the greater the similarity between prime and target words, the greater the advantage for participants with higher vocabularies.
+Both language-based similarity and visual-strength difference produced significant main effects.
+As expected, their effects had opposite directions.
+On the one hand, higher values of language-based similarity facilitated participants' performance, as reflected in shorter RTs.
+On the other hand, higher values of visual-strength difference led to longer RTs.
+Furthermore, language-based similarity interacted with vocabulary size and with SOA.
+There were no effects of participants' gender (see interaction figures below).
+
+The effect sizes of language-based similarity and its interactions were larger than those of visual-strength difference.
+Figure \ref{fig:semanticpriming-frequentist-bayesian-plot-weaklyinformativepriors-exgaussian} displays the frequentist and the Bayesian estimates, which are broadly similar.
+The Bayesian estimates are from the weakly-informative prior model.
+The estimates of the two other models, based on informative and diffuse priors, were virtually identical to these (see \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}).
+
+\FloatBarrier
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_bayesian_plots/plots/semanticpriming_frequentist_bayesian_plot_weaklyinformativepriors_exgaussian}
+
+}
+
+\caption{Estimates for the semantic priming study.
+The frequentist means (represented by red points) are flanked by 95\% confidence intervals.
+The Bayesian means (represented by blue vertical lines) are flanked by 95\% credible intervals in light blue.}\label{fig:semanticpriming-frequentist-bayesian-plot-weaklyinformativepriors-exgaussian}
+\end{figure}
+
+Figure \ref{fig:semanticpriming-interactions-with-vocabulary-size}-a shows the significant interaction between language-based similarity and vocabulary size, whereby higher-vocabulary participants presented a greater benefit from the language-based similarity between prime and target words.
 This interaction replicates the results of Yap et al.
@@
 First, Yap et al.
-(2017) operationalised the priming effect as a categorical difference between related and unrelated prime-target pairs.
+(2017) operationalised the priming effect as a categorical difference between related and unrelated prime--target pairs, which were based on association ratings produced by people (Nelson et al., 2004).
 In contrast, the present study applied a continuous measure of relatedness---i.e., cosine similarity---, which is more precise and may thus afford more statistical power (Mandera et al., 2017; Petilli et al., 2021).
-Second, the analysis conducted by Yap et al.
-(2017) was correlational, whereas the present analysis used mixed-effects models that included several covariates to measure the effects of interest as rigorously as possible.
-
-Figure \ref{fig:semanticpriming-interactions-with-vocabulary-size}-b presents the interaction between vocabulary size and visual-strength difference.\footnote{All interaction plots across the three studies are based on the frequentist models.} Albeit a non-significant interaction, it is noteworthy that the effect of visual-strength difference is larger in lower-vocabulary participants.
+Therefore, this interaction demonstrates the consistency between human ratings and computational approximations to meaning (Charbonnier \& Wartena, 2019, 2020; Günther et al., 2016b; Louwerse et al., 2015; Mandera et al., 2017; Petilli et al., 2021; Solovyev, 2021; Wingfield \& Connell, 2022).
+The second difference between the present study and Yap et al.
+(2017) is that Yap et al.
+(2017) performed a correlational analysis, whereas the present analysis used maximal mixed-effects models that included several covariates to measure the effects of interest as rigorously as possible.
+
+Figure \ref{fig:semanticpriming-interactions-with-vocabulary-size}-b presents the non-significant interaction between visual-strength difference and vocabulary size.\footnote{All interaction plots across the three studies are based on the frequentist models.
+Further interaction plots available in \protect\hyperlink{appendix-D-interaction-plots}{\underline{Appendix D}}.} Albeit a non-significant interaction, the effect of visual-strength difference was larger in lower-vocabulary participants.
 
@@
 
-\caption{Interactions of vocabulary size with language-based similarity and visual-strength difference.
-Vocabulary size is constrained to deciles (ten sections) in this plot, whereas in the statistical analysis it contained more values within the current range.
-\emph{n} = number of participants contained between deciles.}\label{fig:semanticpriming-interactions-with-vocabulary-size}
-\end{figure}
-
-Methodologically, the interaction between vocabulary size and language-based similarity underscores the consistency that exists between human ratings and computational approximations to meaning (e.g., Charbonnier \& Wartena, 2019, 2020; Günther et al., 2016b; Louwerse et al., 2015; Mandera et al., 2017; Petilli et al., 2021; Solovyev, 2021; Wingfield \& Connell, 2022).
-In contrast to this consistency, some studies have found human ratings to have more explanatory power than computational measures (De Deyne et al., 2016, 2019; Gagné et al., 2016; Schmidtke et al., 2018), and other research has suggested that some computational measures are not intrinsically contentful, but arise from a missing-data problem (Snefjella \& Blank, 2020).
-In sum, this evidence suggests that computational measures are artificial, and yet valid for the study of cognition.
-
-Figure \ref{fig:semanticpriming-interactions-with-SOA} shows that the effects of language-based similarity and visual strength were both larger with the short SOA.
-Yet there is a notable difference: whereas the effect of language-based similarity is present with both SOAs (i.e., 150 ms and 1,200 ms), the effect of visual strength is almost reserved to the the long SOA.
-This finding replicates Petilli et al.
-(2021), and stands in contrast to previous findings regarding the slower pace of the visual system in semantic priming (Lam et al., 2015) and in other paradigms (Connell \& Lynott, 2013; Louwerse \& Connell, 2011).
-\textbf{conclude}\_\_\_\_\_\_\_\_\_\_\_\_\_
+\caption{Interactions of vocabulary size with language-based similarity (panel a) and with visual-strength difference (panel b).
+Vocabulary size is constrained to deciles (10 sections) in this plot, whereas in the statistical analysis it contained more values within the current range.
+\(n\) = number of participants contained between deciles.}\label{fig:semanticpriming-interactions-with-vocabulary-size}
+\end{figure}
+
+Figure \ref{fig:semanticpriming-interactions-with-SOA} shows that the effects of language-based similarity and visual-strength difference were both larger with the short SOA.
+However, whereas the effect of language-based similarity was present with both SOAs (i.e., 200 ms and 1,200 ms), the effect of visual-strength difference was almost exclusive to the the long SOA.
+These results are consistent with Petilli et al.
+(2021), whereas they contrast with previous findings regarding the slower pace of the visual system in semantic priming (Lam et al., 2015) and in other paradigms (Louwerse \& Connell, 2011).
 
@@
 
-\caption{Interactions of stimulus-onset asynchrony (SOA) with language-based similarity and visual strength.
-SOA was analysed using $z$-scores, but for clarity, the variable is shown in its basic form here.}\label{fig:semanticpriming-interactions-with-SOA}
-\end{figure}
-
-Figure \ref{fig:semanticpriming-interactions-with-gender} shows the interactions of gender with language-based similarity and visual-strength difference, albeit non-significant.\footnote{Plots of other interactions are available in \protect\hyperlink{appendix-D-interaction-plots}{\underline{Appendix D}}.}
+\caption{Interactions of stimulus onset asynchrony (SOA) with language-based similarity (panel a) and with visual-strength difference (panel b) in the semantic priming study.
+SOA was analysed using $z$-scores, but for clarity, the basic labels are used in the legend.}\label{fig:semanticpriming-interactions-with-SOA}
+\end{figure}
+
+Figure \ref{fig:semanticpriming-interactions-with-gender} shows the non-significant interactions of gender with language-based similarity and with visual-strength difference.
 
@@
 
-\caption{Interactions with gender in the semantic priming study.
-Gender was analysed using $z$-scores, but for clarity, the variable is shown in its basic form here.}\label{fig:semanticpriming-interactions-with-gender}
-\end{figure}
-
-\hypertarget{the-importance-of-outliers}{%
-\paragraph{The importance of outliers}\label{the-importance-of-outliers}}
-
-The interaction shown in Figure \ref{fig:semanticpriming-interactions-with-vocabulary-size} was patent in all deciles of vocabulary size but most notably in the participants who lie more than 1 standard deviation away from the mean.
-Outliers in individual differences have played important roles in other areas of cognition as well, such as in the domains of aphantasia and hyperphantasia---traits characterised, respectively, by a diminished and an extraordinary ability to mentally visualise objects (Milton et al., 2021; Zeman et al., 2020).
-Furthermore, if we consider the difficulty of detecting effects involving individual differences (Diaz et al., 2021; Hedge et al., 2018; Rodríguez-Ferreiro et al., 2020), and the limited representativeness of most samples of participants (Henrich et al., 2010), it may be fruitful to study more varied samples, where possible.
-
-\hypertarget{comparing-two-measures-of-vision-based-information}{%
-\subsubsection{Comparing two measures of vision-based information}\label{comparing-two-measures-of-vision-based-information}}
-
-Next, we reflected on the adequacy of visual-strength difference as a measurement instrument, as it had never been used before to operationalise the semantic priming effect.
-On the one hand, its effect on RT was negative, as we would expect.
-However, we were concerned about the low correlation between this variable and language-based similarity (\(r\) = 0.01).
-This concern was especially motivated by the correlation that Petilli et al.
-(2021) had found between their `vision-based similarity' measure and language-based similarity, which reached \(r\) = .50.
-Based on this information, we set out to run a model with the aim of comparing the performance of our measures of vision-based information.
-
-We created a subset of our data set in which we ensured that all the trials contained data from all the relevant variables---i.e., from all the existing variables and from the newly-added visual similarity from Petilli et al.~This subsetting resulted in the loss of 83\% of trials, owing to the strict selection criteria applied by Petilli et al.~in the creation of the visual-similarity measure (e.g., both the target and the prime word had to be associated to at least 100 pictures in ImageNet).
-As a result, our data set in this analysis contained 496 participants, 1,091 prime-target pairs, and 254,140 RTs.
-On average, there were 128 prime-target pairs per participant (\(SD\) = 10.37), and conversely, 58 participants per prime-target pair (\(SD\) = 4.90).
-
-Figure \ref{fig:semanticpriming-with-visualsimilarity-correlations} shows the zero-order correlations among the predictors and the dependent variable.
+\caption{Interactions of gender with language-based similarity (panel a) and with visual-strength difference (panel b) in the semantic priming study.
+Gender was analysed using $z$-scores, but for clarity, the basic labels are used in the legend.}\label{fig:semanticpriming-interactions-with-gender}
+\end{figure}
+
+\hypertarget{results-human-based-and-computational-measures-of-visual-information}{%
+\subsubsection{Human-based and computational measures of visual information}\label{results-human-based-and-computational-measures-of-visual-information}}
+
+Next, we reflected on the adequacy of visual-strength difference as a measurement instrument, as it had never (to our knowledge) been used before in the study of semantic priming.
+Even though the effect of this variable on task performance was---as expected---inhibitory (i.e., higher values of this variable leading to longer RTs), we were concerned about the low correlation between visual-strength difference and language-based similarity (\(r\) = 0.01).
+First, the negligible size of this correlation raised concerns, as we expected a larger and negative correlation.
+Second, Petilli et al.
+(2021) had found a correlation of \(r\) = .50 between vision-based similarity and language-based similarity.
+This prompted us to compare the performance of our measure---i.e., \texttt{visual-strength\ difference}---to that of Petilli et al.---i.e., \texttt{vision-based\ similarity}.
+
+For this purpose, we first subsetted our previous data set to ensure that all trials contained data from all relevant variables---i.e., from all the existing variables and from the newly-added \texttt{vision-based\ similarity} from Petilli et al.
+(2021).
+This process resulted in the loss of 83\% of trials, owing to the strict selection criteria that had been applied by Petilli et al.~in the creation of their variable---for instance, both the target and the prime word had to be associated to at least 100 pictures in ImageNet.
+The rest of the preprocessing involved the same steps as the main analysis (detailed in \protect\hyperlink{semanticpriming-dataset}{\underline{Methods}}).
+The resulting data set contained 496 participants, 1,091 prime--target pairs and 254,140 RTs.
+On average, there were 128 prime--target pairs per participant (\(SD\) = 10.37), and conversely, 58 participants per prime--target pair (\(SD\) = 4.90).
+
+Figure \ref{fig:semanticpriming-with-visualsimilarity-correlations} shows the correlations among the predictors and the dependent variable.
 
@@
 
-\caption{Zero-order correlations in the semantic priming data set that included visual similarity.}\label{fig:semanticpriming-with-visualsimilarity-correlations}
-\end{figure}
-
-\hypertarget{diagnostics-for-the-frequentist-model-1}{%
-\subsubsection{Diagnostics for the frequentist model}\label{diagnostics-for-the-frequentist-model-1}}
+\caption{Zero-order correlations in the semantic priming data set that included vision-based similarity.}\label{fig:semanticpriming-with-visualsimilarity-correlations}
+\end{figure}
+
+\hypertarget{diagnostics-for-the-frequentist-analysis-1}{%
+\subsubsection{Diagnostics for the frequentist analysis}\label{diagnostics-for-the-frequentist-analysis-1}}
 
 The model presented convergence warnings.
-To avoid removing important random slopes, which could increase the Type I error (Brauer \& Curtin, 2018; Singmann \& Kellen, 2019), we examined the model after refitting it using seven optimization algorithms through the `allFit' function of the `lme4' package (Bates et al., 2021).
-The results showed that all optimizers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential (Bates et al., 2021; see \protect\hyperlink{appendix-B-frequentist-analysis-diagnostics}{\underline{Appendix B}}).
+To avoid removing important random slopes, which could increase the Type I error rate---i.e., false positives (Brauer \& Curtin, 2018; Singmann \& Kellen, 2019), we examined the model after refitting it using seven optimisation algorithms through the `allFit' function of the `lme4' package (Bates et al., 2021).
+The results showed that all optimisers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential (Bates et al., 2021; see \protect\hyperlink{appendix-B-frequentist-analysis-diagnostics}{\underline{Appendix B}}).
 
@@
 However, this is not likely to have posed a major problem, as mixed-effects models are fairly robust to deviations from normality (Knief \& Forstmeier, 2021; Schielzeth et al., 2020).
-
-The model did not present multicollinearity problems, all VIFs being smaller than 2 (Dormann et al., 2013; Harrison et al., 2018).
-
-Due to time constraints, this analysis did not include a Bayesian model.
+Last, the model did not present multicollinearity problems, with all VIFs below 2 (see Dormann et al., 2013; Harrison et al., 2018).
 
@@
 
-Table \ref{tab:semanticpriming-with-visualsimilarity-frequentist-model} presents the results of the frequentist model.
+Table \ref{tab:semanticpriming-with-visualsimilarity-frequentist-model} presents the results.
 Due to space, the covariates are shown in Table \ref{tab:semanticpriming-with-visualsimilarity-frequentist-model-covariates}.
-The fixed effects explained 3.53\% of the variance, and the random effects 18.47\% (Nakagawa et al., 2017; for an explanation of this difference, see \protect\hyperlink{semanticpriming-results}{\underline{above}}).
-Figure \ref{fig:semanticpriming-with-visualsimilarity-confidence-intervals-plot} displays the estimates for the effects of interest.
-
-\begin{table}[H]
-
-\caption{\label{tab:semanticpriming-with-visualsimilarity-frequentist-model}Effects of interest in the semantic priming model that included visual similarity.}
+The fixed effects explained 3.53\% of the variance, and the random effects explained 18.47\% (Nakagawa et al., 2017; for an explanation of this difference, see \protect\hyperlink{semanticpriming-results}{\underline{Results of Study 1}}).
+Figure \ref{fig:semanticpriming-with-visualsimilarity-confidence-intervals-plot} displays the frequentist estimates of the effects of interest (Bayesian estimates not computed due to time constraints).
+
+\begin{table}[!h]
+
+\caption{\label{tab:semanticpriming-with-visualsimilarity-frequentist-model}Effects of interest in the semantic priming model that included vision-based similarity.}
 \centering
@@
 \addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{Prime-target semantic relationship}}\\
+\multicolumn{6}{l}{\textbf{Prime--target relationship}}\\
 \hspace{1em}Language-based similarity $^{\text{b}}$ & -0.07 & 0.01 & {}[-0.09, -0.06] & -8.33 & <.001\\
@@
 \multicolumn{6}{l}{\textbf{Task condition}}\\
-\hspace{1em}Stimulus-onset asynchrony (SOA) $^{\text{b}}$ & 0.06 & 0.01 & {}[0.04, 0.08] & 6.80 & <.001\\
+\hspace{1em}Stimulus onset asynchrony (SOA) $^{\text{b}}$ & 0.06 & 0.01 & {}[0.04, 0.08] & 6.80 & <.001\\
 \addlinespace[0.3em]
@@
 \item \textit{Note}.
-$\upbeta$ = Estimate based on $z$-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CI = confidence interval.
+$\upbeta$ = Estimate based on $z$-scored predictors; \textit{SE} = standard error; \linebreak \phantom{.}CI = confidence interval.
 Covariates shown in next table due to space.
@@
 
-\begin{table}[H]
-
-\caption{\label{tab:semanticpriming-with-visualsimilarity-frequentist-model-covariates}Covariates in the semantic priming model that included visual similarity.}
+\begin{table}[!h]
+
+\caption{\label{tab:semanticpriming-with-visualsimilarity-frequentist-model-covariates}Covariates in the semantic priming model that included vision-based similarity.}
 \centering
@@
 \addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{Individual-differences covariate}}\\
+\multicolumn{6}{l}{\textbf{Individual difference covariate}}\\
 \hspace{1em}Attentional control & 0.00 & 0.00 & {}[-0.01, 0.00] & -1.06 & .288\\
@@
 \addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{Prime-target semantic covariate}}\\
+\multicolumn{6}{l}{\textbf{Prime--target covariate}}\\
 \hspace{1em}Word-concreteness difference & 0.02 & 0.01 & {}[0.01, 0.04] & 2.73 & .006\\
@@
 \item \textit{Note}.
-$\upbeta$ = Estimate based on $z$-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CI = confidence interval.
+$\upbeta$ = Estimate based on $z$-scored predictors; \textit{SE} = standard error; \linebreak \phantom{.}CI = confidence interval.
 Some interactions are split over two lines, with the \linebreak \phantom{.}second line indented.
@@
 
+\FloatBarrier
+
 \begin{figure}
@@
 
-\caption{Means and 95\% confidence intervals for the effects of interest in the semantic priming model that included visual similarity.}\label{fig:semanticpriming-with-visualsimilarity-confidence-intervals-plot}
-\end{figure}
-
-The results revealed that visual-strength difference had a significantly larger effect.
-This difference was not due to an excessive collinearity between these measures (\(r\) = -0.04).
-Also importantly, both measures appeared to be valid based on their correlations with language-based similarity and with word concreteness.
-
-\hypertarget{statistical-power-analysis}{%
-\subsubsection{Statistical power analysis}\label{statistical-power-analysis}}
-
-Power curves were performed for most effects of interest in the main model (no power analysis was performed for the model that included visual similarity).
-Figures \ref{fig:semanticpriming-powercurve-plots-1-2-3} and \ref{fig:semanticpriming-powercurve-plots-4-5-6-7-8-9} show the estimated power for the main effects and the interactions, respectively.
+\caption{Means and 95\% confidence intervals for the effects of interest in the semantic priming model that included vision-based similarity.}\label{fig:semanticpriming-with-visualsimilarity-confidence-intervals-plot}
+\end{figure}
+
+The results revealed revealed a significant effect of visual-strength difference, as in the main analysis above.
+In contrast, the effect of vision-based similarity was not significant.
+This difference was not due to collinearity between these measures (\(r\) = -0.04).
+Also importantly, both measures appeared to be valid based on their correlations with language-based similarity and with word concreteness (Figure \ref{fig:semanticpriming-with-visualsimilarity-correlations}).
+We reflect on this result in the discussion.
+
+\hypertarget{statistical-power-analysis-2}{%
+\subsubsection{Statistical power analysis}\label{statistical-power-analysis-2}}
+
+Power curves were performed for most effects of interest in the main model.
+This was done using the main model, not the follow-up that included vision-based similarity.
+Figures \ref{fig:semanticpriming-powercurve-plots-1-2-3} and \ref{fig:semanticpriming-powercurve-plots-4-5-6-7-8-9} show the estimated power for some main effects and interactions of interest, as a function of the number of participants.
+To plan the sample size for future studies, these results must be considered under the assumptions that the future study would apply a statistical method similar to ours---namely, a mixed-effects model with random intercepts and slopes---, and that the analysis would encompass at least as many prime--target pairs as the current study, namely, 5,943 (distributed in various blocks across participants, not all being presented to every participant).
+Furthermore, it is necessary to consider each figure in detail.
+Here, we provide a summary.
+First, detecting the main effect of language-based similarity---which had a strong effect on RTs---would require 50 participants.
+Second, detecting the interaction between language-based similarity and SOA---which was a considerably weaker effect---would require 600 participants.
+Last, the other effects would require more than 1,000 participants---or, in the case of gender differences, many more than that.
 
@@
 
-\_\_\_\_\_\_\_ interpret \_\_\_\_\_\_\_\_\_\_\_\_
-
-\hypertarget{discussion}{%
-\subsection{Discussion}\label{discussion}}
-
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
+\hypertarget{discussion-of-study-1}{%
+\subsection{Discussion of Study 1}\label{discussion-of-study-1}}
+
+The results revealed a significant, facilitatory effect of \texttt{language-based\ similarity} and a smaller but significant, inhibitory effect of \texttt{visual-strength\ difference}.
+That is, a greater language-based similarity resulted in shorter RTs, whereas a greater visual-strength difference resulted in larger RTs.
+There was also a sizable effect of stimulus onset asynchrony (SOA), with shorter RTs in the short SOA condition (200 ms) than in the long SOA (1,200 ms).
+Furthermore, there were significant interactions.
+First, language-based priming was larger in higher-vocabulary participants than in lower-vocabulary ones.
+Second, both language-based priming and vision-based priming were larger with the short SOA than with the long one.
+Thus far, these results broadly replicated those of Petilli et al.
+(2021).
+It is especially noteworthy that vision-based information had a significant effect, consistent with some of the previous research (Connell \& Lynott, 2014; Flores d'Arcais et al., 1985; Petilli et al., 2021; Schreuder et al., 1984), and contrasting with other research that did not find such an effect (Ostarek \& Huettig, 2017) or only observed it after visually-focussed tasks (Pecher et al., 1998; Yee et al., 2012).
+Last, no effect of gender was found.
+Below, we delve into some other aspects of these results.
+
+\hypertarget{the-importance-of-outliers}{%
+\subsubsection{The importance of outliers}\label{the-importance-of-outliers}}
+
+The interaction between language-based similarity and vocabulary size (Figure \ref{fig:semanticpriming-interactions-with-vocabulary-size}-a) was patent in all deciles of vocabulary size but it was clearest among those participants that were more than one standard deviation away from the mean.
+Outliers in individual differences have played important roles in other areas of cognition as well, such as in the study of aphantasia and hyperphantasia---traits characterised, respectively, by a diminished and an extraordinary ability to mentally visualise objects (Milton et al., 2021; Zeman et al., 2020).
+Such an influence of outliers provides a reason to study more varied samples~of participants when possible.
+Furthermore, a greater interindividual variation might help detect the effects of individual differences that have been elusive (e.g., Hedge et al., 2018; Muraki \& Pexman, 2021; Ponari, Norbury, Rotaru, et al., 2018; Rodríguez-Ferreiro et al., 2020; Rouder \& Haaf, 2019).
+
+\hypertarget{human-based-and-computational-measures-of-vision-based-information}{%
+\subsubsection{Human-based and computational measures of vision-based information}\label{human-based-and-computational-measures-of-vision-based-information}}
+
+Next, in a secondary analysis, we compared the roles of two measures of vision-based priming.
+The first measure---\texttt{visual-strength\ difference}---was operationalised as the difference in visual strength (Lynott et al., 2020) between the prime word and the target word in each trial.
+The second measure---\texttt{vision-based\ similarity}---, created by Petilli et al.
+(2021), was based on vector representations trained on labelled images from ImageNet.
+The effect of visual-strength difference was slightly larger.
+The larger effect size of visual-strength difference---being a human-based measure---is consistent with some previous findings suggesting that human-based measures explained more variance than computational measures (De Deyne et al., 2016, 2019; Gagné et al., 2016; Schmidtke et al., 2018; cf.
+Michaelov et al., 2022; Snefjella \& Blank, 2020).
+Furthermore, whereas visual-strength difference produced a significant effect, vision-based similarity did not.
+The result of vision-based similarity contrasts with that obtained by Petilli et al.~There are several possible reasons why this variable is not significant in the present study, including: (I) a more conservative method---i.e., a maximal mixed-effects model containing more predictors than the hierarchical regression that was performed by Petilli et al.---, and (II) the presence of participant-level data in the present study, versus the aggregation performed by Petilli et al.
+
+It is noteworthy that both visual-strength difference and vision-based similarity have \emph{independently} proven to be relevant, and arguably valid, considering their correlations with other measures---especially \texttt{word-concreteness\ difference} and \texttt{language-based\ similarity}---and considering the effects of each measure in semantic priming (see Petilli et al., 2021).
+However, the differences between these measures are worthy of attention.
+Visual-strength difference was barely correlated with language-based similarity.
+Conversely, vision-based similarity was barely correlated with word-concreteness difference (recall Figure \ref{fig:semanticpriming-with-visualsimilarity-correlations}).
+These results call for an investigation into the underlying composition of visual-strength difference and vision-based similarity
+
+Next, we can consider why visual-strength difference played a more important role than vision-based similarity.
+The reason might be the fact that visual-strength difference was based on human ratings whereas vision-based similarity was a computational measure.
+Indeed, some previous studies have found human-based measures to have more explanatory power than computational measures (De Deyne et al., 2016, 2019; Gagné et al., 2016; Schmidtke et al., 2018; but also see Michaelov et al., 2022; Snefjella \& Blank, 2020).
+If the different degree of human dependence of our two variables were indeed behind the explanatory power of each, we would need to consider a related issue.
+The problem of circularity was addressed by Petilli et al.
+(2021), who argued that using human-based predictors---such as ratings---to investigate human behaviour was less valid than using predictors that were more independent of human behaviour---such as computational measures.
+On the one hand, we identify two reasons for skepticism regarding the circularity hypothesis.
+First, the underlying basis of all computational measures (e.g., Mandera et al., 2017; Petilli et al., 2021) is indeed human behaviour, notwithstanding the degree to which this human basis is filtered by computational methods.
+Second, we have not found sufficient research addressing the validity question.
+Yet, on the other hand, the circularity hypothesis is important enough to warrant dedicated research.
+Specifically, future studies could be conducted to systematically compare the theoretical insights provided by human-based measures and by computational ones, as well as the amount of explanatory power achieved by both types.
+
+\hypertarget{the-confounding-influence-of-measurement-instruments}{%
+\subsubsection{The confounding influence of measurement instruments}\label{the-confounding-influence-of-measurement-instruments}}
+
+The present comparison demonstrates the influence of measurement instruments on results, and their potential to act as confounds.
+A previous example of this influence appeared in a set of studies that used latent semantic analysis (LSA) as a predictor of semantic priming.
+Hutchison et al.
+(2008) operationalised LSA as a difference score, and did not find an effect of this variable.
+In contrast, later studies did not use a difference score and they observed a significant effect (Günther et al., 2016a; Mandera et al., 2017).
+
+In the case of linguistic and embodied processing, the large difference between the effect sizes of these systems---found in the three current studies and in previous ones (Banks et al., 2021; Kiela \& Bottou, 2014; Lam et al., 2015; Louwerse et al., 2015; Pecher et al., 1998; Petilli et al., 2021)---would be less trustworthy if the instruments that were used to measure the language system had been far more precise than the instruments used to measure the embodiment system.
+In this sense, it is relevant to consider how variables are improved in research: it is done iteratively, by comparing the performance of different variables.
+Critically, the literature contains many comparisons of text-based variables, some dating back to the 1990s (De Deyne et al., 2016, 2013; Günther et al., 2016a, 2016b; M.
+N.
+Jones et al., 2006; Lund \& Burgess, 1996; Mandera et al., 2017; Mikolov et al., 2013; Wingfield \& Connell, 2022).
+In contrast, the work on embodiment variables began more than a decade afterwards, and it has been less concerned with benchmarking the explanatory power of variables (but see Vergallito et al., 2020).
+Instead, this literature contains more comparisons of different \emph{modalities}---e.g., visual strength, auditory strength, valence, etc.
+(Lynott et al., 2020; Lynott \& Connell, 2009; Newcombe et al., 2012).
+Thus, if linguistic measures are more precise than embodiment measures due to greater work on the variables, such a difference could account for a certain portion of the superiority of linguistic information over embodied information (see Banks et al., 2021; Kiela \& Bottou, 2014; Lam et al., 2015; Louwerse et al., 2015; Pecher et al., 1998; Petilli et al., 2021).
+In conclusion, the case of different measurement instruments is one of several factors that can greatly influence the conclusions of research.
+In the medium term, it may pay dividends to devote more work to comparing different instruments and, more generally, different analytical approaches (see Barsalou, 2019; Botvinik-Nezer et al., 2020; Wagenmakers et al., 2022).
+
+\hypertarget{statistical-power-analysis-3}{%
+\subsubsection{Statistical power analysis}\label{statistical-power-analysis-3}}
+
+We analysed the statistical power associated with several effects of interest, across various sample sizes.
+The results of this power analysis can help determine the number of participants required to reliably examine each of these effects in a future study.
+Importantly, the results assume two conditions.
+First, the future study would apply a statistical method similar to ours---namely, a mixed-effects model with random intercepts and slopes.
+Second, the analysis of the future study would encompass at least 5,943 prime--target pairs (distributed in various blocks across participants, not all being presented to every participant).
+
+First, the results revealed that detecting the main effect of language-based similarity would require 50 participants.
+Next, detecting the interaction between language-based similarity and SOA would require 600 participants.
+Last, the other effects would require more than 1,000 participants---or, in the case of gender differences, many more than that.
 
@@
 
-The semantic decision task probes into the role of concreteness in conceptual processing.
-Specifically, this task requires participants to classify words as abstract or concrete.
+The semantic decision task probes the role of concreteness in conceptual processing.
+Specifically, this task requires participants to classify words as abstract or concrete, which elicits deeper semantic processing than the task of identifying word forms (i.e., lexical decision).
 Researchers then analyse whether the responses can be explained by the sensory experientiality of the referents---that is, the degree to which they can be experienced through our senses---and by other variables, such as word frequency.
 The core data set in this study was that of the Calgary Semantic Decision Project (Pexman et al., 2017; Pexman \& Yap, 2018).
-The experimental task is semantic decision, in which participants judge whether words are relatively concrete (e.g., `building') or abstract (e.g., `thought').
+The experimental task is semantic decision, in which participants judge whether words are primarily abstract (e.g., \emph{thought}) or concrete (e.g., \emph{building}).
 
 Research has found that the processing of relatively concrete words relies considerably on sensorimotor information (Hultén et al., 2021; Kousta et al., 2011; Vigliocco et al., 2014).
-In contrast, the processing of relatively abstract words seems to draw more heavily on information from language (Barca et al., 2020; Duñabeitia et al., 2009; Snefjella \& Blank, 2020), emotion (Kousta et al., 2011; Ponari et al., 2020; Ponari, Norbury, Rotaru, et al., 2018; Ponari, Norbury, \& Vigliocco, 2018; Vigliocco et al., 2014) and sociality (Borghi et al., 2019; Diveica et al., 2022).
+In contrast, the processing of relatively abstract words seems to draw more heavily on information from language (Barca et al., 2020; Duñabeitia et al., 2009; Snefjella \& Blank, 2020), emotion (Kousta et al., 2011; Ponari et al., 2020; Ponari, Norbury, Rotaru, et al., 2018; Ponari, Norbury, \& Vigliocco, 2018; Vigliocco et al., 2014), interoception (Connell et al., 2018) and social information (Borghi et al., 2022, 2019; Diveica et al., 2022).
+
+\hypertarget{methods-1}{%
+\subsection{Methods}\label{methods-1}}
+
+\hypertarget{data-set}{%
+\subsubsection{Data set}\label{data-set}}
+
+The data set was trimmed by removing rows that lacked values on any variable, and by also removing RTs that were more than 3 standard deviations away from the mean.\footnote{In the removal of missing values, six participants whose gender appeared as `NA' were inadvertently removed from the data set.} The standard deviation trimming was performed within participants and within trial blocks, as done in the Calgary Semantic Decision Project (Pexman et al., 2017).
+The resulting data set contained 306 participants, 8,927 words and 246,432 RTs.
+On average, there were 755 words per participant (\(SD\) = 42.05), and conversely, 26 participants per word (\(SD\) = 4.80).
+
+\hypertarget{variables-1}{%
+\subsubsection{Variables}\label{variables-1}}
+
+While the variables are generally described in the \protect\hyperlink{present-studies}{\underline{general introduction}}, a few further details are provided below regarding some of them.
+
+\hypertarget{vocabulary-size}{%
+\paragraph{Vocabulary size}\label{vocabulary-size}}
+
+In the vocabulary test used by Pexman et al.
+(2017), participants were presented with 35 rare words with irregular pronunciations (e.g., \emph{gaoled}, \emph{ennui}), and they were asked to read the words aloud (also see Pexman \& Yap, 2018).
+When they pronounced a word correctly, it was inferred that they knew the word.
+This test was based on NAART35, a short version of the North American Adult Reading Test (Uttl, 2002).
 
 \hypertarget{word-co-occurrence}{%
-\subsection{Word co-occurrence}\label{word-co-occurrence}}
+\paragraph{Word co-occurrence}\label{word-co-occurrence}}
 
@@
 (2017) using language-based variables that are more related to the language system than to the visual system.
-The task used by Pexman et al.~had been semantic decision, in which participants assessed whether words were abstract or concrete.
+The task used by Pexman et al.~was semantic decision, in which participants assessed whether words were abstract or concrete.
 Wingfield and Connell found that the variables that best explained RTs were word co-occurrence measures.
-Specifically, one of these variables was the correlation distance between each stimulus word and the word `abstract'.
-The other variable was the correlation distance between each stimulus word and the word `concrete'.
+Specifically, one of these variables was the corpus distance between each stimulus word and the word `abstract'.
+The other variable was the corpus distance between each stimulus word and the word `concrete'.
 Wingfield and Connell studied these distance measures in various forms, and found that cosine and correlation distance yielded the best results.
-We used the correlation distance, following the advice of Kiela and Bottou (2014) (see details below).
-
-\hypertarget{methods-2}{%
-\subsection{Methods}\label{methods-2}}
-
-\hypertarget{effects-of-interest-1}{%
-\subsubsection{Effects of interest}\label{effects-of-interest-1}}
-
-\hypertarget{vocabulary-size-1}{%
-\paragraph{Vocabulary size}\label{vocabulary-size-1}}
-
-{[}\texttt{z\_vocabulary\_size}; calculated from \texttt{NAART} in Pexman et al.
-(2017){]}.
-In the test used by Pexman and Yap (2018), participants were presented with 35 rare words, whose pronunciations are not regular (e.g., \emph{gaoled}, \emph{ennui}), and they were asked to read the words aloud.
-When they pronounced a word correctly, it was inferred that they knew the word.
-This test was based on NAART35, a short version of the North American Adult Reading Test (Uttl, 2002).
-
-\hypertarget{participants-gender}{%
-\paragraph{Participant's gender}\label{participants-gender}}
-
-{[}\texttt{z\_recoded\_participant\_gender}; calculated from \texttt{Gender} in Pexman and Yap (2018){]}
-
-\hypertarget{word-co-occurrence-1}{%
-\paragraph{Word co-occurrence}\label{word-co-occurrence-1}}
+We used the correlation distances following the advice of Kiela and Bottou (2014).
 
@@
 This new variable was named `word co-occurrence'.
-As Figure \ref{fig:semanticdecision-cooccurrence-correlations} demonstrates, the difference score captured the explanatory power of the two original variables, resulting in an increase of the correlation with word concreteness.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.58\linewidth]{manuscript_files/figure-latex/semanticdecision-cooccurrence-correlations-1}
+As shown in Figure \ref{fig:semanticdecision-cooccurrence-correlations}, the correlation between word co-occurrence and word concreteness was twice as large as the correlation between either form of the distance and word concreteness.
+This suggested that the difference score had successfully encapsulated the information of both distances.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.63\linewidth]{manuscript_files/figure-latex/semanticdecision-cooccurrence-correlations-1}
 
@@
 
-\hypertarget{visual-strength}{%
-\paragraph{Visual strength}\label{visual-strength}}
-
-{[}\texttt{z\_visual\_rating}; calculated from \texttt{Visual.mean} in Lynott et al. (2020){]}
-
-The final data set contained 306 participants, 8,927 words, and 246,432 RTs.
-On average, there were 755 words per participant (\(SD\) = 42.05), and conversely, 26 participants per word (\(SD\) = 4.80).
-
-Figure \ref{fig:semanticdecision-correlations} shows the zero-order correlations among the predictors among the predictors and the dependent variable.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.57\linewidth]{manuscript_files/figure-latex/semanticdecision-correlations-1}
-
-}
-
-\caption{Zero-order correlations in the semantic decision study.}\label{fig:semanticdecision-correlations}
-\end{figure}
-
-\hypertarget{covariates-1}{%
-\subsubsection{Covariates}\label{covariates-1}}
-
-The following covariates were included in the model to allow a rigorous analysis of the effects of interest.
+A few details regarding the covariates follow.
 
@@
 \item
-  Lexical (see \protect\hyperlink{appendix-A-lexical-covariates}{\underline{Appendix A}}): \(z\)-scored word frequency and orthographic Levenshtein distance (Balota et al., 2007)
+  \texttt{Information\ uptake} was included as a measure akin to general cognition, and specifically as a covariate of vocabulary size (Ratcliff et al., 2010; also see James et al., 2018; Pexman \& Yap, 2018).
+Information uptake was effectively the drift rate per participant in Pexman and Yap (2018).
+This drift rate measured participants' ability to correctly and quickly perform the semantic decision task, in which they classified words as abstract or concrete (for graphical illustrations, see Lerche et al., 2020; van Ravenzwaaij et al., 2012).
+In other words, drift rate measures an individual's ability (Lerche et al., 2020; Pexman \& Yap, 2018).
 \item
-  Semantic: \(z\)-scored word concreteness (Brysbaert et al., 2014).
-This variable is used as a covariate of visual strength, and it is especially fundamental in the semantic decision task, in which participants judge whether words are concrete or abstract (for a more general consideration of concreteness, see Bottini et al., 2021).
+  Lexical covariates (see \protect\hyperlink{appendix-A-lexical-covariates}{\underline{Appendix A}}): \texttt{word\ frequency} and \texttt{orthographic\ Levenshtein\ distance} (Balota et al., 2007).
+\item
+  \texttt{Word\ concreteness} (Brysbaert et al., 2014): a fundamental variable in the semantic decision task, in which participants judge whether words are abstract or concrete (for further considerations, see Bottini et al., 2021).
 Indeed, owing to the instructions of the task, word concreteness is likely to be more relevant to the participants' task than our effects of interest.
-\item
-  Individual differences: \(z\)-scored information uptake (Pexman \& Yap, 2018). This covariate is related to vocabulary size (Ratcliff et al., 2010; also see James et al., 2018; Pexman \& Yap, 2018).
 \end{itemize}
 
-\hypertarget{diagnostics-for-the-frequentist-model-2}{%
-\subsubsection{Diagnostics for the frequentist model}\label{diagnostics-for-the-frequentist-model-2}}
+Figure \ref{fig:semanticdecision-correlations} shows the correlations among the predictors and the dependent variable.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.61\linewidth]{manuscript_files/figure-latex/semanticdecision-correlations-1}
+
+}
+
+\caption{Zero-order correlations in the semantic decision study.}\label{fig:semanticdecision-correlations}
+\end{figure}
+
+\hypertarget{diagnostics-for-the-frequentist-analysis-2}{%
+\subsubsection{Diagnostics for the frequentist analysis}\label{diagnostics-for-the-frequentist-analysis-2}}
 
 The model presented convergence warnings.
-To avoid removing important random slopes, which could increase the Type I error (Brauer \& Curtin, 2018; Singmann \& Kellen, 2019), we examined the model after refitting it using seven optimization algorithms through the `allFit' function of the `lme4' package (Bates et al., 2021).
-The results showed that all optimizers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential (Bates et al., 2021; see \protect\hyperlink{appendix-B-frequentist-analysis-diagnostics}{\underline{Appendix B}}).
+To avoid removing important random slopes, which could increase the Type I error rate---i.e., false positives (Brauer \& Curtin, 2018; Singmann \& Kellen, 2019), we examined the model after refitting it using seven optimisation algorithms through the `allFit' function of the `lme4' package (Bates et al., 2021).
+The results showed that all optimisers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential (Bates et al., 2021; see \protect\hyperlink{appendix-B-frequentist-analysis-diagnostics}{\underline{Appendix B}}).
 
@@
 However, this is not likely to have posed a major problem, as mixed-effects models are fairly robust to deviations from normality (Knief \& Forstmeier, 2021; Schielzeth et al., 2020).
-
-The model did not present multicollinearity problems, all VIFs being smaller than 2 (Dormann et al., 2013; Harrison et al., 2018).
-
-\hypertarget{diagnostics-for-the-bayesian-model-1}{%
-\subsubsection{Diagnostics for the Bayesian model}\label{diagnostics-for-the-bayesian-model-1}}
+Last, the model did not present multicollinearity problems, with all VIFs below 2 (see Dormann et al., 2013; Harrison et al., 2018).
+
+\hypertarget{diagnostics-for-the-bayesian-analysis-1}{%
+\subsubsection{Diagnostics for the Bayesian analysis}\label{diagnostics-for-the-bayesian-analysis-1}}
 
@@
 Similarly, the maximum \(\widehat R\) value for the random effects was 1.31.
-Furthermore, the posterior predictive checks revealed major divergences between the observed data and the predicted outcome (see \protect\hyperlink{appendix-C-Bayesian-analysis-diagnostics}{\underline{Appendix C}}).
-Since the results were not valid, they are not shown in the main text but in \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}.
-
-\hypertarget{results-1}{%
-\subsection{Results}\label{results-1}}
-
-Table \ref{tab:semanticdecision-frequentist-model} presents the results of the frequentist model.
-The fixed effects explained 4.11\% of the variance, and the random effects 17.48\% {[}Nakagawa et al.
-(2017); for an explanation of this difference, see \protect\hyperlink{semanticpriming-results}{\underline{Results of Study 1}}).
-Figure \ref{fig:semanticdecision-confidence-intervals-plot} displays these estimates.\footnote{Bayesian estimates not shown as they were not valid.
-They are nonetheless available in \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}.}
-
-\begin{table}[H]
+Furthermore, the posterior predictive checks revealed major divergences between the observed data and the posterior distributions (see \protect\hyperlink{appendix-C-Bayesian-analysis-diagnostics}{\underline{Appendix C}}).
+In conclusion, since the Bayesian results were not valid, they are not shown in the main text, but are available in \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}.
+
+\hypertarget{results-of-study-2}{%
+\subsection{Results of Study 2}\label{results-of-study-2}}
+
+Table \ref{tab:semanticdecision-frequentist-model} presents the results.
+The fixed effects explained 4.11\% of the variance, and the random effects explained 17.48\% (Nakagawa et al., 2017; for an explanation of this difference, see \protect\hyperlink{semanticpriming-results}{\underline{Results of Study 1}}).
+Both word co-occurrence and visual strength produced significant main effects.
+Higher values of these variables facilitated participants' performance, as reflected in shorter RTs.
+Furthermore, visual strength interacted with vocabulary size.
+There were no effects of participants' gender (see interaction figures below).
+
+The effect sizes of word co-occurrence and its interactions were larger than those of visual strength.
+Figure \ref{fig:semanticdecision-confidence-intervals-plot} displays these estimates.\footnote{Only frequentist estimates shown, as Bayesian ones were not valid (see \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}).}
+
+\begin{table}[!h]
 
@@
 \addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{Lexical covariates}}\\
+\multicolumn{6}{l}{\textbf{Lexicosemantic covariates}}\\
 \cellcolor{gray!6}{\hspace{1em}Word frequency} & \cellcolor{gray!6}{-0.12} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[-0.13, -0.12]} & \cellcolor{gray!6}{-28.63} & \cellcolor{gray!6}{<.001}\\
 \cellcolor{gray!6}{\hspace{1em}Orthographic Levenshtein distance} & \cellcolor{gray!6}{-0.01} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[-0.02, 0.00]} & \cellcolor{gray!6}{-3.05} & \cellcolor{gray!6}{.002}\\
+\cellcolor{gray!6}{\hspace{1em}Word concreteness} & \cellcolor{gray!6}{-0.13} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[-0.14, -0.11]} & \cellcolor{gray!6}{-21.39} & \cellcolor{gray!6}{<.001}\\
 \addlinespace[0.3em]
 \multicolumn{6}{l}{\textbf{Semantic variables}}\\
-\cellcolor{gray!6}{\hspace{1em}Word concreteness} & \cellcolor{gray!6}{-0.13} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[-0.14, -0.11]} & \cellcolor{gray!6}{-21.39} & \cellcolor{gray!6}{<.001}\\
 \hspace{1em}Word co-occurrence $^{\text{b}}$ & -0.03 & 0.01 & {}[-0.04, -0.02] & -4.48 & <.001\\
@@
 \item \textit{Note}.
-$\upbeta$ = Estimate based on $z$-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CI = confidence interval.
+$\upbeta$ = Estimate based on $z$-scored predictors; \textit{SE} = standard error; \linebreak \phantom{.}CI = confidence interval.
 Shaded rows contain covariates.
-Some interactions are \linebreak \phantom{.}split over two lines, with the second line indented.
 \linebreak \linebreak \phantom{.}$^{\text{a}}$ By-word random slopes were included for this effect.
@@
 
-Figures \ref{fig:semanticdecision-interactions-with-vocabulary-size}-a and \ref{fig:semanticdecision-interactions-with-vocabulary-size}-b demonstrate how lower-vocabulary participants (compared to higher-vocabulary participants) were more strongly influenced by both language- and vision-based similarity.
-In contrast, Figure \ref{fig:semanticdecision-interactions-with-vocabulary-size}-c shows that higher-vocabulary participants benefitted more strongly from word concreteness.
-Since the variable that is most relevant to the semantic decision task is word concreteness, the present interactions suggest that higher-vocabulary participants were better able to focus on the most relevant information, whereas lower-vocabulary participants were sensitive to a greater breadth of information (Lim et al., 2020; Pexman \& Yap, 2018; Yap et al., 2009, 2012, 2017).
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.9\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/plots/semanticdecision-interactions-with-vocabulary-size}
-
-}
-
-\caption{Interactions of vocabulary size with (a) language-based information, (b) visual strength and (c) word concreteness.
+Figure \ref{fig:semanticdecision-interactions-with-vocabulary-size}-a shows the non-significant interaction between word co-occurrence and vocabulary size, whereby lower-vocabulary participants were more sensitive to word co-occurrence than higher-vocabulary participants.
+Next, Figure \ref{fig:semanticdecision-interactions-with-vocabulary-size}-b shows the significant interaction between visual strength and vocabulary size, demonstrating that lower-vocabulary participants were also more sensitive to visual strength.
+Last, Figure \ref{fig:semanticdecision-interactions-with-vocabulary-size}-c shows the significant interaction between word concreteness and vocabulary size, whereby higher-vocabulary participants were more sensitive to word concreteness than lower-vocabulary participants.
+Word concreteness is likely the most relevant variable for the semantic decision task, in which participants classify words as abstract or concrete.
+In conclusion, these interactions suggest that higher-vocabulary participants were better able to focus on the most relevant information, whereas lower-vocabulary participants were
+sensitive to a greater breadth of information (see Lim et al., 2020; Pexman \& Yap, 2018; Yap et al., 2009, 2012, 2017).
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.98\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/plots/semanticdecision-interactions-with-vocabulary-size}
+
+}
+
+\caption{Interactions of vocabulary size with language-based information (panel a), with visual strength (panel b) and with word concreteness (panel c) in the semantic decision study.
 Vocabulary size is constrained to deciles in this plot, whereas in the statistical analysis it contained more values within the current range.
-\emph{n} = number of participants contained between deciles.}\label{fig:semanticdecision-interactions-with-vocabulary-size}
-\end{figure}
-
-The present analysis used a continuous measure of word concreteness.
-In contrast, Pexman and Yap (2018) analysed the same data set after dividing the stimulus words into abstract and concrete subsets, which they analysed separately.
+\(n\) = number of participants contained between deciles.}\label{fig:semanticdecision-interactions-with-vocabulary-size}
+\end{figure}
+
+A continuous measure of word concreteness was used in the present study.
+In contrast, Pexman and Yap (2018) split the data set it into a subset with abstract words and another subset with concrete words, and they analysed these subsets separately.
 Pexman and Yap found that high-vocabulary participants were more sensitive to the relative abstractness of words.
-Specifically, these participants were faster to classify very abstract words than mid-abstract ones, thus presenting a reverse concreteness effect.
-Such a reverse effect might stem from the bimodal distributions of concreteness ratings (Brysbaert et al., 2014) and semantic decisions (Pexman \& Yap, 2018).
-The reverse effect has also been found in semantic dementia patients (Connell \& Lynott, 2012).
-Since the reverse effect contrasted with the long-established concreteness effect, the former has sometimes been regarded as an inconsistency.
-
-Notwithstanding the aforementioned bimodal distributions, Troche et al.
-(2017) suggested that a continuous analysis remains necessary to study word concreteness (also see Cohen, 1983).
+Specifically, these participants were faster to classify very abstract words than mid-abstract ones, thus presenting a reverse concreteness effect (also see Bonner et al., 2009).
+Such a reverse effect might stem from the bimodal distributions that have appeared in concreteness ratings (Brysbaert et al., 2014) and in semantic decisions (Pexman \& Yap, 2018), or it might be due to confounding variables (Hoffman \& Lambon Ralph, 2011).
+Notwithstanding the bimodal distributions, Troche et al.
+(2017) suggested that a continuous analysis remained necessary to study word concreteness (also see Cohen, 1983).
 Consistent with this, our present findings demonstrated the sensitivity of a continuous word concreteness variable to patterns such as the greater role of task-relevant variables in high-vocabulary participants.
 In conclusion, the literature and our findings suggest that the split-data approach and the continuous approach to word concreteness are both useful.
-Where feasible, the application of both approaches would provide the most information.
-
-Figure \ref{fig:semanticdecision-interactions-with-gender} shows the interactions of gender with language-based similarity and visual-strength difference, albeit non-significant.\footnote{Plots of other interactions are available in \protect\hyperlink{appendix-D-interaction-plots}{\underline{Appendix D}}.}
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.9\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/plots/semanticdecision-interactions-with-gender}
-
-}
-
-\caption{Interactions with gender in the semantic decision study.
-Gender was analysed using $z$-scores, but for clarity, the variable is shown in its basic form here.}\label{fig:semanticdecision-interactions-with-gender}
-\end{figure}
-
-\hypertarget{statistical-power-analysis-1}{%
-\subsubsection{Statistical power analysis}\label{statistical-power-analysis-1}}
-
-Figures \ref{fig:semanticdecision-powercurve-plots-1-2-3} and \ref{fig:semanticdecision-powercurve-plots-4-5-6-7} show the estimated power available for main effects and interactions of interest, respectively.
+Where it is feasible, the application of both approaches would provide the greatest information.
+
+Figure \ref{fig:semanticdecision-interactions-with-gender} shows the interactions with gender.
+The interactions of interest, in panels a and b, were non-significant.\footnote{Further interaction plots available in \protect\hyperlink{appendix-D-interaction-plots}{\underline{Appendix D}}.}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.98\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/plots/semanticdecision-interactions-with-gender}
+
+}
+
+\caption{Interactions of gender with word co-occurrence (panel a), with visual strength (panel b) and with word concreteness (panel c) in the semantic decision study.
+Gender was analysed using $z$-scores, but for clarity, the basic labels are used in the legend.}\label{fig:semanticdecision-interactions-with-gender}
+\end{figure}
+
+\hypertarget{statistical-power-analysis-4}{%
+\subsubsection{Statistical power analysis}\label{statistical-power-analysis-4}}
+
+Figures \ref{fig:semanticdecision-powercurve-plots-1-2-3} and \ref{fig:semanticdecision-powercurve-plots-4-5-6-7} show the estimated power for some main effects and interactions of interest, as a function of the number of participants.
+To plan the sample size for future studies, these results must be considered under the assumptions that the future study would apply a statistical method similar to ours---namely, a mixed-effects model with random intercepts and slopes---, and that the analysis would encompass at least as many words as the current study, namely, 8,927 (distributed in various blocks across participants, not all being presented to every participant).
+Furthermore, it is necessary to consider each figure in detail.
+Here, we provide a summary.
+First, detecting the main effect of word co-occurrence would require 300 participants.
+Second, detecting the main effect of visual strength would require 1,200 participants.
+Third, detecting the interactions of word co-occurrence and visual strength with vocabulary size would require 1,500 participants.
+Last, detecting the other effects would require more than 2,000 participants---or, in the case of gender differences, many more than that.
 
@@
 
-\_\_\_\_\_\_\_ interpret \_\_\_\_\_\_\_\_\_\_\_\_
-
-\hypertarget{discussion-1}{%
-\subsection{Discussion}\label{discussion-1}}
-
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
+\hypertarget{discussion-of-study-2}{%
+\subsection{Discussion of Study 2}\label{discussion-of-study-2}}
+
+The results revealed a significant, facilitatory effect of \texttt{word\ co-occurrence} and a smaller but significant, facilitatory effect of \texttt{visual\ strength}.
+That is, higher values of these variables resulted in shorter RTs.
+Furthermore, there were significant interactions.
+First, language-based priming was larger in higher-vocabulary participants than in lower-vocabulary ones.
+Second, both language-based priming and vision-based priming were larger with the short SOA than with the long one.
+Thus far, these results broadly replicated those of Petilli et al.
+(2021).
+As in Study 1, vision-based information had a significant effect.
+This was to be expected, as semantic decision is likely to engage deeper semantic processing.
+Last, no effect of gender was found.
+Below, we delve into some other aspects of these results.
+
+\hypertarget{statistical-power-analysis-5}{%
+\subsubsection{Statistical power analysis}\label{statistical-power-analysis-5}}
+
+We analysed the statistical power associated with several effects of interest, across various sample sizes.
+The results of this power analysis can help determine the number of participants required to reliably examine each of these effects in a future study.
+Importantly, the results assume two conditions.
+First, the future study would apply a statistical method similar to ours---namely, a mixed-effects model with random intercepts and slopes.
+Second, the analysis of the future study would encompass at least 8,927 stimulus words (distributed in various blocks across participants, not all being presented to every participant).
+
+First, the results revealed that detecting the main effect of word co-occurrence would require 300 participants.
+Next, detecting the interactions with vocabulary size would require 1,500 participants.
+Last, detecting the other effects would require more than 2,000 participants---or, in the case of gender differences, many more than that.
 
@@
 
-\hypertarget{study-3-lexical-decision}{%
-\section{Study 3: Lexical decision}\label{study-3-lexical-decision}}
-
-The core data set in this study was the lexical decision subset of the English Lexicon Project---ELP (Balota et al., 2007).
+\hypertarget{lexicaldecision}{%
+\section{Study 3: Lexical decision}\label{lexicaldecision}}
+
+The core data set in this study was the lexical decision subset of the English Lexicon Project (ELP; Balota et al., 2007).
+As in Study 1, we limited our analysis to the lexical decision task because it was more relevant to a subsequent study that we were planning.
 The lexical decision task differs from semantic priming and semantic decision in two important aspects.
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\item
-  \textbf{Less semantic processing.} The lexical decision paradigm is likely to involve less semantic processing than the other paradigms. \_\_\_\_\_\_\_\_\_\_\_\_
-\item
-  \textbf{Single-word measures.} Compared to semantic priming and semantic decision, it is more difficult in the lexical decision paradigm to create word-to-word distance measures to capture language-based and vision-based information.
-The possibility of calculating the distance between words in consecutive trials is hindered by the need to skip trials, owing to the high prevalence of nonword trials in the lexical decision paradigm.
+First, lexical decision is likely to involve less semantic processing than the other paradigms (Balota \& Lorch, 1986; Becker et al., 1997; de Wit \& Kinoshita, 2015; Joordens \& Becker, 1997; Muraki \& Pexman, 2021; Ostarek \& Huettig, 2017).
+
+Second, it is more difficult in the lexical decision task to create word-to-word distance measures to capture language-based and vision-based information.
+The possibility of calculating the distance between words in consecutive trials is hindered by the need to skip trials, owing to the high prevalence of nonword trials throughout the lexical decision task.
 Therefore, the measures must be based on each word alone.
 Accordingly, vision-based information can be operationalised as the visual strength of each word.
-Language-based information could be operationalised as any of several lexical variables.
-In the present study, word frequency was chosen as it had the most explanatory power out of 5 candidates---the other candidates being number of letters, number of syllables, orthographic Levenshtein distance and phonological Levenshtein distance (see \protect\hyperlink{appendix-A-lexical-covariates}{\underline{Appendix A}}).
-It should also be noted that word frequency has been found to be more closely related to semantic variables than to lexical ones, such as word length, orthography, phonology (see Table 4 in Yap et al., 2012).
-\end{enumerate}
-
-Word frequency is also of interest due to its varying relationship to vocabulary size across different paradigms.
-Yap et al.
-(2012) found that higher-vocabulary participants in the ELP were more strongly influenced by word frequency than lower-vocabulary participants.
-The same finding also appeared in a lexical decision study in Chinese (Lim et al., 2020).
-In contrast, deeper semantic tasks, such as semantic priming (Yap et al., 2017) and semantic decision (Pexman \& Yap, 2018), have yielded the opposite pattern, with the effect of word frequency decreasing in higher-vocabulary participants.
-
-\hypertarget{effects-of-interest-2}{%
-\subsection{Effects of interest}\label{effects-of-interest-2}}
+Language-based information could be operationalised as one of several lexical variables.
+In the present study, word frequency was chosen as it had the most explanatory power out of five candidates---the other candidates being number of letters, number of syllables, orthographic Levenshtein distance and phonological Levenshtein distance (see \protect\hyperlink{appendix-A-lexical-covariates}{\underline{Appendix A}}).
+It should also be noted that word frequency has been found to be more closely related to semantic variables than to lexical ones, such as word length, orthography and phonology (see Table 4 in Yap et al., 2012).
+Another noteworthy feature of word frequency how it relates to vocabulary size across different paradigms.
+In lexical decision, the effect of word frequency has been stronger in higher-vocabulary participants than in lower-vocabulary ones (Lim et al., 2020; Yap et al., 2012).
+In contrast, the opposite pattern has emerged in deeper semantic tasks, such as semantic priming (Yap et al., 2017) and semantic decision (Pexman \& Yap, 2018).
+
+\hypertarget{methods-2}{%
+\subsection{Methods}\label{methods-2}}
+
+\hypertarget{data-set-1}{%
+\subsubsection{Data set}\label{data-set-1}}
+
+The data set was trimmed by removing rows that lacked values on any variable, and by also removing RTs that were more than 3 standard deviations away from the mean.
+The standard deviation trimming was performed within participants, as done in the English Lexicon Project (Balota et al., 2007).
+The resulting data set contained 795 participants, 12,636 words and 19,828 RTs.
+On average, there were 25 words per participant (\(SD\) = 36.04), and conversely, 2 participants per word (\(SD\) = 0.86).
+
+Figure \ref{fig:lexicaldecision-correlations} shows the correlations among the predictors and the dependent variable.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.52\linewidth]{manuscript_files/figure-latex/lexicaldecision-correlations-1}
+
+}
+
+\caption{Zero-order correlations in the lexical decision study.}\label{fig:lexicaldecision-correlations}
+\end{figure}
+
+\hypertarget{variables-2}{%
+\subsubsection{Variables}\label{variables-2}}
+
+While the variables are generally described in the \protect\hyperlink{present-studies}{\underline{general introduction}}, a few further details are provided below regarding some of them.
+
+\begin{itemize}
+\tightlist
+\item
+  \texttt{Vocabulary\ age}: the present study uses the name vocabulary \emph{age}, as used in the study of Balota et al. (2007). It measures the same linguistic experience as vocabulary size.
+\end{itemize}
+
+A few details regarding the covariates follow.
 
@@
 \item
-  \(Z\)-scored vocabulary age {[}\texttt{z\_vocabulary\_age}; calculated from \texttt{vocabAge} in Balota et al. (2007){]}
+  General cognition covariate: unlike in the two previous studies, the present study did not include a general cognition covariate as such a variable was not available in the data set of Balota et al.
+(2007).
 \item
-  \(Z\)-scored, recoded participant's gender {[}\texttt{z\_recoded\_participant\_gender}; calculated from \texttt{Gender} in Balota et al. (2007){]}
+  Lexical covariates (see preselection in \protect\hyperlink{appendix-A-lexical-covariates}{\underline{Appendix A}}): \texttt{orthographic\ Levenshtein\ distance} (Balota et al., 2007).
 \item
-  \(Z\)-scored word frequency {[}\texttt{z\_word\_frequency}; calculated from \texttt{LgSUBTLWF} in Balota et al. (2007){]}
-\item
-  \(Z\)-scored vision-based information in words {[}\texttt{z\_visual\_rating}; calculated from \texttt{Visual.mean} in Lynott et al. (2020){]}
+  \texttt{Word\ concreteness} (Brysbaert et al., 2014), used as a covariate of visual strength.
 \end{itemize}
 
-The final data set contained 795 participants, 12,636 words, and 19,828 RTs. On average, there were 25 words per participant (\(SD\) = 36.04), and conversely, 2 participants per word (\(SD\) = 0.86).
-
-Figure \ref{fig:lexicaldecision-correlations} shows the zero-order correlations among the predictors and the dependent variable.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.5\linewidth]{manuscript_files/figure-latex/lexicaldecision-correlations-1}
-
-}
-
-\caption{Zero-order correlations in the lexical decision study.}\label{fig:lexicaldecision-correlations}
-\end{figure}
-
-\hypertarget{covariates-2}{%
-\subsection{Covariates}\label{covariates-2}}
-
-The following lexical covariates were included in the model to allow a rigorous analysis of the effects of interest.
-
-\begin{itemize}
-\item
-  Lexical (see \protect\hyperlink{appendix-A-lexical-covariates}{\underline{Appendix A}}): \(Z\)-scored orthographic Levenshtein distance (Balota et al., 2007)
-\item
-  Semantic: \(z\)-scored word concreteness (Brysbaert et al., 2014), used as a covariate of visual rating.
-\end{itemize}
-
-\hypertarget{diagnostics-for-the-frequentist-model-3}{%
-\subsubsection{Diagnostics for the frequentist model}\label{diagnostics-for-the-frequentist-model-3}}
+\hypertarget{diagnostics-for-the-frequentist-analysis-3}{%
+\subsubsection{Diagnostics for the frequentist analysis}\label{diagnostics-for-the-frequentist-analysis-3}}
 
 The model presented convergence warnings.
-To avoid removing important random slopes, which could increase the Type I error (Brauer \& Curtin, 2018; Singmann \& Kellen, 2019), we examined the model after refitting it using seven optimization algorithms through the `allFit' function of the `lme4' package (Bates et al., 2021).
-The results showed that all optimizers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential (Bates et al., 2021; see \protect\hyperlink{appendix-B-frequentist-analysis-diagnostics}{\underline{Appendix B}}).
+To avoid removing important random slopes, which could increase the Type I error rate---i.e., false positives (Brauer \& Curtin, 2018; Singmann \& Kellen, 2019), we examined the model after refitting it using seven optimisation algorithms through the `allFit' function of the `lme4' package (Bates et al., 2021).
+The results showed that all optimisers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential (Bates et al., 2021; see \protect\hyperlink{appendix-B-frequentist-analysis-diagnostics}{\underline{Appendix B}}).
 
@@
 However, this is not likely to have posed a major problem, as mixed-effects models are fairly robust to deviations from normality (Knief \& Forstmeier, 2021; Schielzeth et al., 2020).
-
-The model did not present multicollinearity problems, all VIFs being smaller than 2 (Dormann et al., 2013; Harrison et al., 2018).
-
-\hypertarget{diagnostics-for-the-bayesian-model-2}{%
-\subsubsection{Diagnostics for the Bayesian model}\label{diagnostics-for-the-bayesian-model-2}}
+Last, the model did not present multicollinearity problems, with all VIFs below 2 (see Dormann et al., 2013; Harrison et al., 2018).
+
+\hypertarget{diagnostics-for-the-bayesian-analysis-2}{%
+\subsubsection{Diagnostics for the Bayesian analysis}\label{diagnostics-for-the-bayesian-analysis-2}}
 
@@
 
-The maximum \(\widehat R\) value for the fixed effects across the three models was 1.00, suggesting that these effects converged (Schoot et al., 2021; Vehtari et al., 2021).
+The maximum \(\widehat R\) value for the fixed effects across the three models was 1.00, suggesting that these effects hadconverged (Schoot et al., 2021; Vehtari et al., 2021).
 For the random effects, the maximum \(\widehat R\) value was 1.02, barely exceeding the 1.01 threshold (Vehtari et al., 2021).
 
-The posterior predictive checks were sound (see \protect\hyperlink{appendix-C-Bayesian-analysis-diagnostics}{\underline{Appendix C}}).
+The results of the posterior predictive checks were sound (see \protect\hyperlink{appendix-C-Bayesian-analysis-diagnostics}{\underline{Appendix C}}), indicating that the posterior distributions were sufficiently consistent with the observed data.
 Furthermore, in the prior sensitivity analysis, the results were virtually identical with the three priors that were considered (to recall the priors, see Figure \ref{fig:bayesian-priors} above; to view the results in detail, see \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}).
 
-\hypertarget{results-2}{%
-\subsection{Results}\label{results-2}}
-
-Table \ref{tab:lexicaldecision-frequentist-model} presents the results of the frequentist model.
-The fixed effects explained 5.61\% of the variance, and the random effects 10.25\% {[}Nakagawa et al.
-(2017); for an explanation of this difference, see \protect\hyperlink{semanticpriming-results}{\underline{Results of Study 1}}).
-Figure \ref{fig:lexicaldecision-frequentist-bayesian-plot-weaklyinformativepriors-exgaussian} displays the frequentist estimates alongside the Bayesian estimates.
-The latter are from the weakly-informative prior model.
-The estimates of the two other models (i.e., with informative and diffuse priors, respectively) were virtually identical to these (see \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}).
-
-\begin{table}[H]
+\hypertarget{results-of-study-3}{%
+\subsection{Results of Study 3}\label{results-of-study-3}}
+
+Table \ref{tab:lexicaldecision-frequentist-model} presents the results.
+The fixed effects explained 5.61\% of the variance, and the random effects explained 10.25\% (Nakagawa et al., 2017; for an explanation of this difference, see \protect\hyperlink{semanticpriming-results}{\underline{Results of Study 1}}).
+Word frequency produced a significant main effect, with higher values of variable facilitating participants' performance, as reflected in shorter RTs.
+None of the other effects of interest were significant.
+
+The effect size of word frequency was far larger than that of visual strength.
+Figure \ref{fig:lexicaldecision-frequentist-bayesian-plot-weaklyinformativepriors-exgaussian} displays the frequentist and the Bayesian estimates, which are broadly similar.
+The Bayesian estimates are from the weakly-informative prior model.
+The estimates of the two other models, based on informative and diffuse priors, were virtually identical to these (see \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}).
+
+\FloatBarrier
+
+\begin{table}[!h]
 
@@
 \addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{Lexical covariate}}\\
+\multicolumn{6}{l}{\textbf{Lexicosemantic covariates}}\\
 \cellcolor{gray!6}{\hspace{1em}Orthographic Levenshtein distance} & \cellcolor{gray!6}{0.11} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[0.09, 0.12]} & \cellcolor{gray!6}{13.41} & \cellcolor{gray!6}{<.001}\\
+\cellcolor{gray!6}{\hspace{1em}Word concreteness} & \cellcolor{gray!6}{-0.02} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[-0.04, -0.01]} & \cellcolor{gray!6}{-2.79} & \cellcolor{gray!6}{.005}\\
 \addlinespace[0.3em]
 \multicolumn{6}{l}{\textbf{Semantic variables}}\\
-\cellcolor{gray!6}{\hspace{1em}Word concreteness} & \cellcolor{gray!6}{-0.02} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[-0.04, -0.01]} & \cellcolor{gray!6}{-2.79} & \cellcolor{gray!6}{.005}\\
 \hspace{1em}Word frequency $^{\text{b}}$ & -0.16 & 0.01 & {}[-0.18, -0.14] & -13.01 & <.001\\
@@
 
-\caption{Estimates from the frequentist analysis (in red) and from the Bayesian analysis (in blue) for the lexical decision study.
-The frequentist means (represented by points) are flanked by 95\% confidence intervals.
-The Bayesian means (represented by vertical lines) are flanked by 95\% credible intervals, in light blue (in some cases, the interval is covered up by the bar of the mean).}\label{fig:lexicaldecision-frequentist-bayesian-plot-weaklyinformativepriors-exgaussian}
-\end{figure}
-
-Figure \ref{fig:lexicaldecision-interactions-with-vocabulary-age} presents the interactions of vocabulary age with word frequency and with visual strength, albeit non-significant.
+\caption{Estimates for the lexical decision study.
+The frequentist means (represented by red points) are flanked by 95\% confidence intervals.
+The Bayesian means (represented by blue vertical lines) are flanked by 95\% credible intervals in light blue.}\label{fig:lexicaldecision-frequentist-bayesian-plot-weaklyinformativepriors-exgaussian}
+\end{figure}
+
+Figure \ref{fig:lexicaldecision-interactions-with-vocabulary-age} presents the interactions of vocabulary age with word frequency and with visual strength, both non-significant.
+Figure \ref{fig:lexicaldecision-interactions-with-gender} shows the interactions with gender, both non-significant too.\footnote{Further interaction plots available in \protect\hyperlink{appendix-D-interaction-plots}{\underline{Appendix D}}.}
 
@@
 
-\caption{Interactions of vocabulary age with word frequency and visual strength.
-Vocabulary age is constrained to sextiles (six sections) in this plot, whereas in the statistical analysis it contained more values within the current range.
-\emph{n} = number of participants contained between sextiles.}\label{fig:lexicaldecision-interactions-with-vocabulary-age}
-\end{figure}
-
-Figure \ref{fig:lexicaldecision-interactions-with-gender} shows the interactions of gender with language-based similarity and visual-strength difference, albeit non-significant.\footnote{Plots of other interactions are available in \protect\hyperlink{appendix-D-interaction-plots}{\underline{Appendix D}}.}
+\caption{Interactions of vocabulary age with word frequency (panel a) and with visual strength (panel b).
+Vocabulary age is constrained to sextiles (6 sections) in this plot, whereas in the statistical analysis it contained more values within the current range.
+Sextiles were used because there was not enough data for deciles nor for octiles.
+\(n\) = number of participants contained between sextiles.}\label{fig:lexicaldecision-interactions-with-vocabulary-age}
+\end{figure}
 
@@
 
-\caption{Interactions with gender in the lexical decision study.
-Gender was analysed using $z$-scores, but for clarity, the variable is shown in its basic form here.}\label{fig:lexicaldecision-interactions-with-gender}
-\end{figure}
-
-\hypertarget{statistical-power-analysis-2}{%
-\subsubsection{Statistical power analysis}\label{statistical-power-analysis-2}}
-
-Figures \ref{fig:lexicaldecision-powercurve-plots-1-2-3} and \ref{fig:lexicaldecision-powercurve-plots-4-5-6-7} show the estimated power available for main effects and interactions of interest, respectively.
+\caption{Interactions of gender with word frequency (panel a) and with visual strength (panel b) in the lexical decision study.
+Gender was analysed using $z$-scores, but for clarity, the basic labels are used in the legend.}\label{fig:lexicaldecision-interactions-with-gender}
+\end{figure}
+
+\hypertarget{statistical-power-analysis-6}{%
+\subsubsection{Statistical power analysis}\label{statistical-power-analysis-6}}
+
+Figures \ref{fig:lexicaldecision-powercurve-plots-1-2-3} and \ref{fig:lexicaldecision-powercurve-plots-4-5-6-7} show the estimated power for some main effects and interactions of interest, as a function of the number of participants.
+To plan the sample size for future studies, these results must be considered under the assumptions that the future study would apply a statistical method similar to ours---namely, a mixed-effects model with random intercepts and slopes---, and that the analysis would encompass at least as many words as the current study, namely, 12,636 (distributed in various blocks across participants, not all being presented to every participant).
+Furthermore, it is necessary to consider each figure in detail.
+Here, we provide a summary.
+First, detecting the main effect of word frequency would require 100 participants.
+Second, detecting the interactions of word frequency and visual strength with vocabulary size would require 1,500 participants.
+Third, detecting the other effects would require more than 2,000 participants.
 
@@
 
-\_\_\_\_\_\_\_ interpret \_\_\_\_\_\_\_\_\_\_\_\_
-
-\hypertarget{discussion-2}{%
-\subsection{Discussion}\label{discussion-2}}
-
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
-
-\hypertarget{general-discussion}{%
-\section{General discussion}\label{general-discussion}}
-
-In all three studies, the main effects and the interactions of language-based information were larger than those of vision-based information, consistent with previous research {[}\ldots{]}.
-Beyond that, the results revealed a dynamic process influenced by three levels of variation: participants, words and tasks.
-The associations that appeared across these levels revealed the roles of language-based and vision-based mechanisms in conceptual processing.
+\hypertarget{discussion-of-study-3}{%
+\subsection{Discussion of Study 3}\label{discussion-of-study-3}}
+
+In the present study, we have delved into a task that is likely to elicit a shallower level of semantic processing than the tasks from the previous studies.
+Furthermore, the data set used in this study was considerably smaller (19,828 RTs, compared to 345,666 RTs in Study 1 and 246,432 in Study 2).
+While the covariates presented large effects, none of the effects of interest turned out to be significant or noteworthy.
+The comparison with the two previous tasks is hindered by the major difference in the size of the data sets.
+Therefore, while it would be reasonable to expect---in the lexical decision task---smaller semantic effects---as we indeed observed---, we cannot reliably attribute this difference to the nature of the task, due to the difference in the size of the data sets.
+As a minor suggestion, future studies could operationalise language using a measure of orthographic neighbourhood size, such as Levenshtein distance, instead of word frequency.
+While we used word frequency guided by a data-driven selection (see Appendix A), neighbourhood size is a measure created for the purpose of indexing word co-occurrence where only one word is directly available to the researcher (Suárez et al., 2011; Yap \& Balota, 2009).
+
+\hypertarget{statistical-power-analysis-7}{%
+\subsubsection{Statistical power analysis}\label{statistical-power-analysis-7}}
+
+We analysed the statistical power associated with several effects of interest, across various sample sizes.
+The results of this power analysis can help determine the number of participants required to reliably examine each of these effects in a future study.
+Importantly, the results assume two conditions.
+First, the future study would apply a statistical method similar to ours---namely, a mixed-effects model with random intercepts and slopes.
+Second, the analysis of the future study would encompass at least 12,636 stimulus words (distributed in various blocks across participants, not all being presented to every participant).
+
+The results revealed that detecting the main effect of word frequency would require 100 participants. In contrast, detecting the other effects would require more than 2,000 participants.
+
+\hypertarget{general-discussion-of-study-2}{%
+\section{General discussion of Study 2}\label{general-discussion-of-study-2}}
+
+In the present study, we have revisited three existing data sets in conceptual processing to investigate the interplay between language-based and vision-based information.
+Specifically, we have investigated how this interplay is modulated by individual differences in vocabulary size, by the linguistic and visual information contained in words, and by contextual demands such as semantic depth and presentation speed.
+Although both language and vision played significant roles in some contexts (detailed below), the main effects and the interactions of language-based information were larger than those of vision-based information, consistent with previous research (Banks et al., 2021; Kiela \& Bottou, 2014; Lam et al., 2015; Louwerse et al., 2015; Pecher et al., 1998; Petilli et al., 2021).
+Whereas we focussed on the visual domain to investigate sensorimotor simulation, future research could consider other domains (Bernabeu et al., 2021).
+
+Important covariates such as word concreteness and individual differences in general cognition were controlled for in these analyses, and the models had a maximal random-effects structure providing for a conservative analysis.
+These methodological features are not trivial.
+First, the maximal random-effects structure served to impede a violation of the independence of observations.
+Specifically, random intercepts and slopes ensured that sources of dependence such as participants and stimuli were kept outside of the fixed effects, which are the relevant ones for the conclusions of this research.
+Second, the covariates are important because research has suggested that some correlated variables represent fundamentally different processes.
+For instance, word concreteness and visual strength are highly correlated.
+However, whereas visual strength indexes a perceptual component of semantic information, word concreteness might be circumscribed to the lexical level (Bottini et al., 2021), in contrast to other descriptions (Connell \& Lynott, 2012; Pexman \& Yap, 2018).
+Similarly, it was important to control for general cognition measures as covariates of vocabulary size (Ratcliff et al., 2010; also see James et al., 2018; Pexman \& Yap, 2018).
 
@@
 This converges with previous findings suggesting that higher and lower-vocabulary participants are affected by different variables.
-Potentially, the variables affecting higher-vocabulary participants are more relevant to the task (Lim et al., 2020; Pexman \& Yap, 2018; Yap et al., 2012, 2017).
-
-\hypertarget{differences-between-measurement-instruments-and-the-associated-risks}{%
-\subsection{Differences between measurement instruments and the associated risks}\label{differences-between-measurement-instruments-and-the-associated-risks}}
-
-We also compared two measures of visual priming.
-The first measure was operationalised as the difference in visual strength (Lynott et al., 2020) between the prime and the target word in each trial.
-The second measure, created by (Petilli et al., 2021), was based on vector representations trained on images.
-The results revealed that the visual strength measure was significantly superior in explaining RTs.
-This difference was not due to an excessive collinearity between these measures (\(r\) = .02).
-Also importantly, both measures appeared to be valid based on their correlations with language-based similarity and with word concreteness.
-
-If we indeed accept that both the above measures were valid, we must reflect on the possibility that measurement instruments create confounds when different systems are compared.
-That is, in the case of linguistic and embodied processing, the large difference between the effect sizes of these systems---found in the three current studies and in the previous literature {[}\ldots{]}---would not be trustworthy if the instruments that were used to measure the language system were far more precise than the instruments used to measure the embodiment system.
-In this sense, consider how variables are refined in research: it is done by comparing the performance of different variables.
-Critically, the literature seems to contain many comparisons of text-based variables, some dating from the 1990s (De Deyne et al., 2016, 2013; Günther et al., 2016a, 2016b; Jones et al., 2006; Lund \& Burgess, 1996; Mikolov et al., 2013; Wingfield \& Connell, 2022).
-In contrast, the work on embodiment variables began more than a decade afterwards, and this work has been more concerned with comparisons of different \emph{modalities}---e.g., valence, visual strength, auditory strength, etc.
-(Lynott et al., 2020; Lynott \& Connell, 2009; Newcombe et al., 2012).
-Thus, this historical accident could account for a portion of the superiority of linguistic information over embodied information (Banks et al., 2021; Kiela \& Bottou, 2014; as found in Lam et al., 2015; Louwerse et al., 2015; Pecher et al., 1998; Petilli et al., 2021).
-
-The case of different measurement instruments is one of several factors that can exert a great influence in analyses.
-In the medium term, it may pay dividends to devote more work to comparing different instruments and, more generally, different analyses (see Barsalou, 2019; Botvinik-Nezer et al., 2020; Wagenmakers et al., 2022).
+In this regard, some research has suggested that the variables affecting higher-vocabulary participants most are especially relevant to the task (Lim et al., 2020; Pexman \& Yap, 2018; Yap et al., 2012, 2017).
+Our results were consistent with the `task-relevance advantage' associated with greater vocabulary knowledge.
+Specifically, in lexical decision, higher-vocabulary participants were more sensitive than lower-vocabulary participants to language-based information.
+In contrast, in semantic decision, higher-vocabulary participants were more sensitive to word concreteness.
+In summary, the present findings suggest that greater linguistic experience may be associated with greater task adaptabiity during cognitive performance, with better comprehenders able to selectively attend to task-relevant features compared to poorer comprehenders (Lim et al., 2020; Pexman \& Yap, 2018).
+
+In addition, the semantic priming paradigm analysed in Study 1 revealed that both language and vision were more important with the short SOA (200 ms) than with the long SOA (1,200 ms).
+This finding replicates some of the previous literature (Petilli et al., 2021) while highlighting the importance of the time course and the level of semantic processing.
+That is, although the finding seems to be at odds with the theory that perceptual simulation peaks after language-based associations (Barsalou et al., 2008; Louwerse \& Connell, 2011), the long SOA may have been too long for perceptual simulation to be maintained in the lexical decision task that was performed by participants, which is semantically shallow {[}Petilli et al.
+(2021); see `Future directions' below{]}.
+
+\hypertarget{human-based-and-computational-measures-of-vision-based-information-1}{%
+\subsection{Human-based and computational measures of vision-based information}\label{human-based-and-computational-measures-of-vision-based-information-1}}
+
+We compared two measures of vision-based priming.
+The first measure---\texttt{visual-strength\ difference}---was operationalised as the difference in visual strength (Lynott et al., 2020) between the prime word and the target word in each trial.
+The second measure---\texttt{vision-based\ similarity}---, created by Petilli et al.
+(2021), was based on vector representations trained on images.
+The results revealed that both measures---including their interactions with other variables---produced similar effect sizes.
+This underscores the consistency that exists between human ratings and computational approximations to meaning (e.g., Charbonnier \& Wartena, 2019, 2020; Günther et al., 2016b; Louwerse et al., 2015; Mandera et al., 2017; Petilli et al., 2021; Solovyev, 2021; Wingfield \& Connell, 2022).
+Nonetheless, only the effect of the human-based variable was significant, and its effect size was slightly larger, which is consistent with previous comparisons of human-based and computational measures (De Deyne et al., 2016, 2019; Gagné et al., 2016; Schmidtke et al., 2018; cf.
+Michaelov et al., 2022; Snefjella \& Blank, 2020).
+
+Furthermore, the present comparison demonstrates the influence of measurement instruments on results, and their potential to act as confounds.
+Critically, the literature contains many comparisons of text-based variables (De Deyne et al., 2016, 2013; Günther et al., 2016a, 2016b; M.
+N.
+Jones et al., 2006; Lund \& Burgess, 1996; Mandera et al., 2017; Mikolov et al., 2013; Wingfield \& Connell, 2022), whereas the work on embodiment variables is more sparse and tends to compare different \emph{modalities}---e.g., valence, visual strength, auditory strength, etc.
+(Lynott et al., 2020; Lynott \& Connell, 2009; Newcombe et al., 2012; for an exception, see Vergallito et al., 2020).
+This accident of history might in part account for the superiority of linguistic information over embodied information (see Banks et al., 2021; Kiela \& Bottou, 2014; Lam et al., 2015; Louwerse et al., 2015; Pecher et al., 1998; Petilli et al., 2021).
+Therefore, it will be important to consider whether \emph{engineering work} should be devoted to the betterment of embodiment variables.
 
@@
 
-Power analyses were performed to \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_.
-\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_.
-The sample sizes required for some of the effects are not easily feasible with the usual distribution of funding in psychological research projects.
+Power analyses were performed to estimate the sample sizes required to reliably investigate a range of effects.
+The results suggested that 300 participants were sufficient to examine the effect of language-based information contained in words, whereas more than 1,000 participants were necessary for the effect of vision-based information and for the interactions of both former variables with vocabulary size, gender and presentation speed.
+Regarding interactions specifically, The large sample sizes required to investigate some of the effects relevant to embodied cognition and individual differences are not easily attainable with the usual organisation of funding in Psychology and Neuroscience.
 
@@
 \url{https://doi.org/10.1037/0278-7393.23.5.1059}
+
+\leavevmode\vadjust pre{\hypertarget{ref-beilockSportsExperienceChanges2008}{}}%
+Beilock, S.
+L., Lyons, I.
+M., Mattarella-Micke, A., Nusbaum, H.
+C., \& Small, S.
+L.
+(2008).
+Sports experience changes the neural processing of action language.
+\emph{Proceedings of the National Academy of Sciences}, \emph{105}(36), 13269--13273.
+\url{https://doi.org/10.1073/pnas.0803424105}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bernabeuDutchModalityExclusivity2018}{}}%
+Bernabeu, P. (2018). \emph{Dutch modality exclusivity norms for 336 properties and 411 concepts}. {PsyArXiv}. \url{https://doi.org/10.31234/osf.io/s2c5h}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-bonnerReversalConcretenessEffect2009}{}}%
+Bonner, M.
+F., Vesely, L., Price, C., Anderson, C., Richmond, L., Farag, C., Avants, B., \& Grossman, M.
+(2009).
+Reversal of the concreteness effect in semantic dementia.
+\emph{Cognitive Neuropsychology}, \emph{26}(6), 568--579.
+\url{https://doi.org/10.1080/02643290903512305}
+
 \leavevmode\vadjust pre{\hypertarget{ref-borghiWordsSocialTools2019}{}}%
@@
 \url{https://doi.org/10.1016/j.plrev.2018.12.001}
+
+\leavevmode\vadjust pre{\hypertarget{ref-borghiAbstractConceptsExternal2022}{}}%
+Borghi, A.
+M., Shaki, S., \& Fischer, M.
+H.
+(2022).
+Abstract concepts: External influences, internal constraints, and methodological issues.
+\emph{Psychological Research}.
+\url{https://doi.org/10.1007/s00426-022-01698-4}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bottiniNatureSemanticPriming2016}{}}%
+Bottini, R., Bucur, M., \& Crepaldi, D.
+(2016).
+The nature of semantic priming by subliminal spatial words: {Embodied} or disembodied?
+\emph{Journal of Experimental Psychology: General}, \emph{145}(9), 1160--1176.
+\url{https://doi.org/10.1037/xge0000197}
 
@@
 \url{https://doi.org/10.1037/met0000159}
+
+\leavevmode\vadjust pre{\hypertarget{ref-brunelliereCooccurrenceFrequencyEvaluated2017}{}}%
+Brunellière, A., Perre, L., Tran, T., \& Bonnotte, I.
+(2017).
+Co-occurrence frequency evaluated with large language corpora boosts semantic priming effects.
+\emph{Quarterly Journal of Experimental Psychology}, \emph{70}(9), 1922--1934.
+\url{https://doi.org/10.1080/17470218.2016.1215479}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-calvo-merinoActionObservationAcquired2005}{}}%
+Calvo-Merino, B., Glaser, D.
+E., Grèzes, J., Passingham, R.
+E., \& Haggard, P.
+(2005).
+Action observation and acquired motor skills: {An} {FMRI} study with expert dancers.
+\emph{Cerebral Cortex}, \emph{15}(8), 1243--1249.
+\url{https://doi.org/10.1093/cercor/bhi007}
+
 \leavevmode\vadjust pre{\hypertarget{ref-cerniMotorExpertiseTyping2016}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-chenMandarinChineseModality2019}{}}%
+Chen, I.-H., Zhao, Q., Long, Y., Lu, Q., \& Huang, C.-R.
+(2019).
+Mandarin {Chinese} modality exclusivity norms.
+\emph{PLOS ONE}, \emph{14}(2), e0211336.
+\url{https://doi.org/10.1371/journal.pone.0211336}
+
 \leavevmode\vadjust pre{\hypertarget{ref-cohenCostDichotomization1983}{}}%
@@
 (2011).
-Modality switching in a property verification task: {An} erp study of what happens when candles flicker after high heels click.
-\emph{Frontiers in Psychology}, \emph{2}.
-\url{https://www.frontiersin.org/article/10.3389/fpsyg.2011.00010}
+Modality switching in a property verification task: {An} {ERP} study of what happens when candles flicker after high heels click.
+\emph{Frontiers in Psychology}, \emph{2}(10).
+\url{https://doi.org/10.3389/fpsyg.2011.00010}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-daidoneVocabularySizeKey2021}{}}%
+Daidone, D., \& Darcy, I.
+(2021).
+Vocabulary size is a key factor in predicting second language lexical encoding accuracy.
+\emph{Frontiers in Psychology}, \emph{12}, 688356.
+\url{https://doi.org/10.3389/fpsyg.2021.688356}
+
 \leavevmode\vadjust pre{\hypertarget{ref-davies2017a}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-davisBuildingSemanticMemory2021}{}}%
+Davis, C.
+P., \& Yee, E.
+(2021).
+Building semantic memory from embodied and distributional language experience.
+\emph{WIREs Cognitive Science}, \emph{12}(5), e1555.
+\url{https://doi.org/10.1002/wcs.1555}
+
 \leavevmode\vadjust pre{\hypertarget{ref-dedeyneVisualAffectiveMultimodal2021}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-dilolloDecouplingStimulusDuration2004}{}}%
-Di Lollo, V., Mühlenen, A.
-von, Enns, J.
-T., \& Bridgeman, B.
-(2004).
-Decoupling stimulus duration from brightness in metacontrast masking: {Data} and models.
-\emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{30}(4), 733--745.
-\url{https://doi.org/10.1037/0096-1523.30.4.733}
+\leavevmode\vadjust pre{\hypertarget{ref-delucaRedefiningBilingualismSpectrum2019}{}}%
+DeLuca, V., Rothman, J., Bialystok, E., \& Pliatsikas, C.
+(2019).
+Redefining bilingualism as a spectrum of experiences that differentially affects brain structure and function.
+\emph{Proceedings of the National Academy of Sciences}, \emph{116}(15), 7565--7574.
+\url{https://doi.org/10.1073/pnas.1811513116}
 
@@
 (2016).
-Processing english compounds: {Investigating} semantic transparency.
+Processing {English} compounds: {Investigating} semantic transparency.
 \emph{SKASE Journal of Theoretical Linguistics}, \emph{13}(2), 2--22.
@@
 (2014).
-Beyond power calculations: Assessing type s (sign) and type m (magnitude) errors.
+Beyond power calculations: Assessing type {S} (sign) and type {M} (magnitude) errors.
 \emph{Perspectives on Psychological Science}, \emph{9}(6), 641--651.
@@
 Predicting lexical priming effects from distributional semantic similarities: {A} replication with extension.
-\emph{Frontiers in Psychology}, \emph{7}.
+\emph{Frontiers in Psychology}, \emph{7}, 1646.
 \url{https://doi.org/10.3389/fpsyg.2016.01646}
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-henrich2010a}{}}%
-Henrich, J., Heine, S. J., \& Norenzayan, A. (2010). The weirdest people in the world? \emph{Behavioral and Brain Sciences}, \emph{33}(2-3), 61--135. \url{https://doi.org/10.1017/S0140525X0999152X}
+\leavevmode\vadjust pre{\hypertarget{ref-heymanReliabilityItemlevelSemantic2018}{}}%
+Heyman, T., Bruninx, A., Hutchison, K.
+A., \& Storms, G.
+(2018).
+The (un)reliability of item-level semantic priming effects.
+\emph{Behavior Research Methods}, \emph{50}(6), 2173--2183.
+\url{https://doi.org/10.3758/s13428-018-1040-9}
 
@@
 Hoenig, J. M., \& Heisey, D. M. (2001). The {Abuse} of {Power}. \emph{The American Statistician}, \emph{55}(1), 19--24. \url{https://doi.org/10.1198/000313001300339897}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hoffmanReverseConcretenessEffects2011}{}}%
+Hoffman, P., \& Lambon Ralph, M.
+A.
+(2011).
+Reverse concreteness effects are not a typical feature of semantic dementia: {Evidence} for the hub-and-spoke model of conceptual representation.
+\emph{Cerebral Cortex}, \emph{21}(9), 2103--2112.
+\url{https://doi.org/10.1093/cercor/bhq288}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-hutchisonAttentionalControlAsymmetric2014}{}}%
+Hutchison, K.
+A., Heap, S.
+J., Neely, J.
+H., \& Thomas, M.
+A.
+(2014).
+Attentional control and asymmetric associative priming.
+\emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{40}(3), 844--856.
+\url{https://doi.org/10.1037/a0035781}
+
 \leavevmode\vadjust pre{\hypertarget{ref-james2018a}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-jaredSkilledAdultReaders2017}{}}%
+Jared, D., \& O'Donnell, K.
+(2017).
+Skilled adult readers activate the meanings of high-frequency words using phonology: {Evidence} from eye tracking.
+\emph{Memory \& Cognition}, \emph{45}(2), 334--346.
+\url{https://doi.org/10.3758/s13421-016-0661-4}
+
+\leavevmode\vadjust pre{\hypertarget{ref-jonesDistrubutionalSemanticsStill2022}{}}%
+Jones, C.
+R., Chang, T.
+A., Coulson, S., Michaelov, J.
+A., Trott, S., \& Bergen, B.
+(2022).
+Distrubutional semantics still can't account for affordances.
+\emph{Proceedings of the Annual Meeting of the Cognitive Science Society}, \emph{44}(44).
+\url{https://escholarship.org/uc/item/44z7r3j3}
+
 \leavevmode\vadjust pre{\hypertarget{ref-jones2006a}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-khatin-zadehStrongVersionsEmbodied2021}{}}%
+Khatin-Zadeh, O., Eskandari, Z., Cervera-Torres, S., Ruiz Fernández, S., Farzi, R., \& Marmolejo-Ramos, F.
+(2021).
+The strong versions of embodied cognition: {Three} challenges faced.
+\emph{Psychology \& Neuroscience}, \emph{14}(1), 16--33.
+\url{https://doi.org/10.1037/pne0000252}
+
 \leavevmode\vadjust pre{\hypertarget{ref-kieferDifferentialTemporospatialPattern2022}{}}%
@@
 (2012).
-Individual {Variation} in the {Late Positive Complex} to {Semantic Anomalies}.
-\emph{Frontiers in Psychology}, \emph{3}.
-\url{https://www.frontiersin.org/article/10.3389/fpsyg.2012.00318}
+Individual variation in the late positive complex to semantic anomalies.
+\emph{Frontiers in Psychology}, \emph{3}(318).
+\url{https://doi.org/10.3389/fpsyg.2012.00318}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-lercheDiffusionModelingIntelligence2020}{}}%
+Lerche, V., von Krause, M., Voss, A., Frischkorn, G.
+T., Schubert, A.-L., \& Hagemann, D.
+(2020).
+Diffusion modeling and intelligence: {Drift} rates show both domain-general and domain-specific relations with intelligence.
+\emph{Journal of Experimental Psychology: General}, \emph{149}(12), 2207--2249.
+\url{https://doi.org/10.1037/xge0000774}
+
 \leavevmode\vadjust pre{\hypertarget{ref-lewandowskiGeneratingRandomCorrelation2009}{}}%
@@
 (2020).
-Individual differences in cantonese chinese word recognition: {Insights} from the chinese lexicon project.
+Individual differences in {Cantonese Chinese} word recognition: {Insights} from the {Chinese Lexicon Project}.
 \emph{Quarterly Journal of Experimental Psychology}, \emph{73}(4), 504--518.
@@
 To transform or not to transform: Using generalized linear mixed models to analyse reaction time data.
-\emph{Frontiers in Psychology}, \emph{6}.
+\emph{Frontiers in Psychology}, \emph{6}, 1171.
 \url{https://doi.org/10.3389/fpsyg.2015.01171}
@@
 Loken, E., \& Gelman, A. (2017). Measurement error and the replication crisis. \emph{Science}, \emph{355}(6325), 584--585. \url{https://doi.org/10.1126/science.aal3618}
-
-\leavevmode\vadjust pre{\hypertarget{ref-louwerseSymbolInterdependencySymbolic2011}{}}%
-Louwerse, M.
-M.
-(2011).
-Symbol {Interdependency} in {Symbolic} and {Embodied Cognition}.
-\emph{Topics in Cognitive Science}, \emph{3}(2), 273--302.
-\url{https://doi.org/10.1111/j.1756-8765.2010.01106.x}
 
@@
 \url{https://doi.org/10.1111/j.1551-6709.2010.01157.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-louwerseNeurologicalEvidenceLinguistic2012}{}}%
+Louwerse, M.
+M., \& Hutchinson, S.
+(2012).
+Neurological evidence linguistic processes precede perceptual simulation in conceptual processing.
+\emph{Frontiers in Psychology}, \emph{3}, 385.
+\url{https://doi.org/10.3389/fpsyg.2012.00385}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-miceliPerceptualInteroceptiveStrength2021}{}}%
+Miceli, A., Wauthia, E., Lefebvre, L., Ris, L., \& Simoes Loureiro, I.
+(2021).
+Perceptual and interoceptive strength norms for 270 french words.
+\emph{Frontiers in Psychology}, \emph{12}.
+\url{https://www.frontiersin.org/article/10.3389/fpsyg.2021.667271}
+
 \leavevmode\vadjust pre{\hypertarget{ref-miceliDifferencesRelatedAging2022}{}}%
@@
 \url{https://doi.org/10.1016/j.archger.2022.104715}
+
+\leavevmode\vadjust pre{\hypertarget{ref-michaelovClozeFarN4002022}{}}%
+Michaelov, J.
+A., Coulson, S., \& Bergen, B.
+K.
+(2022).
+So cloze yet so far: {N400} amplitude is better predicted by distributional information than human predictability judgements.
+\emph{IEEE Transactions on Cognitive and Developmental Systems}, 1--1.
+\url{https://doi.org/10.1109/TCDS.2022.3176783}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-morucciAugmentedModalityExclusivity2019}{}}%
+Morucci, P., Bottini, R., \& Crepaldi, D.
+(2019).
+Augmented modality exclusivity norms for concrete and abstract {Italian} property words.
+\emph{Journal of Cognition}, \emph{2}(1), 42.
+\url{https://doi.org/10.5334/joc.88}
+
+\leavevmode\vadjust pre{\hypertarget{ref-murakiSimulatingSemanticsAre2021}{}}%
+Muraki, E.
+J., \& Pexman, P.
+M.
+(2021).
+Simulating semantics: {Are} individual differences in motor imagery related to sensorimotor effects in language processing?
+\emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{47}(12), 1939--1957.
+\url{https://doi.org/10.1037/xlm0001039}
+
 \leavevmode\vadjust pre{\hypertarget{ref-nakagawaCoefficientDeterminationR22017}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-nelsonUniversitySouthFlorida2004}{}}%
+Nelson, D.
+L., McEvoy, C.
+L., \& Schreiber, T.
+A.
+(2004).
+The {University} of {South Florida} free association, rhyme, and word fragment norms.
+\emph{Behavior Research Methods, Instruments, \& Computers}, \emph{36}(3), 402--407.
+\url{https://doi.org/10.3758/BF03195588}
+
 \leavevmode\vadjust pre{\hypertarget{ref-newcombeEffectsEmotionalSensorimotor2012}{}}%
@@
 Effects of emotional and sensorimotor knowledge in semantic processing of concrete and abstract nouns.
-\emph{Frontiers in Human Neuroscience}, \emph{6}.
-\url{https://www.frontiersin.org/article/10.3389/fnhum.2012.00275}
+\emph{Frontiers in Human Neuroscience}, \emph{6}(275).
+\url{https://doi.org/10.3389/fnhum.2012.00275}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-planchueloNatureWordAssociations2022}{}}%
+Planchuelo, C., Buades-Sitjar, F., Hinojosa, J.
+A., \& Duñabeitia, J.
+A.
+(2022).
+The nature of word associations in sentence contexts.
+\emph{Experimental Psychology}.
+\url{https://doi.org/10.1027/1618-3169/a000547}
+
+\leavevmode\vadjust pre{\hypertarget{ref-plautIndividualDevelopmentalDifferences2000}{}}%
+Plaut, D.
+C., \& Booth, J.
+R.
+(2000).
+Individual and developmental differences in semantic priming: {Empirical} and computational support for a single-mechanism account of lexical processing.
+\emph{Psychological Review}, \emph{107}(4), 786--823.
+\url{https://doi.org/10.1037/0033-295X.107.4.786}
+
 \leavevmode\vadjust pre{\hypertarget{ref-ponari2018a}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-rajanandaRandomdotKinematogramWebbased2018}{}}%
-Rajananda, S., Lau, H., \& Odegaard, B.
-(2018).
-A random-dot kinematogram for web-based vision research.
-\emph{Journal of Open Research Software}, \emph{6}(1, 1), 6.
-\url{https://doi.org/10.5334/jors.194}
-
 \leavevmode\vadjust pre{\hypertarget{ref-ratcliff2010a}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-roadsLearningUnsupervisedAlignment2020}{}}%
+Roads, B.
+D., \& Love, B.
+C.
+(2020).
+Learning as the unsupervised alignment of conceptual systems.
+\emph{Nature Machine Intelligence}, \emph{2}(1, 1), 76--82.
+\url{https://doi.org/10.1038/s42256-019-0132-2}
+
 \leavevmode\vadjust pre{\hypertarget{ref-rodriguez-ferreiroSemanticPrimingSchizotypal2020}{}}%
@@
 \url{https://doi.org/10.7717/peerj.9511}
+
+\leavevmode\vadjust pre{\hypertarget{ref-roqueVisionVerbsDominate2015}{}}%
+Roque, L.
+S., Kendrick, K.
+H., Norcliffe, E., Brown, P., Defina, R., Dingemanse, M., Dirksmeyer, T., Enfield, N.
+J., Floyd, S., Hammond, J., Rossi, G., Tufvesson, S., Putten, S.
+van, \& Majid, A.
+(2015).
+Vision verbs dominate in conversation across cultures, but the ranking of non-visual verbs varies.
+\emph{Cognitive Linguistics}, \emph{26}(1), 31--60.
+\url{https://doi.org/10.1515/cog-2014-0089}
 
@@
 \url{https://doi.org/10.1007/BF00309710}
+
+\leavevmode\vadjust pre{\hypertarget{ref-simmonsFMRIEvidenceWord2008}{}}%
+Simmons, W.
+K., Hamann, S.
+B., Harenski, C.
+L., Hu, X.
+P., \& Barsalou, L.
+W.
+(2008).
+{fMRI} evidence for word association and situated simulation in conceptual processing.
+\emph{Journal of Physiology-Paris}, \emph{102}(1), 106--119.
+\url{https://doi.org/10.1016/j.jphysparis.2008.03.014}
 
@@
 \url{https://doi.org/10.1007/978-3-030-71637-0_33}
+
+\leavevmode\vadjust pre{\hypertarget{ref-speedDutchSensoryModality2021}{}}%
+Speed, L. J., \& Brybaert, M. (2021). Dutch sensory modality norms. \emph{Behavior Research Methods}. \url{https://doi.org/10.3758/s13428-021-01656-9}
+
+\leavevmode\vadjust pre{\hypertarget{ref-speedGroundingLanguageNeglected2020}{}}%
+Speed, L.
+J., \& Majid, A.
+(2020).
+Grounding language in the neglected senses of touch, taste, and smell.
+\emph{Cognitive Neuropsychology}, \emph{37}(5-6), 363--392.
+\url{https://doi.org/10.1080/02643294.2019.1623188}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-tiokhinCompetitionPriorityHarms2021}{}}%
+Tiokhin, L., Yan, M., \& Morgan, T.
+J.
+H.
+(2021).
+Competition for priority harms the reliability of science, but reforms can help.
+\emph{Nature Human Behaviour}, \emph{5}(7, 7), 857--867.
+\url{https://doi.org/10.1038/s41562-020-01040-1}
+
 \leavevmode\vadjust pre{\hypertarget{ref-trocheDefiningConceptualTopography2017}{}}%
@@
 (2017).
-Defining a conceptual topography of word concreteness: {Clustering} properties of emotion, sensation, and magnitude among 750 english words.
+Defining a conceptual topography of word concreteness: {Clustering} properties of emotion, sensation, and magnitude among 750 {English} words.
 \emph{Frontiers in Psychology}, \emph{8}, 1787.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-vanravenzwaaijOptimalDecisionMaking2012}{}}%
+van Ravenzwaaij, D., van der Maas, H.
+L.
+J., \& Wagenmakers, E.-J.
+(2012).
+Optimal decision making in neural inhibition models.
+\emph{Psychological Review}, \emph{119}(1), 201--215.
+\url{https://doi.org/10.1037/a0026275}
+
 \leavevmode\vadjust pre{\hypertarget{ref-vanravenzwaaijAdvantagesMasqueradingIssues2021}{}}%
@@
 \url{https://doi.org/10.1214/20-BA1221}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vergallitoPerceptualModalityNorms2020}{}}%
+Vergallito, A., Petilli, M.
+A., \& Marelli, M.
+(2020).
+Perceptual modality norms for 1,121 {Italian} words: {A} comparison with concreteness and imageability scores and an analysis of their impact in word processing tasks.
+\emph{Behavior Research Methods}, \emph{52}(4), 1599--1616.
+\url{https://doi.org/10.3758/s13428-019-01337-8}
 
@@
 \url{https://doi.org/10.1093/cercor/bht025}
+
+\leavevmode\vadjust pre{\hypertarget{ref-viglioccoTheorySemanticRepresentation2009}{}}%
+Vigliocco, G., Meteyard, L., Andrews, M., \& Kousta, S. (2009). \emph{Toward a theory of semantic representation}. \emph{1}(2), 219--247. \url{https://doi.org/10.1515/LANGCOG.2009.011}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-wangSocialEmotionDimensional2021}{}}%
+Wang, X., Li, G., Zhao, G., Li, Y., Wang, B., Lin, C.-P., Liu, X., \& Bi, Y.
+(2021).
+Social and emotion dimensional organizations in the abstract semantic space: The neuropsychological evidence.
+\emph{Scientific Reports}, \emph{11}(1, 1), 23572.
+\url{https://doi.org/10.1038/s41598-021-02824-9}
+
 \leavevmode\vadjust pre{\hypertarget{ref-williamsImprovingPsychologicalScience2014}{}}%
@@
 Woodcock, R. W., McGrew, K. S., \& Mather, N. (2001). \emph{Woodcock {Johnson III} tests of cognitive abilities}. {Riverside Publishing}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-yapVisualWordRecognition2009}{}}%
+Yap, M. J., \& Balota, D. A. (2009). Visual word recognition of multisyllabic words. \emph{Journal of Memory and Language}, \emph{60}(4), 502--529. \url{https://doi.org/10.1016/j.jml.2009.02.001}
 
@@
 Yarkoni, T., Balota, D., \& Yap, M.
+J.
 (2008).
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-zhongSensorimotorNormsChinese2022}{}}%
+Zhong, Y., Wan, M., Ahrens, K., \& Huang, C.-R.
+(2022).
+Sensorimotor norms for {Chinese} nouns and their relationship with orthographic and semantic variables.
+\emph{Language, Cognition and Neuroscience}, \emph{0}(0), 1--23.
+\url{https://doi.org/10.1080/23273798.2022.2035416}
+
+\leavevmode\vadjust pre{\hypertarget{ref-zwaanReplicationsShouldBe2014}{}}%
+Zwaan, R.
+A.
+(2014).
+Replications should be performed with power and precision: {A} response to {Rommers}, {Meyer}, and {Huettig} (2013).
+\emph{Psychological Science}, \emph{25}(1), 305--307.
+\url{https://doi.org/10.1177/0956797613509634}
+
 \end{CSLReferences}
@@
 
-Lexical covariates are usually used in conceptual processing studies due to the widespread connections among lexical and semantic variables.
+Lexical covariates are usually used in conceptual processing studies due to the widespread connections among lexical and semantic variables (Petilli et al., 2021; e.g., Pexman \& Yap, 2018; Wingfield \& Connell, 2022).
 Including these covariates---or nuisance variables---in the model allows a more rigorous analysis of the predictors of interest (Sassenhagen \& Alday, 2016).
-
-In each study, the covariates were selected out of a group of 5 variables that had been used as covariates in Wingfield and Connell (2022), and are widely used (e.g., Petilli et al., 2021).
+In each of the present studies, the covariates were selected out of a group of five variables that had been used as covariates in Wingfield and Connell (2022), and are widely used (e.g., Petilli et al., 2021).
 Some of these covariates were highly intercorrelated (\(r\) \textgreater{} .70), as shown below.
@@
 
-In Studies 1 (semantic priming) and 2 (semantic decision), the lexical covariates were selected out of five variables, which mirrored those used by Wingfield and Connell (2022): namely, number of letters (i.e., orthographic length, which we computed in R), word frequency, number of syllables (both the latter from Balota et al., 2007), orthographic Levenshtein distance (Yarkoni et al., 2008) and phonological Levenshtein distance (Suárez et al., 2011).
-In Study 3 (lexical decision), the procedure was identical except that word frequency could not be selected as a covariate because it constituted a predictor of interest, specifically corresponding to linguistic information (for details, see Study 3 in the main article).
+In Studies 1 (semantic priming) and 2 (semantic decision), the lexical covariates were selected out of five variables, which mirrored those used by Wingfield and Connell (2022): namely, number of letters (i.e., orthographic length, which we computed in R), word frequency, number of syllables (both the latter from Balota et al., 2007), orthographic Levenshtein distance (Yarkoni et al., 2008) and phonological Levenshtein distance (Suárez et al., 2011; Yap \& Balota, 2009).
+In Study 3 (lexical decision), the procedure was more particular, as it served two purposes.
+First, the variable that had the largest effect out of the five was selected as the language-based predictor of interest (see reason in \protect\hyperlink{lexicaldecision}{\underline{Study 3 in the main text}}).
+Second, one variable was selected as a covariate among the remaining four.
 
@@
 
-\begin{table}[H]
+\begin{table}[!h]
 
@@
 \item \textit{Note}.
-$\upbeta$ = Estimate based on $z$-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CI = confidence interval.
+$\upbeta$ = Estimate based on $z$-scored predictors; \textit{SE} = standard error; \linebreak \phantom{.}CI = confidence interval.
 By-participant random slopes were included for \linebreak \phantom{.}every effect.
@@
 
-\hypertarget{study-3-lexical-decision-1}{%
-\subsection{Study 3: Lexical decision}\label{study-3-lexical-decision-1}}
+\hypertarget{study-3-lexical-decision}{%
+\subsection{Study 3: Lexical decision}\label{study-3-lexical-decision}}
+
+The selection model for Study 3 served a twofold purpose.
+First, the variable that had the largest effect out of the five was selected as the language-based predictor of interest (see reason in \protect\hyperlink{lexicaldecision}{\underline{Study 3 in the main text}}).
+Second, one variable was selected as a covariate among the remaining four.
 
@@
 
-\hypertarget{the-multiple-optimizers-sanity-check-from-lme4allfit}{%
-\subsubsection{\texorpdfstring{The multiple-optimizers sanity check from \texttt{lme4::allFit()}}{The multiple-optimizers sanity check from lme4::allFit()}}\label{the-multiple-optimizers-sanity-check-from-lme4allfit}}
-
-Framed within the drive to maintain random slopes wherever possible, the developers of the `lme4' package propose a sanity check that uses a part of the `lme4' \emph{engine} called `optimizer'.
-Every model has a default optimizer, unless a specific one is chosen through \texttt{control\ =\ lmerControl(optimizer\ =\ \textquotesingle{}...\textquotesingle{})} (in \texttt{lmer} models) or \texttt{control\ =\ glmerControl(optimizer\ =\ \textquotesingle{}...\textquotesingle{})} (in \texttt{glmer} models).
-The 7 widely-available optimizers are:
+\hypertarget{the-multiple-optimisers-sanity-check-from-lme4allfit}{%
+\subsubsection{\texorpdfstring{The multiple-optimisers sanity check from \texttt{lme4::allFit()}}{The multiple-optimisers sanity check from lme4::allFit()}}\label{the-multiple-optimisers-sanity-check-from-lme4allfit}}
+
+Framed within the drive to maintain random slopes wherever possible, the developers of the `lme4' package propose a sanity check that uses a part of the `lme4' \emph{engine} called `optimiser'.
+Every model has a default optimiser, unless a specific one is chosen through \texttt{control\ =\ lmerControl(optimiser\ =\ \textquotesingle{}...\textquotesingle{})} (in \texttt{lmer} models) or \texttt{control\ =\ glmerControl(optimiser\ =\ \textquotesingle{}...\textquotesingle{})} (in \texttt{glmer} models).
+The seven widely-available optimisers are:
 
@@
 To assess whether convergence warnings render the results invalid, or on the contrary, the results can be deemed valid in spite of the warnings, Bates et al.
-(2021) suggest refitting models affected by convergence warnings with a variety of optimizers.
-The authors argue that if the different optimizers produce practically-equivalent results, the results are valid.
-For this purpose, the `allFit' function from the `lme4' package allows the refitting of models using a number of optimizers.
-To use the 7 optimizers listed above, two extra packages were installed: `dfoptim' and `optimx' (see \href{https://cran.r-project.org/web/packages/lme4/lme4.pdf}{lme4 manual}).
-The output from `allFit' contains several statistics on the fixed and the random effects fitted by each optimizer (see \href{https://github.com/lme4/lme4/issues/512\#issue-425198940}{example}).
+(2021) suggest refitting models affected by convergence warnings with a variety of optimisers.
+The authors argue that if the different optimisers produce practically-equivalent results, the results are valid.
+For this purpose, the `allFit' function from the `lme4' package allows the refitting of models using a number of optimisers.
+To use the seven optimisers listed above, two extra packages were installed: `dfoptim' and `optimx' (see \href{https://cran.r-project.org/web/packages/lme4/lme4.pdf}{lme4 manual}).
+The output from `allFit' contains several statistics on the fixed and the random effects fitted by each optimiser (see \href{https://github.com/lme4/lme4/issues/512\#issue-425198940}{example}).
 
@@
 
-The residuals of the linear mixed-effects models in all three studies violated the assumption of normality.
+The residuals of the linear mixed-effects models in the three studies violated the assumption of normality.
 Even though linear mixed-effects models tend to be quite robust to deviations from normality (Knief \& Forstmeier, 2021; Schielzeth et al., 2020), we sought to verify our results.
@@
 
-In the initial model, the optimizer used (the default one in `lmerTest') was `nloptwrap', and the convergence warning read: `boundary (singular) fit: see ?isSingular'.
-
-Based on the reanalysis using 7 optimizers, Figure \ref{fig:main-effects-semanticpriming-allFit-convergence} shows the fixed, main effects, and Figure \ref{fig:interactions-semanticpriming-allFit-convergence} shows the fixed interactions.
+In the initial model, the optimiser used (the default one in `lmerTest') was '`, and the convergence warning read: 'boundary (singular) fit: see ?isSingular'.
+
+Based on the reanalysis using seven optimisers, Figure \ref{fig:main-effects-semanticpriming-allFit-convergence} shows the fixed, main effects, and Figure \ref{fig:interactions-semanticpriming-allFit-convergence} shows the fixed interactions.
 
@@
 
-\caption{Fixed, main effects from the semantic priming study fitted by 7 optimizers.}\label{fig:main-effects-semanticpriming-allFit-convergence}
+\caption{Fixed, main effects from the semantic priming study fitted by seven optimisers.}\label{fig:main-effects-semanticpriming-allFit-convergence}
 \end{figure}
@@
 
-\caption{Fixed interaction effects from the semantic priming study fitted by 7 optimizers.}\label{fig:interactions-semanticpriming-allFit-convergence}
+\caption{Fixed interaction effects from the semantic priming study fitted by seven optimisers.}\label{fig:interactions-semanticpriming-allFit-convergence}
 \end{figure}
@@
 
-In the initial model, the optimizer used (the default one in `lmerTest') was `nloptwrap', and the convergence warning read: `boundary (singular) fit: see ?isSingular'.
-
-Based on the reanalysis using 7 optimizers, Figure \ref{fig:main-effects-semanticpriming-with-visualsimilarity-allFit-convergence} shows the fixed, main effects, and Figure \ref{fig:interactions-semanticpriming-with-visualsimilarity-allFit-convergence} shows the fixed interactions.
+In the initial model, the optimiser used (the default one in `lmerTest') was '`, and the convergence warning read: 'boundary (singular) fit: see ?isSingular'.
+
+Based on the reanalysis using seven optimisers, Figure \ref{fig:main-effects-semanticpriming-with-visualsimilarity-allFit-convergence} shows the fixed, main effects, and Figure \ref{fig:interactions-semanticpriming-with-visualsimilarity-allFit-convergence} shows the fixed interactions.
 
@@
 
-\caption{Fixed, main effects from the semantic priming study fitted by 7 optimizers.}\label{fig:main-effects-semanticpriming-with-visualsimilarity-allFit-convergence}
+\caption{Fixed, main effects from the semantic priming study fitted by seven optimisers.}\label{fig:main-effects-semanticpriming-with-visualsimilarity-allFit-convergence}
 \end{figure}
@@
 
-\caption{Fixed interaction effects from the semantic priming study fitted by 7 optimizers.}\label{fig:interactions-semanticpriming-with-visualsimilarity-allFit-convergence}
+\caption{Fixed interaction effects from the semantic priming study fitted by seven optimisers.}\label{fig:interactions-semanticpriming-with-visualsimilarity-allFit-convergence}
 \end{figure}
@@
 
-In the initial model, the optimizer used (the default one in `lmerTest') was `nloptwrap', and the convergence warning read: `boundary (singular) fit: see ?isSingular'.
-
-Based on the reanalysis using 7 optimizers, Figure \ref{fig:main-effects-semanticdecision-allFit-convergence} shows the fixed, main effects, and Figure \ref{fig:interactions-semanticdecision-allFit-convergence} shows the fixed interactions.
+In the initial model, the optimiser used (the default one in `lmerTest') was '`, and the convergence warning read: 'boundary (singular) fit: see ?isSingular'.
+
+Based on the reanalysis using seven optimisers, Figure \ref{fig:main-effects-semanticdecision-allFit-convergence} shows the fixed, main effects, and Figure \ref{fig:interactions-semanticdecision-allFit-convergence} shows the fixed interactions.
 
@@
 
-\caption{Fixed, main effects from the semantic decision study fitted by 7 optimizers.}\label{fig:main-effects-semanticdecision-allFit-convergence}
+\caption{Fixed, main effects from the semantic decision study fitted by seven optimisers.}\label{fig:main-effects-semanticdecision-allFit-convergence}
 \end{figure}
@@
 
-\caption{Fixed interaction effects from the semantic decision study fitted by 7 optimizers.}\label{fig:interactions-semanticdecision-allFit-convergence}
+\caption{Fixed interaction effects from the semantic decision study fitted by seven optimisers.}\label{fig:interactions-semanticdecision-allFit-convergence}
 \end{figure}
@@
 
-\hypertarget{study-3-lexical-decision-2}{%
-\subsection{Study 3: Lexical decision}\label{study-3-lexical-decision-2}}
+\hypertarget{study-3-lexical-decision-1}{%
+\subsection{Study 3: Lexical decision}\label{study-3-lexical-decision-1}}
 
@@
 
-In the initial model, the optimizer used (the default one in `lmerTest') was `nloptwrap', and the convergence warning read: `boundary (singular) fit: see ?isSingular'.
-
-Based on the reanalysis using 7 optimizers, Figure \ref{fig:main-effects-lexicaldecision-allFit-convergence} shows the fixed, main effects, and Figure \ref{fig:interactions-lexicaldecision-allFit-convergence} shows the fixed interactions.
+In the initial model, the optimiser used (the default one in `lmerTest') was '`, and the convergence warning read: 'boundary (singular) fit: see ?isSingular'.
+
+Based on the reanalysis using seven optimisers, Figure \ref{fig:main-effects-lexicaldecision-allFit-convergence} shows the fixed, main effects, and Figure \ref{fig:interactions-lexicaldecision-allFit-convergence} shows the fixed interactions.
 
@@
 
-\caption{Fixed, main effects from the lexical decision study fitted by 7 optimizers.}\label{fig:main-effects-lexicaldecision-allFit-convergence}
+\caption{Fixed, main effects from the lexical decision study fitted by seven optimisers.}\label{fig:main-effects-lexicaldecision-allFit-convergence}
 \end{figure}
@@
 
-\caption{Fixed interaction effects from the lexical decision study fitted by 7 optimizers.}\label{fig:interactions-lexicaldecision-allFit-convergence}
+\caption{Fixed interaction effects from the lexical decision study fitted by seven optimisers.}\label{fig:interactions-lexicaldecision-allFit-convergence}
 \end{figure}
@@
 In each study, prior predictive checks are presented before posterior predictive checks.
-Furthermore, in each of these checks, the models presented first have the default Gaussian distribution, whereas the next series have an exponentially modified Gaussian (dubbed `ex-Gaussian') distribution with an identity link function (for details, see the section titled `Distributions and prior predictive checks' in the main article).
+Furthermore, in each of these checks, the models presented first have the default Gaussian distribution, whereas the next series have an exponentially modified Gaussian (dubbed `ex-Gaussian') distribution with an identity link function (for details, see the section titled `Distributions and prior predictive checks' in the main text).
 Eyeball estimation is used to assess the outcomes of these checks (for background on predictive checks and for alternative estimation procedures, see Gelman et al., 1996; Moran et al., 2021; Schoot et al., 2021).
@@
 The way of interpreting these plots is by comparing the observed data to the predicted distribution.
-The specifics of this vary across the three plots in the series.
-Firstly, in the upper plot, which shows the maximum values, the ideal scenario would have the observed (\(y\)) value overlapping with the maximum value of the predicted distribution (\(y_{rep}\)).
-Secondly, in the middle plot, showing the mean values, the ideal scenario would show the observed (\(y\)) value overlapping with the mean value of the predicted distribution (\(y_{rep}\)).
-Lastly, in the lower plot, which shows the minimum values, the ideal scenario would have the observed (\(y\)) value overlapping with the minimum value of the predicted distribution (\(y_{rep}\)).
-The overlap need not be absolute but the closer the observed and the predicted values on the X axis, the better.
+The specifics of this comparison vary across the three plots.
+First, in the upper plot, which shows the maximum values, the ideal scenario would show the observed maximum value (\(y\)) overlapping with the maximum value of the predicted distribution (\(y_{rep}\)).
+Second, in the middle plot, showing the mean values, the ideal scenario would show the observed mean value (\(y\)) overlapping with the mean value of the predicted distribution (\(y_{rep}\)).
+Last, in the lower plot, which shows the minimum values, the ideal scenario would have the observed minimum value (\(y\)) overlapping with the minimum value of the predicted distribution (\(y_{rep}\)).
+While the overlap need not be absolute, the closer the observed and the predicted values are on the X axis, the better.
 As such, the three predictive checks below---corresponding to models that used the default Gaussian distribution---show that the priors fitted the data acceptably but not very well.
@@
 Based on the above results, the ex-Gaussian distribution was used in the final models.
-Figure \ref{fig:semanticpriming-posteriorpredictivechecks-allpriors-exgaussian} presents the posterior predictive checks the latter models.
+Figure \ref{fig:semanticpriming-posteriorpredictivechecks-allpriors-exgaussian} presents the posterior predictive checks for the latter models.
 The interpretation of these plots is simple: the distributions of the observed (\(y\)) and the predicted data (\(y_{rep}\)) should be as similar as possible.
@@
 \caption{Posterior predictive checks for the (ex-Gaussian) models from the semantic priming study.
-\(y\) = observed data; \(y_{rep}\) = predicted data.}\label{fig:semanticpriming-posteriorpredictivechecks-allpriors-exgaussian}
+The observed data (\(y\)) and the predicted data (\(y_{rep}\)) almost entirely overlap with each other, demonstrating a very good fit.}\label{fig:semanticpriming-posteriorpredictivechecks-allpriors-exgaussian}
 \end{figure}
@@
 
-Figures \ref{fig:semanticdecision-priorpredictivecheck-informativepriors}, \ref{fig:semanticdecision-priorpredictivecheck-weaklyinformativepriors} and \ref{fig:semanticdecision-priorpredictivecheck-diffusepriors} show the prior predictive checks for the Gaussian models (for background on these checks, see \protect\hyperlink{study1-bayesian-diagnostics}{\underline{Study 1 above}}).
+Figures \ref{fig:semanticdecision-priorpredictivecheck-informativepriors}, \ref{fig:semanticdecision-priorpredictivecheck-weaklyinformativepriors} and \ref{fig:semanticdecision-priorpredictivecheck-diffusepriors} show the prior predictive checks for the Gaussian models (for background on these checks, see \protect\hyperlink{study1-bayesian-diagnostics}{\underline{Study 1}}).
 The three plots---corresponding to models that used the default Gaussian distribution---show that the priors fitted the data acceptably but not very well.
@@
 
-\hypertarget{study-3-lexical-decision-3}{%
-\subsection{Study 3: Lexical decision}\label{study-3-lexical-decision-3}}
+\hypertarget{study-3-lexical-decision-2}{%
+\subsection{Study 3: Lexical decision}\label{study-3-lexical-decision-2}}
 
@@
 
-Figures \ref{fig:lexicaldecision-priorpredictivecheck-informativepriors}, \ref{fig:lexicaldecision-priorpredictivecheck-weaklyinformativepriors} and \ref{fig:lexicaldecision-priorpredictivecheck-diffusepriors} show the prior predictive checks for the Gaussian models (for background on these checks, see \protect\hyperlink{study1-bayesian-diagnostics}{\underline{Study 1 above}}).
+Figures \ref{fig:lexicaldecision-priorpredictivecheck-informativepriors}, \ref{fig:lexicaldecision-priorpredictivecheck-weaklyinformativepriors} and \ref{fig:lexicaldecision-priorpredictivecheck-diffusepriors} show the prior predictive checks for the Gaussian models (for background on these checks, see \protect\hyperlink{study1-bayesian-diagnostics}{\underline{Study 1}}).
 The three plots---corresponding to models that used the default Gaussian distribution---show that the priors fitted the data acceptably but not very well.
@@
 
-This appendix presents plots of interactions that were not shown in the main text.
+Figures \ref{fig:semanticpriming-interactions-with-attentional-control} -- \ref{fig:lexicaldecision-interaction-word-concreteness-gender} present interactions that were not displayed in the main article.
+All interaction plots are based on the frequentist analysis.
 
@@
 
-\caption{Interactions of attentional control with language-based similarity and visual-strength difference.
-Attentional control is constrained to deciles (ten sections) in this plot, whereas in the statistical analysis it contained more values within the current range.
-\emph{n} = number of participants contained between decile values.}\label{fig:semanticpriming-interactions-with-attentional-control}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.65\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interaction-word-concreteness-difference-SOA}
-
-}
-
-\caption{Interaction of stimulus-onset asynchrony (SOA) with word-concreteness difference.
-SOA was analysed using $z$-scores, but for clarity, the variable is shown in its basic form here.}\label{fig:semanticpriming-interaction-word-concreteness-difference-SOA}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.85\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interaction-word-concreteness-difference-vocabulary-size}
-
-}
-
-\caption{Interaction of word-concreteness difference with vocabulary size.
+\caption{Interactions of attentional control with language-based similarity (panel a) and with visual-strength difference (panel b).
+Attentional control is constrained to deciles (10 sections) in this plot, whereas in the statistical analysis it contained more values within the current range.
+\(n\) = number of participants contained between deciles.}\label{fig:semanticpriming-interactions-with-attentional-control}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.7\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interaction-word-concreteness-difference-SOA}
+
+}
+
+\caption{Interaction between stimulus onset asynchrony (SOA) and word-concreteness difference.
+SOA was analysed using $z$-scores, but for clarity, the basic labels are used in the legend.}\label{fig:semanticpriming-interaction-word-concreteness-difference-SOA}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.9\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interaction-word-concreteness-difference-vocabulary-size}
+
+}
+
+\caption{Interaction between word-concreteness difference and vocabulary size.
 Vocabulary size is constrained to deciles in this plot, whereas in the statistical analysis it contained more values within the current range.
-\emph{n} = number of participants contained between decile values.}\label{fig:semanticpriming-interaction-word-concreteness-difference-vocabulary-size}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.65\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interaction-word-concreteness-difference-gender}
-
-}
-
-\caption{Interaction of word-concreteness difference with gender.
-Gender was analysed using \(z\)-scores, but for clarity, the variable is shown in its basic form here.
-\emph{n} = number of participants contained between decile values.}\label{fig:semanticpriming-interaction-word-concreteness-difference-gender}
+\(n\) = number of participants contained between deciles.}\label{fig:semanticpriming-interaction-word-concreteness-difference-vocabulary-size}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.7\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interaction-word-concreteness-difference-gender}
+
+}
+
+\caption{Interaction between word-concreteness difference and gender.
+Gender was analysed using \(z\)-scores, but for clarity, the basic labels are used in the legend.
+\(n\) = number of participants contained between deciles.}\label{fig:semanticpriming-interaction-word-concreteness-difference-gender}
 \end{figure}
@@
 
-{\centering \includegraphics[width=0.9\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/plots/semanticdecision-interactions-with-information-uptake}
-
-}
-
-\caption{Interactions of information uptake with language-based similarity and visual-strength difference.
+{\centering \includegraphics[width=0.95\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/plots/semanticdecision-interactions-with-information-uptake}
+
+}
+
+\caption{Interactions of information uptake with word co-occurrence (panel a) and with visual strength (panel b).
 Information uptake is constrained to deciles in this plot, whereas in the statistical analysis it contained more values within the current range.
-\emph{n} = number of participants contained between decile values.}\label{fig:semanticdecision-interactions-with-information-uptake}
+\(n\) = number of participants contained between deciles.}\label{fig:semanticdecision-interactions-with-information-uptake}
 \end{figure}
@@
 
-\hypertarget{study-3-lexical-decision-4}{%
-\subsection{Study 3: Lexical decision}\label{study-3-lexical-decision-4}}
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.85\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/plots/lexicaldecision-interaction-word-concreteness-vocabulary-age}
-
-}
-
-\caption{Interaction of word concreteness with vocabulary age.
-Vocabulary age is constrained to sextiles (six sections) in this plot, whereas in the statistical analysis it contained more values within the current range.
-\emph{n} = number of participants contained between sextile values.}\label{fig:lexicaldecision-interaction-word-concreteness-vocabulary-age}
+\hypertarget{study-3-lexical-decision-3}{%
+\subsection{Study 3: Lexical decision}\label{study-3-lexical-decision-3}}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.9\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/plots/lexicaldecision-interaction-word-concreteness-vocabulary-age}
+
+}
+
+\caption{Interaction between word concreteness and vocabulary age.
+Vocabulary age is constrained to sextiles (6 sections) in this plot, whereas in the statistical analysis it contained more values within the current range.
+\(n\) = number of participants contained between sextiles.}\label{fig:lexicaldecision-interaction-word-concreteness-vocabulary-age}
 \end{figure}
@@
 
-\caption{Interaction of word concreteness with gender.
-Gender was analysed using \(z\)-scores, but for clarity, the variable is shown in its basic form here.
-\emph{n} = number of participants contained between sextile values.}\label{fig:lexicaldecision-interaction-word-concreteness-gender}
+\caption{Interaction between word concreteness and gender.
+Gender was analysed using \(z\)-scores, but for clarity, the basic labels are used in the legend.
+\(n\) = number of participants contained between sextiles.}\label{fig:lexicaldecision-interaction-word-concreteness-gender}
 \end{figure}
@@
 For each study, three tables are presented that contain the results from the informative prior model (\(SD\) = 0.1), the weakly-informative prior model (\(SD\) = 0.2) and the diffuse prior model (\(SD\) = 0.3).
-All models had an exponentially modified Gaussian (dubbed `ex-Gaussian') distribution with an identity link function (for background, see main article and \protect\hyperlink{appendix-C-Bayesian-analysis-diagnostics}{\underline{Appendix C}}).
+All models had an exponentially modified Gaussian (dubbed `ex-Gaussian') distribution with an identity link function (for background, see main text and \protect\hyperlink{appendix-C-Bayesian-analysis-diagnostics}{\underline{Appendix C}}).
 The \(\widehat R\) value is a convergence diagnostic that should ideally be smaller than 1.01 (Vehtari et al., 2021).
@@
 
-Table \ref{tab:semanticpriming-informativepriors-model} presents the results of the informative prior model, and Table \ref{tab:semanticpriming-diffusepriors-model} presents those of the diffuse prior model (further to this, the weakly-informative prior model will be added when it finishes running).
-
-\begin{table}[H]
+Table \ref{tab:semanticpriming-informativepriors-model} presents the results of the informative prior model, Table \ref{tab:semanticpriming-weaklyinformativepriors-model} those of the weakly-informative prior model, and Table \ref{tab:semanticpriming-diffusepriors-model} those of the diffuse prior model.
+
+\begin{table}[!h]
 
@@
 \addlinespace[0.3em]
-\multicolumn{5}{l}{\textbf{Prime-target semantic relationship}}\\
+\multicolumn{5}{l}{\textbf{Prime--target relationship}}\\
 \cellcolor{gray!6}{\hspace{1em}Word-concreteness difference} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.00, 0.01]} & \cellcolor{gray!6}{1.00}\\
@@
 \multicolumn{5}{l}{\textbf{Task condition}}\\
-\hspace{1em}Stimulus-onset asynchrony (SOA) $^{\text{b}}$ & 0.03 & 0.01 & {}[0.02, 0.04] & 1.00\\
+\hspace{1em}Stimulus onset asynchrony (SOA) $^{\text{b}}$ & 0.03 & 0.01 & {}[0.02, 0.04] & 1.00\\
 \addlinespace[0.3em]
@@
 \item \textit{Note}.
-$\upbeta$ = Estimate based on $z$-scored variables; \textit{SE} = standard error; \linebreak \phantom{.}CrI = credible interval.
+$\upbeta$ = Estimate based on $z$-scored predictors; \textit{SE} = standard error; \linebreak \phantom{.}CrI = credible interval.
 Shaded rows contain covariates.
@@
 
-\begin{table}[H]
-
-\caption{\label{tab:semanticpriming-diffusepriors-model}Diffuse prior model for the semantic priming study.}
+\begin{table}[!h]
+
+\caption{\label{tab:semanticpriming-weaklyinformativepriors-model}Weakly-informative prior model for the semantic priming study.}
 \centering
@@
 
+\begin{table}[!h]
+
+\caption{\label{tab:semanticpriming-diffusepriors-model}Diffuse prior model for the semantic priming study.}
+\centering
+\begin{threeparttable}
+\begin{tabular}[t]{lrrrr}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{1}{c}{$\upbeta$} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{95\% CrI} & \multicolumn{1}{c}{$\widehat R$}\\
+\midrule
+(Intercept) & 0.00 & 0.00 & {}[0.00, 0.01] & 1.00\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textbf{Individual differences}}\\
+\cellcolor{gray!6}{\hspace{1em}Attentional control} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.00, 0.01]} & \cellcolor{gray!6}{1.00}\\
+\hspace{1em}Vocabulary size $^{\text{a}}$ & -0.01 & 0.00 & {}[-0.01, 0.00] & 1.00\\
+\hspace{1em}Gender $^{\text{a}}$ & 0.00 & 0.00 & {}[0.00, 0.01] & 1.00\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textbf{Target-word lexical covariates}}\\
+\cellcolor{gray!6}{\hspace{1em}Word frequency} & \cellcolor{gray!6}{-0.11} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[-0.12, -0.11]} & \cellcolor{gray!6}{1.00}\\
+\cellcolor{gray!6}{\hspace{1em}Number of syllables} & \cellcolor{gray!6}{0.07} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.06, 0.07]} & \cellcolor{gray!6}{1.00}\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textbf{Prime--target relationship}}\\
+\cellcolor{gray!6}{\hspace{1em}Word-concreteness difference} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.00, 0.01]} & \cellcolor{gray!6}{1.00}\\
+\hspace{1em}Language-based similarity $^{\text{b}}$ & -0.06 & 0.00 & {}[-0.07, -0.06] & 1.00\\
+\hspace{1em}Visual-strength difference $^{\text{b}}$ & 0.01 & 0.00 & {}[0.01, 0.01] & 1.00\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textbf{Task condition}}\\
+\hspace{1em}Stimulus onset asynchrony (SOA) $^{\text{b}}$ & 0.03 & 0.01 & {}[0.02, 0.04] & 1.00\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textbf{Interactions}}\\
+\cellcolor{gray!6}{\hspace{1em}\makecell[l]{Word-concreteness difference  $\times$ \\ \hspace{0.3cm} Vocabulary size}} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.00, 0.00]} & \cellcolor{gray!6}{1.00}\\
+\cellcolor{gray!6}{\hspace{1em}Word-concreteness difference  $\times$  SOA} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.00, 0.00]} & \cellcolor{gray!6}{1.00}\\
+\cellcolor{gray!6}{\hspace{1em}Word-concreteness difference  $\times$  Gender} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.00, 0.00]} & \cellcolor{gray!6}{1.00}\\
+\cellcolor{gray!6}{\hspace{1em}\makecell[l]{Language-based similarity  $\times$ \\ \hspace{0.3cm} Attentional control}} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[-0.01, 0.00]} & \cellcolor{gray!6}{1.00}\\
+\cellcolor{gray!6}{\hspace{1em}\makecell[l]{Visual-strength difference  $\times$ \\ \hspace{0.3cm} Attentional control}} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{{}[0.00, 0.00]} & \cellcolor{gray!6}{1.00}\\
+\hspace{1em}\makecell[l]{Language-based similarity  $\times$ \\ \hspace{0.3cm} Vocabulary size} & 0.00 & 0.00 & {}[-0.01, 0.00] & 1.00\\
+\hspace{1em}\makecell[l]{Visual-strength difference  $\times$ \\ \hspace{0.3cm} Vocabulary size} & 0.00 & 0.00 & {}[0.00, 0.00] & 1.00\\
+\hspace{1em}Language-based similarity  $\times$  Gender & 0.00 & 0.00 & {}[-0.01, 0.00] & 1.00\\
+\hspace{1em}Visual-strength difference  $\times$  Gender & 0.00 & 0.00 & {}[0.00, 0.00] & 1.00\\
+\hspace{1em}Language-based similarity  $\times$  SOA $^{\text{b}}$ & 0.00 & 0.00 & {}[0.00, 0.00] & 1.00\\
+\hspace{1em}Visual-strength difference  $\times$  SOA $^{\text{b}}$ & 0.00 & 0.00 & {}[0.00, 0.00] & 1.00\\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\item \textit{\linebreak} 
+\item \textit{Note}.
+$\upbeta$ = Estimate based on $z$-scored predictors; \textit{SE} = standard error; \linebreak \phantom{.}CrI = credible interval.
+Shaded rows contain covariates.
+Some interactions \linebreak \phantom{.}are split over two lines, with the second line indented.
+\linebreak \linebreak \phantom{.}$^{\text{a}}$ By-word random slopes were included for this effect.
+\linebreak \phantom{.}$^{\text{b}}$ By-participant random slopes were included for this effect.
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+\clearpage
+
 Figure \ref{fig:semanticpriming-frequentist-bayesian-plot-allpriors-exgaussian} presents the posterior distribution of each effect in each model.
@@
 The frequentist means (represented by points) are flanked by 95\% confidence intervals.
-The Bayesian means (represented by vertical lines) are flanked by 95\% credible intervals, in light blue (in some cases, the interval is covered up by the bar of the mean).}\label{fig:semanticpriming-frequentist-bayesian-plot-allpriors-exgaussian}
-\end{figure}
+The Bayesian means (represented by vertical lines) are flanked by 95\% credible intervals in light blue (in some cases, the interval is occluded by the bar of the mean).}\label{fig:semanticpriming-frequentist-bayesian-plot-allpriors-exgaussian}
+\end{figure}
+
+\clearpage
 
@@
 
-Table \ref{tab:semanticdecision-informativepriors-model} presents the results of the informative prior model, Table \ref{tab:semanticdecision-weaklyinformativepriors-model} presents those of the weakly-informative prior model and Table \ref{tab:semanticdecision-diffusepriors-model} presents those of the diffuse prior model.
-
-\begin{table}[H]
+Table \ref{tab:semanticdecision-informativepriors-model} presents the results of the informative prior model, Table \ref{tab:semanticdecision-weaklyinformativepriors-model} those of the weakly-informative prior model, and Table \ref{tab:semanticdecision-diffusepriors-model} those of the diffuse prior model.
+
+\begin{table}[!h]
 
@@
 \addlinespace[0.3em]
-\multicolumn{5}{l}{\textbf{Lexical covariates}}\\
+\multicolumn{5}{l}{\textbf{Lexicosemantic covariates}}\\
 \cellcolor{gray!6}{\hspace{1em}Word frequency} & \cellcolor{gray!6}{-0.18} & \cellcolor{gray!6}{0.31} & \cellcolor{gray!6}{{}[-1.34, -0.07]} & \cellcolor{gray!6}{1.30}\\
 \cellcolor{gray!6}{\hspace{1em}Orthographic Levenshtein distance} & \cellcolor{gray!6}{0.06} & \cellcolor{gray!6}{0.56} & \cellcolor{gray!6}{{}[-1.14, 1.94]} & \cellcolor{gray!6}{1.41}\\
+\cellcolor{gray!6}{\hspace{1em}Word concreteness} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.26} & \cellcolor{gray!6}{{}[-0.08, 1.01]} & \cellcolor{gray!6}{1.30}\\
 \addlinespace[0.3em]
 \multicolumn{5}{l}{\textbf{Semantic variables}}\\
-\cellcolor{gray!6}{\hspace{1em}Word concreteness} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.26} & \cellcolor{gray!6}{{}[-0.08, 1.01]} & \cellcolor{gray!6}{1.30}\\
 \hspace{1em}Word co-occurrence $^{\text{b}}$ & -0.05 & 0.23 & {}[-0.87, 0.40] & 1.41\\
@@
 \addlinespace[0.3em]
-\multicolumn{5}{l}{\textbf{Lexical covariates}}\\
+\multicolumn{5}{l}{\textbf{Lexicosemantic covariates}}\\
 \cellcolor{gray!6}{\hspace{1em}Word frequency} & \cellcolor{gray!6}{-0.18} & \cellcolor{gray!6}{0.31} & \cellcolor{gray!6}{{}[-1.34, -0.07]} & \cellcolor{gray!6}{1.31}\\
 \cellcolor{gray!6}{\hspace{1em}Orthographic Levenshtein distance} & \cellcolor{gray!6}{0.06} & \cellcolor{gray!6}{0.56} & \cellcolor{gray!6}{{}[-1.14, 1.94]} & \cellcolor{gray!6}{1.40}\\
+\cellcolor{gray!6}{\hspace{1em}Word concreteness} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.26} & \cellcolor{gray!6}{{}[-0.08, 1.01]} & \cellcolor{gray!6}{1.30}\\
 \addlinespace[0.3em]
 \multicolumn{5}{l}{\textbf{Semantic variables}}\\
-\cellcolor{gray!6}{\hspace{1em}Word concreteness} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.26} & \cellcolor{gray!6}{{}[-0.08, 1.01]} & \cellcolor{gray!6}{1.30}\\
 \hspace{1em}Word co-occurrence $^{\text{b}}$ & -0.05 & 0.23 & {}[-0.87, 0.40] & 1.41\\
@@
 
+\clearpage
+
 Figure \ref{fig:semanticdecision-frequentist-bayesian-plot-allpriors-exgaussian} presents the posterior distribution of each effect in each model.
@@
 The frequentist means (represented by points) are flanked by 95\% confidence intervals.
-The Bayesian means (represented by vertical lines) are flanked by 95\% credible intervals, in light blue (in some cases, the interval is covered up by the bar of the mean).}\label{fig:semanticdecision-frequentist-bayesian-plot-allpriors-exgaussian}
-\end{figure}
-
-\hypertarget{study-3-lexical-decision-5}{%
-\subsection{Study 3: Lexical decision}\label{study-3-lexical-decision-5}}
-
-Table \ref{tab:lexicaldecision-informativepriors-model} presents the results of the informative prior model, Table \ref{tab:lexicaldecision-weaklyinformativepriors-model} presents those of the weakly-informative prior model and Table \ref{tab:lexicaldecision-diffusepriors-model} presents those of the diffuse prior model.
-
-\begin{table}[H]
+The Bayesian means (represented by vertical lines) are flanked by 95\% credible intervals in light blue (in some cases, the interval is occluded by the bar of the mean).}\label{fig:semanticdecision-frequentist-bayesian-plot-allpriors-exgaussian}
+\end{figure}
+
+\clearpage
+
+\hypertarget{study-3-lexical-decision-4}{%
+\subsection{Study 3: Lexical decision}\label{study-3-lexical-decision-4}}
+
+Table \ref{tab:lexicaldecision-informativepriors-model} presents the results of the informative prior model, Table \ref{tab:lexicaldecision-weaklyinformativepriors-model} those of the weakly-informative prior model, and Table \ref{tab:lexicaldecision-diffusepriors-model} those of the diffuse prior model.
+
+\begin{table}[!h]
 
@@
 \addlinespace[0.3em]
-\multicolumn{5}{l}{\textbf{Lexical covariate}}\\
+\multicolumn{5}{l}{\textbf{Lexicosemantic covariates}}\\
 \cellcolor{gray!6}{\hspace{1em}Orthographic Levenshtein distance $^{\text{b}}$} & \cellcolor{gray!6}{0.15} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[0.13, 0.17]} & \cellcolor{gray!6}{1.00}\\
+\cellcolor{gray!6}{\hspace{1em}Word concreteness $^{\text{b}}$} & \cellcolor{gray!6}{-0.03} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[-0.05, -0.02]} & \cellcolor{gray!6}{1.00}\\
 \addlinespace[0.3em]
 \multicolumn{5}{l}{\textbf{Semantic variables}}\\
-\cellcolor{gray!6}{\hspace{1em}Word concreteness $^{\text{b}}$} & \cellcolor{gray!6}{-0.03} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{{}[-0.05, -0.02]} & \cellcolor{gray!6}{1.00}\\
 \hspace{1em}Word frequency $^{\text{b}}$ & -0.14 & 0.01 & {}[-0.16, -0.12] & 1.00\\
@@
 
+\clearpage
+
 Figure \ref{fig:lexicaldecision-frequentist-bayesian-plot-allpriors-exgaussian} presents the posterior distribution of each effect in each model.
@@
 The frequentist means (represented by points) are flanked by 95\% confidence intervals.
-The Bayesian means (represented by vertical lines) are flanked by 95\% credible intervals, in light blue (in some cases, the interval is covered up by the bar of the mean).}\label{fig:lexicaldecision-frequentist-bayesian-plot-allpriors-exgaussian}
+The Bayesian means (represented by vertical lines) are flanked by 95\% credible intervals in light blue (in some cases, the interval is occluded by the bar of the mean).}\label{fig:lexicaldecision-frequentist-bayesian-plot-allpriors-exgaussian}
 \end{figure}

### 2022-09-26 R_functions/plot.fixef.allFit.R

@@ -1,6 +1,6 @@
 
 
-# Plot the results from the fixed effects produced by different optimizers. This function 
+# Plot the results from the fixed effects produced by different optimisers. This function 
 # takes the output from lme4::allFit(), tidies it, selects fixed effects and plots them.
 
 plot.fixef.allFit = function(allFit_output, 
@@ -19,8 +19,8 @@ plot.fixef.allFit = function(allFit_output,
                              y_title = 'Fixed effect',
                              # Alignment of the Y axis title
                              y_title_hjust = NULL,
-                             # Add number to the names of optimizers
-                             number_optimizers = TRUE,
+                             # Add number to the names of optimisers
+                             number_optimisers = TRUE,
                              # Replace colon in interactions with x
                              interaction_symbol_x = TRUE) {
   
@@ -39,11 +39,11 @@ plot.fixef.allFit = function(allFit_output,
   # Extract fixed effects from the allFit() output
   allFit_fixef = summary(allFit_output)$fixef %>%  # Select fixed effects in the allFit results
     reshape2::melt() %>%  # Structure the output as a data frame
-    rename('Optimizer' = 'Var1', 'fixed_effect' = 'Var2')  # set informative names
+    rename('Optimiser' = 'Var1', 'fixed_effect' = 'Var2')  # set informative names
   
-  # If number_optimizers = TRUE, assign number to each optimizer and place it before its name
-  if(number_optimizers == TRUE) {
-    allFit_fixef$Optimizer = paste0(as.numeric(allFit_fixef$Optimizer), '. ', allFit_fixef$Optimizer)
+  # If number_optimisers = TRUE, assign number to each optimiser and place it before its name
+  if(number_optimisers == TRUE) {
+    allFit_fixef$Optimiser = paste0(as.numeric(allFit_fixef$Optimiser), '. ', allFit_fixef$Optimiser)
   }
   
   # If select_predictors were supplied, select them along with the intercept (the latter required)
@@ -52,7 +52,7 @@ plot.fixef.allFit = function(allFit_output,
   }
   
   # Order variables
-  allFit_fixef = allFit_fixef[, c('Optimizer', 'fixed_effect', 'value')]
+  allFit_fixef = allFit_fixef[, c('Optimiser', 'fixed_effect', 'value')]
   
[…]

### 2022-09-26 bayesian_priors/bayesian_priors.R

@@ -196,7 +196,7 @@ fill_colours = c('#CCCBE7', '#D7D7D7', '#E7CBCB')
     facet_wrap(vars(informativeness), scales = 'free', dir = 'v') +
     # Vertical line at x = 0
     geom_vline(xintercept = 0, linetype = 'dashed', color = 'grey50') +
-    xlab('Estimate (*z*)') + 
+    xlab('Effect size (&beta;)') + 
     ylab('Direction of the prior and corresponding distribution') +
     theme_minimal() +
     theme(axis.title.x = ggtext::element_markdown(size = 12, margin = margin(t = 9)),

### 2022-09-26 lexicaldecision/frequentist_analysis/model_diagnostics/lexicaldecision_allFit_convergence.R

@@ -5,16 +5,16 @@
 # Convergence diagnostics
 
 # Following Brauer and Curtin (2018), avoid removing random slopes to prevent an inflation of the Type I error rate.
-# As a sanity check, refit mixed-effects model with several optimizers. This check is done by comparing the results 
-# from these optimizers. If they are similar, especially for the fixed effects, then the results are likely valid,
+# As a sanity check, refit mixed-effects model with several optimisers. This check is done by comparing the results 
+# from these optimisers. If they are similar, especially for the fixed effects, then the results are likely valid,
 # even in the presence of convergence warnings (see https://cran.r-project.org/web/packages/lme4/lme4.pdf).
 
 
 library(tidyverse)  # Data wrangling, text processing and plotting
-library(dfoptim)  # Refit model with various optimizers using lme4::allFit()
-library(optimx)  # Refit model with various optimizers using lme4::allFit()
+library(dfoptim)  # Refit model with various optimisers using lme4::allFit()
+library(optimx)  # Refit model with various optimisers using lme4::allFit()
 library(lme4)   # Main analysis and adjustment of effect labels
-library(parallel)   # Allow parallel processing using several cores
+library(parallel)  # Allow parallel processing using several cores
 
 
 # Data set below created in the script 'lexicaldecision_data_preparation.R',
@@ -27,7 +27,7 @@ lexicaldecision =
 lexicaldecision_lmerTest = 
   readRDS('lexicaldecision/frequentist_analysis/results/lexicaldecision_lmerTest.rds')
 
-# Fit model using the seven available optimizers
+# Fit model using the seven available optimisers
 lexicaldecision_allFit_convergence =
   allFit(lexicaldecision_lmerTest, 
          # Set maximum iterations to 1m to facilitate convergence 
@@ -47,7 +47,7 @@ saveRDS(lexicaldecision_allFit_convergence,
 ################################################################################
 
 
-# PLOT fixed effects from all the optimizers
+# PLOT fixed effects from all the optimisers
 
 # Adjust the names of the predictors in two ways, as detailed below
 labels = colnames(lexicaldecision_allFit_convergence[[1]]@pp$X) %>% 
@@ -74,7 +74,7 @@ labels = colnames(lexicaldecision_allFit_convergence[[1]]@pp$X) %>%
   # order does not affect the results in any way.
   sub("(\\w+.*):(Word frequency|Visual strength)", '\\2:\\1', .)
 
[…]

### 2022-09-26 semanticdecision/frequentist_analysis/semanticdecision-interactions-with-information-uptake.R

@@ -71,5 +71,5 @@ plot3 =
     plot_annotation(tag_levels = list(c('(a)', '(b)', '(c)'))) + 
     guide_area() + plot_layout(ncol = 2, guides = 'collect') ) %>%
   ggsave(filename = 'semanticdecision/frequentist_analysis/plots/semanticdecision-interactions-with-information-uptake.pdf',
-         device = cairo_pdf, width = 6, height = 7, dpi = 900)
+         device = cairo_pdf, width = 7.5, height = 7, dpi = 900)
 

### 2022-09-26 semanticdecision/frequentist_bayesian_plots/semanticdecision_frequentist_bayesian_plots.R

@@ -95,7 +95,7 @@ plot_semanticdecision_frequentist_bayesian_plot_informativepriors_exgaussian =
                             semanticdecision_posteriordistributions_informativepriors_exgaussian,
                             labels = new_labels, interaction_symbol_x = TRUE,
                             vertical_line_at_x = 0, x_title = 'Effect size (&beta;)', 
-                            note_frequentist_no_prior = TRUE) +
+                            x_axis_labels = 3, note_frequentist_no_prior = TRUE) +
   ggtitle('Prior *SD* = 0.1')
 
 #####
@@ -118,7 +118,7 @@ plot_semanticdecision_frequentist_bayesian_plot_weaklyinformativepriors_exgaussi
                             semanticdecision_posteriordistributions_weaklyinformativepriors_exgaussian,
                             labels = new_labels, interaction_symbol_x = TRUE,
                             vertical_line_at_x = 0, x_title = 'Effect size (&beta;)', 
-                            note_frequentist_no_prior = TRUE) +
+                            x_axis_labels = 3, note_frequentist_no_prior = TRUE) +
   ggtitle('Prior *SD* = 0.2') +
   theme(axis.text.y = element_blank())
 
@@ -130,7 +130,7 @@ plot_semanticdecision_frequentist_bayesian_plot_diffusepriors_exgaussian =
                             semanticdecision_posteriordistributions_diffusepriors_exgaussian,
                             labels = new_labels, interaction_symbol_x = TRUE,
                             vertical_line_at_x = 0, x_title = 'Effect size (&beta;)', 
-                            note_frequentist_no_prior = TRUE) +
+                            x_axis_labels = 3, note_frequentist_no_prior = TRUE) +
   ggtitle('Prior *SD* = 0.3') + 
   theme(axis.text.y = element_blank())
 

### 2022-09-26 semanticdecision/power_analysis/semanticdecision_all_powercurves.R

@@ -46,7 +46,7 @@ for(i in 1 : length(files_list)) {
     
     # First, adjust names of variables (both in main effects and in interactions)
     str_replace(pattern = 'z_word_cooccurrence',
-                replacement = "Distance to word \'abstract\'") %>%
+                replacement = 'Word co-occurrence') %>%
     str_replace(pattern = 'z_visual_rating',
                 replacement = 'Visual strength') %>%
     str_replace(pattern = 'z_vocabulary_size',
@@ -60,9 +60,7 @@ for(i in 1 : length(files_list)) {
     # code below moves those word-level variables (with their new names) to the 
     # first position in their interactions. Note that the order does not affect 
     # the results in any way.
-    sub("'(\\w+.*):(Distance to word \'abstract\'|Visual strength)'", 
-        '\\2:\\1', 
-        .)
+    sub("'(\\w+.*):(Word co-occurrence|Visual strength)'", '\\2:\\1', .)
 }
 
 # Furthermore, the 'powercurvePlot' function used below internally removes the 

### 2022-09-26 semanticpriming/analysis_with_visualsimilarity/model_diagnostics/semanticpriming_with_visualsimilarity_allFit_convergence.R

@@ -5,16 +5,16 @@
 # Convergence diagnostics
 
 # Following Brauer and Curtin (2018), avoid removing random slopes to prevent an inflation of the Type I error rate.
-# As a sanity check, refit mixed-effects model with several optimizers. This check is done by comparing the results 
-# from these optimizers. If they are similar, especially for the fixed effects, then the results are likely valid,
+# As a sanity check, refit mixed-effects model with several optimisers. This check is done by comparing the results 
+# from these optimisers. If they are similar, especially for the fixed effects, then the results are likely valid,
 # even in the presence of convergence warnings (see https://cran.r-project.org/web/packages/lme4/lme4.pdf).
 
 
 library(tidyverse)  # Data wrangling, text processing and plotting
-library(dfoptim)  # Refit model with various optimizers using lme4::allFit()
-library(optimx)  # Refit model with various optimizers using lme4::allFit()
+library(dfoptim)  # Refit model with various optimisers using lme4::allFit()
+library(optimx)  # Refit model with various optimisers using lme4::allFit()
 library(lme4)   # Main analysis and adjustment of effect labels
-library(parallel)   # Allow parallel processing using several cores
+library(parallel)  # Allow parallel processing using several cores
 
 
 # Data set below created in the script 'semanticpriming_with_visualsimilarity_data_preparation.R',
@@ -27,7 +27,7 @@ semanticpriming_with_visualsimilarity =
 semanticpriming_with_visualsimilarity_lmerTest = 
   readRDS('semanticpriming/analysis_with_visualsimilarity/results/semanticpriming_with_visualsimilarity_lmerTest.rds')
 
-# Fit model using the seven available optimizers
+# Fit model using the seven available optimisers
 semanticpriming_with_visualsimilarity_allFit_convergence =
   allFit(semanticpriming_with_visualsimilarity_lmerTest, 
          # Set maximum iterations to 1m to facilitate convergence 
@@ -36,18 +36,14 @@ semanticpriming_with_visualsimilarity_allFit_convergence =
          # Use 7 cores in parallel for faster computation
          ncpus = 7)
 
-# Save
-saveRDS(semanticpriming_with_visualsimilarity_allFit_convergence,
-        'semanticpriming/analysis_with_visualsimilarity/model_diagnostics/results/semanticpriming_with_visualsimilarity_allFit_convergence.rds')
-
-# Load the result back in, if needed later
[…]

### 2022-09-26 semanticpriming/bayesian_analysis/divergent_models/semanticpriming_brms_informativepriors_exgaussian.R

@@ -83,16 +83,31 @@ semanticpriming_brms_informativepriors_exgaussian =
       # Interactions only require random slopes if all variables involved vary within the same units.
       
       # By-participant random slopes
-      (z_cosine_similarity + z_visual_rating_diff +
-         z_recoded_interstimulus_interval + 
-         z_cosine_similarity : z_recoded_interstimulus_interval +
-         z_visual_rating_diff : z_recoded_interstimulus_interval +
-         z_target_word_frequency + z_target_number_syllables + 
-         z_word_concreteness_diff | Participant) +
+      
+      # Below, the random slopes for control covariates (i.e., 'z_target_word_frequency', 
+      # 'z_target_number_syllables' and 'z_word_concreteness_diff') were removed due to 
+      # non-convergence, inspired by Remedy 11 from Table 17 in Brauer and Curtin (2018). 
+      # However, whereas Brauer and Curtin constrained such a removal to cases in which the 
+      # covariate does not interact with any effects of interest, the random slopes for 
+      # 'z_word_concreteness_diff' were removed below because the interactions between this 
+      # covariate and the effects of interest were control covariates, not interactions 
+      # of interest. That is, they were not critical to the research question.
+    
+    (z_cosine_similarity + z_visual_rating_diff + z_recoded_interstimulus_interval + 
+       z_cosine_similarity : z_recoded_interstimulus_interval +
+       z_visual_rating_diff : z_recoded_interstimulus_interval | Participant) +
       
       # Random slopes by prime-target pair
-      (z_vocabulary_size + z_recoded_participant_gender +
-         z_attentional_control | primeword_targetword),
+      
+      # Below, the random slopes for the control covariate (i.e., 'z_attentional_control') 
+      # were removed due to non-convergence, inspired by Remedy 11 from Table 17 in Brauer 
+      # and Curtin (2018). However, whereas Brauer and Curtin constrained such a removal to 
+      # cases in which the covariate does not interact with any effects of interest, the 
+      # random slopes for 'z_attentional_control' were removed below because the interactions 
+      # between this covariate and the effects of interest were control covariates, not 
+      # interactions of interest. That is, they were not critical to the research question.
+      
+    (z_vocabulary_size + z_recoded_participant_gender | primeword_targetword),
     
     data = semanticpriming, prior = informative_priors,
     
[…]

### 2022-09-26 semanticpriming/bayesian_analysis/posterior_predictive_checks/semanticpriming_posteriorpredictivechecks.R

@@ -22,8 +22,8 @@ source('R_functions/plot_posteriorpredictivecheck.R')
 semanticpriming_posteriorpredictivecheck_informativepriors_exgaussian =
   readRDS('semanticpriming/bayesian_analysis/posterior_predictive_checks/results/semanticpriming_posteriorpredictivecheck_informativepriors_exgaussian.rds')
 
-# semanticpriming_posteriorpredictivecheck_weaklyinformativepriors_exgaussian =
-#   readRDS('semanticpriming/bayesian_analysis/posterior_predictive_checks/results/semanticpriming_posteriorpredictivecheck_weaklyinformativepriors_exgaussian.rds')
+semanticpriming_posteriorpredictivecheck_weaklyinformativepriors_exgaussian =
+  readRDS('semanticpriming/bayesian_analysis/posterior_predictive_checks/results/semanticpriming_posteriorpredictivecheck_weaklyinformativepriors_exgaussian.rds')
 
 semanticpriming_posteriorpredictivecheck_diffusepriors_exgaussian =
   readRDS('semanticpriming/bayesian_analysis/posterior_predictive_checks/results/semanticpriming_posteriorpredictivecheck_diffusepriors_exgaussian.rds')
@@ -50,19 +50,21 @@ semanticpriming_posteriorpredictivecheck_diffusepriors_exgaussian =
   plot_posteriorpredictivecheck() + 
   ggtitle('Prior *SD* = 0.3') + xlab('RT (*z*)') + 
   theme(axis.title.y = element_blank(), 
+        legend.position = c(.75, .7),
+        legend.text = element_text(size = 17), 
         plot.margin = margin(12, 0, 14, 12))
 
 
 # Combine plots
 
 ( semanticpriming_posteriorpredictivecheck_informativepriors_exgaussian +
-    # semanticpriming_posteriorpredictivecheck_weaklyinformativepriors_exgaussian +
+    semanticpriming_posteriorpredictivecheck_weaklyinformativepriors_exgaussian +
     semanticpriming_posteriorpredictivecheck_diffusepriors_exgaussian +
     # plot_annotation(tag_levels = list(c('(a)', '(b)', '(c)'))) + 
-    plot_layout(ncol = 2) ) %>%
+    plot_layout(ncol = 3) ) %>%
   
   # Save to disk
[…]

### 2022-09-26 semanticpriming/bayesian_analysis/semanticpriming_brms_diffusepriors_exgaussian.R

@@ -122,9 +122,9 @@ semanticpriming_brms_diffusepriors_exgaussian =
     family = exgaussian(),
     
     seed = 123,  # allow exact replication of results
-    warmup = 2000,  # warmup iterations
-    iter = 8000, chains = 16,  # (iter - warmup) x chains = total post-warmup draws (brms v2.17.0)
-    cores = 5,  # parallel computation
+    warmup = 1500,  # warmup iterations
+    iter = 9000, chains = 16,  # (iter - warmup) x chains = total post-warmup draws (brms v2.17.0)
+    cores = 16,  # parallel computation
     control = list(adapt_delta = 0.99, max_treedepth = 15)  # facilitate convergence
   )
 

### 2022-09-26 semanticpriming/bayesian_analysis/semanticpriming_brms_informativepriors_exgaussian.R

@@ -122,9 +122,9 @@ semanticpriming_brms_informativepriors_exgaussian =
     family = exgaussian(),
     
     seed = 123,  # allow exact replication of results
-    warmup = 2000,  # warmup iterations
-    iter = 8000, chains = 16,  # (iter - warmup) x chains = total post-warmup draws (brms v2.17.0)
-    cores = 5,  # parallel computation
+    warmup = 1500,  # warmup iterations
+    iter = 9000, chains = 16,  # (iter - warmup) x chains = total post-warmup draws (brms v2.17.0)
+    cores = 16,  # parallel computation
     control = list(adapt_delta = 0.99, max_treedepth = 15)  # facilitate convergence
   )
 

### 2022-09-26 semanticpriming/frequentist_analysis/semanticpriming-interactions-with-word-concreteness-difference.R

@@ -15,9 +15,9 @@ library(patchwork)
 semanticpriming = read.csv('semanticpriming/data/final_dataset/semanticpriming.csv')
 
 
-## Convert interstimulus interval to stimulus-onset asynchrony ##
+## Convert interstimulus interval to stimulus onset asynchrony ##
 
-# The stimulus-onset asynchrony (SOA) has an alternative formula called the 
+# The stimulus onset asynchrony (SOA) has an alternative formula called the 
 # 'interstimulus interval' (ISI). The difference between these is that the 
 # ISI does not count the presentation of the prime word (example 
 # equivalences between ISI and SOA are available ISI and SOA in Lam et al., 
@@ -74,7 +74,7 @@ source('R_functions/deciles_interaction_plot.R')
   x_title = 'Word-concreteness difference (*z*)',
   y_title = 'Predicted RT (*z*)',
   fill_title = 'SOA (ms)'
-) + theme(legend.position = c(.9, .15)) ) %>%
+) + theme(legend.position = c(.88, .17)) ) %>%
   # save to disk
   ggsave(filename = 'semanticpriming/frequentist_analysis/plots/semanticpriming-interaction-word-concreteness-difference-SOA.pdf',
          device = cairo_pdf, width = 5, height = 4.5, dpi = 900)

### 2022-09-26 semanticpriming/frequentist_bayesian_plots/semanticpriming_frequentist_bayesian_plots.R

@@ -33,8 +33,8 @@ rownames(confint_semanticpriming_lmerTest)
 semanticpriming_posteriordistributions_informativepriors_exgaussian = 
   readRDS('semanticpriming/bayesian_analysis/results/semanticpriming_posteriordistributions_informativepriors_exgaussian.rds')
 
-# semanticpriming_posteriordistributions_weaklyinformativepriors_exgaussian = 
-#   readRDS('semanticpriming/bayesian_analysis/results/semanticpriming_posteriordistributions_weaklyinformativepriors_exgaussian.rds')
+semanticpriming_posteriordistributions_weaklyinformativepriors_exgaussian =
+  readRDS('semanticpriming/bayesian_analysis/results/semanticpriming_posteriordistributions_weaklyinformativepriors_exgaussian.rds')
 
 semanticpriming_posteriordistributions_diffusepriors_exgaussian = 
   readRDS('semanticpriming/bayesian_analysis/results/semanticpriming_posteriordistributions_diffusepriors_exgaussian.rds')
@@ -96,7 +96,7 @@ new_labels =
               replacement = 'SOA') %>%
   # Show acronym in main effect of SOA
   str_replace(pattern = '^SOA$',
-              replacement = 'Stimulus-onset asynchrony (SOA)') %>%
+              replacement = 'Stimulus onset asynchrony (SOA)') %>%
   
   # Second, adjust order of effects in interactions. In the output from the model, 
   # the word-level variables of interest (i.e., 'z_cosine_similarity' and 
@@ -114,38 +114,38 @@ new_labels =
 
 # Create plots, beginning with the informative-prior model
 
-# Save single plot
-( frequentist_bayesian_plot(KR_summary_semanticpriming_lmerTest,
-                            confint_semanticpriming_lmerTest,
-                            semanticpriming_posteriordistributions_informativepriors_exgaussian,
-                            labels = new_labels, interaction_symbol_x = TRUE,
-                            vertical_line_at_x = 0, x_title = 'Effect size (&beta;)',
-                            legend_ncol = 1) + 
-    theme(legend.position = 'bottom') ) %>%
-  ggsave(filename = 'semanticpriming/frequentist_bayesian_plots/plots/semanticpriming_frequentist_bayesian_plot_informativepriors_exgaussian.pdf',
-         device = cairo_pdf, width = 6.5, height = 7.5, dpi = 900)
-
-# Plot adjusted to fit in the combination of all three plots
[…]

### 2022-09-26 semanticpriming/power_analysis/reduced_randomeffects_model/semanticpriming-interactions-with-gender.R

@@ -2,6 +2,9 @@
 
 # Part of Study 1: Semantic priming
 
+# Deprecated model. For details, please see README.md in the directory
+# 'semanticpriming/power_analysis/reduced_randomeffects_model'
+
 # Combination of plots:
 # 1. Interaction between gender and cosine similarity
 # 2. Interaction between gender and visual rating difference
@@ -80,6 +83,6 @@ plot2 =
 
 # Combine plots using {patchwork}
 (plot1 + plot2 + plot_layout(ncol = 1, guides = 'collect')) %>%
-  ggsave(filename = 'semanticpriming/power_analysis/model/plots/semanticpriming-interactions-with-gender.pdf',
+  ggsave(filename = 'semanticpriming/power_analysis/reduced_randomeffects_model/plots/semanticpriming-interactions-with-gender.pdf',
          device = cairo_pdf, width = 6.5, height = 7, dpi = 900)
 

### 2022-09-26 semanticpriming/power_analysis/reduced_randomeffects_model/semanticpriming-interactions-with-interstimulus-interval.R

@@ -2,6 +2,9 @@
 
 # Part of Study 1: Semantic priming
 
+# Deprecated model. For details, please see README.md in the directory
+# 'semanticpriming/power_analysis/reduced_randomeffects_model'
+
 # Combination of plots:
 # 1. Interaction between cosine similarity and interstimulus interval
 # 2. Interaction between visual rating difference and interstimulus interval
@@ -51,6 +54,6 @@ plot2 =
 
 # Combine plots using {patchwork}
 (plot1 + plot2 + plot_layout(ncol = 1, guides = 'collect')) %>%
-  ggsave(filename = 'semanticpriming/power_analysis/model/plots/semanticpriming-interactions-with-interstimulus-interval.pdf',
+  ggsave(filename = 'semanticpriming/power_analysis/reduced_randomeffects_model/plots/semanticpriming-interactions-with-interstimulus-interval.pdf',
          device = cairo_pdf, width = 6.5, height = 7, dpi = 900)
 

### 2022-09-26 semanticpriming/power_analysis/reduced_randomeffects_model/semanticpriming-interactions-with-vocabulary-size.R

@@ -2,6 +2,9 @@
 
 # Part of Study 1: Semantic priming
 
+# Deprecated model. For details, please see README.md in the directory
+# 'semanticpriming/power_analysis/reduced_randomeffects_model'
+
 # Combination of plots:
 # 1. Interaction between vocabulary size and language-based similarity
 # 2. Interaction between vocabulary size and visual-strength difference
@@ -49,6 +52,6 @@ plot2 =
 
 # Combine plots using {patchwork}
 (plot1 + plot2 + plot_layout(ncol = 1, guides = 'collect')) %>%
-  ggsave(filename = 'semanticpriming/power_analysis/model/plots/semanticpriming-interactions-with-vocabulary-size.pdf',
+  ggsave(filename = 'semanticpriming/power_analysis/reduced_randomeffects_model/plots/semanticpriming-interactions-with-vocabulary-size.pdf',
          device = cairo_pdf, width = 6.5, height = 7, dpi = 900)
 

### 2022-09-26 semanticpriming/power_analysis/reduced_randomeffects_model/semanticpriming_lmerTest.R

@@ -2,7 +2,8 @@
 
 # Part of Study 1: Semantic priming
 
-# This model was run 
+# Deprecated model. For details, please see README.md in the directory
+# 'semanticpriming/power_analysis/reduced_randomeffects_model'
 
 library(dplyr)  # data wrangling
 # The following lme4-relevant package was installed before lme4 to avoid a conflict 
@@ -103,26 +104,26 @@ system.time({
 })
 
 saveRDS(semanticpriming_lmerTest, 
-        'semanticpriming/power_analysis/model/results/semanticpriming_lmerTest.rds')
+        'semanticpriming/power_analysis/reduced_randomeffects_model/results/semanticpriming_lmerTest.rds')
 
 # Calculate p values using Kenward-Roger method (Luke, 2017; 
 # https://doi.org/10.3758/s13428-016-0809-y)
 summary(semanticpriming_lmerTest, ddf = 'Kenward-Roger') %>%
-  saveRDS('semanticpriming/power_analysis/model/results/KR_summary_semanticpriming_lmerTest.rds')
+  saveRDS('semanticpriming/power_analysis/reduced_randomeffects_model/results/KR_summary_semanticpriming_lmerTest.rds')
 
 # Calculate R^2. The result must be interpreted with caution as it differs from the 
 # traditional R^2 (Nakagawa et al., 2017; https://doi.org/10.1098/rsif.2017.0213)
 MuMIn::r.squaredGLMM(semanticpriming_lmerTest) %>%
-  saveRDS('semanticpriming/power_analysis/model/results/Nakagawa2017_R2_semanticpriming_lmerTest.rds')
+  saveRDS('semanticpriming/power_analysis/reduced_randomeffects_model/results/Nakagawa2017_R2_semanticpriming_lmerTest.rds')
 
 # Calculate 95% confidence intervals of fixed effects
 lme4::confint.merMod(semanticpriming_lmerTest, method = 'profile',
                      # Compute 95% CIs for every effect, as well as for the intercept
                      parm = rownames(summary(semanticpriming_lmerTest)$coefficients)) %>%
-  saveRDS('semanticpriming/power_analysis/model/results/confint_semanticpriming_lmerTest.rds')
+  saveRDS('semanticpriming/power_analysis/reduced_randomeffects_model/results/confint_semanticpriming_lmerTest.rds')
 
 # Save random effects
 lme4::ranef(semanticpriming_lmerTest) %>%
[…]

### 2022-10-23 manuscript/manuscript.tex
23102022

@@
 % \newenvironment{ltable}
-%   {\begin{landscape}\begin{center}\begin{threeparttable}}
-%   {\end{threeparttable}\end{center}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+%   {\begin{landscape}\centering\begin{threeparttable}}
+%   {\end{threeparttable}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
 
@@
 Correspondence can be addressed to Pablo Bernabeu on \href{mailto:pcbernabeu@gmail.com}{\nolinkurl{pcbernabeu@gmail.com}}.
-All materials needed to inspect and reproduce the present research---comprising documentation, data, analysis and results---are available at \url{http://doi.org/10.17605/OSF.IO/UERYQ}.
+All the materials needed to inspect and reproduce the present research---comprising documentation, data, analysis and results---are available at \url{http://doi.org/10.17605/OSF.IO/UERYQ}.
 
@@
 We tested this interplay at three levels of the experimental structure: individuals, words and tasks.
-To this end, we drew on three existing data sets that were composed of large samples, and implemented the paradigms of semantic priming, semantic decision and lexical decision.
-We extended these data sets with language-based and vision-based measures, and analysed their interactions with participants' vocabulary size and gender, and with presentation speed in the semantic priming study.
+To this end, we drew on three existing, large data sets that implemented the paradigms of semantic priming, semantic decision and lexical decision.
+We extended these data sets with measures of language-based and vision-based information, and analysed how the latter variables interacted with participants' vocabulary size and gender, and also with presentation speed in the semantic priming study.
 We performed the analysis using mixed-effects models that included a comprehensive array of fixed effects---including covariates---and random effects.
-First, language-based information was found to be more important than vision-based information.
+First, we found that language-based information was found to be more important than vision-based information.
 Second, in the semantic priming study---whose task required distinguishing between words and nonwords---, both language-based and vision-based information were more influential when words were presented faster.
 Third, a `task-relevance advantage' was identified in higher-vocabulary participants.
-Specifically, in lexical decision, higher-vocabulary participants were more sensitive than lower-vocabulary participants to language-based information.
+Specifically, in lexical decision, higher-vocabulary participants were more sensitive to language-based information than lower-vocabulary participants.
 In contrast, in semantic decision, higher-vocabulary participants were more sensitive to word concreteness.
-Fourth, a human-based measure of visual information was found to be superior to a computational measure.
+Fourth, we demonstrated the influence of the analytical method on the results.
 These findings support the interplay between language and vision in conceptual processing, and demonstrate the influence of measurement instruments on the results.
@@
 We found that 300 participants were sufficient to examine the effect of language-based information contained in words, whereas more than 1,000 participants were necessary for the effect of vision-based information and for the interactions of both former variables with vocabulary size, gender and presentation speed.
-In conclusion, this power analysis reveals the need to increase sample sizes in research on perceptual simulation and individual differences.
+In conclusion, this power analysis reveals the need to increase sample sizes for research on perceptual simulation and individual differences.
 }
@@
 
-Over the last two decades, research in cognitive science has suggested that conceptual processing depends on both language and embodiment systems.
-That is, understanding words involves---on the one hand---lexical and semantic associations of an amodal kind, and---on the other hand---modality-specific associations within perceptual, motor, affective and social domains (Barsalou et al., 2008; Connell, 2019; Davis \& Yee, 2021; Khatin-Zadeh et al., 2021; Roads \& Love, 2020; Vigliocco et al., 2009).
+Over the last two decades, research in the cognitive sciences has suggested that conceptual processing depends on both language and embodiment systems.
+That is, understanding words involves---on the one hand---lexical and semantic associations of an amodal kind, and---on the other hand---modality-specific associations within perceptual, motor, affective and social domains (Barsalou et al., 2008; Connell, 2019; Davis \& Yee, 2021; Khatin-Zadeh et al., 2021; Vigliocco et al., 2009).
 Studies addressing these systems have found that the language system is overall more prevalent in word processing, producing larger effect sizes (Banks et al., 2021; Kiela \& Bottou, 2014; Lam et al., 2015; Louwerse et al., 2015; Pecher et al., 1998; Petilli et al., 2021).
@@
 Petilli et al., 2021) and property generation (Santos et al., 2011; Simmons et al., 2008), (II) when participants produce slower responses (Louwerse \& Connell, 2011), and (III) in tasks that elicit deeper semantic processing---e.g., semantic decision, as opposed to lexical decision (Ostarek \& Huettig, 2017; Petilli et al., 2021).
+Last, research in computational linguistics has provided further support for the complementarity of language and embodied information, by revealing increased predictive performance when models are provided with perceptual information on top of text-based information (Frome et al., 2013; Roads \& Love, 2020).
 
@@
 Each of these central studies contained measures of participants' vocabulary size and gender.
-Furthermore, the core data sets were expanded by adding variables that captured the language-based information in words (Mandera et al., 2017; Wingfield \& Connell, 2022) and the vision-based information in words (Lynott et al., 2020; Petilli et al., 2021)---the latter being used to represent the embodiment system.
+Furthermore, the core data sets were expanded by adding variables that captured the language-based information in words (Mandera et al., 2017; Wingfield \& Connell, 2022a) and the vision-based information in words (Lynott et al., 2020; Petilli et al., 2021)---the latter being used to represent the embodiment system.
 One of the key questions we investigated using this array of variables was whether individual differences in vocabulary and gender modulated participants' sensivity to the language-based and vision-based information in words.
@@
 Studies have operationalised the language system at the word level using measures that capture the relationships among words without explicitly drawing on any sensory or affective modalities.
-Two main types of linguistic measures exist: those based on text corpora---dubbed \emph{word co-occurrence} measures (Bullinaria \& Levy, 2007; Petilli et al., 2021; Wingfield \& Connell, 2022)---and those based on associations collected from human participants---dubbed \emph{word association} measures (De Deyne et al., 2016, 2019).
+Two main types of linguistic measures exist: those based on text corpora---dubbed \emph{word co-occurrence} measures (Bullinaria \& Levy, 2007; Petilli et al., 2021; Wingfield \& Connell, 2022a)---and those based on associations collected from human participants---dubbed \emph{word association} measures (De Deyne et al., 2016, 2019).
 Notwithstanding the interrelation between word co-occurrence and word association (Planchuelo et al., 2022), co-occurrence is more purely linguistic, whereas association indirectly captures more of the sensory and affective meaning of words (De Deyne et al., 2021).
@@
 Specifically, in Study 1, this measure was called \texttt{language-based\ similarity}, and it was based on the degree of text-based co-occurrence between the prime word and the target word in each trial (Mandera et al., 2017).
-In Study 2, the measure was called \texttt{word\ co-occurrence}, and it was based on the degree of text-based co-occurrence between each stimulus word and the words `abstract' and `concrete' (Wingfield \& Connell, 2022).
+In Study 2, the measure was called \texttt{word\ co-occurrence}, and it was based on the degree of text-based co-occurrence between each stimulus word and the words `abstract' and `concrete' (Wingfield \& Connell, 2022a).
 In Study 3 (lexical decision), a co-occurrence measure could not be used, as the co-occurrence of words in consecutive trials could not be calculated due to the high frequency of nonword trials throughout the lexical decision task.
@@
 
-We hypothesised that word co-occurrence, word frequency and vocabulary size would all have facilitatory effects on participants' performance, with higher values leading to shorter RTs (Pexman \& Yap, 2018; Wingfield \& Connell, 2022; Yap et al., 2009).
+We hypothesised that word co-occurrence, word frequency and vocabulary size would all have facilitatory effects on participants' performance, with higher values leading to shorter RTs (Pexman \& Yap, 2018; Wingfield \& Connell, 2022a; Yap et al., 2009).
 
@@
 For instance, the perceptual modalities have often corresponded to the five Aristotelian senses---vision, hearing, touch, taste and smell (Bernabeu et al., 2017, 2021; Louwerse \& Connell, 2011)---and, less often, to interoception (Connell et al., 2018).
-Yet, out of all these senses, vision has been most frequently used in research (e.g., Bottini et al., 2021; De Deyne et al., 2021; Pearson \& Kosslyn, 2015; Petilli et al., 2021; Yee et al., 2012).
-The hegemony of vision is likely due to the central position of this sense in the human brain (Reilly et al., 2020) as well as in several languages (Bernabeu, 2018; Chen et al., 2019; Lynott et al., 2020; Miceli et al., 2021; Morucci et al., 2019; Roque et al., 2015; Speed \& Brybaert, 2021; Speed \& Majid, 2020; Vergallito et al., 2020; Winter et al., 2018; Zhong et al., 2022).
-In the present study, we focussed on vision alone both because of its prominence in cognition and because we had planned to use the present research to determine the sample size of a subsequent study that focusses on vision (indeed, the present study grew out of a statistical power analysis).
+Yet, out of all these domains, vision has been most frequently used in research (e.g., Bottini et al., 2021; De Deyne et al., 2021; Pearson \& Kosslyn, 2015; Petilli et al., 2021; Yee et al., 2012).
+The hegemony of vision is likely due to the central position of vision in the human brain (Reilly et al., 2020) as well as in several languages (Bernabeu, 2018; Chen et al., 2019; Lynott et al., 2020; Miceli et al., 2021; Morucci et al., 2019; Roque et al., 2015; Speed \& Brybaert, 2021; Speed \& Majid, 2020; Vergallito et al., 2020; Winter et al., 2018; Zhong et al., 2022).
+In the present study, we focussed on vision alone due to three reasons.
+First, we wanted to use a single variable to represent sensorimotor information, just as a single variable would be used to represent linguistic information.
+Using a single variable for each system facilitates the analysis of interactions with other variables.
+Second, vision is very prominent in cognition, as we just reviewed.
+Third, we had planned to use the present research to determine the sample size of a subsequent study that focusses on vision (indeed, the present study grew out of a statistical power analysis).
 
@@
 Experimental data in psycholinguistics can be divided into various levels, such as individuals, words and tasks.
-The simultaneous examination of a theory across several levels is expected to enhance our understanding of the theory (Ostarek \& Bottini, 2021)---for instance, by revealing the distribution of explanatory power within and across these levels.
+The simultaneous examination of a theory across several levels is expected to enhance our understanding of the theory (Ostarek \& Bottini, 2021)---for instance, by revealing the distribution of explanatory power (that is, effect size) within and across these levels.
 Several studies have probed more than one level---for instance, word level and individual level (Aujla, 2021; Lim et al., 2020; Pexman \& Yap, 2018; Yap et al., 2009), or word level and task level (Al-Azary et al., 2022; Connell \& Lynott, 2013, 2014; Ostarek \& Huettig, 2019; Petilli et al., 2021).
@@
 
-The word level is concerned with the lexical and semantic information in words (e.g., De Deyne et al., 2021; Lam et al., 2015; Lund et al., 1995; Lund \& Burgess, 1996; Lynott et al., 2020; Mandera et al., 2017; Petilli et al., 2021; Pexman et al., 2017; Santos et al., 2011; Wingfield \& Connell, 2022).
+The word level is concerned with the lexical and semantic information in words (e.g., De Deyne et al., 2021; Lam et al., 2015; Lund et al., 1995; Lund \& Burgess, 1996; Lynott et al., 2020; Mandera et al., 2017; Petilli et al., 2021; Pexman et al., 2017; Santos et al., 2011; Wingfield \& Connell, 2022a).
 The word-level variables of interest in this study are language-based and vision-based information (both described above).
@@
 Beyond task-level variables, there is an additional source of task-related information across the three studies---namely, the experimental paradigm used in each study (i.e., semantic priming, semantic decision and lexical decision).
-Indeed, it is possible to examine how the effects vary across these paradigms (see Wingfield \& Connell, 2022).
+Indeed, it is possible to examine how the effects vary across these paradigms (see Wingfield \& Connell, 2022a).
 This comparison, however, must be considered cautiously due to the existence of other non-trivial differences across these studies, such as the numbers of observations.
-With this caveat noted, the tasks used across these studies likely elicit varying degrees of semantic depth, as ordered below (see Balota \& Lorch, 1986; Barsalou et al., 2008; Becker et al., 1997; de Wit \& Kinoshita, 2015; Joordens \& Becker, 1997; Lam et al., 2015; Muraki \& Pexman, 2021; Ostarek \& Huettig, 2017; Versace et al., 2021; Wingfield \& Connell, 2022).
+With this caveat noted, the tasks used across these studies likely elicit varying degrees of semantic depth, as ordered below (see Balota \& Lorch, 1986; Barsalou et al., 2008; Becker et al., 1997; de Wit \& Kinoshita, 2015; Joordens \& Becker, 1997; Lam et al., 2015; Muraki \& Pexman, 2021; Ostarek \& Huettig, 2017; Versace et al., 2021; Wingfield \& Connell, 2022a).
 
@@
 The central objective of the present studies is the simultaneous investigation of language-based and vision-based information, along with the interactions between each of those and vocabulary size, gender and presentation speed (i.e., SOA).
-Previous studies have examined subsets of these effects using the same data sets we are using (Balota et al., 2007; Petilli et al., 2021; Pexman et al., 2017; Pexman \& Yap, 2018; Wingfield \& Connell, 2022; Yap et al., 2012, 2017).
+Previous studies have examined subsets of these effects using the same data sets we are using (Balota et al., 2007; Petilli et al., 2021; Pexman et al., 2017; Pexman \& Yap, 2018; Wingfield \& Connell, 2022a; Yap et al., 2012, 2017).
 Out of these studies, only Petilli et al.
@@
 
-The analytical method was broadly similar across the three studies. Below, we present the commonalities in the statistical analysis and in the power analysis.
+The analytical method was broadly similar across the three studies.
+Below, we present the commonalities in the statistical analysis and in the power analysis.
+Several R packages from the `tidyverse' (Wickham et al., 2019) were used.
 
@@
 
-Lexical covariates were selected in every study out of the same five variables, which had been used as covariates in Wingfield and Connell (2022; also see Petilli et al., 2021).
+Lexical covariates were selected in every study out of the same five variables, which had been used as covariates in Wingfield and Connell (2022a; also see Petilli et al., 2021).
 They comprised: number of letters (i.e., orthographic length), word frequency, number of syllables (both the latter from Balota et al., 2007), orthographic Levenshtein distance (Yarkoni et al., 2008) and phonological Levenshtein distance (Suárez et al., 2011; Yap \& Balota, 2009).
@@
 Therefore, linear mixed-effects models were implemented.
-These models included a maximal random-effects structure, with by-participant and by-item random intercepts, and the appropriate random slopes for all effects of interest (Barr et al., 2013).
+These models included a maximal random-effects structure, with by-participant and by-item random intercepts, and the appropriate random slopes for all effects of interest (Barr et al., 2013; Brauer \& Curtin, 2018; Singmann \& Kellen, 2019).
+Random effects---especially random slopes---constrain the analytical space by \emph{claiming} their share of variance.
+As a result, that variance cannot be taken by the fixed effects.
 In the semantic priming study, the items were prime--target pairs, whereas in the semantic decision and lexical decision studies, the items were individual words.
@@
 Diagnostics regarding convergence and normality are provided in \protect\hyperlink{appendix-B-frequentist-analysis-diagnostics}{\underline{Appendix B}}.
-Effects that were non-significant or very small are best interpreted by considering their 95\% confidence intervals, and the 95\% credible intervals (i.e., the Bayesian counterpart) where available (Cumming, 2014).
+Those effects that are non-significant or very small are best interpreted by considering the confidence intervals and the credible intervals (Cumming, 2014).
+
+The R package `GGally' (Schloerke et al., 2021) was used to create correlation plots, whereas the package `sjPlot' (Lüdecke, 2021) was used for interaction plots.
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/bayesian_priors/plots/bayesian_priors}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/bayesian_priors/plots/bayesian_priors}
 
@@
 Second, over the course of the research, a variety of circumstances could create differences between the planned study and the studies that were used in the power analysis.
-Some of these differences could be foreseeable---for instance, if they are due to a limitation in the literature available for the power analysis---, whereas other differences might be unforeseeable and could go unnoticed (Barsalou, 2019).
+Some of these differences could be foreseeable---for instance, if they are due to a limitation in the literature available for the power analysis---, whereas other differences might be unforeseeable and could go unnoticed (Barsalou, 2019; Noah et al., 2018).
 Reducing the effect size in the power analysis leads to an increase of the sample size of the planned study (Brysbaert \& Stevens, 2018; Green \& MacLeod, 2016; Hoenig \& Heisey, 2001).
@@
 N.
-Jones et al., 2006; Lund et al., 1995; Lund \& Burgess, 1996; Mandera et al., 2017; McDonald \& Brew, 2002; Padó \& Lapata, 2007; Petilli et al., 2021; Wingfield \& Connell, 2022).
+Jones et al., 2006; Lund et al., 1995; Lund \& Burgess, 1996; Mandera et al., 2017; McDonald \& Brew, 2002; Padó \& Lapata, 2007; Petilli et al., 2021; Wingfield \& Connell, 2022a).
 In one of these studies, Mandera et al.
@@
 It had 300 dimensions and a window size of six words.
+The R package `LSAfun' (Günther et al., 2015) was used to import this variable.\footnote{Despite the name of the package, the measure we used was not based on Latent Semantic Analysis.}
 \item
@@
 The results of the posterior predictive checks were sound (see \protect\hyperlink{appendix-C-Bayesian-analysis-diagnostics}{\underline{Appendix C}}), indicating that the posterior distributions were sufficiently consistent with the observed data.
-Furthermore, in the prior sensitivity analysis, the results were virtually identical with the three priors that were considered (to recall the priors, see Figure \ref{fig:bayesian-priors} above; to view the results in detail, see \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}).
+Furthermore, in the prior sensitivity analysis, the results were virtually identical with the three priors that were considered (refer to the priors in Figure \ref{fig:bayesian-priors} above; to view the results in detail, see \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}}).
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_bayesian_plots/plots/semanticpriming_frequentist_bayesian_plot_weaklyinformativepriors_exgaussian}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_bayesian_plots/plots/semanticpriming_frequentist_bayesian_plot_weaklyinformativepriors_exgaussian}
 
@@
 In contrast, the present study applied a continuous measure of relatedness---i.e., cosine similarity---, which is more precise and may thus afford more statistical power (Mandera et al., 2017; Petilli et al., 2021).
-Therefore, this interaction demonstrates the consistency between human ratings and computational approximations to meaning (Charbonnier \& Wartena, 2019, 2020; Günther et al., 2016b; Louwerse et al., 2015; Mandera et al., 2017; Petilli et al., 2021; Solovyev, 2021; Wingfield \& Connell, 2022).
+Therefore, this interaction demonstrates the consistency between human ratings and computational approximations to meaning (Charbonnier \& Wartena, 2019, 2020; Günther et al., 2016b; Louwerse et al., 2015; Mandera et al., 2017; Petilli et al., 2021; Solovyev, 2021; Wingfield \& Connell, 2022a).
 The second difference between the present study and Yap et al.
@@
 
-{\centering \includegraphics[width=0.85\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-vocabulary-size}
+{\centering \includegraphics[width=0.85\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-vocabulary-size}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-SOA}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-SOA}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-gender}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-gender}
 
@@
 Next, we reflected on the adequacy of visual-strength difference as a measurement instrument, as it had never (to our knowledge) been used before in the study of semantic priming.
-Even though the effect of this variable on task performance was---as expected---inhibitory (i.e., higher values of this variable leading to longer RTs), we were concerned about the low correlation between visual-strength difference and language-based similarity (\(r\) = 0.01).
+Even though the effect of this variable on task performance was---as expected---inhibitory (i.e., higher values of this variable leading to longer RTs), we were concerned about the low correlation between visual-strength difference and language-based similarity (\(r\) = .01).
 First, the negligible size of this correlation raised concerns, as we expected a larger and negative correlation.
@@
 
-{\centering \includegraphics[width=0.89\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/analysis_with_visualsimilarity/plots/semanticpriming_with_visualsimilarity_confidence_intervals_plot}
+{\centering \includegraphics[width=0.89\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/analysis_with_visualsimilarity/plots/semanticpriming_with_visualsimilarity_confidence_intervals_plot}
 
@@
 
-The results revealed revealed a significant effect of visual-strength difference, as in the main analysis above.
-In contrast, the effect of vision-based similarity was not significant.
-This difference was not due to collinearity between these measures (\(r\) = -0.04).
+The results revealed an effect of the human-based measure, \texttt{visual-strength\ difference} (as in the main analysis above), along with a smaller effect of the computational measure, \texttt{vision-based\ similarity}.
+There was an important difference between these measures regarding the interaction with SOA.
+Whereas visual-strength difference had a larger effect with the short SOA, vision-based similarity did not interact with SOA, contrary to the results of Petilli et al.
+(2021).
+This difference was not due to collinearity between these measures (\(r\) = -.04).
 Also importantly, both measures appeared to be valid based on their correlations with language-based similarity and with word concreteness (Figure \ref{fig:semanticpriming-with-visualsimilarity-correlations}).
@@
 This was done using the main model, not the follow-up that included vision-based similarity.
-Figures \ref{fig:semanticpriming-powercurve-plots-1-2-3} and \ref{fig:semanticpriming-powercurve-plots-4-5-6-7-8-9} show the estimated power for some main effects and interactions of interest, as a function of the number of participants.
+Figures \ref{fig:semanticpriming-powercurve-plots-1-2-3} and \ref{fig:semanticpriming-powercurve-plots-4-5-6-7-8-9} show the estimated power for some main effects and interactions of interest as a function of the number of participants.
 To plan the sample size for future studies, these results must be considered under the assumptions that the future study would apply a statistical method similar to ours---namely, a mixed-effects model with random intercepts and slopes---, and that the analysis would encompass at least as many prime--target pairs as the current study, namely, 5,943 (distributed in various blocks across participants, not all being presented to every participant).
@@
 
-{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/power_analysis/plots/semanticpriming_powercurve_plots_1_2_3}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/power_analysis/plots/semanticpriming_powercurve_plots_1_2_3}
 
@@
 
-{\centering \includegraphics[width=0.92\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/power_analysis/plots/semanticpriming_powercurve_plots_4_5_6_7_8_9}
+{\centering \includegraphics[width=0.92\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/power_analysis/plots/semanticpriming_powercurve_plots_4_5_6_7_8_9}
 
@@
 Next, in a secondary analysis, we compared the roles of two measures of vision-based priming.
-The first measure---\texttt{visual-strength\ difference}---was operationalised as the difference in visual strength (Lynott et al., 2020) between the prime word and the target word in each trial.
+The first measure---\texttt{visual-strength\ difference}---was operationalised as the difference in visual strength between the prime word and the target word in each trial.
+This difference score was thus based on modality-specific ratings provided by human participants (Lynott et al., 2020).
 The second measure---\texttt{vision-based\ similarity}---, created by Petilli et al.
 (2021), was based on vector representations trained on labelled images from ImageNet.
-The effect of visual-strength difference was slightly larger.
-The larger effect size of visual-strength difference---being a human-based measure---is consistent with some previous findings suggesting that human-based measures explained more variance than computational measures (De Deyne et al., 2016, 2019; Gagné et al., 2016; Schmidtke et al., 2018; cf.
+This variable is therefore computational.
+The effect of visual-strength difference was slightly larger than that of vision-based similarity.
+This result is consistent with some previous findings suggesting that human-based measures explained more variance than computational measures (De Deyne et al., 2016, 2019; Gagné et al., 2016; Schmidtke et al., 2018; cf.
 Michaelov et al., 2022; Snefjella \& Blank, 2020).
-Furthermore, whereas visual-strength difference produced a significant effect, vision-based similarity did not.
-The result of vision-based similarity contrasts with that obtained by Petilli et al.~There are several possible reasons why this variable is not significant in the present study, including: (I) a more conservative method---i.e., a maximal mixed-effects model containing more predictors than the hierarchical regression that was performed by Petilli et al.---, and (II) the presence of participant-level data in the present study, versus the aggregation performed by Petilli et al.
-
-It is noteworthy that both visual-strength difference and vision-based similarity have \emph{independently} proven to be relevant, and arguably valid, considering their correlations with other measures---especially \texttt{word-concreteness\ difference} and \texttt{language-based\ similarity}---and considering the effects of each measure in semantic priming (see Petilli et al., 2021).
-However, the differences between these measures are worthy of attention.
-Visual-strength difference was barely correlated with language-based similarity.
-Conversely, vision-based similarity was barely correlated with word-concreteness difference (recall Figure \ref{fig:semanticpriming-with-visualsimilarity-correlations}).
-These results call for an investigation into the underlying composition of visual-strength difference and vision-based similarity
-
-Next, we can consider why visual-strength difference played a more important role than vision-based similarity.
-The reason might be the fact that visual-strength difference was based on human ratings whereas vision-based similarity was a computational measure.
-Indeed, some previous studies have found human-based measures to have more explanatory power than computational measures (De Deyne et al., 2016, 2019; Gagné et al., 2016; Schmidtke et al., 2018; but also see Michaelov et al., 2022; Snefjella \& Blank, 2020).
-If the different degree of human dependence of our two variables were indeed behind the explanatory power of each, we would need to consider a related issue.
-The problem of circularity was addressed by Petilli et al.
-(2021), who argued that using human-based predictors---such as ratings---to investigate human behaviour was less valid than using predictors that were more independent of human behaviour---such as computational measures.
+If the different degree of human dependence of our two variables were indeed behind the effect size of each, we would need to consider a related issue.
+The problem of circularity was addressed by Petilli et al., who argued that using human-based predictors---such as ratings---to investigate human behaviour was less valid than using predictors that were more independent of human behaviour---such as computational measures.
 On the one hand, we identify two reasons for skepticism regarding the circularity hypothesis.
@@
 Yet, on the other hand, the circularity hypothesis is important enough to warrant dedicated research.
-Specifically, future studies could be conducted to systematically compare the theoretical insights provided by human-based measures and by computational ones, as well as the amount of explanatory power achieved by both types.
-
-\hypertarget{the-confounding-influence-of-measurement-instruments}{%
-\subsubsection{The confounding influence of measurement instruments}\label{the-confounding-influence-of-measurement-instruments}}
-
-The present comparison demonstrates the influence of measurement instruments on results, and their potential to act as confounds.
-A previous example of this influence appeared in a set of studies that used latent semantic analysis (LSA) as a predictor of semantic priming.
+Specifically, future studies could be conducted to systematically compare the theoretical insights provided by human-based measures and by computational ones, as well as the effect size achieved by both types.
+
+It is noteworthy that both visual-strength difference and vision-based similarity have \emph{independently} proven to be relevant, and arguably valid, considering their correlations with other measures---especially \texttt{word-concreteness\ difference} and \texttt{language-based\ similarity}---and considering the effects of each measure in semantic priming (see Petilli et al., 2021).
+However, the differences between these measures are worthy of attention.
+Visual-strength difference was barely correlated with language-based similarity.
+Conversely, vision-based similarity was barely correlated with word-concreteness difference (refer to Figure \ref{fig:semanticpriming-with-visualsimilarity-correlations}).
+These results call for an investigation into the underlying composition of visual-strength difference and vision-based similarity.
+
+Furthermore, whereas visual-strength difference retained its significant interaction with SOA---also observed in the main analysis presented above---, in contrast, vision-based similarity did not present such an interaction.
+The lack of an interaction between vision-based similarity and SOA contrasts with the results of Petilli et al.
+(2021), who found that vision-based similarity was only significant in the short SOA condition.
+There are several possible reasons for this difference, including: (I) a more conservative method in our current analysis---i.e., a maximal mixed-effects model containing more predictors than the hierarchical regression performed by Petilli et al.---, and (II) the presence of individual differences in the present study (i.e., vocabulary size, attentional control and gender), versus the aggregation performed by Petilli et al.
+
+Last, the interaction between language-based similarity and SOA became non-significant in this sub-analysis.
+This difference from the original analysis may have been caused by the sizable correlation between language-based similarity and vision-based similarity (\(r\) = .49).
+In this regard, we should notice the large influence of the addition of a single variable (along with its interactions) into the model.
+
+\hypertarget{the-influence-of-the-analytical-method}{%
+\subsubsection{The influence of the analytical method}\label{the-influence-of-the-analytical-method}}
+
+Taken together, the sub-analysis that included vision-based similarity offered a glimpse into the crucial role of analytical choices in the present topic.
+A previous example of this influence appeared in a set of studies that used Latent Semantic Analysis (LSA) as a predictor of semantic priming.
 Hutchison et al.
@@
 In contrast, later studies did not use a difference score and they observed a significant effect (Günther et al., 2016a; Mandera et al., 2017).
-
-In the case of linguistic and embodied processing, the large difference between the effect sizes of these systems---found in the three current studies and in previous ones (Banks et al., 2021; Kiela \& Bottou, 2014; Lam et al., 2015; Louwerse et al., 2015; Pecher et al., 1998; Petilli et al., 2021)---would be less trustworthy if the instruments that were used to measure the language system had been far more precise than the instruments used to measure the embodiment system.
+We can extrapolate this issue to a very important comparison we often make---namely, that between language-based and embodied simulation.
+The pervasive superiority of language over the other systems (perception, action, emotion and sociality)---found in the three current studies and in previous ones (Banks et al., 2021; Kiela \& Bottou, 2014; Lam et al., 2015; Louwerse et al., 2015; Pecher et al., 1998; Petilli et al., 2021)---would be less trustworthy if the instruments that were used to measure the language system had been far more precise than the instruments used to measure the embodiment system.
 In this sense, it is relevant to consider how variables are improved in research: it is done iteratively, by comparing the performance of different variables.
-Critically, the literature contains many comparisons of text-based variables, some dating back to the 1990s (De Deyne et al., 2016, 2013; Günther et al., 2016a, 2016b; M.
+Critically, the literature contains many comparisons of text-based variables, some dating back to the 1990s (De Deyne et al., 2013, 2016; Günther et al., 2016a, 2016b; M.
 N.
-Jones et al., 2006; Lund \& Burgess, 1996; Mandera et al., 2017; Mikolov et al., 2013; Wingfield \& Connell, 2022).
+Jones et al., 2006; Lund \& Burgess, 1996; Mandera et al., 2017; Mikolov et al., 2013; Wingfield \& Connell, 2022a).
 In contrast, the work on embodiment variables began more than a decade afterwards, and it has been less concerned with benchmarking the explanatory power of variables (but see Vergallito et al., 2020).
@@
 Thus, if linguistic measures are more precise than embodiment measures due to greater work on the variables, such a difference could account for a certain portion of the superiority of linguistic information over embodied information (see Banks et al., 2021; Kiela \& Bottou, 2014; Lam et al., 2015; Louwerse et al., 2015; Pecher et al., 1998; Petilli et al., 2021).
-In conclusion, the case of different measurement instruments is one of several factors that can greatly influence the conclusions of research.
-In the medium term, it may pay dividends to devote more work to comparing different instruments and, more generally, different analytical approaches (see Barsalou, 2019; Botvinik-Nezer et al., 2020; Wagenmakers et al., 2022).
+Analytical choices such as the operationalisation of variables and the complexity of statistical models can greatly influence the conclusions of research.
+Indeed, our current results and previous ones suggest that the conclusions of research are inextricable from the method used in each study (see Barsalou, 2019; Botvinik-Nezer et al., 2020; Perret \& Bonin, 2019; Wagenmakers et al., 2022).
+Therefore, in the medium term, it may pay dividends to continue examining the influence of analytical choices.
+Unfortunately, in many research fields, reflecting on the sensitivity of our analyses might conflict with the incentives of the system, which may penalise nuanced conclusions in favour of simplified stories.
+To overcome such a bias, it may be necessary to devote greater importance to the methodology in scientific papers---for instance, by commenting on the method in the abstract and by extending the methods section in the body of the paper.
+In stark contrast, our current results should make us question some decisions by scientific publishers such as rendering the methods section in a smaller font than the results section, or placing the method section at the end of the paper.
+In a nutshell, it may be useful to ensure that scientists are aware that research findings are fundamentally dependent on research methods.
 
@@
 
-Wingfield and Connell (2022) reanalysed the data from Pexman et al.
+Wingfield and Connell (2022a) reanalysed the data from Pexman et al.
 (2017) using language-based variables that are more related to the language system than to the visual system.
@@
 
-The zero-order correlation between Wingfield and Connell's (2022) distance to `abstract' and distance to `concrete' was \(r\) = 0.98.
+The zero-order correlation between Wingfield and Connell's (2022) distance to `abstract' and distance to `concrete' was \(r\) = .98.
 To avoid the collinearity between these variables in the model (Dormann et al., 2013; Harrison et al., 2018), and to facilitate the analysis of interactions with other variables, we created a difference score by subtracting the distance to `abstract' from the distance to `concrete'.
@@
 
-{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/plots/semanticdecision_confidence_intervals_plot}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/plots/semanticdecision_confidence_intervals_plot}
 
@@
 
-{\centering \includegraphics[width=0.98\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/plots/semanticdecision-interactions-with-vocabulary-size}
+{\centering \includegraphics[width=0.98\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/plots/semanticdecision-interactions-with-vocabulary-size}
 
@@
 
-{\centering \includegraphics[width=0.98\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/plots/semanticdecision-interactions-with-gender}
+{\centering \includegraphics[width=0.98\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/plots/semanticdecision-interactions-with-gender}
 
@@
 
-Figures \ref{fig:semanticdecision-powercurve-plots-1-2-3} and \ref{fig:semanticdecision-powercurve-plots-4-5-6-7} show the estimated power for some main effects and interactions of interest, as a function of the number of participants.
+Figures \ref{fig:semanticdecision-powercurve-plots-1-2-3} and \ref{fig:semanticdecision-powercurve-plots-4-5-6-7} show the estimated power for some main effects and interactions of interest as a function of the number of participants.
 To plan the sample size for future studies, these results must be considered under the assumptions that the future study would apply a statistical method similar to ours---namely, a mixed-effects model with random intercepts and slopes---, and that the analysis would encompass at least as many words as the current study, namely, 8,927 (distributed in various blocks across participants, not all being presented to every participant).
@@
 
-{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/power_analysis/plots/semanticdecision_powercurve_plots_1_2_3}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/power_analysis/plots/semanticdecision_powercurve_plots_1_2_3}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/power_analysis/plots/semanticdecision_powercurve_plots_4_5_6_7}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/power_analysis/plots/semanticdecision_powercurve_plots_4_5_6_7}
 
@@
 Language-based information could be operationalised as one of several lexical variables.
-In the present study, word frequency was chosen as it had the most explanatory power out of five candidates---the other candidates being number of letters, number of syllables, orthographic Levenshtein distance and phonological Levenshtein distance (see \protect\hyperlink{appendix-A-lexical-covariates}{\underline{Appendix A}}).
+In the present study, word frequency was chosen as it had the largest effect size out of five candidates---the other candidates being number of letters, number of syllables, orthographic Levenshtein distance and phonological Levenshtein distance (see \protect\hyperlink{appendix-A-lexical-covariates}{\underline{Appendix A}}).
 It should also be noted that word frequency has been found to be more closely related to semantic variables than to lexical ones, such as word length, orthography and phonology (see Table 4 in Yap et al., 2012).
@@
 
-{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_bayesian_plots/plots/lexicaldecision_frequentist_bayesian_plot_weaklyinformativepriors_exgaussian}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_bayesian_plots/plots/lexicaldecision_frequentist_bayesian_plot_weaklyinformativepriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/plots/lexicaldecision-interactions-with-vocabulary-age}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/plots/lexicaldecision-interactions-with-vocabulary-age}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/plots/lexicaldecision-interactions-with-gender}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/plots/lexicaldecision-interactions-with-gender}
 
@@
 
-Figures \ref{fig:lexicaldecision-powercurve-plots-1-2-3} and \ref{fig:lexicaldecision-powercurve-plots-4-5-6-7} show the estimated power for some main effects and interactions of interest, as a function of the number of participants.
+Figures \ref{fig:lexicaldecision-powercurve-plots-1-2-3} and \ref{fig:lexicaldecision-powercurve-plots-4-5-6-7} show the estimated power for some main effects and interactions of interest as a function of the number of participants.
 To plan the sample size for future studies, these results must be considered under the assumptions that the future study would apply a statistical method similar to ours---namely, a mixed-effects model with random intercepts and slopes---, and that the analysis would encompass at least as many words as the current study, namely, 12,636 (distributed in various blocks across participants, not all being presented to every participant).
@@
 
-{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/power_analysis/plots/lexicaldecision_powercurve_plots_1_2_3}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/power_analysis/plots/lexicaldecision_powercurve_plots_1_2_3}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/power_analysis/plots/lexicaldecision_powercurve_plots_4_5_6_7}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/power_analysis/plots/lexicaldecision_powercurve_plots_4_5_6_7}
 
@@
 Furthermore, the data set used in this study was considerably smaller (19,828 RTs, compared to 345,666 RTs in Study 1 and 246,432 in Study 2).
+The relatively small size of the data set of Study 3 was due to the small number of words per participant (\(M\) = 25) and participants per word (\(M\) = 2 participants per word).
+In this regard, the English Lexicon Project (Balota et al., 2007) prioritised the total number of words included in their archive.
+
 While the covariates presented large effects, none of the effects of interest turned out to be significant or noteworthy.
-The comparison with the two previous tasks is hindered by the major difference in the size of the data sets.
-Therefore, while it would be reasonable to expect---in the lexical decision task---smaller semantic effects---as we indeed observed---, we cannot reliably attribute this difference to the nature of the task, due to the difference in the size of the data sets.
-As a minor suggestion, future studies could operationalise language using a measure of orthographic neighbourhood size, such as Levenshtein distance, instead of word frequency.
+Furthermore, he comparison with the two previous tasks is hindered by the major difference in the size of the data sets.
+Therefore, while it is reasonable to find smaller semantic effects in the lexical decision task than in the other two, we cannot reliably attribute this difference to the nature of the task.
+
+As a minor suggestion, future studies could operationalise language using a measure of orthographic neighbourhood size (e.g., orthographic Levenshtein distance), instead of using word frequency as in the present study.
 While we used word frequency guided by a data-driven selection (see Appendix A), neighbourhood size is a measure created for the purpose of indexing word co-occurrence where only one word is directly available to the researcher (Suárez et al., 2011; Yap \& Balota, 2009).
@@
 Although both language and vision played significant roles in some contexts (detailed below), the main effects and the interactions of language-based information were larger than those of vision-based information, consistent with previous research (Banks et al., 2021; Kiela \& Bottou, 2014; Lam et al., 2015; Louwerse et al., 2015; Pecher et al., 1998; Petilli et al., 2021).
-Whereas we focussed on the visual domain to investigate sensorimotor simulation, future research could consider other domains (Bernabeu et al., 2021).
-
-Important covariates such as word concreteness and individual differences in general cognition were controlled for in these analyses, and the models had a maximal random-effects structure providing for a conservative analysis.
-These methodological features are not trivial.
-First, the maximal random-effects structure served to impede a violation of the independence of observations.
-Specifically, random intercepts and slopes ensured that sources of dependence such as participants and stimuli were kept outside of the fixed effects, which are the relevant ones for the conclusions of this research.
-Second, the covariates are important because research has suggested that some correlated variables represent fundamentally different processes.
-For instance, word concreteness and visual strength are highly correlated.
-However, whereas visual strength indexes a perceptual component of semantic information, word concreteness might be circumscribed to the lexical level (Bottini et al., 2021), in contrast to other descriptions (Connell \& Lynott, 2012; Pexman \& Yap, 2018).
-Similarly, it was important to control for general cognition measures as covariates of vocabulary size (Ratcliff et al., 2010; also see James et al., 2018; Pexman \& Yap, 2018).
+
+In our current approach, the sensorimotor domain was represented by a single variable in each study, just as the language domain was represented by a single variable.
+In the sensorimotor domain, we focussed on the vision to its hegemonic role in the human brain (Reilly et al., 2020) as well as in several languages (Bernabeu, 2018; Chen et al., 2019; Lynott et al., 2020; Miceli et al., 2021; Morucci et al., 2019; Roque et al., 2015; Speed \& Brybaert, 2021; Speed \& Majid, 2020; Vergallito et al., 2020; Winter et al., 2018; Zhong et al., 2022).
+Notably, vision was also the domain chosen in a recent study that strongly influenced the present study (Petilli et al., 2021), as well as in previous studies (Bottini et al., 2021; De Deyne et al., 2021; Pearson \& Kosslyn, 2015; Yee et al., 2012).
+In contrast to this parsimonious approach, more comprehensive alternatives could be used in future research to consider more sensorimotor domains.
+The first of these approaches is the preselection approach, which incorporates a step prior to the main analysis.
+In this prior step, a selection is performed among a large variety of word-level information, including visual, auditory and motor information, etc.
+(Bernabeu et al., 2021).
+Selecting a single variable provides a convenient way to compare the role of sensorimotor information to that of linguistic information, if the latter is also represented by a single variable.
+The second approach is using a variable that aggregates sensorimotor information (Wingfield \& Connell, 2022b).
+Last, the third approach would be using more than one variable to represent sensorimotor information in the main analysis.
+This would complicate the analysis of interactions with other variables, as the overall number of terms in the model could quickly exceed the maximum normally encountered in mixed-effects models---that is, around 15.
+If random slopes are included for all those effects of interest (see Brauer \& Curtin, 2018; Singmann \& Kellen, 2019), the model would most likely present convergence warnings.
+In the face of this challenge, authors could either probe into those warnings (see \protect\hyperlink{appendix-B-frequentist-analysis-diagnostics}{\underline{Appendix B}}), or could opt for different method, such as linear regression or machine learning.
+Ultimately, in any selection of variables, there is a trade-off between parsimony and comprehensiveness, and negotiating this trade-off often involves a certain degree of arbitrariness.
+A time-consuming, stepwise selection can help reduce this arbitrariness (for an example, see \protect\hyperlink{appendix-A-lexical-covariates}{\underline{Appendix A}}).
+
+Insofar as both `language' and `vision' were present in the models, it is (arguably) valid to make conclusions based on them (see Louwerse, 2011; Louwerse \& Connell, 2011; Santos et al., 2011; Simmons et al., 2008).
+In contrast, when only one of these variables is analysed, it may contain information from the other variable.
+If the superiority of language is genuine---rather than due to a bogus reflection of sensorimotor information---, the present results suggest that language is the main source of information in conceptual processing, whereas sensorimotor information provides extra help, especially for higher-vocabulary individuals (see Study 2, Semantic decision) and in deeper semantic tasks (refer to task-relevance advantage above).
+As the ultimate conclusion, should sensorimotor simulation be considered smaller but nonetheless important---especially for some individuals and in some contexts---, or should it be considered a negligible by-product of conceptual processing (Mahon \& Caramazza, 2008)?
+Although the jury is still out, the present results provide support for the tenet that sensorimotor simulation is smaller yet important, especially for some individuals and in some contexts, whereas language is important across the board.
+
+Furthermore, it is necessary to acknowledge a longstanding caveat in the present topic, which also affects the present study.
+That is, it is extremely difficult to ascertain whether our variables encode what we intend for them to encode.
+Specifically, it is possible that the variables for language-based information encode some sensorimotor information, and vice versa.
+To address this caveat, future research could combine the use of continuous word-level variables---as used in the present study---with the use of brain-level measurements (see Borghesani et al., 2016).
+Specifically, such an investigation should examine whether language-based information is primarily circumscribed to the brain regions in charge of semantic retrieval---such as the posterior left inferior frontal gyrus, the right posterior inferior frontal gyrus, the left anterior superior temporal gyrus and sulcus, and the left middle and posterior middle temporal gyrus (Hagoort, 2017; Skeide \& Friederici, 2016).
+Conversely, this investigation should also examine whether vision-based information is primarily circumscribed to the brain regions in charge of visual semantic information---such as Brodmann area 17, in the occipital lobe, corresponding to primary visual cortex (Borghesani et al., 2016).
+Due to the importance of the time course, a method that provides both spatial and temporal resolution, such as magnetoencephalography, would be ideally suited for this research.
+If both sources of information are largely circumscribed to their regions of interest in the brain, we could conclude that the variables are valid.
+In contrast, if there are \emph{drifts} in the processing---whereby language-based information is consistently associated with activation in primary visual cortex, or whereby vision-based information is associated with activation in the language regions of interest---, we would need to question the validity of the variables.
+
+As an alternative to the above design, a thriftier method would be available by using two clusters of covariates.
+One of these clusters would be primarily associated with language-based information, whereas the other cluster would be primarily associated with vision-based information.\footnote{Thank you to Prof.~Max Louwerse for suggesting this idea.} This research should examine whether the variables in each cluster all behave similarly, or whether---instead---there are any drifts between the language and vision.
+As in the above design, the absence of drifts would validate the operationalisation of the two sides in the dichotomy, whereas the presence of drifts would question the validity.
+
+The present analysis controlled important sources of variance in the fixed effects and in the random effects.
+First, in the fixed effects, covariates such as word concreteness and individual differences in general cognition were included in the models.
+It was important to include these covariates as they were substantially correlated with some of our variables of interest, and research has suggested that these covariates may represent fundamentally different processes from those of our variables of interest.
+For instance, word concreteness and visual strength were highly correlated.
+However, whereas visual strength indexes a perceptual component of semantic information, word concreteness might be circumscribed to the lexical level, which does not require the processing of meaning (Bottini et al., 2021; cf.
+Connell \& Lynott, 2012; Pexman \& Yap, 2018).
+Similarly, it was important to control for individual differences in general cognition measures as covariates of vocabulary size (Ratcliff et al., 2010; also see James et al., 2018; Pexman \& Yap, 2018).
+We contend that controlling (or, in other words, statistically adjusting) for important covariates is a valuable asset of our present research.
+Furthermore, we think that the number of covariates we selected was enough but not excessive.
+We did not find any signs of overfitting in the models, as the variables that have been consistently influential in the literature were also influential in our current models.
+To further delve into the role of covariates in conceptual processing, we think that it would be valuable to investigate how the presence and the absence of several covariates in a model can affect the effect sizes and the significance results.\footnote{Thank you to Prof.~Max Louwerse for this idea.} Indeed, the differences between the results of Study 1 (semantic priming) and the results of Petilli et al.
+(2021) suggested that the influence of covariates can be very important.
+However, because these analyses differed in other aspects of the models, a study focussed on covariates would be insightful (see Botvinik-Nezer et al., 2020; Perret \& Bonin, 2019; Wagenmakers et al., 2022).
+
+Second, in the random effects, the models contained a maximal structure that accounted for far more variance than the fixed effects, thus providing for a conservative analysis.
+Indeed, the maximal random-effects structure served to impede a violation of the independence of observations (Barr et al., 2013; Brauer \& Curtin, 2018; Singmann \& Kellen, 2019).
+Specifically, random intercepts and slopes ensured that sources of dependence such as participants and stimuli were kept outside of the fixed effects, which are the relevant effects for the conclusions of this (and most other) research in conceptual processing.
 
@@
 This finding replicates some of the previous literature (Petilli et al., 2021) while highlighting the importance of the time course and the level of semantic processing.
-That is, although the finding seems to be at odds with the theory that perceptual simulation peaks after language-based associations (Barsalou et al., 2008; Louwerse \& Connell, 2011), the long SOA may have been too long for perceptual simulation to be maintained in the lexical decision task that was performed by participants, which is semantically shallow {[}Petilli et al.
-(2021); see `Future directions' below{]}.
-
-\hypertarget{human-based-and-computational-measures-of-vision-based-information-1}{%
-\subsection{Human-based and computational measures of vision-based information}\label{human-based-and-computational-measures-of-vision-based-information-1}}
+That is, although the finding seems to be at odds with the theory that perceptual simulation peaks after language-based associations (Barsalou et al., 2008; Louwerse \& Connell, 2011), the long SOA may have been too long for perceptual simulation to be maintained in the lexical decision task that was performed by participants, which is semantically shallow (Petilli et al., 2021).
+
+\hypertarget{operationalisation-of-variables-and-other-analytical-choices}{%
+\subsection{Operationalisation of variables and other analytical choices}\label{operationalisation-of-variables-and-other-analytical-choices}}
 
@@
 The results revealed that both measures---including their interactions with other variables---produced similar effect sizes.
-This underscores the consistency that exists between human ratings and computational approximations to meaning (e.g., Charbonnier \& Wartena, 2019, 2020; Günther et al., 2016b; Louwerse et al., 2015; Mandera et al., 2017; Petilli et al., 2021; Solovyev, 2021; Wingfield \& Connell, 2022).
-Nonetheless, only the effect of the human-based variable was significant, and its effect size was slightly larger, which is consistent with previous comparisons of human-based and computational measures (De Deyne et al., 2016, 2019; Gagné et al., 2016; Schmidtke et al., 2018; cf.
+This underscores the consistency that exists between human ratings and computational approximations to meaning (e.g., Charbonnier \& Wartena, 2019, 2020; Günther et al., 2016b; Louwerse et al., 2015; Mandera et al., 2017; Petilli et al., 2021; Solovyev, 2021; Wingfield \& Connell, 2022a).
+However, the effect of the human-based variable was slightly larger, which is consistent with previous comparisons of human-based and computational measures (De Deyne et al., 2016, 2019; Gagné et al., 2016; Schmidtke et al., 2018; cf.
 Michaelov et al., 2022; Snefjella \& Blank, 2020).
 
-Furthermore, the present comparison demonstrates the influence of measurement instruments on results, and their potential to act as confounds.
-Critically, the literature contains many comparisons of text-based variables (De Deyne et al., 2016, 2013; Günther et al., 2016a, 2016b; M.
+In contrast to the results of Petilli et al.
+(2021), vision-based similarity did not significantly interact with SOA.
+Furthermore, in contrast to the main analysis, this sub-analysis did not present a significant interaction between language-based similarity and SOA.
+These two differences demonstrate how the results of our analyses can be critically influenced by analytical choices such as the operationalisation of variables and the degree of complexity of statistical models.
+In this regard, we must draw attention to an often-overlooked difference between the variables used to operationalise the language system---usually, text-based measures based on large corpora---and the variables used to operationalise the embodiment system---usually, human-based measures based on ratings.
+Critically, the literature contains many comparisons of text-based variables (De Deyne et al., 2013, 2016; Günther et al., 2016a, 2016b; M.
 N.
-Jones et al., 2006; Lund \& Burgess, 1996; Mandera et al., 2017; Mikolov et al., 2013; Wingfield \& Connell, 2022), whereas the work on embodiment variables is more sparse and tends to compare different \emph{modalities}---e.g., valence, visual strength, auditory strength, etc.
+Jones et al., 2006; Lund \& Burgess, 1996; Mandera et al., 2017; Mikolov et al., 2013; Wingfield \& Connell, 2022a), whereas the work on embodiment variables is more sparse and tends to compare different \emph{modalities}---e.g., valence, visual strength, auditory strength, etc.
 (Lynott et al., 2020; Lynott \& Connell, 2009; Newcombe et al., 2012; for an exception, see Vergallito et al., 2020).
 This accident of history might in part account for the superiority of linguistic information over embodied information (see Banks et al., 2021; Kiela \& Bottou, 2014; Lam et al., 2015; Louwerse et al., 2015; Pecher et al., 1998; Petilli et al., 2021).
-Therefore, it will be important to consider whether \emph{engineering work} should be devoted to the betterment of embodiment variables.
+Therefore, it may be important to consider whether \emph{engineering work} should be devoted to the betterment of embodiment variables.
+On a more general conclusion, the present results suggest that research findings are fundamentally dependent on research methods.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-borghesaniWordMeaningVentral2016}{}}%
+Borghesani, V., Pedregosa, F., Buiatti, M., Amadon, A., Eger, E., \& Piazza, M.
+(2016).
+Word meaning in the ventral visual path: {A} perceptual to conceptual gradient of semantic coding.
+\emph{NeuroImage}, \emph{143}, 128--140.
+\url{https://doi.org/10.1016/j.neuroimage.2016.08.068}
+
 \leavevmode\vadjust pre{\hypertarget{ref-borghiWordsSocialTools2019}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-charbonnierPredictingWordConcreteness2019}{}}%
+Charbonnier, J., \& Wartena, C.
+(2019).
+Predicting word concreteness and imagery.
+\emph{Proceedings of the 13th {International Conference} on {Computational Semantics} - {Long Papers}}, 176--187.
+\url{https://doi.org/10.18653/v1/W19-0415}
+
 \leavevmode\vadjust pre{\hypertarget{ref-charbonnierPredictingConcretenessGerman2020}{}}%
@@
 \url{https://doi.org/10.25968/opus-2075}
-
-\leavevmode\vadjust pre{\hypertarget{ref-charbonnierPredictingWordConcreteness2019}{}}%
-Charbonnier, J., \& Wartena, C.
-(2019).
-Predicting word concreteness and imagery.
-\emph{Proceedings of the 13th {International Conference} on {Computational Semantics} - {Long Papers}}, 176--187.
-\url{https://doi.org/10.18653/v1/W19-0415}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-NIPS2013_7cce53cf}{}}%
+Frome, A., Corrado, G.
+S., Shlens, J., Bengio, S., Dean, J., Ranzato, M., \& Mikolov, T.
+(2013).
+{DeViSE}: {A} deep visual-semantic embedding model.
+In C.
+J.
+Burges, L.
+Bottou, M.
+Welling, Z.
+Ghahramani, \& K.
+Q.
+Weinberger (Eds.), \emph{Advances in neural information processing systems} (Vol.
+26).
+{Curran Associates, Inc.} \url{https://proceedings.neurips.cc/paper/2013/file/7cce53cf90577442771720a370c3c723-Paper.pdf}
+
 \leavevmode\vadjust pre{\hypertarget{ref-gagneProcessingEnglishCompounds2016}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-LSAfun}{}}%
+Günther, F., Dudschig, C., \& Kaup, B.
+(2015).
+LSAfun: An r package for computations based on latent semantic analysis.
+\emph{Behavior Research Methods}, \emph{47}(4), 930--944.
+\url{https://doi.org/10.3758/s13428-014-0529-0}
+
 \leavevmode\vadjust pre{\hypertarget{ref-guenther2016a}{}}%
@@
 \url{https://doi.org/10.3389/fpsyg.2016.01646}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hagoortCoreLanguagereadyBrain2017}{}}%
+Hagoort, P. (2017). The core and beyond in the language-ready brain. \emph{Neuroscience \& Biobehavioral Reviews}, \emph{81}, 194--204. \url{https://doi.org/10.1016/j.neubiorev.2017.01.048}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-louwerseSymbolInterdependencySymbolic2011}{}}%
+Louwerse, M. M. (2011). Symbol interdependency in symbolic and embodied cognition. \emph{Topics in Cognitive Science}, \emph{3}(2), 273--302. \url{https://doi.org/10.1111/j.1756-8765.2010.01106.x}
+
 \leavevmode\vadjust pre{\hypertarget{ref-louwerseTasteWordsLinguistic2011}{}}%
@@
 \url{https://doi.org/10.1080/23273798.2014.981552}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-sjPlot}{}}%
+Lüdecke, D. (2021). \emph{sjPlot: Data visualization for statistics in social science}. \url{https://CRAN.R-project.org/package=sjPlot}
 
@@
 \url{https://doi.org/10.1027/1864-9335/a000187}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mahonCriticalLookEmbodied2008}{}}%
+Mahon, B.
+Z., \& Caramazza, A.
+(2008).
+A critical look at the embodied cognition hypothesis and a new proposal for grounding conceptual content.
+\emph{Journal of Physiology-Paris}, \emph{102}(1), 59--70.
+\url{https://doi.org/10.1016/j.jphysparis.2008.03.004}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-moranPosteriorPredictiveNull2021}{}}%
-Moran, G. E., Cunningham, J. P., \& Blei, D. M. (2021). \emph{Posterior predictive null checks} (No. arXiv:2112.03333). {arXiv}. \url{https://doi.org/10.48550/arXiv.2112.03333}
+\leavevmode\vadjust pre{\hypertarget{ref-moranPosteriorPredictiveNull2022}{}}%
+Moran, G. E., Cunningham, J. P., \& Blei, D. M. (2022). The posterior predictive null. \emph{Bayesian Analysis}, \emph{-1}. \url{https://doi.org/10.1214/22-BA1313}
 
@@
 \url{https://doi.org/10.3389/fnhum.2012.00275}
+
+\leavevmode\vadjust pre{\hypertarget{ref-noahWhenBothOriginal2018}{}}%
+Noah, T., Schul, Y., \& Mayo, R.
+(2018).
+When both the original study and its failed replication are correct: {Feeling} observed eliminates the facial-feedback effect.
+\emph{Journal of Personality and Social Psychology}, \emph{114}, 657--664.
+\url{https://doi.org/10.1037/pspa0000121}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-perretWhichVariablesShould2019}{}}%
+Perret, C., \& Bonin, P.
+(2019).
+Which variables should be controlled for to investigate picture naming in adults?
+{A Bayesian} meta-analysis.
+\emph{Behavior Research Methods}, \emph{51}(6), 2533--2545.
+\url{https://doi.org/10.3758/s13428-018-1100-1}
+
 \leavevmode\vadjust pre{\hypertarget{ref-petilli2021a}{}}%
@@
 (2022).
-The nature of word associations in sentence contexts.
+The {Nature} of {Word Associations} in {Sentence Contexts}.
 \emph{Experimental Psychology}.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-GGally}{}}%
+Schloerke, B., Cook, D., Larmarange, J., Briatte, F., Marbach, M., Thoen, E., Elberg, A., \& Crowley, J. (2021). \emph{GGally: Extension to 'ggplot2'}. \url{https://CRAN.R-project.org/package=GGally}
+
 \leavevmode\vadjust pre{\hypertarget{ref-schmalzWhatBayesFactor2021}{}}%
@@
 {Psychology Press}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-skeideOntogenyCorticalLanguage2016}{}}%
+Skeide, M. A., \& Friederici, A. D. (2016). The ontogeny of the cortical language network. \emph{Nature Reviews Neuroscience}, \emph{17}(5, 5), 323--332. \url{https://doi.org/10.1038/nrn.2016.23}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-tidyverse}{}}%
+Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
+D., François, R., Grolemund, G., Hayes, A., Henry, L., Hester, J., Kuhn, M., Pedersen, T.
+L., Miller, E., Bache, S.
+M., Müller, K., Ooms, J., Robinson, D., Seidel, D.
+P., Spinu, V., \ldots{} Yutani, H.
+(2019).
+Welcome to the {tidyverse}.
+\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
+\url{https://doi.org/10.21105/joss.01686}
+
 \leavevmode\vadjust pre{\hypertarget{ref-williamsImprovingPsychologicalScience2014}{}}%
@@
 Wingfield, C., \& Connell, L.
-(2022).
+(2022a).
 Understanding the role of linguistic distributional knowledge in cognition.
@@
 \url{https://doi.org/10.1080/23273798.2022.2069278}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wingfieldSensorimotorDistanceGrounded2022}{}}%
+Wingfield, C., \& Connell, L.
+(2022b).
+Sensorimotor distance: {A} grounded measure of semantic similarity for 800 million concept pairs.
+\emph{Behavior Research Methods}.
+\url{https://doi.org/10.3758/s13428-022-01965-7}
 
@@
 
-Lexical covariates are usually used in conceptual processing studies due to the widespread connections among lexical and semantic variables (Petilli et al., 2021; e.g., Pexman \& Yap, 2018; Wingfield \& Connell, 2022).
+Lexical covariates are usually used in conceptual processing studies due to the widespread connections among lexical and semantic variables (Petilli et al., 2021; e.g., Pexman \& Yap, 2018; Wingfield \& Connell, 2022a).
 Including these covariates---or nuisance variables---in the model allows a more rigorous analysis of the predictors of interest (Sassenhagen \& Alday, 2016).
-In each of the present studies, the covariates were selected out of a group of five variables that had been used as covariates in Wingfield and Connell (2022), and are widely used (e.g., Petilli et al., 2021).
+In each of the present studies, the covariates were selected out of a group of five variables that had been used as covariates in Wingfield and Connell (2022a), and are widely used (e.g., Petilli et al., 2021).
 Some of these covariates were highly intercorrelated (\(r\) \textgreater{} .70), as shown below.
@@
 
-In Studies 1 (semantic priming) and 2 (semantic decision), the lexical covariates were selected out of five variables, which mirrored those used by Wingfield and Connell (2022): namely, number of letters (i.e., orthographic length, which we computed in R), word frequency, number of syllables (both the latter from Balota et al., 2007), orthographic Levenshtein distance (Yarkoni et al., 2008) and phonological Levenshtein distance (Suárez et al., 2011; Yap \& Balota, 2009).
+In Studies 1 (semantic priming) and 2 (semantic decision), the lexical covariates were selected out of five variables, which mirrored those used by Wingfield and Connell (2022a): namely, number of letters (i.e., orthographic length, which we computed in R), word frequency, number of syllables (both the latter from Balota et al., 2007), orthographic Levenshtein distance (Yarkoni et al., 2008) and phonological Levenshtein distance (Suárez et al., 2011; Yap \& Balota, 2009).
 In Study 3 (lexical decision), the procedure was more particular, as it served two purposes.
@@
 
-{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/model_diagnostics/plots/main_effects_semanticpriming_allFit_convergence}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/model_diagnostics/plots/main_effects_semanticpriming_allFit_convergence}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/model_diagnostics/plots/interactions_semanticpriming_allFit_convergence}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/model_diagnostics/plots/interactions_semanticpriming_allFit_convergence}
 
@@
 
-{\centering \includegraphics[width=0.65\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/model_diagnostics/plots/semanticpriming_residuals}
+{\centering \includegraphics[width=0.65\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/model_diagnostics/plots/semanticpriming_residuals}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/analysis_with_visualsimilarity/model_diagnostics/plots/main_effects_semanticpriming_with_visualsimilarity_allFit_convergence}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/analysis_with_visualsimilarity/model_diagnostics/plots/main_effects_semanticpriming_with_visualsimilarity_allFit_convergence}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/analysis_with_visualsimilarity/model_diagnostics/plots/interactions_semanticpriming_with_visualsimilarity_allFit_convergence}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/analysis_with_visualsimilarity/model_diagnostics/plots/interactions_semanticpriming_with_visualsimilarity_allFit_convergence}
 
@@
 
-{\centering \includegraphics[width=0.65\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/analysis_with_visualsimilarity/model_diagnostics/plots/semanticpriming_with_visualsimilarity_residuals}
+{\centering \includegraphics[width=0.65\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/analysis_with_visualsimilarity/model_diagnostics/plots/semanticpriming_with_visualsimilarity_residuals}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/model_diagnostics/plots/main_effects_semanticdecision_allFit_convergence}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/model_diagnostics/plots/main_effects_semanticdecision_allFit_convergence}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/model_diagnostics/plots/interactions_semanticdecision_allFit_convergence}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/model_diagnostics/plots/interactions_semanticdecision_allFit_convergence}
 
@@
 
-{\centering \includegraphics[width=0.65\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/model_diagnostics/plots/semanticdecision_residuals}
+{\centering \includegraphics[width=0.65\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/model_diagnostics/plots/semanticdecision_residuals}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/model_diagnostics/plots/main_effects_lexicaldecision_allFit_convergence}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/model_diagnostics/plots/main_effects_lexicaldecision_allFit_convergence}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/model_diagnostics/plots/interactions_lexicaldecision_allFit_convergence}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/model_diagnostics/plots/interactions_lexicaldecision_allFit_convergence}
 
@@
 
-{\centering \includegraphics[width=0.65\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/model_diagnostics/plots/lexicaldecision_residuals}
+{\centering \includegraphics[width=0.65\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/model_diagnostics/plots/lexicaldecision_residuals}
 
@@
 Furthermore, in each of these checks, the models presented first have the default Gaussian distribution, whereas the next series have an exponentially modified Gaussian (dubbed `ex-Gaussian') distribution with an identity link function (for details, see the section titled `Distributions and prior predictive checks' in the main text).
-Eyeball estimation is used to assess the outcomes of these checks (for background on predictive checks and for alternative estimation procedures, see Gelman et al., 1996; Moran et al., 2021; Schoot et al., 2021).
+Eyeball estimation is used to assess the outcomes of these checks (for background on predictive checks and for alternative estimation procedures, see Gelman et al., 1996; Moran et al., 2022; Schoot et al., 2021).
 One diagnostic not shown in this appendix is the \(\widehat R\), which is shown in \protect\hyperlink{appendix-E-Bayesian-analysis-results}{\underline{Appendix E}} instead.
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_informativepriors}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_informativepriors}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_weaklyinformativepriors}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_weaklyinformativepriors}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_diffusepriors}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_diffusepriors}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_informativepriors_exgaussian}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_informativepriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_weaklyinformativepriors_exgaussian}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_weaklyinformativepriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_diffusepriors_exgaussian}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_diffusepriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/posterior_predictive_checks/plots/semanticpriming_posteriorpredictivechecks_allpriors_exgaussian}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/posterior_predictive_checks/plots/semanticpriming_posteriorpredictivechecks_allpriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_informativepriors}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_informativepriors}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_weaklyinformativepriors}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_weaklyinformativepriors}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_diffusepriors}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_diffusepriors}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_informativepriors_exgaussian}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_informativepriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_weaklyinformativepriors_exgaussian}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_weaklyinformativepriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_diffusepriors_exgaussian}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_diffusepriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/posterior_predictive_checks/plots/semanticdecision_posteriorpredictivechecks_allpriors_exgaussian}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/posterior_predictive_checks/plots/semanticdecision_posteriorpredictivechecks_allpriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_informativepriors}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_informativepriors}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_weaklyinformativepriors}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_weaklyinformativepriors}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_diffusepriors}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_diffusepriors}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_informativepriors_exgaussian}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_informativepriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_weaklyinformativepriors_exgaussian}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_weaklyinformativepriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_diffusepriors_exgaussian}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_diffusepriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/posterior_predictive_checks/plots/lexicaldecision_posteriorpredictivechecks_allpriors_exgaussian}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/posterior_predictive_checks/plots/lexicaldecision_posteriorpredictivechecks_allpriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=0.85\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-attentional-control}
+{\centering \includegraphics[width=0.85\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-attentional-control}
 
@@
 
-{\centering \includegraphics[width=0.7\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interaction-word-concreteness-difference-SOA}
+{\centering \includegraphics[width=0.7\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interaction-word-concreteness-difference-SOA}
 
@@
 
-{\centering \includegraphics[width=0.9\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interaction-word-concreteness-difference-vocabulary-size}
+{\centering \includegraphics[width=0.9\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interaction-word-concreteness-difference-vocabulary-size}
 
@@
 
-{\centering \includegraphics[width=0.7\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interaction-word-concreteness-difference-gender}
+{\centering \includegraphics[width=0.7\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interaction-word-concreteness-difference-gender}
 
@@
 
-{\centering \includegraphics[width=0.95\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/plots/semanticdecision-interactions-with-information-uptake}
+{\centering \includegraphics[width=0.95\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/plots/semanticdecision-interactions-with-information-uptake}
 
@@
 
-{\centering \includegraphics[width=0.9\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/plots/lexicaldecision-interaction-word-concreteness-vocabulary-age}
+{\centering \includegraphics[width=0.9\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/plots/lexicaldecision-interaction-word-concreteness-vocabulary-age}
 
@@
 
-{\centering \includegraphics[width=0.65\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/plots/lexicaldecision-interaction-word-concreteness-gender}
+{\centering \includegraphics[width=0.65\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/plots/lexicaldecision-interaction-word-concreteness-gender}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_bayesian_plots/plots/semanticpriming_frequentist_bayesian_plot_allpriors_exgaussian}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_bayesian_plots/plots/semanticpriming_frequentist_bayesian_plot_allpriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_bayesian_plots/plots/semanticdecision_frequentist_bayesian_plot_allpriors_exgaussian}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_bayesian_plots/plots/semanticdecision_frequentist_bayesian_plot_allpriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{/Users/pablodejuanbernabeu/Library/CloudStorage/OneDrive-LancasterUniversity/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_bayesian_plots/plots/lexicaldecision_frequentist_bayesian_plot_allpriors_exgaussian}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_bayesian_plots/plots/lexicaldecision_frequentist_bayesian_plot_allpriors_exgaussian}
 

### 2022-10-23 manuscript/appendix-B-frequentist-analysis-diagnostics.Rmd
23102022

@@
 Even though linear mixed-effects models tend to be quite robust to deviations from normality [@kniefViolatingNormalityAssumption2021; @schielzethRobustnessLinearMixed2020], we sought to verify our results.
-To this end, two robust models were performed in each study, as described below.
+To this end, we attempted to run robust models using two methods, neither of which worked.
+The methods are nonetheless described below.
 
@@
 
-The first method uses the R package 'robustlmm' v2.4-4 [@R-robustlmm].
-To calculate the p values, we followed the procedure of @sleegersPupillometryHindsightBias2021, but used the Kenward-Roger method instead of Satterthwaite [see @luke2017a].
+The first method drew on the R package 'robustlmm' v2.4-4 [@R-robustlmm].
+To calculate the $p$ values, we followed the procedure of @sleegersPupillometryHindsightBias2021, but used the Kenward-Roger method instead of Satterthwaite [see @luke2017a].
 
@@
 
-We followed a method proposed by @loTransformNotTransform2015, based on generalized linear mixed-effects models (GLMM) implementing an identity link function.
+In the second approach, we followed a method proposed by @loTransformNotTransform2015, based on generalized linear mixed-effects models (GLMM) implementing an identity link function.
 According to @loTransformNotTransform2015, the link function helps avoid directly transforming the dependent variable, which can hinder the interpretability of the results [also see @kniefViolatingNormalityAssumption2021].
@@
 
-*P* values were to be calculated through parametric bootstrapping, which is the most robust method for GLMMs, as the Kenward-Roger and Satterthwaite methods are not available for these models [@luke2017a; @R-afex].
+$P$ values were to be calculated through parametric bootstrapping, which is the most robust method for GLMMs, as the Kenward-Roger and Satterthwaite methods are not available for these models [@luke2017a; @R-afex].
 
-Neither Method A nor Method B could finally be used, as the code produced errors.
-These errors are shown in the corresponding scripts inside the 'model_diagnostics' folder in each study.
-Nonetheless, the residuals are shown below.
+Neither Method A nor Method B could finally be used, as the code produced errors. These errors are shown in the corresponding scripts inside the 'model_diagnostics' folder in each study.
+
+The residuals of the final models are shown in the corresponding sections below.
 

### 2022-10-23 manuscript/manuscript.tex
23102022

@@
 Even though linear mixed-effects models tend to be quite robust to deviations from normality (Knief \& Forstmeier, 2021; Schielzeth et al., 2020), we sought to verify our results.
-To this end, two robust models were performed in each study, as described below.
+To this end, we attempted to run robust models using two methods, neither of which worked.
+The methods are nonetheless described below.
 
@@
 
-The first method uses the R package `robustlmm' v2.4-4 (Koller, 2016).
-To calculate the p values, we followed the procedure of Sleegers et al.
+The first method drew on the R package `robustlmm' v2.4-4 (Koller, 2016).
+To calculate the \(p\) values, we followed the procedure of Sleegers et al.
 (2021), but used the Kenward-Roger method instead of Satterthwaite (see Luke, 2017).
@@
 
-We followed a method proposed by Lo and Andrews (2015), based on generalized linear mixed-effects models (GLMM) implementing an identity link function.
+In the second approach, we followed a method proposed by Lo and Andrews (2015), based on generalized linear mixed-effects models (GLMM) implementing an identity link function.
 According to Lo and Andrews (2015), the link function helps avoid directly transforming the dependent variable, which can hinder the interpretability of the results (also see Knief \& Forstmeier, 2021).
@@
 
-\emph{P} values were to be calculated through parametric bootstrapping, which is the most robust method for GLMMs, as the Kenward-Roger and Satterthwaite methods are not available for these models (Luke, 2017; Singmann et al., 2021).
-
-Neither Method A nor Method B could finally be used, as the code produced errors.
-These errors are shown in the corresponding scripts inside the `model\_diagnostics' folder in each study.
-Nonetheless, the residuals are shown below.
+\(P\) values were to be calculated through parametric bootstrapping, which is the most robust method for GLMMs, as the Kenward-Roger and Satterthwaite methods are not available for these models (Luke, 2017; Singmann et al., 2021).
+
+Neither Method A nor Method B could finally be used, as the code produced errors. These errors are shown in the corresponding scripts inside the `model\_diagnostics' folder in each study.
+
+The residuals of the final models are shown in the corresponding sections below.
 

### 2022-10-24 manuscript/manuscript.Rmd
24102022

@@
 
-  This manuscript is a draft and includes some appendices.
+  This manuscript is a draft.
 Correspondence can be addressed to Pablo Bernabeu on pcbernabeu@gmail.com.
-All materials are available at [http://doi.org/10.17605/OSF.IO/UERYQ](http://doi.org/10.17605/OSF.IO/UERYQ).
+All the materials needed to inspect and reproduce the present research---comprising documentation, data, analysis and results---are available at [http://doi.org/10.17605/OSF.IO/UERYQ](http://doi.org/10.17605/OSF.IO/UERYQ).
 
 abstract: |
-   Research over the past two decades has suggested that conceptual processing depends on both language-based and vision-based information.
-We tested this interplay at three levels of the data: individuals, words and tasks.
-To this aim, we drew on three existing data sets that were composed of large samples, and implemented the paradigms of semantic priming, semantic decision and lexical decision.
-After extending these data sets with language-based and vision-based measures, we performed the analysis using mixed-effects models that included a comprehensive array of fixed effects---including covariates---and random effects.
-Overall, language-based information was found to be more important than vision-based information.
-Furthermore, in the semantic priming study---whose task required distinguishing between words and nonwords---, both language-based and vision-based information were more influential when words were presented faster.
-In addition, higher-vocabulary participants presented a greater effect of language-based similarity than lower-vocabulary participants.
-In contrast, this pattern did not hold for vision-based information, which was less relevant to the task.
-The 'relevance advantage' in higher-vocabulary participants also appeared in the semantic decision and the lexical decision studies.
-Furthermore, we compare the effects of two visual information measures, and discuss the role of measurement instruments in this research topic.
-Lastly, we estimated the sample size required to reliably examine each effect of interest.
-We found that 300 participants suffice to examine language-based information contained in words, whereas more than 1,000 participants are necessary to examine vision-based information as well as the interactions between both the former variables and vocabulary size, gender and presentation speed.
+  Research has suggested that conceptual processing depends on both language-based and vision-based information.
+We tested this interplay at three levels of the experimental structure: individuals, words and tasks.
+To this end, we drew on three existing, large data sets that implemented the paradigms of semantic priming, semantic decision and lexical decision.
+We extended these data sets with measures of language-based and vision-based information, and analysed how the latter variables interacted with participants' vocabulary size and gender, and also with presentation speed in the semantic priming study.
+We performed the analysis using mixed-effects models that included a comprehensive array of fixed effects---including covariates---and random effects.
+First, we found that language-based information was more important than vision-based information.
+Second, in the semantic priming study---whose task required distinguishing between words and nonwords---, both language-based and vision-based information were more influential when words were presented faster.
+Third, a 'task-relevance advantage' was identified in higher-vocabulary participants.
+Specifically, in lexical decision, higher-vocabulary participants were more sensitive to language-based information than lower-vocabulary participants.
+In contrast, in semantic decision, higher-vocabulary participants were more sensitive to word concreteness.
+Fourth, we demonstrated the influence of the analytical method on the results.
+These findings support the interplay between language and vision in conceptual processing, and demonstrate the influence of measurement instruments on the results.
+Last, we estimated the sample size required to reliably investigate various effects.
+We found that 300 participants were sufficient to examine the effect of language-based information contained in words, whereas more than 1,000 participants were necessary to examine the effect of vision-based information and the interactions of both former variables with vocabulary size, gender and presentation speed.
+In conclusion, this power analysis reveals the need to increase sample sizes when conducting research on perceptual simulation and individual differences.
 
@@
   papaja::apa6_pdf:
-    extra_dependencies: ["flafter"]   # Place figures and tables below where they are first mentioned in the text.
+    extra_dependencies: ['flafter']   # Place tables and figures below where they are first mentioned in the text.
 
@@
 header-includes: 
-# Background on the first four lines: https://stackoverflow.com/a/70658799/7050882
+# Background on the first 4 lines: https://stackoverflow.com/a/70658799/7050882
   - \renewcommand\author[1]{}
@@
   - \renewcommand{\floatpagefraction}{.6}   # Reduce page margins
-  - \setlength{\@fptop}{0pt}                # Vertically-align tables & figures to the top
+  - \setlength{\@fptop}{0pt}                # Vertically-align tables and figures to the top
   - \setcounter{topnumber}{3}               # Reduce page margins
@@
   - \setcounter{totalnumber}{4}             # Reduce page margins
+  - \usepackage{placeins}                   # Allow use of `\FloatBarrier` to position tables and figures
   - \usepackage{amsmath}                    # Maths formatting
@@
 library(knitr)        # Document rendering
-options(kableExtra.latex.load_packages = FALSE)  # instead, LaTeX packages loaded in header/preamble above
+options(kableExtra.latex.load_packages = FALSE,   # instead, LaTeX packages loaded in header/preamble above
+        knitr.graphics.rel_path = FALSE)          # avoid warning (https://github.com/yihui/knitr/issues/2119#issuecomment-1092411877)
+knitr::opts_knit$set(root.dir = '../')            # move working directory to the project root
 library(kableExtra)   # Tables
@@
 
-# Move working directory to the project root
-knitr::opts_knit$set(root.dir = '../')
-
 ```
@@
 
-# Subset of the semantic priming study that included visual similarity.
+# Subset of the semantic priming study that included vision-based similarity.
 # Code for data set below in 'semanticpriming/data' folder
@@
 # Code for models below in 'semanticpriming/bayesian_analysis' folder
-semanticpriming_summary_informativepriors_exgaussian =   # Primary model object
+semanticpriming_summary_informativepriors_exgaussian = 
   readRDS('semanticpriming/bayesian_analysis/results/semanticpriming_summary_informativepriors_exgaussian.rds')
-# semanticpriming_summary_weaklyinformativepriors_exgaussian =   # Primary model object
-#   readRDS('semanticpriming/bayesian_analysis/results/semanticpriming_summary_weaklyinformativepriors_exgaussian.rds')
-semanticpriming_summary_diffusepriors_exgaussian =   # Primary model object
+semanticpriming_summary_weaklyinformativepriors_exgaussian = 
+  readRDS('semanticpriming/bayesian_analysis/results/semanticpriming_summary_weaklyinformativepriors_exgaussian.rds')
+semanticpriming_summary_diffusepriors_exgaussian = 
   readRDS('semanticpriming/bayesian_analysis/results/semanticpriming_summary_diffusepriors_exgaussian.rds')
@@
 # Code for models below in 'semanticdecision/bayesian_analysis' folder
-semanticdecision_summary_informativepriors_exgaussian =   # Primary model object
+semanticdecision_summary_informativepriors_exgaussian = 
   readRDS('semanticdecision/bayesian_analysis/results/semanticdecision_summary_informativepriors_exgaussian.rds')
-semanticdecision_summary_weaklyinformativepriors_exgaussian =   # Primary model object
+semanticdecision_summary_weaklyinformativepriors_exgaussian = 
   readRDS('semanticdecision/bayesian_analysis/results/semanticdecision_summary_weaklyinformativepriors_exgaussian.rds')
-semanticdecision_summary_diffusepriors_exgaussian =   # Primary model object
+semanticdecision_summary_diffusepriors_exgaussian = 
   readRDS('semanticdecision/bayesian_analysis/results/semanticdecision_summary_diffusepriors_exgaussian.rds')
@@
 # Code for models below in 'lexicaldecision/bayesian_analysis' folder
-lexicaldecision_summary_informativepriors_exgaussian =   # Primary model object
+lexicaldecision_summary_informativepriors_exgaussian = 
   readRDS('lexicaldecision/bayesian_analysis/results/lexicaldecision_summary_informativepriors_exgaussian.rds')
-lexicaldecision_summary_weaklyinformativepriors_exgaussian =   # Primary model object
+lexicaldecision_summary_weaklyinformativepriors_exgaussian = 
   readRDS('lexicaldecision/bayesian_analysis/results/lexicaldecision_summary_weaklyinformativepriors_exgaussian.rds')
-lexicaldecision_summary_diffusepriors_exgaussian =   # Primary model object
+lexicaldecision_summary_diffusepriors_exgaussian = 
   readRDS('lexicaldecision/bayesian_analysis/results/lexicaldecision_summary_diffusepriors_exgaussian.rds')
@@
 
-Over the past decades, research in psycholinguistics has suggested that conceptual processing depends on both language and embodiment systems [@barsalouLanguageSimulationConceptual2008; @louwerseSymbolInterdependencySymbolic2011; @connell2013a].
-A comprehensive approach to both these systems requires a direct comparison of them.
-Studies tackling such a comparison have found that the systems are selectively engaged, following contextual demands [@connell2013a; @louwerseTasteWordsLinguistic2011; @ostarekTaskdependentCausalRole2017; @petilli2021a].
-For instance, the role of perceptual simulation appears to be augmented in slower responses [@louwerseTasteWordsLinguistic2011], when words are presented more slowly [@lam2015a], and in tasks prompting deeper semantic processing [@connell2013a; @louwerseTasteWordsLinguistic2011; @ostarekTaskdependentCausalRole2017; @petilli2021a].
-
-In spite of the amount of evidence favouring the interplay between language and embodiment, there are at least 2 reasons to continue testing the interplay theory.
-Firstly, the coexistence of several systems in a scientific theory must be thoroughly justified, due to the value of simplicity, as epitomised by Occam's razor [@galleseBrainConceptsRole2005; @tillmanHowSharpOccam2015].
-This point is particularly pressing because the language system has consistently produced larger effect sizes than the embodiment system [@lam2015a; @pecherDoesPizzaPrime1998; @petilli2021a; @banksLinguisticDistributionalKnowledge2021; @kiela2014a; @louwerse2015a].
-Consequently, in this research question, we examine whether the interplay between linguistic and visual processing holds in the expected directions and at multiple levels of the experimental structure.
-
-Secondly, mixed evidence has appeared regarding some aspects of the interplay.
-For instance, whereas some studies have suggested that the language system is activated before the embodiment system [@lam2015a; @louwerseTasteWordsLinguistic2011], a recent study found the opposite pattern in a lexical decision task [@petilli2021a].
-Similarly, some evidence has suggested that high-vocabulary participants are more sensitive to linguistic features [@yap2017a], whereas other evidence has suggested the opposite [@yapIndividualDifferencesJoint2009; @yap2012a].
-Another case of mixed evidence regards gender: whereas some evidence has suggested that female participants draw on the language system more prominently than males [@hutchinson2013a], other research has suggested that this difference is negligible in the general population [@wallentinChapterGenderDifferences2020].
-Presumably, the scarcity of statistical power that has ailed some studies in cognitive psychology and neuroscience [@vasishthHowEmbraceVariation2021; @marekReproducibleBrainwideAssociation2022] may have affected some studies in the present topic area as well [see @lynottReplicationExperiencingPhysical2014; @montero-melisNoEvidenceEmbodiment2022].
-Therefore, in this study, we re-examine longstanding questions using larger-than-average data sets, and calculate the sample size required to reliably detect a range of effects.
-
-## Language and vision
-
-To retest the interplay theory, we revisit previous studies that contained larger-than-average samples of participants.
-Each of our three studies is organised around one *hub* study.
-In Study 1, the hub is @hutchison2013a, which implements a semantic priming paradigm.
-In Study 2, the hub is @pexman2017a, which implements a lexical decision paradigm.
-In Study 3, the hub is @balota2007a, which implements a lexical decision paradigm.
-Upon this basis, we added word-level variables from other studies to tap into language [@mandera2017a; @wingfieldUnderstandingRoleLinguistic2022] and vision [@lynott2020a; @petilli2021a].
-Additionally, we included several covariates---or nuisance variables---to allow a rigorous analysis of the effects of interest [@sassenhagenCommonMisapplicationStatistical2016].
-These covariates comprised participant-specific variables (e.g., attentional control), lexical variables (e.g., word frequency) and word concreteness.
-
-# Levels of analysis
-
-Experimental data in psycholinguistics often consists of various levels, such as participants, words and tasks.
-A simultaneous examination of these levels should enhance our understanding of the evidence collected [@ostarekStrongInferenceResearch2021]---for instance, by shedding light on the distribution of explanatory power within and across levels.
-This multilevel approach is complementary to another approach in the field that seeks to test the causal contribution of different sources of information to conceptual processing---e.g., language [@ponari2018a], perception [@stasenkoWhenConceptsLose2014] and action [@speedImpairedComprehensionSpeed2017].
-
-The three levels examined in this study are described below.
-
-## Individual level
-
-Variation  The role of individual differences in domains such as language, perception, mental imagery and physical experience [e.g., @davies2017a; @dils2010a; @fettermanFeelingWarmBeing2018; @holt2006a; @mak2019a; @miceliDifferencesRelatedAging2022; @pexman2018a; @vukovic2015a; @yap2012a; @yap2017a].^[According to @lamiellStatisticalThinkingPsychology2019, 'individual differences' is a misnomer in that the methods used to analyse individual differences (e.g, regression) are not participant-specific.
-We think that this observation is mitigated in the context of mixed-effects models (as used in our current study), which incorporate by-participant random intercepts and random slopes.] Furthermore, in some topic areas in which individual differences have not featured as prominently, the data have revealed a non-trivial role of individual differences [@montero-melisConsistencyMotionEvent2021; @kosIndividualVariationLate2012].
-
-### Vocabulary size
-
-Vocabulary size refers to the number of words a person can recognise out of a discrete set.
-Higher-vocabulary participants are expected to respond faster overall [@pexman2018a].
-Some previous studies have found that the effect of vocabulary size was moderated by variables related to general intelligence, such as processing speed [@ratcliff2010a; @yap2012a].
-Owing to those findings, and the recommendations from other studies [@james2018a; @pexman2018a; @sassenhagenCommonMisapplicationStatistical2016], the present studies included covariates of vocabulary size, where available.
-These covariates were measures of intelligence that were not vocabulary-based, namely, attentional control in Study 1 and information uptake in Study 2 (such a variable was not available for Study 3).
-
-## Word level
-
-*** to be edited *** Semantic or lexical information in words [e.g., @dedeyneVisualAffectiveMultimodal2021; @lam2015a; @lund1995a; @lund1996a; @lynott2020a; @mandera2017a; @petilli2021a; @pexman2017a; @santosPropertyGenerationReflects2011; @wingfieldUnderstandingRoleLinguistic2022]
-
-- Variables in this study: language-based and vision-based information;
-
-- Covariates: lexical variables and word concreteness;
-
-  - Lexical variables: The lexical covariates were selected in each study out of the same 5 variables, which have been identified as important in previous research (Wingfield & Connell, 2022; see [\underline{General statistical analysis}](#general-statistical-analyses) for details).
-
-  - Word concreteness: Adjusting for word concreteness was deemed important due to the pervasive effect of this variable across lexical-semantic tasks [@brysbaert2014a; @connellStrengthPerceptualExperience2012; @pexman2018a].
-Furthermore, it has been recently suggested that the effect of word concreteness does not stem from perceptual simulation, but instead from modality-independent properties of words [@bottiniConcretenessAdvantageLexical2021].
-
-Studies have operationalised the *language system* using measures that capture the relationships among words without explicitly drawing on any sensory or affective modalities.
+Over the last two decades, research in the cognitive sciences has suggested that conceptual processing depends on both language and embodiment systems.
+That is, understanding words involves---on the one hand---lexical and semantic associations of an amodal kind, and---on the other hand---modality-specific associations within perceptual, motor, affective and social domains [@barsalouLanguageSimulationConceptual2008; @connell2019a; @davisBuildingSemanticMemory2021; @khatin-zadehStrongVersionsEmbodied2021; @viglioccoTheorySemanticRepresentation2009].
+Studies addressing these systems have found that the language system is overall more prevalent in word processing, producing larger effect sizes [@banksLinguisticDistributionalKnowledge2021; @kiela2014a; @louwerse2015a; @lam2015a; @pecherDoesPizzaPrime1998; @petilli2021a].
+More intricately, the roles of language and embodiment are modulated by the characteristics of individuals, words and tasks.
+For instance, people's individual experience with language is associated with differential effects relating to phonological, lexical and semantic features of words [@jaredSkilledAdultReaders2017; @pexman2018a; @yap2012a; @yap2017a; @yapIndividualDifferencesJoint2009].
+Similarly, physical expertise and perceptual biases are associated with differences in the mental simulation of meaning [@beilockSportsExperienceChanges2008; @calvo-merinoActionObservationAcquired2005; @vukovic2015a].
+Furthermore, the embodiment system is especially suited for the processing of concrete concepts---e.g., *red*, *building* [@jonesDistrubutionalSemanticsStill2022; @kousta2011a; @ponari2018a; cf.
+@borghiAbstractConceptsExternal2022].
+Embodied information also becomes more important in the following conditions: (I) later in the time courses of word recognition [@bernabeu2017a; @louwerseNeurologicalEvidenceLinguistic2012; cf.
+@petilli2021a] and property generation [@santosPropertyGenerationReflects2011; @simmonsFMRIEvidenceWord2008], (II) when participants produce slower responses [@louwerseTasteWordsLinguistic2011], and (III) in tasks that elicit deeper semantic processing---e.g., semantic decision, as opposed to lexical decision [@ostarekTaskdependentCausalRole2017; @petilli2021a].
+Last, research in computational linguistics has provided further support for the complementarity of language and embodied information, by revealing increased predictive performance when models are provided with perceptual information on top of text-based information [@NIPS2013_7cce53cf; @roadsLearningUnsupervisedAlignment2020].
+
+In spite of the amount of evidence demonstrating the interplay between language and embodiment, there are four reasons to continue testing the interplay theory.
+First, the coexistence of several systems in a scientific theory must be thoroughly justified due to the value of simplicity [@galleseBrainConceptsRole2005; @tillmanHowSharpOccam2015].
+This scrutiny is particularly necessary because the language system has consistently produced larger effect sizes than the embodiment system [@banksLinguisticDistributionalKnowledge2021; @kiela2014a; @louwerse2015a; @lam2015a; @pecherDoesPizzaPrime1998; @petilli2021a].
+Therefore, it should be ruled out that the language system can suffice in all contexts.
+
+Second, it is important to examine both language and embodiment across various levels of the experimental structure---namely, individuals (i.e., due to individual differences such as vocabulary size), words (i.e., lexical and semantic variables) and tasks (i.e., experimental conditions affecting, for instance, processing speed).
+Some studies have approached this comprehensive structure but there is still room to widen the scope.
+One of the findings revealed by cross-level analyses is the influence of word processing tasks on the importance of modality-specific information.
+For instance, @connellSeeHearWhat2014 found that the vision-based information in words is important both for word identification (i.e., lexical decision) and for reading aloud (i.e., naming).
+In contrast, the auditory information in words is important for reading aloud but not so much for word identification.
+Another finding from cross-level research is a 'task-relevance advantage' for individuals that have a greater linguistic experience.
+Specifically, @pexman2018a found that higher-vocabulary individuals were more sensitive to task-relevant information, such as word concreteness in the semantic decision task.
+Furthermore, regarding embodiment, research has revealed that individuals who are briefly exposed to a certain sport develop neural activity that allows them to mentally simulate sport-specific actions during language processing [@beilockSportsExperienceChanges2008].
+While these works have covered a large swathe of the present topic, one question remains unanswered: how does an individual's linguistic experience relate to their sensivity to both linguistic and embodied information in words?
+
+Third, there is some inconclusive evidence.
+First, some findings have suggested that higher-vocabulary participants are more sensitive to language-based information---as reflected in greater semantic priming [@yap2017a]---, whereas other findings have suggested the opposite [@yapIndividualDifferencesJoint2009].
+Second, some studies have suggested that the language system is activated before the embodiment system [@lam2015a; @louwerseTasteWordsLinguistic2011], whereas a recent study suggested that this pattern does not hold in the lexical decision task [@petilli2021a].
+Third, some evidence has suggested that female participants draw on the language system more prominently than males [@burman2008a; @hutchinson2013a; @jung2019a; @ullman2008a], whereas other research has suggested that this difference is negligible in the general population [@wallentinChapterGenderDifferences2020].
+
+Fourth, some of the previous studies could have been affected by the scarcity of statistical power that has been identified in cognitive psychology and neuroscience [@marekReproducibleBrainwideAssociation2022; @lynottReplicationExperiencingPhysical2014; @montero-melisNoEvidenceEmbodiment2022].
+Problematically, low-powered studies present more errors in the estimation of effect sizes and $p$ values [@lokenMeasurementErrorReplication2017; @heymanReliabilityItemlevelSemantic2018; @vasishthStatisticalSignificanceFilter2018].
+The current studies address these four key issues.
+
+# The present studies {#present-studies}
+
+We revisit three larger-than-average studies to investigate the interplay between language and embodiment in conceptual processing.
+We devote a study to each of the three original studies.
+Thus, Study 1 is centred on @hutchison2013a and uses the semantic priming paradigm.
+Study 2 is centred on @pexman2017a and uses the semantic decision paradigm.
+Study 3 is centred on @balota2007a and uses the lexical decision paradigm.
+Each of these central studies contained measures of participants' vocabulary size and gender.
+Furthermore, the core data sets were expanded by adding variables that captured the language-based information in words [@mandera2017a; @wingfieldUnderstandingRoleLinguistic2022] and the vision-based information in words [@lynott2020a; @petilli2021a]---the latter being used to represent the embodiment system.
+One of the key questions we investigated using this array of variables was whether individual differences in vocabulary and gender modulated participants' sensivity to the language-based and vision-based information in words.
+Alongside the effects of interest, several covariates were included in the models to allow a rigorous analysis [@sassenhagenCommonMisapplicationStatistical2016].
+These covariates comprised measures of general cognition and lexical characteristics of the stimulus words.
+Last, in each study, we performed a statistical power analysis to help estimate the sample size needed to investigate a variety of effects in future studies.
+
+Below, we delve into the language and the embodiment components of these studies.
+
+## Language {#language}
+
+Studies have operationalised the language system at the word level using measures that capture the relationships among words without explicitly drawing on any sensory or affective modalities.
 Two main types of linguistic measures exist: those based on text corpora---dubbed *word co-occurrence* measures [@bullinariaExtractingSemanticRepresentations2007; @petilli2021a; @wingfieldUnderstandingRoleLinguistic2022]---and those based on associations collected from human participants---dubbed *word association* measures [@de2016a; @de2019a].
-Word co-occurrence is more purely linguistic, as word association captures more of the sensory and affective meaning of words [@dedeyneVisualAffectiveMultimodal2021].
-In Studies 1 and 2 below, word co-occurrence measures are used to represent the language system at the word level.
-In Study 3, however, such a measure could not be implemented.
-The measurement of priming across consecutive trials was not possible due to the high prevalence of nonword trials throughout the experiment.
-
-The embodiment system has been represented by measures that explicitly draw on perceptual, motor or affective modalities [@fernandinoDecodingInformationStructure2022].
-The perceptual modalities used in studies have often matched the 5 prototypical senses---vision, hearing, touch, taste, smell [@bernabeu2017a; @bernabeu2021a; @louwerseTasteWordsLinguistic2011]---and, less often, interoception [@connellInteroceptionForgottenModality2018].
-Yet, out of these senses, vision has been most frequently used in research [e.g., @bottiniConcretenessAdvantageLexical2021; @dedeyneVisualAffectiveMultimodal2021; @pearsonHeterogeneityMentalRepresentation2015; @petilli2021a; @yeeColorlessGreenIdeas2012].
-The prevalence of vision in research could be due to the prevalence of this sense in the brain [@reillyEnglishLexiconMirrors2020] and in language [@lynott2020a; @winterVisionDominatesPerceptual2018].
-Furthermore, for the purpose of examining individual differences along with word-level variables, vision is easier to tap into than other senses.
-For instance, the perception of visual motion can be measured using a standard computer screen [@rajanandaRandomdotKinematogramWebbased2018].
-Owing to these reasons, the three studies reported below implement the visual modality to represent the embodiment system at the word level.
-
-## Task level
-
-*** to be edited ***
-
-- *Variable in this study:* stimulus-onset asynchrony (SOA), present in Study 1 only.^[The names of all variables were slightly adjusted for this text to facilitate their understanding---for instance, by replacing underscores with spaces (see code scripts at [https://osf.io/ueryq](https://osf.io/ueryq)).
+Notwithstanding the interrelation between word co-occurrence and word association [@planchueloNatureWordAssociations2022], co-occurrence is more purely linguistic, whereas association indirectly captures more of the sensory and affective meaning of words [@dedeyneVisualAffectiveMultimodal2021].
+
+### Operationalisation and hypotheses
+
+In Study 1 (semantic priming) and Study 2 (semantic decision), co-occurrence measures were used to represent the language system at the word level.
+Specifically, in Study 1, this measure was called `language-based similarity`, and it was based on the degree of text-based co-occurrence between the prime word and the target word in each trial [@mandera2017a].
+In Study 2, the measure was called `word co-occurrence`, and it was based on the degree of text-based co-occurrence between each stimulus word and the words 'abstract' and 'concrete' [@wingfieldUnderstandingRoleLinguistic2022].
+In Study 3 (lexical decision), a co-occurrence measure could not be used, as the co-occurrence of words in consecutive trials could not be calculated due to the high frequency of nonword trials throughout the lexical decision task.
+Therefore, a single-word measure had to be used instead.
+Word frequency was used as it was the lexical variable, among five, that had the largest effect (see [\underline{Appendix A}](#appendix-A-lexical-covariates)).
+
+At the individual level, language was represented by participants' vocabulary size in Studies 1 and 2, and by participants' vocabulary age in Study 3.
+Vocabulary *size* and *age* did not differ in any consequential way.
+They both captured the amount of vocabulary knowledge of each participant, by testing their knowledge of a small sample of pre-normed words, and thereby inferring their overall knowledge.
+
+We hypothesised that word co-occurrence, word frequency and vocabulary size would all have facilitatory effects on participants' performance, with higher values leading to shorter RTs [@pexman2018a; @yapIndividualDifferencesJoint2009; @wingfieldUnderstandingRoleLinguistic2022].
+
+## Embodiment represented by vision-based information
+
+In previous studies, the embodiment system has been represented at the word level by perceptual, motor, affective or social variables [@fernandinoDecodingInformationStructure2022; @viglioccoTheorySemanticRepresentation2009; @wangSocialEmotionDimensional2021].
+For instance, the perceptual modalities have often corresponded to the five Aristotelian senses---vision, hearing, touch, taste and smell [@bernabeu2017a; @bernabeu2021a; @louwerseTasteWordsLinguistic2011]---and, less often, to interoception [@connellInteroceptionForgottenModality2018].
+Yet, out of all these domains, vision has been most frequently used in research [e.g., @bottiniConcretenessAdvantageLexical2021; @dedeyneVisualAffectiveMultimodal2021; @pearsonHeterogeneityMentalRepresentation2015; @petilli2021a; @yeeColorlessGreenIdeas2012].
+The hegemony of vision is likely due to the central position of vision in the human brain [@reillyEnglishLexiconMirrors2020] as well as in several languages [@bernabeuDutchModalityExclusivity2018; @chenMandarinChineseModality2019; @miceliPerceptualInteroceptiveStrength2021; @morucciAugmentedModalityExclusivity2019; @roqueVisionVerbsDominate2015; @speedDutchSensoryModality2021; @speedGroundingLanguageNeglected2020; @lynott2020a; @vergallitoPerceptualModalityNorms2020; @winterVisionDominatesPerceptual2018; @zhongSensorimotorNormsChinese2022].
+In the present study, we focussed on vision alone due to three reasons.
+First, we wanted to use a single variable to represent sensorimotor information, just as a single variable would be used to represent linguistic information.
+Using a single variable for each system facilitates the analysis of interactions with other variables.
+Second, vision is very prominent in cognition, as we just reviewed.
+Third, we had planned to use the present research to determine the sample size of a subsequent study that focusses on vision (indeed, the present study grew out of a statistical power analysis).
+
+### Operationalisation and hypotheses
+
+At the word level, we operationalised visual information using the visual strength variable from the Lancaster Sensorimotor Norms [@lynott2020a].
+This variable measures the degree of visual experience associated with concepts.
+In Study 1, we created the variable `visual-strength difference` by subtracting the visual strength of the prime word from that of the target word, in each trial.
+Thus, visual-strength difference measured---in each trial---how much the prime word and the target word differed in their degrees of vision-based information.
+Even though we could not find any previous studies that reported the effect of visual strength (or visual-strength difference) on RT, we hypothesised a priming effect underpinned by this variable, consistent with related research [@petilli2021a].
+Specifically, we hypothesised that visual-strength difference would have an inhibitory effect on participants' performance, with higher values leading to longer RTs.
+
+In Studies 2 and 3, we used the `visual strength` score per stimulus word.
+We hypothesised that this variable would have a facilitatory effect on participants' performance---i.e., higher values leading to shorter RTs---, consistent with related research [@petilli2021a].
+
+Unlike language, vision was not examined at the individual level because the available variables were based on one self-reported value per participant [@hutchison2013a; @balota2007a], contrasting with the greater precision of the vocabulary measures, which consisted of multiple trials.
+Nonetheless, we recognise the need to investigate the role of perceptual experience [@murakiSimulatingSemanticsAre2021; @plautIndividualDevelopmentalDifferences2000] alongside that of linguistic experience in the future.
+
+## Levels of analysis
+
+Experimental data in psycholinguistics can be divided into various levels, such as individuals, words and tasks.
+The simultaneous examination of a theory across several levels is expected to enhance our understanding of the theory [@ostarekStrongInferenceResearch2021]---for instance, by revealing the distribution of explanatory power (that is, effect size) within and across these levels.
+Several studies have probed more than one level---for instance, word level and individual level [@aujlaLanguageExperiencePredicts2021; @lim2020a; @pexman2018a; @yapIndividualDifferencesJoint2009], or word level and task level [@al-azaryCanYouTouch2022; @connell2013a; @connellSeeHearWhat2014; @ostarekSixChallengesEmbodiment2019; @petilli2021a].
+This multilevel approach is complementary to a different line of research that aims to test the causality of various sources of information in conceptual processing, such as language [@ponari2018a], perception [@stasenkoWhenConceptsLose2014] and action [@speedImpairedComprehensionSpeed2017].
+
+The three levels considered in this study---individual, word and task---are described below.
+
+### Individual level
+
+The individual level is concerned with the role of individual differences in domains such as language, perception, mental imagery and physical experience [e.g., @daidoneVocabularySizeKey2021; @davies2017a; @dils2010a; @fettermanFeelingWarmBeing2018; @holt2006a; @mak2019a; @miceliDifferencesRelatedAging2022; @pexman2018a; @vukovic2015a; @yap2012a; @yap2017a; @yapIndividualDifferencesJoint2009].^[According to @lamiellStatisticalThinkingPsychology2019, 'individual differences' is a misnomer in that the analyses used to examine those (e.g, regression) are not participant-specific.
+While this may partly hold for the current study too, the use of by-participant random effects increases the role of individuals in the analysis.] Recent studies have revealed important roles of participant-specific variables in topics where these variables have not traditionally been considered [@delucaRedefiningBilingualismSpectrum2019; @kosIndividualVariationLate2012; @montero-melisConsistencyMotionEvent2021].
+
+Vocabulary size is used to represent the language system at the individual level.
+It measures the number of words a person can recognise out of a sample.
+Furthermore, covariates akin to general cognition---where available---were included the models (see [\underline{Covariates}](#covariates) section below).
+
+### Word level
+
+The word level is concerned with the lexical and semantic information in words [e.g., @dedeyneVisualAffectiveMultimodal2021; @lam2015a; @lund1995a; @lund1996a; @lynott2020a; @mandera2017a; @petilli2021a; @pexman2017a; @santosPropertyGenerationReflects2011; @wingfieldUnderstandingRoleLinguistic2022].
+The word-level variables of interest in this study are language-based and vision-based information (both described above).
+The covariates are lexical variables and word concreteness.
+The lexical covariates were selected in each study out of the same five variables (see [\underline{Covariates}](#covariates) section below).
+
+### Task level
+
+The task level is concerned with experimental conditions affecting, for instance, processing speed.
+In Study 1 (semantic priming), there is one task-level factor, namely, stimulus onset asynchrony (SOA), which measures the temporal interval between the onset of the prime word and the onset of the target word.^[The names of all variables used in the analyses were slightly adjusted for this text to facilitate their understanding---for instance, by replacing underscores with spaces (conversions reflected in the scripts available at [http://doi.org/10.17605/OSF.IO/UERYQ](http://doi.org/10.17605/OSF.IO/UERYQ)).
 One specific case deserves further comment.
-We use the formula of the 'stimulus-onset asynchrony' (SOA) in this paper, instead of the 'interstimulus interval' (ISI), as the SOA has been more commonly used in previous papers [e.g., @hutchison2013a; @pecherDoesPizzaPrime1998; @petilli2021a; @yap2017a].
-The difference between these formulas is that the ISI does not count the presentation of the prime word [example equivalences between ISI and SOA are available in @lam2015a, and in Figure 1A of @dilolloDecouplingStimulusDuration2004].
-In the current study, the presentation of the prime word lasts 150 ms.
-Thus, the 200-ms SOA is equivalent to an ISI of 50 ms, and the 1,200-ms SOA corresponds to an ISI of 1,050 ms [@hutchison2013a].
-The use of either formula in the analysis would not change our results, as we recoded the levels of the factor as -0.5 and +0.5, and then $z$-scored those, following the advice of @brauer2018a.
-In our analyses ([https://osf.io/ueryq](https://osf.io/ueryq)), we used the ISI formula as it was the one present in the data set of @hutchison2013a (retrieved from [https://www.montana.edu/attmemlab/documents/all%20ldt%20subs_all%20trials3.xlsx](https://www.montana.edu/attmemlab/documents/all%20ldt%20subs_all%20trials3.xlsx)]).
-
-In addition, the different paradigms applied across the three studies can be compared, albeit cautiously as the studies differ in other influential ways, such as the number of participants and stimulus words.
-The three tasks examined in the present studies are likely to reflect different degrees of semantic depth, in the following order [for background, see @connell2013a; @lam2015a; @ostarekTaskdependentCausalRole2017; @versaceImpactEmbodiedSimulation2021; @wingfieldUnderstandingRoleLinguistic2022].
+We use the formula of the SOA in this paper, instead of the 'interstimulus interval' (ISI)---which we used in the analysis---, as the SOA has been more commonly used in previous papers [e.g., @hutchison2013a; @pecherDoesPizzaPrime1998; @petilli2021a; @yap2017a].
+In our analysis, we used the ISI formula as it was the one present in the data set of @hutchison2013a---retrieved from [https://www.montana.edu/attmemlab/documents/all%20ldt%20subs_all%20trials3.xlsx](https://www.montana.edu/attmemlab/documents/all%20ldt%20subs_all%20trials3.xlsx).
+The only difference between these formulas is that the ISI does not count the presentation of the prime word.
+In the current study [@hutchison2013a], the presentation of the prime word lasted 150 ms.
+Therefore, the 50 ms ISI is equivalent to a 200 ms SOA, and the 1,050 ms ISI is equivalent to a 1,200 ms SOA.
+The use of either formula in the analysis would not affect our results, as the ISI conditions were recoded as -0.5 and 0.5 [@brauer2018a].] In Studies 2 and 3, there are no task-level variables.
+
+Beyond task-level variables, there is an additional source of task-related information across the three studies---namely, the experimental paradigm used in each study (i.e., semantic priming, semantic decision and lexical decision).
+Indeed, it is possible to examine how the effects vary across these paradigms [see @wingfieldUnderstandingRoleLinguistic2022].
+This comparison, however, must be considered cautiously due to the existence of other non-trivial differences across these studies, such as the numbers of observations.
+With this caveat noted, the tasks used across these studies likely elicit varying degrees of semantic depth, as ordered below [see @balotaDepthAutomaticSpreading1986; @barsalouLanguageSimulationConceptual2008; @beckerLongtermSemanticPriming1997; @dewitMaskedSemanticPriming2015; @joordensLongShortSemantic1997; @lam2015a; @murakiSimulatingSemanticsAre2021; @ostarekTaskdependentCausalRole2017; @versaceImpactEmbodiedSimulation2021; @wingfieldUnderstandingRoleLinguistic2022].
 
 1.
-**Semantic decision** (Study 2) likely elicits the deepest semantic processing, as the instructions of this task ask for a concreteness judgement.
-In this task, participants are asked to classify words as abstract or concrete.
+*Semantic decision* (Study 2) likely elicits the deepest semantic processing, as the instructions of this task ask for a concreteness judgement.
+In this task, participants are asked to classify words as abstract or concrete, which elicits deeper semantic processing than the task of identifying word forms---i.e., lexical decision [@dewitMaskedSemanticPriming2015].
 
 2.
-**Semantic priming** (Study 1).
-The task in the semantic priming paradigm is often lexical decision, as in Study 1 herein.
-The fundamental characteristic of this paradigm is that, in each trial, a prime word is presented for a very short period before the target word.
-The prime word is not relevant to the task.
-Nonetheless, participants process both the prime word and the target word, and this combination allows researchers to analyse responses based on the relationship between those words.
-Therefore, this paradigm is more deeply semantic than the lexical decision paradigm.
-Indeed, slower responses in semantic priming studies---reflecting difficult lexical decisions---have been linked to larger priming effects [@balotaMeanResponseLatency2008; @hoedemakerItTakesTime2014; @yapAdditiveInteractiveEffects2013], suggesting a degree of semantic association that does not appear in the standard lexical decision paradigm.
-
-3.
-**Lexical decision** (Study 3) is likely the semantically-shallowest task [see @balotaDepthAutomaticSpreading1986; @beckerLongtermSemanticPriming1997; @connell2013a; @dewitMaskedSemanticPriming2015; @joordensLongShortSemantic1997; @ostarekTaskdependentCausalRole2017].
-
-## Interactions across levels
-
-The three levels are strongly intertwined, and studies have probed into more than one level at once: for instance, word level and individual level [@aujlaLanguageExperiencePredicts2021; @lim2020a; @pexman2018a; @yapIndividualDifferencesJoint2009], or word level and task level [@al-azaryCanYouTouch2022; @connell2013a; @ostarekSixChallengesEmbodiment2019; @petilli2021a].
-Thus, hypotheses are available regarding interactions across levels, as addressed below.
-
-### Vocabulary size and linguistic features
-
-Three hypotheses exist regarding the interaction between vocabulary size and lexical-semantic features.
-First, higher-vocabulary participants---compared to lower-vocabulary ones---might be more sensitive to linguistic features, thanks to a larger number of semantic associations [@connell2019a; @landauerIntroductionLatentSemantic1998; @louwerse2015a; @paivioMentalRepresentationsDual1990; @pylyshynWhatMindEye1973].
-For instance, @yap2017a observed a larger semantic priming effect in higher-vocabulary participants from [@hutchinson2013a].
-The second hypothesis, in contrast, states that higher-vocabulary participants would be *less* sensitive to linguistic features, thanks to a more automatic process [@perfettiLexicalQualityHypothesis2002].
-For instance, @yapIndividualDifferencesJoint2009 observed a smaller semantic priming effect in higher-vocabulary participants.
+*Semantic priming* (Study 1).
+The task administered to participants in semantic priming studies is often lexical decision, as in Study 1 below.
+The fundamental characteristic of semantic priming is that, in each trial, a prime word is briefly presented before the target word.
+The prime word is not directly relevant to the task, as participants respond to the target word.
+Nonetheless, participants normally process both the prime word and the target word in each trial, and this combination allows researchers to analyse responses based on the prime--target relationship.
+In this regard, this paradigm could be considered more deeply semantic than lexical decision.
+Indeed, slower responses in semantic priming studies---reflecting difficult lexical decisions---have been linked to larger priming effects [@balotaMeanResponseLatency2008; @hoedemakerItTakesTime2014; @yapAdditiveInteractiveEffects2013], revealing a degree of semantic association that has not been identified in the lexical decision task.
+
+3. *Lexical decision* (Study 3) is likely the semantically-shallowest task of these three, as it focusses solely on the identification of word forms.
+
+## Hypotheses {#hypotheses}
+
+The central objective of the present studies is the simultaneous investigation of language-based and vision-based information, along with the interactions between each of those and vocabulary size, gender and presentation speed (i.e., SOA).
+Previous studies have examined subsets of these effects using the same data sets we are using [@balota2007a; @petilli2021a; @pexman2017a; @pexman2018a; @yap2012a; @yap2017a; @wingfieldUnderstandingRoleLinguistic2022].
+Out of these studies, only @petilli2021a investigated *both* language and vision.
+However, in contrast to our present study, Petilli et al.
+did not examine the role of vocabulary size or any other individual differences, instead collapsing the data across participants.
+
+In addition to main effects of the aforementioned variables, our three studies have four interactions in common: (1a) language-based information $\times$ vocabulary size, (1b) vision-based information $\times$ vocabulary size, (2a) language-based information $\times$ participants' gender, and (2b) vision-based information $\times$ participants' gender.
+In addition, Study 1 contained two further interactions: (3a) language-based information $\times$ SOA, (3b) vision-based information $\times$ SOA (note that the names of some predictors vary across studies, as detailed in the [\underline{present studies}](#language) section above).
+Each interaction and the corresponding hypotheses are addressed below.
+
+### 1a. Language-based information $\times$ vocabulary size
+
+We outline three hypotheses supported by literature regarding the interaction between language-based information and participants’ vocabulary size.
+
+- *Larger vocabulary, larger effects.* Higher-vocabulary participants might be more sensitive to linguistic features than lower-vocabulary participants, thanks to a larger number of semantic associations [@connell2019a; @landauerIntroductionLatentSemantic1998; @louwerse2015a; @paivioMentalRepresentationsDual1990; @pylyshynWhatMindEye1973].
+For instance, @yap2017a revisited the semantic priming study of @hutchinson2013a and observed a larger semantic priming effect in higher-vocabulary participants.
+
+- *Larger vocabulary, smaller effects.* Higher-vocabulary participants might be less sensitive to linguistic features, thanks to a more automated language processing [@perfettiLexicalQualityHypothesis2002].
+Some of the evidence aligned with this hypothesis was obtained by @yapIndividualDifferencesJoint2009, who observed a smaller semantic priming effect in higher-vocabulary participants.
 Similarly, @yap2012a found that higher-vocabulary participants in a lexical decision task [@balota2007a] were less sensitive to a cluster of lexical and semantic features (i.e., word frequency, semantic neighborhood density and number of senses).
-Last, the third hypothesis proposes that higher-vocabulary participants might present a selective sensitivity, tailored to the task.
-For instance, @pexman2018a analysed the semantic decision task of @pexman2017a, in which participants assessed the concreteness of words.
-Pexman and Yap found that higher-vocabulary participants---compared to lower-vocabulary ones---were more sensitive to word concreteness and less sensitive to word frequency and age of acquisition, which were less relevant to the task [also see @lim2020a].
-The three hypotheses herein were tested in the present study by revisiting some of the aforementioned studies [@hutchinson2013a; @pexman2017a; @balota2007a].
-
-### Vocabulary size and visual strength
-
-Research demonstrating the interplay between linguistic and embodied information [@connell2019a; @louwerse2015a; @paivioMentalRepresentationsDual1990] affords the hypothesis that lower-vocabulary participants---compared to higher-vocabulary ones---might profit more from sensory, motor, affective and social associations of the words.
-
-### Gender and linguistic features
-
-In addition, the language system is expected to be more important in female than male participants [@burman2008a; @hutchinson2013a; @jung2019a; @ullman2008a], provided that this interaction effect is not too small to be detected [@wallentinChapterGenderDifferences2020].
-
-In another study, @schmidtke2018a collected human ratings on the association between words that make up compounds.
-Some compounds were found to be relatively transparent---e.g., *doorbell*---, and others relatively opaque---e.g., *deadline*.
-Furthermore, @schmidtke2018a found an interaction between semantic transparency and participants' reading experience (the latter measure encompassing vocabulary size and exposure to printed materials): namely, more experienced readers processed transparent compounds more quickly than opaque ones, whereas less experienced readers processed opaque compounds more quickly than transparent ones.
-This interaction suggests __________________________.
-Thus, ________________________.
-
-## Power analysis
+
+- *Larger vocabulary, more task-relevant effects.* Higher-vocabulary participants might present a greater sensitivity to task-relevant variables, borne out of their greater linguistic experience, relative to lower vocabulary participants.
+This would be consistent with the findings of @pexman2018a, who revisited the semantic decision study of @pexman2017a.
+The semantic decision task of the Pexman et al.
+consisted of classifying words as abstract or concrete.
+Pexman and Yap found that word concreteness---a very relevant source of information for this task---was more influential in higher-vocabulary participants than in lower-vocabulary ones.
+In contrast, word frequency and age of acquisition----not as relevant to the task--were more influential in lower-vocabulary participants [also see @lim2020a].
+In our present studies, we set our hypotheses regarding the 'task-relevance advantage' by working under the assumption that the language-based information in words---represented by one variable in each study---is important for the three tasks, given the large effects of language across tasks [@banksLinguisticDistributionalKnowledge2021; @kiela2014a; @louwerse2015a; @lam2015a; @pecherDoesPizzaPrime1998; @petilli2021a].
+Therefore, the relevance hypothesis predicts that higher-vocabulary participants---compared to lower-vocabulary ones---will be more sensitive to language-based information (as represented by `language-based similarity` in Study 1, `word co-occurrence` in Study 2, and `word frequency` in Study 3).
+
+### 1b. Vision-based information $\times$ vocabulary size
+
+To our knowledge, no previous studies have investigated the interaction between vision-based information and participants' vocabulary size.
+We entertained two hypotheses.
+First, lower-vocabulary participants might be more sensitive to visual strength than higher-vocabulary participants.
+In this way, lower-vocabulary participants might *compensate* for the disadvantage on the language side.
+Second, we considered the possibility that there were no interaction effect.
+
+### 2a. Language-based information $\times$ gender
+
+We entertained two hypotheses regarding the interaction between language-based information and participants' gender: (a) that the language system would be more important in female participants than in males [@burman2008a; @hutchinson2013a; @jung2019a; @ullman2008a], and (b) that this interaction effect would be absent, as a recent review suggested that gender differences are negligible in the general population [@wallentinChapterGenderDifferences2020].
+
+### 2b. Vision-based information $\times$ gender
+
+To our knowledge, no previous studies have investigated the interaction between vision-based information and participants' gender.
+We entertained two hypotheses.
+Our first hypothesis was that this interaction would stand opposite to the interaction between language and gender.
+That is, if female participants were to present a greater role of language-based information, male participants would present a greater role of vision-based information, thereby compensating for the disadvantage on the language side.
+Our second hypothesis was the absence of this interaction effect [see @wallentinChapterGenderDifferences2020].
+
+### 3a. Language-based information $\times$ SOA
+
+Previous research predicts that language-based information will have a larger effect with the short SOA than with the long one [@lam2015a; @petilli2021a]), which also aligns with research demonstrating the fast activation of language-based information [@louwerseTasteWordsLinguistic2011; @santosPropertyGenerationReflects2011; @simmonsFMRIEvidenceWord2008].
+
+### 3b. Vision-based information $\times$ SOA
+
+The interaction between vision-based information and SOA allows three hypotheses.
+First, some previous research predicts that the role of vision-based information will be more prevalent with the long SOA than with the short one [@louwerseTasteWordsLinguistic2011; @santosPropertyGenerationReflects2011; @simmonsFMRIEvidenceWord2008; also see @barsalouLanguageSimulationConceptual2008].
+Second, in contrast, other research [@petilli2021a] based on the same data that we are analysing [@hutchison2013a] predicts vision-based priming only with the short SOA (200 ms), and not with the long one (1,200 ms).
+Third, other research does not predict any vision-based priming effect [@hutchisonSemanticPrimingDue2003; @ostarekTaskdependentCausalRole2017; @pecherDoesPizzaPrime1998; @yeeColorlessGreenIdeas2012].
+In this regard, some studies have observed vision-based priming when the task was preceded by another task that required attention to visual features of concepts [@pecherDoesPizzaPrime1998; @yeeColorlessGreenIdeas2012], but the present data [@hutchison2013a] does not contain such a prior task.
+
+### Language and vision across studies
+
+Next, we consider our hypotheses regarding the role of language and vision across studies.
+Yet, before addressing those, we reiterate that caution is required due to the existence of other differences across these studies, such as the number of observations.
+First, we hypothesise that language-based information will be relevant in the three studies due to the consistent importance of language observed in past studies [@banksLinguisticDistributionalKnowledge2021; @kiela2014a; @louwerse2015a; @lam2015a; @pecherDoesPizzaPrime1998; @petilli2021a].
+Second, the extant evidence regarding vision-based information is less conclusive.
+Some studies have observed effects of vision-based information [@floresdarcaisSemanticActivationRecognition1985; @schreuderEffectsPerceptualConceptual1984; @connellSeeHearWhat2014; @petilli2021a], whereas others have not [@hutchisonSemanticPrimingDue2003; @ostarekTaskdependentCausalRole2017], and a third set of studies have only observed them when the critical task was preceded by a task that required attention to visual features of concepts [@pecherDoesPizzaPrime1998; @yeeColorlessGreenIdeas2012].
+Based on these precedents, we hypothesise that vision-based information will be relevant in semantic decision, whereas it might or might not be relevant in semantic priming and in lexical decision.
+
+## Statistical power analysis
 
@@
 Out of these, sample size is the factor that can best be controlled by researchers [@kumleEstimatingPowerGeneralized2021].
-The three studies we present below, containing larger-than-average sample sizes, offer an opportunity to conduct an a-priori power analysis to help determine the sample size of future studies [@albersWhenPowerAnalyses2018].
+The three studies we present below, containing larger-than-average sample sizes, offer an opportunity to perform an a-priori power analysis to help determine the sample size of future studies [@albersWhenPowerAnalyses2018].
 
@@
 
-Insufficient statistical power lowers the reliability of effect sizes, and increases the likelihood of false positive results---i.e., Type I error---and of false negative results---i.e., Type II error [@gelmanPowerCalculationsAssessing2014; @lokenMeasurementErrorReplication2017; @tverskyBeliefLawSmall1971; @vondermalsburgFalsePositivesOther2017].
+Insufficient statistical power lowers the reliability of effect sizes, and increases the likelihood of false positive results---i.e., Type I errors---as well as the likelihood of false negative results---i.e., Type II errors [@gelmanPowerCalculationsAssessing2014; @lokenMeasurementErrorReplication2017; @tverskyBeliefLawSmall1971; @vondermalsburgFalsePositivesOther2017].
 For instance, @vasishthHowEmbraceVariation2021 illustrate how, in low-powered studies, effect sizes associated with significant results tend to be overestimated [also see @vasishthStatisticalSignificanceFilter2018].
 
-Over the past decade, replication studies and power analyses have uncovered insufficient sample sizes in psychology [@brysbaertHowManyParticipants2019; @lynottReplicationExperiencingPhysical2014; @montero-melisSatelliteVsVerbframing2017; @montero-melisNoEvidenceEmbodiment2022; @rodriguez-ferreiroSemanticPrimingSchizotypal2020; @vasishthStatisticalSignificanceFilter2018].
-In the neighbouring field of neuroscience, @marekReproducibleBrainwideAssociation2022 recently estimated the sample size that is required to reliably study the mapping between individual differences, such as fluid intelligence, and brain structures.
-Marek et al.
-found that the current median of 25 participants contributing to one of these studies contrasted with the thousands of participants---around 10,000---that would be needed for a well-powered study [also see @buttonPowerFailureWhy2013].
-
-More topic-specific power analyses are necessary due to three reasons.
-Firstly, power analyses provide greater certainty on the reasons behind non-replications [e.g., @opensciencecollaborationEstimatingReproducibilityPsychological2015], and behind non-significant results.
-Indeed, insufficient power is one of the possible reasons, alongside procedural errors or subtler methodological differences, and publication bias [@andersonResponseCommentEstimating2016; @barsalouEstablishingGeneralizableMechanisms2019; @corkerHighQualityDirect2014; @gilbertCommentEstimatingReproducibility2016; @williamsImprovingPsychologicalScience2014].
-Currently, if we consider---for instance---research on individual differences, we will find several non-significant results, both in behavioural studies [e.g., @hedge2018a; @rodriguez-ferreiroSemanticPrimingSchizotypal2020; for a Bayes factor analysis, see @rouderPsychometricsIndividualDifferences2019] and in neuroscientific studies [e.g., @diazNeuralSensitivityPhonological2021].
-A greater availability of power analyses in specific topics will at least shed light on the role of power in the results.
-Secondly, power analyses facilitate the identification of sensible sample sizes for future studies.
-Thirdly, power analyses help maximise the use of research funding in the long term by fostering studies that are more replicable [see @vasishthHowEmbraceVariation2021].
-
-# Methods
-
-The analytical method was largely similar across the three studies. Below, we present the commonalities in the statistical analyses and in the power analyses.
-
-## General method for statistical analysis {#general-statistical-analyses}
-
-The statistical analysis was designed to examine the unique contribution of each effect of interest.
-In all three studies, the dependent variable---response time (RT)---was $z$-scored around each participant's mean to curb the influence of each participant's baseline speed [@balota2007a; @lim2020a; @kumarDistantConnectivityMultiplestep2020; @pexman2017a; @pexman2018a; @yap2012a; @yap2017a].
+Over the past decade, replication studies and power analyses have uncovered insufficient sample sizes in psychology [@brysbaertHowManyParticipants2019; @heymanReliabilityItemlevelSemantic2018; @lynottReplicationExperiencingPhysical2014; @montero-melisSatelliteVsVerbframing2017; @montero-melisNoEvidenceEmbodiment2022; @rodriguez-ferreiroSemanticPrimingSchizotypal2020; @vasishthStatisticalSignificanceFilter2018].
+In one of these studies, @heymanReliabilityItemlevelSemantic2018 demonstrated that increasing the sample size resulted in an increase of the reliability of the estimates, which in turn lowered the Type I error rate and the Type II error rate---i.e., false negative and false positive results, respectively.
+Calls for larger sample sizes have also been voiced in the field of neuroscience.
+For instance, @marekReproducibleBrainwideAssociation2022 estimated the sample size that would be required to reliably study the mapping between individual differences---such as general cognition---and brain structures.
+The authors found that the current median of 25 participants in each of these studies contrasted with the thousands of participants---around 10,000---that would be needed for a well-powered study [also see @buttonPowerFailureWhy2013].
+
+More topic-specific power analyses are necessary due to several reasons.
+First, power analyses provide greater certainty on the reasons behind non-replications [e.g., @opensciencecollaborationEstimatingReproducibilityPsychological2015], and behind non-significant results at large.
+Non-replications are not solely explained by methodological differences across studies, questionable research practices and publication bias [@andersonResponseCommentEstimating2016; @barsalouEstablishingGeneralizableMechanisms2019; @corkerHighQualityDirect2014; @gilbertCommentEstimatingReproducibility2016; @williamsImprovingPsychologicalScience2014; @zwaanReplicationsShouldBe2014; also see @tiokhinCompetitionPriorityHarms2021].
+In addition to these factors, a lack of statistical power can cause non-replications and non-significant results [see @lokenMeasurementErrorReplication2017; @vasishthHowEmbraceVariation2021].
+
+Regarding non-significant results, it is worthwhile to consider some examples from research on individual differences.
+In this literature, there is a body of non-significant results, both in behavioural studies [@daidoneVocabularySizeKey2021; @hedge2018a; @murakiSimulatingSemanticsAre2021; @ponari2018a; @rodriguez-ferreiroSemanticPrimingSchizotypal2020; for a Bayes factor analysis, see @rouderPsychometricsIndividualDifferences2019] and in neuroscientific studies [@diazNeuralSensitivityPhonological2021].
+A greater availability of power analyses within this topic area and others will at least shed light on the influence of statistical power on the results.
+Furthermore, power analyses facilitate the identification of sensible sample sizes for future studies.
+Last, it should be noted that although increasing the statistical power comes at a cost in the short term, power analyses will help maximise the use of research funding in the long term by fostering more replicable research [see @vasishthHowEmbraceVariation2021; remember @opensciencecollaborationEstimatingReproducibilityPsychological2015].
+
+# General methods
+
+The analytical method was broadly similar across the three studies.
+Below, we present the commonalities in the statistical analysis and in the power analysis.
+Several R packages from the 'tidyverse' [@R-tidyverse] were used.
+
+## Covariates {#covariates}
+
+Several covariates---or nuisance variables---were included in each study to allow a rigorous analysis of the effects of interest [@sassenhagenCommonMisapplicationStatistical2016].
+Unlike the effects of interest, these covariates were not critical to our research question (i.e., the interplay between language-based and vision-based information).
+They comprised participant-specific variables (e.g., attentional control), lexical variables (e.g., word frequency) and word concreteness.
+The covariates are distinguished from the effects of interest in the results table(s) in each study.
+The three kinds of covariates included were as follows.
+
+Participant-specific covariates were measures akin to general cognition, and were included because some studies have found that the effect of vocabulary size was moderated by general cognition variables such as processing speed [@ratcliff2010a; @yap2012a].
+Similarly, research has evidenced the role of attentional control [@hutchisonAttentionalControlAsymmetric2014; @yap2017a], and authors have expressed the desirability of including such covariates in models [@james2018a; @pexman2018a].
+Therefore, we included in the analyses a individual measure of 'general cognition', where available.
+These measures were available in the first two studies, and they indexed task performance abilities that were different from vocabulary knowledge.
+We refer to them by their more specific names in each study.^[The general cognition measures could also be dubbed general or fluid intelligence, but we think that cognition is more appropriate in our present context.] In Study 1, the measure used was `attentional control` [@hutchison2013a].
+In Study 2, it was `information uptake` [@pexman2018a].
+In Study 3, such a covariate was not used as it was not available in the data set of @balota2007a.
+
+Lexical covariates were selected in every study out of the same five variables, which had been used as covariates in @wingfieldUnderstandingRoleLinguistic2022 [also see @petilli2021a].
+They comprised: number of letters (i.e., orthographic length), word frequency, number of syllables [both the latter from @balota2007a], orthographic Levenshtein distance [@yarkoniMovingColtheartNew2008] and phonological Levenshtein distance [@suarezObservingNeighborhoodEffects2011; @yapVisualWordRecognition2009].
+The selection among these candidates was performed because some of them were highly intercorrelated---i.e., $r$ > .70 [@dormannCollinearityReviewMethods2013; @harrison2018a].
+The correlations and the selection models are available in [\underline{Appendix A}](#appendix-A-lexical-covariates).
+
+Word concreteness was included due to the pervasive effect of this variable across lexical and semantic tasks [@brysbaert2014a; @connellStrengthPerceptualExperience2012; @pexman2018a], and due to the sizable correlations ($r$ > .30) between word concreteness and some other predictors, such as visual strength (see correlation figures in each study).
+Furthermore, the role of word concreteness has been contested, with some research suggesting that its effect stems from perceptual simulation [@connellStrengthPerceptualExperience2012] versus other research suggesting that the effect is amodal [@bottiniConcretenessAdvantageLexical2021].
+In passing, we will bring our results to bear on the role of word concreteness.
+
+## Data preprocessing and statistical analysis
+
+In the three studies, the statistical analysis was designed to investigate the contribution of each effect of interest.
+The following preprocessing steps were applied.
+First, incorrect responses were removed.
+Second, nonword trials were removed (only necessary in Studies 1 and 3).
+Third, too fast and too slow responses were removed.
+For the latter purpose, we applied the same thresholds that had been applied in each of the original studies.
+That is, in Study 1, we removed responses faster than 200 ms or slower than 3,000 ms [@hutchison2013a].
+In Study 2, we removed responses faster than 250 ms or slower than 3,000 ms [@pexman2018a].
+In Study 3, we removed responses faster than 200 ms or slower than 4,000 ms [@balota2007a].
+Next, the dependent variable---response time (RT)---was $z$-scored around each participant's mean to curb the influence of each participant's baseline speed [@balota2007a; @lim2020a; @kumarDistantConnectivityMultiplestep2020; @pexman2017a; @pexman2018a; @yap2012a; @yap2017a].
 This was important because the size of experimental effects is known to increase with longer RTs [@faust1999a].
 Next, binary predictors were recoded into continuous variables [@brauer2018a].
-Specifically, participants' gender was recoded as follows: male = -0.5; female = 0.5; NA = 0.
-The SOAs in Study 1 were recoded as follows: 150 ms = -0.5; 1,200 ms = 0.5.
-Finally, following @brauer2018a, all predictors were $z$-scored (i.e., $M \approx$ 0, $SD \approx$ 1).
-
-Several covariates---or nuisance variables---were included in each study, to allow a rigorous analysis of the effects of interest [@sassenhagenCommonMisapplicationStatistical2016].
-Unlike the effects of interest, these covariates were not critical to the research question.
-They comprised participant-specific variables (e.g., attentional control), lexical variables (e.g., word frequency) and word concreteness.
-
-The lexical covariates were selected in every study out of the same 5 variables, which had been used as covariates in @wingfieldUnderstandingRoleLinguistic2022 [also see @petilli2021a].
-They comprised: number of letters (i.e., orthographic length), word frequency, number of syllables [both the latter from @balota2007a], orthographic Levenshtein distance [@yarkoniMovingColtheartNew2008] and phonological Levenshtein distance [@suarezObservingNeighborhoodEffects2011].
-The selection among these candidates was performed because some of them were highly intercorrelated---i.e., $r$ > .70 [@dormannCollinearityReviewMethods2013; @harrison2018a].
-The correlations and the selection models are available in [\underline{Appendix A}](#appendix-A-lexical-covariates).
-
-Word concreteness was included due to its correlation with visual strength, as shown in each study below.
-A recent study suggested that the psycholinguistic import of concreteness is fundamentally lexical, and does not involve perceptual simulation [@bottiniConcretenessAdvantageLexical2021].
-
-The participant-specific covariates were measures akin to fluid intelligence, and were included due to their relationship with vocabulary size, as previous studies have expressed the desirability of including such covariates [@james2018a; @pexman2018a].
-As described in each study, these covariates were used in Studies 1 and 2, but not in Study 3, as such a variable was not available.
+Specifically, participants' gender was recoded as follows: Female = 0.5, X = 0, Male = -0.5.
+The SOAs in Study 1 were recoded as follows: 200 ms = -0.5; 1,200 ms = 0.5.
+Next, the data sets were trimmed by removing rows that lacked values on any variable, and by also removing RTs that were more than 3 standard deviations ($SD$) away from the mean ($M$).
+The nesting factors applied in the trimming are specified in each study.
+Finally, all predictors were $z$-scored, resulting in $M \approx$ 0 and $SD \approx$ 1 (values not exact as the variables were not normally distributed).
+More specifically, between-item predictors---i.e., word-level variables (e.g., language-based information) and task-level variables (e.g., SOA)---were $z$-scored around each participant's own mean [@brauer2018a].
 
@@
 
-The participants and the stimulus items were crossed in the three studies.
-That is, each participant was presented with a subset of the stimulus words.
+With regard to random effects, participants and stimuli were *crossed* in the three studies.
+That is, each participant was presented with a subset of the stimuli.
 Conversely, each word was presented to a subset of participants.
 Therefore, linear mixed-effects models were implemented.
-These models included a maximal random-effects structure, with by-participant and by-item random intercepts, and the appropriate random slopes for all effects of interest [@barrRandomEffectsStructure2013].
-In the semantic priming study, the items were prime-target pairs, whereas in the semantic decision and lexical decision studies, the items were individual words.
+These models included a maximal random-effects structure, with by-participant and by-item random intercepts, and the appropriate random slopes for all effects of interest [@barrRandomEffectsStructure2013; @brauer2018a; @singmann2019a].
+Random effects---especially random slopes---constrain the analytical space by *claiming* their share of variance.
+As a result, that variance cannot be taken by the fixed effects.
+In the semantic priming study, the items were prime--target pairs, whereas in the semantic decision and lexical decision studies, the items were individual words.
 In the case of interactions, random slopes were included only when the interacting variables varied within the same unit [@brauer2018a]---e.g., an interaction of two variables varying within participants (only present in Study 1).
 Where required due to convergence warnings, random slopes for covariates were removed, as inspired by Remedy 11 from @brauer2018a.
-In this regard, whereas @brauer2018a contemplate the removal of random slopes for covariates only when the covariates are not interacting with any effects of interest, we removed random slopes for covariates even if they interacted with effects of interest because these interactions were covariates themselves (covariates are indicated in the results tables).
-
-To avoid inflating the Type I error rate (false positives), the random slopes for the effects of interest (indicated by non-shaded rows in the results tables below) were never removed [see Table 17 in @brauer2018a; for an example of this approach, see @diazNeuralSensitivityPhonological2021].
+In this regard, whereas @brauer2018a contemplate the removal of random slopes for covariates only when the covariates are not interacting with any effects of interest, we removed random slopes for covariates even if they interacted with effects of interest because these interactions were covariates themselves.
+
+To avoid an inflation of the Type I error rate---i.e., false positives---, the random slopes for the effects of interest (as indicated in each study) were never removed [see Table 17 in @brauer2018a; for an example of this approach, see @diazNeuralSensitivityPhonological2021].
 This approach arguably provides a better protection against false positives [@barrRandomEffectsStructure2013; @brauer2018a; @singmann2019a] than the practice of removing random slopes when they do not significantly improve the fit [e.g., @bernabeu2017a; @pexman2018a; @batesFittingLinearMixedeffects2015; @baayenMixedeffectsModelingCrossed2008; but also see @matuschekBalancingTypeError2017].
@@
 
-$P$ values were calculated using the Kenward-Roger approximation for degrees of freedom [@luke2017a], in the R package 'lmerTest', Version 3.1-3 [@R-lmerTest].
+$P$ values were calculated using the Kenward-Roger approximation for degrees of freedom [@luke2017a] in the R package 'lmerTest', Version 3.1-3 [@R-lmerTest].
 The latter package in turn used 'lme4', Version 1.1-26 [@batesPackageLme42021; @batesFittingLinearMixedeffects2015].
@@
 Diagnostics regarding convergence and normality are provided in [\underline{Appendix B}](#appendix-B-frequentist-analysis-diagnostics).
-Effects that were non-significant or very small are best interpreted by considering their 95% confidence intervals [@cummingNewStatisticsWhy2014], which are shown in the results tables as well as in plots.
+Those effects that are non-significant or very small are best interpreted by considering the confidence intervals and the credible intervals [@cummingNewStatisticsWhy2014].
+
+The R package 'GGally' [@R-GGally] was used to create correlation plots, whereas the package 'sjPlot' [@R-sjPlot] was used for interaction plots.
 
@@
 A Bayesian analysis was performed to complement the estimates that had been obtained in the frequentist analysis.
-Whereas the focus of the frequentist analysis had been hypothesis testing, using $p$ values, the purpose of the Bayesian analysis was parameter estimation.
-Accordingly, we estimated the posterior distribution of every effect, without calculating Bayes factors [for other examples of this approach, see @milekEavesdroppingHappinessRevisited2018; @preglaVariabilitySentenceComprehension2021; @rodriguez-ferreiroSemanticPrimingSchizotypal2020; for comparisons between estimation and hypothesis testing, see @cummingNewStatisticsWhy2014; @kruschkeBayesianNewStatistics2018; @schmalzWhatBayesFactor2021; @tendeiroReviewIssuesNull2019; @tendeiroOnTheWhite2022; @rouderBayesianInferencePsychology2018; @vanravenzwaaijAdvantagesMasqueradingIssues2021].
+Whereas the goal of the frequentist analysis had been hypothesis testing, for which $p$ values were used, the goal of the Bayesian analysis was parameter estimation.
+Accordingly, we estimated the posterior distribution of every effect, without calculating Bayes factors [for other examples of the same *estimation approach*, see @milekEavesdroppingHappinessRevisited2018; @preglaVariabilitySentenceComprehension2021; @rodriguez-ferreiroSemanticPrimingSchizotypal2020; for comparisons between estimation and hypothesis testing, see @cummingNewStatisticsWhy2014; @kruschkeBayesianNewStatistics2018; @schmalzWhatBayesFactor2021; @tendeiroReviewIssuesNull2019; @tendeiroOnTheWhite2022; @rouderBayesianInferencePsychology2018; @vanravenzwaaijAdvantagesMasqueradingIssues2021].
 In the estimation approach, the estimates are interpreted by considering the position of their credible intervals in relation to the expected effect size.
@@
 
-This analysis served two purposes: firstly, to ascertain the interpretation of the smaller effects---which were identified as unreliable in the power analyses---, and secondly, to complement the estimates obtained in the frequentist analysis.
+This analysis served two purposes: first, to ascertain the interpretation of the smaller effects---which were identified as unreliable in the power analyses---, and second, to complement the estimates obtained in the frequentist analysis.
 The latter purpose was pertinent because the frequentist models presented convergence warnings---even though it must be noted that a previous study found that frequentist and Bayesian estimates were similar despite convergence warnings appearing in the frequentist analysis [@rodriguez-ferreiroSemanticPrimingSchizotypal2020].
 Furthermore, the complementary analysis was pertinent because the frequentist models presented residual errors that deviated from normality---even though mixed-effects models are fairly robust to such a deviation [@kniefViolatingNormalityAssumption2021; @schielzethRobustnessLinearMixed2020].
-Owing to these precedents, we expected to find broadly similar estimates in the frequentist and the Bayesian analyses.
-Each frequentist model in the three studies has a Bayesian counterpart, with the exception of a sub-analysis performed in the first study (semantic priming), which included 'vision-based similarity' as a predictor.
-
-The R package 'brms', Version 2.17.0, was used for this analysis [@burknerPackageBrms2022; @burknerAdvancedBayesianMultilevel2018].
+Owing to these precedents, we expected to find broadly similar estimates in the frequentist analyses and in the Bayesian ones.
+Across studies, each frequentist model has a Bayesian counterpart, with the exception of the secondary analysis performed in Study 1 (semantic priming) that included `vision-based similarity` as a predictor.
+The R package 'brms', Version 2.17.0, was used for the Bayesian analysis [@burknerPackageBrms2022; @burknerAdvancedBayesianMultilevel2018].
 
@@
 
-The priors were established by inspecting the effect sizes obtained in previous studies as well as the effect sizes obtained in our frequentist analyses of Studies 1, 2 and 3.
-
-The previous studies that were considered for determining the priors were selected because they had used experimental paradigms and analytical procedures similar to those used in the current studies.
-Specifically, the paradigms were (I) semantic priming with a lexical decision task---as in Study 1---, (II) semantic decision---as in Study 2---,and (III) lexical decision---as in Study 3.
-The analytical procedures consisted of the z-scoring of the dependent and the independent variables.
-We found two studies that matched these characteristics: @lim2020a (see Table 5 therein) and @pexman2018a (see Tables 6 and 7 therein).
-These studies and the frequentist analyses reported below yielded effect sizes smaller than ±0.30.
-The bounds of this range were determined by the results from @pexman2018a, who found a word concreteness effect of $\upbeta$ = 0.41 in the concrete-words analysis, and an effect of $\upbeta$ = 0.20 in the abstract-words analysis.
-Since we did not separate abstract from concrete words, we averaged the former values, and set -0.30 as the lower bound, and 0.30 as the upper bound.
-This provided the basis for informative priors.
-Specifically, in these informative priors, 95% of values would fall within the range [-0.30, 0.30].
-
-Next, we considered the direction of effects.
-In the results of @lim2020a and @pexman2018a, and in our frequentist results, some effects consistently presented a negative direction---i.e., an inhibitory effect on RT---, whereas some other effects were consistently positive.
-We only incorporated the direction of effects into the priors in cases of large effects that had presented consistent directions in previous studies and in our frequentist analyses.
+The priors were established by inspecting the effect sizes obtained in previous studies as well as the effect sizes obtained in our frequentist analyses of the present data (reported in Studies 1, 2 and 3 below).
+In the first regard, the previous studies that were considered were selected because the experimental paradigms, variables and analytical procedures they had used were similar to those used in our current studies.
+Specifically, regarding paradigms, we sought studies that implemented: (I) semantic priming with a lexical decision task---as in Study 1---, (II) semantic decision---as in Study 2---, or (III) lexical decision---as in Study 3.
+Regarding analytical procedures, we sought studies in which both the dependent and the independent variables were $z$-scored.
+We found two studies that broadly matched these criteria: @lim2020a (see Table 5 therein) and @pexman2018a (see Tables 6 and 7 therein).
+Out of these studies, @pexman2018a contained the variables that were most similar to ours, which included vocabulary size (labelled 'NAART') and word frequency.
+
+Based on both these studies and on the frequentist analyses reported below, a range of effect sizes was identified that spanned between $\upbeta$ = -0.30 and $\upbeta$ = 0.30.
+This range was centred around 0 as the variables were $z$-scored.
+The bounds of this range were determined by the largest effects, which appeared in @pexman2018a.
+Pexman et al.
+conducted a semantic decision study, and split the data set into abstract and concrete words.
+The two largest effects they found were---first---a word concreteness effect in the concrete-words analysis of $\upbeta$ = -0.41, and---second---a word concreteness effect in the abstract-words analysis of $\upbeta$ = 0.20.
+Unlike Pexman et al., we did not split the data set into abstract and concrete words, but analysed these sets together.
+Therefore, we averaged between the aforementioned values, obtaining a range between $\upbeta$ = -0.30 and $\upbeta$ = 0.30.
+
+In the results of @lim2020a and @pexman2018a, and in our frequentist results, some effects consistently presented a negative polarity (i.e., leading to shorter response times), whereas some other effects were consistently positive.
+We incorporated the direction of effects into the priors only in cases of large effects that had presented a consistent direction (either positive or negative) in previous studies and in our frequentist analyses in the present studies.
 These criteria were matched by the following variables: word frequency---with a negative direction, as higher word frequency leads to shorter RTs [@brysbaertImpactWordPrevalence2016; @brysbaertWordFrequencyEffect2018a; @lim2020a; @mendesPervasiveEffectWord2021; @pexman2018a]---, number of letters and number of syllables---both with positive directions [@bartonWordlengthEffectReading2014; @beyersmannEvidenceEmbeddedWord2020; @pexman2018a]---, and orthographic Levenshtein distance---with a positive direction [@cerniMotorExpertiseTyping2016; @dijkstraMultilinkComputationalModel2019; @kimEffectsLexicalFeatures2018; @yarkoniMovingColtheartNew2008].
-We did not incorporate information about the direction of the word concreteness effect as this effect can follow different directions in abstract and concrete words [@pexman2018a], and we analysed both sets of words together.
-Last, it is noteworthy that some previous studies have integrated effect direction in some priors [e.g., @stoneInteractionGrammaticallyDistinct2021], but most have not [e.g., @preglaVariabilitySentenceComprehension2021; @rodriguez-ferreiroSemanticPrimingSchizotypal2020; @stoneEffectDecayLexical2020].
-In conclusion, the four predictors that had directional priors were covariates (also known as nuisance variables).
+We did not incorporate information about the direction of the word concreteness effect, as this effect can follow different directions in abstract and concrete words [@brysbaert2014a; @pexman2018a], and we analysed both sets of words together.
+In conclusion, the four predictors that had directional priors were covariates.
 All the other predictors had priors centred on 0.
-
-These priors were used on the fixed effects and on the corresponding standard deviation parameters.
-The correlation among the random effects had a weakly-informative prior, LKJ(2) [@lewandowskiGeneratingRandomCorrelation2009], which assumes that high correlations among the random effects are rare [also used in @rodriguez-ferreiroSemanticPrimingSchizotypal2020; @stoneEffectDecayLexical2020; @stoneInteractionGrammaticallyDistinct2021; @vasishthBayesianDataAnalysis2018].
+Last, as a methodological matter, it is noteworthy that most of the psycholinguistic studies applying Bayesian analysis have not incorporated any directional information in priors [e.g., @preglaVariabilitySentenceComprehension2021; @rodriguez-ferreiroSemanticPrimingSchizotypal2020; @stoneEffectDecayLexical2020; cf.
+@stoneInteractionGrammaticallyDistinct2021].
 
@@
 
-We aimed to perform prior sensitivity analyses of our results.
-Prior sensitivity analyses are checks that assess the influence of different priors on the results [@leeBayesianCognitiveModeling2014; @schootBayesianStatisticsModelling2021; @stoneEffectDecayLexical2020].
-The range of priors established for this purpose varied in their standard deviations.
-Their means were the same, most being centred on 0, as explained above.
-
-The priors we settled upon---shown in Figure \@ref(fig:bayesian-priors)---comprised an 'informative' prior ($SD$ = 0.1), a 'weakly-informative' one ($SD$ = 0.2) and a 'diffuse' one ($SD$ = 0.3).
+The choice of priors can influence the results in consequential ways.
+To assess the extent of this influence, *prior sensitivity analyses* have been recommended.
+These analyses are performed by comparing the effect of more and less strict priors---or, in other words, priors varying in their degree of informativeness.
+The degree of variation is adjusted through the standard deviation, and the means are not varied [@leeBayesianCognitiveModeling2014; @schootBayesianStatisticsModelling2021; @stoneEffectDecayLexical2020].
+
+In this way, we compared the results obtained using 'informative' priors ($SD$ = 0.1), 'weakly-informative' priors ($SD$ = 0.2) and 'diffuse' priors ($SD$ = 0.3).
+These standard deviations were chosen so that around 95% of values in the informative priors would fall within our initial range of effect sizes that spanned from -0.30 to 0.30.
+All priors are illustrated in Figure \@ref(fig:bayesian-priors).
 These priors resembled others from previous psycholinguistic studies [@preglaVariabilitySentenceComprehension2021; @stoneEffectDecayLexical2020; @stoneInteractionGrammaticallyDistinct2021].
@@
 The range of standard deviations we used---i.e., 0.1, 0.2 and 0.3---was narrower than those of previous studies because our dependent variable and our predictors were $z$-scored, resulting in small estimates and small $SD$s [see @lim2020a; @pexman2018a].
-
-```{r bayesian-priors, fig.cap = 'Priors used in the three studies. The green vertical rectangle shows the range of plausible effect sizes based on previous studies and on our frequentist analyses.'}
+These priors were used on the fixed effects and on the standard deviation parameters of the fixed effects.
+For the correlations among the random effects, an $LKJ$(2) prior was used [@lewandowskiGeneratingRandomCorrelation2009].
+This is a 'regularising' prior, as it assumes that high correlations among random effects are rare [also used in @rodriguez-ferreiroSemanticPrimingSchizotypal2020; @stoneEffectDecayLexical2020; @stoneInteractionGrammaticallyDistinct2021; @vasishthBayesianDataAnalysis2018].
+
+```{r bayesian-priors, fig.cap = 'Priors used in the three studies.
+The green vertical rectangle shows the range of plausible effect sizes based on previous studies and on our frequentist analyses.
+In the informative priors, around 95\\% of the values fall within the range.'}
 
@@
 
-The adequacy of each of these priors was assessed with prior predictive checks, in which we compared the observed data to data predicted by the priors [@schootBayesianStatisticsModelling2021].
-In these checks, we also tested the adequacy of two model-wide distributions: the traditional Gaussian distribution (default in most analyses) and an exponentially modified Gaussian---dubbed 'ex-Gaussian'---distribution [@matzkePsychologicalInterpretationExGaussian2009].
-The ex-Gaussian distribution was considered because the residual errors of the frequentist models were not normally distributed [@loTransformNotTransform2015], and because this distribution was found to be more appropriate than the Gaussian one in a related, previous study [see supplementary materials of @rodriguez-ferreiroSemanticPrimingSchizotypal2020].
+The adequacy of each of these priors was assessed by performing prior predictive checks, in which we compared the observed data to the predictions of the model [@schootBayesianStatisticsModelling2021].
+Furthermore, in these checks we also tested the adequacy of two model-wide distributions: the traditional Gaussian distribution (default in most analyses) and an exponentially modified Gaussian---dubbed 'ex-Gaussian'---distribution [@matzkePsychologicalInterpretationExGaussian2009].
+The ex-Gaussian distribution was considered because the residual errors of the frequentist models were not normally distributed [@loTransformNotTransform2015], and because this distribution was found to be more appropriate than the Gaussian one in a previous, related study [see supplementary materials of @rodriguez-ferreiroSemanticPrimingSchizotypal2020].
 The ex-Gaussian distribution had an identity link function, which preserves the interpretability of the coefficients, as opposed to a transformation applied directly to the dependent variable [@loTransformNotTransform2015].
-
-Prior predictive checks revealed that the priors were adequate, and that the ex-Gaussian distribution was more appropriate than the Gaussian one, converging with @rodriguez-ferreiroSemanticPrimingSchizotypal2020 (see the corresponding plots in [\underline{Appendix C}](#appendix-C-Bayesian-analysis-diagnostics)).
+The results of these prior predictive checks revealed that the priors were adequate, and that the ex-Gaussian distribution was more appropriate than the Gaussian one (see [\underline{Appendix C}](#appendix-C-Bayesian-analysis-diagnostics)), converging with @rodriguez-ferreiroSemanticPrimingSchizotypal2020.
 Therefore, the ex-Gaussian distribution was used in the final models.
@@
 
-In the main analyses, the informative, weakly-informative and diffuse priors were used in separate models.
+In the main analysis, the informative, weakly-informative and diffuse priors were used in separate models.
 In other words, in each model, all priors had the same degree of informativeness [as done in @preglaVariabilitySentenceComprehension2021; @rodriguez-ferreiroSemanticPrimingSchizotypal2020; @stoneEffectDecayLexical2020; @stoneInteractionGrammaticallyDistinct2021].
@@
 
-Posterior predictive checks were performed to assess the fit between the observed data and new data predicted by the posterior [@schootBayesianStatisticsModelling2021].
+Posterior predictive checks were performed to assess the consistency between the observed data and new data predicted by the posterior distributions [@schootBayesianStatisticsModelling2021].
 These checks are available in [\underline{Appendix C}](#appendix-C-Bayesian-analysis-diagnostics).
@@
 
-Where convergence was not reached in a model, as indicated by $\widehat R$ > 1.01 [@schootBayesianStatisticsModelling2021; @vehtariRanknormalizationFoldingLocalization2021], the number of iterations was increased.
-Furthermore, where necessary, the random slopes for covariates were removed [@brauer2018a].
+When convergence was not reached in a model, as indicated by $\widehat R$ > 1.01 [@schootBayesianStatisticsModelling2021; @vehtariRanknormalizationFoldingLocalization2021], the number of iterations was increased and the random slopes for covariates were removed [@brauer2018a].
 The resulting random effects in these models were largely the same as those present in the frequentist models.
-The only exception regarded the lexical decision models.
-In the frequentist model for lexical decision, the random slopes for covariates were removed due to convergence warnings, whereas in the Bayesian analysis, these random slopes did not have to be removed as the models converged.
-
-The Bayesian models in the semantic decision study could not be made to converge, and the results were not valid.
-Therefore, those estimates are not shown in the main text but in [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results).
-
-## General method for statistical power analysis
-
-Power curves based on Monte Carlo simulations were performed for most of the effects of interest, using the R package 'simr', Version 1.0.5 [@greenSIMRPackagePower2016].
+The only exception concerned the models of the lexical decision study.
+In the frequentist model for the latter study, the random slopes for covariates were removed due to convergence warnings, whereas in the Bayesian analysis, these random slopes did not have to be removed as the models converged, thanks to the large number of iterations that were run.
+In the lexical decision study, it was possible to run a larger number of iterations than in the two other studies, as the lexical decision data set had fewer observations, resulting in faster running.
+
+The Bayesian models in the semantic decision study could not be made to converge, and the final results of these models were not valid.
+Therefore, those estimates are not shown in the main text, but are available in [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results).
+
+## Statistical power analysis
+
+Power curves based on Monte Carlo simulations were performed for most of the effects of interest using the R package 'simr', Version 1.0.5 [@greenSIMRPackagePower2016].
 Obtaining power curves for a range of effects in each study allows for a comprehensive assessment of the plausibility of the power estimated for each effect.
 
-Monte Carlo simulations are performed by running the statistical model a large number of times, under slight, random variations of the dependent variable [@greenSIMRPackagePower2016; for a comparable approach, see @lokenMeasurementErrorReplication2017].
+In each study, the item-level sample size---i.e., the number of words---was not modified.
+Therefore, to plan the sample size for future studies, these results must be considered under the assumptions that the future study would apply a statistical method similar to ours---namely, a mixed-effects model with random intercepts and slopes---, and that the analysis would encompass at least as many stimuli as the corresponding study (numbers detailed in each study below).
+$P$ values were calculated using the Satterthwaite approximation for degrees of freedom [@luke2017a].
+
+Monte Carlo simulations consist of running the statistical model a large number of times, under slight, random variations of the dependent variable [@greenSIMRPackagePower2016; for a comparable approach, see @lokenMeasurementErrorReplication2017].
 The power to detect each effect of interest is calculated by dividing the number of times that the effect is significant by the total number of simulations run.
@@
 Thus, for a power curve examining the power for an effect across 12 sample sizes, 2,400 simulations were run.
-In each study, the item-level sample size---i.e., the number of words---was not modified.
-Thus, each of the power curves we present assume the same number of words that existed in each of our studies (these numbers are detailed in each study below).
-$P$ values were calculated using the Satterthwaite approximation for degrees of freedom [@luke2017a].
-
-It is difficult to determine an effect size for each effect examined in a power analysis, as the amount and the scope of relevant research are usually finite and biased [@albersWhenPowerAnalyses2018; @gelmanPowerCalculationsAssessing2014; @kumleEstimatingPowerGeneralized2021].
-Power analyses sometimes use the original effect sizes from previous studies [e.g., @paciniExocentricCodingMapping2021; @villalongaPerceptualTimingPrecision2021].
-In contrast, some authors have opted to reduce the previous effect sizes to account for factors that can influence the effect size of the planned study.
-First, publication bias and low-powered studies cause published effect sizes to be inflated [@brysbaertHowManyParticipants2019; @lokenMeasurementErrorReplication2017; @vasishthStatisticalSignificanceFilter2018; @vasishthHowEmbraceVariation2021; @opensciencecollaborationEstimatingReproducibilityPsychological2015].
-Second, there might be differences between the studies used in the power analysis and the study to be conducted.
-Some of these differences could be foreseeable---for instance, if they are due to a limitation in the literature available for the power analysis---, whereas other differences might arise from unexpected circumstances arising during the project or from random variation [@barsalouEstablishingGeneralizableMechanisms2019].
+
+Power analyses require setting an effect size for each effect.
+Often, it is difficult to determine the effect size, as the amount and the scope of relevant research are usually finite and biased [@albersWhenPowerAnalyses2018; @gelmanPowerCalculationsAssessing2014; @kumleEstimatingPowerGeneralized2021].
+In some power analyses, the original effect sizes from previous studies have been adopted without any modification [e.g., @paciniExocentricCodingMapping2021; @villalongaPerceptualTimingPrecision2021].
+In contrast, some authors have opted to reduce the previous effect sizes to account for two intervening factors.
+First, publication bias and insufficient statistical power cause published effect sizes to be inflated [@brysbaertHowManyParticipants2019; @lokenMeasurementErrorReplication2017; @vasishthStatisticalSignificanceFilter2018; @vasishthHowEmbraceVariation2021; @opensciencecollaborationEstimatingReproducibilityPsychological2015].
+Second, over the course of the research, a variety of circumstances could create differences between the planned study and the studies that were used in the power analysis.
+Some of these differences could be foreseeable---for instance, if they are due to a limitation in the literature available for the power analysis---, whereas other differences might be unforeseeable and could go unnoticed  [@barsalouEstablishingGeneralizableMechanisms2019; @noahWhenBothOriginal2018].
 Reducing the effect size in the power analysis leads to an increase of the sample size of the planned study [@brysbaertPowerAnalysisEffect2018; @greenSIMRPackagePower2016; @hoenigAbusePower2001].
-The reduced effect size---sometimes dubbed the smallest effect size of interest---is often set with a certain arbitrariness.
-For instance, @fleurDefinitelySawIt2020 applied a reduction of 1/8 (i.e., 12.5%), whereas @kumleEstimatingPowerGeneralized2021 applied a 15% reduction.
-In the present study, a reduction of 20% was applied to every effect examined in the power analysis.
-By comparison with the power analyses reviewed in this paragraph, the present reduction will lead to a relatively-conservative estimate of required sample sizes.
-Yet, it is intrinsically difficult to determine how conservative a power analysis is, once we consider the insufficient power of most studies in psychology, and the resulting overestimation of effect sizes.
+The reduced effect size---sometimes dubbed the smallest effect size of interest---is often set with a degree of arbitrariness.
+In previous studies, @fleurDefinitelySawIt2020 applied a reduction of 1/8 (i.e., 12.5%), whereas @kumleEstimatingPowerGeneralized2021 applied a 15% reduction.
+In the present study, a reduction of 20% was applied to every effect in the power analysis.
+By comparison with the power analyses reviewed in this paragraph, the present reduction will lead to a more conservative estimate of required sample sizes.
+However, after considering the precedents of small samples and publication bias reviewed above, a 20% reduction is arguably a reasonable safeguard.
+Indeed, a posteriori, the results of our power analyses suggested that the 20% reduction had not been excessive, as some of the effects examined were detectable with small sample sizes.
 
 Both the primary analysis and the power analysis were performed in R [@R-base].
-Version 4.0.2 was used for the frequentist analysis, Version 4.1.0 was used for the Bayesian analysis, and Version 4.1.2 was used for fast operations such as plotting.
-All the statistical and the power analyses were run on the High-End Computing facility at Lancaster University.^[Information about this facility is available at [https://answers.lancaster.ac.uk/display/ISS/High+End+Computing+%28HEC%29+help](https://answers.lancaster.ac.uk/display/ISS/High+End+Computing+%28HEC%29+help)]
+Version 4.0.2 was used for the frequentist analysis, Version 4.1.0 was used for the Bayesian analysis, and Version 4.1.2 was used for fast operations such as data preprocessing and plotting.
+Given the complexity of these analyses, all the statistical and the power analyses were run on the High-End Computing facility at Lancaster University.^[Information about this facility is available at [https://answers.lancaster.ac.uk/display/ISS/High+End+Computing+%28HEC%29+help](https://answers.lancaster.ac.uk/display/ISS/High+End+Computing+%28HEC%29+help).
+Even though analysis jobs were run in parallel, some of the statistical analyses took four months to complete (specifically, one month for the final model to run, which was delayed due to three reasons: limited availability of machines, occasional cancellations of jobs to allow maintenance work on the machines, and lack of convergence of the models).
+Furthermore, the power analysis for the semantic priming study took six months (specifically, two months of running, with delays due to the limited availability of machines and occasional cancellations of jobs).]
 
@@
 The core data set in this study was that of the Semantic Priming Project [@hutchison2013a; also see @yap2017a].
-Out of the tasks delivered in the experiment, we used the lexical decision one because it was most relevant to our forthcoming research.
-In the lexical decision task, participants judged whether strings of letters constituted real words (e.g., 'building') or nonwords (e.g., 'gop').
-Crucially, in the experimental manipulation that characterises semantic priming, a prime word was presented before the target word in each trial.
-Since prime words facilitate the comprehension of target words, the participants' responses to the targets can be analysed as a function of the semantic relationship between primes and targets [@hoedemakerItTakesTime2014].
-
-In some studies, the association between prime and target words has been examined in terms of related versus unrelated pairs [@pecherDoesPizzaPrime1998; @trumppMaskedPrimingConceptual2013], and in terms of first- and second-order relationships [@hutchison2013a].
-In contrast to these categorical associations, other studies have measured the association between the prime and the target words using language-based similarity estimates [@guntherLatentSemanticAnalysis2016; @guenther2016a; @hutchisonPredictingSemanticPriming2008; @jones2006a; @lam2015a; @lund1995a; @lund1996a; @mandera2017a; @mcdonald2002a; @pad2007a; @petilli2021a; @wingfieldUnderstandingRoleLinguistic2022].
-In one of these studies, @mandera2017a found that the latter computational measures outperformed human-based associations at explaining the priming effect.
-
-Priming associations beyond the linguistic realm have also been examined, with early studies finding perceptual priming effects [@floresdarcaisSemanticActivationRecognition1985; @schreuderEffectsPerceptualConceptual1984].
-Yet, the earliest findings were soon reframed by @pecherDoesPizzaPrime1998, who conducted a follow-up with an improved design, and observed the perceptual priming effect only when the word processing task was preceded by a visually-intensive task [@pecherDoesPizzaPrime1998].
-This moderating condition, replicated by @yeeColorlessGreenIdeas2012, is consistent with other conceptual-processing studies using a non-priming paradigm [@ostarekTaskdependentCausalRole2017].
-However, a considerable number of studies have observed perceptual priming even in the absence of a preparatory perceptual task.
-A set of these studies used the Conceptual Modality Switch paradigm, in which the primes and the targets are presented in separate, consecutive trials [@pecherVerifyingDifferentmodalityProperties2003; @lynottModalityExclusivityNorms2009; @louwerseTasteWordsLinguistic2011; @collinsModalitySwitchingProperty2011; @hald2011a; @hald2013a; @trumppMaskedPrimingConceptual2013; @bernabeu2017a].
-The other set of studies, using the more standard priming intervals, are described below.
-
-@lam2015a conducted a semantic priming experiment containing a lexical decision task.
-Participants were instructed to respond whether the prime word and the target word in each trial were both real words or pseudowords.
-The semantic-priming manipulation consisted of the following types of associations between the prime and the target words: (1) semantic association (e.g., bolt → screwdriver), (2) action association (e.g., housekey → screwdriver), (3) visual association (e.g., soldering iron → screwdriver), and (4) no association (e.g., charger → screwdriver).
-In addition, four conditions were present that consisted of SOAs of 500, 650, 800 and 1,400 ms.
-In the results, Lam et al.
-firstly observed priming effects of the semantic-association type with all SOAs.
-Secondly, the authors observed motor-association priming effects with the SOAs of 500, 650 and 1,400 ms.
-Lastly, they observed visual-association priming effects only with the SOA of 1,400 ms.
-Overall, semantic-association priming---corresponding to language-based association---was more consistent than the priming based on visual and action associations.
-This greater influence of the language system converges with other studies on semantic priming [@lam2015a; @pecherDoesPizzaPrime1998; @petilli2021a] and with studies using other paradigms [@banksLinguisticDistributionalKnowledge2021; @kiela2014a; @louwerse2015a].
-
-Similarly, the results of @lam2015a regarding the time course of language-based and vision-based priming were consistent with a wealth of literature observing that perceptual systems, such as vision, are activated later than the language system [@barsalouLanguageSimulationConceptual2008; @connell2013a; @louwerseTasteWordsLinguistic2011; @santosPropertyGenerationReflects2011].
-For instance, studies using electroencephalography have found that perceptual priming effects emerged in the first 300 ms.
-Following the 300-ms stage, the perceptual priming increased in some studies [@bernabeu2017a; @amselEmpiricallyGroundingGrounded2014], whereas other studies it stabilised [@kieferDifferentialTemporospatialPattern2022], and in a third set of studies, the effect fluctuated [@amselTrackingRealtimeNeural2011].
-Taken together, the most prevalent pattern is of a gradual accumulation of information throughout word processing [also see @haukOnlyTimeWill2016], which is consistent with the accummulation of information required for the integration of context in sentences [@haldEEGThetaGamma2006].
-This progression invites two hypotheses regarding SOA in the current study: (1) that language-based information will be more prevalent than vision-based information in both the short and the long SOA, and (2) that vision-based information will be more prevalent in the long SOA than in the short one.
-Consistent with the first hypothesis, @petilli2021a observed that language-based information was more influential in both the short and the long SOA, within the data set of @hutchison2013a.
-The second hypothesis, in contrast, is challenged by other findings.
-First, @hutchisonSemanticPrimingDue2003 concluded that the vision-based priming effect was negligible.
-Second, other studies have observed the effect only when the word processing task was preceded by a visually-intensive task [@pecherDoesPizzaPrime1998; @yeeColorlessGreenIdeas2012].
-Third, Petilli et al.
-observed vision-based priming with the short SOA (150 ms) but not with the long one (1,200 ms).
-
-The findings of @petilli2021a were based on a novel analysis of the data set of @hutchison2013a.
-The strengths of Petilli et al.'s study centred on the simultaneous analysis of language- and vision-based similarity using predictors that were continuous [see @cohenCostDichotomization1983; @guntherLatentSemanticAnalysis2016; @mandera2017a] and not based on human ratings [cf.
+The study of @hutchison2013a comprised two tasks: lexical decision and naming.
+We limited our analysis to the lexical decision task because it was more relevant to a subsequent study that we were planning.
+In the lexical decision task, participants judged whether strings of letters constituted real words (e.g., *building*) or nonwords (e.g.
+*gop*).
+Importantly, in each trial, the target word that participants assessed was preceded by a prime word.
+Participants were only required to provide a response regarding the *target* word.
+The characteristic feature of the semantic priming paradigm is the analysis of responses to the targets as a function of the semantic relationship between the primes and the targets [@hoedemakerItTakesTime2014; @brunelliereCooccurrenceFrequencyEvaluated2017; @dewitMaskedSemanticPriming2015].
+
+In some studies, the association between prime and target words has been investigated in terms of related versus unrelated pairs [@lam2015a; @pecherDoesPizzaPrime1998; @trumppMaskedPrimingConceptual2013] and---in other studies---in terms of first- and second-order relationships [@hutchison2013a].
+In contrast to these categorical associations, a third set of studies have measured the association between the prime and the target words using continuous estimates of text-based similarity [@guntherLatentSemanticAnalysis2016; @guenther2016a; @hutchisonPredictingSemanticPriming2008; @jones2006a; @lund1995a; @lund1996a; @mandera2017a; @mcdonald2002a; @pad2007a; @petilli2021a; @wingfieldUnderstandingRoleLinguistic2022].
+In one of these studies, @mandera2017a found that computational measures of similarity outperformed human-based associations at explaining language-based priming.
+
+## Language, vision and SOA
+
+Priming associations beyond the linguistic realm have also been investigated, with early studies observing perceptual priming effects [@floresdarcaisSemanticActivationRecognition1985; @schreuderEffectsPerceptualConceptual1984].
+Yet, those early findings were soon reframed by @pecherDoesPizzaPrime1998, who conducted a follow-up with an improved design, and observed vision-based priming only when the task was preceded by another task that required attention to visual features of concepts [also see @yeeColorlessGreenIdeas2012; @ostarekTaskdependentCausalRole2017].
+Furthermore, two studies have failed to observe vision-based priming [@hutchisonSemanticPrimingDue2003; @ostarekTaskdependentCausalRole2017].
+
+Nonetheless, a considerable number of studies have observed perceptual priming, even in the absence of a pretask.
+A set of these studies used the Conceptual Modality Switch paradigm, in which the primes and the targets are presented in separate, consecutive trials---e.g., *Loud Welcome* → *Fine Selection* [@pecherVerifyingDifferentmodalityProperties2003; @lynottModalityExclusivityNorms2009; @louwerseTasteWordsLinguistic2011; @collinsModalitySwitchingProperty2011; @hald2011a; @hald2013a; @trumppMaskedPrimingConceptual2013; @bernabeu2017a].
+The other set of studies implemented the more classic priming manipulation, whereby a prime word is briefly presented before the target word in each trial---e.g., *Welcome* → *Selection*.
+This design is more relevant to our present study, as it was used in the study we are revisiting [@hutchison2013a].
+Below, we review studies that have used the *prime* → *target* design.
+
+@lam2015a conducted a semantic priming experiment containing a lexical decision task, in which participants were instructed to assess whether the prime word and the target word in each trial were both real words.
+The semantic priming manipulation consisted of the following types of associations between the prime and the target words: (1) semantic association (e.g., bolt → screwdriver), (2) action association (e.g., housekey → screwdriver), (3) visual association (e.g., soldering iron → screwdriver), and (4) no association (e.g., charger → screwdriver).
+In addition, the following SOAs were compared: 500, 650, 800 and 1,400 ms.
+First, Lam et al.
+observed priming effects of the semantic type with all SOAs.
+Second, the authors observed action-based priming with the SOAs of 500, 650 and 1,400 ms.
+Last, they observed vision-based priming only with the SOA of 1,400 ms.
+Overall, semantic---i.e., language-based---priming was more prevalent than visual and action priming.
+The greater role of language-based information converges with other semantic priming studies [@bottiniNatureSemanticPriming2016; @lam2015a; @pecherDoesPizzaPrime1998; @petilli2021a], as well as with studies that used other paradigms [@banksLinguisticDistributionalKnowledge2021; @kiela2014a; @louwerse2015a].
+
+Similarly, the results of @lam2015a regarding the time course of language-based and vision-based priming were consistent with a wealth of literature observing that the influence of perceptual systems, such as vision, peaks later than the influence of the language system [@barsalouLanguageSimulationConceptual2008; @louwerseTasteWordsLinguistic2011; @santosPropertyGenerationReflects2011].
+For instance, studies using electroencephalography have observed perceptual priming effects within 300 ms from the word onset.
+Thereafter, the perceptual priming effect increased [@bernabeu2017a; @amselEmpiricallyGroundingGrounded2014], or it stabilised [@kieferDifferentialTemporospatialPattern2022], or fluctuated [@amselTrackingRealtimeNeural2011].
+Overall, these patterns reveal a gradual accumulation of information throughout word processing [also see @haukOnlyTimeWill2016], which is consistent with the integration of contextual information [see @haldEEGThetaGamma2006].
+
+In a more recent study, @petilli2021a revisited the data of @hutchison2013a using new variables that indexed language-based and vision-based associations between the prime and the target words.
+These variables had two important characteristics: (1) they were continuous rather than categorical [see @cohenCostDichotomization1983; @guntherLatentSemanticAnalysis2016; @mandera2017a], and (2) they were not dependent on human ratings [cf.
 @hutchisonPredictingSemanticPriming2008; @hutchison2013a; @lam2015a; @pecherDoesPizzaPrime1998].
-The authors used such measures to pursue a comprehensive analysis that was not affected by the problem of circularity between the independent and the dependent variables.
-The circularity problem obtains even though the participants who contributed to the ratings---or 'norms'---are always different from those who participate in the main experiment.
-
+By this means, Petilli et al.
+avoided the circularity problem (rarely addressed in studies) that arises (or may arise) when human-based ratings are used to explain human behaviour.
+
+@petilli2021a operationalised word co-occurrence using text-based similarity [@mandera2017a].
+Next, to operationalise vision-based similarity, the authors obtained images from ImageNet corresponding to each word (a minimum of 100 images per word), and trained vector representations on those images using neural networks [for related work, see @roadsLearningUnsupervisedAlignment2020].
+The resulting computational measure of vision-based similarity was then validated against human-based ratings [@pecherDoesPizzaPrime1998], with a satisfactory result.
+In a concrete demonstration, Petilli et al.
+show how vision-based similarity correctly concluded that drills were more visually similar to pistols than to screwdrivers, showing that the measure was not misled by functional similarity.
+In conclusion, using `language-based similarity` and `vision-based similarity`, Petilli et al.
+investigated language-based and vision-based priming in two tasks---lexical decision and naming---and with both a short and a long SOA.
+
+In lexical decision, the largest effect observed by @petilli2021a was that of language-based priming with the short SOA (200 ms).
+The second largest effect was that of language-based priming with the long SOA (1,200 ms).
+Next, the weakest, significant effect was that of vision-based priming with the short SOA.
+Last, there was no effect of vision-based priming with the long SOA.
 Petilli et al.
-operationalised language-based similarity based on text-based co-occurrence, producing a continuous measure in contrast to the categorical factors used earlier.
-Next, Petilli et al.
-created a visual-similarity measure by retrieving ImageNet images for each word, and training vector representations on those images using neural networks.
-Importantly, the authors compared the resulting visual-similarity measure to previous scores based on human ratings [@pecherDoesPizzaPrime1998], and found a comparable pattern.
-Using these materials, Petilli et al.
-examined language-based and vision-based priming in two tasks---lexical decision and naming---and with both a short and a long SOA.
-In lexical decision, the largest effect observed by the authors was that of language-based priming with the short SOA (150 ms).
-The second largest effect was that of language-based priming with the long SOA (1,200 ms).
-Next, the weakest effect that was significant was that of vision-based priming with the short SOA.
-Last, there was no effect of vision-based priming with the long SOA.
-@petilli2021a explained the absence of vision-based priming with the long SOA in lexical decision by contending that visual activation had likely decayed before participants processed the target words [also see @yeeFunctionFollowsForm2011], owing to the limited semantic processing required for lexical decision [also see @balotaDepthAutomaticSpreading1986; @beckerLongtermSemanticPriming1997; @connell2013a; @dewitMaskedSemanticPriming2015; @joordensLongShortSemantic1997; @ostarekTaskdependentCausalRole2017].
-Therefore, the authors suggested that perceptual simulation does *not* outlast language-based processing in lexical decision, in contrast to the longer latency found in other tasks [@barsalouLanguageSimulationConceptual2008; @louwerseTasteWordsLinguistic2011].
-
-In the naming task of @petilli2021a, the largest effect was that of language-based priming with the long SOA.
+explained the absence of vision-based priming with the long SOA by contending that visual activation had likely decayed before participants processed the target words [also see @yeeFunctionFollowsForm2011], owing to the limited semantic processing required for lexical decision [also see @balotaDepthAutomaticSpreading1986; @beckerLongtermSemanticPriming1997; @dewitMaskedSemanticPriming2015; @joordensLongShortSemantic1997; @ostarekTaskdependentCausalRole2017].
+Therefore, the authors suggested that perceptual simulation does *not* peak before language-based processing in lexical decision, contrasting with the results of @lam2015a and with the results found in other tasks [@louwerseTasteWordsLinguistic2011; @santosPropertyGenerationReflects2011; @simmonsFMRIEvidenceWord2008; also see @barsalouLanguageSimulationConceptual2008].
+
+In the naming task, the largest effect observed by @petilli2021a was that of language-based priming with the long SOA.
 The second largest effect was that of language-based priming with the short SOA.
 Last, there was no effect of vision-based priming with either SOA.
-This finding contrasted with @connellSeeHearWhat2014, who found facilitatory effects of visual strength in both lexical decision and naming.
+This finding contrasts with @connellSeeHearWhat2014, who found facilitatory effects of visual strength in both lexical decision and naming.
 Petilli et al.
-explained the lack of vision-based priming in the naming task by alluding to the lower semantic depth of this task---compared to lexical decision---, and the mixture of visual and auditory processing in the naming task [@connellSeeHearWhat2014].
-
-In the present study, we revisited the interplay between linguistic and perceptual simulation by conceptually replicating @petilli2021a.
-Specifically, we used the same primary data set [@hutchison2013a], and a language-based similarity measure that was very similar to that used by @petilli2021a [both our measure and theirs originated from @mandera2017a].
-In contrast, our predictors in the domain of vision differed.
+explained the lack of vision-based priming in the naming task by alluding to the lower semantic depth of this task---compared to lexical decision---, and the mixture of visual and auditory processing in this task [also see @connellSeeHearWhat2014].
+
+In conclusion, there is mixed evidence regarding the time course of language-based and vision-based information in conceptual processing, and particularly in semantic priming.
+First, regarding language, previous research predicts that language-based priming will have a larger effect with the short SOA than with the long one [@lam2015a; @petilli2021a].
+Second, regarding vision, three hypotheses are available: (a) more vision-based priming with the long SOA [@louwerseTasteWordsLinguistic2011; @santosPropertyGenerationReflects2011; @simmonsFMRIEvidenceWord2008; also see @barsalouLanguageSimulationConceptual2008], (b) vision-based priming only with the short SOA [@petilli2021a], and (c) no vision-based priming [@hutchisonSemanticPrimingDue2003; @ostarekTaskdependentCausalRole2017; @pecherDoesPizzaPrime1998; @yeeColorlessGreenIdeas2012].
+
+## Language, vision and vocabulary size
+
+Next, we turn to considering the role of participants' vocabulary size with respect to language-based and vision-based information (this recaps the general [\underline{Hypotheses}](#hypotheses) section).
+First, three hypotheses exist the interaction with language.
+On the one hand, some research predicts a larger effect of language-based priming in higher-vocabulary participants [@yap2017a; also see @connell2019a; @landauerIntroductionLatentSemantic1998; @louwerse2015a; @paivioMentalRepresentationsDual1990; @pylyshynWhatMindEye1973].
+On the other hand, other research has found the opposite pattern [@yapIndividualDifferencesJoint2009; also see @yap2012a].
+Also relevant to these mixed findings is the notion that vocabulary knowledge is associated with increased attention to task-relevant variables [@pexman2018a].
+We hypothesised that language-based information---represented by `language-based similarity` in this study---was indeed important for present task, given its importance across the board [@banksLinguisticDistributionalKnowledge2021; @kiela2014a; @louwerse2015a; @lam2015a; @pecherDoesPizzaPrime1998; @petilli2021a].
+Accordingly, the relevance hypothesis predicted that higher-vocabulary participants would present a larger priming effect.
+
+To our knowledge, no previous studies have investigated the interaction between vision-based information and participants' vocabulary size.
+We entertained two hypotheses: (a) that lower-vocabulary participants would be more sensitive to visual strength than higher-vocabulary participants, thereby compensating for the disadvantage on the language side, and (b) that this interaction effect would be absent.
+
+## The present study
+
+In the present study, we expanded on @petilli2021a by examining the role of participants' vocabulary size.
+In other regards, we used the same primary data set [@hutchison2013a], and a language-based similarity measure that was very similar to that used by Petilli et al.
+[also created by @mandera2017a].
+In contrast, our vision-based predictors differed.
 Whereas Petilli et al.
-used a human-independent measure based on images from the Internet (see description above), we drew on visual strength---from the modality ratings of @lynott2020a---and calculated the difference in visual strength between the prime and the target word in each trial.^[These measures are compared at [\underline{the end of the Results section}](#comparing-two-measures-of-vision-based-information).]
+used a human-independent measure trained on images (see description above), we calculated the difference in visual strength [@lynott2020a] between the prime and the target word in each trial.^[These measures are compared at [\underline{the end of the Results section}](#results-human-based-and-computational-measures-of-visual-information).]
 
@@
 
-### Effects of interest
-
-- $Z$-scored vocabulary size [`z_vocabulary_size`; calculated from average of `vocaba`, `vocabb` and `vocabc` in @hutchison2013a].
-The test used by @hutchison2013a comprised a synonym test, an antonym test, and an analogy test, all three extracted from the Woodcock–Johnson III diagnostic reading battery [@woodcockWoodcockJohnsonIII2001].
-We operationalised the vocabulary measure as the mean score across the three tasks per participant.
-
-- $Z$-scored, recoded participants' gender [`z_recoded_participant_gender`; calculated from `gender` in @hutchison2013a]
-
-- $Z$-scored language-based similarity between prime and target words [`z_cosine_similarity`].
-This measure was calculated using a semantic space from @mandera2017a, which the authors found to be the second-best predictor ($R$^2^ = .465) of the semantic priming effect in the lexical decision task of @hutchison2013a (we could not use the best semantic space, $R$^2^ = .471, owing to computational limitations).
-The second-best semantic space [see first row in Table 5 of @mandera2017a] was based on lemmas from a subtitle corpus, processed in a Continuous Bag Of Words model, and the space had 300 dimensions and a window size of 6.
-
-- $Z$-scored vision-based information in words [`z_visual_rating_diff`; calculated from `Visual.mean` in @lynott2020a]
-
-- $Z$-scored, recoded SOA [`z_recoded_interstimulus_interval`; calculated from `isi` in @hutchison2013a]
+### Data set {#semanticpriming-dataset}
 
@@
 
-# Calculate numbers to be reported in the paragraph below
-
-# Save number of participants and prime-target pairs
-semanticpriming_number_participants = 
-  length(unique(semanticpriming$Participant))
-
-semanticpriming_number_primetarget_pairs = 
-  length(unique(semanticpriming$primeword_targetword))
+# Calculate some of the sample sizes to be reported in the paragraph below
 
@@
 
-The final data set contained `r semanticpriming_number_participants` participants, `r semanticpriming_number_primetarget_pairs %>% formattable::comma(digits = 0)` prime-target pairs, and `r length(semanticpriming$z_target.RT) %>% formattable::comma(digits = 0)` RTs.
-On average, there were `r semanticpriming_mean_primetarget_pairs_per_participant` prime-target pairs per participant ($SD$ = `r semanticpriming_SD_primetarget_pairs_per_participant`), and conversely, `r semanticpriming_mean_participants_per_primetarget_pair` participants per prime-target pair ($SD$ = `r semanticpriming_SD_participants_per_primetarget_pair`).
-
-Figure \@ref(fig:semanticpriming-correlations) shows the zero-order correlations among the predictors and the dependent variable.
+The data set was trimmed by removing rows that lacked values on any variable, and by also removing RTs that were more than 3 standard deviations away from the mean.
+The standard deviation trimming was performed within participants, within sessions and within SOA conditions, as done in the Semantic Priming Project [@hutchison2013a].
+The resulting data set contained `r length(unique(semanticpriming$Participant))` participants, `r length(unique(semanticpriming$primeword_targetword)) %>% formattable::comma(digits = 0)` prime--target pairs and `r length(semanticpriming$z_target.RT) %>% formattable::comma(digits = 0)` RTs.
+On average, there were `r semanticpriming_mean_primetarget_pairs_per_participant` prime--target pairs per participant ($SD$ = `r semanticpriming_SD_primetarget_pairs_per_participant`), and conversely, `r semanticpriming_mean_participants_per_primetarget_pair` participants per prime--target pair ($SD$ = `r semanticpriming_SD_participants_per_primetarget_pair`).
+
+### Variables
+
+While the variables are generally described in the [\underline{general introduction}](#present-studies), a few further details are provided below regarding two of them.
+
+- `Vocabulary size`.
+The test used by @hutchison2013a comprised a synonym test, an antonym test, and an analogy test, all three extracted from the Woodcock–Johnson III diagnostic reading battery [@woodcockWoodcockJohnsonIII2001].
+We operationalised the vocabulary measure as the mean score across the three tasks per participant.
+
+- `Language-based similarity`.
+This measure was calculated using a semantic space from @mandera2017a, which the authors found to be the second-best predictor ($R$^2^ = .465) of the semantic priming effect in the lexical decision task of @hutchison2013a (we could not use the best semantic space, $R$^2^ = .471, owing to computational limitations).
+The second-best semantic space [see first row in Table 5 in @mandera2017a] was based on lemmas from a subtitle corpus, and was processed using a Continuous Bag Of Words model.
+It had 300 dimensions and a window size of six words.
+The R package 'LSAfun' [@R-LSAfun] was used to import this variable.^[Despite the name of the package, the measure we used was not based on Latent Semantic Analysis.]
+
+- `Stimulus onset asynchrony (SOA)`. Following @brauer2018a, the categories of this factor were recoded as follows: 200 ms = -0.5, 1,200 ms = 0.5.
+
+A few details regarding the covariates follow.
+
+- `Attentional control` [@hutchison2013a] was included as a measure akin to general cognition, and specifically as a covariate of vocabulary size [@ratcliff2010a].
+The role of attentional control in semantic priming was evidenced by @yap2017a.
+Attentional control comprised three attention-demanding tasks, namely, operation span, Stroop and antisaccade [@hutchison2013a].
+
+- Lexical covariates (see [\underline{Appendix A}](#appendix-A-lexical-covariates)): `word frequency` and `orthographic Levenshtein distance` [@balota2007a].
+
+- `Word concreteness` [@brysbaert2014a], used as a covariate of visual strength.
+
+Figure \@ref(fig:semanticpriming-correlations) shows the correlations among the predictors and the dependent variable.
 
@@
 
-### Covariates
-
-The following covariates were included in the model to allow a rigorous analysis of the effects of interest.
-
-- Lexical (see [\underline{Appendix A}](#appendix-A-lexical-covariates)): $z$-scored word frequency and orthographic Levenshtein distance [@balota2007a]
-
-- Semantic: $z$-scored word concreteness [@brysbaert2014a], used as a covariate of visual rating.
-
-- Individual differences: $z$-scored attentional control [@hutchison2013a].
-This covariate is related to vocabulary size [@ratcliff2010a], and previous studies have expressed the desirability of including such covariates [@james2018a; @pexman2018a].
-Attentional control was operationalised as the average score across three tasks of @hutchison2013a---namely, operation span, Stroop and antisaccade.
-
-### Diagnostics for the frequentist model
+### Diagnostics for the frequentist analysis
 
 The model presented convergence warnings.
-To avoid removing important random slopes, which could increase the Type I error [@brauer2018a; @singmann2019a], we examined the model after refitting it using seven optimization algorithms through the 'allFit' function of the R package 'lme4' [@batesPackageLme42021].
-The results showed that all optimizers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential (Bates et al., 2021; see [\underline{Appendix B}](#appendix-B-frequentist-analysis-diagnostics)).
+To avoid removing important random slopes, which could increase the Type I error rate---i.e., false positives [@brauer2018a; @singmann2019a], we examined the model after refitting it using seven optimisation algorithms through the 'allFit' function of the R package 'lme4' [@batesPackageLme42021].
+The results showed that all optimisers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential (Bates et al., 2021; see [\underline{Appendix B}](#appendix-B-frequentist-analysis-diagnostics)).
+
+```{r}
+
+# Calculate VIF for every predictor and return only the maximum VIF rounded up
+maxVIF_semanticpriming = car::vif(semanticpriming_lmerTest) %>% max %>% ceiling
+
+```
 
@@
 However, this is not likely to have posed a major problem, as mixed-effects models are fairly robust to deviations from normality [@kniefViolatingNormalityAssumption2021; @schielzethRobustnessLinearMixed2020].
+Last, the model did not present multicollinearity problems, with all variance inflation factors (VIF) below `r maxVIF_semanticpriming` [see @dormannCollinearityReviewMethods2013; @harrison2018a].
+
+### Diagnostics for the Bayesian analysis
 
@@
 
-# Calculate VIF for every predictor and return only the maximum VIF rounded up
-maxVIF_semanticpriming = car::vif(semanticpriming_lmerTest) %>% max %>% ceiling
-
-```
-
-The model did not present multicollinearity problems, all variance inflation factors (VIF) being smaller than `r maxVIF_semanticpriming` [@dormannCollinearityReviewMethods2013; @harrison2018a].
-
-### Diagnostics for the Bayesian model
-
-```{r}
-
 # Calculate number of post-warmup draws (as in 'brms' version 2.17.0).
-# Informative prior model used but same numbers in all three models.
+# Informative prior model used but numbers are identical in the three models.
 semanticpriming_post_warmup_draws = 
@@
   max(semanticpriming_summary_informativepriors_exgaussian$fixed$Rhat,
-      # semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed$Rhat,
+      semanticpriming_summary_weaklyinformativepriors_exgaussian$fixed$Rhat,
       semanticpriming_summary_diffusepriors_exgaussian$fixed$Rhat) %>% 
@@
 
-# Next, find find maximum R-hat value for the random effects 
-# across the three models. 
+# Next, find find maximum R-hat value for the random effects across the three models
 semanticpriming_randomeffects_max_Rhat = 
   max(semanticpriming_summary_informativepriors_exgaussian$random[['Participant']]$Rhat,
-      # semanticpriming_summary_weaklyinformativepriors_exgaussian$random[['Participant']]$Rhat,
+      semanticpriming_summary_weaklyinformativepriors_exgaussian$random[['Participant']]$Rhat,
       semanticpriming_summary_diffusepriors_exgaussian$random[['Participant']]$Rhat,
       semanticpriming_summary_informativepriors_exgaussian$random[['primeword_targetword']]$Rhat,
-      # semanticpriming_summary_weaklyinformativepriors_exgaussian$random[['primeword_targetword']]$Rhat,
+      semanticpriming_summary_weaklyinformativepriors_exgaussian$random[['primeword_targetword']]$Rhat,
       semanticpriming_summary_diffusepriors_exgaussian$random[['primeword_targetword']]$Rhat) %>% 
@@
 
-Three Bayesian models were run that were respectively characterised by informative, weakly-informative and diffuse priors (note that the weakly-informative prior model has not yet finished running).
+Three Bayesian models were run that were respectively characterised by informative, weakly-informative and diffuse priors.
 In each model, `r semanticpriming_summary_informativepriors_exgaussian$chains` chains were used.
@@
 
-The maximum $\widehat R$ value for the fixed effects in both models was `r semanticpriming_fixedeffects_max_Rhat`, suggesting that these parameters had converged [@schootBayesianStatisticsModelling2021; @vehtariRanknormalizationFoldingLocalization2021].
-In contrast, the maximum $\widehat R$ value for the random effects was `r semanticpriming_randomeffects_max_Rhat`, exceeding the 1.01 threshold [@vehtariRanknormalizationFoldingLocalization2021].
-Therefore, models with more iterations will be run, and once completed, they will be reported in this manuscript.
-
-The posterior predictive checks were sound (see [\underline{Appendix C}](#appendix-C-Bayesian-analysis-diagnostics)).
-Furthermore, in the prior sensitivity analysis, the results were virtually identical with the three priors that were considered (to recall the priors, see Figure \@ref(fig:bayesian-priors) above; to view the results in detail, see [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results)).
-
-## Results {#semanticpriming-results}
+The maximum $\widehat R$ value for the fixed effects across the three models was `r semanticpriming_fixedeffects_max_Rhat`, suggesting that these parameters had converged [@schootBayesianStatisticsModelling2021; @vehtariRanknormalizationFoldingLocalization2021].
+In contrast, the maximum $\widehat R$ value for the random effects was `r semanticpriming_randomeffects_max_Rhat`, slightly exceeding the 1.01 threshold [@vehtariRanknormalizationFoldingLocalization2021].
+Since the interest of the present research is on the fixed effects, and the random effects were very close to convergence, the present model is valid.
+
+The results of the posterior predictive checks were sound (see [\underline{Appendix C}](#appendix-C-Bayesian-analysis-diagnostics)), indicating that the posterior distributions were sufficiently consistent with the observed data.
+Furthermore, in the prior sensitivity analysis, the results were virtually identical with the three priors that were considered (refer to the priors in Figure \@ref(fig:bayesian-priors) above; to view the results in detail, see [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results)).
+
+## Results of Study 1 {#semanticpriming-results}
 
@@
 
-Table \@ref(tab:semanticpriming-frequentist-model) presents the results of the frequentist model.
-The fixed effects explained `r Nakagawa2017_fixedeffects_R2_semanticpriming_lmerTest` of the variance, and the random effects `r Nakagawa2017_randomeffects_R2_semanticpriming_lmerTest` [@nakagawaCoefficientDeterminationR22017].
-It is to be expected that random effects explain more variance, as they involve a far larger number of coefficients for each effect.
-For instance, the by-item random slopes (specifically, by prime-target pair) for a single individual-level variable (e.g., vocabulary size) involve as many coefficients as the number of items.
-Conversely, the by-participant random slopes for a single item-level variable (e.g., language-based similarity) involve as many coefficients as the number of participants.
-In contrast, each fixed effect involves 1 coefficient only.
+Table \@ref(tab:semanticpriming-frequentist-model) presents the results.
+The fixed effects explained `r Nakagawa2017_fixedeffects_R2_semanticpriming_lmerTest` of the variance, and the random effects explained `r Nakagawa2017_randomeffects_R2_semanticpriming_lmerTest` [@nakagawaCoefficientDeterminationR22017].
+It is reasonable that random effects explain more variance, as they involve a far larger number of estimates for each effect.
+That is, whereas each fixed effect is formed of one estimate, the by-item random slopes for an individual difference variable---such as vocabulary size---comprise as many estimates as the number of stimulus items (in this study, the stimuli refer to the prime--target pairs).^[For future reference, it should be noted that, in Studies 2 and 3, the *stimuli* are the stimulus words, as there are no prime words in those studies.] Conversely, the by-participant random slopes for an item-level variable---such as language-based similarity---comprise as many estimates as the number of participants.
 
@@
   rownames(KR_summary_semanticpriming_lmerTest$coefficients) == 
-    'z_recoded_interstimulus_interval'] = 'Stimulus-onset asynchrony (SOA) $^{\\text{b}}$'
+    'z_recoded_interstimulus_interval'] = 'Stimulus onset asynchrony (SOA) $^{\\text{b}}$'
 
@@
   rownames(confint_semanticpriming_lmerTest) == 
-    'z_recoded_interstimulus_interval'] = 'Stimulus-onset asynchrony (SOA) $^{\\text{b}}$'
+    'z_recoded_interstimulus_interval'] = 'Stimulus onset asynchrony (SOA) $^{\\text{b}}$'
 
@@
   footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
-           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored variables; \\\\textit{SE} = standard error;',
+           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored predictors; \\\\textit{SE} = standard error;',
                            'CI = confidence interval. Shaded rows contain covariates. Some interactions are',
@@
 
-Figure \@ref(fig:semanticpriming-frequentist-bayesian-plot-informativepriors-exgaussian) displays the frequentist estimates alongside the Bayesian estimates.
-The latter are from the informative prior model.
-The estimates of the diffuse prior model were virtually identical to these (see [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results)).
-
-```{r semanticpriming-frequentist-bayesian-plot-informativepriors-exgaussian, fig.cap = 'Estimates from the frequentist analysis (in red) and from the Bayesian analysis (in blue) for the semantic priming study.
-The frequentist means (represented by points) are flanked by 95\\% confidence intervals.
-The Bayesian means (represented by vertical lines) are flanked by 95\\% credible intervals, in light blue (in some cases, the interval is covered up by the bar of the mean).'}
+Both language-based similarity and visual-strength difference produced significant main effects.
+As expected, their effects had opposite directions.
+On the one hand, higher values of language-based similarity facilitated participants' performance, as reflected in shorter RTs.
+On the other hand, higher values of visual-strength difference led to longer RTs.
+Furthermore, language-based similarity interacted with vocabulary size and with SOA.
+There were no effects of participants' gender (see interaction figures below).
+
+The effect sizes of language-based similarity and its interactions were larger than those of visual-strength difference.
+Figure \@ref(fig:semanticpriming-frequentist-bayesian-plot-weaklyinformativepriors-exgaussian) displays the frequentist and the Bayesian estimates, which are broadly similar.
+The Bayesian estimates are from the weakly-informative prior model.
+The estimates of the two other models, based on informative and diffuse priors, were virtually identical to these (see [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results)).
+
+\FloatBarrier
+
+```{r semanticpriming-frequentist-bayesian-plot-weaklyinformativepriors-exgaussian, fig.cap = 'Estimates for the semantic priming study.
+The frequentist means (represented by red points) are flanked by 95\\% confidence intervals.
+The Bayesian means (represented by blue vertical lines) are flanked by 95\\% credible intervals in light blue.'}
 
@@
     getwd(),  # Circumvent illegal characters in file path
-    '/semanticpriming/frequentist_bayesian_plots/plots/semanticpriming_frequentist_bayesian_plot_informativepriors_exgaussian.pdf'
+    '/semanticpriming/frequentist_bayesian_plots/plots/semanticpriming_frequentist_bayesian_plot_weaklyinformativepriors_exgaussian.pdf'
   ))
@@
 
-Figure \@ref(fig:semanticpriming-interactions-with-vocabulary-size)-a shows the interaction between vocabulary size and language-based similarity, whereby higher-vocabulary participants presented a greater benefit from the language-based similarity between prime and target words.
-That is, the greater the similarity between prime and target words, the greater the advantage for participants with higher vocabularies.
+Figure \@ref(fig:semanticpriming-interactions-with-vocabulary-size)-a shows the significant interaction between language-based similarity and vocabulary size, whereby higher-vocabulary participants presented a greater benefit from the language-based similarity between prime and target words.
 This interaction replicates the results of @yap2017a, who analysed the same data set but using a categorical measure of similarity instead.
 Indeed, this replication is noteworthy as it holds in spite of some methodological differences between the studies.
-First, @yap2017a operationalised the priming effect as a categorical difference between related and unrelated prime-target pairs.
+First, @yap2017a operationalised the priming effect as a categorical difference between related and unrelated prime--target pairs, which were based on association ratings produced by people [@nelsonUniversitySouthFlorida2004].
 In contrast, the present study applied a continuous measure of relatedness---i.e., cosine similarity---, which is more precise and may thus afford more statistical power [@mandera2017a; @petilli2021a].
-Second, the analysis conducted by @yap2017a was correlational, whereas the present analysis used mixed-effects models that included several covariates to measure the effects of interest as rigorously as possible.
-
-Figure \@ref(fig:semanticpriming-interactions-with-vocabulary-size)-b presents the interaction between vocabulary size and visual-strength difference.^[All interaction plots across the three studies are based on the frequentist models.] Albeit a non-significant interaction, it is noteworthy that the effect of visual-strength difference is larger in lower-vocabulary participants.
-
-(ref:semanticpriming-interactions-with-vocabulary-size) Interactions of vocabulary size with language-based similarity and visual-strength difference.
-Vocabulary size is constrained to deciles (ten sections) in this plot, whereas in the statistical analysis it contained more values within the current range.
-*n* = number of participants contained between deciles.
+Therefore, this interaction demonstrates the consistency between human ratings and computational approximations to meaning [@charbonnierPredictingWordConcreteness2019; @charbonnierPredictingConcretenessGerman2020; @guenther2016a; @louwerse2015a; @mandera2017a; @petilli2021a; @solovyevConcretenessAbstractnessConcept2021; @wingfieldUnderstandingRoleLinguistic2022].
+The second difference between the present study and @yap2017a is that @yap2017a performed a correlational analysis, whereas the present analysis used maximal mixed-effects models that included several covariates to measure the effects of interest as rigorously as possible.
+
+Figure \@ref(fig:semanticpriming-interactions-with-vocabulary-size)-b presents the non-significant interaction between visual-strength difference and vocabulary size.^[All interaction plots across the three studies are based on the frequentist models.
+Further interaction plots available in [\underline{Appendix D}](#appendix-D-interaction-plots).] Albeit a non-significant interaction, the effect of visual-strength difference was larger in lower-vocabulary participants.
+
+(ref:semanticpriming-interactions-with-vocabulary-size) Interactions of vocabulary size with language-based similarity (panel a) and with visual-strength difference (panel b).
+Vocabulary size is constrained to deciles (10 sections) in this plot, whereas in the statistical analysis it contained more values within the current range.
+$n$ = number of participants contained between deciles.
 
@@
 
-Methodologically, the interaction between vocabulary size and language-based similarity underscores the consistency that exists between human ratings and computational approximations to meaning [e.g., @charbonnierPredictingWordConcreteness2019; @charbonnierPredictingConcretenessGerman2020; @guenther2016a; @louwerse2015a; @mandera2017a; @petilli2021a; @solovyevConcretenessAbstractnessConcept2021; @wingfieldUnderstandingRoleLinguistic2022].
-In contrast to this consistency, some studies have found human ratings to have more explanatory power than computational measures [@de2016a; @de2019a; @gagneProcessingEnglishCompounds2016; @schmidtke2018a], and other research has suggested that some computational measures are not intrinsically contentful, but arise from a missing-data problem [@snefjella2020a].
-In sum, this evidence suggests that computational measures are artificial, and yet valid for the study of cognition.
-
-Figure \@ref(fig:semanticpriming-interactions-with-SOA) shows that the effects of language-based similarity and visual strength were both larger with the short SOA.
-Yet there is a notable difference: whereas the effect of language-based similarity is present with both SOAs (i.e., 150 ms and 1,200 ms), the effect of visual strength is almost reserved to the the long SOA.
-This finding replicates @petilli2021a, and stands in contrast to previous findings regarding the slower pace of the visual system in semantic priming [@lam2015a] and in other paradigms [@connell2013a; @louwerseTasteWordsLinguistic2011].
-__conclude_______________
-
-```{r semanticpriming-interactions-with-SOA, fig.cap = 'Interactions of stimulus-onset asynchrony (SOA) with language-based similarity and visual strength.
-SOA was analysed using $z$-scores, but for clarity, the variable is shown in its basic form here.', out.width = '80%'}
+Figure \@ref(fig:semanticpriming-interactions-with-SOA) shows that the effects of language-based similarity and visual-strength difference were both larger with the short SOA.
+However, whereas the effect of language-based similarity was present with both SOAs (i.e., 200 ms and 1,200 ms), the effect of visual-strength difference was almost exclusive to the the long SOA.
+These results are consistent with @petilli2021a, whereas they contrast with previous findings regarding the slower pace of the visual system in semantic priming [@lam2015a] and in other paradigms [@louwerseTasteWordsLinguistic2011].
+
+```{r semanticpriming-interactions-with-SOA, fig.cap = 'Interactions of stimulus onset asynchrony (SOA) with language-based similarity (panel a) and with visual-strength difference (panel b) in the semantic priming study.
+SOA was analysed using $z$-scores, but for clarity, the basic labels are used in the legend.', out.width = '80%'}
 
@@
 
-Figure \@ref(fig:semanticpriming-interactions-with-gender) shows the interactions of gender with language-based similarity and visual-strength difference, albeit non-significant.^[Plots of other interactions are available in [\underline{Appendix D}](#appendix-D-interaction-plots).]
-
-```{r semanticpriming-interactions-with-gender, fig.cap = 'Interactions with gender in the semantic priming study.
-Gender was analysed using $z$-scores, but for clarity, the variable is shown in its basic form here.', out.width = '80%'}
+Figure \@ref(fig:semanticpriming-interactions-with-gender) shows the non-significant interactions of gender with language-based similarity and with visual-strength difference.
+
+```{r semanticpriming-interactions-with-gender, fig.cap = 'Interactions of gender with language-based similarity (panel a) and with visual-strength difference (panel b) in the semantic priming study.
+Gender was analysed using $z$-scores, but for clarity, the basic labels are used in the legend.', out.width = '80%'}
 
@@
 
-#### The importance of outliers
-
-The interaction shown in Figure \@ref(fig:semanticpriming-interactions-with-vocabulary-size) was patent in all deciles of vocabulary size but most notably in the participants who lie more than 1 standard deviation away from the mean.
-Outliers in individual differences have played important roles in other areas of cognition as well, such as in the domains of aphantasia and hyperphantasia---traits characterised, respectively, by a diminished and an extraordinary ability to mentally visualise objects [@milton2021a; @zeman2020a].
-Furthermore, if we consider the difficulty of detecting effects involving individual differences [@diazNeuralSensitivityPhonological2021; @hedge2018a; @rodriguez-ferreiroSemanticPrimingSchizotypal2020], and the limited representativeness of most samples of participants [@henrich2010a], it may be fruitful to study more varied samples, where possible.
-
-### Comparing two measures of vision-based information {#comparing-two-measures-of-vision-based-information}
-
-Next, we reflected on the adequacy of visual-strength difference as a measurement instrument, as it had never been used before to operationalise the semantic priming effect.
-On the one hand, its effect on RT was negative, as we would expect.
-However, we were concerned about the low correlation between this variable and language-based similarity ($r$ = `r cor(semanticpriming$z_cosine_similarity, semanticpriming$z_visual_rating_diff) %>% sprintf('%.2f', .)`).
-This concern was especially motivated by the correlation that @petilli2021a had found between their 'vision-based similarity' measure and language-based similarity, which reached $r$ = .50.
-Based on this information, we set out to run a model with the aim of comparing the performance of our measures of vision-based information.
+### Human-based and computational measures of visual information {#results-human-based-and-computational-measures-of-visual-information}
+
+Next, we reflected on the adequacy of visual-strength difference as a measurement instrument, as it had never (to our knowledge) been used before in the study of semantic priming.
+Even though the effect of this variable on task performance was---as expected---inhibitory (i.e., higher values of this variable leading to longer RTs), we were concerned about the low correlation between visual-strength difference and language-based similarity ($r$ = `r cor(semanticpriming$z_cosine_similarity, semanticpriming$z_visual_rating_diff) %>% sprintf('%.2f', .) %>% sub('^(-)?0[.]', '\\1.', .)`).
+First, the negligible size of this correlation raised concerns, as we expected a larger and negative correlation.
+Second, @petilli2021a had found a correlation of $r$ = .50 between vision-based similarity and language-based similarity.
+This prompted us to compare the performance of our measure---i.e., `visual-strength difference`---to that of Petilli et al.---i.e., `vision-based similarity`.
 
@@
 
-# Calculate numbers to be reported in the paragraph below
-
-# Save number of participants and prime-target pairs
-semanticpriming_with_visualsimilarity_number_participants = 
-  length(unique(semanticpriming_with_visualsimilarity$Participant))
-
-semanticpriming_with_visualsimilarity_number_primetarget_pairs =
-  length(unique(semanticpriming_with_visualsimilarity$primeword_targetword))
-
-# Number of prime-target pairs per participant.
+# Calculate some of the sample sizes to be reported in the paragraph below
+
+# Number of prime--target pairs per participant.
 # Save mean as integer and SD rounded while keeping trailing zeros
@@
 
-# Number of participants per prime-target pair.
+# Number of participants per prime--target pair.
 # Save mean as integer and SD rounded while keeping trailing zeros
@@
 
-We created a subset of our data set in which we ensured that all the trials contained data from all the relevant variables---i.e., from all the existing variables and from the newly-added visual similarity from Petilli et al.
-This subsetting resulted in the loss of 83% of trials, owing to the strict selection criteria applied by Petilli et al.
-in the creation of the visual-similarity measure (e.g., both the target and the prime word had to be associated to at least 100 pictures in ImageNet).
-As a result, our data set in this analysis contained `r semanticpriming_with_visualsimilarity_number_participants` participants, `r semanticpriming_with_visualsimilarity_number_primetarget_pairs %>% formattable::comma(digits = 0)` prime-target pairs, and `r length(semanticpriming_with_visualsimilarity$z_target.RT) %>% formattable::comma(digits = 0)` RTs.
-On average, there were `r semanticpriming_with_visualsimilarity_mean_primetarget_pairs_per_participant` prime-target pairs per participant ($SD$ = `r semanticpriming_with_visualsimilarity_SD_primetarget_pairs_per_participant`), and conversely, `r semanticpriming_with_visualsimilarity_mean_participants_per_primetarget_pair` participants per prime-target pair ($SD$ = `r semanticpriming_with_visualsimilarity_SD_participants_per_primetarget_pair`).
-
-Figure \@ref(fig:semanticpriming-with-visualsimilarity-correlations) shows the zero-order correlations among the predictors and the dependent variable.
-
-```{r semanticpriming-with-visualsimilarity-correlations, fig.cap = 'Zero-order correlations in the semantic priming data set that included visual similarity.', fig.width = 8.3, fig.height = 5, out.width = '73%'}
+For this purpose, we first subsetted our previous data set to ensure that all trials contained data from all relevant variables---i.e., from all the existing variables and from the newly-added `vision-based similarity` from @petilli2021a.
+This process resulted in the loss of 83% of trials, owing to the strict selection criteria that had been applied by Petilli et al.
+in the creation of their variable---for instance, both the target and the prime word had to be associated to at least 100 pictures in ImageNet.
+The rest of the preprocessing involved the same steps as the main analysis (detailed in [\underline{Methods}](#semanticpriming-dataset)).
+The resulting data set contained `r length(unique(semanticpriming_with_visualsimilarity$Participant))` participants, `r length(unique(semanticpriming_with_visualsimilarity$primeword_targetword)) %>% formattable::comma(digits = 0)` prime--target pairs and `r length(semanticpriming_with_visualsimilarity$z_target.RT) %>% formattable::comma(digits = 0)` RTs.
+On average, there were `r semanticpriming_with_visualsimilarity_mean_primetarget_pairs_per_participant` prime--target pairs per participant ($SD$ = `r semanticpriming_with_visualsimilarity_SD_primetarget_pairs_per_participant`), and conversely, `r semanticpriming_with_visualsimilarity_mean_participants_per_primetarget_pair` participants per prime--target pair ($SD$ = `r semanticpriming_with_visualsimilarity_SD_participants_per_primetarget_pair`).
+
+Figure \@ref(fig:semanticpriming-with-visualsimilarity-correlations) shows the correlations among the predictors and the dependent variable.
+
+```{r semanticpriming-with-visualsimilarity-correlations, fig.cap = 'Zero-order correlations in the semantic priming data set that included vision-based similarity.', fig.width = 8.3, fig.height = 5, out.width = '73%'}
 
@@
 
-### Diagnostics for the frequentist model
+### Diagnostics for the frequentist analysis
 
 The model presented convergence warnings.
-To avoid removing important random slopes, which could increase the Type I error [@brauer2018a; @singmann2019a], we examined the model after refitting it using seven optimization algorithms through the 'allFit' function of the 'lme4' package [@batesPackageLme42021].
-The results showed that all optimizers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential (Bates et al., 2021; see [\underline{Appendix B}](#appendix-B-frequentist-analysis-diagnostics)).
-
-The residual errors were not normally distributed, and attempts to mitigate this deviation proved unsuccessful (see [\underline{Appendix B}](#appendix-B-frequentist-analysis-diagnostics)).
-However, this is not likely to have posed a major problem, as mixed-effects models are fairly robust to deviations from normality [@kniefViolatingNormalityAssumption2021; @schielzethRobustnessLinearMixed2020].
+To avoid removing important random slopes, which could increase the Type I error rate---i.e., false positives [@brauer2018a; @singmann2019a], we examined the model after refitting it using seven optimisation algorithms through the 'allFit' function of the 'lme4' package [@batesPackageLme42021].
+The results showed that all optimisers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential (Bates et al., 2021; see [\underline{Appendix B}](#appendix-B-frequentist-analysis-diagnostics)).
 
@@
 
-The model did not present multicollinearity problems, all VIFs being smaller than `r maxVIF_semanticpriming_with_visualsimilarity` [@dormannCollinearityReviewMethods2013; @harrison2018a].
-
-Due to time constraints, this analysis did not include a Bayesian model.
+The residual errors were not normally distributed, and attempts to mitigate this deviation proved unsuccessful (see [\underline{Appendix B}](#appendix-B-frequentist-analysis-diagnostics)).
+However, this is not likely to have posed a major problem, as mixed-effects models are fairly robust to deviations from normality [@kniefViolatingNormalityAssumption2021; @schielzethRobustnessLinearMixed2020].
+Last, the model did not present multicollinearity problems, with all VIFs below `r maxVIF_semanticpriming_with_visualsimilarity` [see @dormannCollinearityReviewMethods2013; @harrison2018a].
 
@@
 
-Table \@ref(tab:semanticpriming-with-visualsimilarity-frequentist-model) presents the results of the frequentist model.
+Table \@ref(tab:semanticpriming-with-visualsimilarity-frequentist-model) presents the results.
 Due to space, the covariates are shown in Table \@ref(tab:semanticpriming-with-visualsimilarity-frequentist-model-covariates).
-The fixed effects explained `r Nakagawa2017_fixedeffects_R2_semanticpriming_with_visualsimilarity_lmerTest` of the variance, and the random effects `r Nakagawa2017_randomeffects_R2_semanticpriming_with_visualsimilarity_lmerTest` (Nakagawa et al., 2017; for an explanation of this difference, see [\underline{above}](#semanticpriming-results)).
-Figure \@ref(fig:semanticpriming-with-visualsimilarity-confidence-intervals-plot) displays the estimates for the effects of interest.
+The fixed effects explained `r Nakagawa2017_fixedeffects_R2_semanticpriming_with_visualsimilarity_lmerTest` of the variance, and the random effects explained `r Nakagawa2017_randomeffects_R2_semanticpriming_with_visualsimilarity_lmerTest` (Nakagawa et al., 2017; for an explanation of this difference, see [\underline{Results of Study 1}](#semanticpriming-results)).
+Figure \@ref(fig:semanticpriming-with-visualsimilarity-confidence-intervals-plot) displays the frequentist estimates of the effects of interest (Bayesian estimates not computed due to time constraints).
 
@@
   rownames(KR_summary_semanticpriming_with_visualsimilarity_lmerTest$coefficients) == 
-    'z_recoded_interstimulus_interval'] = 'Stimulus-onset asynchrony (SOA) $^{\\text{b}}$'
+    'z_recoded_interstimulus_interval'] = 'Stimulus onset asynchrony (SOA) $^{\\text{b}}$'
 
@@
   rownames(confint_semanticpriming_with_visualsimilarity_lmerTest) == 
-    'z_recoded_interstimulus_interval'] = 'Stimulus-onset asynchrony (SOA) $^{\\text{b}}$'
+    'z_recoded_interstimulus_interval'] = 'Stimulus onset asynchrony (SOA) $^{\\text{b}}$'
 
@@
                      'Vision-based similarity $^{\\text{b}}$',
-                     'Stimulus-onset asynchrony (SOA) $^{\\text{b}}$',
+                     'Stimulus onset asynchrony (SOA) $^{\\text{b}}$',
                      # 'Word-concreteness difference :: Vocabulary size',
@@
   interaction_symbol_x = TRUE,
-  caption = 'Effects of interest in the semantic priming model that included visual similarity.') %>%
+  caption = 'Effects of interest in the semantic priming model that included vision-based similarity.') %>%
   # kable_styling(latex_options = 'scale_down') %>%
@@
   pack_rows('Individual differences', 2, 3) %>% 
-  pack_rows('Prime-target semantic relationship', 4, 6) %>% 
+  pack_rows('Prime--target relationship', 4, 6) %>% 
   pack_rows('Task condition', 7, 7) %>% 
@@
   # Place table close to designated position
-  kable_styling(latex_options = c('HOLD_position')) %>%
+  kable_styling(latex_options = c('hold_position')) %>%
 
@@
   footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
-           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored variables; \\\\textit{SE} = standard error;',
+           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored predictors; \\\\textit{SE} = standard error;',
                            'CI = confidence interval. Covariates shown in next table due to space. Some ',
@@
                      # 'Vision-based similarity $^{\\text{b}}$',
-                     # 'Stimulus-onset asynchrony (SOA) $^{\\text{b}}$',
+                     # 'Stimulus onset asynchrony (SOA) $^{\\text{b}}$',
                      'Word-concreteness difference :: Vocabulary size',
@@
   interaction_symbol_x = TRUE,
-  caption = 'Covariates in the semantic priming model that included visual similarity.') %>%
+  caption = 'Covariates in the semantic priming model that included vision-based similarity.') %>%
   # kable_styling(latex_options = 'scale_down') %>%
@@
   # Group predictors under headings
-  pack_rows('Individual-differences covariate', 1, 1) %>% 
+  pack_rows('Individual difference covariate', 1, 1) %>% 
   pack_rows('Target-word lexical covariates', 2, 3) %>% 
-  pack_rows('Prime-target semantic covariate', 4, 4) %>% 
+  pack_rows('Prime--target covariate', 4, 4) %>% 
   pack_rows('Covariate interactions', 5, 10) %>%
@@
   footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
-           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored variables; \\\\textit{SE} = standard error;',
+           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored predictors; \\\\textit{SE} = standard error;',
                            'CI = confidence interval. Some interactions are split over two lines, with the',
@@
                            # '$^{\\\\text{b}}$ By-participant random slopes were included for this effect.', 
-                           # Begin lines after first one with a dot-sized indent
+                           # After first line in the footnote, begin next lines with a dot-sized indent to correct default error.
                            sep = ' \\\\linebreak \\\\phantom{.}'))
@@
 
-```{r semanticpriming-with-visualsimilarity-confidence-intervals-plot, fig.cap = 'Means and 95\\% confidence intervals for the effects of interest in the semantic priming model that included visual similarity.', out.width = '89%'}
+\FloatBarrier
+
+```{r semanticpriming-with-visualsimilarity-confidence-intervals-plot, fig.cap = 'Means and 95\\% confidence intervals for the effects of interest in the semantic priming model that included vision-based similarity.', out.width = '89%'}
 
@@
 
-The results revealed that visual-strength difference had a significantly larger effect.
-This difference was not due to an excessive collinearity between these measures ($r$ = `r cor(semanticpriming_with_visualsimilarity$z_visual_rating_diff, semanticpriming_with_visualsimilarity$z_visual_similarity) %>% sprintf('%.2f', .)`).
-Also importantly, both measures appeared to be valid based on their correlations with language-based similarity and with word concreteness.
+The results revealed an effect of the human-based measure, `visual-strength difference` (as in the main analysis above), along with a smaller effect of the computational measure, `vision-based similarity`.
+There was an important difference between these measures regarding the interaction with SOA.
+Whereas visual-strength difference had a larger effect with the short SOA, vision-based similarity did not interact with SOA, contrary to the results of @petilli2021a.
+This difference was not due to collinearity between these measures ($r$ = `r cor(semanticpriming_with_visualsimilarity$z_visual_rating_diff, semanticpriming_with_visualsimilarity$z_visual_similarity) %>% sprintf('%.2f', .) %>% sub('^(-)?0[.]', '\\1.', .)`).
+Also importantly, both measures appeared to be valid based on their correlations with language-based similarity and with word concreteness (Figure \@ref(fig:semanticpriming-with-visualsimilarity-correlations)).
+We reflect on this result in the discussion.
 
@@
 
-Power curves were performed for most effects of interest in the main model (no power analysis was performed for the model that included visual similarity).
-Figures \@ref(fig:semanticpriming-powercurve-plots-1-2-3) and \@ref(fig:semanticpriming-powercurve-plots-4-5-6-7-8-9) show the estimated power for the main effects and the interactions, respectively.
+Power curves were performed for most effects of interest in the main model.
+This was done using the main model, not the follow-up that included vision-based similarity.
+Figures \@ref(fig:semanticpriming-powercurve-plots-1-2-3) and \@ref(fig:semanticpriming-powercurve-plots-4-5-6-7-8-9) show the estimated power for some main effects and interactions of interest as a function of the number of participants.
+To plan the sample size for future studies, these results must be considered under the assumptions that the future study would apply a statistical method similar to ours---namely, a mixed-effects model with random intercepts and slopes---, and that the analysis would encompass at least as many prime--target pairs as the current study, namely, `r length(unique(semanticpriming$primeword_targetword)) %>% formattable::comma(digits = 0)` (distributed in various blocks across participants, not all being presented to every participant).
+Furthermore, it is necessary to consider each figure in detail.
+Here, we provide a summary.
+First, detecting the main effect of language-based similarity---which had a strong effect on RTs---would require 50 participants.
+Second, detecting the interaction between language-based similarity and SOA---which was a considerably weaker effect---would require 600 participants.
+Last, the other effects would require more than 1,000 participants---or, in the case of gender differences, many more than that.
 
@@
 
-_______ interpret ____________
-
-## Discussion
-
-___________________
+## Discussion of Study 1
+
+The results revealed a significant, facilitatory effect of `language-based similarity` and a smaller but significant, inhibitory effect of `visual-strength difference`.
+That is, a greater language-based similarity resulted in shorter RTs, whereas a greater visual-strength difference resulted in larger RTs.
+There was also a sizable effect of stimulus onset asynchrony (SOA), with shorter RTs in the short SOA condition (200 ms) than in the long SOA (1,200 ms).
+Furthermore, there were significant interactions.
+First, language-based priming was larger in higher-vocabulary participants than in lower-vocabulary ones.
+Second, both language-based priming and vision-based priming were larger with the short SOA than with the long one.
+Thus far, these results broadly replicated those of @petilli2021a.
+It is especially noteworthy that vision-based information had a significant effect, consistent with some of the previous research [@floresdarcaisSemanticActivationRecognition1985; @schreuderEffectsPerceptualConceptual1984; @connellSeeHearWhat2014; @petilli2021a], and contrasting with other research that did not find such an effect [@ostarekTaskdependentCausalRole2017] or only observed it after visually-focussed tasks [@pecherDoesPizzaPrime1998; @yeeColorlessGreenIdeas2012].
+Last, no effect of gender was found.
+Below, we delve into some other aspects of these results.
+
+### The importance of outliers
+
+The interaction between language-based similarity and vocabulary size (Figure \@ref(fig:semanticpriming-interactions-with-vocabulary-size)-a) was patent in all deciles of vocabulary size but it was clearest among those participants that were more than one standard deviation away from the mean.
+Outliers in individual differences have played important roles in other areas of cognition as well, such as in the study of aphantasia and hyperphantasia---traits characterised, respectively, by a diminished and an extraordinary ability to mentally visualise objects [@milton2021a; @zeman2020a].
+Such an influence of outliers provides a reason to study more varied samples of participants when possible.
+Furthermore, a greater interindividual variation might help detect the effects of individual differences that have been elusive [e.g., @hedge2018a; @murakiSimulatingSemanticsAre2021; @ponari2018a; @rodriguez-ferreiroSemanticPrimingSchizotypal2020; @rouderPsychometricsIndividualDifferences2019].
+
+### Human-based and computational measures of vision-based information
+
+Next, in a secondary analysis, we compared the roles of two measures of vision-based priming.
+The first measure---`visual-strength difference`---was operationalised as the difference in visual strength between the prime word and the target word in each trial.
+This difference score was thus based on modality-specific ratings provided by human participants [@lynott2020a].
+The second measure---`vision-based similarity`---, created by @petilli2021a, was based on vector representations trained on labelled images from ImageNet.
+This variable is therefore computational.
+The effect of visual-strength difference was slightly larger than that of vision-based similarity.
+This result is consistent with some previous findings suggesting that human-based measures explained more variance than computational measures [@de2016a; @de2019a; @gagneProcessingEnglishCompounds2016; @schmidtke2018a; cf.
+@michaelovClozeFarN4002022; @snefjella2020a].
+If the different degree of human dependence of our two variables were indeed behind the effect size of each, we would need to consider a related issue.
+The problem of circularity was addressed by Petilli et al., who argued that using human-based predictors---such as ratings---to investigate human behaviour was less valid than using predictors that were more independent of human behaviour---such as computational measures.
+On the one hand, we identify two reasons for skepticism regarding the circularity hypothesis.
+First, the underlying basis of all computational measures [e.g., @mandera2017a; @petilli2021a] is indeed human behaviour, notwithstanding the degree to which this human basis is filtered by computational methods.
+Second, we have not found sufficient research addressing the validity question.
+Yet, on the other hand, the circularity hypothesis is important enough to warrant dedicated research.
+Specifically, future studies could be conducted to systematically compare the theoretical insights provided by human-based measures and by computational ones, as well as the effect size achieved by both types.
+
+It is noteworthy that both visual-strength difference and vision-based similarity have *independently* proven to be relevant, and arguably valid, considering their correlations with other measures---especially `word-concreteness difference` and `language-based similarity`---and considering the effects of each measure in semantic priming [see @petilli2021a].
+However, the differences between these measures are worthy of attention.
+Visual-strength difference was barely correlated with language-based similarity.
+Conversely, vision-based similarity was barely correlated with word-concreteness difference (refer to Figure \@ref(fig:semanticpriming-with-visualsimilarity-correlations)).
+These results call for an investigation into the underlying composition of visual-strength difference and vision-based similarity.
+
+Furthermore, whereas visual-strength difference retained its significant interaction with SOA---also observed in the main analysis presented above---, in contrast, vision-based similarity did not present such an interaction.
+The lack of an interaction between vision-based similarity and SOA contrasts with the results of  @petilli2021a, who found that vision-based similarity was only significant in the short SOA condition.
+There are several possible reasons for this difference, including: (I) a more conservative method in our current analysis---i.e., a maximal mixed-effects model containing more predictors than the hierarchical regression performed by Petilli et al.---, and (II) the presence of individual differences in the present study (i.e., vocabulary size, attentional control and gender), versus the aggregation performed by Petilli et al.
+
+Last, the interaction between language-based similarity and SOA became non-significant in this sub-analysis.
+This difference from the original analysis may have been caused by the sizable correlation between language-based similarity and vision-based similarity ($r$ = `r cor(semanticpriming_with_visualsimilarity$z_cosine_similarity, semanticpriming_with_visualsimilarity$z_visual_similarity) %>% sprintf('%.2f', .) %>% sub('^(-)?0[.]', '\\1.', .)`).
+In this regard, we should notice the large influence of the addition of a single variable (along with its interactions) into the model.
+
+### The influence of the analytical method
+
+Taken together, the sub-analysis that included vision-based similarity offered a glimpse into the crucial role of analytical choices in the present topic.
+A previous example of this influence appeared in a set of studies that used Latent Semantic Analysis (LSA) as a predictor of semantic priming.
+@hutchisonPredictingSemanticPriming2008 operationalised LSA as a difference score, and did not find an effect of this variable.
+In contrast, later studies did not use a difference score and they observed a significant effect [@guntherLatentSemanticAnalysis2016; @mandera2017a].
+We can extrapolate this issue to a very important comparison we often make---namely, that between language-based and embodied simulation.
+The pervasive superiority of language over the other systems (perception, action, emotion and sociality)---found in the three current studies and in previous ones [@banksLinguisticDistributionalKnowledge2021; @kiela2014a; @louwerse2015a; @lam2015a; @pecherDoesPizzaPrime1998; @petilli2021a]---would be less trustworthy if the instruments that were used to measure the language system had been far more precise than the instruments used to measure the embodiment system.
+In this sense, it is relevant to consider how variables are improved in research: it is done iteratively, by comparing the performance of different variables.
+Critically, the literature contains many comparisons of text-based variables, some dating back to the 1990s [@jones2006a; @lund1996a; @mandera2017a; @mikolovEfficientEstimationWord2013; @dedeyneBetterExplanationsLexical2013; @de2016a; @guenther2016a; @guntherLatentSemanticAnalysis2016; @wingfieldUnderstandingRoleLinguistic2022].
+In contrast, the work on embodiment variables began more than a decade afterwards, and it has been less concerned with benchmarking the explanatory power of variables [but see @vergallitoPerceptualModalityNorms2020].
+Instead, this literature contains more comparisons of different *modalities*---e.g., visual strength, auditory strength, valence, etc.
+[@lynott2020a; @lynottModalityExclusivityNorms2009; @newcombeEffectsEmotionalSensorimotor2012].
+Thus, if linguistic measures are more precise than embodiment measures due to greater work on the variables, such a difference could account for a certain portion of the superiority of linguistic information over embodied information [see @banksLinguisticDistributionalKnowledge2021; @kiela2014a; @louwerse2015a; @lam2015a; @pecherDoesPizzaPrime1998; @petilli2021a].
+Analytical choices such as the operationalisation of variables and the complexity of statistical models can greatly influence the conclusions of research.
+Indeed, our current results and previous ones suggest that the conclusions of research are inextricable from the method used in each study [see @barsalouEstablishingGeneralizableMechanisms2019; @botvinik-nezerVariabilityAnalysisSingle2020; @perretWhichVariablesShould2019; @wagenmakersOneStatisticalAnalysis2022].
+Therefore, in the medium term, it may pay dividends to continue examining the influence of analytical choices.
+Unfortunately, in many research fields, reflecting on the sensitivity of our analyses might conflict with the incentives of the system, which may penalise nuanced conclusions in favour of simplified stories.
+To overcome such a bias, it may be necessary to devote greater importance to the methodology in scientific papers---for instance, by commenting on the method in the abstract and by extending the methods section in the body of the paper.
+In stark contrast, our current results should make us question some decisions by scientific publishers such as rendering the methods section in a smaller font than the results section, or placing the method section at the end of the paper.
+In a nutshell, it may be useful to ensure that scientists are aware that research findings are fundamentally dependent on research methods.
+
+### Statistical power analysis
+
+We analysed the statistical power associated with several effects of interest, across various sample sizes.
+The results of this power analysis can help determine the number of participants required to reliably examine each of these effects in a future study.
+Importantly, the results assume two conditions.
+First, the future study would apply a statistical method similar to ours---namely, a mixed-effects model with random intercepts and slopes.
+Second, the analysis of the future study would encompass at least `r length(unique(semanticpriming$primeword_targetword)) %>% formattable::comma(digits = 0)` prime--target pairs (distributed in various blocks across participants, not all being presented to every participant).
+
+First, the results revealed that detecting the main effect of language-based similarity would require 50 participants.
+Next, detecting the interaction between language-based similarity and SOA would require 600 participants.
+Last, the other effects would require more than 1,000 participants---or, in the case of gender differences, many more than that.
 
@@
 
-The semantic decision task probes into the role of concreteness in conceptual processing.
-Specifically, this task requires participants to classify words as abstract or concrete.
+The semantic decision task probes the role of concreteness in conceptual processing.
+Specifically, this task requires participants to classify words as abstract or concrete, which elicits deeper semantic processing than the task of identifying word forms (i.e., lexical decision).
 Researchers then analyse whether the responses can be explained by the sensory experientiality of the referents---that is, the degree to which they can be experienced through our senses---and by other variables, such as word frequency.
 The core data set in this study was that of the Calgary Semantic Decision Project [@pexman2017a; @pexman2018a].
-The experimental task is semantic decision, in which participants judge whether words are relatively concrete (e.g., 'building') or abstract (e.g., 'thought').
+The experimental task is semantic decision, in which participants judge whether words are primarily abstract (e.g., *thought*) or concrete (e.g., *building*).
 
 Research has found that the processing of relatively concrete words relies considerably on sensorimotor information [@hultenNeuralRepresentationAbstract2021; @kousta2011a; @vigliocco2014a].
-In contrast, the processing of relatively abstract words seems to draw more heavily on information from language [@barca2020a; @dunabeitiaQualitativeDifferencesRepresentation2009; @snefjella2020a], emotion [@kousta2011a; @ponari2018a; @ponari2018b; @ponariRoleEmotionalValence2020; @vigliocco2014a] and sociality [@borghiWordsSocialTools2019; @diveicaQuantifyingSocialSemantics2022].
-
-## Word co-occurrence
-
-@wingfieldUnderstandingRoleLinguistic2022 reanalysed the data from @pexman2017a using language-based variables that are more related to the language system than to the visual system.
-The task used by Pexman et al.
-had been semantic decision, in which participants assessed whether words were abstract or concrete.
-Wingfield and Connell found that the variables that best explained RTs were word co-occurrence measures.
-Specifically, one of these variables was the correlation distance between each stimulus word and the word 'abstract'.
-The other variable was the correlation distance between each stimulus word and the word 'concrete'.
-Wingfield and Connell studied these distance measures in various forms, and found that cosine and correlation distance yielded the best results.
-We used the correlation distance, following the advice of @kiela2014a (see details below).
+In contrast, the processing of relatively abstract words seems to draw more heavily on information from language [@barca2020a; @dunabeitiaQualitativeDifferencesRepresentation2009; @snefjella2020a], emotion [@kousta2011a; @ponari2018a; @ponari2018b; @ponariRoleEmotionalValence2020; @vigliocco2014a], interoception [@connellInteroceptionForgottenModality2018] and social information [@borghiWordsSocialTools2019; @borghiAbstractConceptsExternal2022; @diveicaQuantifyingSocialSemantics2022].
 
@@
 
-### Effects of interest
-
-#### Vocabulary size
-
-[`z_vocabulary_size`; calculated from `NAART` in @pexman2017a].
-In the test used by @pexman2018a, participants were presented with 35 rare words, whose pronunciations are not regular (e.g., *gaoled*, *ennui*), and they were asked to read the words aloud.
-When they pronounced a word correctly, it was inferred that they knew the word.
-This test was based on NAART35, a short version of the North American Adult Reading Test [@uttlNorthAmericanAdult2002].
-
-#### Participant's gender
-
-[`z_recoded_participant_gender`; calculated from `Gender` in @pexman2018a]
-
-#### Word co-occurrence
-
-The zero-order correlation between Wingfield and Connell's (2022) distance to 'abstract' and distance to 'concrete' was $r$ = `r cor(semanticdecision$Conditional_probability_BNC_r5_correlation_abstract_distance, semanticdecision$Conditional_probability_BNC_r5_correlation_concrete_distance) %>% sprintf('%.2f', .)`.
-To avoid the collinearity between these variables in the model [@dormannCollinearityReviewMethods2013; @harrison2018a], and to facilitate the analysis of interactions with other variables, we created a difference score by subtracting the distance to 'abstract' from the distance to 'concrete'.
-This new variable was named 'word co-occurrence'.
-As Figure \@ref(fig:semanticdecision-cooccurrence-correlations) demonstrates, the difference score captured the explanatory power of the two original variables, resulting in an increase of the correlation with word concreteness.
-
-```{r semanticdecision-cooccurrence-correlations, fig.cap = "Zero-order correlations among Wingfield and Connell's (2022) distances, the difference score (word co-occurrence) and word concreteness (Brysbaert et al., 2014).", fig.width = 7, fig.height = 2.2, out.width = '58%'}
-
-# Using the following variables...
-semanticdecision[, c('word_concreteness', 'word_cooccurrence',
-                     'Conditional_probability_BNC_r5_correlation_concrete_distance',
-                     'Conditional_probability_BNC_r5_correlation_abstract_distance')] %>%
-
-  # renamed for the sake of clarity
-  rename('Word concreteness' = word_concreteness, 
-         'Word co-occurrence' = word_cooccurrence,
-         "Distance to 'concrete'" = Conditional_probability_BNC_r5_correlation_concrete_distance,
-         "Distance to 'abstract'" = Conditional_probability_BNC_r5_correlation_abstract_distance) %>%
-
-  # make correlation matrix (custom function from the 'R_functions' folder)
-  correlation_matrix() + 
-  theme(plot.margin = unit(c(0, -0.5, 0.05, -3.78), 'in'))
-
-```
-
-#### Visual strength
-
-[`z_visual_rating`; calculated from `Visual.mean` in @lynott2020a]
+### Data set
 
@@
 
-# Calculate numbers to be reported in the paragraph below
-
-# Save number of participants and words
-semanticdecision_number_participants = 
-  length(unique(semanticdecision$Participant))
-
-semanticdecision_number_words = length(unique(semanticdecision$Word))
+# Calculate some of the sample sizes to be reported in the paragraph below
 
@@
 
-The final data set contained `r semanticdecision_number_participants` participants, `r semanticdecision_number_words %>% formattable::comma(digits = 0)` words, and `r length(semanticdecision$z_RTclean) %>% formattable::comma(digits = 0)` RTs.
+The data set was trimmed by removing rows that lacked values on any variable, and by also removing RTs that were more than 3 standard deviations away from the mean.^[In the removal of missing values, six participants whose gender appeared as 'NA' were inadvertently removed from the data set.] The standard deviation trimming was performed within participants and within trial blocks, as done in the Calgary Semantic Decision Project [@pexman2017a].
+The resulting data set contained `r length(unique(semanticdecision$Participant))` participants, `r length(unique(semanticdecision$Word)) %>% formattable::comma(digits = 0)` words and `r length(semanticdecision$z_RTclean) %>% formattable::comma(digits = 0)` RTs.
 On average, there were `r semanticdecision_mean_words_per_participant` words per participant ($SD$ = `r semanticdecision_SD_words_per_participant`), and conversely, `r semanticdecision_mean_participants_per_word` participants per word ($SD$ = `r semanticdecision_SD_participants_per_word`).
 
-Figure \@ref(fig:semanticdecision-correlations) shows the zero-order correlations among the predictors among the predictors and the dependent variable.
-
-```{r semanticdecision-correlations, fig.cap = 'Zero-order correlations in the semantic decision study.', fig.width = 7, fig.height = 4.5, out.width = '57%'}
+### Variables
+
+While the variables are generally described in the [\underline{general introduction}](#present-studies), a few further details are provided below regarding some of them.
+
+#### Vocabulary size
+
+In the vocabulary test used by @pexman2017a, participants were presented with 35 rare words with irregular pronunciations (e.g., *gaoled*, *ennui*), and they were asked to read the words aloud [also see @pexman2018a].
+When they pronounced a word correctly, it was inferred that they knew the word.
+This test was based on NAART35, a short version of the North American Adult Reading Test [@uttlNorthAmericanAdult2002].
+
+#### Word co-occurrence
+
+@wingfieldUnderstandingRoleLinguistic2022 reanalysed the data from @pexman2017a using language-based variables that are more related to the language system than to the visual system.
+The task used by Pexman et al.
+was semantic decision, in which participants assessed whether words were abstract or concrete.
+Wingfield and Connell found that the variables that best explained RTs were word co-occurrence measures.
+Specifically, one of these variables was the corpus distance between each stimulus word and the word 'abstract'.
+The other variable was the corpus distance between each stimulus word and the word 'concrete'.
+Wingfield and Connell studied these distance measures in various forms, and found that cosine and correlation distance yielded the best results.
+We used the correlation distances following the advice of @kiela2014a.
+
+The zero-order correlation between Wingfield and Connell's (2022) distance to 'abstract' and distance to 'concrete' was $r$ = `r cor(semanticdecision$Conditional_probability_BNC_r5_correlation_abstract_distance, semanticdecision$Conditional_probability_BNC_r5_correlation_concrete_distance) %>% sprintf('%.2f', .) %>% sub('^(-)?0[.]', '\\1.', .)`.
+To avoid the collinearity between these variables in the model [@dormannCollinearityReviewMethods2013; @harrison2018a], and to facilitate the analysis of interactions with other variables, we created a difference score by subtracting the distance to 'abstract' from the distance to 'concrete'.
+This new variable was named 'word co-occurrence'.
+As shown in Figure \@ref(fig:semanticdecision-cooccurrence-correlations), the correlation between word co-occurrence and word concreteness was twice as large as the correlation between either form of the distance and word concreteness.
+This suggested that the difference score had successfully encapsulated the information of both distances.
+
+```{r semanticdecision-cooccurrence-correlations, fig.cap = "Zero-order correlations among Wingfield and Connell's (2022) distances, the difference score (word co-occurrence) and word concreteness (Brysbaert et al., 2014).", fig.width = 7, fig.height = 2.2, out.width = '63%'}
+
+# Using the following variables...
+semanticdecision[, c('word_concreteness', 'word_cooccurrence',
+                     'Conditional_probability_BNC_r5_correlation_concrete_distance',
+                     'Conditional_probability_BNC_r5_correlation_abstract_distance')] %>%
+
+  # renamed for the sake of clarity
+  rename('Word concreteness' = word_concreteness, 
+         'Word co-occurrence' = word_cooccurrence,
+         "Distance to 'concrete'" = Conditional_probability_BNC_r5_correlation_concrete_distance,
+         "Distance to 'abstract'" = Conditional_probability_BNC_r5_correlation_abstract_distance) %>%
+
+  # make correlation matrix (custom function from the 'R_functions' folder)
+  correlation_matrix() + 
+  theme(plot.margin = unit(c(0, -0.5, 0.05, -3.78), 'in'))
+
+```
+
+A few details regarding the covariates follow.
+
+- `Information uptake` was included as a measure akin to general cognition, and specifically as a covariate of vocabulary size [@ratcliff2010a; also see @james2018a; @pexman2018a].
+Information uptake was effectively the drift rate per participant in @pexman2018a.
+This drift rate measured participants' ability to correctly and quickly perform the semantic decision task, in which they classified words as abstract or concrete [for graphical illustrations, see @lercheDiffusionModelingIntelligence2020; @vanravenzwaaijOptimalDecisionMaking2012].
+In other words, drift rate measures an individual's ability  [@lercheDiffusionModelingIntelligence2020; @pexman2018a].
+
+- Lexical covariates (see [\underline{Appendix A}](#appendix-A-lexical-covariates)): `word frequency` and `orthographic Levenshtein distance` [@balota2007a].
+
+- `Word concreteness` [@brysbaert2014a]: a fundamental variable in the semantic decision task, in which participants judge whether words are abstract or concrete [for further considerations, see @bottiniConcretenessAdvantageLexical2021].
+Indeed, owing to the instructions of the task, word concreteness is likely to be more relevant to the participants' task than our effects of interest.
+
+Figure \@ref(fig:semanticdecision-correlations) shows the correlations among the predictors and the dependent variable.
+
+```{r semanticdecision-correlations, fig.cap = 'Zero-order correlations in the semantic decision study.', fig.width = 7, fig.height = 4.5, out.width = '61%'}
 
@@
 
-### Covariates
-
-The following covariates were included in the model to allow a rigorous analysis of the effects of interest.
-
-- Lexical (see [\underline{Appendix A}](#appendix-A-lexical-covariates)): $z$-scored word frequency and orthographic Levenshtein distance [@balota2007a]
-
-- Semantic: $z$-scored word concreteness [@brysbaert2014a].
-This variable is used as a covariate of visual strength, and it is especially fundamental in the semantic decision task, in which participants judge whether words are concrete or abstract [for a more general consideration of concreteness, see @bottiniConcretenessAdvantageLexical2021].
-Indeed, owing to the instructions of the task, word concreteness is likely to be more relevant to the participants' task than our effects of interest.
-
-- Individual differences: $z$-scored information uptake [@pexman2018a]. This covariate is related to vocabulary size [@ratcliff2010a; also see @james2018a; @pexman2018a].
-
-### Diagnostics for the frequentist model
+### Diagnostics for the frequentist analysis
 
 The model presented convergence warnings.
-To avoid removing important random slopes, which could increase the Type I error [@brauer2018a; @singmann2019a], we examined the model after refitting it using seven optimization algorithms through the 'allFit' function of the 'lme4' package [@batesPackageLme42021].
-The results showed that all optimizers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential (Bates et al., 2021; see [\underline{Appendix B}](#appendix-B-frequentist-analysis-diagnostics)).
+To avoid removing important random slopes, which could increase the Type I error rate---i.e., false positives [@brauer2018a; @singmann2019a], we examined the model after refitting it using seven optimisation algorithms through the 'allFit' function of the 'lme4' package [@batesPackageLme42021].
+The results showed that all optimisers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential (Bates et al., 2021; see [\underline{Appendix B}](#appendix-B-frequentist-analysis-diagnostics)).
+
+```{r}
+
+# Calculate VIF for every predictor and return only the maximum VIF rounded up
+maxVIF_semanticdecision = car::vif(semanticdecision_lmerTest) %>% max %>% ceiling
+
+```
 
@@
 However, this is not likely to have posed a major problem, as mixed-effects models are fairly robust to deviations from normality [@kniefViolatingNormalityAssumption2021; @schielzethRobustnessLinearMixed2020].
+Last, the model did not present multicollinearity problems, with all VIFs below `r maxVIF_semanticdecision` [see @dormannCollinearityReviewMethods2013; @harrison2018a].
+
+### Diagnostics for the Bayesian analysis
 
@@
 
-# Calculate VIF for every predictor and return only the maximum VIF rounded up
-maxVIF_semanticdecision = car::vif(semanticdecision_lmerTest) %>% max %>% ceiling
-
-```
-
-The model did not present multicollinearity problems, all VIFs being smaller than `r maxVIF_semanticdecision` [@dormannCollinearityReviewMethods2013; @harrison2018a].
-
-### Diagnostics for the Bayesian model
-
-```{r}
-
 # Calculate number of post-warmup draws (as in 'brms' version 2.17.0).
-# Informative prior model used but same numbers in all three models.
+# Informative prior model used but numbers are identical in the three models.
 semanticdecision_post_warmup_draws = 
@@
 
-# Next, find find maximum R-hat value for the random effects 
-# across the three models. 
+# Next, find find maximum R-hat value for the random effects across the three models
 semanticdecision_randomeffects_max_Rhat = 
@@
 Similarly, the maximum $\widehat R$ value for the random effects was `r semanticdecision_randomeffects_max_Rhat`.
-Furthermore, the posterior predictive checks revealed major divergences between the observed data and the predicted outcome (see [\underline{Appendix C}](#appendix-C-Bayesian-analysis-diagnostics)).
-Since the results were not valid, they are not shown in the main text but in [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results).
-
-## Results
+Furthermore, the posterior predictive checks revealed major divergences between the observed data and the posterior distributions (see [\underline{Appendix C}](#appendix-C-Bayesian-analysis-diagnostics)).
+In conclusion, since the Bayesian results were not valid, they are not shown in the main text, but are available in [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results).
+
+## Results of Study 2
 
@@
 
-Table \@ref(tab:semanticdecision-frequentist-model) presents the results of the frequentist model.
-The fixed effects explained `r Nakagawa2017_fixedeffects_R2_semanticdecision_lmerTest` of the variance, and the random effects `r Nakagawa2017_randomeffects_R2_semanticdecision_lmerTest` [@nakagawaCoefficientDeterminationR22017; for an explanation of this difference, see [\underline{Results of Study 1}](#semanticpriming-results)).
-Figure \@ref(fig:semanticdecision-confidence-intervals-plot) displays these estimates.^[Bayesian estimates not shown as they were not valid.
-They are nonetheless available in [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results).]
+Table \@ref(tab:semanticdecision-frequentist-model) presents the results.
+The fixed effects explained `r Nakagawa2017_fixedeffects_R2_semanticdecision_lmerTest` of the variance, and the random effects explained `r Nakagawa2017_randomeffects_R2_semanticdecision_lmerTest` (Nakagawa et al., 2017; for an explanation of this difference, see [\underline{Results of Study 1}](#semanticpriming-results)).
+Both word co-occurrence and visual strength produced significant main effects.
+Higher values of these variables facilitated participants' performance, as reflected in shorter RTs.
+Furthermore, visual strength interacted with vocabulary size.
+There were no effects of participants' gender (see interaction figures below).
+
+The effect sizes of word co-occurrence and its interactions were larger than those of visual strength.
+Figure \@ref(fig:semanticdecision-confidence-intervals-plot) displays these estimates.^[Only frequentist estimates shown, as Bayesian ones were not valid (see [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results)).]
 
@@
   footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
-           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored variables; \\\\textit{SE} = standard error;',
-                           'CI = confidence interval. Shaded rows contain covariates. Some interactions are',
-                           'split over two lines, with the second line indented. \\\\linebreak', 
+           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored predictors; \\\\textit{SE} = standard error;',
+                           'CI = confidence interval. Shaded rows contain covariates. \\\\linebreak', 
                            '$^{\\\\text{a}}$ By-word random slopes were included for this effect.',
                            '$^{\\\\text{b}}$ By-participant random slopes were included for this effect.', 
-                           # Begin lines after first one with a dot-sized indent
+                           # After first line in the footnote, begin next lines with a dot-sized indent to correct default error.
                            sep = ' \\\\linebreak \\\\phantom{.}'))
@@
 ```
+
+\FloatBarrier
 
@@
 
-Figures \@ref(fig:semanticdecision-interactions-with-vocabulary-size)-a and \@ref(fig:semanticdecision-interactions-with-vocabulary-size)-b demonstrate how lower-vocabulary participants (compared to higher-vocabulary participants) were more strongly influenced by both language- and vision-based similarity.
-In contrast, Figure \@ref(fig:semanticdecision-interactions-with-vocabulary-size)-c shows that higher-vocabulary participants benefitted more strongly from word concreteness.
-Since the variable that is most relevant to the semantic decision task is word concreteness, the present interactions suggest that higher-vocabulary participants were better able to focus on the most relevant information, whereas lower-vocabulary participants were sensitive to a greater breadth of information [@lim2020a; @pexman2018a; @yap2012a; @yap2017a; @yapIndividualDifferencesJoint2009].
-
-(ref:semanticdecision-interactions-with-vocabulary-size) Interactions of vocabulary size with (a) language-based information, (b) visual strength and (c) word concreteness.
+Figure \@ref(fig:semanticdecision-interactions-with-vocabulary-size)-a shows the non-significant interaction between word co-occurrence and vocabulary size, whereby lower-vocabulary participants were more sensitive to word co-occurrence than higher-vocabulary participants.
+Next, Figure \@ref(fig:semanticdecision-interactions-with-vocabulary-size)-b shows the significant interaction between visual strength and vocabulary size, demonstrating that lower-vocabulary participants were also more sensitive to visual strength.
+Last, Figure \@ref(fig:semanticdecision-interactions-with-vocabulary-size)-c shows the significant interaction between word concreteness and vocabulary size, whereby higher-vocabulary participants were more sensitive to word concreteness than lower-vocabulary participants.
+Word concreteness is likely the most relevant variable for the semantic decision task, in which participants classify words as abstract or concrete.
+In conclusion, these interactions suggest that higher-vocabulary participants were better able to focus on the most relevant information, whereas lower-vocabulary participants were
+sensitive to a greater breadth of information [see @lim2020a; @pexman2018a; @yap2012a; @yap2017a; @yapIndividualDifferencesJoint2009].
+
+(ref:semanticdecision-interactions-with-vocabulary-size) Interactions of vocabulary size with language-based information (panel a), with visual strength (panel b) and with word concreteness (panel c) in the semantic decision study.
 Vocabulary size is constrained to deciles in this plot, whereas in the statistical analysis it contained more values within the current range.
-*n* = number of participants contained between deciles.
-
-```{r semanticdecision-interactions-with-vocabulary-size, fig.cap = '(ref:semanticdecision-interactions-with-vocabulary-size)', out.width = '90%'}
+$n$ = number of participants contained between deciles.
+
+```{r semanticdecision-interactions-with-vocabulary-size, fig.cap = '(ref:semanticdecision-interactions-with-vocabulary-size)', out.width = '98%'}
 
@@
 
-The present analysis used a continuous measure of word concreteness.
-In contrast, @pexman2018a analysed the same data set after dividing the stimulus words into abstract and concrete subsets, which they analysed separately.
+A continuous measure of word concreteness was used in the present study.
+In contrast, @pexman2018a split the data set it into a subset with abstract words and another subset with concrete words, and they analysed these subsets separately.
 Pexman and Yap found that high-vocabulary participants were more sensitive to the relative abstractness of words.
-Specifically, these participants were faster to classify very abstract words than mid-abstract ones, thus presenting a reverse concreteness effect.
-Such a reverse effect might stem from the bimodal distributions of concreteness ratings [@brysbaert2014a] and semantic decisions [@pexman2018a].
-The reverse effect has also been found in semantic dementia patients [@connellStrengthPerceptualExperience2012].
-Since the reverse effect contrasted with the long-established concreteness effect, the former has sometimes been regarded as an inconsistency.
-
-Notwithstanding the aforementioned bimodal distributions, @trocheDefiningConceptualTopography2017 suggested that a continuous analysis remains necessary to study word concreteness [also see @cohenCostDichotomization1983].
+Specifically, these participants were faster to classify very abstract words than mid-abstract ones, thus presenting a reverse concreteness effect [also see @bonnerReversalConcretenessEffect2009].
+Such a reverse effect might stem from the bimodal distributions that have appeared in concreteness ratings [@brysbaert2014a] and in semantic decisions [@pexman2018a], or it might be due to confounding variables [@hoffmanReverseConcretenessEffects2011].
+Notwithstanding the bimodal distributions, @trocheDefiningConceptualTopography2017 suggested that a continuous analysis remained necessary to study word concreteness [also see @cohenCostDichotomization1983].
 Consistent with this, our present findings demonstrated the sensitivity of a continuous word concreteness variable to patterns such as the greater role of task-relevant variables in high-vocabulary participants.
 In conclusion, the literature and our findings suggest that the split-data approach and the continuous approach to word concreteness are both useful.
-Where feasible, the application of both approaches would provide the most information.
-
-Figure \@ref(fig:semanticdecision-interactions-with-gender) shows the interactions of gender with language-based similarity and visual-strength difference, albeit non-significant.^[Plots of other interactions are available in [\underline{Appendix D}](#appendix-D-interaction-plots).]
-
-```{r semanticdecision-interactions-with-gender, fig.cap = 'Interactions with gender in the semantic decision study.
-Gender was analysed using $z$-scores, but for clarity, the variable is shown in its basic form here.', out.width = '90%'}
+Where it is feasible, the application of both approaches would provide the greatest information.
+
+Figure \@ref(fig:semanticdecision-interactions-with-gender) shows the interactions with gender.
+The interactions of interest, in panels a and b, were non-significant.^[Further interaction plots available in [\underline{Appendix D}](#appendix-D-interaction-plots).]
+
+```{r semanticdecision-interactions-with-gender, fig.cap = 'Interactions of gender with word co-occurrence (panel a), with visual strength (panel b) and with word concreteness (panel c) in the semantic decision study.
+Gender was analysed using $z$-scores, but for clarity, the basic labels are used in the legend.', out.width = '98%'}
 
@@
 
-Figures \@ref(fig:semanticdecision-powercurve-plots-1-2-3) and \@ref(fig:semanticdecision-powercurve-plots-4-5-6-7) show the estimated power available for main effects and interactions of interest, respectively.
+Figures \@ref(fig:semanticdecision-powercurve-plots-1-2-3) and \@ref(fig:semanticdecision-powercurve-plots-4-5-6-7) show the estimated power for some main effects and interactions of interest as a function of the number of participants.
+To plan the sample size for future studies, these results must be considered under the assumptions that the future study would apply a statistical method similar to ours---namely, a mixed-effects model with random intercepts and slopes---, and that the analysis would encompass at least as many words as the current study, namely, `r length(unique(semanticdecision$Word)) %>% formattable::comma(digits = 0)` (distributed in various blocks across participants, not all being presented to every participant).
+Furthermore, it is necessary to consider each figure in detail.
+Here, we provide a summary.
+First, detecting the main effect of word co-occurrence would require 300 participants.
+Second, detecting the main effect of visual strength would require 1,200 participants.
+Third, detecting the interactions of word co-occurrence and visual strength with vocabulary size would require 1,500 participants.
+Last, detecting the other effects would require more than 2,000 participants---or, in the case of gender differences, many more than that.
 
@@
 
-_______ interpret ____________
-
-## Discussion
-
-___________________
+## Discussion of Study 2
+
+The results revealed a significant, facilitatory effect of `word co-occurrence` and a smaller but significant, facilitatory effect of `visual strength`.
+That is, higher values of these variables resulted in shorter RTs.
+Furthermore, there were significant interactions.
+First, language-based priming was larger in higher-vocabulary participants than in lower-vocabulary ones.
+Second, both language-based priming and vision-based priming were larger with the short SOA than with the long one.
+Thus far, these results broadly replicated those of @petilli2021a.
+As in Study 1, vision-based information had a significant effect.
+This was to be expected, as semantic decision is likely to engage deeper semantic processing.
+Last, no effect of gender was found.
+Below, we delve into some other aspects of these results.
+
+### Statistical power analysis
+
+We analysed the statistical power associated with several effects of interest, across various sample sizes.
+The results of this power analysis can help determine the number of participants required to reliably examine each of these effects in a future study.
+Importantly, the results assume two conditions.
+First, the future study would apply a statistical method similar to ours---namely, a mixed-effects model with random intercepts and slopes.
+Second, the analysis of the future study would encompass at least `r length(unique(semanticdecision$Word)) %>% formattable::comma(digits = 0)` stimulus words (distributed in various blocks across participants, not all being presented to every participant).
+
+First, the results revealed that detecting the main effect of word co-occurrence would require 300 participants.
+Next, detecting the interactions with vocabulary size would require 1,500 participants.
+Last, detecting the other effects would require more than 2,000 participants---or, in the case of gender differences, many more than that.
 
@@
 
-# Study 3: Lexical decision
-
-The core data set in this study was the lexical decision subset of the English Lexicon Project---ELP [@balota2007a].
+# Study 3: Lexical decision {#lexicaldecision}
+
+The core data set in this study was the lexical decision subset of the English Lexicon Project (ELP; Balota et al., 2007).
+As in Study 1, we limited our analysis to the lexical decision task because it was more relevant to a subsequent study that we were planning.
 The lexical decision task differs from semantic priming and semantic decision in two important aspects.
-
-1. **Less semantic processing.** The lexical decision paradigm is likely to involve less semantic processing than the other paradigms. ____________
-
-2.
-**Single-word measures.** Compared to semantic priming and semantic decision, it is more difficult in the lexical decision paradigm to create word-to-word distance measures to capture language-based and vision-based information.
-The possibility of calculating the distance between words in consecutive trials is hindered by the need to skip trials, owing to the high prevalence of nonword trials in the lexical decision paradigm.
+First, lexical decision is likely to involve less semantic processing than the other paradigms [@balotaDepthAutomaticSpreading1986; @beckerLongtermSemanticPriming1997; @dewitMaskedSemanticPriming2015; @joordensLongShortSemantic1997; @murakiSimulatingSemanticsAre2021; @ostarekTaskdependentCausalRole2017].
+
+Second, it is more difficult in the lexical decision task to create word-to-word distance measures to capture language-based and vision-based information.
+The possibility of calculating the distance between words in consecutive trials is hindered by the need to skip trials, owing to the high prevalence of nonword trials throughout the lexical decision task.
 Therefore, the measures must be based on each word alone.
 Accordingly, vision-based information can be operationalised as the visual strength of each word.
-Language-based information could be operationalised as any of several lexical variables.
-In the present study, word frequency was chosen as it had the most explanatory power out of 5 candidates---the other candidates being number of letters, number of syllables, orthographic Levenshtein distance and phonological Levenshtein distance (see [\underline{Appendix A}](#appendix-A-lexical-covariates)).
-It should also be noted that word frequency has been found to be more closely related to semantic variables than to lexical ones, such as word length, orthography, phonology [see Table 4 in @yap2012a].
-
-Word frequency is also of interest due to its varying relationship to vocabulary size across different paradigms.
-@yap2012a found that higher-vocabulary participants in the ELP were more strongly influenced by word frequency than lower-vocabulary participants.
-The same finding also appeared in a lexical decision study in Chinese [@lim2020a].
-In contrast, deeper semantic tasks, such as semantic priming [@yap2017a] and semantic decision [@pexman2018a], have yielded the opposite pattern, with the effect of word frequency decreasing in higher-vocabulary participants.
-
-## Effects of interest
-
-- $Z$-scored vocabulary age [`z_vocabulary_age`; calculated from `vocabAge` in @balota2007a]
-
-- $Z$-scored, recoded participant's gender [`z_recoded_participant_gender`; calculated from `Gender` in @balota2007a]
-
-- $Z$-scored word frequency [`z_word_frequency`; calculated from `LgSUBTLWF` in @balota2007a]
-
-- $Z$-scored vision-based information in words [`z_visual_rating`; calculated from `Visual.mean` in @lynott2020a]
+Language-based information could be operationalised as one of several lexical variables.
+In the present study, word frequency was chosen as it had the largest effect size out of five candidates---the other candidates being number of letters, number of syllables, orthographic Levenshtein distance and phonological Levenshtein distance (see [\underline{Appendix A}](#appendix-A-lexical-covariates)).
+It should also be noted that word frequency has been found to be more closely related to semantic variables than to lexical ones, such as word length, orthography and phonology [see Table 4 in @yap2012a].
+Another noteworthy feature of word frequency how it relates to vocabulary size across different paradigms.
+In lexical decision, the effect of word frequency has been stronger in higher-vocabulary participants than in lower-vocabulary ones [@lim2020a; @yap2012a].
+In contrast, the opposite pattern has emerged in deeper semantic tasks, such as semantic priming [@yap2017a] and semantic decision [@pexman2018a].
+
+## Methods
+
+### Data set
 
@@
 
-# Calculate numbers to be reported in the paragraph below
-
-# Save number of participants and words
-lexicaldecision_number_participants = 
-  length(unique(lexicaldecision$Participant))
-
-lexicaldecision_number_words = length(unique(lexicaldecision$word))
+# Calculate some of the sample sizes to be reported in the paragraph below
 
@@
 
-The final data set contained `r lexicaldecision_number_participants` participants, `r lexicaldecision_number_words %>% formattable::comma(digits = 0)` words, and `r length(lexicaldecision$z_RT) %>% formattable::comma(digits = 0)` RTs.
+The data set was trimmed by removing rows that lacked values on any variable, and by also removing RTs that were more than 3 standard deviations away from the mean.
+The standard deviation trimming was performed within participants, as done in the English Lexicon Project [@balota2007a].
+The resulting data set contained `r length(unique(lexicaldecision$Participant))` participants, `r length(unique(lexicaldecision$word)) %>% formattable::comma(digits = 0)` words and `r length(lexicaldecision$z_RT) %>% formattable::comma(digits = 0)` RTs.
 On average, there were `r lexicaldecision_mean_words_per_participant` words per participant ($SD$ = `r lexicaldecision_SD_words_per_participant`), and conversely, `r lexicaldecision_mean_participants_per_word` participants per word ($SD$ = `r lexicaldecision_SD_participants_per_word`).
 
-Figure \@ref(fig:lexicaldecision-correlations) shows the zero-order correlations among the predictors and the dependent variable.
-
-```{r lexicaldecision-correlations, fig.cap = 'Zero-order correlations in the lexical decision study.', fig.width = 6, fig.height = 3.5, out.width = '50%'}
+Figure \@ref(fig:lexicaldecision-correlations) shows the correlations among the predictors and the dependent variable.
+
+```{r lexicaldecision-correlations, fig.cap = 'Zero-order correlations in the lexical decision study.', fig.width = 6, fig.height = 3.5, out.width = '52%'}
 
@@
 
-## Covariates
-
-The following lexical covariates were included in the model to allow a rigorous analysis of the effects of interest.
-
-- Lexical (see [\underline{Appendix A}](#appendix-A-lexical-covariates)): $Z$-scored orthographic Levenshtein distance [@balota2007a]
-
-- Semantic: $z$-scored word concreteness [@brysbaert2014a], used as a covariate of visual rating.
-
-### Diagnostics for the frequentist model
+### Variables
+
+While the variables are generally described in the [\underline{general introduction}](#present-studies), a few further details are provided below regarding some of them.
+
+- `Vocabulary age`: the present study uses the name vocabulary *age*, as used in the study of @balota2007a. It measures the same linguistic experience as vocabulary size.
+
+A few details regarding the covariates follow.
+
+- General cognition covariate: unlike in the two previous studies, the present study did not include a general cognition covariate as such a variable was not available in the data set of @balota2007a.
+
+- Lexical covariates (see preselection in [\underline{Appendix A}](#appendix-A-lexical-covariates)): `orthographic Levenshtein distance` [@balota2007a].
+
+- `Word concreteness` [@brysbaert2014a], used as a covariate of visual strength.
+
+### Diagnostics for the frequentist analysis
 
 The model presented convergence warnings.
-To avoid removing important random slopes, which could increase the Type I error [@brauer2018a; @singmann2019a], we examined the model after refitting it using seven optimization algorithms through the 'allFit' function of the 'lme4' package [@batesPackageLme42021].
-The results showed that all optimizers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential (Bates et al., 2021; see [\underline{Appendix B}](#appendix-B-frequentist-analysis-diagnostics)).
+To avoid removing important random slopes, which could increase the Type I error rate---i.e., false positives [@brauer2018a; @singmann2019a], we examined the model after refitting it using seven optimisation algorithms through the 'allFit' function of the 'lme4' package [@batesPackageLme42021].
+The results showed that all optimisers produced virtually identical means for all effects, suggesting that the convergence warnings were not consequential (Bates et al., 2021; see [\underline{Appendix B}](#appendix-B-frequentist-analysis-diagnostics)).
+
+```{r}
+
+# Calculate VIF for every predictor and return only the maximum VIF rounded up
+maxVIF_lexicaldecision = car::vif(lexicaldecision_lmerTest) %>% max %>% ceiling
+
+```
 
@@
 However, this is not likely to have posed a major problem, as mixed-effects models are fairly robust to deviations from normality [@kniefViolatingNormalityAssumption2021; @schielzethRobustnessLinearMixed2020].
+Last, the model did not present multicollinearity problems, with all VIFs below `r maxVIF_lexicaldecision` [see @dormannCollinearityReviewMethods2013; @harrison2018a].
+
+### Diagnostics for the Bayesian analysis
 
@@
 
-# Calculate VIF for every predictor and return only the maximum VIF rounded up
-maxVIF_lexicaldecision = car::vif(lexicaldecision_lmerTest) %>% max %>% ceiling
-
-```
-
-The model did not present multicollinearity problems, all VIFs being smaller than `r maxVIF_lexicaldecision` [@dormannCollinearityReviewMethods2013; @harrison2018a].
-
-### Diagnostics for the Bayesian model
-
-```{r}
-
 # Calculate number of post-warmup draws (as in 'brms' version 2.17.0).
-# Informative prior model used but same numbers in all three models.
+# Informative prior model used but numbers are identical in the three models.
 lexicaldecision_post_warmup_draws = 
@@
 
-# Next, find find maximum R-hat value for the random effects 
-# across the three models. 
+# Next, find find maximum R-hat value for the random effects across the three models
 lexicaldecision_randomeffects_max_Rhat = 
@@
 
-The maximum $\widehat R$ value for the fixed effects across the three models was `r lexicaldecision_fixedeffects_max_Rhat`, suggesting that these effects converged [@schootBayesianStatisticsModelling2021; @vehtariRanknormalizationFoldingLocalization2021].
+The maximum $\widehat R$ value for the fixed effects across the three models was `r lexicaldecision_fixedeffects_max_Rhat`, suggesting that these effects hadconverged [@schootBayesianStatisticsModelling2021; @vehtariRanknormalizationFoldingLocalization2021].
 For the random effects, the maximum $\widehat R$ value was `r lexicaldecision_randomeffects_max_Rhat`, barely exceeding the 1.01 threshold [@vehtariRanknormalizationFoldingLocalization2021].
 
-The posterior predictive checks were sound (see [\underline{Appendix C}](#appendix-C-Bayesian-analysis-diagnostics)).
-Furthermore, in the prior sensitivity analysis, the results were virtually identical with the three priors that were considered (to recall the priors, see Figure \@ref(fig:bayesian-priors) above; to view the results in detail, see [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results)).
-
-## Results
+The results of the posterior predictive checks were sound (see [\underline{Appendix C}](#appendix-C-Bayesian-analysis-diagnostics)), indicating that the posterior distributions were sufficiently consistent with the observed data.
+Furthermore, in the prior sensitivity analysis, the results were virtually identical with the three priors that were considered (refer to the priors in Figure \@ref(fig:bayesian-priors) above; to view the results in detail, see [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results)).
+
+## Results of Study 3
 
@@
 
-Table \@ref(tab:lexicaldecision-frequentist-model) presents the results of the frequentist model.
-The fixed effects explained `r Nakagawa2017_fixedeffects_R2_lexicaldecision_lmerTest` of the variance, and the random effects `r Nakagawa2017_randomeffects_R2_lexicaldecision_lmerTest` [@nakagawaCoefficientDeterminationR22017; for an explanation of this difference, see [\underline{Results of Study 1}](#semanticpriming-results)).
-Figure \@ref(fig:lexicaldecision-frequentist-bayesian-plot-weaklyinformativepriors-exgaussian) displays the frequentist estimates alongside the Bayesian estimates.
-The latter are from the weakly-informative prior model.
-The estimates of the two other models (i.e., with informative and diffuse priors, respectively) were virtually identical to these (see [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results)).
+Table \@ref(tab:lexicaldecision-frequentist-model) presents the results.
+The fixed effects explained `r Nakagawa2017_fixedeffects_R2_lexicaldecision_lmerTest` of the variance, and the random effects explained `r Nakagawa2017_randomeffects_R2_lexicaldecision_lmerTest` (Nakagawa et al., 2017; for an explanation of this difference, see [\underline{Results of Study 1}](#semanticpriming-results)).
+Word frequency produced a significant main effect, with higher values of variable facilitating participants' performance, as reflected in shorter RTs.
+None of the other effects of interest were significant.
+
+The effect size of word frequency was far larger than that of visual strength.
+Figure \@ref(fig:lexicaldecision-frequentist-bayesian-plot-weaklyinformativepriors-exgaussian) displays the frequentist and the Bayesian estimates, which are broadly similar.
+The Bayesian estimates are from the weakly-informative prior model.
+The estimates of the two other models, based on informative and diffuse priors, were virtually identical to these (see [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results)).
+
+\FloatBarrier
 
@@
   footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
-           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored variables; \\\\textit{SE} = standard error;',
+           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored predictors; \\\\textit{SE} = standard error;',
                            'CI = confidence interval. Shaded rows contain covariates. \\\\linebreak', 
@@
 
-```{r lexicaldecision-frequentist-bayesian-plot-weaklyinformativepriors-exgaussian, fig.cap = 'Estimates from the frequentist analysis (in red) and from the Bayesian analysis (in blue) for the lexical decision study.
-The frequentist means (represented by points) are flanked by 95\\% confidence intervals.
-The Bayesian means (represented by vertical lines) are flanked by 95\\% credible intervals, in light blue (in some cases, the interval is covered up by the bar of the mean).'}
+```{r lexicaldecision-frequentist-bayesian-plot-weaklyinformativepriors-exgaussian, fig.cap = 'Estimates for the lexical decision study.
+The frequentist means (represented by red points) are flanked by 95\\% confidence intervals.
+The Bayesian means (represented by blue vertical lines) are flanked by 95\\% credible intervals in light blue.'}
 
@@
 
-Figure \@ref(fig:lexicaldecision-interactions-with-vocabulary-age) presents the interactions of vocabulary age with word frequency and with visual strength, albeit non-significant.
-
-(ref:lexicaldecision-interactions-with-vocabulary-age) Interactions of vocabulary age with word frequency and visual strength.
-Vocabulary age is constrained to sextiles (six sections) in this plot, whereas in the statistical analysis it contained more values within the current range.
-*n* = number of participants contained between sextiles.
+Figure \@ref(fig:lexicaldecision-interactions-with-vocabulary-age) presents the interactions of vocabulary age with word frequency and with visual strength, both non-significant.
+Figure \@ref(fig:lexicaldecision-interactions-with-gender) shows the interactions with gender, both non-significant too.^[Further interaction plots available in [\underline{Appendix D}](#appendix-D-interaction-plots).]
+
+(ref:lexicaldecision-interactions-with-vocabulary-age) Interactions of vocabulary age with word frequency (panel a) and with visual strength (panel b).
+Vocabulary age is constrained to sextiles (6 sections) in this plot, whereas in the statistical analysis it contained more values within the current range.
+Sextiles were used because there was not enough data for deciles nor for octiles.
+$n$ = number of participants contained between sextiles.
 
@@
 
-Figure \@ref(fig:lexicaldecision-interactions-with-gender) shows the interactions of gender with language-based similarity and visual-strength difference, albeit non-significant.^[Plots of other interactions are available in [\underline{Appendix D}](#appendix-D-interaction-plots).]
-
-```{r lexicaldecision-interactions-with-gender, fig.cap = 'Interactions with gender in the lexical decision study.
-Gender was analysed using $z$-scores, but for clarity, the variable is shown in its basic form here.', out.width = '80%'}
+```{r lexicaldecision-interactions-with-gender, fig.cap = 'Interactions of gender with word frequency (panel a) and with visual strength (panel b) in the lexical decision study.
+Gender was analysed using $z$-scores, but for clarity, the basic labels are used in the legend.', out.width = '80%'}
 
@@
 
-Figures \@ref(fig:lexicaldecision-powercurve-plots-1-2-3) and \@ref(fig:lexicaldecision-powercurve-plots-4-5-6-7) show the estimated power available for main effects and interactions of interest, respectively.
+Figures \@ref(fig:lexicaldecision-powercurve-plots-1-2-3) and \@ref(fig:lexicaldecision-powercurve-plots-4-5-6-7) show the estimated power for some main effects and interactions of interest as a function of the number of participants.
+To plan the sample size for future studies, these results must be considered under the assumptions that the future study would apply a statistical method similar to ours---namely, a mixed-effects model with random intercepts and slopes---, and that the analysis would encompass at least as many words as the current study, namely, `r length(unique(lexicaldecision$word)) %>% formattable::comma(digits = 0)` (distributed in various blocks across participants, not all being presented to every participant).
+Furthermore, it is necessary to consider each figure in detail.
+Here, we provide a summary.
+First, detecting the main effect of word frequency would require 100 participants.
+Second, detecting the interactions of word frequency and visual strength with vocabulary size would require 1,500 participants.
+Third, detecting the other effects would require more than 2,000 participants.
 
@@
 
-_______ interpret ____________
-
-## Discussion
-
-___________________
-
-# General discussion
-
-In all three studies, the main effects and the interactions of language-based information were larger than those of vision-based information, consistent with previous research [...].
-Beyond that, the results revealed a dynamic process influenced by three levels of variation: participants, words and tasks.
-The associations that appeared across these levels revealed the roles of language-based and vision-based mechanisms in conceptual processing.
+## Discussion of Study 3
+
+In the present study, we have delved into a task that is likely to elicit a shallower level of semantic processing than the tasks from the previous studies.
+Furthermore, the data set used in this study was considerably smaller (`r length(lexicaldecision$z_RT) %>% formattable::comma(digits = 0)` RTs, compared to `r length(semanticpriming$z_target.RT) %>% formattable::comma(digits = 0)` RTs in Study 1 and `r length(semanticdecision$z_RTclean) %>% formattable::comma(digits = 0)` in Study 2).
+The relatively small size of the data set of Study 3 was due to the small number of words per participant ($M$ = `r lexicaldecision_mean_words_per_participant`) and participants per word ($M$ = `r lexicaldecision_mean_participants_per_word` participants per word).
+In this regard, the English Lexicon Project [@balota2007a] prioritised the total number of words included in their archive.
+
+While the covariates presented large effects, none of the effects of interest turned out to be significant or noteworthy.
+Furthermore, he comparison with the two previous tasks is hindered by the major difference in the size of the data sets.
+Therefore, while it is reasonable to find smaller semantic effects in the lexical decision task than in the other two, we cannot reliably attribute this difference to the nature of the task.
+
+As a minor suggestion, future studies could operationalise language using a measure of orthographic neighbourhood size (e.g., orthographic Levenshtein distance), instead of using word frequency as in the present study.
+While we used word frequency guided by a data-driven selection (see Appendix A), neighbourhood size is a measure created for the purpose of indexing word co-occurrence where only one word is directly available to the researcher [@suarezObservingNeighborhoodEffects2011; @yapVisualWordRecognition2009].
+
+### Statistical power analysis
+
+We analysed the statistical power associated with several effects of interest, across various sample sizes.
+The results of this power analysis can help determine the number of participants required to reliably examine each of these effects in a future study.
+Importantly, the results assume two conditions.
+First, the future study would apply a statistical method similar to ours---namely, a mixed-effects model with random intercepts and slopes.
+Second, the analysis of the future study would encompass at least `r length(unique(lexicaldecision$word)) %>% formattable::comma(digits = 0)` stimulus words (distributed in various blocks across participants, not all being presented to every participant).
+
+The results revealed that detecting the main effect of word frequency would require 100 participants. In contrast, detecting the other effects would require more than 2,000 participants.
+
+# General discussion of Study 2
+
+In the present study, we have revisited three existing data sets in conceptual processing to investigate the interplay between language-based and vision-based information.
+Specifically, we have investigated how this interplay is modulated by individual differences in vocabulary size, by the linguistic and visual information contained in words, and by contextual demands such as semantic depth and presentation speed.
+Although both language and vision played significant roles in some contexts (detailed below), the main effects and the interactions of language-based information were larger than those of vision-based information, consistent with previous research [@banksLinguisticDistributionalKnowledge2021; @kiela2014a; @louwerse2015a; @lam2015a; @pecherDoesPizzaPrime1998; @petilli2021a].
+
+In our current approach, the sensorimotor domain was represented by a single variable in each study, just as the language domain was represented by a single variable.
+In the sensorimotor domain, we focussed on the vision to its hegemonic role in the human brain [@reillyEnglishLexiconMirrors2020] as well as in several languages [@bernabeuDutchModalityExclusivity2018; @chenMandarinChineseModality2019; @miceliPerceptualInteroceptiveStrength2021; @morucciAugmentedModalityExclusivity2019; @roqueVisionVerbsDominate2015; @speedDutchSensoryModality2021; @speedGroundingLanguageNeglected2020; @lynott2020a; @vergallitoPerceptualModalityNorms2020; @winterVisionDominatesPerceptual2018; @zhongSensorimotorNormsChinese2022].
+Notably, vision was also the domain chosen in a recent study that strongly influenced the present study [@petilli2021a], as well as in previous studies [@bottiniConcretenessAdvantageLexical2021; @dedeyneVisualAffectiveMultimodal2021; @pearsonHeterogeneityMentalRepresentation2015; @yeeColorlessGreenIdeas2012].
+In contrast to this parsimonious approach, more comprehensive alternatives could be used in future research to consider more sensorimotor domains.
+The first of these approaches is the preselection approach, which incorporates a step prior to the main analysis.
+In this prior step, a selection is performed among a large variety of word-level information, including visual, auditory and motor information, etc.
+[@bernabeu2021a].
+Selecting a single variable provides a convenient way to compare the role of sensorimotor information to that of linguistic information, if the latter is also represented by a single variable.
+The second approach is using a variable that aggregates sensorimotor information [@wingfieldSensorimotorDistanceGrounded2022].
+Last, the third approach would be using more than one variable to represent sensorimotor information in the main analysis.
+This would complicate the analysis of interactions with other variables, as the overall number of terms in the model could quickly exceed the maximum normally encountered in mixed-effects models---that is, around 15.
+If random slopes are included for all those effects of interest [see @brauer2018a; @singmann2019a], the model would most likely present convergence warnings.
+In the face of this challenge, authors could either probe into those warnings (see [\underline{Appendix B}](#appendix-B-frequentist-analysis-diagnostics)), or could opt for different method, such as linear regression or machine learning.
+Ultimately, in any selection of variables, there is a trade-off between parsimony and comprehensiveness, and negotiating this trade-off often involves a certain degree of arbitrariness.
+A time-consuming, stepwise selection can help reduce this arbitrariness (for an example, see [\underline{Appendix A}](#appendix-A-lexical-covariates)).
+
+Insofar as both 'language' and 'vision' were present in the models, it is (arguably) valid to make conclusions based on them [see @louwerseSymbolInterdependencySymbolic2011; @louwerseTasteWordsLinguistic2011; @santosPropertyGenerationReflects2011; @simmonsFMRIEvidenceWord2008].
+In contrast, when only one of these variables is analysed, it may contain information from the other variable.
+If the superiority of language is genuine---rather than due to a bogus reflection of sensorimotor information---, the present results suggest that language is the main source of information in conceptual processing, whereas sensorimotor information provides extra help, especially for higher-vocabulary individuals (see Study 2, Semantic decision) and in deeper semantic tasks (refer to task-relevance advantage above).
+As the ultimate conclusion, should sensorimotor simulation be considered smaller but nonetheless important---especially for some individuals and in some contexts---, or should it be considered a negligible by-product of conceptual processing [@mahonCriticalLookEmbodied2008]?
+Although the jury is still out, the present results provide support for the tenet that sensorimotor simulation is smaller yet important, especially for some individuals and in some contexts, whereas language is important across the board.
+
+Furthermore, it is necessary to acknowledge a longstanding caveat in the present topic, which also affects the present study.
+That is, it is extremely difficult to ascertain whether our variables encode what we intend for them to encode.
+Specifically, it is possible that the variables for language-based information encode some sensorimotor information, and vice versa.
+To address this caveat, future research could combine the use of continuous word-level variables---as used in the present study---with the use of brain-level measurements [see @borghesaniWordMeaningVentral2016].
+Specifically, such an investigation should examine whether language-based information is primarily circumscribed to the brain regions in charge of semantic retrieval---such as the posterior left inferior frontal gyrus, the right posterior inferior frontal gyrus, the left anterior superior temporal gyrus and sulcus, and the left middle and posterior middle temporal gyrus [@hagoortCoreLanguagereadyBrain2017; @skeideOntogenyCorticalLanguage2016].
+Conversely, this investigation should also examine whether vision-based information is primarily circumscribed to the brain regions in charge of visual semantic information---such as Brodmann area 17, in the occipital lobe, corresponding to primary visual cortex [@borghesaniWordMeaningVentral2016].
+Due to the importance of the time course, a method that provides both spatial and temporal resolution, such as magnetoencephalography, would be ideally suited for this research.
+If both sources of information are largely circumscribed to their regions of interest in the brain, we could conclude that the variables are valid.
+In contrast, if there are *drifts* in the processing---whereby language-based information is consistently associated with activation in primary visual cortex, or whereby vision-based information is associated with activation in the language regions of interest---, we would need to question the validity of the variables.
+
+As an alternative to the above design, a thriftier method would be available by using two clusters of covariates.
+One of these clusters would be primarily associated with language-based information, whereas the other cluster would be primarily associated with vision-based information.^[Thank you to Prof.
+Max Louwerse for suggesting this idea.] This research should examine whether the variables in each cluster all behave similarly, or whether---instead---there are any drifts between the language and vision.
+As in the above design, the absence of drifts would validate the operationalisation of the two sides in the dichotomy, whereas the presence of drifts would question the validity.
+
+The present analysis controlled important sources of variance in the fixed effects and in the random effects.
+First, in the fixed effects, covariates such as word concreteness and individual differences in general cognition were included in the models.
+It was important to include these covariates as they were substantially correlated with some of our variables of interest, and research has suggested that these covariates may represent fundamentally different processes from those of our variables of interest.
+For instance, word concreteness and visual strength were highly correlated.
+However, whereas visual strength indexes a perceptual component of semantic information, word concreteness might be circumscribed to the lexical level, which does not require the processing of meaning [@bottiniConcretenessAdvantageLexical2021; cf.
+@connellStrengthPerceptualExperience2012; @pexman2018a].
+Similarly, it was important to control for individual differences in general cognition measures as covariates of vocabulary size [@ratcliff2010a; also see @james2018a; @pexman2018a].
+We contend that controlling (or, in other words, statistically adjusting) for important covariates is a valuable asset of our present research.
+Furthermore, we think that the number of covariates we selected was enough but not excessive.
+We did not find any signs of overfitting in the models, as the variables that have been consistently influential in the literature were also influential in our current models.
+To further delve into the role of covariates in conceptual processing, we think that it would be valuable to investigate how the presence and the absence of several covariates in a model can affect the effect sizes and the significance results.^[Thank you to Prof.
+Max Louwerse for this idea.] Indeed, the differences between the results of Study 1 (semantic priming) and the results of @petilli2021a suggested that the influence of covariates can be very important.
+However, because these analyses differed in other aspects of the models, a study focussed on covariates would be insightful [see @botvinik-nezerVariabilityAnalysisSingle2020; @perretWhichVariablesShould2019; @wagenmakersOneStatisticalAnalysis2022].
+
+Second, in the random effects, the models contained a maximal structure that accounted for far more variance than the fixed effects, thus providing for a conservative analysis.
+Indeed, the maximal random-effects structure served to impede a violation of the independence of observations [@barrRandomEffectsStructure2013; @brauer2018a; @singmann2019a].
+Specifically, random intercepts and slopes ensured that sources of dependence such as participants and stimuli were kept outside of the fixed effects, which are the relevant effects for the conclusions of this (and most other) research in conceptual processing.
 
@@
 This converges with previous findings suggesting that higher and lower-vocabulary participants are affected by different variables.
-Potentially, the variables affecting higher-vocabulary participants are more relevant to the task [@lim2020a; @pexman2018a; @yap2012a; @yap2017a].
-
-## Differences between measurement instruments and the associated risks
-
-We also compared two measures of visual priming.
-The first measure was operationalised as the difference in visual strength [@lynott2020a] between the prime and the target word in each trial.
-The second measure, created by [@petilli2021a], was based on vector representations trained on images.
-The results revealed that the visual strength measure was significantly superior in explaining RTs.
-This difference was not due to an excessive collinearity between these measures ($r$ = .02).
-Also importantly, both measures appeared to be valid based on their correlations with language-based similarity and with word concreteness.
-
-If we indeed accept that both the above measures were valid, we must reflect on the possibility that measurement instruments create confounds when different systems are compared.
-That is, in the case of linguistic and embodied processing, the large difference between the effect sizes of these systems---found in the three current studies and in the previous literature [...]---would not be trustworthy if the instruments that were used to measure the language system were far more precise than the instruments used to measure the embodiment system.
-In this sense, consider how variables are refined in research: it is done by comparing the performance of different variables.
-Critically, the literature seems to contain many comparisons of text-based variables, some dating from the 1990s [@jones2006a; @lund1996a; @mikolovEfficientEstimationWord2013; @dedeyneBetterExplanationsLexical2013; @de2016a; @guenther2016a; @guntherLatentSemanticAnalysis2016; @wingfieldUnderstandingRoleLinguistic2022].
-In contrast, the work on embodiment variables began more than a decade afterwards, and this work has been more concerned with comparisons of different *modalities*---e.g., valence, visual strength, auditory strength, etc.
-[@lynott2020a; @lynottModalityExclusivityNorms2009; @newcombeEffectsEmotionalSensorimotor2012].
-Thus, this historical accident could account for a portion of the superiority of linguistic information over embodied information [as found in @lam2015a; @pecherDoesPizzaPrime1998; @petilli2021a; @banksLinguisticDistributionalKnowledge2021; @kiela2014a; @louwerse2015a].
-
-The case of different measurement instruments is one of several factors that can exert a great influence in analyses.
-In the medium term, it may pay dividends to devote more work to comparing different instruments and, more generally, different analyses [see @barsalouEstablishingGeneralizableMechanisms2019; @botvinik-nezerVariabilityAnalysisSingle2020; @wagenmakersOneStatisticalAnalysis2022].
+In this regard, some research has suggested that the variables affecting higher-vocabulary participants most are especially relevant to the task [@lim2020a; @pexman2018a; @yap2012a; @yap2017a].
+Our results were consistent with the 'task-relevance advantage' associated with greater vocabulary knowledge.
+Specifically, in lexical decision, higher-vocabulary participants were more sensitive than lower-vocabulary participants to language-based information.
+In contrast, in semantic decision, higher-vocabulary participants were more sensitive to word concreteness.
+In summary, the present findings suggest that greater linguistic experience may be associated with greater task adaptabiity during cognitive performance, with better comprehenders able to selectively attend to task-relevant features compared to poorer comprehenders [@lim2020a; @pexman2018a].
+
+In addition, the semantic priming paradigm analysed in Study 1 revealed that both language and vision were more important with the short SOA (200 ms) than with the long SOA (1,200 ms).
+This finding replicates some of the previous literature [@petilli2021a] while highlighting the importance of the time course and the level of semantic processing.
+That is, although the finding seems to be at odds with the theory that perceptual simulation peaks after language-based associations [@barsalouLanguageSimulationConceptual2008; @louwerseTasteWordsLinguistic2011], the long SOA may have been too long for perceptual simulation to be maintained in the lexical decision task that was performed by participants, which is semantically shallow [@petilli2021a].
+
+## Operationalisation of variables and other analytical choices
+
+We compared two measures of vision-based priming.
+The first measure---`visual-strength difference`---was operationalised as the difference in visual strength [@lynott2020a] between the prime word and the target word in each trial.
+The second measure---`vision-based similarity`---, created by @petilli2021a, was based on vector representations trained on images.
+The results revealed that both measures---including their interactions with other variables---produced similar effect sizes.
+This underscores the consistency that exists between human ratings and computational approximations to meaning [e.g., @charbonnierPredictingWordConcreteness2019; @charbonnierPredictingConcretenessGerman2020; @guenther2016a; @louwerse2015a; @mandera2017a; @petilli2021a; @solovyevConcretenessAbstractnessConcept2021; @wingfieldUnderstandingRoleLinguistic2022].
+However, the effect of the human-based variable was slightly larger, which is consistent with previous comparisons of human-based and computational measures [@de2016a; @de2019a; @gagneProcessingEnglishCompounds2016; @schmidtke2018a; cf.
+@michaelovClozeFarN4002022; @snefjella2020a].
+
+In contrast to the results of @petilli2021a, vision-based similarity did not significantly interact with SOA.
+Furthermore, in contrast to the main analysis, this sub-analysis did not present a significant interaction between language-based similarity and SOA.
+These two differences demonstrate how the results of our analyses can be critically influenced by analytical choices such as the operationalisation of variables and the degree of complexity of statistical models.
+In this regard, we must draw attention to an often-overlooked difference between the variables used to operationalise the language system---usually, text-based measures based on large corpora---and the variables used to operationalise the embodiment system---usually, human-based measures based on ratings.
+Critically, the literature contains many comparisons of text-based variables [@jones2006a; @lund1996a; @mandera2017a; @mikolovEfficientEstimationWord2013; @dedeyneBetterExplanationsLexical2013; @de2016a; @guenther2016a; @guntherLatentSemanticAnalysis2016; @wingfieldUnderstandingRoleLinguistic2022], whereas the work on embodiment variables is more sparse and tends to compare different *modalities*---e.g., valence, visual strength, auditory strength, etc.
+[@lynott2020a; @lynottModalityExclusivityNorms2009; @newcombeEffectsEmotionalSensorimotor2012; for an exception, see @vergallitoPerceptualModalityNorms2020].
+This accident of history might in part account for the superiority of linguistic information over embodied information [see @banksLinguisticDistributionalKnowledge2021; @kiela2014a; @louwerse2015a; @lam2015a; @pecherDoesPizzaPrime1998; @petilli2021a].
+Therefore, it may be important to consider whether *engineering work* should be devoted to the betterment of embodiment variables.
+On a more general conclusion, the present results suggest that research findings are fundamentally dependent on research methods.
 
@@
 
-Power analyses were performed to _____________________.
-_______________________.
-The sample sizes required for some of the effects are not easily feasible with the usual distribution of funding in psychological research projects.
+Power analyses were performed to estimate the sample sizes required to reliably investigate a range of effects.
+The results suggested that 300 participants were sufficient to examine the effect of language-based information contained in words, whereas more than 1,000 participants were necessary for the effect of vision-based information and for the interactions of both former variables with vocabulary size, gender and presentation speed.
+Regarding interactions specifically, The large sample sizes required to investigate some of the effects relevant to embodied cognition and individual differences are not easily attainable with the usual organisation of funding in Psychology and Neuroscience.
 

### 2022-10-24 manuscript/manuscript.tex
24102022

@@
 We performed the analysis using mixed-effects models that included a comprehensive array of fixed effects---including covariates---and random effects.
-First, we found that language-based information was found to be more important than vision-based information.
+First, we found that language-based information was more important than vision-based information.
 Second, in the semantic priming study---whose task required distinguishing between words and nonwords---, both language-based and vision-based information were more influential when words were presented faster.
@@
 Last, we estimated the sample size required to reliably investigate various effects.
-We found that 300 participants were sufficient to examine the effect of language-based information contained in words, whereas more than 1,000 participants were necessary for the effect of vision-based information and for the interactions of both former variables with vocabulary size, gender and presentation speed.
-In conclusion, this power analysis reveals the need to increase sample sizes for research on perceptual simulation and individual differences.
+We found that 300 participants were sufficient to examine the effect of language-based information contained in words, whereas more than 1,000 participants were necessary to examine the effect of vision-based information and the interactions of both former variables with vocabulary size, gender and presentation speed.
+In conclusion, this power analysis reveals the need to increase sample sizes when conducting research on perceptual simulation and individual differences.
 }
@@
 
-We entertained two hypothesis regarding the interaction between language-based information and participants' gender: (a) that the language system would be more important in female participants than in males (Burman et al., 2008; Hutchinson \& Louwerse, 2013; Jung et al., 2019; Ullman et al., 2008), and (b) that this interaction effect would be absent, as a recent review suggested that gender differences are negligible in the general population (Wallentin, 2020).
+We entertained two hypotheses regarding the interaction between language-based information and participants' gender: (a) that the language system would be more important in female participants than in males (Burman et al., 2008; Hutchinson \& Louwerse, 2013; Jung et al., 2019; Ullman et al., 2008), and (b) that this interaction effect would be absent, as a recent review suggested that gender differences are negligible in the general population (Wallentin, 2020).
 
@@
 To our knowledge, no previous studies have investigated the interaction between vision-based information and participants' gender.
-We entertained two hypothesis.
+We entertained two hypotheses.
 Our first hypothesis was that this interaction would stand opposite to the interaction between language and gender.

### 2022-10-29 manuscript/manuscript.Rmd
22102022

@@
 We found that 300 participants were sufficient to examine the effect of language-based information contained in words, whereas more than 1,000 participants were necessary to examine the effect of vision-based information and the interactions of both former variables with vocabulary size, gender and presentation speed.
-In conclusion, this power analysis reveals the need to increase sample sizes when conducting research on perceptual simulation and individual differences.
-
-keywords: conceptual processing, semantic priming, semantic decision, lexical decision, language, vision, vocabulary size, statistical power
+In conclusion, this power analysis suggests that larger sample sizes are necessary to investigate perceptual simulation and individual differences in conceptual processing.
+
+keywords: conceptual processing, replication, object orientation effect, semantic priming, semantic decision, lexical decision, language, visual strength, vocabulary size, statistical power
 
@@
 library(stringr)      # Text processing
+library(car)          # Analysis
+library(lmerTest)     # Analysis
+library(simr)         # Analysis
 library(ggplot2)      # Plots
+library(ggridges)     # Plots
+library(ggtext)       # Plots
 library(GGally)       # Correlation plots

### 2022-10-29 manuscript/manuscript.Rmd
29102022

@@
 library(dplyr)        # Data wrangling
+library(reshape2)     # Data wrangling
 library(formattable)  # Format numbers

### 2022-10-29 manuscript/manuscript.tex
29102022

@@
 {}{\PatchFailed}
-\keywords{conceptual processing, semantic priming, semantic decision, lexical decision, language, vision, vocabulary size, statistical power}
+\keywords{conceptual processing, replication, object orientation effect, semantic priming, semantic decision, lexical decision, language, visual strength, vocabulary size, statistical power}
 \usepackage{csquotes}
@@
   pdflang={en-EN},
-  pdfkeywords={conceptual processing, semantic priming, semantic decision, lexical decision, language, vision, vocabulary size, statistical power},
+  pdfkeywords={conceptual processing, replication, object orientation effect, semantic priming, semantic decision, lexical decision, language, visual strength, vocabulary size, statistical power},
   hidelinks,
@@
 We found that 300 participants were sufficient to examine the effect of language-based information contained in words, whereas more than 1,000 participants were necessary to examine the effect of vision-based information and the interactions of both former variables with vocabulary size, gender and presentation speed.
-In conclusion, this power analysis reveals the need to increase sample sizes when conducting research on perceptual simulation and individual differences.
+In conclusion, this power analysis suggests that larger sample sizes are necessary to investigate perceptual simulation and individual differences in conceptual processing.
 }
@@
 
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/bayesian_priors/plots/bayesian_priors}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/bayesian_priors/plots/bayesian_priors}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_bayesian_plots/plots/semanticpriming_frequentist_bayesian_plot_weaklyinformativepriors_exgaussian}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticpriming/frequentist_bayesian_plots/plots/semanticpriming_frequentist_bayesian_plot_weaklyinformativepriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=0.85\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-vocabulary-size}
+{\centering \includegraphics[width=0.85\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-vocabulary-size}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-SOA}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-SOA}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-gender}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-gender}
 
@@
 
-{\centering \includegraphics[width=0.89\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/analysis_with_visualsimilarity/plots/semanticpriming_with_visualsimilarity_confidence_intervals_plot}
+{\centering \includegraphics[width=0.89\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticpriming/analysis_with_visualsimilarity/plots/semanticpriming_with_visualsimilarity_confidence_intervals_plot}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/power_analysis/plots/semanticpriming_powercurve_plots_1_2_3}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticpriming/power_analysis/plots/semanticpriming_powercurve_plots_1_2_3}
 
@@
 
-{\centering \includegraphics[width=0.92\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/power_analysis/plots/semanticpriming_powercurve_plots_4_5_6_7_8_9}
+{\centering \includegraphics[width=0.92\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticpriming/power_analysis/plots/semanticpriming_powercurve_plots_4_5_6_7_8_9}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/plots/semanticdecision_confidence_intervals_plot}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticdecision/frequentist_analysis/plots/semanticdecision_confidence_intervals_plot}
 
@@
 
-{\centering \includegraphics[width=0.98\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/plots/semanticdecision-interactions-with-vocabulary-size}
+{\centering \includegraphics[width=0.98\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticdecision/frequentist_analysis/plots/semanticdecision-interactions-with-vocabulary-size}
 
@@
 
-{\centering \includegraphics[width=0.98\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/plots/semanticdecision-interactions-with-gender}
+{\centering \includegraphics[width=0.98\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticdecision/frequentist_analysis/plots/semanticdecision-interactions-with-gender}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/power_analysis/plots/semanticdecision_powercurve_plots_1_2_3}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticdecision/power_analysis/plots/semanticdecision_powercurve_plots_1_2_3}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/power_analysis/plots/semanticdecision_powercurve_plots_4_5_6_7}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticdecision/power_analysis/plots/semanticdecision_powercurve_plots_4_5_6_7}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_bayesian_plots/plots/lexicaldecision_frequentist_bayesian_plot_weaklyinformativepriors_exgaussian}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/lexicaldecision/frequentist_bayesian_plots/plots/lexicaldecision_frequentist_bayesian_plot_weaklyinformativepriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/plots/lexicaldecision-interactions-with-vocabulary-age}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/lexicaldecision/frequentist_analysis/plots/lexicaldecision-interactions-with-vocabulary-age}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/plots/lexicaldecision-interactions-with-gender}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/lexicaldecision/frequentist_analysis/plots/lexicaldecision-interactions-with-gender}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/power_analysis/plots/lexicaldecision_powercurve_plots_1_2_3}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/lexicaldecision/power_analysis/plots/lexicaldecision_powercurve_plots_1_2_3}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/power_analysis/plots/lexicaldecision_powercurve_plots_4_5_6_7}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/lexicaldecision/power_analysis/plots/lexicaldecision_powercurve_plots_4_5_6_7}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/model_diagnostics/plots/main_effects_semanticpriming_allFit_convergence}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticpriming/frequentist_analysis/model_diagnostics/plots/main_effects_semanticpriming_allFit_convergence}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/model_diagnostics/plots/interactions_semanticpriming_allFit_convergence}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticpriming/frequentist_analysis/model_diagnostics/plots/interactions_semanticpriming_allFit_convergence}
 
@@
 
-{\centering \includegraphics[width=0.65\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/model_diagnostics/plots/semanticpriming_residuals}
+{\centering \includegraphics[width=0.65\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticpriming/frequentist_analysis/model_diagnostics/plots/semanticpriming_residuals}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/analysis_with_visualsimilarity/model_diagnostics/plots/main_effects_semanticpriming_with_visualsimilarity_allFit_convergence}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticpriming/analysis_with_visualsimilarity/model_diagnostics/plots/main_effects_semanticpriming_with_visualsimilarity_allFit_convergence}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/analysis_with_visualsimilarity/model_diagnostics/plots/interactions_semanticpriming_with_visualsimilarity_allFit_convergence}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticpriming/analysis_with_visualsimilarity/model_diagnostics/plots/interactions_semanticpriming_with_visualsimilarity_allFit_convergence}
 
@@
 
-{\centering \includegraphics[width=0.65\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/analysis_with_visualsimilarity/model_diagnostics/plots/semanticpriming_with_visualsimilarity_residuals}
+{\centering \includegraphics[width=0.65\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticpriming/analysis_with_visualsimilarity/model_diagnostics/plots/semanticpriming_with_visualsimilarity_residuals}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/model_diagnostics/plots/main_effects_semanticdecision_allFit_convergence}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticdecision/frequentist_analysis/model_diagnostics/plots/main_effects_semanticdecision_allFit_convergence}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/model_diagnostics/plots/interactions_semanticdecision_allFit_convergence}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticdecision/frequentist_analysis/model_diagnostics/plots/interactions_semanticdecision_allFit_convergence}
 
@@
 
-{\centering \includegraphics[width=0.65\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/model_diagnostics/plots/semanticdecision_residuals}
+{\centering \includegraphics[width=0.65\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticdecision/frequentist_analysis/model_diagnostics/plots/semanticdecision_residuals}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/model_diagnostics/plots/main_effects_lexicaldecision_allFit_convergence}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/lexicaldecision/frequentist_analysis/model_diagnostics/plots/main_effects_lexicaldecision_allFit_convergence}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/model_diagnostics/plots/interactions_lexicaldecision_allFit_convergence}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/lexicaldecision/frequentist_analysis/model_diagnostics/plots/interactions_lexicaldecision_allFit_convergence}
 
@@
 
-{\centering \includegraphics[width=0.65\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/model_diagnostics/plots/lexicaldecision_residuals}
+{\centering \includegraphics[width=0.65\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/lexicaldecision/frequentist_analysis/model_diagnostics/plots/lexicaldecision_residuals}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_informativepriors}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_informativepriors}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_weaklyinformativepriors}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_weaklyinformativepriors}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_diffusepriors}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_diffusepriors}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_informativepriors_exgaussian}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_informativepriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_weaklyinformativepriors_exgaussian}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_weaklyinformativepriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_diffusepriors_exgaussian}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticpriming/bayesian_analysis/prior_predictive_checks/plots/semanticpriming_priorpredictivecheck_diffusepriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/bayesian_analysis/posterior_predictive_checks/plots/semanticpriming_posteriorpredictivechecks_allpriors_exgaussian}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticpriming/bayesian_analysis/posterior_predictive_checks/plots/semanticpriming_posteriorpredictivechecks_allpriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_informativepriors}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_informativepriors}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_weaklyinformativepriors}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_weaklyinformativepriors}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_diffusepriors}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_diffusepriors}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_informativepriors_exgaussian}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_informativepriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_weaklyinformativepriors_exgaussian}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_weaklyinformativepriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_diffusepriors_exgaussian}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticdecision/bayesian_analysis/prior_predictive_checks/plots/semanticdecision_priorpredictivecheck_diffusepriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/bayesian_analysis/posterior_predictive_checks/plots/semanticdecision_posteriorpredictivechecks_allpriors_exgaussian}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticdecision/bayesian_analysis/posterior_predictive_checks/plots/semanticdecision_posteriorpredictivechecks_allpriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_informativepriors}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_informativepriors}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_weaklyinformativepriors}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_weaklyinformativepriors}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_diffusepriors}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_diffusepriors}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_informativepriors_exgaussian}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_informativepriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_weaklyinformativepriors_exgaussian}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_weaklyinformativepriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_diffusepriors_exgaussian}
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/lexicaldecision/bayesian_analysis/prior_predictive_checks/plots/lexicaldecision_priorpredictivecheck_diffusepriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/bayesian_analysis/posterior_predictive_checks/plots/lexicaldecision_posteriorpredictivechecks_allpriors_exgaussian}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/lexicaldecision/bayesian_analysis/posterior_predictive_checks/plots/lexicaldecision_posteriorpredictivechecks_allpriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=0.85\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-attentional-control}
+{\centering \includegraphics[width=0.85\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticpriming/frequentist_analysis/plots/semanticpriming-interactions-with-attentional-control}
 
@@
 
-{\centering \includegraphics[width=0.7\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interaction-word-concreteness-difference-SOA}
+{\centering \includegraphics[width=0.7\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticpriming/frequentist_analysis/plots/semanticpriming-interaction-word-concreteness-difference-SOA}
 
@@
 
-{\centering \includegraphics[width=0.9\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interaction-word-concreteness-difference-vocabulary-size}
+{\centering \includegraphics[width=0.9\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticpriming/frequentist_analysis/plots/semanticpriming-interaction-word-concreteness-difference-vocabulary-size}
 
@@
 
-{\centering \includegraphics[width=0.7\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_analysis/plots/semanticpriming-interaction-word-concreteness-difference-gender}
+{\centering \includegraphics[width=0.7\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticpriming/frequentist_analysis/plots/semanticpriming-interaction-word-concreteness-difference-gender}
 
@@
 
-{\centering \includegraphics[width=0.95\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_analysis/plots/semanticdecision-interactions-with-information-uptake}
+{\centering \includegraphics[width=0.95\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticdecision/frequentist_analysis/plots/semanticdecision-interactions-with-information-uptake}
 
@@
 
-{\centering \includegraphics[width=0.9\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/plots/lexicaldecision-interaction-word-concreteness-vocabulary-age}
+{\centering \includegraphics[width=0.9\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/lexicaldecision/frequentist_analysis/plots/lexicaldecision-interaction-word-concreteness-vocabulary-age}
 
@@
 
-{\centering \includegraphics[width=0.65\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_analysis/plots/lexicaldecision-interaction-word-concreteness-gender}
+{\centering \includegraphics[width=0.65\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/lexicaldecision/frequentist_analysis/plots/lexicaldecision-interaction-word-concreteness-gender}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticpriming/frequentist_bayesian_plots/plots/semanticpriming_frequentist_bayesian_plot_allpriors_exgaussian}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticpriming/frequentist_bayesian_plots/plots/semanticpriming_frequentist_bayesian_plot_allpriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/semanticdecision/frequentist_bayesian_plots/plots/semanticdecision_frequentist_bayesian_plot_allpriors_exgaussian}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/semanticdecision/frequentist_bayesian_plots/plots/semanticdecision_frequentist_bayesian_plot_allpriors_exgaussian}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Pablo/Documents/semanticpriming-semanticdecision-lexicaldecision/lexicaldecision/frequentist_bayesian_plots/plots/lexicaldecision_frequentist_bayesian_plot_allpriors_exgaussian}
+{\centering \includegraphics[width=1\linewidth]{C:/Users/pbe044/Documents/osf.io-ueryq/lexicaldecision/frequentist_bayesian_plots/plots/lexicaldecision_frequentist_bayesian_plot_allpriors_exgaussian}
 

### 2022-11-04 manuscript/manuscript.Rmd
typo busting

@@
 
-While the variables are generally described in the [\underline{general introduction}](#present-studies), a few further details are provided below regarding two of them.
+While the variables are outlined in the [\underline{general introduction}](#present-studies), a few further details are provided below regarding some of them.
 
@@
 
-While the variables are generally described in the [\underline{general introduction}](#present-studies), a few further details are provided below regarding some of them.
+While the variables are outlined in the [\underline{general introduction}](#present-studies), a few further details are provided below regarding some of them.
 

### 2022-11-04 manuscript/manuscript.tex
typo busting

@@
 
-While the variables are generally described in the \protect\hyperlink{present-studies}{\underline{general introduction}}, a few further details are provided below regarding two of them.
+While the variables are outlined in the \protect\hyperlink{present-studies}{\underline{general introduction}}, a few further details are provided below regarding some of them.
 
@@
 
-While the variables are generally described in the \protect\hyperlink{present-studies}{\underline{general introduction}}, a few further details are provided below regarding some of them.
+While the variables are outlined in the \protect\hyperlink{present-studies}{\underline{general introduction}}, a few further details are provided below regarding some of them.
 
